### 2020-10-08 input/abstract.tex
initialize

\begin{abstract}

\TODO{Locating the closest copy of a specific content across a
  distributed infrastructure requires to keep up-to-date an index of
  all replicas and their respective locations. Existing methods mostly
  rely on an external service to store this index, either on a
  centralized server or using a Distributed Hash Table (DHT). However,
  contacting a remote node to obtain localization information
  contradicts with emerging Fog infrastructures in terms of locality
  and robustness. In this paper, we present $A^3$, an epidemic
  protocol that will efficiently inform the relevant nodes about the
  presence of replicas in their neighborhood. Upon the exchange of
  messages, each node maintains a personalized index that will
  eventually contain the location of the closest copy for each object
  according to its place in the network topology. We implemented $A^3$
  and deployed it on a dedicated testbed with real-world
  topologies. Experimental results show that the time to retrieve
  objects is significantly decreased from 10\% up to 60\%, when
  compared to a DHT-based localization service.}

\end{abstract}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2020-10-08 input/background.tex
initialize

\section{Background and motivation}
\label{sec:background}

Fog infrastructures are distributed systems comprising heterogeneous
machines interconnected by communication links.

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ij}$ with $i, j \in V$.
\end{definition}

\begin{definition}[Logical partitions]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition.
\end{definition}

\TODO{Multiple destinations shortest path \REF}.

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Adding partitions by Process $p$.}
\end{algorithm}

Algorithm~\ref{algo:add} shows the instructions of dynamic
partitioning where the only operation available to processes is the
adding of a partition.  Line~\ref{line:lowestbound} shows the lowest
bound. Line~\ref{line:accumulator} shows the accumulator.

\TODO{Removing partition is more difficult.}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2020-10-08 input/conclusion.tex
initialize

--- 2020-10-08 input/background.tex
@@
-\section{Background and motivation}
-\label{sec:background}
-
-Fog infrastructures are distributed systems comprising heterogeneous
-machines interconnected by communication links.
-
-\begin{definition}[Fog infrastructure]
-  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
-  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
-  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
-  w_{ij}$ with $i, j \in V$.
-\end{definition}
-
-\begin{definition}[Logical partitions]
-  A logical \underline{p}artition $P_s$ originated at a
-  \underline{s}ource process $s \in V$ is a set of interconnected
-  processes that do not belong to another logical partition.
-\end{definition}
-
-\TODO{Multiple destinations shortest path \REF}.
-
-\begin{algorithm}
-  \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding partitions by Process $p$.}
-\end{algorithm}
-
-Algorithm~\ref{algo:add} shows the instructions of dynamic
-partitioning where the only operation available to processes is the
-adding of a partition.  Line~\ref{line:lowestbound} shows the lowest
-bound. Line~\ref{line:accumulator} shows the accumulator.
-
-\TODO{Removing partition is more difficult.}
+\section{Conclusion}
+\label{sec:conclusion}
 
@@
 %%% TeX-master: "../paper"
-%%% ispell-local-dictionary: "english"
 %%% End:

### 2020-10-08 input/experiments.tex
initialize

\section{Experimentation}
\label{sec:experimentation}

\subsection{Global properties}

\subsection{Use case: caching}

\subsection{Use case: routing}

\subsection{Use case: broadcast domain}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2020-10-08 input/introduction.tex
initialize

\section{Introduction}

\TODO{With the advent of Fog infrastructures, content will be increasingly
located at the edges of the network. Either because it is where it has
been created and it is too expensive to be transmitted to a cloud
platform, or because it has been replicated to bring data closer to
the end users [1]. Thanks to the locality, caching at the edge can
benefit many diverse applications, as confirmed by recent proposals
[2], [3], [4]. To favor this transition, the design and development of
building blocks to manage data sets across Fog infrastructures are
critical. One of the key challenges of such systems resides in
locating a given content inside the network. Some systems, such as
Cassandra [5] or CEPH [6] only rely on Hash-based functions to
directly find an object location. A given hash is associated with a
specific node according to a mapping that all nodes agree with,
removing the need for any localization service. However, this implies
moving the content to a specific node in the network according to its
hash, thus violating the locality properties inherent to Fog
architectures [7]. To ensure network traffic containment and avoid
unnecessary data movements, we argue that content should be written
locally and replicated on other nodes only if solicited (e.g.,
according to the popularity of the object in a social media). Thereby,
such requirements prevent relying on hash-based solutions and calls
for a localization service [8].}

\TODO{Most existing implementations of such a localization service imply
contacting a remote node, either a centralized server [9], or a node
of a DHT [10]: When a client wants to access a specific content, first
it has to perform a request to a specific node to determine where to
retrieve this content from.  Once it has retrieved the data from the
location it selected, a local replica is created to improve the
performance for future accesses. The node in charge of maintaining the
index is finally updated to reflect this new location. Yet, accessing
a remote node to find the location of an object (or one of its copies)
has many drawbacks: (i) The lookup penalty: the network latency to
reach this remote node incurs an additional delay to get the object,
before being able to start its downloading, (ii) Answering external
queries increases the load on the remote node, potentially impacting
its performance, (iii) It prevents nodes to access objects in case of
network partitioning: if the node in charge of maintaining the object
locations is isolated from the rest of the infrastructure, nodes
cannot access the object replicas even if some would be reachable.}

\TODO{To tackle the aforementioned limitations of a remote service, we
propose A3, an epidemic protocol that propagates information about
replica localizations asynchronously. A3 leverages the underlying
infrastructure topology to avoid flooding the network so that it only
informs the relevant nodes, according to the existing replicas in the
system. Upon receiving messages, nodes maintain a personalised index
about replica localization, according to their place in the topology,
ensuring that each request will be routed towards its closest
replica. We implemented our protocol and deployed it on a dedicated
testbed emulating real-world topologies from the Internet Toplogy Zoo
[11]. Our evaluation shows that A3 is able to provide a similar
localization service when compared to a DHT-based approach while
removing the lookup penalty.  This directly translates into faster
data access as shown by our measurements, with a time reduction from
20\% to 60\%, depending on the sizes of the objects. Finally, we show
that by slightly delaying the sending of messages, A3 can match the
number of messages of a DHT-based approach, at the cost of a moderate
increase in message sizes.}

\TODO{The rest of this paper is organized as follows. Section II
  introduces background, related works and details the motivation
  behind our proposal.  Section III describes the protocol behavior,
  as well as the formal definition of the underlying
  algorithms. Section IV presents the evaluation of the A3
  implementation and provides an extensive comparison with a DHT-based
  approach. We discuss some extensions of this work and future
  directions in Section V before concluding in Section VI.}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2020-10-08 input/proposal.tex
initialize

--- 2020-10-08 input/introduction.tex
@@
-\section{Introduction}
-
-\TODO{With the advent of Fog infrastructures, content will be increasingly
-located at the edges of the network. Either because it is where it has
-been created and it is too expensive to be transmitted to a cloud
-platform, or because it has been replicated to bring data closer to
-the end users [1]. Thanks to the locality, caching at the edge can
-benefit many diverse applications, as confirmed by recent proposals
-[2], [3], [4]. To favor this transition, the design and development of
-building blocks to manage data sets across Fog infrastructures are
-critical. One of the key challenges of such systems resides in
-locating a given content inside the network. Some systems, such as
-Cassandra [5] or CEPH [6] only rely on Hash-based functions to
-directly find an object location. A given hash is associated with a
-specific node according to a mapping that all nodes agree with,
-removing the need for any localization service. However, this implies
-moving the content to a specific node in the network according to its
-hash, thus violating the locality properties inherent to Fog
-architectures [7]. To ensure network traffic containment and avoid
-unnecessary data movements, we argue that content should be written
-locally and replicated on other nodes only if solicited (e.g.,
-according to the popularity of the object in a social media). Thereby,
-such requirements prevent relying on hash-based solutions and calls
-for a localization service [8].}
-
-\TODO{Most existing implementations of such a localization service imply
-contacting a remote node, either a centralized server [9], or a node
-of a DHT [10]: When a client wants to access a specific content, first
-it has to perform a request to a specific node to determine where to
-retrieve this content from.  Once it has retrieved the data from the
-location it selected, a local replica is created to improve the
-performance for future accesses. The node in charge of maintaining the
-index is finally updated to reflect this new location. Yet, accessing
-a remote node to find the location of an object (or one of its copies)
-has many drawbacks: (i) The lookup penalty: the network latency to
-reach this remote node incurs an additional delay to get the object,
-before being able to start its downloading, (ii) Answering external
-queries increases the load on the remote node, potentially impacting
-its performance, (iii) It prevents nodes to access objects in case of
-network partitioning: if the node in charge of maintaining the object
-locations is isolated from the rest of the infrastructure, nodes
-cannot access the object replicas even if some would be reachable.}
-
-\TODO{To tackle the aforementioned limitations of a remote service, we
-propose A3, an epidemic protocol that propagates information about
-replica localizations asynchronously. A3 leverages the underlying
-infrastructure topology to avoid flooding the network so that it only
-informs the relevant nodes, according to the existing replicas in the
-system. Upon receiving messages, nodes maintain a personalised index
-about replica localization, according to their place in the topology,
-ensuring that each request will be routed towards its closest
-replica. We implemented our protocol and deployed it on a dedicated
-testbed emulating real-world topologies from the Internet Toplogy Zoo
-[11]. Our evaluation shows that A3 is able to provide a similar
-localization service when compared to a DHT-based approach while
-removing the lookup penalty.  This directly translates into faster
-data access as shown by our measurements, with a time reduction from
-20\% to 60\%, depending on the sizes of the objects. Finally, we show
-that by slightly delaying the sending of messages, A3 can match the
-number of messages of a DHT-based approach, at the cost of a moderate
-increase in message sizes.}
-
-\TODO{The rest of this paper is organized as follows. Section II
-  introduces background, related works and details the motivation
-  behind our proposal.  Section III describes the protocol behavior,
-  as well as the formal definition of the underlying
-  algorithms. Section IV presents the evaluation of the A3
-  implementation and provides an extensive comparison with a DHT-based
-  approach. We discuss some extensions of this work and future
-  directions in Section V before concluding in Section VI.}
+\section{Dynamic partitioning}
+\label{sec:proposal}
 

### 2020-10-08 input/background.tex
wip

@@
 
-\TODO{Multiple destinations shortest path \REF}.
+\begin{definition}[Optimal partitioning]
+  The optimal partitioning $\mathcal{P}$ is a set of logical
+  partitions such that each process belongs to a logical partition
+  comprising its closest source process. $\forall p \in P_{s_1},
+  \nexists P_{s_2}$ such that \TODO{$distance(p, s_2) < distance(p,
+    s_1)$}.
+\end{definition}
+
+When $distance$ involves monotonically increasing scalars such as
+latency or number of hops between sources and processes, the optimal
+partitioning consists in processing the multiple destinations shortest
+path~\REF at each process. \TODO{Easy to solve when all processes
+  receives all messages.}
+
+Algorithm~\ref{algo:add} shows the instructions of dynamic
+partitioning where the only operation available to processes is the
+adding of a partition.  Line~\ref{line:lowestbound} shows the lowest
+bound. Line~\ref{line:accumulator} shows the accumulator.
 
@@
 
-Algorithm~\ref{algo:add} shows the instructions of dynamic
-partitioning where the only operation available to processes is the
-adding of a partition.  Line~\ref{line:lowestbound} shows the lowest
-bound. Line~\ref{line:accumulator} shows the accumulator.
+\begin{figure*}
+  \begin{center}
+    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
+    \hspace{5pt}
+    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
+  \end{center}
+\end{figure*}
 
-\TODO{Removing partition is more difficult.}
+Transitive relationships ensure that each process gets its closest
+source while accumulators ensure that messages propagation
+terminates. The system converges towards the optimal partitioning
+despite processes not broadcasting all messages. Removals of
+partitions are more challenging. \TODO{Figure.} One could solve this
+issue by removing partitions that were not advertised for a defined
+time~\REF. However, relying on physical timeout could lead to either
+premature removals of partitions when they are still operating; or
+slow convergence where processes believe they belong to a partition
+that was removed.
+
+\TODO{Problem statement.}
+
+\TODO{Next Section presents our approach that solves this problem
+  statement by relying only on logical control information.}
 

### 2020-10-08 input/figaddA.tex
wip

\begin{tikzpicture}[scale=1]

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

  \draw[fill=white] (0, 0) node{$\bm{a}$} +(-5, -5) rectangle +(5, 5);

\end{tikzpicture}

### 2020-10-08 input/background.tex
figure of simple add

@@
   \begin{center}
-    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
+    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
+      Process $c$ initiate a partition.
+      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
     \hspace{5pt}
-    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
+    \subfloat[Part B][\label{fig:addB}Messages transit through communication
+      links and carry increasing weights.]{\input{input/figaddB.tex}}
+    \hspace{5pt}
+    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
+      $Add_{c, +1}$ then discards $Add_{a, +1.5}$, for the latter distance
+      is higher.]{\input{input/figaddC.tex}}
+    \hspace{5pt}
+    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
+      incoming messages. The system converged to optimal partitions.]{
+      \input{input/figaddD.tex}}
+    \caption{\label{fig:add}Simple accumulation in messages makes the
+      system converge to optimal partitions with contained
+      flooding.}
   \end{center}
@@
 despite processes not broadcasting all messages. Removals of
-partitions are more challenging. \TODO{Figure.} One could solve this
+partitions are more challenging. \TODO{Figure.} \TODO{Also easy to
+  solve when all processes receive all messages}. One could solve this
 issue by removing partitions that were not advertised for a defined

### 2020-10-08 input/background.tex
text of figure

@@
 
-\begin{definition}[Logical partitions]
+\begin{definition}[Logical partition]
   A logical \underline{p}artition $P_s$ originated at a
@@
 partitioning consists in processing the multiple destinations shortest
-path~\REF at each process. \TODO{Easy to solve when all processes
-  receives all messages.}
-
-Algorithm~\ref{algo:add} shows the instructions of dynamic
-partitioning where the only operation available to processes is the
-adding of a partition.  Line~\ref{line:lowestbound} shows the lowest
-bound. Line~\ref{line:accumulator} shows the accumulator.
+path~\REF at each process.  Algorithm~\ref{algo:add} shows the
+instructions of such dynamic partitioning where the only operation
+available to processes is the adding of a
+partition. Figure~\ref{fig:add} illustrates its behavior on a system
+comprising 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and
+$c$ concurrently create a partition. They initialize their own state
+with the lowest possible bound $0$ (see Line~\ref{line:lowestbound}),
+and send a message to each of their neighbors by accumulating the
+corresponding edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, Process $b$ receives $Add_{c, 1}$. Since it
+improves its own partition distance, it keeps it and forwards it to
+its neighbors. Process $b$ discards $Add_{b, 1.5}$, for it does not
+improve its partition distance. Processes $c$ and $d$ will never hear
+of Process $a$'s partition. In Figure~\ref{fig:addD}, processes
+discard last transiting messages. The system converged to the optimal
+partitioning.
 
@@
   \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding partitions by Process $p$.}
+  \caption{\label{algo:add}Adding a partition by Process $p$.}
 \end{algorithm}
@@
       system converge to optimal partitions with contained
-      flooding.}
+      broadcast.}
   \end{center}
@@
 
+Order on the broadcast.
+
 \TODO{Problem statement.}

### 2020-10-09 input/background.tex
wip

@@
 
+\begin{figure*}
+  \begin{center}
+    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
+      Process $c$ initiate a partition.
+      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
+    \hspace{5pt}
+    \subfloat[Part B][\label{fig:addB}Messages transit through communication
+      links and carry increasing weights.]{\input{input/figaddB.tex}}
+    \hspace{5pt}
+    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
+      $Add_{c, 1}$ then discards $Add_{a, 1.5}$, for the latter distance
+      is higher.]{\input{input/figaddC.tex}}
+    \hspace{5pt}
+    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
+      incoming messages. The system converged to optimal partitions.]{
+      \input{input/figaddD.tex}}
+    \caption{\label{fig:add}Simple accumulation in messages makes the
+      system converge to optimal partitions with contained
+      broadcast.}
+  \end{center}
+\end{figure*}
+
+\begin{algorithm}
+  \input{input/algoadd.tex}
+  \caption{\label{algo:add}Adding a partition by Process $p$.}
+\end{algorithm}
+
 When $distance$ involves monotonically increasing scalars such as
@@
 
-\begin{algorithm}
-  \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding a partition by Process $p$.}
-\end{algorithm}
-
-\begin{figure*}
-  \begin{center}
-    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
-      Process $c$ initiate a partition.
-      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
-    \hspace{5pt}
-    \subfloat[Part B][\label{fig:addB}Messages transit through communication
-      links and carry increasing weights.]{\input{input/figaddB.tex}}
-    \hspace{5pt}
-    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
-      $Add_{c, +1}$ then discards $Add_{a, +1.5}$, for the latter distance
-      is higher.]{\input{input/figaddC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
-      incoming messages. The system converged to optimal partitions.]{
-      \input{input/figaddD.tex}}
-    \caption{\label{fig:add}Simple accumulation in messages makes the
-      system converge to optimal partitions with contained
-      broadcast.}
-  \end{center}
-\end{figure*}
-
 Transitive relationships ensure that each process gets its closest
@@
 that was removed.
+
+\begin{figure*}
+  \begin{center}
+    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
+      Process $c$ initiate then remove a partition.
+      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
+    \hspace{5pt}
+    \subfloat[Part B][\label{fig:delB}\TODO{mew}.]{\input{input/figdelB.tex}}
+    \hspace{5pt}
+    \subfloat[Part C][\label{fig:delC}\TODO{mew}.]{\input{input/figdelC.tex}}
+    \hspace{5pt}
+
+  \end{center}
+  \caption{\label{algo:add}Removing partition may lead to inconsistent states.}
+\end{figure*}
 

### 2020-10-09 input/figdelA.tex
wip

\begin{tikzpicture}[scale=0.87]

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

  \newcommand\ADD{Add}
  \newcommand\DEL{Del}

  \draw (-\X, 0) -- node[above,font=\tiny]{$\ADD_{a, 1.5}$} (0, 0); %% a - b
  \draw (0, 0) -- node[above, font=\tiny]{$\ADD_{c, 1}$} (\X, 0); %% b - c
  \draw (0, 0) -- (0, \Y); %% b - d
  \draw (\X, 0) -- node[below, font=\tiny, sloped]{$\ADD_{c, 1}$} (0, \Y); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
  \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};

\end{tikzpicture}

### 2020-10-09 input/figaddA.tex
rework figure

@@
-\begin{tikzpicture}[scale=1]
+\begin{tikzpicture}[scale=0.87]
 
@@
 
-  \draw[fill=white] (0, 0) node{$\bm{a}$} +(-5, -5) rectangle +(5, 5);
+  \newcommand\ADD{\alpha}
+
+  \draw[->] (-\X + 5pt, 0 + 2pt ) -- (0 - 5pt, 0 + 2pt); %% a - b
+  \draw[<-] (-\X + 5pt, 0 - 2pt ) -- (0 - 5pt, 0 - 2pt); %% b - a
+
+  \draw[->] (0 +5pt, 0 - 2pt) -- (\X -5pt, 0 - 2pt); %% b - c
+  \draw[<-] (0 +5pt, 0 + 2pt) -- (\X -5pt, 0 + 2pt); %% c - b
+
+  \draw[->] (0 + 2pt, 0 - 5pt) -- (0 + 2pt, \Y + 5pt); %% b - d
+  \draw[<-] (0 - 2pt, 0 - 5pt) -- (0 - 2pt, \Y + 5pt); %% d - b
+
+  \draw[<-] (\X - 3pt, 0 - 5pt) -- (0 + 5pt, \Y + 3pt); %% d - c
+  \draw[->] (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d
+
+  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
+  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+
+  \draw (-\X, 5pt) node[above]{$\ADD_a^0$};
+  \draw (\X, 5pt) node[above]{$\ADD_c^0$};
 

### 2020-10-09 input/background.tex
removal of partition figure

@@
 improve its partition distance. Processes $c$ and $d$ will never hear
-of Process $a$'s partition. In Figure~\ref{fig:addD}, processes
-discard last transiting messages. The system converged to the optimal
-partitioning.
+of Process $a$'s partition. \TODO{At scale.} In Figure~\ref{fig:addD},
+processes discard last transiting messages. The system converged to
+the optimal partitioning.
 
@@
     \hspace{5pt}
-    \subfloat[Part B][\label{fig:delB}\TODO{mew}.]{\input{input/figdelB.tex}}
+    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
+      messages based on their weights. $a$'s partition propagates to all processes.]
+             {\input{input/figdelB.tex}}
     \hspace{5pt}
-    \subfloat[Part C][\label{fig:delC}\TODO{mew}.]{\input{input/figdelC.tex}}
+    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
+      Its removal shortly follows. Process $b$ does not have any control
+      information about partitions any more.]{\input{input/figdelC.tex}}
     \hspace{5pt}
-
+    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
+      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
+      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
+      partition.]{\input{input/figdelD.tex}}
   \end{center}

### 2020-10-09 input/figdelA.tex
removal of partition figure

@@
 
-  \newcommand\ADD{Add}
-  \newcommand\DEL{Del}
+  \newcommand\ADD{\alpha}
+  \newcommand\DEL{\delta}
 
-  \draw (-\X, 0) -- node[above,font=\tiny]{$\ADD_{a, 1.5}$} (0, 0); %% a - b
-  \draw (0, 0) -- node[above, font=\tiny]{$\ADD_{c, 1}$} (\X, 0); %% b - c
-  \draw (0, 0) -- (0, \Y); %% b - d
-  \draw (\X, 0) -- node[below, font=\tiny, sloped]{$\ADD_{c, 1}$} (0, \Y); %% c - d
+  \draw[->] (-\X + 5pt, 0 + 2pt ) --
+  node[above=-0.3em,font=\tiny]{$\ADD_{a}^{1.5}$}
+  (0 - 5pt, 0 + 2pt); %% a - b
+  \draw[<-] (-\X + 5pt, 0 - 2pt ) --
+  (0 - 5pt, 0 - 2pt); %% b - a
+
+  \draw[<-] (0 +5pt, 0 + 2pt) --
+  node[above=-0.3em, font=\tiny]{$\ADD_{c}^{1}$}
+  (\X -5pt, 0 + 2pt); %% c - b
+  \draw[->] (0 +5pt, 0 - 2pt) --
+  (\X -5pt, 0 - 2pt); %% b - c
+
+  \draw[->] (0 + 2pt, 0 - 5pt) --
+  (0 + 2pt, \Y + 5pt); %% b - d
+  \draw[->] (0 - 2pt, \Y + 5pt) --
+  (0 - 2pt, 0 - 5pt);  %% d - b
+
+  \draw[<-] (\X - 3pt, 0 - 5pt) --
+  (0 + 5pt, \Y + 3pt); %% d - c
+  \draw[->] (\X + 3pt, 0 - 5pt) --
+  node[below=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{1}$}
+  (0 + 5pt, \Y - 3pt); %% c - d
 
@@
 
-  \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
-  \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};
+  \draw (-\X, 5pt) node[above]{$\DEL_a$};
+  \draw (\X, 5pt) node[above]{$\DEL_c$};
 

### 2020-10-09 input/background.tex
meow

@@
 
+When $distance$ involves latency or number of hops between sources and
+processes, the optimal partitioning consists in processing the
+multiple destinations shortest path~\REF at each process.
+
 \begin{figure*}
@@
     \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
-      $Add_{c, 1}$ then discards $Add_{a, 1.5}$, for the latter distance
+      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
       is higher.]{\input{input/figaddC.tex}}
@@
 
-When $distance$ involves monotonically increasing scalars such as
-latency or number of hops between sources and processes, the optimal
-partitioning consists in processing the multiple destinations shortest
-path~\REF at each process.  Algorithm~\ref{algo:add} shows the
-instructions of such dynamic partitioning where the only operation
-available to processes is the adding of a
-partition. Figure~\ref{fig:add} illustrates its behavior on a system
-comprising 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and
-$c$ concurrently create a partition. They initialize their own state
-with the lowest possible bound $0$ (see Line~\ref{line:lowestbound}),
-and send a message to each of their neighbors by accumulating the
-corresponding edge weight (see Line~\ref{line:accumulator}). In
-Figure~\ref{fig:addC}, Process $b$ receives $Add_{c, 1}$. Since it
-improves its own partition distance, it keeps it and forwards it to
-its neighbors. Process $b$ discards $Add_{b, 1.5}$, for it does not
-improve its partition distance. Processes $c$ and $d$ will never hear
-of Process $a$'s partition. \TODO{At scale.} In Figure~\ref{fig:addD},
-processes discard last transiting messages. The system converged to
-the optimal partitioning.
+Algorithm~\ref{algo:add} shows the instructions of optimal
+partitioning where the only operation available to processes is the
+adding of partitions. Figure~\ref{fig:add} illustrates its behavior on
+a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
+$a$ and $c$ concurrently create a partition. They initialize their own
+state with the lowest possible bound $0$ (see
+Line~\ref{line:lowestbound}), and send a message to each of their
+neighbors by accumulating the corresponding edge weight (see
+Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
+receives $\alpha_{c}^{1}$. Since it improves its own partition
+distance, it keeps it and forwards it to its neighbors. Process $b$
+discards $\alpha_{b}^{1.5}$, for it does not improve its partition
+distance. Processes $c$ and $d$ will never hear of Process $a$'s
+partition. At scale, it saves bandwidth by limiting generated traffic
+to subsets of processes. In Figure~\ref{fig:addD}, processes discard
+last transiting messages. The system converged to the optimal
+partitioning. Interestingly, while the receipt order of messages does
+not impact on local control information, it impacts on control
+information broadcast in the network.
 
 Transitive relationships ensure that each process gets its closest
-source while accumulators ensure that messages propagation
-terminates. The system converges towards the optimal partitioning
-despite processes not broadcasting all messages. Removals of
-partitions are more challenging. \TODO{Figure.} \TODO{Also easy to
-  solve when all processes receive all messages}. One could solve this
-issue by removing partitions that were not advertised for a defined
+source while accumulation of weights ensures that messages propagation
+terminates.  Removals of partitions are more
+challenging. \TODO{Figure.} \TODO{Also easy to solve when all
+  processes receive all messages}. One could solve this issue by
+removing partitions that were not advertised for a defined
 time~\REF. However, relying on physical timeout could lead to either
@@
   \end{center}
-  \caption{\label{algo:add}Removing partition may lead to inconsistent states.}
+  \caption{\label{algo:add}Removing partition may lead to inconsistent partitions.}
 \end{figure*}

### 2020-10-11 input/background.tex
meow meow meow

@@
   \underline{s}ource process $s \in V$ is a set of interconnected
-  processes that do not belong to another logical partition.
+  processes that do not belong to another logical partition. The set
+  of sources is $S$.
 \end{definition}
@@
   partitions such that each process belongs to a logical partition
-  comprising its closest source process. $\forall p \in P_{s_1},
-  \nexists P_{s_2}$ such that \TODO{$distance(p, s_2) < distance(p,
-    s_1)$}.
+  comprising its closest source process. $\forall p \in P_{s_1\in S},
+  \nexists P_{s_2 \in S}$ such that \TODO{$distance(p, s_2) <
+    distance(p, s_1)$}.
 \end{definition}
@@
 multiple destinations shortest path~\REF at each process.
+
+\begin{definition}[Shortest path]
+  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
+  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
+  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
+  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
+  that there exists no lower sum of weights from $i$ to $j$.
+\end{definition}
+
+\TODO{Define operation alpha. Receipt and deliveries.}
+
+Without global knowledge, processes only rely on their own behavior to
+deduce the behavior of their neighbor processes.
+
+\begin{definition}[\label{def:pathdelivery}\TODO{Shortest path} delivery]
+  \TODO{Shortest path} delivery ensures the system eventually converges to
+  optimal partitioning:
+  \begin{inparaenum}[(i)]
+  \item (\textbf{termination}) processes do not need to propagate
+    operations they do not deliver: $\forall \langle i, j \rangle \in
+    E, \neg d_i(\alpha_{s}^w)\implies \neg
+    d_j(\alpha_{s}^{w+w_{ij}})$;
+  \item (\textbf{propagation}) operations delivered by a process may
+    also benefit neighbor processes: $\forall \langle i, j \rangle \in
+    E, d_i(\alpha_{s}^{w_1}) \implies
+    d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
+    d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
+  \end{inparaenum}
+\end{definition}
 
@@
 
-Algorithm~\ref{algo:add} shows the instructions of optimal
-partitioning where the only operation available to processes is the
-adding of partitions. Figure~\ref{fig:add} illustrates its behavior on
-a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
+Algorithm~\ref{algo:add} shows the instructions that implement the
+rules of Definition~\ref{def:pathdelivery} to converge towards optimal
+partitioning. Figure~\ref{fig:add} illustrates its behavior on a
+system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
 $a$ and $c$ concurrently create a partition. They initialize their own
@@
 not impact on local control information, it impacts on control
-information broadcast in the network.
+information broadcast in the network. \TODO{explain with r() d() b().}
 

### 2020-10-12 input/background.tex
meow
better integration of def path

@@
   processes that do not belong to another logical partition. The set
-  of sources is $S$.
+  of sources is $S \subseteq V$.
+\end{definition}
+
+Processes belong to logical partitions depending on path lengths. When
+weights are latency or hop numbers, the optimal partitioning consists
+in processing the multiple destinations shortest path at each process
+\REF.
+
+\begin{definition}[Shortest path]
+  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
+  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
+  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
+  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
+  that there exists no lower sum of weights $|\Pi_{ij}|$ from $i$ to
+  $j$.
 \end{definition}
@@
   comprising its closest source process.  $\forall p \in P_{s_1\in S},
-  \nexists P_{s_2 \in S}$ such that \TODO{$distance(p, s_2) <
-    distance(p, s_1)$}.
+  \nexists P_{s_2 \in S}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
 \end{definition}
 
-When $distance$ involves latency or number of hops between sources and
-processes, the optimal partitioning consists in processing the
-multiple destinations shortest path~\REF at each process.
+Processes use reliable asynchronous message passing to reach optimal
+partitioning together. Process $s$ generates a message
+$\alpha_s^0$. Upon \underline{r}eceipt $r_i(\alpha_s^{w})$, Process
+$i$ knows that Process $s$ created a partition at a path length of
+$w$. Process $i$ may choose to \underline{d}eliver $d_i(\alpha_s^{w})$
+if it improves its partitioning. Process $i$ may choose to propagate
+its change through \underline{b}roadcast $b_i(\alpha_s^w)$.  Without
+global knowledge, processes only rely on their own behavior to deduce
+the behavior of their neighbor processes.
 
-\begin{definition}[Shortest path]
-  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
-  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
-  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
-  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
-  that there exists no lower sum of weights from $i$ to $j$.
-\end{definition}
-
-\TODO{Define operation alpha. Receipt and deliveries.}
-
-Without global knowledge, processes only rely on their own behavior to
-deduce the behavior of their neighbor processes.
-
-\begin{definition}[\label{def:pathdelivery}\TODO{Shortest path} delivery]
-  \TODO{Shortest path} delivery ensures the system eventually converges to
+\begin{definition}[\label{def:transitivedelivery}Transitive delivery]
+  Transitive delivery ensures the system eventually converges to
   optimal partitioning:
@@
 Algorithm~\ref{algo:add} shows the instructions that implement the
-rules of Definition~\ref{def:pathdelivery} to converge towards optimal
-partitioning. Figure~\ref{fig:add} illustrates its behavior on a
-system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
+rules of Definition~\ref{def:transitivedelivery} to converge towards
+optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
+a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
 $a$ and $c$ concurrently create a partition. They initialize their own
@@
 last transiting messages. The system converged to the optimal
-partitioning. Interestingly, while the receipt order of messages does
-not impact on local control information, it impacts on control
-information broadcast in the network. \TODO{explain with r() d() b().}
+partitioning.  Transitive relationships ensure that each process gets
+its closest source while accumulation of weights ensures that messages
+propagation terminates.  Interestingly, while the receipt order of
+messages does not impact on local control information
+($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
+r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
+\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
+broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
+\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
+$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
+b_b(\alpha_a^{1})$).
 
-Transitive relationships ensure that each process gets its closest
-source while accumulation of weights ensures that messages propagation
-terminates.  Removals of partitions are more
-challenging. \TODO{Figure.} \TODO{Also easy to solve when all
+While only adding logical partitions to the distributed system is
+straightforward, removing them introduces additional complexity.
+
+\begin{definition}[Dynamic optimal partitioning]
+  \TODO{add and del operations.}
+\end{definition}
+
+\TODO{Figure.} \TODO{Also easy to solve when all
   processes receive all messages}. One could solve this issue by
@@
 
-Order on the broadcast.
-
 \TODO{Problem statement.}

### 2020-10-12 input/background.tex
small changes

@@
 \begin{definition}[Dynamic optimal partitioning]
-  \TODO{add and del operations.}
+  A dynamic optimal partitioning is an optimal partitioning where the
+  set of sources $S$ does not monotonically increase. Process $i$
+  joins the set of sources by adding its partition $\alpha_i^{0}$ and
+  leaves the set of sources by removing its partition $\delta_i$.
 \end{definition}
 
-\TODO{Figure.} \TODO{Also easy to solve when all
-  processes receive all messages}. One could solve this issue by
-removing partitions that were not advertised for a defined
-time~\REF. However, relying on physical timeout could lead to either
-premature removals of partitions when they are still operating; or
-slow convergence where processes believe they belong to a partition
-that was removed.
+\TODO{Figure~\ref{fig:del} shows that.}
+
+One could solve this issue by using a conflict-free replicated data
+type for set data structures, then deliver and broadcast all
+operations to all processes~\REF. However, this would be costly in
+terms of generated traffic with some processes delivering and
+broadcasting unrelated to their partitions \TODO{(include locality)}.
+One could also solve this issue by removing partitions that were not
+advertised for a defined time~\REF. However, relying on physical
+timeout could lead to either premature removals of partitions when
+they are still operating; or slow convergence where processes believe
+they belong to a partition that was removed.
 
@@
   \end{center}
-  \caption{\label{algo:add}Removing partition may lead to inconsistent partitions.}
+  \caption{\label{fig:del}Partition removals cannot rely only on
+    current partition, for it may lead to inconsistent partitioning.}
 \end{figure*}
 
-\TODO{Problem statement.}
+\begin{problem}[Consistent partitioning]
+  \TODO{How to enable \emph{consistent} dynamic optimal partitioning
+    with contained broadcast?}
+\end{problem}
 

### 2020-10-19 input/proposal.tex
a bit of time complexity

@@
 \label{sec:proposal}
+
+\subsection{Complexity}
+\label{subsec:complexity}
+
+We focus on average-case and worst-case complexity. We divide our
+analysis into space, time, and communication complexity.
+
+\textbf{The communication complexity} concerns the size and number of
+messages required to reach optimal partitioning. In the average-case,
+a process $i$ chosen uniformly at random among all processes creates
+a logical partition. Its messages $\alpha_i$ propagate through the
+network until reaching processes that belong to another partition
+closer to them. This splits partitions in half in average. Overall,
+the $a^{th}$ new partition comprises
+\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
+processes. This decreases every new partition until reaching $0$
+processes per new partition: even the chosen process already belongs
+to its optimal partition. The average number of messages per process
+is \smash{$\mathcal{O}(\frac{\overline{|O|}}{|2^{\lfloor \log_2 a
+      \rfloor}})$}.  Deleting the $a^{th}$ partition generates the
+exact same number of messages than the $a^{th}$ partition
+creation. \TODO{But what about echos?} In the worst-case, every new
+partition includes all but one process belonging to the previous
+partition. The total number of messages after the $a^{th}$ new
+partition is $O(\overline{|O|}\cdot a^2)$. As for the average-case,
+the number of messages for the partition deletion is identical to the
+number of messages of the corresponding partition creation.
 
@@
 %%% TeX-master: "../paper"
+%%% ispell-local-dictionary: "english"
 %%% End:

### 2020-10-20 input/background.tex
a bit of time complexity
meow

@@
   A dynamic optimal partitioning is an optimal partitioning where the
-  set of sources $S$ does not monotonically increase. Process $i$
-  joins the set of sources by adding its partition $\alpha_i^{0}$ and
-  leaves the set of sources by removing its partition $\delta_i$.
+  set of sources $S$ does not monotonically increase. We suffix this
+  set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
+  of sources by \underline{a}dding its partition with messages
+  $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
+  leaves the set of sources by \underline{d}eleting its partition with
+  messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
 \end{definition}
@@
   \TODO{How to enable \emph{consistent} dynamic optimal partitioning
-    with contained broadcast?}
+    in dynamic network with contained broadcast?}
 \end{problem}
+
+\TODO{Dynamic Multiple-sources All-destinations shortest path on
+  dynamic graphs?}
 

### 2020-10-20 input/proposal.tex
meow

@@
 \label{sec:proposal}
+
+A reactive logical partitioning the cost of which actually depends on
+its usage.
 
@@
 messages required to reach optimal partitioning. In the average-case,
-a process $i$ chosen uniformly at random among all processes creates
-a logical partition. Its messages $\alpha_i$ propagate through the
+a process $i$ chosen uniformly at random among all processes creates a
+logical partition. Its messages $\alpha_i$ propagate through the
 network until reaching processes that belong to another partition
@@
 to its optimal partition. The average number of messages per process
-is \smash{$\mathcal{O}(\frac{\overline{|O|}}{|2^{\lfloor \log_2 a
-      \rfloor}})$}.  Deleting the $a^{th}$ partition generates the
-exact same number of messages than the $a^{th}$ partition
-creation. \TODO{But what about echos?} In the worst-case, every new
-partition includes all but one process belonging to the previous
-partition. The total number of messages after the $a^{th}$ new
-partition is $O(\overline{|O|}\cdot a^2)$. As for the average-case,
-the number of messages for the partition deletion is identical to the
-number of messages of the corresponding partition creation.
+is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
+      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
+  more messages (receipt bounded by $|O|$ as well).} Deleting the
+$a^{th}$ partition generates the exact same number of messages than
+the $a^{th}$ partition creation. \TODO{But what about echos?} In the
+worst-case, every new partition includes all but one process belonging
+to the previous partition. The total number of messages after the
+$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
+for the average-case, the number of messages for the partition
+deletion is identical to the number of messages of the corresponding
+partition creation.
 

### 2021-01-28 input/proposal.tex
nixos file + general idea

@@
 its usage.
+
+The main idea is maintaining graphs of partitions using local
+knowledge only and use graphs as often as possible: it improves
+resilience to crashes, convergence speed etc. Unfortunately,
+maintaining graphs of partitions in dynamic networks may require the
+use of broadcast tree. The removal of a communication channel between
+2 processes may remove an advantageous path from processes downstream
+to the source of the partition they belong to.
 

### 2021-01-28 input/proposal.tex
wip

@@
 
-A reactive logical partitioning the cost of which actually depends on
-its usage.
+In this section, we introduce \NAME, (\TODO{stands for}) a reactive
+protocol for logical partitioning the cost of which actually depends
+on its usage: when the system becomes quiescent, processes eventually
+converge to their respective partition and do not require further
+communication afterwards.
 
@@
 
+This section describes \NAME's components by starting from the
+simplest case of add-only partition, to the most complex case of
+dynamic partitions in dynamic networks.
+
+\TODO{Probably better to pair operation as ``ins, del'' and ``add, rem''?}
+
+\paragraph{Static network with add-only.}
+At any time, a process can become a source, hence \TODO{creating} a
+new partition in the system. This partition eventually includes all
+processes that are closer from this new source than any other else. We
+described such protocol in Section~\ref{sec:background}. Processes
+naturally converge towards their respective best partition by only
+piggybacking a monotonically increasing distance in forwarded
+messages.  \TODO{Traffic of each partition is contained to the
+  partition.}
+
+\paragraph{Static network with dynamic partitions.}
+At any time, a source can revoke its self-appointed status of source,
+hence \TODO{removing} its partition of the system. All processes that
+belong to this partition must choose another partition to belong to.
+To handle dynamic partitions, processes require two additional
+components.
+
+\noindent \textbf{First,} since the number of partitions does not
+monotonically increase in the system any longer, they require a vector
+of versions that monotonically increases over \TODO{add and del}
+operations. This allows processes to quickly discard stale messages
+saving bandwidth. For instance, a process that received a message
+originated at Process $a$ with a version $2$ knows that any message
+originated at Process $a$ with a version $1$ are stale system-wide; it
+must not forward it. As consequence, vectors of versions also ensure
+termination, for messages \TODO{add and del} cannot follow each other
+in an infinite loop. In terms of traffic, this only requires each
+\TODO{delete} message to piggyback a source identifier and version
+number.
+
+\noindent \textbf{Second,} processes need to maintain a local view of
+their neighbors' partition.  Figure~\ref{fig:del} shows that
+\TODO{deletes} may not propagate properly to all processes in
+need. The path leading to processes delivering $add$ may be broken due
+to concurrent deliveries.  To solve this issue, each process is able
+to know with certainty that each of its neighbor does not need a
+delete (either because it is in another partition, or because another
+path exists from the source to this neighbor). \TODO{More, figures
+  etc.} In terms of traffic, this requires to acknowledge each message
+in a way or another (acknowledgement messages or included in each
+add-del message) using FIFO communication channels. The propagation of
+delete messages is limited to the partition it targets plus uncertain
+processes.
+
+\noindent \textbf{Finally,} the delete must trigger another
+competition amongst neighboring partitions. These \TODO{add}
+messages operate normally and fill gaps left open by deletes.
+
+\paragraph{Networks with new communication links.}
+Adding new communication links to the network may create shortcuts
+between processes. Both processes must send their current best
+partition to each other. Upon receipt, they act normally: if a process
+finds out that the received partition is closer than its current one,
+it delivers it which in turns also triggers another competition
+amongst neighbors due to forwarding.
+
+Joining the network is equivalent to add as many communication links
+as necessary between the joining process and its new neighbors.
+
+\paragraph{Dynamic networks with dynamic partitions.}
+When removing a communication link between two processes does not
+break any active path, because neither distances of processes depend
+on the other, then nothing needs to be done. \NAME have no overhead.
+Unfortunately, when a process' distance depends on the other process,
+the protocol becomes much more complex. Indeed, this requires to
+\TODO{undo} all add messages originated from this process. \TODO{Why
+  distance is not sufficient ?} \TODO{Why not use this from the first
+  step then, or why other steps are still relevant?}
+
+\paragraph{A last optimisation}
+
+\TODO{Carry information that is useless. such as order of processes in
+  paths, and identities of processes themselves.}
+
 \subsection{Complexity}
 \label{subsec:complexity}
+
+\TODO{To rework, for there are more components now.}
 

### 2021-01-28 input/proposal.tex
more on dynamic networks

@@
 
-Joining the network is equivalent to add as many communication links
-as necessary between the joining process and its new neighbors.
+\noindent Joining the network is equivalent to add as many
+communication links as necessary between the joining process and its
+new neighbors.
 
@@
 break any active path, because neither distances of processes depend
-on the other, then nothing needs to be done. \NAME have no overhead.
+on the other, then nothing needs to be done. \NAME has no overhead.
 Unfortunately, when a process' distance depends on the other process,
 the protocol becomes much more complex. Indeed, this requires to
-\TODO{undo} all add messages originated from this process. \TODO{Why
-  distance is not sufficient ?} \TODO{Why not use this from the first
-  step then, or why other steps are still relevant?}
+\TODO{undo} all add messages originated from this process. A message
+must convey the fact that
+\begin{inparaenum}[(i)]
+\item an edge at a particular process has been removed, and
+\item the distance that has been delivered by a process comes from
+  this particular process.
+\end{inparaenum}
+
+\noindent \NAME handles this as a particular case of partition within
+current partition: it contains to affected regions the traffic
+generated to patch affected regions. In order to know if it is
+affected by the \TODO{undo} operation, using distances already
+piggybacked in messages is not sufficient.  Each process must know the
+path taken by delivered message. Since we do not beforehand which
+communication links will crash and which messages will be affected by
+undos, each message has to carry its path along forwarding. This also
+allows processes to remove loops, for they cannot rely on version
+number (that remains unchanged) for this operation.
+
+\noindent Instead of version number, one could use such paths to remove loops
+due to \TODO{add and del}, however this may be much more costly in
+terms of generated traffic. Version numbers guarantee that only one
+delete is delivered and all prior inserts are then discarded, while
+using paths, processes may deliver multiple inserts and deletes before
+reaching termination. \TODO{maybe clearer with figures.} As
+consequence, \NAME still makes use of vector of versions.
+
+\noindent Although costly, piggybacking paths with logical partitioning synergies
+well, for the size of these paths decreases quickly as the number of
+partitions grows.
 
 \paragraph{A last optimisation}
-
 \TODO{Carry information that is useless. such as order of processes in
-  paths, and identities of processes themselves.}
+  paths, and identities of processes themselves.} \TODO{Icarus for
+  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
+  know the dimension of networks and
+  partitions~\cite{almeida2007scalable}}.
 
@@
 
-\TODO{To rework, for there are more components now.}
+\TODO{To rework, for there are more components now. Maybe do this
+  along the description of the approach.}
 

### 2021-01-29 input/figdelA.tex
wip

@@
   \draw[->] (-\X + 5pt, 0 + 2pt ) --
-  node[above=-0.3em,font=\tiny]{$\ADD_{a}^{1.5}$}
+  node[above=-0.3em,font=\tiny, color=\PA]{$\ADD_{a}^{1.5}$}
   (0 - 5pt, 0 + 2pt); %% a - b
@@
   \draw[<-] (0 +5pt, 0 + 2pt) --
-  node[above=-0.3em, font=\tiny]{$\ADD_{c}^{1}$}
+  node[above=-0.3em, font=\tiny, color=\PC]{$\ADD_{c}^{1}$}
   (\X -5pt, 0 + 2pt); %% c - b
@@
   \draw[->] (\X + 3pt, 0 - 5pt) --
-  node[below=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{1}$}
+  node[below=-0.3em, font=\tiny, sloped, color=\PC]{$\ADD_{c}^{1}$}
   (0 + 5pt, \Y - 3pt); %% c - d

### 2021-02-01 input/abstract.tex
coloring figures, adding biblio, sketching abstract

@@
 
-\TODO{Locating the closest copy of a specific content across a
-  distributed infrastructure requires to keep up-to-date an index of
-  all replicas and their respective locations. Existing methods mostly
-  rely on an external service to store this index, either on a
-  centralized server or using a Distributed Hash Table (DHT). However,
-  contacting a remote node to obtain localization information
-  contradicts with emerging Fog infrastructures in terms of locality
-  and robustness. In this paper, we present $A^3$, an epidemic
-  protocol that will efficiently inform the relevant nodes about the
-  presence of replicas in their neighborhood. Upon the exchange of
-  messages, each node maintains a personalized index that will
-  eventually contain the location of the closest copy for each object
-  according to its place in the network topology. We implemented $A^3$
-  and deployed it on a dedicated testbed with real-world
-  topologies. Experimental results show that the time to retrieve
-  objects is significantly decreased from 10\% up to 60\%, when
-  compared to a DHT-based localization service.}
+  Fog infrastructures allows content providers to better distribute
+  data over autonomous systems, hence improving on quality of user
+  experience by reducing latency. However, locating the closest data
+  sources can prove challenging in dynamic networks with dynamic
+  sources. Locating sources may effectively take more time than
+  actually downloading contents. \TODO{Related work ?} In this paper,
+  we introduce \NAME, a reactive protocol for dynamic logical
+  partitioning in dynamic networks. \TODO{source automatically create
+    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
+    flooding}). \TODO{costs of operations.} When the system becomes
+  quiescent, every process eventually converges to its closest
+  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
+    testbed?}
 

### 2021-02-01 input/background.tex
coloring figures, adding biblio, sketching abstract

@@
     \caption{\label{fig:add}Simple accumulation in messages makes the
-      system converge to optimal partitions with contained
-      broadcast.}
+      system converge to optimal partitions with scoped flooding.}
   \end{center}
@@
 distance. Processes $c$ and $d$ will never hear of Process $a$'s
-partition. At scale, it saves bandwidth by limiting generated traffic
-to subsets of processes. In Figure~\ref{fig:addD}, processes discard
-last transiting messages. The system converged to the optimal
-partitioning.  Transitive relationships ensure that each process gets
-its closest source while accumulation of weights ensures that messages
-propagation terminates.  Interestingly, while the receipt order of
-messages does not impact on local control information
+partition. At scale, such \emph{scoped flooding} saves bandwidth by
+limiting generated traffic to subsets of
+processes~\cite{wang2015prodiluvian}. In Figure~\ref{fig:addD},
+processes discard last transiting messages. The system converged to
+the optimal partitioning.  Transitive relationships ensure that each
+process gets its closest source while accumulation of weights ensures
+that messages propagation terminates.  Interestingly, while the
+receipt order of messages does not impact on local control information
 ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
@@
 One could solve this issue by using a conflict-free replicated data
-type for set data structures, then deliver and broadcast all
-operations to all processes~\REF. However, this would be costly in
-terms of generated traffic with some processes delivering and
-broadcasting unrelated to their partitions \TODO{(include locality)}.
-One could also solve this issue by removing partitions that were not
-advertised for a defined time~\REF. However, relying on physical
-timeout could lead to either premature removals of partitions when
-they are still operating; or slow convergence where processes believe
-they belong to a partition that was removed.
+type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
+require eventual delivery of messages to ensure convergence. All
+processes need to receive, deliver, hence broadcast all
+operations. Some processes may receive operations unnecessary to their
+correct functioning, for these operations did not happen in their
+locality.  One could also solve this issue by removing partitions that
+were not advertised for a defined
+time~\cite{hemmati2015namebased}. However, relying on physical timeout
+could lead to either premature removals of partitions when they are
+still operating; or slow convergence where processes believe they
+belong to a partition that was removed (\TODO{plot ?}). In addition,
+since timeouts imply a continuous maintenance of partitions, such
+partitioning protocol incurs an overhead even in quiet contexts
+without dynamic partitions.
 
@@
   \caption{\label{fig:del}Partition removals cannot rely only on
-    current partition, for it may lead to inconsistent partitioning.}
+    current partition, for it may lead to either inconsistent
+    partitioning, or every process receiving every broadcast.}
 \end{figure*}
@@
 \begin{problem}[Consistent partitioning]
-  \TODO{How to enable \emph{consistent} dynamic optimal partitioning
-    in dynamic network with contained broadcast?}
+  How to enable \emph{consistent} dynamic optimal partitioning in
+  dynamic network using scoped flooding?
 \end{problem}

### 2021-02-10 input/proposal.tex
wip
rewrite algo, todo test it

@@
 \label{sec:proposal}
+
+\TODO{Remember to say stateless, asynchronous system.}
 
@@
 
-The main idea is maintaining graphs of partitions using local
-knowledge only and use graphs as often as possible: it improves
-resilience to crashes, convergence speed etc. Unfortunately,
-maintaining graphs of partitions in dynamic networks may require the
-use of broadcast tree. The removal of a communication channel between
-2 processes may remove an advantageous path from processes downstream
-to the source of the partition they belong to.
+Each process works autonomously and each change is broadcast to its
+neighborhood, for neighbors may depend on this change as well.
+
+% The main idea is maintaining graphs of partitions using local
+% knowledge only and use graphs as often as possible: it improves
+% resilience to crashes, convergence speed etc. Unfortunately,
+% maintaining graphs of partitions in dynamic networks may require the
+% use of broadcast tree. The removal of a communication channel between
+% 2 processes may remove an advantageous path from processes downstream
+% to the source of the partition they belong to.
 
@@
 \TODO{Probably better to pair operation as ``ins, del'' and ``add, rem''?}
+
+\begin{algorithm}
+  \input{input/algoadddelundo.tex}
+  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
+\end{algorithm}
 
@@
 belong to this partition must choose another partition to belong to.
-To handle dynamic partitions, processes require two additional
-components.
 
-\noindent \textbf{First,} since the number of partitions does not
-monotonically increase in the system any longer, they require a vector
-of versions that monotonically increases over \TODO{add and del}
-operations. This allows processes to quickly discard stale messages
-saving bandwidth. For instance, a process that received a message
-originated at Process $a$ with a version $2$ knows that any message
-originated at Process $a$ with a version $1$ are stale system-wide; it
-must not forward it. As consequence, vectors of versions also ensure
+\noindent Since the number of partitions does not monotonically
+increase in the system any longer, they require a vector of versions
+that monotonically increases over \TODO{add and del} operations. This
+allows processes to quickly discard stale messages saving
+bandwidth. For instance, a process that received a message originated
+at Process $a$ with a version $2$ knows that any message originated at
+Process $a$ with a version $1$ are stale system-wide; it must not
+forward it. As consequence, vectors of versions also ensure
 termination, for messages \TODO{add and del} cannot follow each other
@@
 
-\noindent \textbf{Second,} processes need to maintain a local view of
-their neighbors' partition.  Figure~\ref{fig:del} shows that
-\TODO{deletes} may not propagate properly to all processes in
-need. The path leading to processes delivering $add$ may be broken due
-to concurrent deliveries.  To solve this issue, each process is able
-to know with certainty that each of its neighbor does not need a
-delete (either because it is in another partition, or because another
-path exists from the source to this neighbor). \TODO{More, figures
-  etc.} In terms of traffic, this requires to acknowledge each message
-in a way or another (acknowledgement messages or included in each
-add-del message) using FIFO communication channels. The propagation of
-delete messages is limited to the partition it targets plus uncertain
-processes.
+% \noindent \textbf{Second,} processes need to maintain a local view of
+% their neighbors' partition.  Figure~\ref{fig:del} shows that
+% \TODO{deletes} may not propagate properly to all processes in
+% need. The path leading to processes delivering $add$ may be broken due
+% to concurrent deliveries.  To solve this issue, each process is able
+% to know with certainty that each of its neighbor does not need a
+% delete (either because it is in another partition, or because another
+% path exists from the source to this neighbor). \TODO{More, figures
+%   etc.} In terms of traffic, this requires to acknowledge each message
+% in a way or another (acknowledgement messages or included in each
+% add-del message) using FIFO communication channels. The propagation of
+% delete messages is limited to the partition it targets plus uncertain
+% processes.
 
-\noindent \textbf{Finally,} the delete must trigger another
-competition amongst neighboring partitions. These \TODO{add}
-messages operate normally and fill gaps left open by deletes.
+\noindent Deletes must trigger competition amongst neighboring
+partitions. These \TODO{add} messages operate normally and fill gaps
+left open by deletes.
 

### 2021-02-15 input/figproofA.tex
figures for proofs

\begin{tikzpicture}[scale=0.87]

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

  \newcommand\X{50pt}
  \newcommand\Y{-45pt}

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

  \draw[opacity=0] (-2*\X, 0) -- (3*\X, 0);

  \draw[->] (-\X + 5pt, 0) -- node[above, color=\PA, font=\small]{$\ADD_a^1$} (0 - 5pt, 0); %% a - b

  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% b - ...

  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% ... - c

  \draw[->] ( 0, \Y + 5pt) -- ( 0, -5pt); %% ... - b

  \draw[->] ( -\X + 5pt, \Y ) -- ( -5pt, \Y); %% d - ...

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( 0, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (-\X, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  \draw ( 0, 5pt) node[above, color=\PC]{$\ADD_d^{0.5}$};
  \draw (2*\X, 5pt) node[above]{expect \textcolor{\PA}{$\alpha_a$}};

  \draw (-\X, \Y + 5pt) node[above, color=\PC]{$\DEL_d$};

\end{tikzpicture}

### 2021-02-15 input/figproofB.tex
figures for proofs

\begin{tikzpicture}[scale=0.87]

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

  \newcommand\X{50pt}
  \newcommand\Y{-45pt}

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e

  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - ...

  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% ... - b

  \draw[->] ( 0, \Y + 5pt) -- ( 0, -5pt); %% ... - e

  \draw[->] ( -\X + 5pt, \Y ) -- ( -5pt, \Y); %% f - ...

  \draw[->] ( 5pt, \Y) -- ( \X - 5pt, \Y); % ... - ...

  \draw[->] ( \X + 5pt, \Y + 5pt ) -- ( 2*\X - 5pt, -5pt); % ... - b

  \draw[->] ( 2*\X + 5pt, 0 ) -- ( 3*\X - 5pt, 0); % b - g

  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( 0, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (-\X, \Y) node{$\bm{f}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( \X, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( 3*\X, 0) node{$\bm{g}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PC]{$\DEL_d$};
  \draw ( 0, 5pt) node[above, color=\PB]{$\ADD_f^{0.5}$};
  \draw (2*\X, 5pt) node[above, align=center]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{0.5}}$\\$\textcolor{\PB}{\ADD_f^1} \rightarrow \textcolor{\PB}{\DEL_f} \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};

  \draw (-\X, \Y + 5pt) node[above, color=\PB]{$\DEL_f$};

  \draw (3*\X, -5pt) node[below, align=center]{$\textcolor{\PC}{\ADD_d^{1.5}}$\\expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{1.5}}$};

\end{tikzpicture}

### 2021-02-15 input/proposal.tex
figures for proofs

@@
 left open by deletes.
+
+\begin{figure*}
+  \begin{center}
+    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop up-to-date $\alpha$'s
+    from reaching all processes that require it along the shortest path from $a$ to $c$.
+    To solve this issue, we must guarantee
+    the eventual removal of stale $\alpha$'s (see Figure~\ref{fig:proofB}).]
+    {\input{input/figproofA.tex}}
+    \hspace{10pt}
+    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may stop $\delta$'s from reaching
+    processes with targeted $\alpha$'s. To ensure correctness, $b$ must either
+    deliver $\delta_d$, $\delta_d^{0.5}$, or another $\alpha$, as well as downstream processes
+    that delivered $\alpha$ coming from $b$ such as $g$.]
+    {\input{input/figproofB.tex}}
+    \caption{\label{fig:proof}Dynamic partitioning leads to correctness issues due to
+      staleness and ordering of operations.}
+  \end{center}
+\end{figure*}
 

### 2021-02-17 input/proposal.tex
algos mostly
slight changes, not much

@@
 \label{sec:proposal}
-
-\TODO{Remember to say stateless, asynchronous system.}
 
@@
 
-Each process works autonomously and each change is broadcast to its
-neighborhood, for neighbors may depend on this change as well.
+Each process is stateless, works autonomously and asynchronously, in a
+peer-to-peer fashion. Each process broadcasts each change to its
+neighborhood, for the state of its neighbors may depend on this change
+as well. Yet, generated traffic remains \TODO{low} using scoped
+flooding. Messages that carry changes travel through the network
+depending on partition of processes, stopping as soon as they
+encounter uninterested processes. We demonstrate that \NAME guarantees
+consistent partitioning despite different order in message deliveries
+from one process to another.
 
-% The main idea is maintaining graphs of partitions using local
-% knowledge only and use graphs as often as possible: it improves
-% resilience to crashes, convergence speed etc. Unfortunately,
-% maintaining graphs of partitions in dynamic networks may require the
-% use of broadcast tree. The removal of a communication channel between
-% 2 processes may remove an advantageous path from processes downstream
-% to the source of the partition they belong to.
-
-This section describes \NAME's components by starting from the
-simplest case of add-only partition, to the most complex case of
-dynamic partitions in dynamic networks.
-
-\TODO{Probably better to pair operation as ``ins, del'' and ``add, rem''?}
+This section describes \NAME's components and algorithms. First, it
+starts by detailing a logical partitioning protocol in static
+network. Second, it extends such protocol to dynamic systems. Last, it
+describes an optimization based on Bloom filter.
 
@@
 
-\paragraph{Static network with add-only.}
-At any time, a process can become a source, hence \TODO{creating} a
-new partition in the system. This partition eventually includes all
+\subsection{Dynamic partitions}
+
+At any time, a process can become a source, hence adding a new
+partition to the system. This partition eventually includes all
 processes that are closer from this new source than any other else. We
@@
 piggybacking a monotonically increasing distance in forwarded
-messages.  \TODO{Traffic of each partition is contained to the
-  partition.}
+messages. % \TODO{Traffic of each partition is contained to the
+%  partition.}
 
-\paragraph{Static network with dynamic partitions.}
-At any time, a source can revoke its self-appointed status of source,
-hence \TODO{removing} its partition of the system. All processes that
-belong to this partition must choose another partition to belong to.
+Then, at any time, a source can revoke its self-appointed status of
+source, hence deleting its partition from the system. All processes
+that belong to this partition must eventually choose another partition
+to belong to. Since the number of partitions does not monotonically
+increase in the system any longer, each process requires a vector of
+versions that monotonically increases over delivered operations.
 
-\noindent Since the number of partitions does not monotonically
-increase in the system any longer, they require a vector of versions
-that monotonically increases over \TODO{add and del} operations. This
-allows processes to quickly discard stale messages saving
+This allows processes to quickly discard stale messages saving
 bandwidth. For instance, a process that received a message originated
@@
 
-\paragraph{Networks with new communication links.}
+\subsection{Dynamic networks}
 Adding new communication links to the network may create shortcuts
@@
 
-\paragraph{Dynamic networks with dynamic partitions.}
+\begin{algorithm}
+  \input{input/algoedges.tex}
+  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
+\end{algorithm}
+
 When removing a communication link between two processes does not
@@
 
-\paragraph{A last optimisation}
+\subsection{A last optimization}
 \TODO{Carry information that is useless. such as order of processes in

### 2021-02-22 input/proposal.tex
a4 not so easy after all

@@
-\section{Dynamic partitioning}
+\section{\NAME for Dynamic Partitioning}
 \label{sec:proposal}
@@
 In this section, we introduce \NAME, (\TODO{stands for}) a reactive
-protocol for logical partitioning the cost of which actually depends
-on its usage: when the system becomes quiescent, processes eventually
-converge to their respective partition and do not require further
-communication afterwards.
+protocol for logical partitioning in autonomous sytems the cost of
+which actually depends on its usage: when the system becomes
+quiescent, processes eventually converge to their respective partition
+and do not require further communication afterwards.
 
@@
 
+\subsection{Autonomous systems}
+
+Autonomous systems are geo-distributed networks. Heterogenous
+communication links. Hierarchy of communication links. Per-object
+broadcast.
+
+We leave the link handling to membership protocols~\REF. The ordering
+of links can be done based on latency. For instance, from 0 to 100 ms,
+rank 0, from 100 to 1s, rank 2 \ldots
+
+\begin{algorithm}
+  \input{input/algoaaaa.tex}
+  \caption{\label{algo:aaaa}Primitives for general purpose logical
+    partitioning in dynamic systems.}
+\end{algorithm}
+
+\TODO{Not so easy\ldots}
+
+\subsection{Dynamic partitions}
+
 \begin{algorithm}
@@
 \end{algorithm}
-
-\subsection{Dynamic partitions}
 

### 2021-02-23 input/figAS.tex
inter AS figure + lighter figures

\begin{tikzpicture}[scale=0.92]

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

  \newcommand\ADD{\alpha}

  \draw (-1.5*\X, 0 - 5pt)
  node[below, circle, draw=black, fill=white, scale=0.35]{\large{0}}
  --  
  (-1.5*\X, \Y + 5pt)
  node[above, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% a - e

  \draw (-1.5*\X + 5pt, 0)
  node[right, circle, draw=black, fill=white, scale=0.35]{\large{1}}
  --
  (-1*\X, 0);

  \draw[dotted] (-1*\X, 0) -- (-0.5*\X, 0);

  \draw (-0.5*\X, 0)
  --  
  (0 - 5pt, 0)
  node[left, circle, draw=black, fill=white, scale=0.35]{\large{2}}; %% a - b

  \draw (0 +5pt, 0)
  node[right, circle, draw=black, fill=white, scale=0.35]{\large{1}}
  --
  (\X -5pt, 0)
  node[left, circle, draw=black, fill=white, scale=0.35]{\large{1}}; %% b - c

  \draw (0, 0 - 5pt)
  node[below, circle, draw=black, fill=white, scale=0.35]{\large{0}}
  --
  (0, \Y + 5pt)
  node[above, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% b - d

  \draw (\X + 3pt, 0 - 5pt)
  node[below left, circle, draw=black, fill=white, scale=0.35]{\large{0}}
  --
  (0 + 5pt, \Y - 3pt)
  node[above right, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% c - d

  \draw[dashed] (-0.75*\X, -0.5*\Y) -- (-0.75*\X, 1.5*\Y)
  node[above left]{\textit{AS 1}}
  node[above right]{\textit{AS 2}};

  \draw[fill=white] (-1.5*\X, 0) node[color=\PA]{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw [left] (-1.5*\X - 5pt, 0) node{\textbf{e: 1}};
  \draw[fill=white] (0, 0) node[color=\PA]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw [above] ( 0, 5pt ) node{\textbf{e: 2}};
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] (-1.5*\X, \Y) node[color=\PA]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw [left] (-1.5*\X - 5pt, \Y) node{\textbf{e: 0}};

  % \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  % \draw (\X, 5pt) node[above, color=\PC]{$\ADD_c^0$};

\end{tikzpicture}

### 2021-02-23 input/figaddA.tex
coloring figures, adding biblio, sketching abstract
inter AS figure + lighter figures

--- 2020-10-08 input/figaddA.tex
@@
-\begin{tikzpicture}[scale=1]
+\begin{tikzpicture}[scale=0.87]
+
+  \thickmuskip=0mu
+  \medmuskip=0mu
+  \thinmuskip=0mu
 
@@
 
-  \draw[fill=white] (0, 0) node{$\bm{a}$} +(-5, -5) rectangle +(5, 5);
+  \newcommand\ADD{\alpha}
+
+  \draw (-\X + 5pt, 0) -- (0 - 5pt, 0); %% a - b
+
+  \draw (0 +5pt, 0) -- (\X -5pt, 0); %% b - c
+
+  \draw (0, 0 - 5pt) -- (0, \Y + 5pt); %% d - b
+
+  \draw (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d
+
+  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
+  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+
+  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
+  \draw (\X, 5pt) node[above, color=\PC]{$\ADD_c^0$};
 

### 2021-02-23 input/proposal.tex
inter AS figure + lighter figures

@@
 In this section, we introduce \NAME, (\TODO{stands for}) a reactive
-protocol for logical partitioning in autonomous sytems the cost of
+protocol for logical partitioning in autonomous systems the cost of
 which actually depends on its usage: when the system becomes
@@
 
-Autonomous systems are geo-distributed networks. Heterogenous
+\begin{figure}
+  \centering\input{input/figAS.tex}
+  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
+      issue not introduced in background}}
+\end{figure}
+
+Autonomous systems are geo-distributed networks. Heterogeneous
 communication links. Hierarchy of communication links. Per-object
@@
 \end{algorithm}
+
+Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
+where each process ranks its communication links, and each process
+forwards messages to its neighbors starting from the rank of the link
+that triggered the receipt, to its highest rank neighbors. In this
+example, Process $e$ adds a partition. It forwards the generated
+message to all its neighbors as if it received it from its lowest rank
+links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
+it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
+stops the propagation, for all its links have lower ranks than the one
+from which it received the message $\alpha_e^2$. Ultimately, the
+partition includes Process $e$, Process $a$, and Process $b$. Process
+$c$ and Process $d$ remain unaware of the new \TODO{object}.
 

### 2021-02-24 input/proposal.tex
reworkd algo a4

@@
 
-\TODO{Not so easy\ldots}
+To ease the reasoning about inter-AS dynamic partitioning in dynamic
+networks, \NAME runs an independant broadcast protocol for each
+object, and for each rank of links.  \TODO{Not so easy\ldots}
+\TODO{Write and describe algo.} \TODO{Overhead of separating things,
+  slightly more memory, but traffic wise? slower ?}  \TODO{In the
+  example, not only Process $b$ keeps $e_1$ as its best partition, but
+  it keeps it for links of rank 0, and links of rank 1.}
+
+The rest of this section describes our proposal to solve these smaller
+scientific problems. It first tackles dynamic partitions where
+processes can add or delete partitions resulting in stale information
+that may impair correctness. It then tackles dynamic networks where
+edges appear and disappear at any time resulting in invalid
+information that may impair correctness.
 
@@
 forward it. As consequence, vectors of versions also ensure
-termination, for messages \TODO{add and del} cannot follow each other
-in an infinite loop. In terms of traffic, this only requires each
-\TODO{delete} message to piggyback a source identifier and version
-number.
+termination, for corresponding add and delete messages cannot follow
+each other in an infinite loop. In terms of traffic, this only
+requires each \TODO{delete} message to piggyback a source identifier
+and version number.
 

### 2021-02-26 input/background.tex
wip
mostly about AS

@@
 Fog infrastructures are distributed systems comprising heterogeneous
-machines interconnected by communication links.
+machines interconnected by communication links. We do not consider
+byzantine processes.
 
@@
   V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
-  w_{ij}$ with $i, j \in V$.
+  w_{ji}$ with $i, j \in V$.
 \end{definition}
@@
 
-Processes belong to logical partitions depending on path lengths. When
-weights are latency or hop numbers, the optimal partitioning consists
-in processing the multiple destinations shortest path at each process
-\REF.
+Processes belong to logical partitions depending on path weights. When
+weights are about latency or hop numbers, the optimal partitioning
+consists in processing the multiple destinations shortest path at each
+process \REF.
 
@@
 
+\input{input/figdel.tex} %% figure positioning
+
 \begin{definition}[\label{def:transitivedelivery}Transitive delivery]
@@
 \end{definition}
-
-\begin{figure*}
-  \begin{center}
-    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
-      Process $c$ initiate a partition.
-      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
-    \hspace{5pt}
-    \subfloat[Part B][\label{fig:addB}Messages transit through communication
-      links and carry increasing weights.]{\input{input/figaddB.tex}}
-    \hspace{5pt}
-    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
-      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
-      is higher.]{\input{input/figaddC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
-      incoming messages. The system converged to optimal partitions.]{
-      \input{input/figaddD.tex}}
-    \caption{\label{fig:add}Simple accumulation in messages makes the
-      system converge to optimal partitions with scoped flooding.}
-  \end{center}
-\end{figure*}
 
@@
 
+Unfortunately, due to differences in receipt order of messages between
+processes, stale information may stop prematurely the propagation of
+relevant messages leading to inconsistent partitioning.
 \TODO{Figure~\ref{fig:del} shows that.}
@@
 
-\begin{figure*}
-  \begin{center}
-    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
-      Process $c$ initiate then remove a partition.
-      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
-    \hspace{5pt}
-    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
-      messages based on their weights. $a$'s partition propagates to all processes.]
-             {\input{input/figdelB.tex}}
-    \hspace{5pt}
-    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
-      Its removal shortly follows. Process $b$ does not have any control
-      information about partitions any more.]{\input{input/figdelC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
-      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
-      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
-      partition.]{\input{input/figdelD.tex}}
-  \end{center}
-  \caption{\label{fig:del}Partition removals cannot rely only on
-    current partition, for it may lead to either inconsistent
-    partitioning, or every process receiving every broadcast.}
-\end{figure*}
-
 \begin{problem}[Consistent partitioning]
@@
 
-\TODO{Dynamic Multiple-sources All-destinations shortest path on
-  dynamic graphs?}
+% \TODO{Dynamic Multiple-sources All-destinations shortest path on
+%  dynamic graphs?}
+
+\begin{figure}
+  \begin{center}
+    \input{input/figASmotivation.tex}
+    \caption{\label{fig:ASmotivation}Scoped flooding extended to
+      objects, processes do not know about all partitions that exist
+      in the whole distributed system.}
+  \end{center}
+\end{figure}
+
+To further improve scoped flooding in autonomous systems, processes
+may belong to multiple partitions representing the objects they are
+aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
+nature of autonomous systems. Autonomous systems have topological
+properties~\cite{nur2018geography} that processes can leverage to
+avoid flooding the whole systems with control information about all
+partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
+partition about a specific object, flooding Paris's AS to notify
+neighboring processes of the object. However, it does not flood the
+whole network, for control information stops at Process $b$. It
+significantly saves bandwidth compared to broadcast since processes
+below entrypoints of autonomous systems are order of magnitude more
+numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
+to return an object they are unaware of. Processes remain efficient in
+answering requests. \TODO{which is important for end users \REF.}
+
+\begin{definition}[Partitions in asynchronous systems]
+  Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
+  \TODO{TODO}
+\end{definition}
+
+\begin{problem}[Consistent partitioning in AS]
+  How to enable scoped flooding of objects in autonomous systems?
+\end{problem}
 

### 2021-02-26 input/figASmotivation.tex
mostly about AS

--- 2021-02-23 input/figAS.tex
@@
-\begin{tikzpicture}[scale=0.92]
+\begin{tikzpicture}[scale=1]
 
@@
 
-  \draw (-1.5*\X, 0 - 5pt)
-  node[below, circle, draw=black, fill=white, scale=0.35]{\large{0}}
-  --  
-  (-1.5*\X, \Y + 5pt)
-  node[above, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% a - e
+  \draw (-1.5*\X, \Y + 5pt)
+  -- node[above, font=\scriptsize, sloped]{$10ms$}
+  (-1.5*\X, 0 - 5pt); %% a-e
 
   \draw (-1.5*\X + 5pt, 0)
-  node[right, circle, draw=black, fill=white, scale=0.35]{\large{1}}
   --
@@
 
-  \draw[dotted] (-1*\X, 0) -- (-0.5*\X, 0);
+  \draw[dotted] (-1*\X, 0) --
+  node[above, font=\scriptsize]{$300ms$} (-0.5*\X, 0);
 
@@
   --  
-  (0 - 5pt, 0)
-  node[left, circle, draw=black, fill=white, scale=0.35]{\large{2}}; %% a - b
+  (0 - 5pt, 0); %% a - b
 
   \draw (0 +5pt, 0)
-  node[right, circle, draw=black, fill=white, scale=0.35]{\large{1}}
-  --
-  (\X -5pt, 0)
-  node[left, circle, draw=black, fill=white, scale=0.35]{\large{1}}; %% b - c
+  -- node[above, font=\scriptsize, sloped]{$15ms$}  
+  (\X -5pt, 0); %% b - c
 
-  \draw (0, 0 - 5pt)
-  node[below, circle, draw=black, fill=white, scale=0.35]{\large{0}}
-  --
-  (0, \Y + 5pt)
-  node[above, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% b - d
+  \draw (0, \Y + 5pt)
+  -- node[above, font=\scriptsize, sloped]{$20ms$}  
+  (0, 0 - 5pt); %% b - d
 
   \draw (\X + 3pt, 0 - 5pt)
-  node[below left, circle, draw=black, fill=white, scale=0.35]{\large{0}}
-  --
-  (0 + 5pt, \Y - 3pt)
-  node[above right, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% c - d
+  -- node[above, font=\scriptsize, sloped]{$10ms$}  
+  (0 + 5pt, \Y - 3pt); %% c - d
 
   \draw[dashed] (-0.75*\X, -0.5*\Y) -- (-0.75*\X, 1.5*\Y)
-  node[above left]{\textit{AS 1}}
-  node[above right]{\textit{AS 2}};
+  node[above left]{\textit{(FR) Paris -- AS 1 \vphantom{g}}}
+  node[above right]{\textit{AS 2 -- Wellington (NZ)}};
 

### 2021-02-26 input/figadd.tex
mostly about AS

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with scoped flooding.}
  \end{center}
\end{figure*}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-02-26 input/figdel.tex
mostly about AS

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{fig:del}Partition removals cannot rely only on
    current partition, for it may lead to either inconsistent
    partitioning, or every process receiving every broadcast.}
\end{figure*}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-02-26 input/proposal.tex
mostly about AS

@@
 network. Second, it extends such protocol to dynamic systems. Last, it
-describes an optimization based on Bloom filter.
-
-\subsection{Autonomous systems}
-
-\begin{figure}
-  \centering\input{input/figAS.tex}
-  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
-      issue not introduced in background}}
-\end{figure}
-
-Autonomous systems are geo-distributed networks. Heterogeneous
-communication links. Hierarchy of communication links. Per-object
-broadcast.
-
-We leave the link handling to membership protocols~\REF. The ordering
-of links can be done based on latency. For instance, from 0 to 100 ms,
-rank 0, from 100 to 1s, rank 2 \ldots
-
-\begin{algorithm}
-  \input{input/algoaaaa.tex}
-  \caption{\label{algo:aaaa}Primitives for general purpose logical
-    partitioning in dynamic systems.}
-\end{algorithm}
-
-Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
-where each process ranks its communication links, and each process
-forwards messages to its neighbors starting from the rank of the link
-that triggered the receipt, to its highest rank neighbors. In this
-example, Process $e$ adds a partition. It forwards the generated
-message to all its neighbors as if it received it from its lowest rank
-links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
-it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
-stops the propagation, for all its links have lower ranks than the one
-from which it received the message $\alpha_e^2$. Ultimately, the
-partition includes Process $e$, Process $a$, and Process $b$. Process
-$c$ and Process $d$ remain unaware of the new \TODO{object}.
-
-To ease the reasoning about inter-AS dynamic partitioning in dynamic
-networks, \NAME runs an independant broadcast protocol for each
-object, and for each rank of links.  \TODO{Not so easy\ldots}
-\TODO{Write and describe algo.} \TODO{Overhead of separating things,
-  slightly more memory, but traffic wise? slower ?}  \TODO{In the
-  example, not only Process $b$ keeps $e_1$ as its best partition, but
-  it keeps it for links of rank 0, and links of rank 1.}
-
-The rest of this section describes our proposal to solve these smaller
-scientific problems. It first tackles dynamic partitions where
-processes can add or delete partitions resulting in stale information
-that may impair correctness. It then tackles dynamic networks where
-edges appear and disappear at any time resulting in invalid
-information that may impair correctness.
+describes an optimization based on Bloom filter. \TODO{More more
+  more. Thousands of pages paper it seems.}
 
@@
 
+\subsection{Autonomous systems}
+
+\begin{figure}
+  \centering\input{input/figAS.tex}
+  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
+      issue not introduced in background}}
+\end{figure}
+
+Autonomous systems are geo-distributed networks. Heterogeneous
+communication links. Hierarchy of communication links. Per-object
+broadcast.
+
+We leave the link handling to membership protocols~\REF. The ordering
+of links can be done based on latency. For instance, from 0 to 100 ms,
+rank 0, from 100 to 1s, rank 2 \ldots
+
+\begin{algorithm}
+  \input{input/algoaaaa.tex}
+  \caption{\label{algo:aaaa}Primitives for general purpose logical
+    partitioning in dynamic systems.}
+\end{algorithm}
+
+Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
+where each process ranks its communication links, and each process
+forwards messages to its neighbors starting from the rank of the link
+that triggered the receipt, to its highest rank neighbors. In this
+example, Process $e$ adds a partition. It forwards the generated
+message to all its neighbors as if it received it from its lowest rank
+links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
+it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
+stops the propagation, for all its links have lower ranks than the one
+from which it received the message $\alpha_e^2$. Ultimately, the
+partition includes Process $e$, Process $a$, and Process $b$. Process
+$c$ and Process $d$ remain unaware of the new \TODO{object}.
+
+To ease the reasoning about inter-AS dynamic partitioning in dynamic
+networks, \NAME runs an independant broadcast protocol for each
+object, and for each rank of links.  \TODO{Not so easy\ldots}
+\TODO{Write and describe algo.} \TODO{Overhead of separating things,
+  slightly more memory, but traffic wise? slower ?}  \TODO{In the
+  example, not only Process $b$ keeps $e_1$ as its best partition, but
+  it keeps it for links of rank 0, and links of rank 1.}  When there
+are no ranking in links, processes solely rely on
+Algorithm~\ref{algo:adddelundo} for optimal partitioning.
+
 \subsection{Complexity}

### 2021-03-01 input/background.tex
structure

@@
 were not advertised for a defined
-time~\cite{hemmati2015namebased}. However, relying on physical timeout
-could lead to either premature removals of partitions when they are
-still operating; or slow convergence where processes believe they
-belong to a partition that was removed (\TODO{plot ?}). In addition,
-since timeouts imply a continuous maintenance of partitions, such
-partitioning protocol incurs an overhead even in quiet contexts
-without dynamic partitions.
+time~\cite{hemmati2015namebased}. \TODO{check distance-vector
+  protocols.} However, relying on physical timeout could lead to
+either premature removals of partitions when they are still operating;
+or slow convergence where processes believe they belong to a partition
+that was removed (\TODO{plot ?}). In addition, since timeouts imply a
+continuous maintenance of partitions, such partitioning protocol
+incurs an overhead even in quiet contexts without dynamic partitions.
 
-\begin{problem}[Consistent partitioning]
+\begin{problem}[\label{prob:intra}Consistent partitioning]
   How to enable \emph{consistent} dynamic optimal partitioning in
@@
   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
-  \TODO{TODO}
+  \TODO{TODO} \TODO{or multi-partitioning?}
 \end{definition}
 
-\begin{problem}[Consistent partitioning in AS]
+\begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
   How to enable scoped flooding of objects in autonomous systems?
@@
 
-\TODO{Next Section presents our approach that solves this problem
-  statement by relying only on logical control information.}
+Next Section presents our approach that solves these scientific
+problems by relying on logical control information only.
 

### 2021-03-01 input/figproof.tex
structure

--- 2021-02-23 input/proposal.tex
@@
-\section{\NAME for Dynamic Partitioning}
-\label{sec:proposal}
-
-In this section, we introduce \NAME, (\TODO{stands for}) a reactive
-protocol for logical partitioning in autonomous systems the cost of
-which actually depends on its usage: when the system becomes
-quiescent, processes eventually converge to their respective partition
-and do not require further communication afterwards.
-
-Each process is stateless, works autonomously and asynchronously, in a
-peer-to-peer fashion. Each process broadcasts each change to its
-neighborhood, for the state of its neighbors may depend on this change
-as well. Yet, generated traffic remains \TODO{low} using scoped
-flooding. Messages that carry changes travel through the network
-depending on partition of processes, stopping as soon as they
-encounter uninterested processes. We demonstrate that \NAME guarantees
-consistent partitioning despite different order in message deliveries
-from one process to another.
-
-This section describes \NAME's components and algorithms. First, it
-starts by detailing a logical partitioning protocol in static
-network. Second, it extends such protocol to dynamic systems. Last, it
-describes an optimization based on Bloom filter.
-
-\subsection{Autonomous systems}
-
-\begin{figure}
-  \centering\input{input/figAS.tex}
-  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
-      issue not introduced in background}}
-\end{figure}
-
-Autonomous systems are geo-distributed networks. Heterogeneous
-communication links. Hierarchy of communication links. Per-object
-broadcast.
-
-We leave the link handling to membership protocols~\REF. The ordering
-of links can be done based on latency. For instance, from 0 to 100 ms,
-rank 0, from 100 to 1s, rank 2 \ldots
-
-\begin{algorithm}
-  \input{input/algoaaaa.tex}
-  \caption{\label{algo:aaaa}Primitives for general purpose logical
-    partitioning in dynamic systems.}
-\end{algorithm}
-
-Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
-where each process ranks its communication links, and each process
-forwards messages to its neighbors starting from the rank of the link
-that triggered the receipt, to its highest rank neighbors. In this
-example, Process $e$ adds a partition. It forwards the generated
-message to all its neighbors as if it received it from its lowest rank
-links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
-it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
-stops the propagation, for all its links have lower ranks than the one
-from which it received the message $\alpha_e^2$. Ultimately, the
-partition includes Process $e$, Process $a$, and Process $b$. Process
-$c$ and Process $d$ remain unaware of the new \TODO{object}.
-
-\TODO{Not so easy\ldots}
-
-\subsection{Dynamic partitions}
-
-\begin{algorithm}
-  \input{input/algoadddelundo.tex}
-  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
-\end{algorithm}
-
-At any time, a process can become a source, hence adding a new
-partition to the system. This partition eventually includes all
-processes that are closer from this new source than any other else. We
-described such protocol in Section~\ref{sec:background}. Processes
-naturally converge towards their respective best partition by only
-piggybacking a monotonically increasing distance in forwarded
-messages. % \TODO{Traffic of each partition is contained to the
-%  partition.}
-
-Then, at any time, a source can revoke its self-appointed status of
-source, hence deleting its partition from the system. All processes
-that belong to this partition must eventually choose another partition
-to belong to. Since the number of partitions does not monotonically
-increase in the system any longer, each process requires a vector of
-versions that monotonically increases over delivered operations.
-
-This allows processes to quickly discard stale messages saving
-bandwidth. For instance, a process that received a message originated
-at Process $a$ with a version $2$ knows that any message originated at
-Process $a$ with a version $1$ are stale system-wide; it must not
-forward it. As consequence, vectors of versions also ensure
-termination, for messages \TODO{add and del} cannot follow each other
-in an infinite loop. In terms of traffic, this only requires each
-\TODO{delete} message to piggyback a source identifier and version
-number.
-
-% \noindent \textbf{Second,} processes need to maintain a local view of
-% their neighbors' partition.  Figure~\ref{fig:del} shows that
-% \TODO{deletes} may not propagate properly to all processes in
-% need. The path leading to processes delivering $add$ may be broken due
-% to concurrent deliveries.  To solve this issue, each process is able
-% to know with certainty that each of its neighbor does not need a
-% delete (either because it is in another partition, or because another
-% path exists from the source to this neighbor). \TODO{More, figures
-%   etc.} In terms of traffic, this requires to acknowledge each message
-% in a way or another (acknowledgement messages or included in each
-% add-del message) using FIFO communication channels. The propagation of
-% delete messages is limited to the partition it targets plus uncertain
-% processes.
-
-\noindent Deletes must trigger competition amongst neighboring
-partitions. These \TODO{add} messages operate normally and fill gaps
-left open by deletes.
-
 \begin{figure*}
@@
 \end{figure*}
-
-\subsection{Dynamic networks}
-Adding new communication links to the network may create shortcuts
-between processes. Both processes must send their current best
-partition to each other. Upon receipt, they act normally: if a process
-finds out that the received partition is closer than its current one,
-it delivers it which in turns also triggers another competition
-amongst neighbors due to forwarding.
-
-\noindent Joining the network is equivalent to add as many
-communication links as necessary between the joining process and its
-new neighbors.
-
-\begin{algorithm}
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
-\end{algorithm}
-
-When removing a communication link between two processes does not
-break any active path, because neither distances of processes depend
-on the other, then nothing needs to be done. \NAME has no overhead.
-Unfortunately, when a process' distance depends on the other process,
-the protocol becomes much more complex. Indeed, this requires to
-\TODO{undo} all add messages originated from this process. A message
-must convey the fact that
-\begin{inparaenum}[(i)]
-\item an edge at a particular process has been removed, and
-\item the distance that has been delivered by a process comes from
-  this particular process.
-\end{inparaenum}
-
-\noindent \NAME handles this as a particular case of partition within
-current partition: it contains to affected regions the traffic
-generated to patch affected regions. In order to know if it is
-affected by the \TODO{undo} operation, using distances already
-piggybacked in messages is not sufficient.  Each process must know the
-path taken by delivered message. Since we do not beforehand which
-communication links will crash and which messages will be affected by
-undos, each message has to carry its path along forwarding. This also
-allows processes to remove loops, for they cannot rely on version
-number (that remains unchanged) for this operation.
-
-\noindent Instead of version number, one could use such paths to remove loops
-due to \TODO{add and del}, however this may be much more costly in
-terms of generated traffic. Version numbers guarantee that only one
-delete is delivered and all prior inserts are then discarded, while
-using paths, processes may deliver multiple inserts and deletes before
-reaching termination. \TODO{maybe clearer with figures.} As
-consequence, \NAME still makes use of vector of versions.
-
-\noindent Although costly, piggybacking paths with logical partitioning synergies
-well, for the size of these paths decreases quickly as the number of
-partitions grows.
-
-\subsection{A last optimization}
-\TODO{Carry information that is useless. such as order of processes in
-  paths, and identities of processes themselves.} \TODO{Icarus for
-  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
-  know the dimension of networks and
-  partitions~\cite{almeida2007scalable}}.
-
-\subsection{Complexity}
-\label{subsec:complexity}
-
-\TODO{To rework, for there are more components now. Maybe do this
-  along the description of the approach.}
-
-We focus on average-case and worst-case complexity. We divide our
-analysis into space, time, and communication complexity.
-
-\textbf{The communication complexity} concerns the size and number of
-messages required to reach optimal partitioning. In the average-case,
-a process $i$ chosen uniformly at random among all processes creates a
-logical partition. Its messages $\alpha_i$ propagate through the
-network until reaching processes that belong to another partition
-closer to them. This splits partitions in half in average. Overall,
-the $a^{th}$ new partition comprises
-\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
-processes. This decreases every new partition until reaching $0$
-processes per new partition: even the chosen process already belongs
-to its optimal partition. The average number of messages per process
-is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
-      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
-  more messages (receipt bounded by $|O|$ as well).} Deleting the
-$a^{th}$ partition generates the exact same number of messages than
-the $a^{th}$ partition creation. \TODO{But what about echos?} In the
-worst-case, every new partition includes all but one process belonging
-to the previous partition. The total number of messages after the
-$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
-for the average-case, the number of messages for the partition
-deletion is identical to the number of messages of the corresponding
-partition creation.
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "../paper"
-%%% ispell-local-dictionary: "english"
-%%% End:

### 2021-03-01 input/proposal.tex
structure

@@
 
-In this section, we introduce \NAME, (\TODO{stands for}) a reactive
-protocol for logical partitioning in autonomous systems the cost of
-which actually depends on its usage: when the system becomes
-quiescent, processes eventually converge to their respective partition
-and do not require further communication afterwards.
+In this section, we introduce \NAME (\TODO{stands for}) and its
+\underline{ex}tension \NAMEB, reactive protocols for logical
+partitioning in autonomous systems the cost of which actually depends
+on their usage: when the system becomes quiescent, processes
+eventually converge to their respective partition and do not require
+further communication afterward.
 
@@
 consistent partitioning despite different order in message deliveries
-from one process to another.
+from one process to another. While \NAME is a general purpose logical
+partitioning protocol for dynamic networks, \NAMEB further reduces
+generated traffic in the context of inter-autonomous systems by
+leveraging the hierarchical properties of such networks.
 
-This section describes \NAME's components and algorithms. First, it
-starts by detailing a logical partitioning protocol in static
-network. Second, it extends such protocol to dynamic systems. Last, it
-describes an optimization based on Bloom filter. \TODO{More more
-  more. Thousands of pages paper it seems.}
+This section starts by describing \NAME's functioning by detailing its
+operation to avoid inconsistent states due to ordering and staleness
+of delivered messages. Then, it describes its extension \NAMEB that
+builds multiple broadcast layers ordered using local knowledge only.
+Finally, it ends with a complexity analysis of proposed protocols.
 
-\subsection{Dynamic partitions}
+\subsection{Intra-autonomous system partitioning}
 
@@
 
+\input{input/figproof.tex}
+
+In this section, we aim at solving Problem Statement~\ref{prob:intra}
+by proposing \NAME, a reactive logical partitioning protocol for
+dynamic partitioning in dynamic networks.
+
+\paragraph{Dynamic partitions.}
 At any time, a process can become a source, hence adding a new
@@
 Process $a$ with a version $1$ are stale system-wide; it must not
-forward it. As consequence, vectors of versions also ensure
-termination, for corresponding add and delete messages cannot follow
-each other in an infinite loop. In terms of traffic, this only
-requires each \TODO{delete} message to piggyback a source identifier
-and version number.
-
-% \noindent \textbf{Second,} processes need to maintain a local view of
-% their neighbors' partition.  Figure~\ref{fig:del} shows that
-% \TODO{deletes} may not propagate properly to all processes in
-% need. The path leading to processes delivering $add$ may be broken due
-% to concurrent deliveries.  To solve this issue, each process is able
-% to know with certainty that each of its neighbor does not need a
-% delete (either because it is in another partition, or because another
-% path exists from the source to this neighbor). \TODO{More, figures
-%   etc.} In terms of traffic, this requires to acknowledge each message
-% in a way or another (acknowledgement messages or included in each
-% add-del message) using FIFO communication channels. The propagation of
-% delete messages is limited to the partition it targets plus uncertain
-% processes.
+forward it. As consequence, this also ensure termination, for
+corresponding add and delete messages cannot follow each other in
+infinite loops.
+% In terms of traffic, this only requires each message
+% to piggyback a source identifier and version number.
 
@@
 
-\begin{figure*}
-  \begin{center}
-    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop up-to-date $\alpha$'s
-    from reaching all processes that require it along the shortest path from $a$ to $c$.
-    To solve this issue, we must guarantee
-    the eventual removal of stale $\alpha$'s (see Figure~\ref{fig:proofB}).]
-    {\input{input/figproofA.tex}}
-    \hspace{10pt}
-    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may stop $\delta$'s from reaching
-    processes with targeted $\alpha$'s. To ensure correctness, $b$ must either
-    deliver $\delta_d$, $\delta_d^{0.5}$, or another $\alpha$, as well as downstream processes
-    that delivered $\alpha$ coming from $b$ such as $g$.]
-    {\input{input/figproofB.tex}}
-    \caption{\label{fig:proof}Dynamic partitioning leads to correctness issues due to
-      staleness and ordering of operations.}
-  \end{center}
-\end{figure*}
+\TODO{Paths and \NAME synergize well, for paths tend to be smaller as the
+number of sources increase in the system.}
 
-\subsection{Dynamic networks}
+\paragraph{Dynamic networks.}
 Adding new communication links to the network may create shortcuts
@@
 
-\subsection{A last optimization}
-\TODO{Carry information that is useless. such as order of processes in
-  paths, and identities of processes themselves.} \TODO{Icarus for
-  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
-  know the dimension of networks and
-  partitions~\cite{almeida2007scalable}}.
+\paragraph{A last optimization.}
+\NAME makes extensive use of paths to enable deleting messages without
+incrementing local counters. Messages carry their respective path and
+processes detect when such messages have been looping when they carry
+their identity (see Lines~\ref{line:notloopingA} and
+\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
+membership is all that matters, we propose to trade vectors of
+identities for Bloom filters~\cite{almeida2007scalable} to improve on
+generated traffic and
+anonymity~\cite{whitaker2002forwarding}. Processes know with high
+probability if they already received and forwarded each message
+without knowing the identity of all processes that received it.  False
+positive probability only incurs premature stopping of broadcast
+messages and does not invalidate the delete of specific messages.
 
-\subsection{Autonomous systems}
+\subsection{Inter-autonomous system partitioning}
 
@@
   \centering\input{input/figAS.tex}
-  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
-      issue not introduced in background}}
+  \caption{\label{fig:AS}Inter autonomous systems
+    partitioning. \TODO{More about relative ordering of links at each
+      process}}
 \end{figure}
+
+In this section, we aim at solving Problem Statement~\ref{prob:inter}
+by proposing \NAMEB, an extension of \NAME, that enables dynamic
+logical partitioning in inter-autonomous systems. It leverages
+hierarchical properties of these networks to further improve on scoped
+flooding.
 
@@
   \input{input/algoaaaa.tex}
-  \caption{\label{algo:aaaa}Primitives for general purpose logical
-    partitioning in dynamic systems.}
+  \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
+    partitioning in inter-autonomous systems.}
 \end{algorithm}
@@
 To ease the reasoning about inter-AS dynamic partitioning in dynamic
-networks, \NAME runs an independant broadcast protocol for each
+networks, \NAME runs an independent broadcast protocol for each
 object, and for each rank of links.  \TODO{Not so easy\ldots}

### 2021-03-08 input/background.tex
maybe start by defining scoped broadcast

@@
 \begin{definition}[Fog infrastructure]
-  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
+  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
@@
 \end{definition}
+
+Processes can send messages to their neighboring processes. Processes
+can reliably broadcast messages by forwarding delivered
+messages~\cite{nedelec2018causal,raynal2013distributed}. However,
+reliable broadcast definition states that \emph{all} correct processes
+should deliver broadcast messages. This proves costly in large scale
+systems comprising thousands of processes. Instead, we define
+\emph{scoped broadcast} where messages reach only interested
+processes, significantly reducing generated traffic.
+
+\begin{definition}[Scoped broadcast]
+  \TODO{meow predicate, meow path, meow state, meow message.}
+\end{definition}
+
+This definition highlights the transitive relevance of sent messages
+and encompasses more specific definitions of related
+work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
+process from Paris could scoped broadcast a message to all processes
+in this city. A process from Paris could scoped broadcast a message to
+all processes in this city plus neighboring cities by overloading
+forwarded messages the first time they reach another city. As for
+reliable broadcast, there exists different trade-off on space, time,
+and communication.
 

### 2021-03-10 input/background.tex
wip

@@
   A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
-  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
-  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
-  w_{ji}$ with $i, j \in V$.
+  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
+  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from Process
+  $i$ to Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
+    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
+  \pi_{ij}[m+1] \rangle \in E$.
 \end{definition}
@@
 can reliably broadcast messages by forwarding delivered
-messages~\cite{nedelec2018causal,raynal2013distributed}. However,
-reliable broadcast definition states that \emph{all} correct processes
-should deliver broadcast messages. This proves costly in large scale
+messages~\cite{hadzilacos1994modular,nedelec2018causal,raynal2013distributed}. However,
+uniform reliable broadcast states that \emph{all} correct processes
+must deliver broadcast messages. This proves costly in large scale
 systems comprising thousands of processes. Instead, we define
@@
 
-\begin{definition}[Scoped broadcast]
-  \TODO{meow predicate, meow path, meow state, meow message.}
+\begin{definition}[\underline{S}coped broadcast (S-broadcast)]
+  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
+  \underline{m}essage $m$, every correct Process $y$ within a scope
+  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
+  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
+  processes, \underline{m}etadata $\mu$ within received messages, and
+  a \underline{p}redicate $\phi$ verified from process to process:
+  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
+  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
 \end{definition}
 
-This definition highlights the transitive relevance of sent messages
-and encompasses more specific definitions of related
+This definition highlights the transitive relevance of messages and
+encompasses more specific definitions of related
 work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
@@
 all processes in this city plus neighboring cities by overloading
-forwarded messages the first time they reach another city. As for
-reliable broadcast, there exists different trade-off on space, time,
-and communication.
+forwarded messages the first time they reach another city. Similarly
+to reliable broadcast, scoped broadcast implementations expose
+different trade-offs on space, time, and communication.
 
-\begin{definition}[Logical partition]
-  A logical \underline{p}artition $P_s$ originated at a
-  \underline{s}ource process $s \in V$ is a set of interconnected
-  processes that do not belong to another logical partition. The set
-  of sources is $S \subseteq V$.
+%% \begin{definition}[S-broadcast properties]
+%%   S-broadcast guarantees 3 properties:
+%%   \begin{inparaenum}[(i)]
+%%   \item Validity: If a correct process broadcasts a message, it
+%%     eventually delivers it;
+%%   \item Scoped Agreement: If a process broadcasts a message, then all
+%%     correct processes within the scope eventually delivers it;
+%%   \item Scoped Integrity: A process delivers a message only if it was
+%%     previously broadcast within the scope.
+%%   \end{inparaenum}
+%% \end{definition}
+
+In this paper, we propose to dynamically adapt the scope of
+S-broadcast using S-broadcast itself.  \textbf{First}, at any time, a
+process can become the source of a new logical partition by
+transitively modifying the respective state of neighboring processes
+using path weights.  When a process S-broadcasts a message in this
+partition, it reaches all processes belonging to this partition. While
+the first partition gathers all processes of the system, the following
+partitions reduce the membership size of their neighboring
+partitions. In turns, the traffic generated to adapt scopes scales
+with the number of partitions.
+
+\begin{definition}[Consistent partitioning]
+  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
+  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
+  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
+  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
+  the consistent partitioning $\mathcal{P}$ is a set of logical
+  partitions $P_{s\in S}$ such that each process belongs to a logical
+  partition comprising its closest source process.  $\forall p \in
+  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
 \end{definition}
-
-Processes belong to logical partitions depending on path weights. When
-weights are about latency or hop numbers, the optimal partitioning
-consists in processing the multiple destinations shortest path at each
-process \REF.
-
-\begin{definition}[Shortest path]
-  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
-  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
-  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
-  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
-  that there exists no lower sum of weights $|\Pi_{ij}|$ from $i$ to
-  $j$.
-\end{definition}
-
-\begin{definition}[Optimal partitioning]
-  The optimal partitioning $\mathcal{P}$ is a set of logical
-  partitions such that each process belongs to a logical partition
-  comprising its closest source process.  $\forall p \in P_{s_1\in S},
-  \nexists P_{s_2 \in S}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
-\end{definition}
-
-Processes use reliable asynchronous message passing to reach optimal
-partitioning together. Process $s$ generates a message
-$\alpha_s^0$. Upon \underline{r}eceipt $r_i(\alpha_s^{w})$, Process
-$i$ knows that Process $s$ created a partition at a path length of
-$w$. Process $i$ may choose to \underline{d}eliver $d_i(\alpha_s^{w})$
-if it improves its partitioning. Process $i$ may choose to propagate
-its change through \underline{b}roadcast $b_i(\alpha_s^w)$.  Without
-global knowledge, processes only rely on their own behavior to deduce
-the behavior of their neighbor processes.
 
@@
 
-\begin{definition}[\label{def:transitivedelivery}Transitive delivery]
-  Transitive delivery ensures the system eventually converges to
-  optimal partitioning:
-  \begin{inparaenum}[(i)]
-  \item (\textbf{termination}) processes do not need to propagate
-    operations they do not deliver: $\forall \langle i, j \rangle \in
-    E, \neg d_i(\alpha_{s}^w)\implies \neg
-    d_j(\alpha_{s}^{w+w_{ij}})$;
-  \item (\textbf{propagation}) operations delivered by a process may
-    also benefit neighbor processes: $\forall \langle i, j \rangle \in
-    E, d_i(\alpha_{s}^{w_1}) \implies
-    d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
-    d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
-  \end{inparaenum}
-\end{definition}
+%% \begin{definition}[\label{def:transitivedelivery}Transitive delivery]
+%%   Transitive delivery ensures the system eventually converges to
+%%   optimal partitioning:
+%%   \begin{inparaenum}[(i)]
+%%   \item (\textbf{termination}) processes do not need to propagate
+%%     operations they do not deliver: $\forall \langle i, j \rangle \in
+%%     E, \neg d_i(\alpha_{s}^w)\implies \neg
+%%     d_j(\alpha_{s}^{w+w_{ij}})$;
+%%   \item (\textbf{propagation}) operations delivered by a process may
+%%     also benefit neighbor processes: $\forall \langle i, j \rangle \in
+%%     E, d_i(\alpha_{s}^{w_1}) \implies
+%%     d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
+%%     d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
+%%   \end{inparaenum}
+%% \end{definition}
 
@@
 
-Algorithm~\ref{algo:add} shows the instructions that implement the
-rules of Definition~\ref{def:transitivedelivery} to converge towards
-optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
-a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
-$a$ and $c$ concurrently create a partition. They initialize their own
-state with the lowest possible bound $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
+Algorithm~\ref{algo:add} shows the instructions that implement
+eventually consistent partitioning when weights are scalar values.
+
+%% Processes use reliable asynchronous message passing to reach optimal
+%% partitioning together. When Process $s$ wants to become a source, it
+%% generates a message $\alpha_s^0$. Upon \underline{r}eceipt
+%% $r_i(\alpha_s^{w})$, Process $i$ knows that Process $s$ created a
+%% partition at a path length of $w$. Process $i$ may choose to
+%% \underline{d}eliver $d_i(\alpha_s^{w})$ if it improves its
+%% partitioning. Process $i$ may choose to propagate its change through
+%% \underline{b}roadcast $b_i(\alpha_s^w)$.  Without global knowledge,
+%% processes only rely on their own behavior to deduce the behavior of
+%% their neighbor processes.
+
+\TODO{the rules of Definition~\ref{def:transitivedelivery} to converge
+towards optimal partitioning. Figure~\ref{fig:add} illustrates its
+behavior on a system comprising 4 processes $a$, $b$, $c$, and
+$d$. Two processes $a$ and $c$ concurrently create a partition. They
+initialize their own state with the lowest possible bound $0$ (see
+Line~\ref{line:lowestbound}), and send a message to each of their}
 neighbors by accumulating the corresponding edge weight (see

### 2021-03-11 input/background.tex
removing inter AS, reorganizing for the sake of scoped broadcast

--- 2021-03-01 input/background.tex
@@
 
-Fog infrastructures are distributed systems comprising heterogeneous
-machines interconnected by communication links. We do not consider
-byzantine processes.
+\TODO{More related work. More motivations etc. Maybe describe IPFS?}
 
-\begin{definition}[Fog infrastructure]
-  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
-  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
-  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
-  w_{ji}$ with $i, j \in V$.
-\end{definition}
+%% \begin{definition}[Dynamic optimal partitioning]
+%%   A dynamic optimal partitioning is an optimal partitioning where the
+%%   set of sources $S$ does not monotonically increase. We suffix this
+%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
+%%   of sources by \underline{a}dding its partition with messages
+%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
+%%   leaves the set of sources by \underline{d}eleting its partition with
+%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
+%% \end{definition}
 
-\begin{definition}[Logical partition]
-  A logical \underline{p}artition $P_s$ originated at a
-  \underline{s}ource process $s \in V$ is a set of interconnected
-  processes that do not belong to another logical partition. The set
-  of sources is $S \subseteq V$.
-\end{definition}
-
-Processes belong to logical partitions depending on path weights. When
-weights are about latency or hop numbers, the optimal partitioning
-consists in processing the multiple destinations shortest path at each
-process \REF.
-
-\begin{definition}[Shortest path]
-  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
-  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
-  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
-  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
-  that there exists no lower sum of weights $|\Pi_{ij}|$ from $i$ to
-  $j$.
-\end{definition}
-
-\begin{definition}[Optimal partitioning]
-  The optimal partitioning $\mathcal{P}$ is a set of logical
-  partitions such that each process belongs to a logical partition
-  comprising its closest source process.  $\forall p \in P_{s_1\in S},
-  \nexists P_{s_2 \in S}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
-\end{definition}
-
-Processes use reliable asynchronous message passing to reach optimal
-partitioning together. Process $s$ generates a message
-$\alpha_s^0$. Upon \underline{r}eceipt $r_i(\alpha_s^{w})$, Process
-$i$ knows that Process $s$ created a partition at a path length of
-$w$. Process $i$ may choose to \underline{d}eliver $d_i(\alpha_s^{w})$
-if it improves its partitioning. Process $i$ may choose to propagate
-its change through \underline{b}roadcast $b_i(\alpha_s^w)$.  Without
-global knowledge, processes only rely on their own behavior to deduce
-the behavior of their neighbor processes.
-
-\input{input/figdel.tex} %% figure positioning
-
-\begin{definition}[\label{def:transitivedelivery}Transitive delivery]
-  Transitive delivery ensures the system eventually converges to
-  optimal partitioning:
-  \begin{inparaenum}[(i)]
-  \item (\textbf{termination}) processes do not need to propagate
-    operations they do not deliver: $\forall \langle i, j \rangle \in
-    E, \neg d_i(\alpha_{s}^w)\implies \neg
-    d_j(\alpha_{s}^{w+w_{ij}})$;
-  \item (\textbf{propagation}) operations delivered by a process may
-    also benefit neighbor processes: $\forall \langle i, j \rangle \in
-    E, d_i(\alpha_{s}^{w_1}) \implies
-    d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
-    d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
-  \end{inparaenum}
-\end{definition}
-
-\begin{algorithm}
-  \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding a partition by Process $p$.}
-\end{algorithm}
-
-Algorithm~\ref{algo:add} shows the instructions that implement the
-rules of Definition~\ref{def:transitivedelivery} to converge towards
-optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
-a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
-$a$ and $c$ concurrently create a partition. They initialize their own
-state with the lowest possible bound $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
-neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
-receives $\alpha_{c}^{1}$. Since it improves its own partition
-distance, it keeps it and forwards it to its neighbors. Process $b$
-discards $\alpha_{b}^{1.5}$, for it does not improve its partition
-distance. Processes $c$ and $d$ will never hear of Process $a$'s
-partition. At scale, such \emph{scoped flooding} saves bandwidth by
-limiting generated traffic to subsets of
-processes~\cite{wang2015prodiluvian}. In Figure~\ref{fig:addD},
-processes discard last transiting messages. The system converged to
-the optimal partitioning.  Transitive relationships ensure that each
-process gets its closest source while accumulation of weights ensures
-that messages propagation terminates.  Interestingly, while the
-receipt order of messages does not impact on local control information
-($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
-r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
-\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
-broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
-\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
-$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
-b_b(\alpha_a^{1})$).
-
-While only adding logical partitions to the distributed system is
-straightforward, removing them introduces additional complexity.
-
-\begin{definition}[Dynamic optimal partitioning]
-  A dynamic optimal partitioning is an optimal partitioning where the
-  set of sources $S$ does not monotonically increase. We suffix this
-  set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
-  of sources by \underline{a}dding its partition with messages
-  $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
-  leaves the set of sources by \underline{d}eleting its partition with
-  messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
-\end{definition}
-
-Unfortunately, due to differences in receipt order of messages between
-processes, stale information may stop prematurely the propagation of
-relevant messages leading to inconsistent partitioning.
-\TODO{Figure~\ref{fig:del} shows that.}
+%% Unfortunately, due to differences in receipt order of messages between
+%% processes, stale information may stop prematurely the propagation of
+%% relevant messages leading to inconsistent partitioning.
+%% \TODO{Figure~\ref{fig:del} shows that.}
 
@@
 
-\begin{problem}[\label{prob:intra}Consistent partitioning]
-  How to enable \emph{consistent} dynamic optimal partitioning in
-  dynamic network using scoped flooding?
-\end{problem}
+%% \begin{problem}[\label{prob:intra}Consistent partitioning]
+%%   How to enable \emph{consistent} dynamic optimal partitioning in
+%%   dynamic network using scoped flooding?
+%% \end{problem}
 
@@
 
-\begin{figure}
-  \begin{center}
-    \input{input/figASmotivation.tex}
-    \caption{\label{fig:ASmotivation}Scoped flooding extended to
-      objects, processes do not know about all partitions that exist
-      in the whole distributed system.}
-  \end{center}
-\end{figure}
+%% \begin{figure}
+%%   \begin{center}
+%%     \input{input/figASmotivation.tex}
+%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
+%%       objects, processes do not know about all partitions that exist
+%%       in the whole distributed system.}
+%%   \end{center}
+%% \end{figure}
 
-To further improve scoped flooding in autonomous systems, processes
-may belong to multiple partitions representing the objects they are
-aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
-nature of autonomous systems. Autonomous systems have topological
-properties~\cite{nur2018geography} that processes can leverage to
-avoid flooding the whole systems with control information about all
-partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
-partition about a specific object, flooding Paris's AS to notify
-neighboring processes of the object. However, it does not flood the
-whole network, for control information stops at Process $b$. It
-significantly saves bandwidth compared to broadcast since processes
-below entrypoints of autonomous systems are order of magnitude more
-numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
-to return an object they are unaware of. Processes remain efficient in
-answering requests. \TODO{which is important for end users \REF.}
+%% To further improve scoped flooding in autonomous systems, processes
+%% may belong to multiple partitions representing the objects they are
+%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
+%% nature of autonomous systems. Autonomous systems have topological
+%% properties~\cite{nur2018geography} that processes can leverage to
+%% avoid flooding the whole systems with control information about all
+%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
+%% partition about a specific object, flooding Paris's AS to notify
+%% neighboring processes of the object. However, it does not flood the
+%% whole network, for control information stops at Process $b$. It
+%% significantly saves bandwidth compared to broadcast since processes
+%% below entrypoints of autonomous systems are order of magnitude more
+%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
+%% to return an object they are unaware of. Processes remain efficient in
+%% answering requests. \TODO{which is important for end users \REF.}
 
-\begin{definition}[Partitions in asynchronous systems]
-  Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
-  \TODO{TODO} \TODO{or multi-partitioning?}
-\end{definition}
+%% \begin{definition}[Partitions in asynchronous systems]
+%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
+%%   \TODO{TODO} \TODO{or multi-partitioning?}
+%% \end{definition}
 
-\begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
-  How to enable scoped flooding of objects in autonomous systems?
-\end{problem}
+%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
+%%   How to enable scoped flooding of objects in autonomous systems?
+%% \end{problem}
 
-Next Section presents our approach that solves these scientific
-problems by relying on logical control information only.
+%% Next Section presents our approach that solves these scientific
+%% problems by relying on logical control information only.
 

### 2021-03-11 input/conclusion.tex
meow
coloring figures, adding biblio, sketching abstract
removing inter AS, reorganizing for the sake of scoped broadcast

@@
 \label{sec:conclusion}
+
+As future work, we plan on enhancing the
+\underline{I}nter\underline{P}lanetary \underline{F}ile
+\underline{S}ystem (IPFS)~\cite{henningsen2020mapping} with dynamic
+logical partitioning capabilities in order to improve its caching
+policy of popular contents at marginal cost.
+
+\noindent We also plan on further improving scoped broadcast between
+multiple autonomous systems. Indeed, processes could leverage the
+hierarchical properties of such topology~\cite{nur2018geography} to
+avoid flooding the whole systems with control information about all
+partitions.
 

### 2021-03-11 input/proposal.tex
removing inter AS, reorganizing for the sake of scoped broadcast

@@
-\section{\NAME for Dynamic Partitioning}
-\label{sec:proposal}
+\section{Scoped broadcast}
+\label{sec:scoped}
 
-In this section, we introduce \NAME (\TODO{stands for}) and its
-\underline{ex}tension \NAMEB, reactive protocols for logical
-partitioning in autonomous systems the cost of which actually depends
-on their usage: when the system becomes quiescent, processes
-eventually converge to their respective partition and do not require
-further communication afterward.
+Fog infrastructures are distributed systems comprising heterogeneous
+machines interconnected by communication links. We do not consider
+byzantine processes.
+
+\begin{definition}[Fog infrastructure]
+  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
+  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
+  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from Process
+  $i$ to Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
+    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
+  \pi_{ij}[m+1] \rangle \in E$.
+\end{definition}
+
+Processes can send messages to their neighboring processes. Processes
+can reliably broadcast messages by forwarding delivered
+messages~\cite{hadzilacos1994modular,nedelec2018causal,raynal2013distributed}. However,
+uniform reliable broadcast states that \emph{all} correct processes
+must deliver broadcast messages. This proves costly in large scale
+systems comprising thousands of processes. Instead, we define
+\emph{scoped broadcast} where messages reach only interested
+processes, significantly reducing generated traffic.
+
+\begin{definition}[\underline{S}coped broadcast (S-broadcast)]
+  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
+  \underline{m}essage $m$, every correct Process $y$ within a scope
+  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
+  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
+  processes, \underline{m}etadata $\mu$ within received messages, and
+  a \underline{p}redicate $\phi$ verified from process to process:
+  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
+  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
+\end{definition}
+
+This definition highlights the transitive relevance of messages and
+encompasses more specific definitions of related
+work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
+process from Paris could scoped broadcast a message to all processes
+in this city. A process from Paris could scoped broadcast a message to
+all processes in this city plus neighboring cities by overloading
+forwarded messages the first time they reach another city. Similarly
+to reliable broadcast, scoped broadcast implementations expose
+different trade-offs on space, time, and communication.
+
+%% \begin{definition}[S-broadcast properties]
+%%   S-broadcast guarantees 3 properties:
+%%   \begin{inparaenum}[(i)]
+%%   \item Validity: If a correct process broadcasts a message, it
+%%     eventually delivers it;
+%%   \item Scoped Agreement: If a process broadcasts a message, then all
+%%     correct processes within the scope eventually delivers it;
+%%   \item Scoped Integrity: A process delivers a message only if it was
+%%     previously broadcast within the scope.
+%%   \end{inparaenum}
+%% \end{definition}
+
+In this paper, we propose to dynamically adapt the scope of
+S-broadcast using S-broadcast itself.  At any time, a process can
+become the source of a new logical partition by transitively modifying
+the respective state of neighboring processes using path weights.
+When a process S-broadcasts a message in this partition, it reaches
+all processes belonging to this partition. While the first partition
+gathers all processes of the system, the following partitions reduce
+the membership size of their neighboring partitions. In turns, the
+traffic generated to adapt scopes scales with the number of
+partitions.
+
+\begin{definition}[Consistent partitioning]
+  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
+  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
+  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
+  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
+  the consistent partitioning $\mathcal{P}$ is a set of logical
+  partitions $P_{s\in S}$ such that each process belongs to a logical
+  partition comprising its closest source process.  $\forall p \in
+  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
+\end{definition}
+
+\input{input/figdel.tex} %% figure positioning
+
+%% \begin{definition}[\label{def:transitivedelivery}Transitive delivery]
+%%   Transitive delivery ensures the system eventually converges to
+%%   optimal partitioning:
+%%   \begin{inparaenum}[(i)]
+%%   \item (\textbf{termination}) processes do not need to propagate
+%%     operations they do not deliver: $\forall \langle i, j \rangle \in
+%%     E, \neg d_i(\alpha_{s}^w)\implies \neg
+%%     d_j(\alpha_{s}^{w+w_{ij}})$;
+%%   \item (\textbf{propagation}) operations delivered by a process may
+%%     also benefit neighbor processes: $\forall \langle i, j \rangle \in
+%%     E, d_i(\alpha_{s}^{w_1}) \implies
+%%     d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
+%%     d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
+%%   \end{inparaenum}
+%% \end{definition}
+
+\begin{algorithm}
+  \input{input/algoadd.tex}
+  \caption{\label{algo:add}Adding a partition by Process $p$.}
+\end{algorithm}
+
+Algorithm~\ref{algo:add} shows the instructions that implement
+eventually consistent partitioning when weights are scalar values.  At
+any time, a process running this protocol can add a logical partition
+to its distributed system.  Figure~\ref{fig:add} illustrates its
+behavior on a system comprising 4 processes $a$, $b$, $c$, and
+$d$. Two processes $a$ and $c$ concurrently create a partition by
+S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
+and $\alpha_c^0$. They initialize their own state with the lowest
+possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
+message to each of their neighbors by accumulating the corresponding
+edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
+improves its own partition distance, it keeps it and forwards it to
+its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
+not improve its partition distance. Processes $c$ and $d$ will never
+hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
+discard last transiting messages. The system converged to the optimal
+partitioning.  Transitive relationships ensure that each process gets
+its closest source while accumulation of weights ensures that messages
+propagation terminates.
+
+%% Interestingly, while the receipt order of messages does not impact on
+%% local control information ($r_b(\alpha_a^{1.5}) \cdot
+%% r_b(\alpha_a^{1}) \Leftrightarrow r_b(\alpha_a^{1}) \cdot
+%% r_b(\alpha_a^{1.5}) \implies \TODO{d_b(\alpha_a^{1})}$), it impacts on
+%% control information broadcast in the network ($r_b(\alpha_a^{1.5})
+%% \cdot r_b(\alpha_a^{1}) \implies b_b(\alpha_{b}^{1.5}) \cdot
+%% b_b(\alpha_{b}^{1})$ while $r_b(\alpha_a^{1}) \cdot
+%% r_b(\alpha_a^{1.5}) \implies b_b(\alpha_a^{1})$).
+
+While only adding logical partitions to the distributed system is
+straightforward, removing them introduces additional complexity.
+
+\section{Adaptive scoped broadcast}
+\label{sec:adaptive}
+
+In this section, we introduce \NAME, a wait-free reactive protocol for
+logical partitioning in dynamic distributed systems the cost of which
+actually depends on its usage: When the system becomes quiescent,
+processes eventually converge to their respective partition and do not
+require further communication afterward.
 
@@
 as well. Yet, generated traffic remains \TODO{low} using scoped
-flooding. Messages that carry changes travel through the network
+broadcast. Messages that carry changes travel through the network
 depending on partition of processes, stopping as soon as they
@@
 consistent partitioning despite different order in message deliveries
-from one process to another. While \NAME is a general purpose logical
-partitioning protocol for dynamic networks, \NAMEB further reduces
-generated traffic in the context of inter-autonomous systems by
-leveraging the hierarchical properties of such networks.
+from one process to another.
 
@@
 operation to avoid inconsistent states due to ordering and staleness
-of delivered messages. Then, it describes its extension \NAMEB that
-builds multiple broadcast layers ordered using local knowledge only.
-Finally, it ends with a complexity analysis of proposed protocols.
+of delivered messages. This section ends with a complexity analysis of
+proposed protocols.
 
-\subsection{Intra-autonomous system partitioning}
+%% \subsection{Intra-autonomous system partitioning}
 
@@
 
-In this section, we aim at solving Problem Statement~\ref{prob:intra}
-by proposing \NAME, a reactive logical partitioning protocol for
-dynamic partitioning in dynamic networks.
+%% In this section, we aim at solving Problem Statement~\ref{prob:intra}
+%% by proposing \NAME, a reactive logical partitioning protocol for
+%% dynamic partitioning in dynamic networks.
 
@@
 processes that are closer from this new source than any other else. We
-described such protocol in Section~\ref{sec:background}. Processes
+described such protocol in Section~\ref{sec:scoped}. Processes
 naturally converge towards their respective best partition by only
@@
 
-\subsection{Inter-autonomous system partitioning}
+%% \subsection{Inter-autonomous system partitioning}
 
-\begin{figure}
-  \centering\input{input/figAS.tex}
-  \caption{\label{fig:AS}Inter autonomous systems
-    partitioning. \TODO{More about relative ordering of links at each
-      process}}
-\end{figure}
+%% \begin{figure}
+%%   \centering\input{input/figAS.tex}
+%%   \caption{\label{fig:AS}Inter autonomous systems
+%%     partitioning. \TODO{More about relative ordering of links at each
+%%       process}}
+%% \end{figure}
 
-In this section, we aim at solving Problem Statement~\ref{prob:inter}
-by proposing \NAMEB, an extension of \NAME, that enables dynamic
-logical partitioning in inter-autonomous systems. It leverages
-hierarchical properties of these networks to further improve on scoped
-flooding.
+%% In this section, we aim at solving Problem Statement~\ref{prob:inter}
+%% by proposing \NAMEB, an extension of \NAME, that enables dynamic
+%% logical partitioning in inter-autonomous systems. It leverages
+%% hierarchical properties of these networks to further improve on scoped
+%% flooding.
 
-Autonomous systems are geo-distributed networks. Heterogeneous
-communication links. Hierarchy of communication links. Per-object
-broadcast.
+%% Autonomous systems are geo-distributed networks. Heterogeneous
+%% communication links. Hierarchy of communication links. Per-object
+%% broadcast.
 
-We leave the link handling to membership protocols~\REF. The ordering
-of links can be done based on latency. For instance, from 0 to 100 ms,
-rank 0, from 100 to 1s, rank 2 \ldots
+%% We leave the link handling to membership protocols~\REF. The ordering
+%% of links can be done based on latency. For instance, from 0 to 100 ms,
+%% rank 0, from 100 to 1s, rank 2 \ldots
 
-\begin{algorithm}
-  \input{input/algoaaaa.tex}
-  \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
-    partitioning in inter-autonomous systems.}
-\end{algorithm}
+%% \begin{algorithm}
+%%   \input{input/algoaaaa.tex}
+%%   \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
+%%     partitioning in inter-autonomous systems.}
+%% \end{algorithm}
 
-Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
-where each process ranks its communication links, and each process
-forwards messages to its neighbors starting from the rank of the link
-that triggered the receipt, to its highest rank neighbors. In this
-example, Process $e$ adds a partition. It forwards the generated
-message to all its neighbors as if it received it from its lowest rank
-links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
-it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
-stops the propagation, for all its links have lower ranks than the one
-from which it received the message $\alpha_e^2$. Ultimately, the
-partition includes Process $e$, Process $a$, and Process $b$. Process
-$c$ and Process $d$ remain unaware of the new \TODO{object}.
+%% Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
+%% where each process ranks its communication links, and each process
+%% forwards messages to its neighbors starting from the rank of the link
+%% that triggered the receipt, to its highest rank neighbors. In this
+%% example, Process $e$ adds a partition. It forwards the generated
+%% message to all its neighbors as if it received it from its lowest rank
+%% links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
+%% it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
+%% stops the propagation, for all its links have lower ranks than the one
+%% from which it received the message $\alpha_e^2$. Ultimately, the
+%% partition includes Process $e$, Process $a$, and Process $b$. Process
+%% $c$ and Process $d$ remain unaware of the new \TODO{object}.
 
-To ease the reasoning about inter-AS dynamic partitioning in dynamic
-networks, \NAME runs an independent broadcast protocol for each
-object, and for each rank of links.  \TODO{Not so easy\ldots}
-\TODO{Write and describe algo.} \TODO{Overhead of separating things,
-  slightly more memory, but traffic wise? slower ?}  \TODO{In the
-  example, not only Process $b$ keeps $e_1$ as its best partition, but
-  it keeps it for links of rank 0, and links of rank 1.}  When there
-are no ranking in links, processes solely rely on
-Algorithm~\ref{algo:adddelundo} for optimal partitioning.
+%% To ease the reasoning about inter-AS dynamic partitioning in dynamic
+%% networks, \NAME runs an independent broadcast protocol for each
+%% object, and for each rank of links.  \TODO{Not so easy\ldots}
+%% \TODO{Write and describe algo.} \TODO{Overhead of separating things,
+%%   slightly more memory, but traffic wise? slower ?}  \TODO{In the
+%%   example, not only Process $b$ keeps $e_1$ as its best partition, but
+%%   it keeps it for links of rank 0, and links of rank 1.}  When there
+%% are no ranking in links, processes solely rely on
+%% Algorithm~\ref{algo:adddelundo} for optimal partitioning.
 
-\subsection{Complexity}
-\label{subsec:complexity}
+\section{Complexity}
+\label{sec:complexity}
 

### 2021-03-12 input/proposal.tex
small changes

@@
 
-Fog infrastructures are distributed systems comprising heterogeneous
-machines interconnected by communication links. We do not consider
-byzantine processes.
+In this section, we introduce model and notations to provide a general
+definition of scoped broadcast in distributed systems.  Distributed
+systems such as Edge infrastructures comprise heterogeneous machines
+interconnected by communication links. We do not consider byzantine
+processes.
 
@@
 Algorithm~\ref{algo:add} shows the instructions that implement
-eventually consistent partitioning when weights are scalar values.  At
-any time, a process running this protocol can add a logical partition
-to its distributed system.  Figure~\ref{fig:add} illustrates its
-behavior on a system comprising 4 processes $a$, $b$, $c$, and
-$d$. Two processes $a$ and $c$ concurrently create a partition by
-S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
-and $\alpha_c^0$. They initialize their own state with the lowest
-possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
-message to each of their neighbors by accumulating the corresponding
-edge weight (see Line~\ref{line:accumulator}). In
-Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
-improves its own partition distance, it keeps it and forwards it to
-its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
-not improve its partition distance. Processes $c$ and $d$ will never
-hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
-discard last transiting messages. The system converged to the optimal
-partitioning.  Transitive relationships ensure that each process gets
-its closest source while accumulation of weights ensures that messages
-propagation terminates.
+eventually consistent partitioning when weights are scalar values, and
+processes only add new partitions to the system.  At any time, a
+process running this protocol can add a logical partition to its
+distributed system.  Figure~\ref{fig:add} illustrates its behavior on
+a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
+$a$ and $c$ concurrently create a partition by S-broadcasting their
+respective \underline{a}dd message: $\alpha_a^0$ and
+$\alpha_c^0$. They initialize their own state with the lowest possible
+bound $0$ (see Line~\ref{line:lowestbound}), and send a message to
+each of their neighbors by accumulating the corresponding edge weight
+(see Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process
+$b$ receives $\alpha_{c}^{1}$. Since it improves its own partition
+distance, it keeps it and forwards it to its neighbors. Process $b$
+discards $\alpha_{b}^{1.5}$, for it does not improve its partition
+distance. Processes $c$ and $d$ will never hear of Process $a$'s
+partition.  In Figure~\ref{fig:addD}, processes discard last
+transiting messages. The system converged to the optimal partitioning.
+Transitive relationships ensure that each process gets its closest
+source while accumulation of weights ensures that messages propagation
+terminates.
 
@@
 In this section, we introduce \NAME, a wait-free reactive protocol for
-logical partitioning in dynamic distributed systems the cost of which
-actually depends on its usage: When the system becomes quiescent,
-processes eventually converge to their respective partition and do not
-require further communication afterward.
+dynamic logical partitioning in dynamic distributed systems the cost
+of which actually depends on its usage. At any time, processes can add
+\emph{and} remove partitions from the system. When the system becomes
+quiescent, processes eventually converge to their respective partition
+and do not require further communication afterward.
 
@@
 neighborhood, for the state of its neighbors may depend on this change
-as well. Yet, generated traffic remains \TODO{low} using scoped
-broadcast. Messages that carry changes travel through the network
-depending on partition of processes, stopping as soon as they
+as well. Yet, the traffic generated to to adapt the scope of
+S-broadcast remains bounded, for it uses the principles of scoped
+broadcast itself. Messages that carry changes travel through the
+network depending on partition of processes, stopping as soon as they
 encounter uninterested processes. We demonstrate that \NAME guarantees
@@
 
-This section starts by describing \NAME's functioning by detailing its
-operation to avoid inconsistent states due to ordering and staleness
-of delivered messages. This section ends with a complexity analysis of
-proposed protocols.
+%% This section starts by describing \NAME's functioning by detailing its
+%% operation to avoid inconsistent states due to ordering and staleness
+%% of delivered messages. This section ends with a complexity analysis of
+%% proposed protocols.
 
@@
 that belong to this partition must eventually choose another partition
-to belong to. Since the number of partitions does not monotonically
-increase in the system any longer, each process requires a vector of
-versions that monotonically increases over delivered operations.
+to belong to.
+
+\begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
+  The transitive, irreflexive, and antisymmetric happens-before
+  relationship defines a strict partial order between events. Two
+  messages are concurrent if none happens before the other.
+\end{definition}
+
+\begin{definition}[\TODO{Last win order}]
+  For any $b_p(m) \rightarrow b_p(m')$, no process can deliver $m$ if
+  it has delivered $m'$.
+\end{definition}
+
+\begin{definition}[\TODO{Adaptive scope}]
+  Eventual consistent partitioning in presence of dynamic
+  partitioning. Eventually get the last partition, eventually remove
+  all outdated control information.
+\end{definition}
+
+Since the number of partitions does not monotonically increase in the
+system any longer, each process requires a vector of versions that
+monotonically increases over delivered operations.
 
@@
 
-\TODO{Paths and \NAME synergize well, for paths tend to be smaller as the
+\TODO{Paths and \NAME synergies well, for paths tend to be smaller as the
 number of sources increase in the system.}

### 2021-03-16 input/experiments.tex
small changes
wip
scoped broadcst section

@@
 
+We also propose an implementation that further decreases generated
+traffic and improves on anonymity~\cite{whitaker2002forwarding}.
+\NAME makes extensive use of paths to enable deleting messages without
+incrementing local counters. Messages carry their respective path and
+processes detect when such messages have been looping when they carry
+their identity (see Lines~\ref{line:notloopingA} and
+\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
+membership is all that matters, we propose to trade vectors of
+identities for Bloom filters~\cite{almeida2007scalable}. Processes
+know with high probability if they already received and forwarded each
+message without knowing the identity of all processes that received
+it.  False positive probability only incurs premature stopping of
+broadcast messages and does not invalidate the delete of specific
+messages.
+
 \subsection{Global properties}
+
+Compare with full broadcast full replication; timeout on removals.
+
+Confirm complexity analysis.
 
@@
 
+\subsection{\TODO{Extension: $A^4$?}}
+
 %%% Local Variables: 

### 2021-03-16 input/proposal.tex
scoped broadcst section

@@
 become the source of a new logical partition by transitively modifying
-the respective state of neighboring processes using path weights.
-When a process S-broadcasts a message in this partition, it reaches
-all processes belonging to this partition. While the first partition
-gathers all processes of the system, the following partitions reduce
-the membership size of their neighboring partitions. In turns, the
-traffic generated to adapt scopes scales with the number of
-partitions.
+the respective state of neighboring processes using path weights. When
+a process S-broadcasts a message in this partition, it eventually
+reaches all processes belonging to this partition.  While the first
+partition gathers all processes of the system, the following
+partitions reduce the membership size of their neighboring
+partitions. In turns, the traffic generated to adapt scopes scales
+with the number of partitions.
 
-\begin{definition}[Consistent partitioning]
+\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
   Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
@@
   weight of which $|\Pi_{xz}|$ is lower than any other path weight,
-  the consistent partitioning $\mathcal{P}$ is a set of logical
+  the only consistent partitioning $\mathcal{P}$ is a set of logical
   partitions $P_{s\in S}$ such that each process belongs to a logical
-  partition comprising its closest source process.  $\forall p \in
-  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
+  partition comprising its closest source: $\forall p \in P_{s_1},
+  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
 \end{definition}
+
+%% \begin{theorem}[$SPED \implies CP$]
+%%   \underline{S}hortest \underline{p}ath \underline{e}ventual
+%%   \underline{d}elivery (SPED) where each process $k_n$ in the shortest
+%%   path $\Pi_{ps}: [s, k_1,\ldots,k_n,p]$ eventually deliver the
+%%   message forwarded by its predecessor $k_{n-1}$ leads to consistent
+%%   partitioning.
+%% \end{theorem}
+
+%% \TODO{or:}
+
+\begin{theorem}[\underline{B}est \underline{e}ventual \underline{d}elivery $(BED) \implies CP$]
+  Every process eventually delivers, hence forwards, the notification
+  message $\alpha_s$ of its best partition $P_s$, eventually leading
+  to consistent partitioning.
+\end{theorem}
+
+\begin{proof} When a process $s_1$ becomes a source, it belongs to
+its own partition, for there exists no better partition than its own:
+$\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It broadcasts such
+message to its neighbors. Since communication channels are reliable,
+neighboring processes eventually receive such notification. In
+particular, whatever the order of received messages, every process
+$p_1$ such that there exists no better partition $s_2$ than the
+received one delivers and forwards it: $\forall s_2 \in S: |\Pi_{p
+  s_1}| < |\Pi_{p s_2}|$. The notification emanating from $s_1$
+transitively reaches all such processes through shortest paths. Since
+there exists only one best value per process that can never be
+retracted, processes eventually reach consistent partitioning.
+\end{proof}
 
@@
 Algorithm~\ref{algo:add} shows the instructions that implement
-eventually consistent partitioning when weights are scalar values, and
-processes only add new partitions to the system.  At any time, a
-process running this protocol can add a logical partition to its
-distributed system.  Figure~\ref{fig:add} illustrates its behavior on
-a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
-$a$ and $c$ concurrently create a partition by S-broadcasting their
-respective \underline{a}dd message: $\alpha_a^0$ and
-$\alpha_c^0$. They initialize their own state with the lowest possible
-bound $0$ (see Line~\ref{line:lowestbound}), and send a message to
-each of their neighbors by accumulating the corresponding edge weight
-(see Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process
-$b$ receives $\alpha_{c}^{1}$. Since it improves its own partition
-distance, it keeps it and forwards it to its neighbors. Process $b$
-discards $\alpha_{b}^{1.5}$, for it does not improve its partition
-distance. Processes $c$ and $d$ will never hear of Process $a$'s
-partition.  In Figure~\ref{fig:addD}, processes discard last
-transiting messages. The system converged to the optimal partitioning.
-Transitive relationships ensure that each process gets its closest
-source while accumulation of weights ensures that messages propagation
-terminates.
+eventually consistent partitioning when
+\begin{inparaenum}[(i)]
+\item processes only have local knowledge about their direct
+  neighborhoods,
+\item weights are scalar values,
+\item and processes only add new partitions to the system.
+\end{inparaenum}
+At any time, a process running this protocol can add a logical
+partition to its distributed system.  Figure~\ref{fig:add} illustrates
+its behavior on a system comprising 4 processes $a$, $b$, $c$, and
+$d$. Two processes $a$ and $c$ concurrently create a partition by
+S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
+and $\alpha_c^0$. They initialize their own state with the lowest
+possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
+message to each of their neighbors by accumulating the corresponding
+edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
+improves its own partition distance, it keeps it and forwards it to
+its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
+not improve its partition distance. Processes $c$ and $d$ will never
+hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
+discard last transiting messages. The system converged to the
+consistent partitioning. However, since processes operate using local
+knowledge only, generated traffic may be sub-optimal, for processes
+may receive, deliver, and forward messages emanating from a same
+source simply because it did not come from the shortest path yet.
+
+%% Transitive relationships ensure that each
+%% process gets its closest source while accumulation of weights ensures
+%% that messages propagation terminates.
 
@@
 While only adding logical partitions to the distributed system is
-straightforward, removing them introduces additional complexity.
+straightforward, removing them introduces additional complexity:
+messages of old partitions may stop the notification of best sources,
+for former weights are better than the newly received one.
 
@@
 
-\paragraph{A last optimization.}
-\NAME makes extensive use of paths to enable deleting messages without
-incrementing local counters. Messages carry their respective path and
-processes detect when such messages have been looping when they carry
-their identity (see Lines~\ref{line:notloopingA} and
-\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
-membership is all that matters, we propose to trade vectors of
-identities for Bloom filters~\cite{almeida2007scalable} to improve on
-generated traffic and
-anonymity~\cite{whitaker2002forwarding}. Processes know with high
-probability if they already received and forwarded each message
-without knowing the identity of all processes that received it.  False
-positive probability only incurs premature stopping of broadcast
-messages and does not invalidate the delete of specific messages.
-
 %% \subsection{Inter-autonomous system partitioning}

### 2021-03-22 input/proposal.tex
small wip

@@
   Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
-  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
+  W_{yx}$ be the symmetric \underline{w}eight between $x$ and $y$,
   $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
@@
 
-In this section, we introduce \NAME, a wait-free reactive protocol for
-dynamic logical partitioning in dynamic distributed systems the cost
-of which actually depends on its usage. At any time, processes can add
-\emph{and} remove partitions from the system. When the system becomes
-quiescent, processes eventually converge to their respective partition
-and do not require further communication afterward.
+In this section, we introduce \NAME (stands for \underline{A}daptive
+\underline{S}coped broad\underline{cast}), a wait-free reactive
+protocol for dynamic logical partitioning in dynamic distributed
+systems the cost of which actually depends on its usage. At any time,
+processes can add \emph{and} remove partitions from the system. When
+the system becomes quiescent, processes eventually converge to their
+respective partition and do not require further communication
+afterward.
 
@@
 
-\paragraph{Dynamic partitions.}
+\subsection{Dynamic partitions}
 At any time, a process can become a source, hence adding a new
@@
 that belong to this partition must eventually choose another partition
-to belong to.
+to belong to. Unfortunately, stale control information about deleted
+partitions may impair the propagation of both
+\begin{inparaenum}[(i)]
+\item notifications about actual sources, and
+\item notifications about other deleted partitions.
+\end{inparaenum}
+The correctness of the partitioning depends on receipt orders at each
+processes.
 
@@
 
-\begin{definition}[\TODO{Last win order}]
-  For any $b_p(m) \rightarrow b_p(m')$, no process can deliver $m$ if
-  it has delivered $m'$.
+We define a last win order to forbid the delivery of stale information
+emanating from a same process. In other terms, the \emph{best}
+notification message is always the most recent known of each process.
+
+\begin{definition}[Last win order]
+  When a process $p$ broadcasts two messages $b_p(m) \rightarrow
+  b_p(m')$, no process $q$ can deliver $m$ if it has delivered $m'$:
+  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$.
 \end{definition}
@@
 
-\paragraph{Dynamic networks.}
+\subsection{Dynamic networks}
 Adding new communication links to the network may create shortcuts
@@
 partitions grows.
+
+\subsection{Implementation}
+
+\TODO{Move everything related to implementation here, including optimizations.}
 

### 2021-03-23 input/figproof.tex
reworkd figures of proofs

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop up-to-date $\alpha$'s
-    from reaching all processes that require it along the shortest path from $a$ to $c$.
-    To solve this issue, we must guarantee
-    the eventual removal of stale $\alpha$'s (see Figure~\ref{fig:proofB}).]
-    {\input{input/figproofA.tex}}
+    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop
+      other $\alpha$'s from reaching all processes ($b$ and $c$) that
+      require it along the shortest path. Hence, we must guarantee
+      eventual purging of stale $\alpha$'s (see
+      Figure~\ref{fig:proofB}).]  {\input{input/figproofA.tex}}
     \hspace{10pt}
-    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may stop $\delta$'s from reaching
-    processes with targeted $\alpha$'s. To ensure correctness, $b$ must either
-    deliver $\delta_d$, $\delta_d^{0.5}$, or another $\alpha$, as well as downstream processes
-    that delivered $\alpha$ coming from $b$ such as $g$.]
+    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may
+      stop $\delta$'s from reaching
+      processes with targeted $\alpha$'s.
+      To ensure consistent partitioning, $b'$ and $b''$
+      must remove $\alpha_{d}$ either by delivering $\delta_d$,
+      or a more specific $\delta_d^{0.5}$ and $\delta_d^{1.5}$ respectively.]
     {\input{input/figproofB.tex}}

### 2021-03-23 input/figproofA.tex
reworkd figures of proofs

@@
 
-  \newcommand\X{50pt}
-  \newcommand\Y{-45pt}
+  \newcommand\X{70pt}
+  \newcommand\Y{-40pt}
 
@@
 
-  \draw[opacity=0] (-2*\X, 0) -- (3*\X, 0);
+  \draw[opacity=0] (-1.5*\X, 0) -- (1.5*\X, 0);
 
-  \draw[->] (-\X + 5pt, 0) -- node[above, color=\PA, font=\small]{$\ADD_a^1$} (0 - 5pt, 0); %% a - b
+  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I
 
-  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% b - ...
+  \draw[->] (-\X + 5pt, 0) --
+  node[above, color=\PA, font=\small]{$\ADD_a^1$}
+  (0 - 5pt, 0); %% a - b
 
-  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% ... - c
-
-  \draw[->] ( 0, \Y + 5pt) -- ( 0, -5pt); %% ... - b
-
-  \draw[->] ( -\X + 5pt, \Y ) -- ( -5pt, \Y); %% d - ...
+  \draw[<->] (-5pt, 5pt -\Y) -- node[above]{II} (5pt + \X, 5pt -\Y); %% II
+  \draw[->] (0 + 5pt, 0) -- (-5pt +  \X, 0); %% b - c
 
@@
   \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (\X, 0) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (2*\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-
-  \draw[fill=white] ( 0, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (-\X, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
   \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
-  \draw ( 0, 5pt) node[above, color=\PC]{$\ADD_d^{0.5}$};
-  \draw (2*\X, 5pt) node[above]{expect \textcolor{\PA}{$\alpha_a$}};
-
-  \draw (-\X, \Y + 5pt) node[above, color=\PC]{$\DEL_d$};
+  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_d^{0.5}$};
+  \draw (\X,-5pt) node[below, font=\scriptsize]{expect \textcolor{\PA}{$\alpha_a$}};
+  \draw (0, -5pt) node[below, font=\scriptsize]{expect $\textcolor{\PC}{\DEL_d} \rightarrow \textcolor{\PA}{\alpha_a}$};
 

### 2021-03-23 input/figproofB.tex
reworkd figures of proofs

@@
 
+  \draw[opacity=0] (-1.5*\X, 0) -- (2.5*\X, 0);
+
+  \draw[<->] (-5pt - \X, -\Y) -- node[above]{III} (5pt, -\Y); %% III    
   \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e
 
-  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - ...
+  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{IV} (5pt + \X, 5pt -\Y); %% IV
+  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'
 
-  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% ... - b
-
-  \draw[->] ( 0, \Y + 5pt) -- ( 0, -5pt); %% ... - e
-
-  \draw[->] ( -\X + 5pt, \Y ) -- ( -5pt, \Y); %% f - ...
-
-  \draw[->] ( 5pt, \Y) -- ( \X - 5pt, \Y); % ... - ...
-
-  \draw[->] ( \X + 5pt, \Y + 5pt ) -- ( 2*\X - 5pt, -5pt); % ... - b
-
-  \draw[->] ( 2*\X + 5pt, 0 ) -- ( 3*\X - 5pt, 0); % b - g
+  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{V} (5pt + 2*\X, 10pt -\Y); %% V
+  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''
 
@@
   \draw[fill=white] (0, 0) node{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (\X, 0) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (2*\X, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-
-  \draw[fill=white] ( 0, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (-\X, \Y) node{$\bm{f}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-
-  \draw[fill=white] ( \X, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-
-  \draw[fill=white] ( 3*\X, 0) node{$\bm{g}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (2*\X, 0) node{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
   \draw (-\X, 5pt) node[above, color=\PC]{$\DEL_d$};
-  \draw ( 0, 5pt) node[above, color=\PB]{$\ADD_f^{0.5}$};
-  \draw (2*\X, 5pt) node[above, align=center]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{0.5}}$\\$\textcolor{\PB}{\ADD_f^1} \rightarrow \textcolor{\PB}{\DEL_f} \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
 
-  \draw (-\X, \Y + 5pt) node[above, color=\PB]{$\DEL_f$};
+  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_f^{0.5}$};
+  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PB}{\DEL_f}$};
 
-  \draw (3*\X, -5pt) node[below, align=center]{$\textcolor{\PC}{\ADD_d^{1.5}}$\\expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{1.5}}$};
+  \draw ( \X, 5pt) node[above]{$\textcolor{\PB}{\ADD_f^1} \rightarrow \textcolor{\PB}{\DEL_f} \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
+  \draw ( \X, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{0.5}}$};
+
+  \draw (2*\X, 5pt) node[above]{$\textcolor{\PC}{\ADD_d^{1.5}}$};
+  \draw (2*\X, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{1.5}}$};
 

### 2021-03-23 input/proposal.tex
reworkd figures of proofs

@@
 
-\input{input/figdel.tex} %% figure positioning
+%% \input{input/figdel.tex} %% figure positioning
 
@@
 
-\begin{algorithm}
-  \input{input/algoadddelundo.tex}
-  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
-\end{algorithm}
-
 \input{input/figproof.tex}
@@
 
-\begin{definition}[\TODO{Adaptive scope}]
-  Eventual consistent partitioning in presence of dynamic
-  partitioning. Eventually get the last partition, eventually remove
-  all outdated control information.
-\end{definition}
+\begin{theorem}[Dynamic consistent partitioning]
+  Eventual consistent partitioning in presence of dynamic sources
+  requires
+  \begin{inparaenum}[(i)]
+  \item eventual purging of stale notifications, and
+  \item eventual delivery of bests partitions.
+  \end{inparaenum}
+\end{theorem}
 
-Since the number of partitions does not monotonically increase in the
-system any longer, each process requires a vector of versions that
-monotonically increases over delivered operations.
-
-This allows processes to quickly discard stale messages saving
-bandwidth. For instance, a process that received a message originated
-at Process $a$ with a version $2$ knows that any message originated at
-Process $a$ with a version $1$ are stale system-wide; it must not
-forward it. As consequence, this also ensure termination, for
-corresponding add and delete messages cannot follow each other in
-infinite loops.
-% In terms of traffic, this only requires each message
-% to piggyback a source identifier and version number.
-
-\noindent Deletes must trigger competition amongst neighboring
-partitions. These \TODO{add} messages operate normally and fill gaps
-left open by deletes.
-
-\TODO{Paths and \NAME synergies well, for paths tend to be smaller as the
-number of sources increase in the system.}
+\begin{proof}
+\TODO{Meow meow meow.}
+\end{proof}
 
@@
 new neighbors.
-
-\begin{algorithm}
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
-\end{algorithm}
 
@@
 
+\begin{algorithm}
+  \input{input/algoadddelundo.tex}
+  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
+\end{algorithm}
+
 \TODO{Move everything related to implementation here, including optimizations.}
+
+Since the number of partitions does not monotonically increase in the
+system any longer, each process requires a vector of versions that
+monotonically increases over delivered operations.
+
+This allows processes to quickly discard stale messages saving
+bandwidth. For instance, a process that received a message originated
+at Process $a$ with a version $2$ knows that any message originated at
+Process $a$ with a version $1$ are stale system-wide; it must not
+forward it. As consequence, this also ensure termination, for
+corresponding add and delete messages cannot follow each other in
+infinite loops.
+% In terms of traffic, this only requires each message
+% to piggyback a source identifier and version number.
+
+\noindent Deletes must trigger competition amongst neighboring
+partitions. These \TODO{add} messages operate normally and fill gaps
+left open by deletes.
+
+\TODO{Paths and \NAME synergies well, for paths tend to be smaller as the
+number of sources increase in the system.}
+
+\begin{algorithm}
+  \input{input/algoedges.tex}
+  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
+\end{algorithm}
 

### 2021-03-23 input/figproofB.tex
issue depiction

@@
 
-  \draw[<->] (-5pt - \X, -\Y) -- node[above]{III} (5pt, -\Y); %% III    
+  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I as well
   \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e
 
-  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{IV} (5pt + \X, 5pt -\Y); %% IV
+  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{III} (5pt + \X, 5pt -\Y); %% IV
   \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'
 
-  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{V} (5pt + 2*\X, 10pt -\Y); %% V
+  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{IV} (5pt + 2*\X, 10pt -\Y); %% V
   \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''
@@
 
-  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_f^{0.5}$};
+  \draw ( 0, 5pt) node[above]{$\textcolor{\PC}{\ADD_d} \rightarrow \textcolor{\WRONG}{\ADD_f^{0.5}}$};
   \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PB}{\DEL_f}$};

### 2021-03-23 input/proposal.tex
issue depiction

@@
 
+Figure~\ref{fig:proof} depicts the issues with staleness and message
+orderings. In Figure~\ref{fig:proofA}, the shortest path from any
+source to Process $c$ is $[a, b, c]$. However, Process $b$ still holds
+a stale $\alpha_d^{0.5}$ without knowing. When it receives
+$\alpha_a^1$, it discards it, for it assumes that downstream processes
+are more interested in $\alpha_d^{0.5}$. To reach consistent
+partitioning, Process $b$ first needs to purge its current partition
+to later accept that of its current actual shortest path:
+$\alpha_a^1$.
+
+\noindent Figure~\ref{fig:proofB} shows that removing stale control
+information is even more complex. The removal must reach all processes
+of the previous shortest path going from $d$ to $b''$. Label I shows
+the most obvious issue where Process $e$ changed partition for a
+better but stale $\alpha_f$. Since it can remember its previous
+deliveries, it could still forward $\delta_d$ for the sake of
+consistency. However, this would lead to every process forwarding
+every $\delta$ they ever delivered. Such protocol's overhead would
+depend on past partitioning instead of current one. Label III shows
+the issue when the blocking partition is already known to be stale at
+Process $b'$. Process $b''$ eventually receives $\alpha_f$ from
+$e$. However, it cannot deliver it, for it would break last win order.
+Process $b'$ may be in an inconsistent state. Label IV shows the
+corollary issue: Process $b''$ delivered a message from a process that
+may be inconsistent without knowing it.
+
 \begin{theorem}[Dynamic consistent partitioning]

### 2021-03-23 input/proposal.tex
wip on implem mostly

@@
 
-\subsection{Dynamic partitions}
+\subsection{Principle}
 At any time, a process can become a source, hence adding a new
@@
 information is even more complex. The removal must reach all processes
-of the previous shortest path going from $d$ to $b''$. Label I shows
+of the previous shortest path going from $d$ to $b''$. Label I' shows
 the most obvious issue where Process $e$ changed partition for a
@@
   \TODO{Meow meow meow.}
+  \TODO{Label I: default propagation to what seems the border of the partition but isn't.}
+  \TODO{Label II: gates eventually break because of I', III, IV.}
+  \TODO{Label I': as Label I.}
+  \TODO{Label III: detecting possible inconsistent partitioning.}
+  \TODO{Label IV: propagation of this issue to all and only concerned parties.}
 \end{proof}
 
-\subsection{Dynamic networks}
+\subsection{Implementation}
+
+\begin{algorithm}
+  \input{input/algoadddelundo.tex}
+  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
+\end{algorithm}
+
+Algorithm~\ref{algo:adddelundo} provides the instructions that
+implement dynamic consistent partitioning:
+\begin{inparaenum}[(i)]
+\item most of the time, it propagates $\alpha$'s and $\delta$'s when
+  the partitions allow it;
+\item sometimes, it detects possible inconsistent partitioning and
+\item solves it using propagation trees (as opposed to propagation
+  graphs);
+\item when required, it triggers competitions among neighboring
+  partitions.
+\end{inparaenum}
+
+\paragraph{Dynamic partitions.}
+We extend Algorithm~\ref{algo:add} to enable each source to revoke its
+self-appointed status of source and become a simple process again. In
+that regard, we enforce the delivery order of messages at each
+process.
+
+\noindent To implement last win order, each process maintains a vector
+of versions that associates to each known source, or has-been source,
+its known local counter. It enables processes to deliver only
+up-to-date $\alpha$'s that may improve their best known partition (see
+Line~\ref{line:detectA}), but also to detect possible inconsistent
+partitioning (see Line~\ref{line:detectB}) as labeled by III in
+Figure~\ref{fig:proofB}. From a global perspective, it ensures
+monotonic increase of knowledge despite the non-monotonic number of
+sources. In turns, it contributes to convergence and termination, for
+corresponding $\alpha$ and $\delta$ cannot follow each other in an
+infinite loop.
+
+\noindent Upon possible inconsistency, the detecting process must
+remove all $\alpha$ messages originating from it, as labeled by IV in
+Figure~\ref{fig:proofB}. Contrarily to delete operations, this applies
+to a sub-partition of the current partition, and cannot rely on local
+counters to operate. Therefore, we implement this behavior by
+piggybacking paths in messages.  \TODO{Paths and \NAME synergies well,
+  for paths tend to be smaller as the number of sources increase in
+  the system.}
+
+\noindent Deletes must trigger competition amongst neighboring
+partitions. These \TODO{add} messages operate normally and fill gaps
+left open by deletes.
+
+\begin{algorithm}
+  \input{input/algoedges.tex}
+  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
+\end{algorithm}
+
+\paragraph{Dynamic network.}
 Adding new communication links to the network may create shortcuts
@@
 
-\subsection{Implementation}
-
-\begin{algorithm}
-  \input{input/algoadddelundo.tex}
-  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
-\end{algorithm}
-
-\TODO{Move everything related to implementation here, including optimizations.}
-
-Since the number of partitions does not monotonically increase in the
-system any longer, each process requires a vector of versions that
-monotonically increases over delivered operations.
-
-This allows processes to quickly discard stale messages saving
-bandwidth. For instance, a process that received a message originated
-at Process $a$ with a version $2$ knows that any message originated at
-Process $a$ with a version $1$ are stale system-wide; it must not
-forward it. As consequence, this also ensure termination, for
-corresponding add and delete messages cannot follow each other in
-infinite loops.
-% In terms of traffic, this only requires each message
-% to piggyback a source identifier and version number.
-
-\noindent Deletes must trigger competition amongst neighboring
-partitions. These \TODO{add} messages operate normally and fill gaps
-left open by deletes.
-
-\TODO{Paths and \NAME synergies well, for paths tend to be smaller as the
-number of sources increase in the system.}
-
-\begin{algorithm}
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
-\end{algorithm}
+\paragraph{Bloom filters.}
+We also propose an implementation that further decreases generated
+traffic and improves on anonymity~\cite{whitaker2002forwarding}.
+\NAME makes extensive use of paths to enable deleting messages without
+incrementing local counters. Messages carry their respective path and
+processes detect when such messages have been looping when they carry
+their identity (see Lines~\ref{line:notloopingA} and
+\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
+membership is all that matters, we propose to trade vectors of
+identities for Bloom filters~\cite{almeida2007scalable}. Processes
+know with high probability if they already received and forwarded each
+message without knowing the identity of all processes that received
+it.  False positive probability only incurs premature stopping of
+broadcast messages and does not invalidate the delete of specific
+messages.
 
@@
 
-\section{Complexity}
+\subsection{Complexity}
 \label{sec:complexity}

### 2021-03-24 input/proposal.tex
about implem

@@
 
-Each process is stateless, works autonomously and asynchronously, in a
-peer-to-peer fashion. Each process broadcasts each change to its
-neighborhood, for the state of its neighbors may depend on this change
-as well. Yet, the traffic generated to to adapt the scope of
-S-broadcast remains bounded, for it uses the principles of scoped
-broadcast itself. Messages that carry changes travel through the
-network depending on partition of processes, stopping as soon as they
+Each process works autonomously and asynchronously, in a peer-to-peer
+fashion. Each process broadcasts each change to its neighborhood, for
+the state of its neighbors may depend on this change as well. Yet, the
+traffic generated to to adapt the scope of scoped broadcast remains
+bounded, for it uses the principles of scoped broadcast
+itself. Messages that carry changes travel through the network
+depending on partition of processes, stopping as soon as they
 encounter uninterested processes. We demonstrate that \NAME guarantees
@@
 
-\begin{theorem}[Dynamic consistent partitioning]
+\begin{theorem}[\label{theo:dcp}Dynamic consistent partitioning]
   Eventual consistent partitioning in presence of dynamic sources
@@
 \begin{inparaenum}[(i)]
-\item most of the time, it propagates $\alpha$'s and $\delta$'s when
-  the partitions allow it;
-\item sometimes, it detects possible inconsistent partitioning and
-\item solves it using propagation trees (as opposed to propagation
-  graphs);
-\item when required, it triggers competitions among neighboring
-  partitions.
+\item \label{algo:most} most of the time, it propagates $\alpha$'s and
+  $\delta$'s when the partitions allow it;
+\item \label{algo:sometimes} sometimes, it detects possible
+  inconsistent partitioning and
+\item \label{algo:solves}solves it using propagation trees (as opposed
+  to propagation graphs);
+\item \label{algo:competition} when required, it triggers competitions
+  among neighboring partitions.
 \end{inparaenum}
+While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
+stale notifications, (\ref{algo:competition}) tackle the eventual
+delivery of the best up-to-date partitions.
 
@@
 
-\noindent To implement last win order, each process maintains a vector
-of versions that associates to each known source, or has-been source,
-its known local counter. It enables processes to deliver only
-up-to-date $\alpha$'s that may improve their best known partition (see
+To implement last win order, each process maintains a vector of
+versions that associates to each known source, or has-been source, its
+known local counter. It enables processes to deliver only up-to-date
+$\alpha$'s that may improve their best known partition (see
 Line~\ref{line:detectA}), but also to detect possible inconsistent
@@
 
-\noindent Upon possible inconsistency, the detecting process must
-remove all $\alpha$ messages originating from it, as labeled by IV in
-Figure~\ref{fig:proofB}. Contrarily to delete operations, this applies
-to a sub-partition of the current partition, and cannot rely on local
-counters to operate. Therefore, we implement this behavior by
-piggybacking paths in messages.  \TODO{Paths and \NAME synergies well,
-  for paths tend to be smaller as the number of sources increase in
-  the system.}
+Implementing the propagation of deletes is no different from the
+propagation of adds as hinted in Figure~\ref{fig:proof} with Labels I
+and I'. Messages and comparisons include the local counter of the
+source. When a process receives a better up-to-date partition, it
+delivers and forwards it. When a process receives a delete
+notification about its partition, it delivers and forwards it. It is
+worth noting that such $\delta$'s apply to the whole partition. They
+travel in the propagation graph of their partition using all
+communication links, allowing processes to change partition as soon as
+possible.
 
-\noindent Deletes must trigger competition amongst neighboring
-partitions. These \TODO{add} messages operate normally and fill gaps
-left open by deletes.
+Vectors of versions also allow each process to detect possible last
+win order violations. Upon possible inconsistency, the detecting
+process must remove all $\alpha$ messages originating from it, as
+labeled by IV in Figure~\ref{fig:proofB}. Contrarily to delete
+operations, this applies to a sub-partition of the current partition,
+and cannot rely on local counters to
+operate. Algorithm~\ref{algo:adddelundo} implements this behavior by
+piggybacking paths in messages. Paths guarantee that such $\delta$
+messages apply to all and only $\alpha$'s that followed an identical
+path. $\delta$'s propagate in the propagation tree rooted at the
+detecting process. Local states of processes remain unchanged, but
+paths in messages monotonically grow. In turns, $\alpha$ and $\delta$
+cannot follow each other in an infinite loop, for a process knows when
+it already received a forwarded a message (see
+Lines~\ref{line:notloopingA} and \ref{line:notloopingB}).
+
+\noindent It is worth noting that scoped broadcast and the
+piggybacking of paths synergies well: Paths tend to be smaller as the
+number of sources in the system increases.
+
+Finally, as stated in Theorem~\ref{theo:dcp}, dynamic consistent
+partitioning not only requires the removal of all stale partitions,
+but also the retrieval of the best up-to-date partitions. In that
+regard, $\delta$'s have dual use: since they already reach borders of
+partitions when they remove stale control informations, they also
+trigger a competition when reaching such bordering processes (see
+Line~\ref{line:compete}). This simply consists in sending the current
+partition through the communication link from which the process
+received the $\delta$. Upon receipt of this answer, processes act
+normally by propagating their changes when they improve. These adds
+fill the gaps left open by deletes.
 
@@
 \paragraph{Dynamic network.}
-Adding new communication links to the network may create shortcuts
-between processes. Both processes must send their current best
-partition to each other. Upon receipt, they act normally: if a process
-finds out that the received partition is closer than its current one,
-it delivers it which in turns also triggers another competition
-amongst neighbors due to forwarding.
+Algorithm~\ref{algo:edges} provides the instructions of \NAME that
+enable dynamic consistent partitioning in dynamic networks where
+processes can join or leave the system without
+notification. \TODO{More.}
 
-\noindent Joining the network is equivalent to add as many
-communication links as necessary between the joining process and its
-new neighbors.
+%% Adding new communication links to the network may create shortcuts
+%% between processes. Both processes must send their current best
+%% partition to each other. Upon receipt, they act normally: if a process
+%% finds out that the received partition is closer than its current one,
+%% it delivers it which in turns also triggers another competition
+%% amongst neighbors due to forwarding.
 
-When removing a communication link between two processes does not
-break any active path, because neither distances of processes depend
-on the other, then nothing needs to be done. \NAME has no overhead.
-Unfortunately, when a process' distance depends on the other process,
-the protocol becomes much more complex. Indeed, this requires to
-\TODO{undo} all add messages originated from this process. A message
-must convey the fact that
-\begin{inparaenum}[(i)]
-\item an edge at a particular process has been removed, and
-\item the distance that has been delivered by a process comes from
-  this particular process.
-\end{inparaenum}
+%% \noindent Joining the network is equivalent to add as many
+%% communication links as necessary between the joining process and its
+%% new neighbors.
 
-\noindent \NAME handles this as a particular case of partition within
-current partition: it contains to affected regions the traffic
-generated to patch affected regions. In order to know if it is
-affected by the \TODO{undo} operation, using distances already
-piggybacked in messages is not sufficient.  Each process must know the
-path taken by delivered message. Since we do not beforehand which
-communication links will crash and which messages will be affected by
-undos, each message has to carry its path along forwarding. This also
-allows processes to remove loops, for they cannot rely on version
-number (that remains unchanged) for this operation.
+%% When removing a communication link between two processes does not
+%% break any active path, because neither distances of processes depend
+%% on the other, then nothing needs to be done. \NAME has no overhead.
+%% Unfortunately, when a process' distance depends on the other process,
+%% the protocol becomes much more complex. Indeed, this requires to
+%% \TODO{undo} all add messages originated from this process. A message
+%% must convey the fact that
+%% \begin{inparaenum}[(i)]
+%% \item an edge at a particular process has been removed, and
+%% \item the distance that has been delivered by a process comes from
+%%   this particular process.
+%% \end{inparaenum}
 
-\noindent Instead of version number, one could use such paths to remove loops
-due to \TODO{add and del}, however this may be much more costly in
-terms of generated traffic. Version numbers guarantee that only one
-delete is delivered and all prior inserts are then discarded, while
-using paths, processes may deliver multiple inserts and deletes before
-reaching termination. \TODO{maybe clearer with figures.} As
-consequence, \NAME still makes use of vector of versions.
-
-\noindent Although costly, piggybacking paths with logical partitioning synergies
-well, for the size of these paths decreases quickly as the number of
-partitions grows.
-
-\paragraph{Bloom filters.}
-We also propose an implementation that further decreases generated
-traffic and improves on anonymity~\cite{whitaker2002forwarding}.
-\NAME makes extensive use of paths to enable deleting messages without
+\paragraph{Another trade-off.}
+We propose an implementation that further decreases generated traffic
+and improves on anonymity~\cite{whitaker2002forwarding}.  \NAME makes
+extensive use of paths to enable deleting messages without
 incrementing local counters. Messages carry their respective path and

### 2021-03-24 input/proposal.tex
wip complexity

@@
 \subsection{Complexity}
-\label{sec:complexity}
-
-\TODO{To rework, for there are more components now. Maybe do this
-  along the description of the approach.}
 
@@
 
-\textbf{The communication complexity} concerns the size and number of
-messages required to reach optimal partitioning. In the average-case,
-a process $i$ chosen uniformly at random among all processes creates a
-logical partition. Its messages $\alpha_i$ propagate through the
-network until reaching processes that belong to another partition
-closer to them. This splits partitions in half in average. Overall,
-the $a^{th}$ new partition comprises
+\paragraph{Space.}
+Each process needs to maintain a vector of versions the size of which
+depends on the number of sources. In the worst case, the size of this
+vector increases linearly with the number of distinct sources that
+ever existed in the system. For the sake of last win order, processes
+can never purge this vector from any entry. \TODO{Even when the
+  process leaves the system.} Fortunately, scoped broadcast limits
+message propagation to interested processes. A process at a side of
+the system may never hear of a source at the other side of the
+system. In turns, it may never have to maintain an entry for this
+source. \TODO{This is application-dependent?}
+
+\noindent Each process must also maintain the partition it belongs to,
+along with its control informations. Among other, it must maintain a
+path the size of which depends on the membership size of the
+partition. In the worst case, this path includes the identity of every
+process of the system that currently belong to the system. Eventually,
+the size of this path increases linearly with the diameter of the
+current partition. \TODO{assuming weight equals 1 \ldots}
+
+\paragraph{\TODO{Time.}}
+In terms of processing time, whatever the operation, it increases
+linearly with the number of neighbors of the process. It scales well,
+for the number of neighbors is commonly order of magnitude lower than
+the number of processes in the system. For instance, random networks
+only require $O(\log(|V|))$ neighbors to work properly \REF; and
+processes in autonomous systems have in average \TODO{X} neighbors
+\REF. Lines~\ref{line:notloopingA} and \ref{line:notloopingB} can
+prove costly depending on the data structure encoding paths. Using
+Bloom filters however, this is \TODO{efficient}: it depends on the
+number of buckets, and the number of hash functions.
+
+\noindent In terms of convergence time, every $\alpha$ needs to travel
+at least its shortest path before termination. Every $\delta$ needs to
+reach the border of its partition, triggering an $\alpha$ that fills
+the gaps left open by the removal. \TODO{More.}
+
+\paragraph{\TODO{Communication.}}
+In terms of number of messages required to reach optimal
+partitioning. In the average-case, a process $i$ chosen uniformly at
+random among all processes creates a logical partition. Its messages
+$\alpha_i$ propagate through the network until reaching processes that
+belong to another partition closer to them. This splits partitions in
+half in average. Overall, the $a^{th}$ new partition comprises
 \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
@@
 
+\noindent \TODO{In terms of size of messages.}
+
 %%% Local Variables: 

### 2021-03-29 input/experiments.tex
wip on implem mostly
wip complexity
first
text of first experiment

--- 2020-10-08 input/experiments.tex
@@
 
-\subsection{Global properties}
+This section aims at highlighting the properties of \NAME that enables
+adaptive scoped broadcast in dynamic networks. Most importantly, it
+aims at answering the following questions: Does \NAME allows the
+system to reach consistent partitioning? Does \NAME scales well in
+large networks? Does \NAME improves scoped broadcast in
+inter-autonomous systems? \TODO{Rework this.} We performed the
+experimentation using PeerSim, a simulator written in Java that allows
+researchers to evaluate and assess distributed algorithms in large
+scale networks~\cite{montresor2009peersim}. The code is available on
+the Github platform at
+\url{https://github.com/Chat-Wane/peersim-partition}.
 
-\subsection{Use case: caching}
+\subsection{Convergence and overhead}
 
-\subsection{Use case: routing}
+\paragraph{Objective:}
 
-\subsection{Use case: broadcast domain}
+To confirm the complexity analysis stating that the overhead in time
+and communication depends on current partitioning.
+
+\paragraph{Description:}
+
+We build a network comprising 10k processes. First, we chain processes
+together, then we add another communication link per process to
+another process. Since links are bidirectional, each process has 4
+communication links on average. We set the latency of links between 20
+and 40 ms at random following a uniform distribution. We set the
+weight of links between 5 and 15 at random following a uniform
+distribution. Weights and latency are different, hence the first
+$\alpha$ received by a process may not be that of its shortest
+path. It implies more concurrent operations, hence more traffic to
+reach consistent partitioning.
+
+\noindent We evaluate dynamic scoped broadcast. First, we create 100
+partitions one at a time: before adding a new partition, consistent
+partitioning must be reached. Second, we remove every partition one at
+a time, in the order of their creation, hence starting from the first
+and oldest partition that had been added.
+
+\noindent We focus on the complexity of \NAME. We measure the average
+number of messages generated per process during the experiment; and
+the time before reaching consistent partitioning after adding or
+removing a partition.
+
+\begin{figure}
+  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
+  \caption{\label{fig:complexity}Overhead of, and time before,
+    reaching consistent partitioning using \NAME.}
+  %% \caption{\label{fig:complexity}Cumulative average number of messages
+  %%   per process in a network comprising 10k processes; along with the
+  %%   duration before reaching consistent partitioning after adding or
+  %%   removing a partition, totaling 100 new partition then removed.}
+\end{figure}
+
+\paragraph{Results:}
+
+Figure~\ref{fig:complexity} shows the results of this experiment. The
+top part of the figure shows the average traffic per process divided
+between $\alpha$ and $\delta$ messages. The bottom part of the figure
+shows the time before reaching consistent partitioning.
+
+\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
+depends on the size of partitions. The first partition is the most
+expensive, for $\alpha$'s must reach every process which takes time
+and generate more traffic. Still, being reactive, as opposed as
+cycle-based protocols~\cite{jelasity2007gossip}, \NAME quickly
+converge towards consistent partitioning in only 350 milliseconds. The
+last and $100^{th}$ partition added around 21 seconds is the least
+expensive. By using scoped broadcast, control information only reaches
+a small subset of the whole network.
+
+\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
+delete operations are more expensive than add operations. Indeed, the
+top part of the figure shows that after 21 seconds, when the
+experiment involves removals, traffic includes both $\alpha$'s and
+$\delta$'s. The latter aims at removing stale information and
+triggering competition while the former aims at updating shortest
+paths. As corollary, the convergence time increases, for $\delta$'s
+must reach every partition border before any sound competitors
+propagate their partition. It is worth noting that this delete
+operation involves concurrency: removals continue to propagate while
+the competition is already partially triggered and propagating.
+
+\noindent Figure~\ref{fig:complexity} shows that the overhead of
+adding the $1^{st}$ partition does not correspond to the overhead of
+deleting this $1^{st}$ partition. When adding it, messages must reach
+all processes while when removing it, messages must reach a small
+subset of this membership. This is important, for it means that
+\NAME's overhead actually depends on the current partitioning, and
+does not depend on the past partitioning.
+
+\noindent Finally, Figure~\ref{fig:complexity} highlights that after
+49 seconds, i.e., after the 100 adds and the 100 deletes, processes do
+not generate traffic anymore. Being reactive, \NAME has no overhead
+when there is no operation in the system. This is important, for it
+means that \NAME's overhead actually depends on its usage.
+
+\subsection{Distribution and hotspots}
+
+\subsection{Inter-autonomous systems}
+
+% \subsection{Use case: caching}
+% \subsection{Use case: routing}
+% \subsection{Use case: broadcast domain}
 

### 2021-03-31 input/proposal.tex
wip

@@
 
-\begin{definition}[\underline{S}coped broadcast (S-broadcast)]
+\begin{definition}[\underline{S}coped broad\underline{cast} (\NAMEB)]
   When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
@@
 to reliable broadcast, scoped broadcast implementations expose
-different trade-offs on space, time, and communication.
+different trade-offs on space, time, and communication. In this paper,
+we introduce an adaptive scoped broadcast the cost of which actually
+depends on its operations, and the current scopes that exist in the
+system.
 
@@
 
-In this paper, we propose to dynamically adapt the scope of
-S-broadcast using S-broadcast itself. At any time, a process can
-become the source of a new logical partition by transitively modifying
-the respective state of neighboring processes using path weights. When
-a process S-broadcasts a message in this partition, it eventually
-reaches all processes belonging to this partition.  While the first
-partition gathers all processes of the system, the following
-partitions reduce the membership size of their neighboring
-partitions. In turns, the traffic generated to adapt scopes scales
-with the number of partitions.
+\section{Adaptive scoped broadcast}
+\label{sec:adaptive}
+
+In this section, we propose to dynamically adapt the scopes of \NAMEB
+using \NAMEB itself for the sake of efficiency. At any time, a process
+decides whether or not it becomes the center (or \emph{source}) of a
+scope (or \emph{partition}). Processes must eventually rally the
+partition corresponding to their closest source despite concurrent
+operations, and dynamic changes in the network.
+
+\noindent In that regard, we introduce \NAME (stands for
+\underline{A}daptive \underline{S}coped broad\underline{cast}), a
+wait-free reactive protocol for dynamic logical partitioning that
+enables adaptive scoped broadcast in dynamic distributed
+systems. \NAME's operation guarantees that processes eventually reach
+consistent partitioning by efficiently propagating their state
+changes. \NAME's overhead actually depends on its operations and
+current partitions in the system. In other terms,
+\begin{inparaenum}[(i)]
+\item when the system becomes quiescent, processes eventually converge to
+their respective partition and do not require further communication
+afterward; and
+\item processes do not pay the price of past partitioning.
+\end{inparaenum}
+
+\noindent This section starts by introducing consistent partitioning
+and its implementation when a process can only become a new source to
+create a new partition, i.e., it cannot revoke its self-appointed
+status of source. Then, it extends to include the latter behavior: it
+introduces the properties that guarantee consistent partitioning in
+such context, and it details our implementation called \NAME. Finally,
+it provides the complexity analysis of \NAME divided in time, space,
+and communication.
+
+\subsection{Consistent partitioning}
+
+At any time, a process can decide to become a source. \TODO{more.}
 
@@
 
-\section{Adaptive scoped broadcast}
-\label{sec:adaptive}
-
-In this section, we introduce \NAME (stands for \underline{A}daptive
-\underline{S}coped broad\underline{cast}), a wait-free reactive
-protocol for dynamic logical partitioning in dynamic distributed
-systems the cost of which actually depends on its usage. At any time,
-processes can add \emph{and} remove partitions from the system. When
-the system becomes quiescent, processes eventually converge to their
-respective partition and do not require further communication
-afterward.
-
-Each process works autonomously and asynchronously, in a peer-to-peer
-fashion. Each process broadcasts each change to its neighborhood, for
-the state of its neighbors may depend on this change as well. Yet, the
-traffic generated to to adapt the scope of scoped broadcast remains
-bounded, for it uses the principles of scoped broadcast
-itself. Messages that carry changes travel through the network
-depending on partition of processes, stopping as soon as they
-encounter uninterested processes. We demonstrate that \NAME guarantees
-consistent partitioning despite different order in message deliveries
-from one process to another.
-
-%% This section starts by describing \NAME's functioning by detailing its
-%% operation to avoid inconsistent states due to ordering and staleness
-%% of delivered messages. This section ends with a complexity analysis of
-%% proposed protocols.
-
-%% \subsection{Intra-autonomous system partitioning}
-
 \input{input/figproof.tex}
 
-%% In this section, we aim at solving Problem Statement~\ref{prob:intra}
-%% by proposing \NAME, a reactive logical partitioning protocol for
-%% dynamic partitioning in dynamic networks.
-
-\subsection{Principle}
+\subsection{Dynamic consistent partitioning}
 At any time, a process can become a source, hence adding a new
@@
 \noindent Each process must also maintain the partition it belongs to,
-along with its control informations. Among other, it must maintain a
+along with its control information. Among other, it must maintain a
 path the size of which depends on the membership size of the

### 2021-04-01 input/abstract.tex
abstract first draft

@@
 \begin{abstract}
+%% Context and problem
+  Edge infrastructures have been proposed as an alternative to Cloud
+  Computing to provide computing and storage capabilities closer to
+  the locations where data is generated/consumed, with the objectives
+  of reducing the latency and the volume of data passing through the
+  network. A few systems have been proposed to store data in those
+  infrastructures. Unfortunately, locating the closest copy of a
+  specific content in these systems requires to keep up-to-date an index
+  of all replicas and their respective locations. While flooding
+  approaches will not enable the maintenance of such an index for each
+  node in large systems, relying on a dedicated service contradicts
+  with the properties of Edge infrastructures in terms of locality and
+  robustness (locating sources may effectively take more time than
+  actually downloading contents).
 
-  Fog infrastructures allows content providers to better distribute
-  data over autonomous systems, hence improving on quality of user
-  experience by reducing latency. However, locating the closest data
-  sources can prove challenging in dynamic networks with dynamic
-  sources. Locating sources may effectively take more time than
-  actually downloading contents. \TODO{Related work ?} In this paper,
-  we introduce \NAME, a reactive protocol for dynamic logical
-  partitioning in dynamic networks. \TODO{source automatically create
-    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
-    flooding}). \TODO{costs of operations.} When the system becomes
-  quiescent, every process eventually converges to its closest
-  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
-    testbed?}
+%%% Our proposal
+  In this paper, we introduce \NAME, an efficient broadcast protocol
+  that relies on dynamic logical partitioning of the
+  infrastructure. \NAME only floods the relevant nodes (\ie the ones
+  that should be informed of a the creation of a closest copy),
+  enabling to keep up-to-date an index for each node eventually.  In
+  addition to demonstrating formally the correctness of our protocol \TODO{Is it true?},
+  we discuss several evaluatons performed by simulations and show
+  \TODO{blabla}.  While \NAME tackles our location problem, it can be
+  used as a building block to design new advanced services such as
+  \TODO{blabla}.
 
 \end{abstract}
+
+%\TODO{source automatically create
+%    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
+%    flooding}). \TODO{costs of operations.} When the system becomes
+%  quiescent, every process eventually converges to its closest
+%  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
+%+    testbed?}
 

### 2021-04-01 input/introduction.tex
wip
coloring figures, adding biblio, sketching abstract
mostly about AS
first draft for the introduction

@@
 
-\TODO{With the advent of Fog infrastructures, content will be increasingly
-located at the edges of the network. Either because it is where it has
-been created and it is too expensive to be transmitted to a cloud
-platform, or because it has been replicated to bring data closer to
-the end users [1]. Thanks to the locality, caching at the edge can
-benefit many diverse applications, as confirmed by recent proposals
-[2], [3], [4]. To favor this transition, the design and development of
-building blocks to manage data sets across Fog infrastructures are
-critical. One of the key challenges of such systems resides in
-locating a given content inside the network. Some systems, such as
-Cassandra [5] or CEPH [6] only rely on Hash-based functions to
-directly find an object location. A given hash is associated with a
-specific node according to a mapping that all nodes agree with,
-removing the need for any localization service. However, this implies
-moving the content to a specific node in the network according to its
-hash, thus violating the locality properties inherent to Fog
-architectures [7]. To ensure network traffic containment and avoid
-unnecessary data movements, we argue that content should be written
-locally and replicated on other nodes only if solicited (e.g.,
-according to the popularity of the object in a social media). Thereby,
-such requirements prevent relying on hash-based solutions and calls
-for a localization service [8].}
+There is an ongoing evlution of storing data from the cloud to the
+edges of the network. Either because it is where it has been created
+and it is too expensive to be transmitted through the network, or
+because it has been replicated to bring data closer to the end users
+~\cite{shi2016edge, fogstore, foggy_cache, cachier}.
+%
+To favour this transition, the design and the development of building
+blocks to manage data sets across Edge infrastructures have been
+investigated for the last few years \cite{confais2017performance,
+  confais2017object, hasenburg2020towards}.  Although these systems,
+provide good properties such as favouring network traffic confinement
+by writting data locally, determining the location where to get the
+content might be more expensive than retrieving the content itself.
+%
+Indeed, those systems, when not using a centralized index stored in a
+Cloud, rely on a Distributed Hash Table (DHT) across the different
+peers composing the infrastructure: When a client wants to access a
+specific content, it has to perform a request to a first node to
+determine from which site it will retrieve the content. Once it has
+retrieved the content from the location it selected, a local replica
+is created to improve the performance for future accesses and the
+server in charge of maintaining the index is updated to reflect this
+new location.
+%
+Accessing a remote node to find the location of an object (or one of
+its copies) has many drawbacks: (i) The \textit{lookup penalty:} the
+network latency to reach this remote node incurs an additional delay
+to get the object, before being able to start its
+downloading~\cite{asrese2019measuring, doan2019tracing}, (ii)
+Answering external queries increases the load on the remote node,
+potentially impacting its performance, (iii) It prevents nodes to
+access objects in case of network partitioning: if the node in charge
+of maintaining the object locations is isolated from the rest of the
+infrastructure, nodes cannot access the object replicas even if some
+would be reachable.
 
-\TODO{Most existing implementations of such a localization service imply
-contacting a remote node, either a centralized server [9], or a node
-of a DHT [10]: When a client wants to access a specific content, first
-it has to perform a request to a specific node to determine where to
-retrieve this content from.  Once it has retrieved the data from the
-location it selected, a local replica is created to improve the
-performance for future accesses. The node in charge of maintaining the
-index is finally updated to reflect this new location. Yet, accessing
-a remote node to find the location of an object (or one of its copies)
-has many drawbacks: (i) The lookup penalty: the network latency to
-reach this remote node incurs an additional delay to get the object,
-before being able to start its downloading, (ii) Answering external
-queries increases the load on the remote node, potentially impacting
-its performance, (iii) It prevents nodes to access objects in case of
-network partitioning: if the node in charge of maintaining the object
-locations is isolated from the rest of the infrastructure, nodes
-cannot access the object replicas even if some would be reachable.}
+A simple way to tackle the aforementioned limitations would be to
+maintain an index of all replicas on each node composing the
+system. In addition to being complicated \TODO{impossible} for large-scale
+systems, maintaining such a global index on each node is useless as there
+is no interest to inform a node of the creation of a replica at the
+opposite of the network (each node trying to get content from the closest node).
+%
+In this paper, we propose to limit the broadcast of creation/deletions
+of replicas only to a subset of the nodes composing the
+infrastructures.  Concretely, our protocol, entitled \NAME, transmits
+messages from peer to peer until a certain condition is reached. In
+the current scenario, the stop condition is related to the distance to
+the nearest copy: if the message that a node receives indicates an
+object has a longer distance than that which the node knows then the
+transfer of the message is useless and so stopped.
 
-\TODO{To tackle the aforementioned limitations of a remote service, we
-propose A3, an epidemic protocol that propagates information about
-replica localizations asynchronously. A3 leverages the underlying
-infrastructure topology to avoid flooding the network so that it only
-informs the relevant nodes, according to the existing replicas in the
-system. Upon receiving messages, nodes maintain a personalised index
-about replica localization, according to their place in the topology,
-ensuring that each request will be routed towards its closest
-replica. We implemented our protocol and deployed it on a dedicated
-testbed emulating real-world topologies from the Internet Toplogy Zoo
-[11]. Our evaluation shows that A3 is able to provide a similar
-localization service when compared to a DHT-based approach while
-removing the lookup penalty.  This directly translates into faster
-data access as shown by our measurements, with a time reduction from
-20\% to 60\%, depending on the sizes of the objects. Finally, we show
-that by slightly delaying the sending of messages, A3 can match the
-number of messages of a DHT-based approach, at the cost of a moderate
-increase in message sizes.}
+\TODO{add something about the paper work}
+
+\input{input/figadd.tex} %% positioning (belong to problem & motivation)
 

### 2021-04-01 input/introduction.tex
fix bib issues and add the simulation paragraph back into the introduction

@@
 because it has been replicated to bring data closer to the end users
-~\cite{shi2016edge, fogstore, foggy_cache, cachier}.
+~\cite{shi2016edge, foggy_cache, cachier}.
 %
@@
 investigated for the last few years \cite{confais2017performance,
-  confais2017object, hasenburg2020towards}.  Although these systems,
+  confais2017object, fogstore, hasenburg2020towards}.  Although these systems,
 provide good properties such as favouring network traffic confinement
@@
 
-\input{input/figadd.tex} %% positioning (belong to problem & motivation)
+We evaluated our protocol through simulations using \textit{Peersim}~\cite{montresor2009peersim}. The topolgies we simulated are based on real-world ones from the Internet Toplogy
+Zoo~\cite{topology-zoo}.  Our evaluation shows that \NAME is able to
+provide a similar localization service when compared to a DHT-based
+approach while removing the lookup penalty or to an hypothetical complete and robust broadcast. This directly translates
+into faster data access as shown by our measurements, with a time
+reduction from $20\%$ to $60\%$, depending on the sizes of the
+objects. %\AVK[Talk about load balancing and traffic containment here]
+We also show that by slightly delaying the sending of messages, \NAME
+can match the number of messages of a DHT-based approach, at the cost
+of a moderate increase in message sizes.
 
+\TODO{Update the conclustion of the experiment}
+
+%\input{input/figadd.tex} %% positioning (belong to problem & motivation)
+
+\TODO{add a paragraph on possible usage of the protocol in other use-cases.}
+
+\TODO{update the outline}
 \TODO{The rest of this paper is organized as follows. Section II

### 2021-04-02 input/background.tex
Add first draft of related work and motivation section

@@
-\section{Background and motivation}
+\section{Related Work and Motivation}
 \label{sec:background}
 
-\TODO{More related work. More motivations etc. Maybe describe IPFS?}
+%\TODO{More related work. More motivations etc. Maybe describe IPFS?}
+This section reviews the existing solutions to locate a given content in a network and details the limitations 
+of such solutions in a Fog context. We first present the related work on content localization at the system level, 
+either with centralized or distributed approaches.
+We then focus on message-passing solutions and explain why well-known existing software middlewares such as broadcast, or gossip protocols are not good candidates in their existing implementations.
+Finally, we provide the intuition that motivated the design of our protocol.
+
+\subsection*{Content indexing}
+
+The easiest way to implement a localization service is to store all replica localizations, namely the \textit{index}, on a centralized server~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
+Before downloading any content, the client first requests the server the list of all its available replicas, in order to select the closest copy, according to its place in the topology.
+While being straightforward to deploy, this solution suffers from well-known disadvantages (load balancing, robustness, locality, etc.) that are even magnified in a Fog context.
+
+A first step to mitigate the drawbacks inherent to a unique centralized server is to deploy a \textit{landmark} system~\cite{landmarks}.
+The idea is to spread special nodes called landmarks across the network so that nodes announce their current cache content to the closest landmarks in a given geographical area.
+Requests are then processed by one or the closest landmarks from the requester.
+One of the the main problems of these lankmark-based solutions is that they require a reliable infrastructure to provide these landmarks which must remain always available to continuously offer the indexing service.
+
+Goind further, fully distributing this index among nodes in the network has been proposed, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example.
+In the latter, each node stores a part of the index, defined by an interval between hash values.
+Before downloading any object, a node first
+hashes the content to obtain the address of the node that stores the replica localizations of this given object.
+After obtaining from the remote node the list of available replicas, it can select the closest copy to download from.
+We emphasize that, in this setting, the DHT only stores information about replicas localizations, not the content itself.
+DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.
+
+However, either being centralized, landmark-based or distributed, solutions that require to contact a remote node to obtain a given content localization usually violate the locality property.
+In other words, a request about a given object localization may travel far away in the network even if this object is actually close to the requester.
+Moreover, they incur a lookup penalty that increases the time to actually get the object.
+In fact, the lookup delay can sometimes be larger than downloading the object itself, especially for smaller objects, as already observed in~\cite{confais2017performance}.
+
+Instead of requesting localization information from a remote node, another approach consists in disseminating this information accross the network.
+Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}.
+Indeed, having the full knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
+Moreover, removing the lookup latency directly involves faster downloading times.
+Multiple broadcast protocols have been designed to cope with various requirements[REF], and [REF or REF].
+One could also solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures~\cite{shapiro2011crdts}. 
+However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventuall receive all messages. 
+That means information that might only interests a small subset of nodes is actually spread out all over the network. This is in contradiction 
+with the locality property we mentionned above.
+
+Gossip protocols are also appealing candidates to disseminate information reliably across a network~\cite{epidemic-protocol}.
+Numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
+These protocols usually relies on a so-called \textit{peer-sampling service}~\cite{gossip-peer-sampling} to efficiently propagate the information.
+This implies that nodes will exchange messages with random nodes in the system that can be physically far away thus violating the locality property once again.
+
+To cope with this locality requirment, we now present the intutition behind the design of our proposal.
+
+\subsection*{Logical partioning}
+At the system level, we claim that distributing the index actually boils down to logicaly partition the physical topology, depending on the current replicas localization. 
+Exemple and Figures ?
+
+\subsection*{Overlays and membership protocols}
+At first glance, membership protocols as proposed in~\cite{t-man}[REF] would appear to provide suitable abstractions to create such a partioning. 
+BUT, usually rely on peer sampling, thus same locality problem.
+Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric. 
+On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node ar not continusously modifed. 
+Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.
+
+\subsection*{Consistency}
+Finally, we emphasize that consistency is at the core of \NAME. some blabla..
+
+To avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the source.
+This enables for a request to be caught \textit{on-path} to the source, and be redirected to the closest replica.
+However, the announcement is only performed towards the source, that is requests can miss closer replicas that are not on the path to the source, thus decreasing the efficiency of the cache sharing mechanism.
+On the contrary, \NAME ensures that eventually all
+
+One could also solve this issue by removing partitions that were not advertised for a defined time~\cite{hemmati2015namebased, garcia-lopez}. \TODO{check distance-vector protocols.} 
+However, relying on physical timeout could lead to either premature removals of partitions when they are still operating; or slow convergence where processes believe they belong to a partition that was removed (\TODO{plot ?}).
+In addition, since timeouts imply a
+continuous maintenance of partitions, such partitioning protocol
+incurs an overhead even in quiet contexts without dynamic partitions.
+
+% AVK
+% t-man: T-Man: Gossip-Based Overlay Topology Management5doat a random time 
+% at a random time once in eachconsecutive interval of T time unit
+% This buffer contains a random sample of the nodes from the entirenetwork. It is provided by apeer sampling service
+% 
+% We do not try to to create a topology aware overlay ! Because locality.
+% We do not provide routing ! routing is two determine path between any pair of nodes. We only provide path to objects 
+% 
+% Koala locality aware routing. Long links. Lazzy (nothing happens)
+% Koala  shares  many  core  aspectswith similar overlays, such as Chord and Symphony.
+% 
+% VoroNet: overlay and routing. i.e. long links 
+% It links application objects rathen than physical nodes so that objects with similar characteristic are neighbors. 
+% are logigal overlay, that are not correlated to the physical infrstructure. 
+% Usually rely on long links...
+% AVK
 
@@
 %% \TODO{Figure~\ref{fig:del} shows that.}
-
-One could solve this issue by using a conflict-free replicated data
-type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
-require eventual delivery of messages to ensure convergence. All
-processes need to receive, deliver, hence broadcast all
-operations. Some processes may receive operations unnecessary to their
-correct functioning, for these operations did not happen in their
-locality.  One could also solve this issue by removing partitions that
-were not advertised for a defined
-time~\cite{hemmati2015namebased}. \TODO{check distance-vector
-  protocols.} However, relying on physical timeout could lead to
-either premature removals of partitions when they are still operating;
-or slow convergence where processes believe they belong to a partition
-that was removed (\TODO{plot ?}). In addition, since timeouts imply a
-continuous maintenance of partitions, such partitioning protocol
-incurs an overhead even in quiet contexts without dynamic partitions.
+% 
+% One could solve this issue by using a conflict-free replicated data
+% type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
+% require eventual delivery of messages to ensure convergence. All
+% processes need to receive, deliver, hence broadcast all
+% operations. Some processes may receive operations unnecessary to their
+% correct functioning, for these operations did not happen in their
+% locality.  One could also solve this issue by removing partitions that
+% were not advertised for a defined
+% time~\cite{hemmati2015namebased}. \TODO{check distance-vector
+%   protocols.} However, relying on physical timeout could lead to
+% either premature removals of partitions when they are still operating;
+% or slow convergence where processes believe they belong to a partition
+% that was removed (\TODO{plot ?}). In addition, since timeouts imply a
+% continuous maintenance of partitions, such partitioning protocol
+% incurs an overhead even in quiet contexts without dynamic partitions.
 

### 2021-04-02 input/experiments.tex
ieee style

@@
 the Github platform at
-\url{https://github.com/Chat-Wane/peersim-partition}.
+\url{https://github.com/Chat-Wane/peersim-partition}.\TODO{Anonoymous.}
 
-\subsection{Convergence and overhead}
+\subsection{Confirm the complexity analysis stating that
+  communication and time overheads depend on the current partitioning
+  of the system.}
 
-\paragraph{Objective:}
-
-To confirm the complexity analysis stating that the overhead in time
-and communication depends on current partitioning.
-
-\paragraph{Description:}
-
-We build a network comprising 10k processes. First, we chain processes
-together, then we add another communication link per process to
-another process. Since links are bidirectional, each process has 4
-communication links on average. We set the latency of links between 20
-and 40 ms at random following a uniform distribution. We set the
-weight of links between 5 and 15 at random following a uniform
-distribution. Weights and latency are different, hence the first
-$\alpha$ received by a process may not be that of its shortest
-path. It implies more concurrent operations, hence more traffic to
-reach consistent partitioning.
+\begin{asparadesc}
+\item [Description:] We build a network comprising 10k
+  processes. First, we chain processes together, then we add another
+  communication link per process to another process. Since links are
+  bidirectional, each process has 4 communication links on average. We
+  set the latency of links between 20 and 40 ms at random following a
+  uniform distribution. We set the weight of links between 5 and 15 at
+  random following a uniform distribution. Weights and latency are
+  different, hence the first $\alpha$ received by a process may not be
+  that of its shortest path. It implies more concurrent operations,
+  hence more traffic to reach consistent partitioning.
 
@@
 
-\paragraph{Results:}
+\item [Results:]
 
@@
 
+\end{asparadesc}
+
 \subsection{Distribution and hotspots}

### 2021-04-02 input/proposal.tex

@@
 
-\begin{definition}[\underline{S}coped broad\underline{cast} (\NAMEB)]
+\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
   When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
@@
 
+\input{input/figadd.tex} %% positioning (belong to problem & motivation)
+
 In this section, we propose to dynamically adapt the scopes of \NAMEB
@@
 
-At any time, a process can decide to become a source. \TODO{more.}
+At any time, a process can decide to become a source, hence creating a
+new partition in the system by executing an \texttt{Add}
+operation. This partition includes at least its source plus
+neighboring processes that estimate they are closer to this source
+than any other source. Such distance (or \emph{weight}) is
+application-dependant. For instance, weights could be latency in live
+streaming applications, or differences in profiles for recommendation
+systems.
+
+\begin{definition}[\label{def:partitioning}Partitioning]
+  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
+  the \underline{p}artition including at least Process $s$, each
+  process belongs to at most one partition $\forall p,q \in V, \forall
+  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
+  \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
+  processes that belong to this partition $\forall q \in \pi_{ps}: q
+  \in P_s$.
+\end{definition}
+
+Definition~\ref{def:scoped} and Definition~\ref{def:partitioning}
+share the transitive relevance of process states. However, we further
+constrain the partitioning in order to guarantee the existence of
+exactly one consistent partitioning that processes eventually converge
+to.
 
 \begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
-  W_{yx}$ be the symmetric \underline{w}eight between $x$ and $y$,
-  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
-  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
-  the only consistent partitioning $\mathcal{P}$ is a set of logical
+  Let $W_{xy} = W_{yx}$ be the symmetric \underline{w}eight between
+  $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to
+  $z$ the weight of which $|\Pi_{xz}|$ is lower than any other path
+  weight, the only consistent partitioning $\mathcal{P}$ is a set of
   partitions $P_{s\in S}$ such that each process belongs to a logical
@@
 
-%% \begin{theorem}[$SPED \implies CP$]
-%%   \underline{S}hortest \underline{p}ath \underline{e}ventual
-%%   \underline{d}elivery (SPED) where each process $k_n$ in the shortest
-%%   path $\Pi_{ps}: [s, k_1,\ldots,k_n,p]$ eventually deliver the
-%%   message forwarded by its predecessor $k_{n-1}$ leads to consistent
-%%   partitioning.
-%% \end{theorem}
-
-%% \TODO{or:}
+Unfortunately, processes do not share a common global knowledge of the
+network state. For process to reach consistent partitioning together,
+a process becoming a source must notify every process that is closer
+to it than any other source. Epidemic
+dissemination~\cite{birman1999bimodal} constitutes an efficient
+communication pattern to perform such operation.
 
 \begin{theorem}[\underline{B}est \underline{e}ventual \underline{d}elivery $(BED) \implies CP$]
-  Every process eventually delivers, hence forwards, the notification
-  message $\alpha_s$ of its best partition $P_s$, eventually leading
-  to consistent partitioning.
+  Assuming reliable communication links, every process eventually
+  delivers, hence forwards, the notification message $\alpha_s$ of its
+  best partition $P_s$, eventually leading to consistent partitioning.
 \end{theorem}

### 2021-04-02 input/proposal.tex
rework scoped broadcast

@@
+%% to better adapt positioning (I expect 2.5 pages
+%% intro+related work)
+\newpage
+
 \section{Scoped broadcast}
@@
 
-In this section, we introduce model and notations to provide a general
-definition of scoped broadcast in distributed systems.  Distributed
-systems such as Edge infrastructures comprise heterogeneous machines
-interconnected by communication links. We do not consider byzantine
-processes.
+Scoped broadcast is a communication primitive that propagates a
+message around its broadcaster within an application-dependant scope.
+For instance, a process from Paris could scoped broadcast messages to
+all processes in Paris; and processes from other cities would never
+deliver such messages. Scoped broadcast allows its implementations to
+reduce generated traffic compared to uniform reliable
+broadcast~\cite{hadzilacos1994modular, raynal2013distributed}, for
+message propagation can stop as soon as messages reach the borders of
+the scope.  This section introduces model and notations to provide a
+general definition of scoped broadcast in distributed
+systems. \TODO{to help understand adaptive scoped broadcast :).}
+\TODO{Better transition to the rest of this section.}
+
+Distributed systems such as Edge infrastructures comprise
+heterogeneous machines interconnected by communication links. We do
+not consider byzantine processes.
 
@@
 can reliably broadcast messages by forwarding delivered
-messages~\cite{hadzilacos1994modular,nedelec2018causal,raynal2013distributed}. However,
-uniform reliable broadcast states that \emph{all} correct processes
-must deliver broadcast messages. This proves costly in large scale
-systems comprising thousands of processes. Instead, we define
-\emph{scoped broadcast} where messages reach only interested
-processes, significantly reducing generated traffic.
+messages~\cite{birman1999bimodal, hadzilacos1994modular,
+  nedelec2018causal, raynal2013distributed}. However, uniform reliable
+broadcast states that \emph{all} correct processes must deliver
+broadcast messages. This proves costly in large scale systems
+comprising thousands of processes. Instead, we define \emph{scoped
+broadcast} where messages reach only interested processes,
+significantly reducing generated traffic.
 
@@
   \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
-  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
-  processes, \underline{m}etadata $\mu$ within received messages, and
-  a \underline{p}redicate $\phi$ verified from process to process:
-  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
-  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
+  $d_y(m)$. The scope depends on the \underline{s}tate $\sigma$ of
+  each process, the \underline{m}etadata $\mu$ piggybacked by each
+  message, and a \underline{p}redicate $\phi$ verified from process to
+  process: $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
+  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$.
 \end{definition}
@@
 encompasses more specific definitions of related
-work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
-process from Paris could scoped broadcast a message to all processes
-in this city. A process from Paris could scoped broadcast a message to
-all processes in this city plus neighboring cities by overloading
-forwarded messages the first time they reach another city. Similarly
-to reliable broadcast, scoped broadcast implementations expose
-different trade-offs on space, time, and communication. In this paper,
-we introduce an adaptive scoped broadcast the cost of which actually
-depends on its operations, and the current scopes that exist in the
-system.
+work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}. For
+instance, a process from Paris could scoped broadcast messages to all
+processes in Paris. This requires processes to know the city they are
+in. In another instance, a process from Paris could scoped broadcast
+messages to all processes in Paris plus neighboring cities. This
+requires processes to overload forwarded messages the first time they
+reach another city. The predicate checks if messages already reached
+two distinct cities before delivery. Similarly to uniform reliable
+broadcast, scoped broadcast implementations expose different
+trade-offs on space, time, and communication.
 
-%% \begin{definition}[S-broadcast properties]
-%%   S-broadcast guarantees 3 properties:
-%%   \begin{inparaenum}[(i)]
-%%   \item Validity: If a correct process broadcasts a message, it
-%%     eventually delivers it;
-%%   \item Scoped Agreement: If a process broadcasts a message, then all
-%%     correct processes within the scope eventually delivers it;
-%%   \item Scoped Integrity: A process delivers a message only if it was
-%%     previously broadcast within the scope.
-%%   \end{inparaenum}
-%% \end{definition}
+Next Section introduces an adaptive scoped broadcast where the state
+of each process is dynamic and changes depending all distinct scopes
+that exist in the system.
+
+% the cost of
+% which actually depends on its operations, and the current scopes that
+% exist in the system.
 
@@
 
-\input{input/figadd.tex} %% positioning (belong to problem & motivation)
+\input{input/figadd.tex}
 
@@
 regard, $\delta$'s have dual use: since they already reach borders of
-partitions when they remove stale control informations, they also
+partitions when they remove stale control information, they also
 trigger a competition when reaching such bordering processes (see

### 2021-04-02 input/proposal.tex
wip, on the understanding of properties

@@
 %% intro+related work)
+
+\vfill \TODO{spacing for intro and related work: 2.5 pages}
 \newpage
@@
 Next Section introduces an adaptive scoped broadcast where the state
-of each process is dynamic and changes depending all distinct scopes
-that exist in the system.
-
-% the cost of
-% which actually depends on its operations, and the current scopes that
-% exist in the system.
+of each process is dynamic and changes depending on all distinct
+scopes that exist in the system.
 
@@
 \label{sec:adaptive}
-
-\input{input/figadd.tex}
 
@@
 Unfortunately, processes do not share a common global knowledge of the
-network state. For process to reach consistent partitioning together,
-a process becoming a source must notify every process that is closer
-to it than any other source. Epidemic
+network state. For processes to reach consistent partitioning
+together, a process becoming a source must notify every process that
+is closer to it than any other source. Epidemic
 dissemination~\cite{birman1999bimodal} constitutes an efficient
@@
 
-\begin{theorem}[\underline{B}est \underline{e}ventual \underline{d}elivery $(BED) \implies CP$]
-  Assuming reliable communication links, every process eventually
-  delivers, hence forwards, the notification message $\alpha_s$ of its
-  best partition $P_s$, eventually leading to consistent partitioning.
+\begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \iff CP$]
+  Assuming reliable communication links where a correct process $q$
+  eventually receives the message $m$ \underline{s}ent to it by a
+  process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a static system ($G^t =
+  G^{t+1}$); assuming local knowledge only, processes eventually reach
+  consistent partitioning if and only if each process eventually
+  forwards its best known partition.
 \end{theorem}
 
-\begin{proof} When a process $s_1$ becomes a source, it belongs to
-its own partition, for there exists no better partition than its own:
-$\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It broadcasts such
-message to its neighbors. Since communication channels are reliable,
-neighboring processes eventually receive such notification. In
-particular, whatever the order of received messages, every process
-$p_1$ such that there exists no better partition $s_2$ than the
-received one delivers and forwards it: $\forall s_2 \in S: |\Pi_{p
-  s_1}| < |\Pi_{p s_2}|$. The notification emanating from $s_1$
-transitively reaches all such processes through shortest paths. Since
-there exists only one best value per process that can never be
-retracted, processes eventually reach consistent partitioning.
+\TODO{If forwarding defined as send to all neighbors, then it also
+  works in dynamic systems where processes join and edges are added,
+  for when a new neighbor appears, the processes must forward their
+  best.}
+
+\begin{proof}
+  \begin{asparadesc}
+  \item [$BEF \implies CP$:] When a process $s_1$ becomes a source, it
+    belongs to its own partition, for there exists no better partition
+    than its own: $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1
+      p}|$. It broadcasts such message to its neighbors. Since
+    communication channels are reliable, neighboring processes
+    eventually receive such notification. In particular, whatever the
+    order of received messages, every process $p_1$ such that there
+    exists no better partition $s_2$ than the received one delivers
+    and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| < |\Pi_{p
+      s_2}|$. The notification emanating from $s_1$ transitively
+    reaches all such processes through shortest paths. Since there
+    exists only one best value per process that can never be
+    retracted, processes eventually reach consistent
+    partitioning. \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
+  \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
+    process $p$ that does not forward, then another process $q$ may
+    never gets its best because it needs the weight $W_{pq}$.}
+  \end{asparadesc}
 \end{proof}
-
-%% \input{input/figdel.tex} %% figure positioning
-
-%% \begin{definition}[\label{def:transitivedelivery}Transitive delivery]
-%%   Transitive delivery ensures the system eventually converges to
-%%   optimal partitioning:
-%%   \begin{inparaenum}[(i)]
-%%   \item (\textbf{termination}) processes do not need to propagate
-%%     operations they do not deliver: $\forall \langle i, j \rangle \in
-%%     E, \neg d_i(\alpha_{s}^w)\implies \neg
-%%     d_j(\alpha_{s}^{w+w_{ij}})$;
-%%   \item (\textbf{propagation}) operations delivered by a process may
-%%     also benefit neighbor processes: $\forall \langle i, j \rangle \in
-%%     E, d_i(\alpha_{s}^{w_1}) \implies
-%%     d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
-%%     d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
-%%   \end{inparaenum}
-%% \end{definition}
 
@@
 
-Algorithm~\ref{algo:add} shows the instructions that implement
-eventually consistent partitioning when
+\input{input/figadd.tex}
+
+Algorithm~\ref{algo:add} shows the instructions that implement such
+consistent partitioning when
 \begin{inparaenum}[(i)]
-\item processes only have local knowledge about their direct
-  neighborhoods,
 \item weights are scalar values,
-\item and processes only add new partitions to the system.
+\item processes only add new partitions to the system,
+\item and processes never crash nor leave the system.
 \end{inparaenum}
-At any time, a process running this protocol can add a logical
-partition to its distributed system.  Figure~\ref{fig:add} illustrates
-its behavior on a system comprising 4 processes $a$, $b$, $c$, and
-$d$. Two processes $a$ and $c$ concurrently create a partition by
-S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
-and $\alpha_c^0$. They initialize their own state with the lowest
-possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
-message to each of their neighbors by accumulating the corresponding
-edge weight (see Line~\ref{line:accumulator}). In
-Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
-improves its own partition distance, it keeps it and forwards it to
-its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
-not improve its partition distance. Processes $c$ and $d$ will never
-hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
-discard last transiting messages. The system converged to the
-consistent partitioning. However, since processes operate using local
-knowledge only, generated traffic may be sub-optimal, for processes
-may receive, deliver, and forward messages emanating from a same
-source simply because it did not come from the shortest path yet.
+ Figure~\ref{fig:add} illustrates its behavior on a system comprising
+ 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and $c$
+ concurrently create a partition by S-broadcasting their respective
+ \underline{a}dd message: $\alpha_a^0$ and $\alpha_c^0$. They
+ initialize their own state with the lowest possible bound $0$ (see
+ Line~\ref{line:lowestbound}), and send a message to each of their
+ neighbors by accumulating the corresponding edge weight (see
+ Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
+ receives $\alpha_{c}^{1}$. Since it improves its own partition
+ distance, it keeps it and forwards it to its neighbors. Process $b$
+ discards $\alpha_{b}^{1.5}$, for it does not improve its partition
+ distance. Processes $c$ and $d$ will never hear of Process $a$'s
+ partition.  In Figure~\ref{fig:addD}, processes discard last
+ transiting messages. The system converged to the consistent
+ partitioning. However, since processes operate using local knowledge
+ only, generated traffic may be sub-optimal, for processes may
+ receive, deliver, and forward messages emanating from a same source
+ simply because it did not come from the shortest path yet.
 
@@
 partition to the system. This partition eventually includes all
-processes that are closer from this new source than any other else. We
-described such protocol in Section~\ref{sec:scoped}. Processes
-naturally converge towards their respective best partition by only
-piggybacking a monotonically increasing distance in forwarded
-messages. % \TODO{Traffic of each partition is contained to the
-%  partition.}
+processes that are closer from this new source than any other
+else. Processes naturally converge towards their respective best
+partition by only piggybacking a monotonically increasing distance in
+forwarded messages.
 
@@
 
-\begin{theorem}[\label{theo:dcp}Dynamic consistent partitioning]
+\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
   Eventual consistent partitioning in presence of dynamic sources
@@
   \end{inparaenum}
-\end{theorem}
+\end{corollary}
 

### 2021-04-07 input/figdel.tex
figures

@@
-\begin{figure*}
+\begin{figure}
   \begin{center}
-    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
-      Process $c$ initiate then remove a partition.
-      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
+    \subfloat[Part A][\label{fig:delA}Process~$a$ deletes its
+      partition.  It notifies all processes that belong to its
+      partition using \NAMEB.]{\input{input/figdelA.tex}}
     \hspace{5pt}
-    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
-      messages based on their weights. $a$'s partition propagates to all processes.]
-             {\input{input/figdelB.tex}}
-    \hspace{5pt}
-    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
-      Its removal shortly follows. Process $b$ does not have any control
-      information about partitions any more.]{\input{input/figdelC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
-      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
-      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
-      partition.]{\input{input/figdelD.tex}}
+    %
+    \subfloat[Part B][\label{fig:delB}$\delta$s stop as soon as they
+      encounter another partition. Process~$b$ answers with its
+      partition.]{\input{input/figdelB.tex}}
   \end{center}
-  \caption{\label{fig:del}Partition removals cannot rely only on
-    current partition, for it may lead to either inconsistent
-    partitioning, or every process receiving every broadcast.}
-\end{figure*}
+  \caption{\label{fig:del}Efficient removal of a partition using
+    \NAME. Process~$a$ eventually knows that it belong to Partition
+    $P_c$.}
+\end{figure}
 

### 2021-04-07 input/figproblem.tex
figures

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:problemB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:problemC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:problemD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Partition removals cannot rely only on
    current partition, for it may lead to either inconsistent
    partitioning, or every process receiving every broadcast.}
\end{figure*}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-04-07 input/figproblemB.tex
figures

\begin{tikzpicture}[scale=0.87]

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

  \draw (-\X + 5pt, 0) --
  node[above=-0.3em,font=\tiny]{$\DEL_{a} \rightarrow$}
  node[below=-0.3em,font=\tiny]{$\leftarrow \ADD_{a}^{3}$}
  (0 - 5pt, 0); %% b - a

  \draw (0 +5pt, 0) --
  node[above=-0.3em, font=\tiny]{$\leftarrow \textcolor{\PC}{\ADD_{c}^{1}}\cdot\DEL{c}$}
  node[below=-0.3em, font=\tiny]{$\textcolor{\PA}{\ADD_a^{2.5}} \rightarrow$}
  (\X -5pt, 0); %% b - c

  \draw[opacity=0] (0, 0 - 5pt) --
  node[opacity=1, above=-0.3em, font=\tiny, sloped]{$\ADD_a^{2.5} \rightarrow$}
  (0, \Y + 5pt); %% b - d
  \draw (0, \Y + 5pt) --
  node[above=-0.3em, font=\tiny, sloped]{$\ADD_c^2 \rightarrow$}
  (0, 0 - 5pt);  %% d - b

  \draw (\X + 3pt, 0 - 5pt) --
  node[above=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{2} \rightarrow$}
  node[below=-0.3em, font=\tiny, sloped]{$\leftarrow \DEL_c$}
  (0 + 5pt, \Y - 3pt); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PA]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node[color=\PC]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  % \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
  % \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};
  \draw (0, 5pt) node[above]{$\bm{a: 1.5}$};
  \draw (-5pt, \Y) node[left]{$\bm{c: 1}$};

\end{tikzpicture}

### 2021-04-07 input/proposal.tex
figures

@@
 dissemination~\cite{birman1999bimodal} constitutes an efficient
-communication pattern to perform such operation.
+communication pattern to perform such operation. \TODO{More about
+  \emph{forwarding}.}
 
@@
     eventually receive such notification. In particular, whatever the
-    order of received messages, every process $p_1$ such that there
-    exists no better partition $s_2$ than the received one delivers
+    order of received messages, every process $p_1$ -- such that there
+    exists no better partition $s_2$ than the received one -- delivers
     and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| < |\Pi_{p
@@
 \item processes only add new partitions to the system,
-\item and processes never crash nor leave the system.
+\item and processes never join nor crash nor leave the system.
 \end{inparaenum}
@@
 
-\input{input/figproof.tex}
+\subsection{Dynamic consistent partitioning}
 
-\subsection{Dynamic consistent partitioning}
 At any time, a process can become a source, hence adding a new
@@
 that belong to this partition must eventually choose another partition
-to belong to. Unfortunately, stale control information about deleted
-partitions may impair the propagation of both
+to belong to. In Figure~\ref{fig:del}, two partitions exist initially:
+$P_a$ and $P_c$ that respectively include $\{a\}$, and $\{b, c,
+d\}$. In Figure~\ref{fig:delA}, Process $a$ deletes its partition. It
+notifies all neighboring processes -- here only Process $b$ -- that
+may belong to its partition using \NAMEB. Upon receipt, Process $b$
+discards the message $\delta_a$, for the latter does not target the
+former's partition. Yet, Process $b$ sends its own partition that may
+be the best for Process $a$. Eventually, every processes belong to the
+same partition $P_c$.
+
+\input{input/figdel.tex}
+
+Unfortunately, stale control information about deleted partitions may
+impair the propagation of both
 \begin{inparaenum}[(i)]
@@
 \end{inparaenum}
+\TODO{Figure showing inconsistency.}
 The correctness of the partitioning depends on receipt orders at each
 processes.
+
+\input{input/figproblem.tex}
 
@@
 \end{definition}
+
+\input{input/figproof.tex}
 

### 2021-04-08 input/introduction.tex
add a todo
fix biblio, first names and duplicated entries
new comment

@@
 specific content, it has to perform a request to a first node to
-determine from which site it will retrieve the content. Once it has
+determine from which site it will retrieve the content.
+\TODO{Add something about the fact that in addition to the location service of the replica, we need a service that maintain a view of the infrastructure topology so that each node can infer which replica is the closest one.}
+
+Once it has
 retrieved the content from the location it selected, a local replica
@@
 
+\TODO{Explain that the problem can be seen as a graph partitioning problem}
+
 \TODO{add something about the paper work}
@@
 We evaluated our protocol through simulations using \textit{Peersim}~\cite{montresor2009peersim}. The topolgies we simulated are based on real-world ones from the Internet Toplogy
-Zoo~\cite{topology-zoo}.  Our evaluation shows that \NAME is able to
+Zoo~\cite{knight2011internet}.  Our evaluation shows that \NAME is able to
 provide a similar localization service when compared to a DHT-based

### 2021-04-08 input/conclusion.tex
text of first experiment
rework issue with delete

@@
 \label{sec:conclusion}
+
+In this paper, we proposed a general purpose definition of scoped
+broadcast, and an extension to automatically adapt the scope of scoped
+broadcast in contexts where each process can decide whether or not it
+decide to be a source. We proposed an implementation called \NAME.
 
@@
 policy of popular contents at marginal cost.
+
+\noindent We propose an implementation that further decreases
+generated traffic and improves on
+anonymity~\cite{whitaker2002forwarding}.  \NAME makes extensive use of
+paths to enable deleting messages without incrementing local
+counters. Messages carry their respective path and processes detect
+when such messages have been looping when they carry their identity
+(see Lines~\ref{line:notloopingA} and \ref{line:notloopingB} of
+Algorithm~\ref{algo:adddelundo}). Since membership is all that
+matters, we propose to trade vectors of identities for Bloom
+filters~\cite{almeida2007scalable}. Processes know with high
+probability if they already received and forwarded each message
+without knowing the identity of all processes that received it.  False
+positive probability only incurs premature stopping of broadcast
+messages and does not invalidate the delete of specific
+messages. \TODO{Rework.}
 

### 2021-04-08 input/figproblemB.tex
rework issue with delete

@@
   node[above=-0.3em,font=\tiny]{$\DEL_{a} \rightarrow$}
-  node[below=-0.3em,font=\tiny]{$\leftarrow \ADD_{a}^{3}$}
+  % node[below=-0.3em,font=\tiny]{$\leftarrow \ADD_{a}^{3}$}
   (0 - 5pt, 0); %% b - a
@@
   \draw (0 +5pt, 0) --
-  node[above=-0.3em, font=\tiny]{$\leftarrow \textcolor{\PC}{\ADD_{c}^{1}}\cdot\DEL{c}$}
-  node[below=-0.3em, font=\tiny]{$\textcolor{\PA}{\ADD_a^{2.5}} \rightarrow$}
+  node[above=-0.3em, font=\tiny]{$\leftarrow \textcolor{\PD}{\ADD_{d}^{4}}\cdot\DEL_{d}$}
+  node[below=-0.3em, font=\tiny]{$\textcolor{\PA}{\ADD_a^{3}} \rightarrow$}
   (\X -5pt, 0); %% b - c
@@
   \draw[opacity=0] (0, 0 - 5pt) --
-  node[opacity=1, above=-0.3em, font=\tiny, sloped]{$\ADD_a^{2.5} \rightarrow$}
+  node[opacity=1, above=-0.3em, font=\tiny, sloped]{$\textcolor{\PA}{\ADD_a^{3}} \rightarrow$}
   (0, \Y + 5pt); %% b - d
   \draw (0, \Y + 5pt) --
-  node[above=-0.3em, font=\tiny, sloped]{$\ADD_c^2 \rightarrow$}
+  node[above=-0.3em, font=\tiny, sloped]{$\DEL_d \cdot \textcolor{\PD}{\ADD_d^1} \rightarrow$}
   (0, 0 - 5pt);  %% d - b
@@
   \draw (\X + 3pt, 0 - 5pt) --
-  node[above=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{2} \rightarrow$}
-  node[below=-0.3em, font=\tiny, sloped]{$\leftarrow \DEL_c$}
+  % node[above=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{2} \rightarrow$}
+  % node[below=-0.3em, font=\tiny, sloped]{$\leftarrow \DEL_c$}
   (0 + 5pt, \Y - 3pt); %% c - d
@@
   \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (0, \Y) node[color=\PC]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
-  % \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
-  % \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};
-  \draw (0, 5pt) node[above]{$\bm{a: 1.5}$};
-  \draw (-5pt, \Y) node[left]{$\bm{c: 1}$};
+  \draw (-\X+5pt, 5pt) node[above, font=\small]{$\alpha_a \rightarrow \DEL_a$};
+  \draw (\X, 5pt) node[above, font=\small]{$\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
+  \draw (0, 5pt) node[above, font=\small]{$\textcolor{\PA}{\ADD_a^{2}}$};
+  \draw (-5pt, \Y) node[left, font=\small]{$\ADD_d \rightarrow \DEL_d$};
 

### 2021-04-08 input/proposal.tex
rework issue with delete

@@
 Then, at any time, a source can revoke its self-appointed status of
-source, hence deleting its partition from the system. All processes
-that belong to this partition must eventually choose another partition
-to belong to. In Figure~\ref{fig:del}, two partitions exist initially:
-$P_a$ and $P_c$ that respectively include $\{a\}$, and $\{b, c,
-d\}$. In Figure~\ref{fig:delA}, Process $a$ deletes its partition. It
-notifies all neighboring processes -- here only Process $b$ -- that
-may belong to its partition using \NAMEB. Upon receipt, Process $b$
-discards the message $\delta_a$, for the latter does not target the
-former's partition. Yet, Process $b$ sends its own partition that may
-be the best for Process $a$. Eventually, every processes belong to the
-same partition $P_c$.
+source, hence deleting its partition from the system, by executing a
+\texttt{Del} operation. All processes that belong to this partition
+must eventually choose another partition to belong to. In
+Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_c$
+that respectively include $\{a\}$, and $\{b, c, d\}$. In
+Figure~\ref{fig:delA}, Process $a$ deletes its partition. It notifies
+all neighboring processes -- here only Process $b$ -- that may belong
+to its partition using \NAMEB. Upon receipt, Process $b$ discards the
+message $\delta_a$, for the latter does not target the former's
+partition. Yet, Process $b$ sends its own partition that may be the
+best for Process $a$. Eventually, every processes belong to the same
+partition $P_c$.
 
@@
 \begin{proof}
+  \TODO{Quite obvious.}
+\end{proof}
+
+\begin{theorem}[\TODO{meow}]
+  \TODO{Puring stale notifications requires to handle I...IV.}
+\end{theorem}
+
+\begin{proof}
   \TODO{Meow meow meow.}
@@
 
+We extend Algorithm~\ref{algo:add} to enable each source to revoke its
+self-appointed status of source and become a simple process again.
 Algorithm~\ref{algo:adddelundo} provides the instructions that
@@
 
-\paragraph{Dynamic partitions.}
-We extend Algorithm~\ref{algo:add} to enable each source to revoke its
-self-appointed status of source and become a simple process again. In
-that regard, we enforce the delivery order of messages at each
-process.
-
-To implement last win order, each process maintains a vector of
-versions that associates to each known source, or has-been source, its
-known local counter. It enables processes to deliver only up-to-date
+To constrain the order of delivery at each process, each process
+implements last win order by maintaining a vector of versions that
+associates to each known source, or has-been source, with its known
+local counter. It enables processes to deliver only up-to-date
 $\alpha$'s that may improve their best known partition (see
@@
 
-\paragraph{Dynamic network.}
 Algorithm~\ref{algo:edges} provides the instructions of \NAME that
@@
 %% \end{inparaenum}
-
-\paragraph{Another trade-off.}
-We propose an implementation that further decreases generated traffic
-and improves on anonymity~\cite{whitaker2002forwarding}.  \NAME makes
-extensive use of paths to enable deleting messages without
-incrementing local counters. Messages carry their respective path and
-processes detect when such messages have been looping when they carry
-their identity (see Lines~\ref{line:notloopingA} and
-\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
-membership is all that matters, we propose to trade vectors of
-identities for Bloom filters~\cite{almeida2007scalable}. Processes
-know with high probability if they already received and forwarded each
-message without knowing the identity of all processes that received
-it.  False positive probability only incurs premature stopping of
-broadcast messages and does not invalidate the delete of specific
-messages.
 

### 2021-04-08 input/figaddA.tex
reworkd figures

@@
 
-  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
+  \draw[fill=white] (-\X, 0) node[color=\PA]{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
   \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
   \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, \Y) node[color=\PD]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
-  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
-  \draw (\X, 5pt) node[above, color=\PC]{$\ADD_c^0$};
+  \draw (-\X, 5pt) node[above, font=\small, color=\PA]{$\ADD_a^0$};
+  \draw (-5pt, \Y) node[left, font=\small, color=\PD]{$\ADD_d^0$};
 

### 2021-04-08 input/figdelA.tex
coloring figures, adding biblio, sketching abstract
reworkd figures

--- 2020-10-09 input/figdelA.tex
@@
 \begin{tikzpicture}[scale=0.87]
+
+  \thickmuskip=0mu
+  \medmuskip=0mu
+  \thinmuskip=0mu
 
@@
 
-  \newcommand\ADD{Add}
-  \newcommand\DEL{Del}
+  \newcommand\ADD{\alpha}
+  \newcommand\DEL{\delta}
 
-  \draw (-\X, 0) -- node[above,font=\tiny]{$\ADD_{a, 1.5}$} (0, 0); %% a - b
-  \draw (0, 0) -- node[above, font=\tiny]{$\ADD_{c, 1}$} (\X, 0); %% b - c
-  \draw (0, 0) -- (0, \Y); %% b - d
-  \draw (\X, 0) -- node[below, font=\tiny, sloped]{$\ADD_{c, 1}$} (0, \Y); %% c - d
+  \draw (-\X + 5pt, 0) --
+  node[above=-0.3em,font=\tiny]{$\DEL_{a} \rightarrow$}
+  (0 - 5pt, 0); %% b - a
+
+  \draw (0 +5pt, 0) --
+  (\X -5pt, 0); %% b - c
+
+  \draw (0, 0 - 5pt) --
+  (0, \Y - 5pt);  %% d - b
+
+  \draw (\X + 3pt, 0 - 5pt) --
+  (0 + 5pt, \Y - 3pt); %% c - d
 
   \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
-  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, 0) node[color=\PD]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, \Y) node[color=\PD]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
-  \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
-  \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};
+  \draw (-\X, 5pt) node[above, font=\small]{$\DEL_a$};
+  \draw (0, 5pt) node[above, font=\small, color=\PD]{$\ADD_d^1$};
+  \draw (\X, 5pt) node[above, font=\small, color=\PD]{$\ADD_d^2$};
+  \draw (-5pt, \Y) node[left, font=\small, color=\PD]{$\ADD_d^0$};
 

### 2021-04-08 input/figadd.tex
figures
on examples

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
-      Process $c$ initiate a partition.
-      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
+    \subfloat[Part A][\label{fig:addA}Both Process~$a$ and Process~$d$
+      become sources.  $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
+      3$.]  {\input{input/figaddA.tex}}
     \hspace{5pt}
@@
       links and carry increasing weights.]{\input{input/figaddB.tex}}
-    \hspace{5pt}
-    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
-      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
-      is higher.]{\input{input/figaddC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
-      incoming messages. The system converged to optimal partitions.]{
-      \input{input/figaddD.tex}}
-    \caption{\label{fig:add}Simple accumulation in messages makes the
-      system converge to optimal partitions with scoped flooding.}
+    \hspace{5pt} \subfloat[Part C][\label{fig:addC}Process~$b$ and
+      Process~$c$ receive, deliver, and forward $\alpha_{d}^{1}$ and
+      $\alpha_d^3$ respectively.]{\input{input/figaddC.tex}}
+    \hspace{5pt} \subfloat[Part D][\label{fig:addD}$a$ and
+      $b$ discarded their received messages. $c$ still improved with $\alpha_d^2$.]
+    {\input{input/figaddD.tex}}
+    \caption{\label{fig:add}Efficient consistent partitioning using
+      \NAMEB. Partition~$P_a$ includes $a$ while Partition~$P_d$
+      includes $b$, $c$, and $d$. Process~$c$ and Process~$d$ never
+      acknowledge the existence of Source~$a$, for Process~$b$ stops
+      the propagation of the latter's notifications.}
   \end{center}

### 2021-04-08 input/proposal.tex
on examples

@@
 \end{inparaenum}
- Figure~\ref{fig:add} illustrates its behavior on a system comprising
- 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and $c$
- concurrently create a partition by S-broadcasting their respective
- \underline{a}dd message: $\alpha_a^0$ and $\alpha_c^0$. They
+Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
+processes $a$, $b$, $c$, and $d$. Process~$a$ and Process~$d$ become
+the sources of their partition. They \NAMEB a notification
+\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
 initialize their own state with the lowest possible bound $0$ (see
@@
 neighbors by accumulating the corresponding edge weight (see
- Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
- receives $\alpha_{c}^{1}$. Since it improves its own partition
- distance, it keeps it and forwards it to its neighbors. Process $b$
- discards $\alpha_{b}^{1.5}$, for it does not improve its partition
- distance. Processes $c$ and $d$ will never hear of Process $a$'s
- partition.  In Figure~\ref{fig:addD}, processes discard last
- transiting messages. The system converged to the consistent
- partitioning. However, since processes operate using local knowledge
- only, generated traffic may be sub-optimal, for processes may
- receive, deliver, and forward messages emanating from a same source
- simply because it did not come from the shortest path yet.
+Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process~$b$
+receives $\alpha_{d}^{1}$. Since it improves its own partition
+distance, it keeps it and forwards it to its neighbors. In
+Figure~\ref{fig:addD}, Process~$b$ discards $\alpha_{a}^{2}$, for it
+does not improve its partition distance. Processes $c$ and $d$ will
+never hear of Source~$a$. Ultimately, processes discard last
+transiting messages. The system reached consistent partitioning.
+
+%% However, since processes operate using local knowledge only, generated
+%% traffic may be sub-optimal, for processes may receive, deliver, and
+%% forward messages emanating from a same source simply because it did
+%% not come from the shortest path yet.
 
@@
 \end{inparaenum}
-\TODO{Figure showing inconsistency.}
-The correctness of the partitioning depends on receipt orders at each
-processes.
+Figure~\ref{fig:problem} highlights such consistency issue with
+dynamic partitions. Both Process~$a$ and Process~$d$ add then delete
+their partition concurrently. Assuming \TODO{FIFO communication
+  links}, Process~$c$ receives, delivers, and forwards $\alpha_d^3$
+followed by $\delta_d$. In the meantime, Process~$b$ receives,
+delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
+both Process~$c$ and Process~$d$ deliver the message about Partition
+$P_a$, for they did not have any known partition at receipt time. On
+the contrary, Process~$b$ delivers $\alpha_d^1$, for it improves its
+distance to a known source. Process~$b$ then blocks Process~$a$'s
+removal notification $\delta_a$. It never reaches Process~$c$ nor
+Process~$d$. Also, Process~$c$ and Process~$d$ do not deliver any
+$\alpha_d$ or $\delta_d$ since they already delivered it. The system
+converges to an unconsistent state where some processes assume they
+belong to a partition while it does not exist any longer.
+
+Dynamic consistent partitioning depends on receipt orders at each
+processes. \TODO{Transition.}
 

### 2021-04-09 input/figproblem.tex
still on examples mostly

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:problemA}Both Process $a$ and
-      Process $c$ initiate then remove a partition.
-      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figproblemA.tex}}
-    \hspace{5pt}
-    \subfloat[Part B][\label{fig:problemB}Process $b$ and Process $d$ receive and deliver
-      messages based on their weights. $a$'s partition propagates to all processes.]
-             {\input{input/figproblemB.tex}}
-    \hspace{5pt}
-    \subfloat[Part C][\label{fig:problemC}Process $c$'s partition reach $b$ and $d$.
-      Its removal shortly follows. Process $b$ does not have any control
-      information about partitions any more.]{\input{input/figproblemC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:problemD}Processes discard remaining messages.
-      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
-      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
-      partition.]{\input{input/figproblemD.tex}}
+    \subfloat[Part A][\label{fig:problemA}Both Process~$a$ and
+      Process~$d$ add then delete their partition. For the recall,
+      $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
+      3$.]{\input{input/figproblemA.tex}}
+    \hspace{5pt} \subfloat[Part B][\label{fig:problemB}Process~$b$
+      delivers and forwards the $\alpha$ message about $P_a$ while
+      Process~$c$ delivers and forwards both $\alpha$ and $\delta$
+      messages about $P_d$.]  {\input{input/figproblemB.tex}}
+    \hspace{5pt} \subfloat[Part C][\label{fig:problemC}Process~$b$
+      already blocks the propagation of $\delta_a$ despite it
+      propagated $\alpha_a$ before. Process~$c$ and Process~$d$ do not
+      deliver $\alpha_d$, for they already deleted
+      it before.]{\input{input/figproblemC.tex}}
+    \hspace{5pt} \subfloat[Part D][\label{fig:problemD}Processes
+      discard remaining messages. Since Process~$b$ cannot deliver
+      $\delta_a$, $c$ and $d$ remain in the deleted partition
+      $P_a$.]{\input{input/figproblemD.tex}}
   \end{center}
-  \caption{\label{fig:problem}Partition removals cannot rely only on
-    current partition, for it may lead to either inconsistent
-    partitioning, or every process receiving every broadcast.}
+  \caption{\label{fig:problem}Naive propagation of $\alpha$ and
+    $\delta$ messages is insufficient to guarantee consistent partitioning.}
 \end{figure*}

### 2021-04-09 input/proposal.tex
still on examples mostly

@@
 Figure~\ref{fig:problem} highlights such consistency issue with
-dynamic partitions. Both Process~$a$ and Process~$d$ add then delete
-their partition concurrently. Assuming \TODO{FIFO communication
-  links}, Process~$c$ receives, delivers, and forwards $\alpha_d^3$
-followed by $\delta_d$. In the meantime, Process~$b$ receives,
-delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
-both Process~$c$ and Process~$d$ deliver the message about Partition
-$P_a$, for they did not have any known partition at receipt time. On
-the contrary, Process~$b$ delivers $\alpha_d^1$, for it improves its
-distance to a known source. Process~$b$ then blocks Process~$a$'s
-removal notification $\delta_a$. It never reaches Process~$c$ nor
-Process~$d$. Also, Process~$c$ and Process~$d$ do not deliver any
-$\alpha_d$ or $\delta_d$ since they already delivered it. The system
-converges to an unconsistent state where some processes assume they
-belong to a partition while it does not exist any longer.
+dynamic partitions, even in contexts where processes have FIFO links,
+\ie where processes receive the messages in the order of their
+sending. Both Process~$a$ and Process~$d$ add then delete their
+partition concurrently. Process~$c$ receives, delivers, and forwards
+$\alpha_d^3$ followed by $\delta_d$. In the meantime, Process~$b$
+receives, delivers, and forwards $\alpha_a^2$. In
+Figure~\ref{fig:problemC}, both Process~$c$ and Process~$d$ deliver
+the message about Partition $P_a$, for they did not have any known
+partition at receipt time. On the contrary, Process~$b$ delivers
+$\alpha_d^1$, for it improves its distance to a known
+source. Process~$b$ then blocks Process~$a$'s removal notification
+$\delta_a$. It never reaches Process~$c$ nor Process~$d$. Also,
+Process~$c$ and Process~$d$ do not deliver any $\alpha_d$ or
+$\delta_d$ since they already delivered it. The system converges to an
+unconsistent state where some processes assume they belong to a
+partition while it does not exist anymore. Naive propagation of
+$\alpha$ and $\delta$ messages is insufficient to guarantee consistent
+partitioning when each process can add or delete its partition at any
+time.
 
-Dynamic consistent partitioning depends on receipt orders at each
-processes. \TODO{Transition.}
+To identify and solve the issue with dynamic consistent partitioning
+where protocols enable processes to \texttt{Add} and \texttt{Del} at
+any time, we need to further constrain the delivery order at each
+process.
 

### 2021-04-09 input/proposal.tex
wip

@@
 
-To identify and solve the issue with dynamic consistent partitioning
-where protocols enable processes to \texttt{Add} and \texttt{Del} at
-any time, we need to further constrain the delivery order at each
-process.
+One could solve this issue by always propagating the $\delta$ messages
+corresponding to the $\alpha$ messages it propagated before. In
+Figure~\ref{fig:problem}, it means that as soon as Process~$b$
+forwards $\alpha_a^2$, it assumes that its neighbors Process~$c$ and
+Process~$d$ may need the notification of removal $\delta_a$ if it
+exists. However, such solution also implies that processes generate
+traffic not only related to their current partition, but also related
+to partitions they belong to in the past. Instead, we propose to use
+the delivery order at each process to detect possible inconsistencies
+and solve them. Together, processes eventually remove all stale
+control information (transiting messages and local states) of the
+system leaving room for propagation of messages about up-to-date
+partitions.
+
+%% To identify and solve the issue with dynamic consistent partitioning
+%% where protocols enable processes to \texttt{Add} and \texttt{Del} at
+%% any time, we need to further constrain the delivery order at each
+%% process.
 
 \input{input/figproblem.tex}
+
+\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
+  Consistent partitioning where each process can \texttt{Add} and
+  \texttt{Del} its partition at any time requires 
+  \begin{inparaenum}[(i)]
+  \item eventual purging of stale notifications, and
+  \item eventual delivery of bests partitions.
+  \end{inparaenum}
+\end{corollary}
+
+\begin{proof}
+  \TODO{Quite obvious.}
+\end{proof}
 
@@
 may be inconsistent without knowing it.
-
-\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
-  Eventual consistent partitioning in presence of dynamic sources
-  requires
-  \begin{inparaenum}[(i)]
-  \item eventual purging of stale notifications, and
-  \item eventual delivery of bests partitions.
-  \end{inparaenum}
-\end{corollary}
-
-\begin{proof}
-  \TODO{Quite obvious.}
-\end{proof}
 

### 2021-04-09 input/proposal.tex
meow

@@
 broadcast} where messages reach only interested processes,
-significantly reducing generated traffic.
+significantly reducing generated traffic. \TODO{Epidemic propagation
+  and forwarding are well-aligned with scoped broadcast.}
+
+%% Epidemic
+%% dissemination~\cite{birman1999bimodal} constitutes an efficient
+%% communication pattern to perform such operation. \TODO{More about
+%%   \emph{forwarding}.}
 
@@
 In this section, we propose to dynamically adapt the scopes of \NAMEB
-using \NAMEB itself for the sake of efficiency. At any time, a process
-decides whether or not it becomes the center (or \emph{source}) of a
-scope (or \emph{partition}). Processes must eventually rally the
-partition corresponding to their closest source despite concurrent
-operations, and dynamic changes in the network.
+using \NAMEB itself for the sake of efficiency. \TODO{States of
+  processes change, predicates change over time.} At any time, a
+process decides whether or not it becomes the center (or
+\emph{source}) of a scope (or \emph{partition}). Processes must
+eventually rally the partition corresponding to their closest source
+despite concurrent operations, and dynamic changes in the network.
 
@@
 changes. \NAME's overhead actually depends on its operations and
-current partitions in the system. In other terms,
-\begin{inparaenum}[(i)]
-\item when the system becomes quiescent, processes eventually converge to
-their respective partition and do not require further communication
-afterward; and
-\item processes do not pay the price of past partitioning.
-\end{inparaenum}
+current partitions in the system. When the system becomes quiescent,
+processes eventually converge to their respective partition and do not
+require further communication afterward.
 
@@
 than any other source. Such distance (or \emph{weight}) is
-application-dependant. For instance, weights could be latency in live
-streaming applications, or differences in profiles for recommendation
-systems.
+application-dependant: in the context of maintaining distributed
+indexes, weights are latency.
+
+%For instance, weights could be latency in live
+% streaming applications, or differences in profiles for recommendation
+%systems.
 
@@
 together, a process becoming a source must notify every process that
-is closer to it than any other source. Epidemic
-dissemination~\cite{birman1999bimodal} constitutes an efficient
-communication pattern to perform such operation. \TODO{More about
-  \emph{forwarding}.}
+is closer to it than any other source, using \NAMEB for the sake of
+efficiency.
 
@@
 
-%% However, since processes operate using local knowledge only, generated
-%% traffic may be sub-optimal, for processes may receive, deliver, and
-%% forward messages emanating from a same source simply because it did
-%% not come from the shortest path yet.
-
-%% Transitive relationships ensure that each
-%% process gets its closest source while accumulation of weights ensures
-%% that messages propagation terminates.
-
-%% Interestingly, while the receipt order of messages does not impact on
-%% local control information ($r_b(\alpha_a^{1.5}) \cdot
-%% r_b(\alpha_a^{1}) \Leftrightarrow r_b(\alpha_a^{1}) \cdot
-%% r_b(\alpha_a^{1.5}) \implies \TODO{d_b(\alpha_a^{1})}$), it impacts on
-%% control information broadcast in the network ($r_b(\alpha_a^{1.5})
-%% \cdot r_b(\alpha_a^{1}) \implies b_b(\alpha_{b}^{1.5}) \cdot
-%% b_b(\alpha_{b}^{1})$ while $r_b(\alpha_a^{1}) \cdot
-%% r_b(\alpha_a^{1.5}) \implies b_b(\alpha_a^{1})$).
-
 While only adding logical partitions to the distributed system is
-straightforward, removing them introduces additional complexity:
-messages of old partitions may stop the notification of best sources,
-for former weights are better than the newly received one.
+straightforward, removing them introduces additional complexity.
 
@@
 must eventually choose another partition to belong to. In
-Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_c$
+Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
 that respectively include $\{a\}$, and $\{b, c, d\}$. In
@@
 best for Process $a$. Eventually, every processes belong to the same
-partition $P_c$.
+partition $P_d$.
 
@@
   \begin{inparaenum}[(i)]
-  \item eventual purging of stale notifications, and
+  \item eventual purging of stale notifications, then
   \item eventual delivery of bests partitions.

### 2021-04-11 input/abstract.tex
reworkd abstract and scoped broadcast

--- 2021-02-01 input/abstract.tex
@@
 \begin{abstract}
+  %% Context and problem
+  Edge infrastructures constitute an alternative to Cloud Computing
+  that aims at improving on latency and traffic by providing computing
+  and storage capabilities closer to data producers and consumers.
+  %% Edge infrastructures have been proposed as an alternative to Cloud
+  %% Computing to provide computing and storage capabilities closer to
+  %% the locations where data is generated/consumed, with the objectives
+  %% of reducing the latency and the volume of data passing through the
+  %% network.
+  A few systems, such as content delivery networks, replicate and
+  distribute produced data in these infrastructures.
+  % A few systems have been proposed to store data in those
+  % infrastructures.
+  Locating the closest replica of a specific content requires to
+  maintain an up-to-date index of all live replicas along with their
+  respective locations. 
+  %
+  Unfortunately, relying on a centralized service would bring
+  scalability issues, single point of failure, as well as additional
+  middleman latency where locating replicas may effectively take more
+  time than actually downloading contents. Instead, data consumer
+  \processes must maintain an up-to-date index
+  themselves. Unfortunately, maintaining an index of all live replicas
+  at every \process would prove overly costly in terms of memory and
+  generated traffic, especially in large scale dynamic systems where
+  \processes create and destroy replicas at any time.
+  % while flooding approaches will not enable the maintenance of such
+  % an index for each node in large systems, relying on a dedicated
+  % service contradicts with the properties of Edge infrastructures in
+  % terms of locality and robustness
 
-  Fog infrastructures allows content providers to better distribute
-  data over autonomous systems, hence improving on quality of user
-  experience by reducing latency. However, locating the closest data
-  sources can prove challenging in dynamic networks with dynamic
-  sources. Locating sources may effectively take more time than
-  actually downloading contents. \TODO{Related work ?} In this paper,
-  we introduce \NAME, a reactive protocol for dynamic logical
-  partitioning in dynamic networks. \TODO{source automatically create
-    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
-    flooding}). \TODO{costs of operations.} When the system becomes
-  quiescent, every process eventually converges to its closest
-  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
-    testbed?}
-
+%%% Our proposal
+  \noindent In this paper, we introduce \NAME, an efficient and
+  decentralized partitioning protocol for dynamic distributed systems:
+  When a \node hosts a replica, it notifies all and only \nodes (new
+  members of its partition) that are closer from it than any other
+  replica; When a \node destroys a replica, it notifies members of its
+  partition to switch to another closer partition. \NAME guarantees
+  that eventually, every \process knows its best partition, hence its
+  closest replica, despite concurrent operations and receipt orders.
+  Our complexity analysis supported by simulations shows that \NAME
+  scales well in terms of generated traffic and convergence time, for
+  the effect of operations remains lock down to its logical
+  partition. While \NAME tackles our content indexing problem, it can
+  be used as a building block to design new advanced services such as
+  decentralized recommendation systems.
 \end{abstract}

### 2021-04-11 input/proposal.tex
reworkd abstract and scoped broadcast

@@
 message around its broadcaster within an application-dependant scope.
-For instance, a process from Paris could scoped broadcast messages to
-all processes in Paris; and processes from other cities would never
-deliver such messages. Scoped broadcast allows its implementations to
-reduce generated traffic compared to uniform reliable
-broadcast~\cite{hadzilacos1994modular, raynal2013distributed}, for
-message propagation can stop as soon as messages reach the borders of
-the scope.  This section introduces model and notations to provide a
-general definition of scoped broadcast in distributed
-systems. \TODO{to help understand adaptive scoped broadcast :).}
-\TODO{Better transition to the rest of this section.}
+For instance, a \process from Paris could scoped broadcast messages to
+all \processes in Paris; and \processes from other cities would never
+deliver such messages.
+%% Dedicated scoped broadcast implementations
+%% outperform uniform reliable broadcast
+%% implementations~\cite{hadzilacos1994modular, raynal2013distributed}
+%% since the former targets a connected \emph{subset} of the whole
+%% network while the latter targets \emph{all} \processes of the
+%% distributed system.
+Scoped broadcast only targets a connected \emph{subset} of \processes
+in the whole distributed system.
+%
+Distributed systems such as Edge infrastructures comprise
+heterogeneous machines interconnected by communication
+links. \Processes may crash but are not byzantine.
 
-Distributed systems such as Edge infrastructures comprise
-heterogeneous machines interconnected by communication links. We do
-not consider byzantine processes.
+% \TODO{dynamic graph: superscript with $t$?}
 
@@
   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
-  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from Process
-  $i$ to Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
+  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from \Process
+  $i$ to \Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
     k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
@@
 
-Processes can send messages to their neighboring processes. Processes
-can reliably broadcast messages by forwarding delivered
-messages~\cite{birman1999bimodal, hadzilacos1994modular,
+\Processes can reliably communicate through asynchronous message
+passing to other known \processes called neighbors. Using epidemic
+propagation (or gossiping), \processes can reliably broadcast messages
+by forwarding delivered messages from neighbors to
+neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
   nedelec2018causal, raynal2013distributed}. However, uniform reliable
-broadcast states that \emph{all} correct processes must deliver
+broadcast states that \emph{all} correct \processes must deliver all
 broadcast messages. This proves costly in large scale systems
-comprising thousands of processes. Instead, we define \emph{scoped
-broadcast} where messages reach only interested processes,
-significantly reducing generated traffic. \TODO{Epidemic propagation
-  and forwarding are well-aligned with scoped broadcast.}
-
-%% Epidemic
-%% dissemination~\cite{birman1999bimodal} constitutes an efficient
-%% communication pattern to perform such operation. \TODO{More about
-%%   \emph{forwarding}.}
+comprising thousands of \processes. Instead, we define \emph{scoped
+broadcast} where messages reach only an application-dependant subset
+of connected \processes, thus significantly reducing the generated
+traffic of broadcast.
 
 \begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
-  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
-  \underline{m}essage $m$, every correct Process $y$ within a scope
+  When \Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
+  \underline{m}essage $m$, every correct \process $y$ within a scope
   \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
   $d_y(m)$. The scope depends on the \underline{s}tate $\sigma$ of
-  each process, the \underline{m}etadata $\mu$ piggybacked by each
-  message, and a \underline{p}redicate $\phi$ verified from process to
-  process: $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
-  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$.
+  each \process, the \underline{m}etadata $\mu$ piggybacked by each
+  message, and a \underline{p}redicate $\phi$ verified from \process to
+  \process: {\small{$b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
+  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$}}.
 \end{definition}
 
-This definition highlights the transitive relevance of messages and
-encompasses more specific definitions of related
-work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}. For
-instance, a process from Paris could scoped broadcast messages to all
-processes in Paris. This requires processes to know the city they are
-in. In another instance, a process from Paris could scoped broadcast
-messages to all processes in Paris plus neighboring cities. This
-requires processes to overload forwarded messages the first time they
-reach another city. The predicate checks if messages already reached
-two distinct cities before delivery. Similarly to uniform reliable
-broadcast, scoped broadcast implementations expose different
-trade-offs on space, time, and communication.
+This definition encompasses more specific definitions of related
+work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  This
+definition also highlights that epidemic propagation and scoped
+broadcast have well-aligned preoccupations: It highlights the
+transitive relevance of messages, thus \processes can stop forwarding
+messages as soon as the corresponding predicate becomes unverified.
+For instance, a \process from Paris could scoped broadcast messages to
+all \processes in Paris. This requires \processes to store and
+maintain their city location in their local state. \Processes stop
+delivering and forwarding their received messages when they come from
+a different city.  In another instance, a \process from Paris could
+scoped broadcast messages to all \processes in Paris plus neighboring
+cities. This requires \processes to overload forwarded messages the
+first time they reach another city. The predicate checks if messages
+already reached two distinct cities before delivery. Similarly to
+uniform reliable broadcast, scoped broadcast implementations expose
+different trade-offs on space, time, and communication.
 
 Next Section introduces an adaptive scoped broadcast where the state
-of each process is dynamic and changes depending on all distinct
+of each \process is dynamic and changes depending on all distinct
 scopes that exist in the system.
@@
 using \NAMEB itself for the sake of efficiency. \TODO{States of
-  processes change, predicates change over time.} At any time, a
-process decides whether or not it becomes the center (or
-\emph{source}) of a scope (or \emph{partition}). Processes must
+  \processes change, predicates change over time.} At any time, a
+\process decides whether or not it becomes the center (or
+\emph{source}) of a scope (or \emph{partition}). \Processes must
 eventually rally the partition corresponding to their closest source
@@
 enables adaptive scoped broadcast in dynamic distributed
-systems. \NAME's operation guarantees that processes eventually reach
+systems. \NAME's operation guarantees that \processes eventually reach
 consistent partitioning by efficiently propagating their state
@@
 current partitions in the system. When the system becomes quiescent,
-processes eventually converge to their respective partition and do not
+\processes eventually converge to their respective partition and do not
 require further communication afterward.
@@
 \noindent This section starts by introducing consistent partitioning
-and its implementation when a process can only become a new source to
+and its implementation when a \process can only become a new source to
 create a new partition, i.e., it cannot revoke its self-appointed
@@
 
-At any time, a process can decide to become a source, hence creating a
+At any time, a \process can decide to become a source, hence creating a
 new partition in the system by executing an \texttt{Add}
 operation. This partition includes at least its source plus
-neighboring processes that estimate they are closer to this source
+neighboring \processes that estimate they are closer to this source
 than any other source. Such distance (or \emph{weight}) is
@@
   Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
-  the \underline{p}artition including at least Process $s$, each
-  process belongs to at most one partition $\forall p,q \in V, \forall
+  the \underline{p}artition including at least \Process $s$, each
+  \process belongs to at most one partition $\forall p,q \in V, \forall
   s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
   \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
-  processes that belong to this partition $\forall q \in \pi_{ps}: q
+  \processes that belong to this partition $\forall q \in \pi_{ps}: q
   \in P_s$.
@@
 Definition~\ref{def:scoped} and Definition~\ref{def:partitioning}
-share the transitive relevance of process states. However, we further
+share the transitive relevance of \process states. However, we further
 constrain the partitioning in order to guarantee the existence of
-exactly one consistent partitioning that processes eventually converge
+exactly one consistent partitioning that \processes eventually converge
 to.
@@
   weight, the only consistent partitioning $\mathcal{P}$ is a set of
-  partitions $P_{s\in S}$ such that each process belongs to a logical
+  partitions $P_{s\in S}$ such that each \process belongs to a logical
   partition comprising its closest source: $\forall p \in P_{s_1},
@@
 
-Unfortunately, processes do not share a common global knowledge of the
-network state. For processes to reach consistent partitioning
-together, a process becoming a source must notify every process that
+Unfortunately, \processes do not share a common global knowledge of the
+network state. For \processes to reach consistent partitioning
+together, a \process becoming a source must notify every \process that
 is closer to it than any other source, using \NAMEB for the sake of
@@
 \begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \iff CP$]
-  Assuming reliable communication links where a correct process $q$
+  Assuming reliable communication links where a correct \process $q$
   eventually receives the message $m$ \underline{s}ent to it by a
-  process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a static system ($G^t =
-  G^{t+1}$); assuming local knowledge only, processes eventually reach
-  consistent partitioning if and only if each process eventually
+  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a static system ($G^t =
+  G^{t+1}$); assuming local knowledge only, \processes eventually reach
+  consistent partitioning if and only if each \process eventually
   forwards its best known partition.
@@
 \TODO{If forwarding defined as send to all neighbors, then it also
-  works in dynamic systems where processes join and edges are added,
-  for when a new neighbor appears, the processes must forward their
+  works in dynamic systems where \processes join and edges are added,
+  for when a new neighbor appears, the \processes must forward their
   best.}
@@
   \begin{asparadesc}
-  \item [$BEF \implies CP$:] When a process $s_1$ becomes a source, it
+  \item [$BEF \implies CP$:] When a \process $s_1$ becomes a source, it
     belongs to its own partition, for there exists no better partition
@@
       p}|$. It broadcasts such message to its neighbors. Since
-    communication channels are reliable, neighboring processes
+    communication channels are reliable, neighboring \processes
     eventually receive such notification. In particular, whatever the
-    order of received messages, every process $p_1$ -- such that there
+    order of received messages, every \process $p_1$ -- such that there
     exists no better partition $s_2$ than the received one -- delivers
@@
       s_2}|$. The notification emanating from $s_1$ transitively
-    reaches all such processes through shortest paths. Since there
-    exists only one best value per process that can never be
-    retracted, processes eventually reach consistent
+    reaches all such \processes through shortest paths. Since there
+    exists only one best value per \process that can never be
+    retracted, \processes eventually reach consistent
     partitioning. \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
   \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
-    process $p$ that does not forward, then another process $q$ may
+    \process $p$ that does not forward, then another \process $q$ may
     never gets its best because it needs the weight $W_{pq}$.}
@@
   \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding a partition by Process $p$.}
+  \caption{\label{algo:add}Adding a partition by \Process $p$.}
 \end{algorithm}
@@
 \item weights are scalar values,
-\item processes only add new partitions to the system,
-\item and processes never join nor crash nor leave the system.
+\item \processes only add new partitions to the system,
+\item and \processes never join nor crash nor leave the system.
 \end{inparaenum}
 Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
-processes $a$, $b$, $c$, and $d$. Process~$a$ and Process~$d$ become
+\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become
 the sources of their partition. They \NAMEB a notification
@@
 neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process~$b$
+Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
 receives $\alpha_{d}^{1}$. Since it improves its own partition
 distance, it keeps it and forwards it to its neighbors. In
-Figure~\ref{fig:addD}, Process~$b$ discards $\alpha_{a}^{2}$, for it
-does not improve its partition distance. Processes $c$ and $d$ will
-never hear of Source~$a$. Ultimately, processes discard last
+Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
+does not improve its partition distance. \Processes $c$ and $d$ will
+never hear of Source~$a$. Ultimately, \processes discard last
 transiting messages. The system reached consistent partitioning.
@@
 
-At any time, a process can become a source, hence adding a new
+At any time, a \process can become a source, hence adding a new
 partition to the system. This partition eventually includes all
-processes that are closer from this new source than any other
-else. Processes naturally converge towards their respective best
+\processes that are closer from this new source than any other
+else. \Processes naturally converge towards their respective best
 partition by only piggybacking a monotonically increasing distance in
@@
 source, hence deleting its partition from the system, by executing a
-\texttt{Del} operation. All processes that belong to this partition
+\texttt{Del} operation. All \processes that belong to this partition
 must eventually choose another partition to belong to. In
@@
 that respectively include $\{a\}$, and $\{b, c, d\}$. In
-Figure~\ref{fig:delA}, Process $a$ deletes its partition. It notifies
-all neighboring processes -- here only Process $b$ -- that may belong
-to its partition using \NAMEB. Upon receipt, Process $b$ discards the
+Figure~\ref{fig:delA}, \Process $a$ deletes its partition. It notifies
+all neighboring \processes -- here only \Process $b$ -- that may belong
+to its partition using \NAMEB. Upon receipt, \Process $b$ discards the
 message $\delta_a$, for the latter does not target the former's
-partition. Yet, Process $b$ sends its own partition that may be the
-best for Process $a$. Eventually, every processes belong to the same
+partition. Yet, \Process $b$ sends its own partition that may be the
+best for \Process $a$. Eventually, every \processes belong to the same
 partition $P_d$.
@@
 Figure~\ref{fig:problem} highlights such consistency issue with
-dynamic partitions, even in contexts where processes have FIFO links,
-\ie where processes receive the messages in the order of their
-sending. Both Process~$a$ and Process~$d$ add then delete their
-partition concurrently. Process~$c$ receives, delivers, and forwards
-$\alpha_d^3$ followed by $\delta_d$. In the meantime, Process~$b$
+dynamic partitions, even in contexts where \processes have FIFO links,
+\ie where \processes receive the messages in the order of their
+sending. Both \Process~$a$ and \Process~$d$ add then delete their
+partition concurrently. \Process~$c$ receives, delivers, and forwards
+$\alpha_d^3$ followed by $\delta_d$. In the meantime, \Process~$b$
 receives, delivers, and forwards $\alpha_a^2$. In
-Figure~\ref{fig:problemC}, both Process~$c$ and Process~$d$ deliver
+Figure~\ref{fig:problemC}, both \Process~$c$ and \Process~$d$ deliver
 the message about Partition $P_a$, for they did not have any known
-partition at receipt time. On the contrary, Process~$b$ delivers
+partition at receipt time. On the contrary, \Process~$b$ delivers
 $\alpha_d^1$, for it improves its distance to a known
-source. Process~$b$ then blocks Process~$a$'s removal notification
-$\delta_a$. It never reaches Process~$c$ nor Process~$d$. Also,
-Process~$c$ and Process~$d$ do not deliver any $\alpha_d$ or
+source. \Process~$b$ then blocks \Process~$a$'s removal notification
+$\delta_a$. It never reaches \Process~$c$ nor \Process~$d$. Also,
+\Process~$c$ and \Process~$d$ do not deliver any $\alpha_d$ or
 $\delta_d$ since they already delivered it. The system converges to an
-unconsistent state where some processes assume they belong to a
+unconsistent state where some \processes assume they belong to a
 partition while it does not exist anymore. Naive propagation of
 $\alpha$ and $\delta$ messages is insufficient to guarantee consistent
-partitioning when each process can add or delete its partition at any
+partitioning when each \process can add or delete its partition at any
 time.
@@
 corresponding to the $\alpha$ messages it propagated before. In
-Figure~\ref{fig:problem}, it means that as soon as Process~$b$
-forwards $\alpha_a^2$, it assumes that its neighbors Process~$c$ and
-Process~$d$ may need the notification of removal $\delta_a$ if it
-exists. However, such solution also implies that processes generate
+Figure~\ref{fig:problem}, it means that as soon as \Process~$b$
+forwards $\alpha_a^2$, it assumes that its neighbors \Process~$c$ and
+\Process~$d$ may need the notification of removal $\delta_a$ if it
+exists. However, such solution also implies that \processes generate
 traffic not only related to their current partition, but also related
 to partitions they belong to in the past. Instead, we propose to use
-the delivery order at each process to detect possible inconsistencies
-and solve them. Together, processes eventually remove all stale
+the delivery order at each \process to detect possible inconsistencies
+and solve them. Together, \processes eventually remove all stale
 control information (transiting messages and local states) of the
@@
 %% To identify and solve the issue with dynamic consistent partitioning
-%% where protocols enable processes to \texttt{Add} and \texttt{Del} at
+%% where protocols enable \processes to \texttt{Add} and \texttt{Del} at
 %% any time, we need to further constrain the delivery order at each
-%% process.
+%% \process.
 
@@
 \begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
-  Consistent partitioning where each process can \texttt{Add} and
+  Consistent partitioning where each \process can \texttt{Add} and
   \texttt{Del} its partition at any time requires
@@
 We define a last win order to forbid the delivery of stale information
-emanating from a same process. In other terms, the \emph{best}
-notification message is always the most recent known of each process.
+emanating from a same \process. In other terms, the \emph{best}
+notification message is always the most recent known of each \process.
 
 \begin{definition}[Last win order]
-  When a process $p$ broadcasts two messages $b_p(m) \rightarrow
-  b_p(m')$, no process $q$ can deliver $m$ if it has delivered $m'$:
+  When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
+  b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
   $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$.
@@
 orderings. In Figure~\ref{fig:proofA}, the shortest path from any
-source to Process $c$ is $[a, b, c]$. However, Process $b$ still holds
+source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
 a stale $\alpha_d^{0.5}$ without knowing. When it receives
-$\alpha_a^1$, it discards it, for it assumes that downstream processes
+$\alpha_a^1$, it discards it, for it assumes that downstream \processes
 are more interested in $\alpha_d^{0.5}$. To reach consistent
-partitioning, Process $b$ first needs to purge its current partition
+partitioning, \Process $b$ first needs to purge its current partition
 to later accept that of its current actual shortest path:
@@
 \noindent Figure~\ref{fig:proofB} shows that removing stale control
-information is even more complex. The removal must reach all processes
+information is even more complex. The removal must reach all \processes
 of the previous shortest path going from $d$ to $b''$. Label I' shows
-the most obvious issue where Process $e$ changed partition for a
+the most obvious issue where \Process $e$ changed partition for a
 better but stale $\alpha_f$. Since it can remember its previous
 deliveries, it could still forward $\delta_d$ for the sake of
-consistency. However, this would lead to every process forwarding
+consistency. However, this would lead to every \process forwarding
 every $\delta$ they ever delivered. Such protocol's overhead would
@@
 the issue when the blocking partition is already known to be stale at
-Process $b'$. Process $b''$ eventually receives $\alpha_f$ from
+\Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
 $e$. However, it cannot deliver it, for it would break last win order.
-Process $b'$ may be in an inconsistent state. Label IV shows the
-corollary issue: Process $b''$ delivered a message from a process that
+\Process $b'$ may be in an inconsistent state. Label IV shows the
+corollary issue: \Process $b''$ delivered a message from a \process that
 may be inconsistent without knowing it.
@@
   \input{input/algoadddelundo.tex}
-  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
+  \caption{\label{algo:adddelundo}Dynamic partitioning by \Process $p$.}
 \end{algorithm}
@@
 We extend Algorithm~\ref{algo:add} to enable each source to revoke its
-self-appointed status of source and become a simple process again.
+self-appointed status of source and become a simple \process again.
 Algorithm~\ref{algo:adddelundo} provides the instructions that
@@
 
-To constrain the order of delivery at each process, each process
+To constrain the order of delivery at each \process, each \process
 implements last win order by maintaining a vector of versions that
 associates to each known source, or has-been source, with its known
-local counter. It enables processes to deliver only up-to-date
+local counter. It enables \processes to deliver only up-to-date
 $\alpha$'s that may improve their best known partition (see
@@
 and I'. Messages and comparisons include the local counter of the
-source. When a process receives a better up-to-date partition, it
-delivers and forwards it. When a process receives a delete
+source. When a \process receives a better up-to-date partition, it
+delivers and forwards it. When a \process receives a delete
 notification about its partition, it delivers and forwards it. It is
@@
 travel in the propagation graph of their partition using all
-communication links, allowing processes to change partition as soon as
+communication links, allowing \processes to change partition as soon as
 possible.
 
-Vectors of versions also allow each process to detect possible last
+Vectors of versions also allow each \process to detect possible last
 win order violations. Upon possible inconsistency, the detecting
-process must remove all $\alpha$ messages originating from it, as
+\process must remove all $\alpha$ messages originating from it, as
 labeled by IV in Figure~\ref{fig:proofB}. Contrarily to delete
@@
 path. $\delta$'s propagate in the propagation tree rooted at the
-detecting process. Local states of processes remain unchanged, but
+detecting \process. Local states of \processes remain unchanged, but
 paths in messages monotonically grow. In turns, $\alpha$ and $\delta$
-cannot follow each other in an infinite loop, for a process knows when
+cannot follow each other in an infinite loop, for a \process knows when
 it already received a forwarded a message (see
@@
 partitions when they remove stale control information, they also
-trigger a competition when reaching such bordering processes (see
+trigger a competition when reaching such bordering \processes (see
 Line~\ref{line:compete}). This simply consists in sending the current
-partition through the communication link from which the process
-received the $\delta$. Upon receipt of this answer, processes act
+partition through the communication link from which the \process
+received the $\delta$. Upon receipt of this answer, \processes act
 normally by propagating their changes when they improve. These adds
@@
   \input{input/algoedges.tex}
-  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
+  \caption{\label{algo:edges}Dynamic partitioning by \Process $p$ in dynamic networks.}
 \end{algorithm}
@@
 enable dynamic consistent partitioning in dynamic networks where
-processes can join or leave the system without
+\processes can join or leave the system without
 notification. \TODO{More.}
@@
 %% Adding new communication links to the network may create shortcuts
-%% between processes. Both processes must send their current best
-%% partition to each other. Upon receipt, they act normally: if a process
+%% between \processes. Both \processes must send their current best
+%% partition to each other. Upon receipt, they act normally: if a \process
 %% finds out that the received partition is closer than its current one,
@@
 %% \noindent Joining the network is equivalent to add as many
-%% communication links as necessary between the joining process and its
+%% communication links as necessary between the joining \process and its
 %% new neighbors.
 
-%% When removing a communication link between two processes does not
-%% break any active path, because neither distances of processes depend
+%% When removing a communication link between two \processes does not
+%% break any active path, because neither distances of \processes depend
 %% on the other, then nothing needs to be done. \NAME has no overhead.
-%% Unfortunately, when a process' distance depends on the other process,
+%% Unfortunately, when a \process' distance depends on the other \process,
 %% the protocol becomes much more complex. Indeed, this requires to
-%% \TODO{undo} all add messages originated from this process. A message
+%% \TODO{undo} all add messages originated from this \process. A message
 %% must convey the fact that
 %% \begin{inparaenum}[(i)]
-%% \item an edge at a particular process has been removed, and
-%% \item the distance that has been delivered by a process comes from
-%%   this particular process.
+%% \item an edge at a particular \process has been removed, and
+%% \item the distance that has been delivered by a \process comes from
+%%   this particular \process.
 %% \end{inparaenum}
@@
 %%     partitioning. \TODO{More about relative ordering of links at each
-%%       process}}
+%%       \process}}
 %% \end{figure}
@@
 %%   \input{input/algoaaaa.tex}
-%%   \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
+%%   \caption{\label{algo:aaaa}\NAMEB running at \Process $p$ for dynamic
 %%     partitioning in inter-autonomous systems.}
@@
 %% Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
-%% where each process ranks its communication links, and each process
+%% where each \process ranks its communication links, and each \process
 %% forwards messages to its neighbors starting from the rank of the link
 %% that triggered the receipt, to its highest rank neighbors. In this
-%% example, Process $e$ adds a partition. It forwards the generated
+%% example, \Process $e$ adds a partition. It forwards the generated
 %% message to all its neighbors as if it received it from its lowest rank
-%% links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
-%% it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
+%% links. When \Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
+%% it forwards it to rank-$0$ links and rank-$1$ links.  \Process $b$
 %% stops the propagation, for all its links have lower ranks than the one
 %% from which it received the message $\alpha_e^2$. Ultimately, the
-%% partition includes Process $e$, Process $a$, and Process $b$. Process
-%% $c$ and Process $d$ remain unaware of the new \TODO{object}.
+%% partition includes \Process $e$, \Process $a$, and \Process $b$. \Process
+%% $c$ and \Process $d$ remain unaware of the new \TODO{object}.
 
@@
 %%   slightly more memory, but traffic wise? slower ?}  \TODO{In the
-%%   example, not only Process $b$ keeps $e_1$ as its best partition, but
+%%   example, not only \Process $b$ keeps $e_1$ as its best partition, but
 %%   it keeps it for links of rank 0, and links of rank 1.}  When there
-%% are no ranking in links, processes solely rely on
+%% are no ranking in links, \processes solely rely on
 %% Algorithm~\ref{algo:adddelundo} for optimal partitioning.
@@
 \paragraph{Space.}
-Each process needs to maintain a vector of versions the size of which
+Each \process needs to maintain a vector of versions the size of which
 depends on the number of sources. In the worst case, the size of this
 vector increases linearly with the number of distinct sources that
-ever existed in the system. For the sake of last win order, processes
+ever existed in the system. For the sake of last win order, \processes
 can never purge this vector from any entry. \TODO{Even when the
-  process leaves the system.} Fortunately, scoped broadcast limits
-message propagation to interested processes. A process at a side of
+  \process leaves the system.} Fortunately, scoped broadcast limits
+message propagation to interested \processes. A \process at a side of
 the system may never hear of a source at the other side of the
@@
 
-\noindent Each process must also maintain the partition it belongs to,
+\noindent Each \process must also maintain the partition it belongs to,
 along with its control information. Among other, it must maintain a
@@
 partition. In the worst case, this path includes the identity of every
-process of the system that currently belong to the system. Eventually,
+\process of the system that currently belong to the system. Eventually,
 the size of this path increases linearly with the diameter of the
@@
 In terms of processing time, whatever the operation, it increases
-linearly with the number of neighbors of the process. It scales well,
+linearly with the number of neighbors of the \process. It scales well,
 for the number of neighbors is commonly order of magnitude lower than
-the number of processes in the system. For instance, random networks
+the number of \processes in the system. For instance, random networks
 only require $O(\log(|V|))$ neighbors to work properly \REF; and
-processes in autonomous systems have in average \TODO{X} neighbors
+\processes in autonomous systems have in average \TODO{X} neighbors
 \REF. Lines~\ref{line:notloopingA} and \ref{line:notloopingB} can
@@
 In terms of number of messages required to reach optimal
-partitioning. In the average-case, a process $i$ chosen uniformly at
-random among all processes creates a logical partition. Its messages
-$\alpha_i$ propagate through the network until reaching processes that
+partitioning. In the average-case, a \process $i$ chosen uniformly at
+random among all \processes creates a logical partition. Its messages
+$\alpha_i$ propagate through the network until reaching \processes that
 belong to another partition closer to them. This splits partitions in
@@
 \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
-processes. This decreases every new partition until reaching $0$
-processes per new partition: even the chosen process already belongs
-to its optimal partition. The average number of messages per process
+\processes. This decreases every new partition until reaching $0$
+\processes per new partition: even the chosen \process already belongs
+to its optimal partition. The average number of messages per \process
 is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
@@
 the $a^{th}$ partition creation. \TODO{But what about echos?} In the
-worst-case, every new partition includes all but one process belonging
+worst-case, every new partition includes all but one \process belonging
 to the previous partition. The total number of messages after the

### 2021-04-12 input/proposal.tex
mostly on the start of adaptive scoped broadcast

@@
 deliver such messages.
-%% Dedicated scoped broadcast implementations
-%% outperform uniform reliable broadcast
-%% implementations~\cite{hadzilacos1994modular, raynal2013distributed}
-%% since the former targets a connected \emph{subset} of the whole
-%% network while the latter targets \emph{all} \processes of the
-%% distributed system.
 Scoped broadcast only targets a connected \emph{subset} of \processes
@@
 In this section, we propose to dynamically adapt the scopes of \NAMEB
-using \NAMEB itself for the sake of efficiency. \TODO{States of
-  \processes change, predicates change over time.} At any time, a
-\process decides whether or not it becomes the center (or
-\emph{source}) of a scope (or \emph{partition}). \Processes must
-eventually rally the partition corresponding to their closest source
-despite concurrent operations, and dynamic changes in the network.
+using \NAMEB itself for the sake of efficiency: a \NAMEB message may
+modify the state of a \process, consequently changing predicate
+evaluations over deliveries.  At any time, a \process decides whether
+or not it becomes the center (or \emph{source}) of a scope (or
+\emph{partition}). \Processes must eventually rally the partition
+corresponding to their closest source despite concurrent operations,
+and dynamic changes in the network.
 
@@
 \begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  Let $W_{xy} = W_{yx}$ be the symmetric \underline{w}eight between
-  $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to
-  $z$ the weight of which $|\Pi_{xz}|$ is lower than any other path
-  weight, the only consistent partitioning $\mathcal{P}$ is a set of
-  partitions $P_{s\in S}$ such that each \process belongs to a logical
-  partition comprising its closest source: $\forall p \in P_{s_1},
-  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
+  Let $W_{xy} = W_{yx}$ be the positive symmetric \underline{w}eight
+  between $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath
+  from $x$ to $z$ the weight of which $|\Pi_{xz}|$ is lower than any
+  other path weight, the only consistent partitioning $\mathcal{P}$ is
+  a set of partitions $P_{s\in S}$ such that each \process belongs to
+  a logical partition comprising its closest source: $\forall p \in
+  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
 \end{definition}
 
-Unfortunately, \processes do not share a common global knowledge of the
-network state. For \processes to reach consistent partitioning
+Unfortunately, \processes do not share a common global knowledge of
+the network state. For \processes to reach consistent partitioning
 together, a \process becoming a source must notify every \process that
-is closer to it than any other source, using \NAMEB for the sake of
-efficiency.
+is closer to it than any other source. As stated in
+Section~\ref{sec:scoped}, since epidemic dissemination and scoped
+broadcast have well-aligned preoccupations, we assume implementations
+relying on forwarding of messages from neighbor to neighbor.
 
@@
   eventually receives the message $m$ \underline{s}ent to it by a
-  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a static system ($G^t =
-  G^{t+1}$); assuming local knowledge only, \processes eventually reach
-  consistent partitioning if and only if each \process eventually
-  forwards its best known partition.
+  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a monotonically
+  growing system ($G^t \subseteq G^{t+1}$); \processes eventually
+  reach consistent partitioning if and only if each \process
+  eventually forwards its best known partition.
 \end{theorem}
-
-\TODO{If forwarding defined as send to all neighbors, then it also
-  works in dynamic systems where \processes join and edges are added,
-  for when a new neighbor appears, the \processes must forward their
-  best.}
 
@@
   \begin{asparadesc}
-  \item [$BEF \implies CP$:] When a \process $s_1$ becomes a source, it
-    belongs to its own partition, for there exists no better partition
-    than its own: $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1
-      p}|$. It broadcasts such message to its neighbors. Since
-    communication channels are reliable, neighboring \processes
-    eventually receive such notification. In particular, whatever the
-    order of received messages, every \process $p_1$ -- such that there
-    exists no better partition $s_2$ than the received one -- delivers
-    and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| < |\Pi_{p
-      s_2}|$. The notification emanating from $s_1$ transitively
+  \item [$BEF \implies CP$:] When a \process $s_1$ becomes a source,
+    it belongs to its own partition, for there exists no better
+    partition than its own: $\forall p \in V: |\Pi_{s_1 s_1}| <
+    |\Pi_{s_1 p}|$. It forwards such message to its neighbors. Since
+    communication links are reliable, neighboring \processes
+    eventually receive such notification. Most importantly, whatever
+    the order of received messages, every \process $p_1$ -- such that
+    there exists no better partition $s_2$ than the received one --
+    delivers and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| <
+    |\Pi_{p s_2}|$. The message originating from $s_1$ transitively
     reaches all such \processes through shortest paths. Since there
@@
     retracted, \processes eventually reach consistent
-    partitioning. \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
+    partitioning. % \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
   \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
@@
 $\delta_d$ since they already delivered it. The system converges to an
-unconsistent state where some \processes assume they belong to a
+inconsistent state where some \processes assume they belong to a
 partition while it does not exist anymore. Naive propagation of

### 2021-04-12 input/proposal.tex
about consistent partitioning

@@
 
-\begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \iff CP$]
+\begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \implies CP$]
   Assuming reliable communication links where a correct \process $q$
@@
   growing system ($G^t \subseteq G^{t+1}$); \processes eventually
-  reach consistent partitioning if and only if each \process
-  eventually forwards its best known partition.
+  reach consistent partitioning if each \process eventually forwards
+  its best known partition.
 \end{theorem}
@@
 \begin{proof}
-  \begin{asparadesc}
-  \item [$BEF \implies CP$:] When a \process $s_1$ becomes a source,
-    it belongs to its own partition, for there exists no better
-    partition than its own: $\forall p \in V: |\Pi_{s_1 s_1}| <
-    |\Pi_{s_1 p}|$. It forwards such message to its neighbors. Since
-    communication links are reliable, neighboring \processes
-    eventually receive such notification. Most importantly, whatever
-    the order of received messages, every \process $p_1$ -- such that
-    there exists no better partition $s_2$ than the received one --
-    delivers and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| <
-    |\Pi_{p s_2}|$. The message originating from $s_1$ transitively
-    reaches all such \processes through shortest paths. Since there
-    exists only one best value per \process that can never be
-    retracted, \processes eventually reach consistent
-    partitioning. % \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
-  \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
-    \process $p$ that does not forward, then another \process $q$ may
-    never gets its best because it needs the weight $W_{pq}$.}
-  \end{asparadesc}
+  % \begin{asparadesc}
+  % \item [$BEF \implies CP$:]
+  When a \process $s_1$ becomes a source, it belongs to its own
+  partition, for there exists no better partition than its own:
+  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
+  hence forwards such $\alpha$ message to its -- current or future --
+  neighbors. Since communication links are reliable, neighboring
+  \processes eventually receive such notification $\forall \langle
+  s_1, q \rangle \in E, s_1 \in S \iff \eventually
+  r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most importantly, whatever the order
+  of received messages, every \process $q'$ in this neighborhood --
+  such that there exists no better partition $s_2$ than the received
+  one -- delivers and forwards it: $\forall s_2 \in S: |\Pi_{q' s_1}|
+  < |\Pi_{q' s_2}| \implies \eventually d_{q'}(\alpha_{s_1}^{w_{s_1
+      q'}})$. By transitivity, the message originating from $s_1$
+  transitively reaches all such \processes through their shortest
+  paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| <
+  |\Pi_{q'' s_2}| \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1
+      q''}|})$.  Since there exists only one best sum of weights per
+  \process that can never be retracted, \processes eventually reach
+  consistent partitioning.
+  %% /!\ not equivalence for there exists other implementations.
+  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
+  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
+  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
+  %%   following \processes from $q'$ to $p$ may mistake another
+  %%   partition for their  because it needs the weight $W_{pq}$.
+  %% \end{asparadesc}
 \end{proof}
@@
 \item \processes only add new partitions to the system,
-\item and \processes never join nor crash nor leave the system.
+\item and \processes never crash nor leave the system.
 \end{inparaenum}
 Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
-\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become
-the sources of their partition. They \NAMEB a notification
+\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
+become the sources of their partition. They \NAMEB a notification
 \underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
@@
 never hear of Source~$a$. Ultimately, \processes discard last
-transiting messages. The system reached consistent partitioning.
+transiting messages. Despite the obvious lack of traffic optimization,
+the system reach consistent partitioning.
 

### 2021-04-12 input/figadd.tex
preparing

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:addA}Both Process~$a$ and Process~$d$
+    \subfloat[Part A][\label{fig:addA}Both \Process~$a$ and \Process~$d$
       become sources.  $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
@@
       links and carry increasing weights.]{\input{input/figaddB.tex}}
-    \hspace{5pt} \subfloat[Part C][\label{fig:addC}Process~$b$ and
-      Process~$c$ receive, deliver, and forward $\alpha_{d}^{1}$ and
+    \hspace{5pt} \subfloat[Part C][\label{fig:addC}\Process~$b$ and
+      \Process~$c$ receive, deliver, and forward $\alpha_{d}^{1}$ and
       $\alpha_d^3$ respectively.]{\input{input/figaddC.tex}}
@@
       \NAMEB. Partition~$P_a$ includes $a$ while Partition~$P_d$
-      includes $b$, $c$, and $d$. Process~$c$ and Process~$d$ never
-      acknowledge the existence of Source~$a$, for Process~$b$ stops
+      includes $b$, $c$, and $d$. \Process~$c$ and \Process~$d$ never
+      acknowledge the existence of Source~$a$, for \Process~$b$ stops
       the propagation of the latter's notifications.}

### 2021-04-12 input/figdel.tex
rework issue with delete
meow
preparing

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:delA}Process~$a$ deletes its
-      partition.  It notifies all processes that belong to its
+    \subfloat[Part A][\label{fig:delA}\Process~$a$ deletes its
+      partition.  It notifies all \processes that belong to its
       partition using \NAMEB.]{\input{input/figdelA.tex}}
@@
     \subfloat[Part B][\label{fig:delB}$\delta$s stop as soon as they
-      encounter another partition. Process~$b$ answers with its
+      encounter another partition. \Process~$b$ answers with its
       partition.]{\input{input/figdelB.tex}}
@@
   \caption{\label{fig:del}Efficient removal of a partition using
-    \NAME. Process~$a$ eventually knows that it belong to Partition
-    $P_c$.}
+    \NAMEB. \Process~$a$ eventually knows that it belong to Partition
+    $P_d$.}
 \end{figure}

### 2021-04-12 input/figproblem.tex
preparing

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:problemA}Both Process~$a$ and
-      Process~$d$ add then delete their partition. For the recall,
+    \subfloat[Part A][\label{fig:problemA}Both \Process~$a$ and
+      \Process~$d$ add then delete their partition. For the recall,
       $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
       3$.]{\input{input/figproblemA.tex}}
-    \hspace{5pt} \subfloat[Part B][\label{fig:problemB}Process~$b$
+    \hspace{5pt} \subfloat[Part B][\label{fig:problemB}\Process~$b$
       delivers and forwards the $\alpha$ message about $P_a$ while
-      Process~$c$ delivers and forwards both $\alpha$ and $\delta$
+      \Process~$c$ delivers and forwards both $\alpha$ and $\delta$
       messages about $P_d$.]  {\input{input/figproblemB.tex}}
-    \hspace{5pt} \subfloat[Part C][\label{fig:problemC}Process~$b$
+    \hspace{5pt} \subfloat[Part C][\label{fig:problemC}\Process~$b$
       already blocks the propagation of $\delta_a$ despite it
-      propagated $\alpha_a$ before. Process~$c$ and Process~$d$ do not
+      propagated $\alpha_a$ before. \Process~$c$ and \Process~$d$ do not
       deliver $\alpha_d$, for they already deleted
       it before.]{\input{input/figproblemC.tex}}
-    \hspace{5pt} \subfloat[Part D][\label{fig:problemD}Processes
-      discard remaining messages. Since Process~$b$ cannot deliver
+    \hspace{5pt} \subfloat[Part D][\label{fig:problemD}\Processes
+      discard remaining messages. Since \Process~$b$ cannot deliver
       $\delta_a$, $c$ and $d$ remain in the deleted partition

### 2021-04-12 input/figproofB.tex
wip on implem mostly
preparing

@@
 
-  \newcommand\X{70pt}
+  \newcommand\X{85pt}
   \newcommand\Y{-40pt}
@@
 
-  \draw[opacity=0] (-1.5*\X, 0) -- (2.5*\X, 0);
+  \draw[opacity=0] (-1.4*\X, 0) -- (2.4*\X, 0);
 
-  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I as well
-  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e
+  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I': propagation} (5pt, -\Y); %% I as well
+  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small]{$\DEL_d$} (0 - 5pt, 0); %% d - e
 
-  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{III} (5pt + \X, 5pt -\Y); %% IV
+  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{III: detection} (5pt + \X, 5pt -\Y); %% IV
   \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'
 
-  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{IV} (5pt + 2*\X, 10pt -\Y); %% V
+  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{IV: propagation} (5pt + 2*\X, 10pt -\Y); %% V
   \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''
@@
 
-  \draw (-\X, 5pt) node[above, color=\PC]{$\DEL_d$};
+  \draw (-\X, 5pt) node[above]{$\DEL_d$};
 
   \draw ( 0, 5pt) node[above]{$\textcolor{\PC}{\ADD_d} \rightarrow \textcolor{\WRONG}{\ADD_f^{0.5}}$};
-  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PB}{\DEL_f}$};
+  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\DEL_f$};
 
-  \draw ( \X, 5pt) node[above]{$\textcolor{\PB}{\ADD_f^1} \rightarrow \textcolor{\PB}{\DEL_f} \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
-  \draw ( \X, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{0.5}}$};
+  \draw ( \X, 5pt) node[above]{$\textcolor{\PB}{\ADD_f^1} \rightarrow \DEL_f \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
+  \draw ( \X, -5pt) node[below, font=\footnotesize]{expect $\DEL_d$ or $\DEL_d^{0.5}$};
 
   \draw (2*\X, 5pt) node[above]{$\textcolor{\PC}{\ADD_d^{1.5}}$};
-  \draw (2*\X, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{1.5}}$};
+  \draw (2*\X, -5pt) node[below, font=\footnotesize]{expect $\DEL_d$ or $\DEL_d^{1.5}$};
 

### 2021-04-12 input/proposal.tex
preparing

@@
 \subsection{Dynamic consistent partitioning}
+\label{subsec:dynamic}
 
@@
 
-Then, at any time, a source can revoke its self-appointed status of
-source, hence deleting its partition from the system, by executing a
+At any time, a source can revoke its self-appointed status of source,
+hence deleting its partition from the system, by executing a
 \texttt{Del} operation. All \processes that belong to this partition
@@
 Figure~\ref{fig:delA}, \Process $a$ deletes its partition. It notifies
-all neighboring \processes -- here only \Process $b$ -- that may belong
-to its partition using \NAMEB. Upon receipt, \Process $b$ discards the
-message $\delta_a$, for the latter does not target the former's
-partition. Yet, \Process $b$ sends its own partition that may be the
-best for \Process $a$. Eventually, every \processes belong to the same
-partition $P_d$.
+all neighboring \processes -- here only \Process $b$ -- that may
+belong to its partition using \NAMEB. Upon receipt, \Process $b$
+discards the message $\delta_a$, for the latter does not target the
+former's partition. \Process $b$ sends its own knowledge of best
+partition $\alpha_d^3$ that may prove to be the best for \Process
+$a$. Eventually, every \processes belong to the same partition
+$P_d$. In this scenario, they reach consistent partitioning.
+
+\texttt{Del}ete operations add a new notion of order between events,
+and most importantly between message deliveries. Delete operations
+implicitly state that all preceding events become obsolete, and that
+all messages originating from these preceding events convey stale
+control information.
+
+\begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
+  The transitive, irreflexive, and antisymmetric happens-before
+  relationship defines a strict partial order between events. Two
+  messages are concurrent if none happens before the other.
+\end{definition}
+
+\begin{definition}[Last win order]
+  When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
+  b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
+  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m'$
+  convey \emph{stale} control information.
+\end{definition}
 
@@
 partitioning when each \process can add or delete its partition at any
-time.
+time. \Processes need to exploit their local knowledge gathered over
+message receipts.
 
-One could solve this issue by always propagating the $\delta$ messages
-corresponding to the $\alpha$ messages it propagated before. In
-Figure~\ref{fig:problem}, it means that as soon as \Process~$b$
-forwards $\alpha_a^2$, it assumes that its neighbors \Process~$c$ and
-\Process~$d$ may need the notification of removal $\delta_a$ if it
-exists. However, such solution also implies that \processes generate
-traffic not only related to their current partition, but also related
-to partitions they belong to in the past. Instead, we propose to use
-the delivery order at each \process to detect possible inconsistencies
-and solve them. Together, \processes eventually remove all stale
-control information (transiting messages and local states) of the
-system leaving room for propagation of messages about up-to-date
-partitions.
+\input{input/figproblem.tex}
+
+One could guarantee consistent partitioning by always propagating the
+$\delta$ messages corresponding to the $\alpha$ messages it propagated
+before. In Figure~\ref{fig:problem}, it means that as soon as
+\Process~$b$ forwards $\alpha_a^2$, it assumes that its neighbors
+\Process~$c$ and \Process~$d$ may need the notification of removal
+$\delta_a$ if it exists. However, such solution also implies that
+\processes generate traffic not only related to their current
+partition, but also related to partitions they belong to in the
+past. Instead, we propose to use the delivery order at each \process
+to detect possible inconsistencies and solve them. Together,
+\processes eventually remove all stale control information (transiting
+messages and local states) of the system leaving room for propagation
+of messages about up-to-date partitions.
 
@@
 
-\input{input/figproblem.tex}
-
 \begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
   Consistent partitioning where each \process can \texttt{Add} and
-  \texttt{Del} its partition at any time requires
+  \texttt{Del}ete its partition at any time requires
   \begin{inparaenum}[(i)]
-  \item eventual purging of stale notifications, then
+  \item eventual purging of stale notifications, and
   \item eventual delivery of bests partitions.
@@
 \begin{proof}
-  \TODO{Quite obvious.}
+  \Processes deliver and forward the best sum of weights they
+  received. The only case where a \process would block such epidemic
+  propagation would be when it received and delivered a message from a
+  partition that has since then been deleted but with a better sum of
+  weights than newly received ones. Removing \emph{forever} all such
+  stale messages about deleted partitions would allow \processes to
+  propagate their best up-to-date partition again, eventually reaching
+  consistent partition together.
 \end{proof}
-
-\begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
-  The transitive, irreflexive, and antisymmetric happens-before
-  relationship defines a strict partial order between events. Two
-  messages are concurrent if none happens before the other.
-\end{definition}
-
-We define a last win order to forbid the delivery of stale information
-emanating from a same \process. In other terms, the \emph{best}
-notification message is always the most recent known of each \process.
-
-\begin{definition}[Last win order]
-  When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
-  b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
-  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$.
-\end{definition}
 
@@
 
-\begin{theorem}[\TODO{meow}]
+\begin{theorem}[Propagation $+$ detection $\implies$ DCP]
+  % Propagating 
   \TODO{Puring stale notifications requires to handle I...IV.}
@@
 
-\begin{algorithm}
-  \input{input/algoadddelundo.tex}
-  \caption{\label{algo:adddelundo}Dynamic partitioning by \Process $p$.}
-\end{algorithm}
-
-We extend Algorithm~\ref{algo:add} to enable each source to revoke its
-self-appointed status of source and become a simple \process again.
 Algorithm~\ref{algo:adddelundo} provides the instructions that
@@
 delivery of the best up-to-date partitions.
+
+\begin{algorithm}
+  \input{input/algoadddelundo.tex}
+  \caption{\label{algo:adddelundo}Dynamic partitioning by \Process $p$.}
+\end{algorithm}
 

### 2021-04-13 input/experiments.tex
figure experiment topo
sketching experiment

@@
 
-\subsection{Distribution and hotspots}
+%% \subsection{Distribution and hotspots}
 
-\subsection{Inter-autonomous systems}
+% \subsection{Confirm the relevance of \NAME in the context of dynamic inter-autonomous
+%   system communications.}
+\subsection{Confirm that \NAME locks down the traffic of decentralized content
+  indexing in the context of dynamic inter-autonomous system
+  communications.}
+
+\begin{figure}
+  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
+  \caption{\label{fig:geant}\TODO{Figure caption}}
+\end{figure}
+
+\begin{asparadesc}
+\item [Description:]
+
+We build a network by duplicating the G{\'E}ANT topology -- a real
+infrastructure spanning across Europe -- and by connecting these two
+clusters with a high latency link: $200$ ms simulating
+cross-continental communications such as Europe-America. The
+experiments comprise $2 \times 271 = 542$ \processes and we derive
+intra-cluster latency from \processes' geographic location~\REF.
+
+\noindent We evaluate the traffic of \NAME by measuring the average
+number of messages per \process over the experiments. In the first
+experiment, at $50$ ms, only one process becomes source, hence there
+is only one partition for the whole distributed system. In the second
+experiment, at $50$ ms, two processes become sources, one per
+cluster. Afterwards both scenarios are identical. At $500$ ms, we
+remove the link between the two clusters. At $1200$ ms, we insert this
+link again.
+
+\item [Results:]
+
+Figure~\ref{fig:geant} shows the results of this experimentation. The
+top part corresponds to the one source experiment, while the bottom
+part corresponds to the one source per cluster experiment.
+
+\noindent Figure~\ref{fig:geant} confirms that concurrent \texttt{Add}
+may generate additional traffic, for processes may deliver and forward
+a partition only to later realize that they have a closer source.
+
+\noindent Figure~\ref{fig:geant} highlights that removing the
+inter-continental link generates additional traffic. The cluster cut
+off the source must remove control information about this
+source. \TODO{There are both $\alpha$s and $\delta$s.}  \TODO{The
+  protocol works when physical partitions exist. The cluster with the
+  source belong to the same partition. The other cluster does not
+  belong to any partition.}
+
+\noindent Figure~\ref{fig:geant} shows that, when adding the link
+again, the two clusters communicate again. \TODO{More.}
+
+\noindent Finally, Figure~\ref{fig:geant} \TODO{(overall less
+  traffic)} empirically demonstrates that \NAME favor
+replication. \TODO{More.}
+\end{asparadesc}
 

### 2021-04-14 input/experiments.tex
removing url and doi of biblio + writing text of second experiment

--- 2021-04-02 input/experiments.tex
@@
 \begin{asparadesc}
-\item [Description:] We build a network comprising 10k
-  processes. First, we chain processes together, then we add another
-  communication link per process to another process. Since links are
-  bidirectional, each process has 4 communication links on average. We
-  set the latency of links between 20 and 40 ms at random following a
-  uniform distribution. We set the weight of links between 5 and 15 at
-  random following a uniform distribution. Weights and latency are
-  different, hence the first $\alpha$ received by a process may not be
-  that of its shortest path. It implies more concurrent operations,
-  hence more traffic to reach consistent partitioning.
+\item [Description:]
+
+We build a network comprising 10k \processes. First, we chain
+\processes together, then we add another communication link per
+\process to another random \process. Since links are bidirectional,
+each \process has 4 communication links on average. We set the latency
+of links between 20 and 40 ms at random following a uniform
+distribution. We set the weight of links between 5 and 15 at random
+following a uniform distribution. Weights and latency are different,
+hence the first $\alpha$ received by a \process may not be that of its
+shortest path. It implies more concurrent operations, hence more
+traffic to reach consistent partitioning.
 
@@
 \noindent We focus on the complexity of \NAME. We measure the average
-number of messages generated per process during the experiment; and
+number of messages generated per \process during the experiment; and
 the time before reaching consistent partitioning after adding or
@@
   \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
-  \caption{\label{fig:complexity}Overhead of, and time before,
-    reaching consistent partitioning using \NAME.}
+  \caption{\label{fig:complexity}Overhead of consistent partitioning
+    using \NAME.}
   %% \caption{\label{fig:complexity}Cumulative average number of messages
@@
 Figure~\ref{fig:complexity} shows the results of this experiment. The
-top part of the figure shows the average traffic per process divided
+top part of the figure shows the average traffic per \process divided
 between $\alpha$ and $\delta$ messages. The bottom part of the figure
@@
 depends on the size of partitions. The first partition is the most
-expensive, for $\alpha$'s must reach every process which takes time
+expensive, for $\alpha$'s must reach every \process which takes time
 and generate more traffic. Still, being reactive, as opposed as
@@
 deleting this $1^{st}$ partition. When adding it, messages must reach
-all processes while when removing it, messages must reach a small
+all \processes while when removing it, messages must reach a small
 subset of this membership. This is important, for it means that
@@
 \noindent Finally, Figure~\ref{fig:complexity} highlights that after
-49 seconds, i.e., after the 100 adds and the 100 deletes, processes do
-not generate traffic anymore. Being reactive, \NAME has no overhead
+49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
+do not generate traffic anymore. Being reactive, \NAME has no overhead
 when there is no operation in the system. This is important, for it
@@
 
-\subsection{Distribution and hotspots}
+%% \subsection{Distribution and hotspots}
 
-\subsection{Inter-autonomous systems}
+% \subsection{Confirm the relevance of \NAME in the context of dynamic inter-autonomous
+%   system communications.}
+\subsection{Confirm that \NAME locks down the traffic of decentralized content
+  indexing in the context of dynamic inter-autonomous system
+  communications.}
+
+\begin{figure}
+  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
+  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
+\end{figure}
+
+\begin{asparadesc}
+\item [Description:]
+
+We build a network by duplicating the G{\'E}ANT
+topology~\cite{knight2011internet} -- a real infrastructure spanning
+across Europe -- and by connecting these two clusters with a high
+latency link: $200$ ms simulating cross-continental communications
+such as Europe-America. The experiments comprise $2 \times 271 = 542$
+\processes and we derive intra-cluster latency from their \processes'
+geographic location.
+
+\noindent We evaluate the traffic of \NAME by measuring the average
+number of messages per \process over the experiments. In the first
+experiment, at $50$ ms, only one \process becomes source, hence there
+is only one partition for the whole distributed system. In the second
+experiment, at $50$ ms, two \processes become sources, one per
+cluster. Afterwards both scenarios are identical. At $500$ ms, we
+remove the link between the two clusters. At $1200$ ms, we insert this
+link again.
+
+\item [Results:]
+
+Figure~\ref{fig:geant} shows the results of this experimentation. The
+top part corresponds to the one source experiment, while the bottom
+part corresponds to the one source per cluster experiment.
+
+\noindent Figure~\ref{fig:geant} confirms that concurrent \texttt{Add}
+may generate additional traffic, for \processes may deliver and forward
+a partition only to later realize that they have a closer source.
+
+\noindent Figure~\ref{fig:geant} highlights that removing the
+inter-continental link generates additional traffic. The cluster cut
+off the source must remove control information about this source. This
+generates $\delta$ messages but also $\alpha$ messages, for \NAME
+still triggers competitions in the cut off cluster with $\alpha$
+messages that monotonically grows until they are purged off the system
+by the anti-looping mechanism and corresponding $\delta$s.  Most
+importantly, Figure~\ref{fig:geant} shows that \NAME still operates
+as expected when \emph{physical} partitions appear. \Processes from the
+cluster without source do not belong to any partition while \processes
+from the other cluster belong to the same partition.
+
+\noindent Figure~\ref{fig:geant} shows that, when adding the
+inter-continental link again, the two clusters can communicate
+again. In the experiment involving one source for two clusters, it
+generates traffic. After a $200$ milliseconds delay corresponding to
+the new link latency, the cut off cluster starts to communicate
+$\alpha$ messages again. Eventually, all \processes belong to the same
+partition. However, in the experiment involving one source \emph{per}
+cluster, the new link does not trigger noticeable traffic (only $2$
+messages total), for \processes already know their closest source
+located in their respective cluster.
+
+\noindent Overall, this experimentation empirically demonstrates the
+benefits of \NAME in the context of Edge infrastructures:
+inter-connected autonomous systems where \processes may join or leave
+or crash, communications links may be added or removed. \NAME coupled
+with replication strategies designed for the Edge would allow locking
+down the traffic of replica indexing, while providing every \processes
+with quick access to replicated content.
+
+\end{asparadesc}
 

### 2021-04-14 input/proposal.tex
removing url and doi of biblio + writing text of second experiment

@@
 
-\paragraph{Space.}
+\begin{asparadesc}
+\item [Space:]
+
 Each \process needs to maintain a vector of versions the size of which
@@
 
-\paragraph{\TODO{Time.}}
+\item[Time:]
+
 In terms of processing time, whatever the operation, it increases
@@
 
-\paragraph{\TODO{Communication.}}
+\item[Communication:]
+
 In terms of number of messages required to reach optimal
@@
 random among all \processes creates a logical partition. Its messages
-$\alpha_i$ propagate through the network until reaching \processes that
-belong to another partition closer to them. This splits partitions in
-half in average. Overall, the $a^{th}$ new partition comprises
-\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
-\processes. This decreases every new partition until reaching $0$
-\processes per new partition: even the chosen \process already belongs
-to its optimal partition. The average number of messages per \process
-is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
+$\alpha_i$ propagate through the network until reaching \processes
+that belong to another partition closer to them. This splits
+partitions in half in average. Overall, the $a^{th}$ new partition
+comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a
+      \rfloor}})$} \processes. This decreases every new partition
+until reaching $0$ \processes per new partition: even the chosen
+\process already belongs to its optimal partition. The average number
+of messages per \process is
+\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
       \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
@@
 the $a^{th}$ partition creation. \TODO{But what about echos?} In the
-worst-case, every new partition includes all but one \process belonging
-to the previous partition. The total number of messages after the
-$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
-for the average-case, the number of messages for the partition
-deletion is identical to the number of messages of the corresponding
-partition creation.
+worst-case, every new partition includes all but one \process
+belonging to the previous partition. The total number of messages
+after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
+a^2)$. As for the average-case, the number of messages for the
+partition deletion is identical to the number of messages of the
+corresponding partition creation.
 
 \noindent \TODO{In terms of size of messages.}
+
+\end{asparadesc}
 

### 2021-04-14 input/experiments.tex
adapt text of experiments to new figures

@@
 \noindent We focus on the complexity of \NAME. We measure the average
-number of messages generated per \process during the experiment; and
-the time before reaching consistent partitioning after adding or
-removing a partition.
+number of messages generated per \process per second during the
+experiment; and the time before reaching consistent partitioning after
+adding or removing a partition.
 
@@
 Figure~\ref{fig:complexity} shows the results of this experiment. The
-top part of the figure shows the average traffic per \process divided
-between $\alpha$ and $\delta$ messages. The bottom part of the figure
-shows the time before reaching consistent partitioning.
+top part of the figure shows the average traffic per \process per
+second divided between $\alpha$ and $\delta$ messages. The bottom part
+of the figure shows the time before reaching consistent partitioning.
 
@@
 all \processes while when removing it, messages must reach a small
-subset of this membership. This is important, for it means that
-\NAME's overhead actually depends on the current partitioning, and
-does not depend on the past partitioning.
+subset of this membership.  \NAME's overhead actually depends on
+current partitioning as opposed to past partitionings.
 
@@
 do not generate traffic anymore. Being reactive, \NAME has no overhead
-when there is no operation in the system. This is important, for it
-means that \NAME's overhead actually depends on its usage.
+when there is no operation in the system.  \NAME's overhead actually
+depends on its usage.
 
@@
 number of messages per \process over the experiments. In the first
-experiment, at $50$ ms, only one \process becomes source, hence there
+experiment, at $50$~ms, only one \process becomes source, hence there
 is only one partition for the whole distributed system. In the second
-experiment, at $50$ ms, two \processes become sources, one per
-cluster. Afterwards both scenarios are identical. At $500$ ms, we
-remove the link between the two clusters. At $1200$ ms, we insert this
+experiment, at $50$~ms, two \processes become sources, one per
+cluster. Afterwards both scenarios are identical. At $850$~ms, we
+remove the link between the two clusters. At $1.7$~s, we insert this
 link again.
@@
 
-\noindent Figure~\ref{fig:geant} confirms that concurrent \texttt{Add}
-may generate additional traffic, for \processes may deliver and forward
-a partition only to later realize that they have a closer source.
+\noindent Figure~\ref{fig:geant} confirms that concurrent
+\texttt{Add}s may reach consistent partitioning faster. In particular,
+Figure~\ref{fig:geant} depicts a slow down in traffic around $500$ ms
+due to the high latency inter-continental link. This link acts as a
+bottleneck that does not exist when each cluster has its own source.
 
@@
 inter-continental link generates additional traffic. The cluster cut
-off the source must remove control information about this source. This
-generates $\delta$ messages but also $\alpha$ messages, for \NAME
-still triggers competitions in the cut off cluster with $\alpha$
-messages that monotonically grows until they are purged off the system
-by the anti-looping mechanism and corresponding $\delta$s.  Most
-importantly, Figure~\ref{fig:geant} shows that \NAME still operates
-as expected when \emph{physical} partitions appear. \Processes from the
-cluster without source do not belong to any partition while \processes
-from the other cluster belong to the same partition.
+off from the source must purge all control information about this
+source.  Most importantly, Figure~\ref{fig:geant} shows that \NAME
+still operates well when \emph{physical} partitions appear. \Processes
+from the cluster without source do not belong to any partition while
+\processes from the other cluster belong to the same partition.
 

### 2021-04-15 input/abstract.tex
abstract pass 1

@@
   %% Context and problem
-  Edge infrastructures constitute an alternative to Cloud Computing
-  that aims at improving on latency and traffic by providing computing
-  and storage capabilities closer to data producers and consumers.
-  %% Edge infrastructures have been proposed as an alternative to Cloud
-  %% Computing to provide computing and storage capabilities closer to
-  %% the locations where data is generated/consumed, with the objectives
-  %% of reducing the latency and the volume of data passing through the
-  %% network.
-  A few systems, such as content delivery networks, replicate and
-  distribute produced data in these infrastructures.
-  % A few systems have been proposed to store data in those
-  % infrastructures.
-  Locating the closest replica of a specific content requires to
+  %By providing computing and storage capabilities closer to data
+  %producers and consumers, Edge infrastructures constitute an alternative to Cloud Computing platforms
+  %A few systems have been proposed to store and manipulate data in
+  %Edge infrastructures. By relying for instance on appropriate
+  %replication policies, those systems reduce the impact of the latency
+  %as well as the volume of data passing through the network overall.
+  %
+  Although, there is no major solution to store and manipulate data in
+  Edge infrastructures yet, existing proposals demonstrated the relevance of appropriate
+  replication strategies to bring contents closer to consumers, reducing the impact of the latency as
+  well as the volume of data passing through the network overall.
+%
+  Unfortunately, locating the closest replica of a specific content requires to
   maintain an up-to-date index of all live replicas along with their
@@
   %
-  Unfortunately, relying on a centralized service would bring
-  scalability issues, single point of failure, as well as additional
-  middleman latency where locating replicas may effectively take more
-  time than actually downloading contents. Instead, data consumer
-  \processes must maintain an up-to-date index
-  themselves. Unfortunately, maintaining an index of all live replicas
-  at every \process would prove overly costly in terms of memory and
-  generated traffic, especially in large scale dynamic systems where
-  \processes create and destroy replicas at any time.
+  %Current proposals built on a centralized service face scalability
+  %issues, single point of failure, as well as latency penalities where
+  %locating replicas may effectively take more time than actually
+  %downloading contents. Instead, data consumer \processes must
+  %maintain an up-to-date index themselves. Unfortunately, maintaining
+  %an index of all live replicas at every \process would prove overly
+  %costly in terms of memory and generated traffic, especially in large
+  %scale dynamic systems where \processes create and destroy replicas
+  %at any time.
+  % 
+  Relying on a remote service contradicts with the properties of
+  Edge infrastructures as locating replicas may
+  effectively take more time than actually downloading contents.
+  At the opposite,  maintaining such an index at every \process would prove overly
+  costly in terms of memory and generated traffic, especially in an
+  edge context where \processes create and destroy replicas at any
+  time.
   % while flooding approaches will not enable the maintenance of such
-  % an index for each node in large systems, relying on a dedicated
-  % service contradicts with the properties of Edge infrastructures in
-  % terms of locality and robustness
+  % an index for each node in large systems,
 

### 2021-04-15 input/introduction.tex
introduction: partition ok but needs to add more content regarding the AS-cast part, help welcome

--- 2021-04-01 input/introduction.tex
@@
 investigated for the last few years \cite{confais2017performance,
-  confais2017object, fogstore, hasenburg2020towards}.  Although these systems,
-provide good properties such as favouring network traffic confinement
-by writting data locally, determining the location where to get the
-content might be more expensive than retrieving the content itself.
+  confais2017object, fogstore, hasenburg2020towards}.  Although these
+systems, provide good properties such as favouring network traffic
+confinement by writting data locally and replicating contents
+according to the effective needs, determining the location where to
+get the content might be more expensive than retrieving the content
+itself.
 %
@@
 Cloud, rely on a Distributed Hash Table (DHT) across the different
-peers composing the infrastructure: When a client wants to access a
-specific content, it has to perform a request to a first node to
-determine from which site it will retrieve the content. Once it has
-retrieved the content from the location it selected, a local replica
+nodes composing the infrastructure: When a client wants to access a
+specific content, it has to perform a request to a remote process to
+determine from which node(s) it will retrieve the content.  Once it has
+retrieved the content, a local replica
 is created to improve the performance for future accesses and the
-server in charge of maintaining the index is updated to reflect this
+process in charge of maintaining the index is contacted once again to reflect this
 new location.
 %
-Accessing a remote node to find the location of an object (or one of
-its copies) has many drawbacks: (i) The \textit{lookup penalty:} the
-network latency to reach this remote node incurs an additional delay
-to get the object, before being able to start its
-downloading~\cite{asrese2019measuring, doan2019tracing}, (ii)
-Answering external queries increases the load on the remote node,
-potentially impacting its performance, (iii) It prevents nodes to
-access objects in case of network partitioning: if the node in charge
-of maintaining the object locations is isolated from the rest of the
-infrastructure, nodes cannot access the object replicas even if some
-would be reachable.
 
-A simple way to tackle the aforementioned limitations would be to
-maintain an index of all replicas on each node composing the
-system. In addition to being complicated \TODO{impossible} for large-scale
-systems, maintaining such a global index on each node is useless as there
-is no interest to inform a node of the creation of a replica at the
-opposite of the network (each node trying to get content from the closest node).
+%This strategy has two majors drawbacks :
+%\begin{itemize}
+%  \item (i) the lookup penalty: the network latency to reach this
+%    remote node incurs an additional delay~\cite{asrese2019measuring,
+%      doan2019tracing} to get the object before
+%    being able to start its downloading ;
+%  \item (ii) the selection of the node(s) from which the content is
+%    returned: due to the lack of information that would allow the  a request to each process storing a
+%%    replica is perfomed in
+%\end{itemize}
+
+Such a protocol contradicts with the objective of Edge
+infrastructures that aims at reducing the impact of the
+latency as well as the volume of data passing through the network:
+\begin{itemize}
+  \item In addition to hot spot and partitioning issues, accessing a
+    remote node to find the location(s) of a content incurs an
+    additional delay~\cite{asrese2019measuring, doan2019tracing} to
+    get the object, before being able to start its downloading.
+  \item There is no information to select the ``best'' node among the
+     possible candidates from which the content  could be
+     retrieved. This results in parallel requests performed by the client node to
+     each candidate with the goal of retrieving the content as efficient
+     as possible.
+\end{itemize}
+
+A ``simple'' way to tackle the aforementioned limitations would be to
+maintain on each node composing the infrastructure and for each
+content, an index of all replicas (and their ``distance'').  In such
+an approach, each time a new replica is created or deleted, a message
+is broadcasted from the node that performed the operation (\ie the
+source) to all nodes, increasing the distance information at each hop.
 %
-In this paper, we propose to limit the broadcast of creation/deletions
-of replicas only to a subset of the nodes composing the
-infrastructures.  Concretely, our protocol, entitled \NAME, transmits
-messages from peer to peer until a certain condition is reached. In
-the current scenario, the stop condition is related to the distance to
-the nearest copy: if the message that a node receives indicates an
-object has a longer distance than that which the node knows then the
-transfer of the message is useless and so stopped.
+In addition to being complicated for large-scale systems, maintaining
+a global view on each node is useless as there is no interest to
+inform a node of the creation/removal of a replica at the opposite of
+the network (each node trying to get content from the ``closest''
+node).  In other words, the broadcast should be limited to a partition
+of the infrastructure, (\ie the subset of nodes that has to update the
+current location for this particular content). Obviously, these
+partitions depend and evolve according to concurrent operations made by nodes and
+dynamic changes in the infrastructure (network failures, node
+apparitions/leaves).
+
+In this paper, we propose a first implementation of such a protocol.
+Entitled \NAME, our protocol relies on a primitive that forwards
+messages until a certain condition is reached, \ie the scope. The
+scope is defined by a boolean function (predicate) that returns
+whether a message should be propagated or not around its
+broadcaster. In the current scenario, the stop condition is related to
+the distance to the nearest replica : if the message that a node receives
+indicates a content has a longer distance than that which the node
+knows then the transfer of the message is useless and so stopped.
+%
+
+This primitive is used to communicate with the different nodes
+according to four events: creation/removal of a replica and node
+apparitions/leaves. \TODO{network failures is considered as a node leave?}
 
@@
 
-\TODO{add a paragraph on possible usage of the protocol in other use-cases.}
+% TODO : Use cases
+While we use the distance to the closest copy in this paper, It is
+notewothy that other scopes can be envisioned according to the
+use-cases.  For instance, the location of a city in order to broadcast
+message to all nodes in the city.  This requires nodes to store and
+maintain their city location in their local state. Nodes stop
+delivering and forwarding their received messages when they come from
+a different city. Such a predicate can be complexified in order to
+broadcast messages to all nodes in the city plus neighboring
+cities. This requires nodes to overload forwarded messages the first
+time they reach another city. The predicate checks if messages already
+reached two distinct cities before delivery.  The predicate can even
+be piggypack within the message and so be different for each
+message.\TODO{Complete the use-cases}
 

### 2021-04-15 input/proposal.tex
abstract reworkd

@@
       q'}})$. By transitivity, the message originating from $s_1$
-  transitively reaches all such \processes through their shortest
-  paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| <
-  |\Pi_{q'' s_2}| \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1
-      q''}|})$.  Since there exists only one best sum of weights per
-  \process that can never be retracted, \processes eventually reach
-  consistent partitioning.
+  reaches all such \processes through their shortest paths: $\forall
+  q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| < |\Pi_{q'' s_2}|
+  \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.
+  Since there exists only one best sum of weights per \process that
+  can never be retracted, \processes eventually reach consistent
+  partitioning.
   %% /!\ not equivalence for there exists other implementations.
@@
   propagate their best up-to-date partition again, eventually reaching
-  consistent partition together.
+  consistent partitioning together.
 \end{proof}
@@
 
+\vfill
+
+\TODO{spacing}
+
+\newpage
+
 \subsection{Complexity}

### 2021-04-15 input/background.tex
fix biblio, first names and duplicated entries
background with oracle

@@
 This section reviews the existing solutions to locate a given content in a network and details the limitations 
-of such solutions in a Fog context. We first present the related work on content localization at the system level, 
-either with centralized or distributed approaches.
+of such solutions in a Fog context. 
+We first present the related work on content localization at the system level, either with centralized or distributed approaches. 
 We then focus on message-passing solutions and explain why well-known existing software middlewares such as broadcast, or gossip protocols are not good candidates in their existing implementations. 
@@
 \subsection*{Content indexing}
+In the context of this paper, an \textit{ideal} content indexing service would enable that for any content, every node would be able to access its closest replica.
+Basically, offering such a service would require (i) to have access to the list, namely the \textit{index}, of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location.
 
-The easiest way to implement a localization service is to store all replica localizations, namely the \textit{index}, on a centralized server~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
-Before downloading any content, the client first requests the server the list of all its available replicas, in order to select the closest copy, according to its place in the topology.
-While being straightforward to deploy, this solution suffers from well-known disadvantages (load balancing, robustness, locality, etc.) that are even magnified in a Fog context.
-
-A first step to mitigate the drawbacks inherent to a unique centralized server is to deploy a \textit{landmark} system~\cite{landmarks}.
-The idea is to spread special nodes called landmarks across the network so that nodes announce their current cache content to the closest landmarks in a given geographical area.
-Requests are then processed by one or the closest landmarks from the requester.
-One of the the main problems of these lankmark-based solutions is that they require a reliable infrastructure to provide these landmarks which must remain always available to continuously offer the indexing service.
-
-Goind further, fully distributing this index among nodes in the network has been proposed, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example.
+(i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
+However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in a Fog context.
+Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example.
 In the latter, each node stores a part of the index, defined by an interval between hash values.
@@
 
-However, either being centralized, landmark-based or distributed, solutions that require to contact a remote node to obtain a given content localization usually violate the locality property.
+(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica .
+Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings.
+This is a well-studied problem in the network community and numerous protocols have been proposed.
+As for the index, this knowledge about the topology can be either centralized[REF] or distributed[REF].
+
+%However, solutions that require to contact a remote node (either a server or a DHT node) to request this index usually violate the locality property.
 In other words, a request about a given object localization may travel far away in the network even if this object is actually close to the requester.
-Moreover, they incur a lookup penalty that increases the time to actually get the object.
+%Moreover, they incur a lookup penalty that increases the time to actually get the object.
 In fact, the lookup delay can sometimes be larger than downloading the object itself, especially for smaller objects, as already observed in~\cite{confais2017performance}.
+Finally, this may prevent accessing objects when network partitons occur, even if they are still accessible.
 
-Instead of requesting localization information from a remote node, another approach consists in disseminating this information accross the network.
+\subsection*{Index dissemination}
+In this paper, we advocate that in the Fog context, content should be accessible without having to request any remote node. 
+To do so, another approach consists in disseminating this information accross the network.
 Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}.
-Indeed, having the full knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
+Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
 Moreover, removing the lookup latency directly involves faster downloading times.
-Multiple broadcast protocols have been designed to cope with various requirements[REF], and [REF or REF].
+Multiple broadcast protocols have been designed to cope with various requirements.
 One could also solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures~\cite{shapiro2011crdts}. 
-However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventuall receive all messages. 
-That means information that might only interests a small subset of nodes is actually spread out all over the network. This is in contradiction 
-with the locality property we mentionned above.
+However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
+That means information that might only interests a small subset of nodes is actually spread out all over the network. This is in contradiction with the locality property we mentionned above.
 
@@
 Numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
-These protocols usually relies on a so-called \textit{peer-sampling service}~\cite{gossip-peer-sampling} to efficiently propagate the information.
+These protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information.
 This implies that nodes will exchange messages with random nodes in the system that can be physically far away thus violating the locality property once again.
 
-To cope with this locality requirment, we now present the intutition behind the design of our proposal.
-
-\subsection*{Logical partioning}
-At the system level, we claim that distributing the index actually boils down to logicaly partition the physical topology, depending on the current replicas localization. 
-Exemple and Figures ?
+\subsection*{Logical partitioning}
+To provide the intuition underlying our proposal, and ease the comparison with other related works, we now describe the problem tackled by this paper at an abstract level. 
+Recall that for any content, every node would be able to access its closest replica \textbf{without any prior request}.
+Suppose there exists an oracle in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas.
+In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system.
+Equipped with these two information, it is then trivial for this oracle to compute for each node, where resides its closest replica for a given content.
+Mapping each node of the topology to a single replica amounts to partition the set of all nodes into $k$ disjoint sets (or partitions), where $k$ is the number of current replicas and every node in the same partition would get the content from the same replica.
+Interestingly, this partitioning matches the physical topology as neighbors physically closed in the infrastructure will most likely reside in the same partition.
+For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event).
+The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge, contrary to the omniscient oracle.
 
 \subsection*{Overlays and membership protocols}
-At first glance, membership protocols as proposed in~\cite{t-man}[REF] would appear to provide suitable abstractions to create such a partioning. 
-BUT, usually rely on peer sampling, thus same locality problem.
+At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create such a partioning.
+Yet, such protocols usually rely on peer sampling, thus same locality problem.
 Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric. 
-On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node ar not continusously modifed. 
+On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed. 
 Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.

### 2021-04-15 input/abstract.tex

--- 2021-04-01 input/abstract.tex
@@
   %% Context and problem
-  Edge infrastructures have been proposed as an alternative to Cloud
-  Computing to provide computing and storage capabilities closer to
-  the locations where data is generated/consumed, with the objectives
-  of reducing the latency and the volume of data passing through the
-  network. A few systems have been proposed to store data in those
-  infrastructures. Unfortunately, locating the closest copy of a
-  specific content in these systems requires to keep up-to-date an index
-  of all replicas and their respective locations. While flooding
-  approaches will not enable the maintenance of such an index for each
-  node in large systems, relying on a dedicated service contradicts
-  with the properties of Edge infrastructures in terms of locality and
-  robustness (locating sources may effectively take more time than
-  actually downloading contents).
+  Although the holy grail to store and manipulate data in Edge
+  infrastructures is yet to be found, state-of-the-art approaches
+  demonstrated the relevance of replication strategies that bring
+  contents closer to consumers: The latter enjoy better response time
+  while the volume of data passing through the network decreases
+  overall.
+  %% Although, there is no major solution to store and manipulate data in
+  %% Edge infrastructures yet, existing proposals demonstrated the
+  %% relevance of appropriate replication strategies to bring contents
+  %% closer to consumers, reducing the impact of the latency as well as
+  %% the volume of data passing through the network overall.  
+  Unfortunately, locating the closest replica of a specific content
+  requires indexing \emph{every live} replica along with its
+  \emph{location}.
+  %
+  %Current proposals built on a centralized service face scalability
+  %issues, single point of failure, as well as latency penalities where
+  %locating replicas may effectively take more time than actually
+  %downloading contents. Instead, data consumer \processes must
+  %maintain an up-to-date index themselves. Unfortunately, maintaining
+  %an index of all live replicas at every \process would prove overly
+  %costly in terms of memory and generated traffic, especially in large
+  %scale dynamic systems where \processes create and destroy replicas
+  %at any time.
+  % 
+  Relying on remote services contradicts with the properties of Edge
+  infrastructures as locating replicas may effectively take more time
+  than actually downloading contents.  At the opposite, maintaining
+  such an index at every \process would prove overly costly in terms
+  of memory and traffic, especially since \processes can create and
+  destroy replicas at any time.
 
   %%% Our proposal
-  In this paper, we introduce \NAME, an efficient broadcast protocol
-  that relies on dynamic logical partitioning of the
-  infrastructure. \NAME only floods the relevant nodes (\ie the ones
-  that should be informed of a the creation of a closest copy),
-  enabling to keep up-to-date an index for each node eventually.  In
-  addition to demonstrating formally the correctness of our protocol \TODO{Is it true?},
-  we discuss several evaluatons performed by simulations and show
-  \TODO{blabla}.  While \NAME tackles our location problem, it can be
-  used as a building block to design new advanced services such as
-  \TODO{blabla}.
-
+  \noindent In this paper, we abstract content indexing as distributed
+  partitioning: every \process only indexes its closest replica, and
+  connected \processes with similar index compose a partition. Our
+  decentralized implementation \NAME
+  \begin{inparaenum}[(i)]
+  \item is efficient, for it uses partitions to lock down the traffic
+    generated by its operations, yet it
+  \item guarantees that every \process eventually acknowledges its
+    partition despite concurrent operations.
+  \end{inparaenum}
+  %% When a \node replicates a content, it notifies all \nodes (new
+  %% members of its partition) that are closer from it than any other
+  %% replica; When a \node destroys a replica, it notifies members of
+  %% its partition to switch to another closer partition. \NAME
+  %% guarantees that eventually, every \process knows its best
+  %% partition, hence its closest replica, despite concurrent
+  %% operations and receipt orders.
+  Our complexity analysis supported by simulations shows that \NAME
+  scales well in terms of generated traffic and termination time,
+  especially in dynamic Edge infrastructures. As such, \NAME could
+  constitute the building block of new advanced services such as
+  decentralized recommendation systems.
 \end{abstract}
-
-%\TODO{source automatically create
-%    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
-%    flooding}). \TODO{costs of operations.} When the system becomes
-%  quiescent, every process eventually converges to its closest
-%  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
-%+    testbed?}
 

### 2021-04-16 input/background.tex
Split section into 2 sections: 1 only about broacast, 1 related work at the end

--- 2021-03-11 input/background.tex
@@
-\section{Background and motivation}
+\section{Background and Problem Definiton}
 \label{sec:background}
 
-\TODO{More related work. More motivations etc. Maybe describe IPFS?}
+Numerous studies exist on content indexing, either being centralized or distributed (see Section\ref{related_work}). In this paper
+we advocate solutions that do not rely on requesting any remote entity before being able to access a given content. 
+Indeed, in the Fog context, requesting a remote node before accessing any content has many drawbacks as previsoulsy explained.
+This section thus focus on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
+We explain why existing implementations are costly thus preventing their deployment in real systems.
+Then, we describe the problem tackled by this paper at an abstract level to underline the challenges that drove the design of our proposal.
 
-%% \begin{definition}[Dynamic optimal partitioning]
-%%   A dynamic optimal partitioning is an optimal partitioning where the
-%%   set of sources $S$ does not monotonically increase. We suffix this
-%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
-%%   of sources by \underline{a}dding its partition with messages
-%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
-%%   leaves the set of sources by \underline{d}eleting its partition with
-%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
-%% \end{definition}
+\subsection*{Disseminate localization information}
+Enabling the accessibility of content without prior requests implies that the information about replica localization has to be pushed directly to the nodes.
+Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}.
+Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
+Moreover, removing the lookup latency directly involves faster downloading times.
+Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
+However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
+That means information that might only interests a small subset of nodes is actually spread out all over the network.
 
-%% Unfortunately, due to differences in receipt order of messages between
-%% processes, stale information may stop prematurely the propagation of
-%% relevant messages leading to inconsistent partitioning.
-%% \TODO{Figure~\ref{fig:del} shows that.}
+\subsection*{Locking down the dissemination}
+To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level. 
+Suppose there exists an oracle in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas.
+In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system.
+Equipped with these two information, it is then trivial for this oracle to compute for each node, where resides its closest replica for a given content.
+Mapping each node of the topology to a single replica amounts to partition the set of all nodes into $k$ disjoint sets (or partitions), where $k$ is the number of current replicas.
+Thus, every node in the same partition would get the content from the same replica.
+Interestingly, this partitioning matches the physical topology as neighbors physically closed in the infrastructure will most likely reside in the same partition.
+For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event).
+The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).
 
-One could solve this issue by using a conflict-free replicated data
-type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
-require eventual delivery of messages to ensure convergence. All
-processes need to receive, deliver, hence broadcast all
-operations. Some processes may receive operations unnecessary to their
-correct functioning, for these operations did not happen in their
-locality.  One could also solve this issue by removing partitions that
-were not advertised for a defined
-time~\cite{hemmati2015namebased}. \TODO{check distance-vector
-  protocols.} However, relying on physical timeout could lead to
-either premature removals of partitions when they are still operating;
-or slow convergence where processes believe they belong to a partition
-that was removed (\TODO{plot ?}). In addition, since timeouts imply a
-continuous maintenance of partitions, such partitioning protocol
-incurs an overhead even in quiet contexts without dynamic partitions.
-
-%% \begin{problem}[\label{prob:intra}Consistent partitioning]
-%%   How to enable \emph{consistent} dynamic optimal partitioning in
-%%   dynamic network using scoped flooding?
-%% \end{problem}
-
-% \TODO{Dynamic Multiple-sources All-destinations shortest path on
-%  dynamic graphs?}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \input{input/figASmotivation.tex}
-%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
-%%       objects, processes do not know about all partitions that exist
-%%       in the whole distributed system.}
-%%   \end{center}
-%% \end{figure}
-
-%% To further improve scoped flooding in autonomous systems, processes
-%% may belong to multiple partitions representing the objects they are
-%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
-%% nature of autonomous systems. Autonomous systems have topological
-%% properties~\cite{nur2018geography} that processes can leverage to
-%% avoid flooding the whole systems with control information about all
-%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
-%% partition about a specific object, flooding Paris's AS to notify
-%% neighboring processes of the object. However, it does not flood the
-%% whole network, for control information stops at Process $b$. It
-%% significantly saves bandwidth compared to broadcast since processes
-%% below entrypoints of autonomous systems are order of magnitude more
-%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
-%% to return an object they are unaware of. Processes remain efficient in
-%% answering requests. \TODO{which is important for end users \REF.}
-
-%% \begin{definition}[Partitions in asynchronous systems]
-%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
-%%   \TODO{TODO} \TODO{or multi-partitioning?}
-%% \end{definition}
-
-%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
-%%   How to enable scoped flooding of objects in autonomous systems?
-%% \end{problem}
-
-%% Next Section presents our approach that solves these scientific
-%% problems by relying on logical control information only.
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "../paper"
-%%% ispell-local-dictionary: "english"
-%%% End:
+Finally, we emphasize that information about a given replica localization should remain in a given geographical scope. 
+Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.
+This prevents the use of gossip protocols for example.
+Indeed, gossip protocols are also appealing candidates to disseminate information reliably across a network~\cite{epidemic-protocol} and numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
+However, these protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information.
+This implies that nodes will exchange messages with random nodes in the system far exceeding the geograhical scope.

### 2021-04-16 input/related_work.tex
add related work section

\section{Related Work}
\label{related_work}

In the context of this paper, an \textit{ideal} content indexing service would enable that for any content, every node would be able to access its closest replica.
Basically, offering such a service would require (i) to have access to the list, namely the \textit{index}, of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location. We review the existing solutions

(i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}. However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in a Fog context.
Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example. In the latter, each node stores a part of the index, defined by an interval between hash values. 
Before downloading any object, a node first
hashes the content to obtain the address of the node that stores the replica localizations of this given object. After obtaining from the remote node the list of available replicas, it can select the closest copy to download from. We emphasize that, in this setting, the DHT only stores information about replicas localizations, not the content itself. DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.

(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica . Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings. This is a well-studied problem in the network community and numerous protocols have been proposed. As for the index, this knowledge about the topology can be either centralized[REF] or distributed[REF].

However, solutions that require to contact a remote node (either a server or a DHT node) to request this index usually implies reaching nodes out of the their geographical scope, as already explained.
At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create a scope-related partioning, as proposed in this paper. Yet, such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology. Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric. 
On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed. Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.
Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica. This enables for a request to be caught \textit{on-path}, and be redirected to the closest replica. However, the announcement is only performed towards this original replica, that is requests can miss closer replicas that are not on this path, thus decreasing the efficiency of the cache sharing mechanism.

%AVK: This should go where we explain the DEL, as this is really specific...
%One could also solve this issue by removing partitions that were not advertised for a defined time~\cite{hemmati2015namebased, garcia-lopez}. 
%However, relying on physical timeout could lead to either premature removals of partitions when they are still operating; or slow convergence where processes believe they belong to a partition that was removed (\TODO{plot ?}). In addition, since timeouts imply a
%continuous maintenance of partitions, such partitioning protocol
%incurs an overhead even in quiet contexts without dynamic partitions.

% AVK
% t-man: T-Man: Gossip-Based Overlay Topology Management5doat a random time 
% at a random time once in eachconsecutive interval of T time unit
% This buffer contains a random sample of the nodes from the entirenetwork. It is provided by apeer sampling service
% 
% We do not try to to create a topology aware overlay ! Because locality.
% We do not provide routing ! routing is two determine path between any pair of nodes. We only provide path to objects 
% 
% Koala locality aware routing. Long links. Lazzy (nothing happens)
% Koala  shares  many  core  aspectswith similar overlays, such as Chord and Symphony.
% 
% VoroNet: overlay and routing. i.e. long links 
% It links application objects rathen than physical nodes so that objects with similar characteristic are neighbors. 
% are logigal overlay, that are not correlated to the physical infrstructure. 
% Usually rely on long links...
% AVK

%% \begin{definition}[Dynamic optimal partitioning]
%%   A dynamic optimal partitioning is an optimal partitioning where the
%%   set of sources $S$ does not monotonically increase. We suffix this
%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
%%   of sources by \underline{a}dding its partition with messages
%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
%%   leaves the set of sources by \underline{d}eleting its partition with
%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
%% \end{definition}

%% Unfortunately, due to differences in receipt order of messages between
%% processes, stale information may stop prematurely the propagation of
%% relevant messages leading to inconsistent partitioning.
%% \TODO{Figure~\ref{fig:del} shows that.}
% 
% One could solve this issue by using a conflict-free replicated data
% type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
% require eventual delivery of messages to ensure convergence. All
% processes need to receive, deliver, hence broadcast all
% operations. Some processes may receive operations unnecessary to their
% correct functioning, for these operations did not happen in their
% locality.  One could also solve this issue by removing partitions that
% were not advertised for a defined
% time~\cite{hemmati2015namebased}. \TODO{check distance-vector
%   protocols.} However, relying on physical timeout could lead to
% either premature removals of partitions when they are still operating;
% or slow convergence where processes believe they belong to a partition
% that was removed (\TODO{plot ?}). In addition, since timeouts imply a
% continuous maintenance of partitions, such partitioning protocol
% incurs an overhead even in quiet contexts without dynamic partitions.

%% \begin{problem}[\label{prob:intra}Consistent partitioning]
%%   How to enable \emph{consistent} dynamic optimal partitioning in
%%   dynamic network using scoped flooding?
%% \end{problem}

% \TODO{Dynamic Multiple-sources All-destinations shortest path on
%  dynamic graphs?}

%% \begin{figure}
%%   \begin{center}
%%     \input{input/figASmotivation.tex}
%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
%%       objects, processes do not know about all partitions that exist
%%       in the whole distributed system.}
%%   \end{center}
%% \end{figure}

%% To further improve scoped flooding in autonomous systems, processes
%% may belong to multiple partitions representing the objects they are
%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
%% nature of autonomous systems. Autonomous systems have topological
%% properties~\cite{nur2018geography} that processes can leverage to
%% avoid flooding the whole systems with control information about all
%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
%% partition about a specific object, flooding Paris's AS to notify
%% neighboring processes of the object. However, it does not flood the
%% whole network, for control information stops at Process $b$. It
%% significantly saves bandwidth compared to broadcast since processes
%% below entrypoints of autonomous systems are order of magnitude more
%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
%% to return an object they are unaware of. Processes remain efficient in
%% answering requests. \TODO{which is important for end users \REF.}

%% \begin{definition}[Partitions in asynchronous systems]
%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
%%   \TODO{TODO} \TODO{or multi-partitioning?}
%% \end{definition}

%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
%%   How to enable scoped flooding of objects in autonomous systems?
%% \end{problem}

%% Next Section presents our approach that solves these scientific
%% problems by relying on logical control information only.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-04-16 input/abstract.tex
small fix in abstract

@@
   \item is efficient, for it uses partitions to lock down the traffic
-    generated by its operations, yet it
+    generated by its operations to relevant \processes, yet it
   \item guarantees that every \process eventually acknowledges its
@@
   especially in dynamic Edge infrastructures. As such, \NAME could
-  constitute the building block of new advanced services such as
-  decentralized recommendation systems.
+  constitute the building block of new geo-distributed services.
 \end{abstract}

### 2021-04-16 input/figaddA.tex
meow

@@
 
-  \draw (-\X + 5pt, 0) -- (0 - 5pt, 0); %% a - b
+  \draw (-\X + 5pt, 0) --
+  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{2}
+  (0 - 5pt, 0); %% a - b
 
-  \draw (0 +5pt, 0) -- (\X -5pt, 0); %% b - c
+  \draw (0 +5pt, 0) --
+  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{1}
+  (\X -5pt, 0); %% b - c
 
-  \draw (0, 0 - 5pt) -- (0, \Y + 5pt); %% d - b
+  \draw (0, 0 - 5pt) --
+  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{1}
+  (0, \Y + 5pt); %% d - b
 
-  \draw (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d
+  \draw (\X + 3pt, 0 - 5pt) --
+  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{3}
+  (0 + 5pt, \Y - 3pt); %% c - d
 

### 2021-04-16 input/proposal.tex
meow

@@
 
-\begin{definition}[Fog infrastructure]
-  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
+\begin{definition}[Edge infrastructure]
+  An edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
@@
 
-\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
+\begin{corollary}[\label{theo:dcp}\underline{D}ynamic \underline{c}onsistent
+    \underline{p}artitioning (DCP)]
   Consistent partitioning where each \process can \texttt{Add} and
@@
 
-Algorithm~\ref{algo:adddelundo} provides the instructions that
+Algorithm~\ref{algo:ascast} provides the instructions that
 implement dynamic consistent partitioning:
@@
 \begin{algorithm}
-  \input{input/algoadddelundo.tex}
-  \caption{\label{algo:adddelundo}Dynamic partitioning by \Process $p$.}
+  \input{input/algoascast.tex}
+  \caption{\label{algo:ascast}\NAME at \Process $p$ in static networks.}
 \end{algorithm}
@@
 and cannot rely on local counters to
-operate. Algorithm~\ref{algo:adddelundo} implements this behavior by
+operate. Algorithm~\ref{algo:ascast} implements this behavior by
 piggybacking paths in messages. Paths guarantee that such $\delta$
@@
   \input{input/algoedges.tex}
-  \caption{\label{algo:edges}Dynamic partitioning by \Process $p$ in dynamic networks.}
+  \caption{\label{algo:edges}\NAME at \Process $p$ in dynamic networks.}
 \end{algorithm}
@@
 
-\vfill
-
-\TODO{spacing}
-
-\newpage
-
 \subsection{Complexity}

### 2021-04-19 input/experiments.tex
meow
small improvements everywhere

@@
+\vfill
+
+\TODO{spacing}
+
+\newpage
+
 \section{Experimentation}
@@
 This section aims at highlighting the properties of \NAME that enables
-adaptive scoped broadcast in dynamic networks. Most importantly, it
-aims at answering the following questions: Does \NAME allows the
-system to reach consistent partitioning? Does \NAME scales well in
-large networks? Does \NAME improves scoped broadcast in
-inter-autonomous systems? \TODO{Rework this.} We performed the
-experimentation using PeerSim, a simulator written in Java that allows
-researchers to evaluate and assess distributed algorithms in large
-scale networks~\cite{montresor2009peersim}. The code is available on
-the Github platform at
-\url{https://github.com/Chat-Wane/peersim-partition}.\TODO{Anonoymous.}
+adaptive scoped broadcast in dynamic networks. It answers the
+following questions: What is the overhead of reaching consistent
+partitioning using \NAME in large scale networks? Does \NAME is
+relevant in Edge infrastructures where \processes are geo-distributed
+into clusters? We performed the experimentation using PeerSim, a
+simulator written in Java that allows researchers to evaluate and
+assess distributed algorithms in large scale
+networks~\cite{montresor2009peersim}. The code is available on the
+Github platform at
+\TODO{\url{https://github.com/Chat-Wane/peersim-partition}}.
 
@@
 
-\begin{figure}
-  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
-  \caption{\label{fig:complexity}Overhead of consistent partitioning
-    using \NAME.}
-  %% \caption{\label{fig:complexity}Cumulative average number of messages
-  %%   per process in a network comprising 10k processes; along with the
-  %%   duration before reaching consistent partitioning after adding or
-  %%   removing a partition, totaling 100 new partition then removed.}
-\end{figure}
-
 \item [Results:]
@@
 the competition is already partially triggered and propagating.
+
+\begin{figure}
+  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
+  \caption{\label{fig:complexity}Overhead of consistent partitioning
+    using \NAME.}
+  %% \caption{\label{fig:complexity}Cumulative average number of messages
+  %%   per process in a network comprising 10k processes; along with the
+  %%   duration before reaching consistent partitioning after adding or
+  %%   removing a partition, totaling 100 new partition then removed.}
+\end{figure}
 

### 2021-04-19 input/proposal.tex
small improvements everywhere

@@
 
-\begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \implies CP$]
+\begin{theorem}[\label{theo:bef}\underline{B}est \underline{e}ventual
+    \underline{f}orwarding $(BEF) \implies CP$]
+%
 Assuming reliable communication links where a correct \process $q$
 eventually receives the message $m$ \underline{s}ent to it by a
-  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a monotonically
-  growing system ($G^t \subseteq G^{t+1}$); \processes eventually
-  reach consistent partitioning if each \process eventually forwards
-  its best known partition.
+\process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a monotonically growing
+system ($G^t \subseteq G^{t+1}$); \processes eventually reach
+consistent partitioning if each \process eventually forwards its best
+known partition.
 \end{theorem}
@@
 does not improve its partition distance. \Processes $c$ and $d$ will
-never hear of Source~$a$. Ultimately, \processes discard last
-transiting messages. Despite the obvious lack of traffic optimization,
-the system reach consistent partitioning.
+never acknowledge that Source~$a$ exists. Ultimately, \processes
+discard last transiting messages. Despite the obvious lack of traffic
+optimization, the system reach consistent partitioning.
 
@@
 
-At any time, a \process can become a source, hence adding a new
-partition to the system. This partition eventually includes all
-\processes that are closer from this new source than any other
-else. \Processes naturally converge towards their respective best
-partition by only piggybacking a monotonically increasing distance in
-forwarded messages.
+%% At any time, a \process can become a source, hence adding a new
+%% partition to the system. This partition eventually includes all
+%% \processes that are closer from this new source than any other
+%% else. \Processes naturally converge towards their respective best
+%% partition by only piggybacking a monotonically increasing distance in
+%% forwarded messages.
 
@@
 
-\texttt{Del}ete operations add a new notion of order between events,
-and most importantly between message deliveries. Delete operations
-implicitly state that all preceding events become obsolete, and that
-all messages originating from these preceding events convey stale
-control information.
+Delete operations add a new notion of order between events, and most
+importantly between message deliveries. Delete operations implicitly
+state that all preceding events become obsolete, and that all messages
+originating from these preceding events convey stale control
+information.
 
@@
 
-\begin{definition}[Last win order]
+\begin{definition}[\label{def:lwo}Last win order]
   When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
@@
 
-Unfortunately, stale control information about deleted partitions may
-impair the propagation of both
+Unfortunately, stale control information as stated in
+Definition~\ref{def:lwo} may impair the propagation of both
 \begin{inparaenum}[(i)]
 \item notifications about actual sources, and
-\item notifications about other deleted partitions.
+\item notifications about deleted partitions.
 \end{inparaenum}
@@
 partition, but also related to partitions they belong to in the
-past. Instead, we propose to use the delivery order at each \process
-to detect possible inconsistencies and solve them. Together,
+past. This would prove overly expensive in dynamic systems where
+\processes join or leave the system, create or delete partitions, at
+any time. Instead, we propose to use the delivery order at each
+\process to detect possible inconsistencies and solve them. Together,
 \processes eventually remove all stale control information (transiting
@@
   \Processes deliver and forward the best sum of weights they
-  received. The only case where a \process would block such epidemic
-  propagation would be when it received and delivered a message from a
-  partition that has since then been deleted but with a better sum of
-  weights than newly received ones. Removing \emph{forever} all such
-  stale messages about deleted partitions would allow \processes to
-  propagate their best up-to-date partition again, eventually reaching
-  consistent partitioning together.
+  received. Figure~\ref{fig:proofA} depicts the only case where a
+  \process would block such epidemic propagation: the \process
+  received and delivered a message from a partition that has since
+  then been deleted but with a better sum of weights than newly
+  received ones. Removing \emph{forever} all such stale messages about
+  deleted partitions would allow \processes to propagate their best
+  up-to-date partition again, eventually reaching consistent
+  partitioning together, as stated by Theorem~\ref{theo:bef}.
 \end{proof}

### 2021-04-19 input/figproofA.tex
preparing
reworkd figure

@@
 
-  \newcommand\X{70pt}
-  \newcommand\Y{-40pt}
+  \newcommand\X{95pt}
+  \newcommand\Y{-50pt}
 
@@
 
-  \draw[opacity=0] (-1.5*\X, 0) -- (1.5*\X, 0);
+  \draw[opacity=0] (-1.2*\X, 0) -- (1.2*\X, 0);
 
-  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I
+  \draw[->] (-1.15*\X, 0) -- (-5pt + -1*\X, 0); \draw[dotted] (-1.25*\X, 0) -- (-1.15*\X, 0);
+  \draw (5pt + \X, 0) -- (1.15*\X, 0); \draw[dotted,->] (1.15*\X, 0) -- (1.25*\X, 0);
 
-  \draw[->] (-\X + 5pt, 0) --
-  node[above, color=\PA, font=\small]{$\ADD_a^1$}
+  \draw[<->] (5pt - \X, 0.4*\Y) -- node[below, font=\small]{\textbf{I: propagation}} (-5pt, 0.4*\Y); %% I
+
+  \draw[->] (-\X + 5pt, 0)
+  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PA}{\ADD_a^{x'}} \rightarrow$}
+  --
   (0 - 5pt, 0); %% a - b
 
-  \draw[<->] (-5pt, 5pt -\Y) -- node[above]{II} (5pt + \X, 5pt -\Y); %% II
+  \draw[<->] (5pt, 0.4*\Y) -- node[below, align=center, font=\small]{\textbf{II: need purge}\\with I', III, IV} (-5pt + \X, 0.4*\Y); %% II
   \draw[->] (0 + 5pt, 0) -- (-5pt +  \X, 0); %% b - c
 
-  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
-  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (-\X, 0) node[color=\PA]{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
+  \draw[fill=white] (0, 0) node[color=\PD]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
   \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
-  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
-  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_d^{0.5}$};
-  \draw (\X,-5pt) node[below, font=\scriptsize]{expect \textcolor{\PA}{$\alpha_a$}};
-  \draw (0, -5pt) node[below, font=\scriptsize]{expect $\textcolor{\PC}{\DEL_d} \rightarrow \textcolor{\PA}{\alpha_a}$};
+  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^x$};
+  \draw ( 0, 5pt) node[above]{$
+    \xrightarrow[\textcolor{\PD}{\ADD_d^y}]{\mbox{\small{last}}}
+    \xrightarrow[\DEL_d \rightarrow \textcolor{\PA}{\ADD_a^{x'}}]{\mbox{\small{expect}}}$};
+
+  \draw (-5pt, 0pt) node [below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\ADD_d^y < \ADD_a^{x'}}$};
+  % \draw (-5pt, 0pt) node [below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\ADD_d^{y} < \ADD_e^z}$};
+
+  \draw (\X, 5pt) node[above]{$
+    \xrightarrow[\textcolor{\PA}{\ADD_a^{x''}}]{\mbox{\small{expect}}}$};
+%  \draw (0, -5pt) node[below, font=\scriptsize]{expect $\DEL_d \rightarrow \textcolor{\PA}{\ADD_a}$};
+
+  \draw[->] (-\X,  0.5*\Y) -- (-\X, -5pt);
+  \draw[dotted] (-\X,  0.5*\Y) -- (-\X, 0.9*\Y);
+
+  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
+  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below, font=\scriptsize]{somewhere: $\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
+
+  \draw[->] ( \X,  0.5*\Y) -- ( \X, -5pt);
+  \draw[dotted] ( \X,  0.5*\Y) -- ( \X, 0.9*\Y);
 

### 2021-04-19 input/figproofB.tex
reworkd figure

@@
   \newcommand\X{85pt}
-  \newcommand\Y{-40pt}
+  \newcommand\Y{-50pt}
 
@@
 
-  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I': propagation} (5pt, -\Y); %% I as well
-  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small]{$\DEL_d$} (0 - 5pt, 0); %% d - e
+  \draw[->] (-1.15*\X, 0) -- (-5pt + -1*\X, 0); \draw[dotted] (-1.25*\X, 0) -- (-1.15*\X, 0);
+  \draw (5pt + 2*\X, 0) -- (2.15*\X, 0); \draw[dotted,->] (2.15*\X, 0) -- (2.25*\X, 0);
 
-  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{III: detection} (5pt + \X, 5pt -\Y); %% IV
-  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'
+  \draw[<->] (5pt - \X, 0.4*\Y) --
+  node[below, font=\small]{\textbf{I': propagation}}
+  (-5pt, 0.4*\Y); %% I as well
 
-  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{IV: propagation} (5pt + 2*\X, 10pt -\Y); %% V
+  \draw[->] (-\X + 5pt, 0)
+  node[below=-0.3em, below right, font=\scriptsize]{$\DEL_d \rightarrow$}
+  -- (0 - 5pt, 0)
+  node [below=-0.15em, below left, font=\tiny]{$\textcolor{\WRONG}{d \neq f}$}
+  ; %% d - e
+
+  \draw[<->] (5pt , 0.4*\Y) --
+  node[below, font=\small]{\textbf{III: detection}}
+  (-5pt + \X, 0.4*\Y); %% IV
+
+  \draw[->] (0 +5pt, 0)
+  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PF}{\ADD_f^{z'}} \rightarrow$}
+  --
+  (\X -5pt, 0)
+  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_f \not\rightarrow \ADD_f^{z'}}$}
+  ; %% e - b'
+
+  \draw[<->] (5pt +\X , 0.4*\Y) --
+  node[below, font=\small]{\textbf{IV: propagation}}
+  (-5pt + 2*\X, 0.4*\Y); %% V
+
   \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''
@@
   \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
-  \draw[fill=white] (0, 0) node{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (\X, 0) node{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (2*\X, 0) node{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, 0) node[color=\PF]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (2*\X, 0) node[color=\PD]{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
-  \draw (-\X, 5pt) node[above]{$\DEL_d$};
+  \draw (-\X, 5pt) node[above]{$\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
 
-  \draw ( 0, 5pt) node[above]{$\textcolor{\PC}{\ADD_d} \rightarrow \textcolor{\WRONG}{\ADD_f^{0.5}}$};
-  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\DEL_f$};
+  \draw ( 0, 5pt) node[above, font=\footnotesize]{$
+    \xrightarrow[\textcolor{\PC}{\ADD_d^{\vphantom{z'}}}]{\mbox{\scriptsize{before}}}
+    \xrightarrow[\textcolor{\PF}{\ADD_f^{z\vphantom{'}}}]{\mbox{\scriptsize{last}}}
+    \xrightarrow[\DEL_f^{\vphantom{z'}} ]{\mbox{\scriptsize{expect}}}$};
 
-  \draw ( \X, 5pt) node[above]{$\textcolor{\PB}{\ADD_f^1} \rightarrow \DEL_f \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
-  \draw ( \X, -5pt) node[below, font=\footnotesize]{expect $\DEL_d$ or $\DEL_d^{0.5}$};
+  \draw ( \X, 5pt) node[above, font=\footnotesize]{$
+    \xrightarrow[\textcolor{\PF}{\ADD_f^{\vphantom{y'}}} \rightarrow \DEL_f]{\mbox{\scriptsize{before}}}
+    \xrightarrow[\textcolor{\PC}{\ADD_d^{y'}}]{\mbox{\scriptsize{last}}}
+    \xrightarrow[\DEL_d^{\vphantom{z'}}?]{\mbox{\scriptsize{expect}}}$};
 
-  \draw (2*\X, 5pt) node[above]{$\textcolor{\PC}{\ADD_d^{1.5}}$};
-  \draw (2*\X, -5pt) node[below, font=\footnotesize]{expect $\DEL_d$ or $\DEL_d^{1.5}$};
+  \draw (2*\X, 5pt) node[above, font=\footnotesize]{$
+    \xrightarrow[\textcolor{\PC}{\ADD_d^{y''}}]{\mbox{\scriptsize{last}}}
+    \xrightarrow[\DEL_d^{\vphantom{y'}}?]{\mbox{\scriptsize{expect}}}$};
+
+  \draw[->] (-\X,  0.5*\Y) -- (-\X, -5pt);
+  \draw[dotted] (-\X,  0.5*\Y) -- (-\X, 0.9*\Y);
+
+  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
+  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below right, font=\scriptsize]{somewhere: $\textcolor{\PF}{\ADD_f} \rightarrow \DEL_f$};
+
+  \draw[->] ( \X,  0.5*\Y) -- ( \X, -5pt);
+  \draw[dotted] ( \X,  0.5*\Y) -- ( \X, 0.9*\Y);
+
+  \draw[->] (2*\X,  0.5*\Y) -- (2*\X, -5pt);
+  \draw[dotted] (2*\X,  0.5*\Y) -- (2*\X, 0.9*\Y);
 

### 2021-04-20 input/background.tex
small fixes in background and related work

@@
 
-Numerous studies exist on content indexing, either being centralized or distributed (see Section\ref{related_work}). In this paper
-we advocate solutions that do not rely on requesting any remote entity before being able to access a given content. 
-Indeed, in the Fog context, requesting a remote node before accessing any content has many drawbacks as previsoulsy explained.
-This section thus focus on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
+Numerous studies exist on content indexing, with solutions being either centralized or distributed (see Section\ref{related_work}).
+As explained above, in this paper we advocate designs that do not rely on requesting any remote entity before being able to access a given content.
+This section thus focuses on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
 We explain why existing implementations are costly thus preventing their deployment in real systems.
@@
 Moreover, removing the lookup latency directly involves faster downloading times.
-Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
+Similarly, one could solve this issue by using a conflict-free replicated datatype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
 However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
@@
 \subsection*{Locking down the dissemination}
-To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level. 
-Suppose there exists an oracle in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas.
+To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level, and explain how an (imaginary) omniscient entity could solve it. 
+In this way, suppose there exists an \textit{oracle} in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas.
 In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system.
@@
 
-Finally, we emphasize that information about a given replica localization should remain in a given geographical scope. 
+Moreover, we emphasize that information about a given replica localization should remain in a given geographical scope. 
 Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.
@@
 However, these protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information.
-This implies that nodes will exchange messages with random nodes in the system far exceeding the geograhical scope.
+This implies that nodes will exchange messages with random nodes in the system far exceeding their geograhical scope.

### 2021-04-20 input/related_work.tex
small fixes in background and related work

@@
 
-In the context of this paper, an \textit{ideal} content indexing service would enable that for any content, every node would be able to access its closest replica.
-Basically, offering such a service would require (i) to have access to the list, namely the \textit{index}, of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location.
-We review the existing solutions
+In the context of this paper, a content indexing service enables that for any content, every node is able to access its closest replica.
+Basically, offering such a service requires (i) to have access to the list of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location.
 
 (i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
-However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in a Fog context.
+However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
 Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example.

### 2021-04-20 input/figproof.tex
issue depiction
purging

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop
-      other $\alpha$'s from reaching all processes ($b$ and $c$) that
-      require it along the shortest path. Hence, we must guarantee
-      eventual purging of stale $\alpha$'s (see
+    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$ messages may
+      stop other $\alpha$ messages from reaching all \processes ($b$
+      and $c$) that require it along the shortest path. Consistent
+      partitioning requires eventual purging of stale messages (see
       Figure~\ref{fig:proofB}).]  {\input{input/figproofA.tex}}
     \hspace{10pt}
-    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may
-      stop $\delta$'s from reaching
-      processes with targeted $\alpha$'s.
-      To ensure consistent partitioning, $b'$ and $b''$
-      must remove $\alpha_{d}$ either by delivering $\delta_d$,
-      or a more specific $\delta_d^{0.5}$ and $\delta_d^{1.5}$ respectively.]
+    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$ messages may
+      stop $\delta$ messages from reaching processes with the corresponding
+      partition. Consistent partitioning requires that all \processes propagate
+      $\delta$ messages as often as possible (I'); detect possible inconsistencies
+      when parents' $\alpha$ messages contradict delivery history (III); notify
+      processes of possible inconsistencies (IV).]
     {\input{input/figproofB.tex}}
-    \caption{\label{fig:proof}Dynamic partitioning leads to correctness issues due to
-      staleness and ordering of operations.}
+    \caption{\label{fig:proof}Concurrent operations,
+      delivery orders, and stale control information may impair
+      consistent partitioning. Dynamic consistent partitioning
+      requires eventual purging of stale messages, and best eventual
+      forwarding.}
   \end{center}
 \end{figure*}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "../paper"
+%%% ispell-local-dictionary: "english"
+%%% End:

### 2021-04-20 input/proposal.tex
purging

@@
 
-At any time, a \process can decide to become a source, hence creating a
-new partition in the system by executing an \texttt{Add}
+At any time, a \process can decide to become a source, hence creating
+a new partition in the system by executing an \texttt{Add}
 operation. This partition includes at least its source plus
@@
 application-dependant: in the context of maintaining distributed
-indexes, weights are latency.
-
-%For instance, weights could be latency in live
-% streaming applications, or differences in profiles for recommendation
-%systems.
+indexes, weights would be link latency.
 
@@
 
-\begin{corollary}[\label{theo:dcp}\underline{D}ynamic \underline{c}onsistent
+\begin{corollary}[\label{theo:dcp}purge + BEF $\implies$
+    \underline{D}ynamic \underline{c}onsistent
     \underline{p}artitioning (DCP)]
-  Consistent partitioning where each \process can \texttt{Add} and
-  \texttt{Del}ete its partition at any time requires
+%
+When each \process can \texttt{Add} and \texttt{Del}ete its partition
+at any time, consistent partitioning requires
 \begin{inparaenum}[(i)]
-  \item eventual purging of stale notifications, and
-  \item eventual delivery of bests partitions.
+\item eventual purging of stale messages ($b_p(m) \rightarrow b_p(m')
+  \implies \eventually (d_q(m) \implies d_q(m) \rightarrow
+  d_q(m''))$);
+\item and best eventual forwarding.
 \end{inparaenum}
@@
   then been deleted but with a better sum of weights than newly
-  received ones. Removing \emph{forever} all such stale messages about
-  deleted partitions would allow \processes to propagate their best
-  up-to-date partition again, eventually reaching consistent
+  received ones (in the example $\alpha_d^y <
+  \alpha_a^{x'}$). Removing \emph{forever} all such stale messages
+  about deleted partitions would allow \processes to propagate their
+  best up-to-date partition again, eventually reaching consistent
   partitioning together, as stated by Theorem~\ref{theo:bef}.
@@
 
-Figure~\ref{fig:proof} depicts the issues with staleness and message
-orderings. In Figure~\ref{fig:proofA}, the shortest path from any
-source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
-a stale $\alpha_d^{0.5}$ without knowing. When it receives
-$\alpha_a^1$, it discards it, for it assumes that downstream \processes
-are more interested in $\alpha_d^{0.5}$. To reach consistent
-partitioning, \Process $b$ first needs to purge its current partition
-to later accept that of its current actual shortest path:
-$\alpha_a^1$.
+%% Figure~\ref{fig:proof} depicts the issues with staleness and message
+%% orderings. In Figure~\ref{fig:proofA}, the shortest path from any
+%% source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
+%% a stale $\alpha_d^{0.5}$ without knowing. When it receives
+%% $\alpha_a^1$, it discards it, for it assumes that downstream \processes
+%% are more interested in $\alpha_d^{0.5}$. To reach consistent
+%% partitioning, \Process $b$ first needs to purge its current partition
+%% to later accept that of its current actual shortest path:
+%% $\alpha_a^1$.
 
-\noindent Figure~\ref{fig:proofB} shows that removing stale control
-information is even more complex. The removal must reach all \processes
-of the previous shortest path going from $d$ to $b''$. Label I' shows
-the most obvious issue where \Process $e$ changed partition for a
-better but stale $\alpha_f$. Since it can remember its previous
-deliveries, it could still forward $\delta_d$ for the sake of
-consistency. However, this would lead to every \process forwarding
-every $\delta$ they ever delivered. Such protocol's overhead would
-depend on past partitioning instead of current one. Label III shows
-the issue when the blocking partition is already known to be stale at
-\Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
-$e$. However, it cannot deliver it, for it would break last win order.
-\Process $b'$ may be in an inconsistent state. Label IV shows the
-corollary issue: \Process $b''$ delivered a message from a \process that
-may be inconsistent without knowing it.
+%% \noindent Figure~\ref{fig:proofB} shows that removing stale control
+%% information is even more complex. The removal must reach all \processes
+%% of the previous shortest path going from $d$ to $b''$. Label I' shows
+%% the most obvious issue where \Process $e$ changed partition for a
+%% better but stale $\alpha_f$. Since it can remember its previous
+%% deliveries, it could still forward $\delta_d$ for the sake of
+%% consistency. However, this would lead to every \process forwarding
+%% every $\delta$ they ever delivered. Such protocol's overhead would
+%% depend on past partitioning instead of current one. Label III shows
+%% the issue when the blocking partition is already known to be stale at
+%% \Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
+%% $e$. However, it cannot deliver it, for it would break last win order.
+%% \Process $b'$ may be in an inconsistent state. Label IV shows the
+%% corollary issue: \Process $b''$ delivered a message from a \process that
+%% may be inconsistent without knowing it.
 
-\begin{theorem}[Propagation $+$ detection $\implies$ DCP]
-  % Propagating 
-  \TODO{Puring stale notifications requires to handle I...IV.}
+\begin{theorem}[Propagations $+$ detection $\implies$ purge]
+  \Processes can purge stale control information by broadcasting a
+  dedicated notification message $\delta$, and detect possible
+  inconsistencies using their history to propagate 
 \end{theorem}
@@
 \begin{proof}
-  \TODO{Meow meow meow.}
-  \TODO{Label I: default propagation to what seems the border of the partition but isn't.}
-  \TODO{Label II: gates eventually break because of I', III, IV.}
-  \TODO{Label I': as Label I.}
-  \TODO{Label III: detecting possible inconsistent partitioning.}
-  \TODO{Label IV: propagation of this issue to all and only concerned parties.}
+  Figure~\ref{fig:proofB} depicts all possible cases that need
+  appropriate purging. A chain of \processes $[d, e, b', b'']$
+  delivered and forwarded a message $\alpha_d$. Some \processes may
+  have delivered messages about other partitions before or after
+  $\alpha_d$.
+  \begin{asparadesc}
+  \item [\processes with last $\alpha_d$:] \Processes such as
+    \Process~$d$ where the last and best partition is still $P_d$. By
+    propagating from process to process the corresponding $\delta_d$
+    message, these \processes purge $\alpha_d$.
+  \item [\processes with $\alpha_d^y \rightarrow \alpha_f^z$ with last
+    $\alpha_f^z$, for $\alpha_f^z < \alpha_d^y$:] \Processes such as
+    \Process~$e$ do not directly suffer from the non-delivery of
+    $\delta_d$. They need to purge their own $P_f$ if need
+    be. Nonetheless, they deliver and forward $\alpha_f$ that at least
+    one following \process will receive:
+  \item [\processes with $\delta_f \rightarrow \alpha_d$:] \Processes
+    such as \Process~$b'$ do not belong to the preceding category, for
+    they already delivered $\delta_f$. However, best eventual
+    forwarding guarantees that they receive $\alpha_f$ that
+    contradicts their history or state. In such case, the detecting
+    \processes purge their own $\alpha_d$. The detecting \processes
+    must also notify subsequent \processes that their current
+    partition \emph{may be} deleted, for their parent may have blocked
+    the corresponding $\delta$ messages. We note such notification
+    $\delta_d?$ to emphasize the uncertainty of a $\delta$ message.
+  \item [\processes with last $\alpha_d$ receiving $\delta_d?$ from
+    their parent:] \Processes such as \Process~$b''$ have $\alpha_d$
+    and preceding delivered messages have not importance. Such
+    \processes must trust detecting \processes by delivering and
+    forwarding $\delta_d?$. Messages are subject to all aforementioned
+    blocking conditions, but are also solved by aforementioned
+    mechanisms.
+  \end{asparadesc}
+
+  Propagation I' terminates: a process do not deliver a $\delta$
+  message if it has already delivered it. Propagation IV terminates: a
+  process do not deliver a looping message.  Propagation and detection
+  ensure that \processes eventually purge stale $\alpha$ messages from
+  the system, leaving room for Propagation I.
+  %% In the meantime, \processes that still belong to a partition can
+  %% propagate their respective last $\alpha$ message, and reach
+  %% consistent partitioning.
 \end{proof}

### 2021-04-20 input/figproof.tex
about proof, about implementation, merge complexity and implementation

@@
       $\delta$ messages as often as possible (I'); detect possible inconsistencies
-      when parents' $\alpha$ messages contradict delivery history (III); notify
+      when parents' $\alpha$ messages contradict delivery history or state (III); notify
       processes of possible inconsistencies (IV).]

### 2021-04-20 input/figproofB.tex
purging
about proof, about implementation, merge complexity and implementation

@@
   \draw[->] (0 +5pt, 0)
-  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PF}{\ADD_f^{z'}} \rightarrow$}
+  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PH}{\ADD_h^{z'}} \rightarrow$}
   --
   (\X -5pt, 0)
-  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_f \not\rightarrow \ADD_f^{z'}}$}
-  ; %% e - b'
+  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_h \not\rightarrow \ADD_h^{z'}}$}
+  ; %% e - f
 
@@
 
-  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''
+  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - g
 
   \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
-  \draw[fill=white] (0, 0) node[color=\PF]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (2*\X, 0) node[color=\PD]{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0, 0) node[color=\PH]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{f}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (2*\X, 0) node[color=\PD]{$\bm{g}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
 
@@
     \xrightarrow[\textcolor{\PC}{\ADD_d^{\vphantom{z'}}}]{\mbox{\scriptsize{before}}}
-    \xrightarrow[\textcolor{\PF}{\ADD_f^{z\vphantom{'}}}]{\mbox{\scriptsize{last}}}
-    \xrightarrow[\DEL_f^{\vphantom{z'}} ]{\mbox{\scriptsize{expect}}}$};
+    \xrightarrow[\textcolor{\PH}{\ADD_h^{z\vphantom{'}}}]{\mbox{\scriptsize{last}}}
+    \xrightarrow[\DEL_h^{\vphantom{z'}} ]{\mbox{\scriptsize{expect}}}$};
 
   \draw ( \X, 5pt) node[above, font=\footnotesize]{$
-    \xrightarrow[\textcolor{\PF}{\ADD_f^{\vphantom{y'}}} \rightarrow \DEL_f]{\mbox{\scriptsize{before}}}
+    \xrightarrow[\textcolor{\PH}{\ADD_h^{\vphantom{y'}}} \rightarrow \DEL_h]{\mbox{\scriptsize{before}}}
     \xrightarrow[\textcolor{\PC}{\ADD_d^{y'}}]{\mbox{\scriptsize{last}}}
@@
   \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
-  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below right, font=\scriptsize]{somewhere: $\textcolor{\PF}{\ADD_f} \rightarrow \DEL_f$};
+  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below right, font=\scriptsize]{somewhere: $\textcolor{\PH}{\ADD_h} \rightarrow \DEL_h$};
 

### 2021-04-20 input/proposal.tex
about proof, about implementation, merge complexity and implementation

@@
 
-\begin{definition}[\label{def:lwo}Last win order]
+\begin{definition}[\label{def:lwo}Last win order and staleness]
   When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
   b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
-  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m'$
+  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
   convey \emph{stale} control information.
@@
 
-\begin{theorem}[Propagations $+$ detection $\implies$ purge]
-  \Processes can purge stale control information by broadcasting a
-  dedicated notification message $\delta$, and detect possible
-  inconsistencies using their history to propagate 
+\begin{theorem}[three-phase purge] % Propagations $+$ detection $\implies$ purge]
+  Purging stale control information from its source to every \process
+  that may have delivered it last requires three
+  phases:
+  \begin{inparaenum}[(i)]
+  \item propagation of delete notifications,
+  \item detection of possible blocking conditions, and
+  \item propagation of possibly deleted but blocked notifications.
+  \end{inparaenum}
 \end{theorem}
@@
   Figure~\ref{fig:proofB} depicts all possible cases that need
-  appropriate purging. A chain of \processes $[d, e, b', b'']$
-  delivered and forwarded a message $\alpha_d$. Some \processes may
-  have delivered messages about other partitions before or after
+  appropriate purging. A chain of \processes $[d, e, f, g]$ delivered
+  and forwarded a message $\alpha_d$. Some \processes may have
+  delivered messages about other partitions before or after
   $\alpha_d$.
@@
     \Process~$d$ where the last and best partition is still $P_d$. By
-    propagating from process to process the corresponding $\delta_d$
+    propagating from \process to \process the corresponding $\delta_d$
     message, these \processes purge $\alpha_d$.
-  \item [\processes with $\alpha_d^y \rightarrow \alpha_f^z$ with last
-    $\alpha_f^z$, for $\alpha_f^z < \alpha_d^y$:] \Processes such as
+  \item [\processes with $\alpha_d^y \rightarrow \alpha_h^z$ with last
+    $\alpha_h^z$, for $\alpha_h^z < \alpha_d^y$:] \Processes such as
     \Process~$e$ do not directly suffer from the non-delivery of
-    $\delta_d$. They need to purge their own $P_f$ if need
-    be. Nonetheless, they deliver and forward $\alpha_f$ that at least
+    $\delta_d$. They need to purge their own $P_h$ if need
+    be. Nonetheless, they deliver and forward $\alpha_h$ that at least
     one following \process will receive:
-  \item [\processes with $\delta_f \rightarrow \alpha_d$:] \Processes
-    such as \Process~$b'$ do not belong to the preceding category, for
-    they already delivered $\delta_f$. However, best eventual
-    forwarding guarantees that they receive $\alpha_f$ that
+  \item [\processes with $\delta_h \rightarrow \alpha_d$:] \Processes
+    such as \Process~$f$ do not belong to the preceding category, for
+    they already delivered $\delta_h$. However, best eventual
+    forwarding guarantees that they receive $\alpha_h$ that
     contradicts their history or state. In such case, the detecting
@@
   \item [\processes with last $\alpha_d$ receiving $\delta_d?$ from
-    their parent:] \Processes such as \Process~$b''$ have $\alpha_d$
-    and preceding delivered messages have not importance. Such
-    \processes must trust detecting \processes by delivering and
-    forwarding $\delta_d?$. Messages are subject to all aforementioned
-    blocking conditions, but are also solved by aforementioned
-    mechanisms.
+    their parent:] \Processes such as \Process~$g$ have $\alpha_d$ and
+    preceding delivered messages have not importance. Such \processes
+    must trust detecting \processes by delivering and forwarding
+    $\delta_d?$. Messages are subject to all aforementioned blocking
+    conditions, but are also solved by aforementioned mechanisms.
   \end{asparadesc}
 
-  Propagation I' terminates: a process do not deliver a $\delta$
-  message if it has already delivered it. Propagation IV terminates: a
-  process do not deliver a looping message.  Propagation and detection
-  ensure that \processes eventually purge stale $\alpha$ messages from
-  the system, leaving room for Propagation I.
+  Propagation~I' terminates: a \process do not deliver a $\delta$
+  message if it has already delivered it. Propagation~IV terminates: a
+  \process do not deliver a looping message.
+  % ; and since \processes forward the messages they deliver, upstream
+  % \processes eventually receive and may deliver messages detected as
+  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
+  % receives $\delta_f$ from \Process~$b'$.
+  These three phases propagation-detection-propagation ensure that
+  \processes eventually purge stale $\alpha$ messages from the system,
+  leaving room for Propagation~I.
+  %
+  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
+  % delete to $e$, it will solve the inconsistency.}
+  %
   %% In the meantime, \processes that still belong to a partition can
@@
 
-\subsection{Implementation}
+\subsection{Implementation and complexity}
 
-Algorithm~\ref{algo:ascast} provides the instructions that
-implement dynamic consistent partitioning:
-\begin{inparaenum}[(i)]
-\item \label{algo:most} most of the time, it propagates $\alpha$'s and
-  $\delta$'s when the partitions allow it;
-\item \label{algo:sometimes} sometimes, it detects possible
-  inconsistent partitioning and
-\item \label{algo:solves}solves it using propagation trees (as opposed
-  to propagation graphs);
-\item \label{algo:competition} when required, it triggers competitions
-  among neighboring partitions.
-\end{inparaenum}
-While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
-stale notifications, (\ref{algo:competition}) tackle the eventual
-delivery of the best up-to-date partitions.
+Algorithm~\ref{algo:ascast} provides the few instructions of \NAME
+that implement three-phase purge and best eventual forwarding to
+enable dynamic consistent partitioning.
+
+%% Similarly to Algorithm~\ref{algo:add}, local operations \texttt{Add}
+%% and \texttt{Del} generate messages that the initiating \process treats
+%% identically to receipts of messages from remote \processes.
+
+%% \begin{inparaenum}[(i)]
+%% \item \label{algo:most} most of the time, it propagates $\alpha$'s and
+%%   $\delta$'s when the partitions allow it;
+%% \item \label{algo:sometimes} sometimes, it detects possible
+%%   inconsistent partitioning and
+%% \item \label{algo:solves}solves it using propagation trees (as opposed
+%%   to propagation graphs);
+%% \item \label{algo:competition} when required, it triggers competitions
+%%   among neighboring partitions.
+%% \end{inparaenum}
+%% While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
+%% stale notifications, (\ref{algo:competition}) tackle the eventual
+%% delivery of the best up-to-date partitions.
 
@@
 
-To constrain the order of delivery at each \process, each \process
-implements last win order by maintaining a vector of versions that
-associates to each known source, or has-been source, with its known
-local counter. It enables \processes to deliver only up-to-date
-$\alpha$'s that may improve their best known partition (see
-Line~\ref{line:detectA}), but also to detect possible inconsistent
-partitioning (see Line~\ref{line:detectB}) as labeled by III in
-Figure~\ref{fig:proofB}. From a global perspective, it ensures
-monotonic increase of knowledge despite the non-monotonic number of
-sources. In turns, it contributes to convergence and termination, for
-corresponding $\alpha$ and $\delta$ cannot follow each other in an
-infinite loop.
+To implement last win order as stated in Definition~\ref{def:lwo},
+each \process maintains a vector of versions that associates the
+respective known local counter of each known source, or has-been
+source.  Each \process delivers and forwards
+\begin{inparaenum}[(i)]
+\item only newest messages (see Line~\ref{line:ascast_version}) that
+\item improve their best known partition (see
+  Line~\ref{line:ascast_better}).
+\end{inparaenum}
+This vector enables both Propagation~I and Propagation~I'.  The size
+of such vector increases linearly with the number of sources that the
+\process ever known which is the number of \processes in the system
+$\mathcal{O}(V)$ in the worst case. Unfortunately, \processes cannot
+remove any entry from this vector without running a costly distributed
+consensus protocol to ensure that no \process can mistake an old but
+removed entry for a new one. However, using \NAMEB, we expect that
+every \process knows only a small subset of sources.
 
-Implementing the propagation of deletes is no different from the
-propagation of adds as hinted in Figure~\ref{fig:proof} with Labels I
-and I'. Messages and comparisons include the local counter of the
-source. When a \process receives a better up-to-date partition, it
-delivers and forwards it. When a \process receives a delete
-notification about its partition, it delivers and forwards it. It is
-worth noting that such $\delta$'s apply to the whole partition. They
-travel in the propagation graph of their partition using all
-communication links, allowing \processes to change partition as soon as
-possible.
+This vector of versions constitutes a summary of deliveries. \NAME
+uses it to detect possible inconsistent partitioning as depicted in
+Figure~\ref{fig:proofB}. A detecting \process then propagates a
+$\delta$ message conveying the unique identifier $s$ and version $c$
+of the partition along with a path $\pi$ comprising the identity of
+\processes that forwarded the corresponding $\alpha$ message. Such
+$\delta$ message implements the uncertain $\delta?$ message of
+Figure~\ref{fig:proofB}. It fulfils the double role of removing stale
+control information without modifying the local counter of the source
+(since the partition may still exist), and removing loops to ensure
+termination (since \processes do not modify their local state to
+reflect such delivery, messages piggyback monotonically such
+increasing control information). Thus, $\delta$ messages used in
+Propagation~I' are more efficient both in propagation time and
+traffic, for they propagate using every communication link available
+in the partition, and they do not need to carry their path.
+Fortunately, Propagation~I' happens more often than Propagation~IV.
+Yet, \processes that belong to a partition need to save the path taken
+by the corresponding $\alpha$ messages to enable Propagation~IV.  In
+the worst case, the path includes every \processes in the system but
+converges in average to the average diameter of partitions. Thus,
+message paths and \NAME have an interesting synergy: Paths tend to be
+smaller as the number of sources in the system increases.
 
-Vectors of versions also allow each \process to detect possible last
-win order violations. Upon possible inconsistency, the detecting
-\process must remove all $\alpha$ messages originating from it, as
-labeled by IV in Figure~\ref{fig:proofB}. Contrarily to delete
-operations, this applies to a sub-partition of the current partition,
-and cannot rely on local counters to
-operate. Algorithm~\ref{algo:ascast} implements this behavior by
-piggybacking paths in messages. Paths guarantee that such $\delta$
-messages apply to all and only $\alpha$'s that followed an identical
-path. $\delta$'s propagate in the propagation tree rooted at the
-detecting \process. Local states of \processes remain unchanged, but
-paths in messages monotonically grow. In turns, $\alpha$ and $\delta$
-cannot follow each other in an infinite loop, for a \process knows when
-it already received a forwarded a message (see
-Lines~\ref{line:notloopingA} and \ref{line:notloopingB}).
+As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
+not only requires eventual purging of stale control information, but
+also the retrieval of the best up-to-date partitions. In that regard,
+$\delta$ messages have dual use: since they already reach the borders
+of their partition when they remove stale control information, they
+also trigger a competition when reaching such bordering \processes
+(see Line~\ref{line:ascast_compete}). This simply consists in sending
+the current partition through the communication link from which the
+\process received the $\delta$. Upon receipt of this answer,
+\processes act normally by propagating their changes when they
+improve.
 
-\noindent It is worth noting that scoped broadcast and the
-piggybacking of paths synergies well: Paths tend to be smaller as the
-number of sources in the system increases.
-
-Finally, as stated in Theorem~\ref{theo:dcp}, dynamic consistent
-partitioning not only requires the removal of all stale partitions,
-but also the retrieval of the best up-to-date partitions. In that
-regard, $\delta$'s have dual use: since they already reach borders of
-partitions when they remove stale control information, they also
-trigger a competition when reaching such bordering \processes (see
-Line~\ref{line:compete}). This simply consists in sending the current
-partition through the communication link from which the \process
-received the $\delta$. Upon receipt of this answer, \processes act
-normally by propagating their changes when they improve. These adds
-fill the gaps left open by deletes.
-
-\begin{algorithm}
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}\NAME at \Process $p$ in dynamic networks.}
-\end{algorithm}
-
-Algorithm~\ref{algo:edges} provides the instructions of \NAME that
-enable dynamic consistent partitioning in dynamic networks where
-\processes can join or leave the system without
-notification. \TODO{More.}
-
-%% Adding new communication links to the network may create shortcuts
-%% between \processes. Both \processes must send their current best
-%% partition to each other. Upon receipt, they act normally: if a \process
-%% finds out that the received partition is closer than its current one,
-%% it delivers it which in turns also triggers another competition
-%% amongst neighbors due to forwarding.
-
-%% \noindent Joining the network is equivalent to add as many
-%% communication links as necessary between the joining \process and its
-%% new neighbors.
-
-%% When removing a communication link between two \processes does not
-%% break any active path, because neither distances of \processes depend
-%% on the other, then nothing needs to be done. \NAME has no overhead.
-%% Unfortunately, when a \process' distance depends on the other \process,
-%% the protocol becomes much more complex. Indeed, this requires to
-%% \TODO{undo} all add messages originated from this \process. A message
-%% must convey the fact that
-%% \begin{inparaenum}[(i)]
-%% \item an edge at a particular \process has been removed, and
-%% \item the distance that has been delivered by a \process comes from
-%%   this particular \process.
-%% \end{inparaenum}
-
-%% \subsection{Inter-autonomous system partitioning}
-
-%% \begin{figure}
-%%   \centering\input{input/figAS.tex}
-%%   \caption{\label{fig:AS}Inter autonomous systems
-%%     partitioning. \TODO{More about relative ordering of links at each
-%%       \process}}
-%% \end{figure}
-
-%% In this section, we aim at solving Problem Statement~\ref{prob:inter}
-%% by proposing \NAMEB, an extension of \NAME, that enables dynamic
-%% logical partitioning in inter-autonomous systems. It leverages
-%% hierarchical properties of these networks to further improve on scoped
-%% flooding.
-
-%% Autonomous systems are geo-distributed networks. Heterogeneous
-%% communication links. Hierarchy of communication links. Per-object
-%% broadcast.
-
-%% We leave the link handling to membership protocols~\REF. The ordering
-%% of links can be done based on latency. For instance, from 0 to 100 ms,
-%% rank 0, from 100 to 1s, rank 2 \ldots
-
-%% \begin{algorithm}
-%%   \input{input/algoaaaa.tex}
-%%   \caption{\label{algo:aaaa}\NAMEB running at \Process $p$ for dynamic
-%%     partitioning in inter-autonomous systems.}
-%% \end{algorithm}
-
-%% Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
-%% where each \process ranks its communication links, and each \process
-%% forwards messages to its neighbors starting from the rank of the link
-%% that triggered the receipt, to its highest rank neighbors. In this
-%% example, \Process $e$ adds a partition. It forwards the generated
-%% message to all its neighbors as if it received it from its lowest rank
-%% links. When \Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
-%% it forwards it to rank-$0$ links and rank-$1$ links.  \Process $b$
-%% stops the propagation, for all its links have lower ranks than the one
-%% from which it received the message $\alpha_e^2$. Ultimately, the
-%% partition includes \Process $e$, \Process $a$, and \Process $b$. \Process
-%% $c$ and \Process $d$ remain unaware of the new \TODO{object}.
-
-%% To ease the reasoning about inter-AS dynamic partitioning in dynamic
-%% networks, \NAME runs an independent broadcast protocol for each
-%% object, and for each rank of links.  \TODO{Not so easy\ldots}
-%% \TODO{Write and describe algo.} \TODO{Overhead of separating things,
-%%   slightly more memory, but traffic wise? slower ?}  \TODO{In the
-%%   example, not only \Process $b$ keeps $e_1$ as its best partition, but
-%%   it keeps it for links of rank 0, and links of rank 1.}  When there
-%% are no ranking in links, \processes solely rely on
-%% Algorithm~\ref{algo:adddelundo} for optimal partitioning.
-
-\subsection{Complexity}
-
-We focus on average-case and worst-case complexity. We divide our
-analysis into space, time, and communication complexity.
-
-\begin{asparadesc}
-\item [Space:]
-
-Each \process needs to maintain a vector of versions the size of which
-depends on the number of sources. In the worst case, the size of this
-vector increases linearly with the number of distinct sources that
-ever existed in the system. For the sake of last win order, \processes
-can never purge this vector from any entry. \TODO{Even when the
-  \process leaves the system.} Fortunately, scoped broadcast limits
-message propagation to interested \processes. A \process at a side of
-the system may never hear of a source at the other side of the
-system. In turns, it may never have to maintain an entry for this
-source. \TODO{This is application-dependent?}
-
-\noindent Each \process must also maintain the partition it belongs to,
-along with its control information. Among other, it must maintain a
-path the size of which depends on the membership size of the
-partition. In the worst case, this path includes the identity of every
-\process of the system that currently belong to the system. Eventually,
-the size of this path increases linearly with the diameter of the
-current partition. \TODO{assuming weight equals 1 \ldots}
-
-\item[Time:]
-
-In terms of processing time, whatever the operation, it increases
-linearly with the number of neighbors of the \process. It scales well,
-for the number of neighbors is commonly order of magnitude lower than
-the number of \processes in the system. For instance, random networks
-only require $O(\log(|V|))$ neighbors to work properly \REF; and
-\processes in autonomous systems have in average \TODO{X} neighbors
-\REF. Lines~\ref{line:notloopingA} and \ref{line:notloopingB} can
-prove costly depending on the data structure encoding paths. Using
-Bloom filters however, this is \TODO{efficient}: it depends on the
-number of buckets, and the number of hash functions.
-
-\noindent In terms of convergence time, every $\alpha$ needs to travel
-at least its shortest path before termination. Every $\delta$ needs to
-reach the border of its partition, triggering an $\alpha$ that fills
-the gaps left open by the removal. \TODO{More.}
-
-\item[Communication:]
-
-In terms of number of messages required to reach optimal
-partitioning. In the average-case, a \process $i$ chosen uniformly at
-random among all \processes creates a logical partition. Its messages
-$\alpha_i$ propagate through the network until reaching \processes
-that belong to another partition closer to them. This splits
-partitions in half in average. Overall, the $a^{th}$ new partition
-comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a
-      \rfloor}})$} \processes. This decreases every new partition
-until reaching $0$ \processes per new partition: even the chosen
-\process already belongs to its optimal partition. The average number
-of messages per \process is
-\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
+\TODO{About communication complexity} In terms of number of messages
+required to reach optimal partitioning. In the average-case, a
+\process $i$ chosen uniformly at random among all \processes creates a
+logical partition. Its messages $\alpha_i$ propagate through the
+network until reaching \processes that belong to another partition
+closer to them. This splits partitions in half in average. Overall,
+the $a^{th}$ new partition comprises
+\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
+\processes. This decreases every new partition until reaching $0$
+\processes per new partition: even the chosen \process already belongs
+to its optimal partition. The average number of messages per \process
+is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
       \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
@@
 corresponding partition creation.
-
 \noindent \TODO{In terms of size of messages.}
 
-\end{asparadesc}
+\begin{algorithm}
+  \input{input/algoedges.tex}
+  \caption{\label{algo:edges}\NAME at \Process $p$ in dynamic networks.}
+\end{algorithm}
+
+Algorithm~\ref{algo:edges} extends the instructions of \NAME that
+enable dynamic consistent partitioning in dynamic networks where
+\processes can join or leave the system without notification. We
+consider that removing a \process is equivalent to removing all its
+edges, and adding a \process is equivalent to add as many edges as
+necessary.
+
+Adding an edge between two \processes may only improve the shortest
+path of one of these \processes. Therefore, it triggers a competition
+between the two \processes only. Removing an edge between two
+\processes may invalidate the shortest path of one of involved
+\processes plus downstream \processes. To implement this behavior,
+\NAME uses the implementation of $\delta?$ messages. This prove costly
+but enables \NAME even in dynamic networks subject to physical
+partitioning.
 

### 2021-04-21 input/background.tex

@@
 
+\begin{figure}[t]
+\centering
+\subfloat[Initial configuration - Every nodes get the content from node $R$\label{fig:1a}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}\hfill
+\subfloat[Adding a second replica in node $G$ partitions the network nodes in $2$ sets.\label{fig:1b}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
+\subfloat[A third replica is created in node $B$ resulting in $3$ partitions.\label{fig:1c}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
+\subfloat[Removing the green partition: only $2$ partitions remain.\label{fig:1d}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
+\caption{Example of the french RENATER topology (edges are not drawn): Partitions shrink or expand according to the creation or removal of replicas.
+Ideally, only a subset of nodes should be informed of these events, according to their place in the topology.} \label{fig:partition_intuition}
+\end{figure}
+
 \subsection*{Locking down the dissemination}
 To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level, and explain how an (imaginary) omniscient entity could solve it. 
-In this way, suppose there exists an \textit{oracle} in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas.
+In this way, suppose there exists an \textit{oracle} in the system that instantly knows the arrival/departure of nodes in the topology and the location of the creation/removal of replicas.
 In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system.
@@
 For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event).
-The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).
 
-Moreover, we emphasize that information about a given replica localization should remain in a given geographical scope. 
+This is illustrated in Figure~\ref{fig:partition_intuition} where we depict the partitions shrinking or expanding according to the creation or removal of replicas respectively.
+In Figure\ref{fig:1a}, there exists a single occurence of a given content in node $R$: all nodes thus belong to the same partition as they would all retrieve the content from the same node. 
+A second replica is created in node $G$ in Figure~\ref{fig:1b}, resulting in $2$ partitions.
+Nodes from the \textit{green} partition would all obtain the content from node $G$ as it is their closest replica, while nodes from the \textit{red} partition would get it from node $R$.
+Note that only the nodes in the green partition has to be informed of the creation of the replica in node $G$.
+Similarly, in Figure~\ref{fig:1c}, only nodes in the blue partition should be informed of the creation of a new replica in node $B$ as it does not impact other nodes.
+Finally, when the replica in node $G$ is removed, nodes in the stale green partition have to join existing ones as illustrated in Figure~\ref{fig:1d}. 
+The challenge of implementing such a partitioning in an asynchronous network resides in informing this minimal subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).
+
+Finally, we emphasize that information about a given replica localization should remain in a given geographical scope. 
 Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.

### 2021-04-21 input/proposal.tex
on implem and complexity wip

@@
 introduces the properties that guarantee consistent partitioning in
-such context, and it details our implementation called \NAME. Finally,
-it provides the complexity analysis of \NAME divided in time, space,
-and communication.
+such context, and it details our implementation called \NAME along
+with its complexity analysis.
 
@@
 \processes join or leave the system, create or delete partitions, at
-any time. Instead, we propose to use the delivery order at each
-\process to detect possible inconsistencies and solve them. Together,
-\processes eventually remove all stale control information (transiting
-messages and local states) of the system leaving room for propagation
-of messages about up-to-date partitions.
-
-%% To identify and solve the issue with dynamic consistent partitioning
-%% where protocols enable \processes to \texttt{Add} and \texttt{Del} at
-%% any time, we need to further constrain the delivery order at each
-%% \process.
+any time.  \TODO{Another paragraph with JJ approach?}  Instead, we
+propose to use the delivery order at each \process to detect possible
+inconsistencies and solve them. Together, \processes eventually remove
+all stale control information (transiting messages and local states)
+of the system leaving room for propagation of messages about
+up-to-date partitions.
 
@@
 consensus protocol to ensure that no \process can mistake an old but
-removed entry for a new one. However, using \NAMEB, we expect that
-every \process knows only a small subset of sources.
+removed entry for a new one. However, following the principles of
+scoped broadcast, we expect that every \process knows only a small
+subset of sources.
 
@@
 message paths and \NAME have an interesting synergy: Paths tend to be
-smaller as the number of sources in the system increases.
+smaller as the number of sources in the system increases. Bloom
+filters could introduce another trade-off by further decreasing the
+size of path data structures at the cost of premature stopped
+propagation that could impair consistent
+partitioning~\cite{whitaker2002forwarding}.
 
@@
 also the retrieval of the best up-to-date partitions. In that regard,
-$\delta$ messages have dual use: since they already reach the borders
-of their partition when they remove stale control information, they
-also trigger a competition when reaching such bordering \processes
-(see Line~\ref{line:ascast_compete}). This simply consists in sending
-the current partition through the communication link from which the
-\process received the $\delta$. Upon receipt of this answer,
-\processes act normally by propagating their changes when they
-improve.
+both kinds of $\delta$ messages have dual use: since they already
+reach the borders of their partition when they remove stale control
+information, they also trigger a competition when reaching such
+bordering \processes (see Line~\ref{line:ascast_compete}). This simply
+consists in sending the current partition through the communication
+link from which the \process received the $\delta$. Upon receipt of
+this answer, \processes act normally by propagating their changes when
+they improve. \TODO{Exemple with figure for detection?}
 
-\TODO{About communication complexity} In terms of number of messages
-required to reach optimal partitioning. In the average-case, a
-\process $i$ chosen uniformly at random among all \processes creates a
-logical partition. Its messages $\alpha_i$ propagate through the
-network until reaching \processes that belong to another partition
-closer to them. This splits partitions in half in average. Overall,
-the $a^{th}$ new partition comprises
-\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
-\processes. This decreases every new partition until reaching $0$
-\processes per new partition: even the chosen \process already belongs
-to its optimal partition. The average number of messages per \process
-is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
+\TODO{Rework this.}\NAME guarantees dynamic consistent partitioning by
+making extensive use of \process to \process communications. In terms
+of number of messages, in the average-case, a \process $i$ chosen
+uniformly at random among all \processes creates a logical
+partition. Its messages $\alpha_i$ propagate through the network until
+reaching \processes that belong to another partition closer to
+them. This splits partitions in half in average. Overall, the $a^{th}$
+new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
+      \log_2 a \rfloor}})$} \processes. This decreases every new
+partition until reaching $0$ \processes per new partition: even the
+chosen \process already belongs to its optimal partition. The average
+number of messages per \process is
+\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
       \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
@@
 corresponding partition creation.
-\noindent \TODO{In terms of size of messages.}
 

### 2021-04-21 input/background.tex
reworking motivation wip

--- 2021-04-20 input/background.tex
@@
-\section{Background and Problem Definiton}
+\section{Motivation and problem}
 \label{sec:background}
 
-Numerous studies exist on content indexing, with solutions being either centralized or distributed (see Section\ref{related_work}).
-As explained above, in this paper we advocate designs that do not rely on requesting any remote entity before being able to access a given content.
-This section thus focuses on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
-We explain why existing implementations are costly thus preventing their deployment in real systems.
-Then, we describe the problem tackled by this paper at an abstract level to underline the challenges that drove the design of our proposal.
+Numerous studies addressed content indexing in geo-distributed
+infrastructures ranging from centralized services to fully
+decentralized approaches~\REF. We advocate for the latter where
+\processes host the service themselves so they do not need to request
+remote -- possibly far away third-party -- entities to retrieve their
+content location.  In this paper, we tackle the content indexing issue
+as a logical partitioning problem. This section motivate this shift
+and explains the shortcomings of existing implementations.
 
-\subsection*{Disseminate localization information}
-Enabling the accessibility of content without prior requests implies that the information about replica localization has to be pushed directly to the nodes.
-Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}.
-Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
-Moreover, removing the lookup latency directly involves faster downloading times.
-Similarly, one could solve this issue by using a conflict-free replicated datatype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
-However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
-That means information that might only interests a small subset of nodes is actually spread out all over the network.
+%% Numerous studies exist on content indexing, with solutions being
+%% either centralized or distributed (see
+%% Section\ref{related_work}). As explained above, in this paper we
+%% advocate designs that do not rely on requesting any remote entity
+%% before being able to access a given content.  This section thus
+%% focuses on the existing solutions so that: \textbf{for any content,
+%% every node is able to access its closest replica without any prior
+%% request.}  We explain why existing implementations are costly thus
+%% preventing their deployment in real systems.  Then, we describe the
+%% problem tackled by this paper at an abstract level to underline the
+%% challenges that drove the design of our proposal.
 
-\subsection*{Locking down the dissemination}
-To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level, and explain how an (imaginary) omniscient entity could solve it. 
-In this way, suppose there exists an \textit{oracle} in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas.
-In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system.
-Equipped with these two information, it is then trivial for this oracle to compute for each node, where resides its closest replica for a given content.
-Mapping each node of the topology to a single replica amounts to partition the set of all nodes into $k$ disjoint sets (or partitions), where $k$ is the number of current replicas.
-Thus, every node in the same partition would get the content from the same replica.
-Interestingly, this partitioning matches the physical topology as neighbors physically closed in the infrastructure will most likely reside in the same partition.
-For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event).
-The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).
+\begin{asparadesc}
+\item [Dissemination:]
 
-Moreover, we emphasize that information about a given replica localization should remain in a given geographical scope. 
-Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.
-This prevents the use of gossip protocols for example.
-Indeed, gossip protocols are also appealing candidates to disseminate information reliably across a network~\cite{epidemic-protocol} and numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
-However, these protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information.
-This implies that nodes will exchange messages with random nodes in the system far exceeding their geograhical scope.
+Figure~\ref{fig:partition_intuition} depicts an infrastructure
+comprising 17 interconnected \processes spread across France. In
+Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
+content, so every other \process downloads from this \process when it
+needs it. In that regard, \Process~$R$ only needs to disseminate a
+message notifying all other processes of its new content. \Process~$R$
+can use uniform reliable broadcast~\REF and epidemic propagation~\REF
+to guarantee that
+\begin{inparaenum}[(i)]
+\item every process eventually knows the content location
+\item efficiently using neighbor-to-neighbor communication.
+\end{inparaenum}
+
+\item [Location:]
+
+Then, in Figure~\ref{fig:partition_intuitionB}, another \Process~$G$
+creates a replica of this content. Similarly to \Process~$R$, it
+notifies other \processes of this new replica. However, to avoid that
+north \processes request its replica, and south \processes request the
+northern replica, \processes hosting a replica must add \emph{location
+information} along with their notifications. As consequence, every
+\process eventually knows every replica location and can download from
+its closest host. \underline{R}ed \processes would request
+\Process~$R$ while \underline{g}reen \processes would request
+\Process~$G$.
+
+\item [Scoped broadcast:]
+
+Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
+creates a replica of this content. Similarly to \Process~$R$ and
+\Process~$G$, \Process~$B$ can notify other \processes of this new
+replica. However, the set of \processes that could actually use this
+new replica is actually much smaller than the network size. Uniform
+reliable broadcast is not designed for such context and would generate
+a lot of unnecessary traffic. Instead, \processes need a communication
+primitive that propagate notifications as long as \processes receiving
+them consider them useful based on location information they carry. We
+call such primitive \emph{scoped broadcast}, for messages transitively
+reach a subset of interconnected \processes (the \emph{scope}) by
+evaluating a predicate starting at its broadcaster (the
+\emph{source}). Using this primitive, \processes can lock down the
+traffic of content indexing to relevant \processes.
+
+\item [Logical partitioning:]
+
+Every \process ends up with at least 1 known replica that is its
+closest. The set of interconnected \processes with the same closest
+replica is a \emph{partition}. Every \process belongs to one, and only
+one, partition. Contrarily to membership protocols that choose
+\processes to communicate with based on metrics~\REF, \processes in
+our context have no control over their neighboring processes.
+
+\item [Dynamic partitioning and adaptive scoped broadcast:]
+
+Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
+destroys its replica. \TODO{Meow.}
+
+\end{asparadesc}
+
+%% \subsection*{Disseminate localization information}
+%% Enabling the accessibility of content without prior requests implies
+%% that the information about replica localization has to be pushed
+%% directly to the nodes.  Broadcasting information about cache updates
+%% to all nodes in the system is a straightforward way to maintain
+%% consistent information about replica localization for all
+%% nodes~\cite{nlsr,lscr}. Indeed, having the entire knowledge of all the
+%% replica localizations along with distance information carried into
+%% messages, each node can easily compute where the closest copy of a
+%% given object resides, without contacting any remote node. Moreover,
+%% removing the lookup latency directly involves faster downloading
+%% times.  Similarly, one could solve this issue by using a conflict-free
+%% replicated datatype (CRDT) for set data structures, for
+%% example~\cite{shapiro2011crdts}.  However, either by broadcasting or
+%% with CRDTs, both inherently imply that every nodes will eventually
+%% receive all messages.  That means information that might only
+%% interests a small subset of nodes is actually spread out all over the
+%% network.
+
+%% \subsection*{Locking down the dissemination}
+%% To provide the intuition underlying our proposal, we now describe the
+%% problem tackled by this paper at an abstract level, and explain how an
+%% (imaginary) omniscient entity could solve it.  In this way, suppose
+%% there exists an \textit{oracle} in the system that instantly knows the
+%% arrival/departure of nodes in the topology and the location of the
+%% creation/removal of replicas. In other words, this oracle is
+%% constantly aware of the current topology and the current list of all
+%% available replicas of a given content in the system. Equipped with
+%% these two information, it is then trivial for this oracle to compute
+%% for each node, where resides its closest replica for a given
+%% content. Mapping each node of the topology to a single replica amounts
+%% to partition the set of all nodes into $k$ disjoint sets (or
+%% partitions), where $k$ is the number of current replicas. Thus, every
+%% node in the same partition would get the content from the same
+%% replica. Interestingly, this partitioning matches the physical
+%% topology as neighbors physically closed in the infrastructure will
+%% most likely reside in the same partition.  For any event such as an
+%% arrival/departure of nodes or creation/removal of replicas, the oracle
+%% is thus able to inform the \textit{exact} subset of nodes that has to
+%% update their location (\ie the exact scope of an event).
+
+%% This is illustrated in Figure~\ref{fig:partition_intuition} where we
+%% depict the partitions shrinking or expanding according to the creation
+%% or removal of replicas respectively.  In Figure\ref{fig:1a}, there
+%% exists a single occurence of a given content in node $R$: all nodes
+%% thus belong to the same partition as they would all retrieve the
+%% content from the same node.  A second replica is created in node $G$
+%% in Figure~\ref{fig:1b}, resulting in $2$ partitions. Nodes from the
+%% \textit{green} partition would all obtain the content from node $G$ as
+%% it is their closest replica, while nodes from the \textit{red}
+%% partition would get it from node $R$.  Note that only the nodes in the
+%% green partition has to be informed of the creation of the replica in
+%% node $G$. Similarly, in Figure~\ref{fig:1c}, only nodes in the blue
+%% partition should be informed of the creation of a new replica in node
+%% $B$ as it does not impact other nodes.  Finally, when the replica in
+%% node $G$ is removed, nodes in the stale green partition have to join
+%% existing ones as illustrated in Figure~\ref{fig:1d}.  The challenge of
+%% implementing such a partitioning in an asynchronous network resides in
+%% informing this minimal subset of nodes (or as close as possible),
+%% without any \textit{a priori} knowledge while only relying on local
+%% information (\ie no node has the knowledge of all the replica
+%% localizations).
+
+%% Finally, we emphasize that information about a given replica
+%% localization should remain in a given geographical scope.
+%% Intuitively, it is most likely that events happening at a given place
+%% in the network will have no impact on nodes that are very far away
+%% from them.  This prevents the use of gossip protocols for example.
+%% Indeed, gossip protocols are also appealing candidates to disseminate
+%% information reliably across a network~\cite{epidemic-protocol} and
+%% numerous studies have shown how quickly they converge despite high
+%% level of churn and/or failures~\cite{lpbcast}.  However, these
+%% protocols usually relies on a so-called \textit{peer-sampling
+%%   service}~\cite{jelasity2007gossip} to efficiently propagate the
+%% information. This implies that nodes will exchange messages with
+%% random nodes in the system far exceeding their geograhical scope.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "../paper"
+%%% ispell-local-dictionary: "english"
+%%% End:

### 2021-04-21 input/figpartitionintuition.tex
reworking motivation wip

\begin{figure*}
\centering
\subfloat[Initial configuration - Every nodes get the content from node $R$\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}\hfill
\subfloat[Adding a second replica in node $G$ partitions the network nodes in $2$ sets.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[A third replica is created in node $B$ resulting in $3$ partitions.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[Removing the green partition: only $2$ partitions remain.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{Example of the french RENATER topology (edges are not drawn):
  Partitions shrink or expand according to the creation or removal of
  replicas. Ideally, only a subset of nodes should be informed of
  these events, according to their place in the
  topology.} \label{fig:partition_intuition}
\end{figure*}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-04-21 input/conclusion.tex
on implem and complexity wip
backport end of the introduction into the conclusion

--- 2021-03-11 input/conclusion.tex
@@
 
+%% \noindent We propose an implementation that further decreases
+%% generated traffic and improves on
+%% anonymity~\cite{whitaker2002forwarding}.  \NAME makes extensive use of
+%% paths to enable deleting messages without incrementing local
+%% counters. Messages carry their respective path and processes detect
+%% when such messages have been looping when they carry their identity
+%% (see Lines~\ref{line:notloopingA} and \ref{line:notloopingB} of
+%% Algorithm~\ref{algo:adddelundo}). Since membership is all that
+%% matters, we propose to trade vectors of identities for Bloom
+%% filters~\cite{almeida2007scalable}. Processes know with high
+%% probability if they already received and forwarded each message
+%% without knowing the identity of all processes that received it.  False
+%% positive probability only incurs premature stopping of broadcast
+%% messages and does not invalidate the delete of specific
+%% messages. \TODO{Rework.}
+
 \noindent We also plan on further improving scoped broadcast between
@@
 
+% TODO : Use cases
+While we use the distance to the closest copy in this paper, It is
+notewothy that other scopes can be envisioned according to the
+use-cases.  For instance, the location of a city in order to broadcast
+message to all nodes in the city.  This requires nodes to store and
+maintain their city location in their local state. Nodes stop
+delivering and forwarding their received messages when they come from
+a different city. Such a predicate can be complexified in order to
+broadcast messages to all nodes in the city plus neighboring
+cities. This requires nodes to overload forwarded messages the first
+time they reach another city. The predicate checks if messages already
+reached two distinct cities before delivery.  The predicate can even
+be piggypack within the message and so be different for each
+message.\TODO{Complete the use-cases}
+
 %%% Local Variables: 

### 2021-04-21 input/figaddA.tex
fix?

--- 2021-04-08 input/figaddA.tex
@@
 
-  \draw (-\X + 5pt, 0) -- (0 - 5pt, 0); %% a - b
+  \draw (-\X + 5pt, 0) --
+  node[shape=circle, draw, fill=white, inner sep=0.5pt, font=\footnotesize]{2}
+  (0 - 5pt, 0); %% a - b
 
-  \draw (0 +5pt, 0) -- (\X -5pt, 0); %% b - c
+  \draw (0 +5pt, 0) --
+  node[shape=circle, draw, fill=white, inner sep=0.5pt, font=\footnotesize]{1}
+  (\X -5pt, 0); %% b - c
 
-  \draw (0, 0 - 5pt) -- (0, \Y + 5pt); %% d - b
+  \draw (0, 0 - 5pt) --
+  node[shape=circle, draw, fill=white, inner sep=0.5pt, font=\footnotesize]{1}
+  (0, \Y + 5pt); %% d - b
 
-  \draw (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d
+  \draw (\X + 3pt, 0 - 5pt) --
+  node[shape=circle, draw, fill=white, inner sep=0.5pt, font=\footnotesize]{3}
+  (0 + 5pt, \Y - 3pt); %% c - d
 

### 2021-04-21 input/introduction.tex
reworking motivation wip
first draft introd

@@
 
-There is an ongoing evlution of storing data from the cloud to the
+There is an ongoing evolution of storing data from the cloud to the
 edges of the network. Either because it is where it has been created
@@
      possible candidates from which the content  could be
-     retrieved. This results in parallel requests performed by the client node to
+     retrieved. In most cases, this results in parallel requests performed by the client node to
      each candidate with the goal of retrieving the content as efficient
@@
 the network (each node trying to get content from the ``closest''
-node).  In other words, the broadcast should be limited to a partition
+one).  In other words, the broadcast should be limited to a partition
 of the infrastructure, (\ie the subset of nodes that has to update the
 current location for this particular content). Obviously, these
-partitions depend and evolve according to concurrent operations made by nodes and
-dynamic changes in the infrastructure (network failures, node
-apparitions/leaves).
+partitions depend and evolve according to concurrent operations made
+by nodes (replica creation/removal) as well as dynamic changes in the
+infrastructure (network failures, node apparitions/leaves).
 
 In this paper, we propose a first implementation of such a protocol.
-Entitled \NAME, our protocol relies on a primitive that forwards
+Entitled Adaptive Scoped broadcast (\NAME), 
+our protocol relies on a primitive that forwards
 messages until a certain condition is reached, \ie the scope. The
@@
 %
+This primitive is used to guarantee that eventually, every node knows
+its best partition, hence its closest replica, despite concurrent
+events and receipt orders. Overall, \NAME is a wait-free reactive protocol for
+dynamic logical partitioning.  Its overhead actually depends on
+its operations and current partitions in the system. When the system
+becomes quiescent, nodes eventually converge to their respective
+partition and do not require further communication afterward.
 
-This primitive is used to communicate with the different nodes
-according to four events: creation/removal of a replica and node
-apparitions/leaves. \TODO{network failures is considered as a node leave?}
+\TODO{talk about the proof}
 
-\TODO{add something about the paper work}
-
-We evaluated our protocol through simulations using \textit{Peersim}~\cite{montresor2009peersim}. The topolgies we simulated are based on real-world ones from the Internet Toplogy
-Zoo~\cite{knight2011internet}.  Our evaluation shows that \NAME is able to
-provide a similar localization service when compared to a DHT-based
-approach while removing the lookup penalty or to an hypothetical complete and robust broadcast. This directly translates
-into faster data access as shown by our measurements, with a time
-reduction from $20\%$ to $60\%$, depending on the sizes of the
-objects. %\AVK[Talk about load balancing and traffic containment here]
-We also show that by slightly delaying the sending of messages, \NAME
-can match the number of messages of a DHT-based approach, at the cost
-of a moderate increase in message sizes.
-
-\TODO{Update the conclustion of the experiment}
+We evaluated our protocol through two simulation scenarios using
+\textit{Peersim}~\cite{montresor2009peersim}. First, we confirm that
+\NAME allow consistent partitioning in an ad-hoc network composed of
+10K nodes.  Second, we illustrate how \NAME enables the lock down of
+the traffic in dynamic inter autonomous systems.  More precisely, we
+simulated a worldwilde infrastructure by duplicating the GEANT
+topology - a real infrastructure spanning across Europe – and by
+connecting these two clusters with a high latency link: 200 ms
+simulating cross-continental communications such as Europe-America.
 
@@
 
-% TODO : Use cases
-While we use the distance to the closest copy in this paper, It is
-notewothy that other scopes can be envisioned according to the
-use-cases.  For instance, the location of a city in order to broadcast
-message to all nodes in the city.  This requires nodes to store and
-maintain their city location in their local state. Nodes stop
-delivering and forwarding their received messages when they come from
-a different city. Such a predicate can be complexified in order to
-broadcast messages to all nodes in the city plus neighboring
-cities. This requires nodes to overload forwarded messages the first
-time they reach another city. The predicate checks if messages already
-reached two distinct cities before delivery.  The predicate can even
-be piggypack within the message and so be different for each
-message.\TODO{Complete the use-cases}
-
-\TODO{update the outline}
-\TODO{The rest of this paper is organized as follows. Section II
-  introduces background, related works and details the motivation
-  behind our proposal.  Section III describes the protocol behavior,
-  as well as the formal definition of the underlying
-  algorithms. Section IV presents the evaluation of the A3
-  implementation and provides an extensive comparison with a DHT-based
-  approach. We discuss some extensions of this work and future
-  directions in Section V before concluding in Section VI.}
+The rest of this paper is organized as
+follows. Section~\ref{sec:background} introduces background, and
+details the motivation behind our proposal.
+Section~\ref{sec:adapative} describes the protocol behavior, as well
+as the formal definition of the underlying
+algorithms. Section~\ref{sec:experimentation} presents the Peersim
+evaluations.  Related work is discussed in
+Section~\ref{sec:related_work} and finally
+Section~\ref{sec:conclusion} concludes this article and highlights a
+few future works.
 

### 2021-04-21 input/background.tex
ref fix
reworkd background

@@
 Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
-destroys its replica. \TODO{Meow.}
+destroys its replica. Every \processes that belong to its green
+partition must choose another partition to be in. While it makes sense
+for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
+\Process~$R$ cannot afford to continuously advertise their replica to
+fill the gap left open by \Process~$G$. Instead, we want to trigger
+scoped broadcast at bordering \processes of red and blue
+partitions. The scope of scoped broadcast changes over receipts by
+processes. Dynamic partitioning raises additional challenges related
+to concurrent operations where removed partition would block the
+propagation of other partitions.
+\end{asparadesc}
 
-\end{asparadesc}
+Next Section details adaptive scoped broadcast in dynamic networks. It
+details the properties of such protocol, and provides an
+implementation along with its complexity.
 

### 2021-04-21 input/abstract.tex
meow

@@
   \noindent In this paper, we abstract content indexing as distributed
-  partitioning: every \process only indexes its closest replica, and
+  partitioning:
+\TODO{weird}
+  every \process only indexes its closest replica, and
   connected \processes with similar index compose a partition. Our
@@
   scales well in terms of generated traffic and termination time,
-  especially in dynamic Edge infrastructures. As such, \NAME could
+  especially in dynamic \TODO{weird, we do not really test dynamic}
+Edge infrastructures. As such, \NAME can
   constitute the building block of new geo-distributed services.

### 2021-04-21 input/figpartitionintuition.tex

@@
 \centering
-\subfloat[Initial configuration - Every nodes get the content from node $R$\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}\hfill
-\subfloat[Adding a second replica in node $G$ partitions the network nodes in $2$ sets.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
-\subfloat[A third replica is created in node $B$ resulting in $3$ partitions.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
-\subfloat[Removing the green partition: only $2$ partitions remain.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
+\subfloat[\Process~$R$ efficiently advertises its content using epidemic propagation.
+Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}
+\hfill
+\subfloat[\Process $G$ creates a second replica splitting the red set in two.
+\Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
+\subfloat[\Process $B$ creates another replica.
+\Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
+\subfloat[\Process $G$ destroys its replica.
+\Processes that belong to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
 %
-\caption{Example of the french RENATER topology (edges are not drawn):
-  Partitions shrink or expand according to the creation or removal of
-  replicas. Ideally, only a subset of nodes should be informed of
-  these events, according to their place in the
-  topology.} \label{fig:partition_intuition}
+\caption{The french RENATER topology. Partitions
+  grow and shrink depending on creations and removals of
+  replicas.} \label{fig:partition_intuition}
 \end{figure*}

### 2021-04-21 input/proposal.tex
combine Sec III and IV - try 1

@@
 
-\section{Scoped broadcast}
-\label{sec:scoped}
+\section{Adaptive scoped broadcast}
+\label{sec:adaptive}
 
-Scoped broadcast is a communication primitive that propagates a
-message around its broadcaster within an application-dependant scope.
-For instance, a \process from Paris could scoped broadcast messages to
-all \processes in Paris; and \processes from other cities would never
-deliver such messages.
-Scoped broadcast only targets a connected \emph{subset} of \processes
-in the whole distributed system.
+%% In this section, we propose to dynamically adapt the scopes of \NAMEB
+%% using \NAMEB itself for the sake of efficiency: a \NAMEB message may
+%% modify the state of a \process, consequently changing predicate
+%% evaluations over deliveries.  At any time, a \process decides whether
+%% or not it becomes the center (or \emph{source}) of a scope (or
+%% \emph{partition}). \Processes must eventually rally the partition
+%% corresponding to their closest source despite concurrent operations,
+%% and dynamic changes in the network.
+
+%% \noindent In that regard, we introduce \NAME (stands for
+%% \underline{A}daptive \underline{S}coped broad\underline{cast}), a
+%% wait-free reactive protocol for dynamic logical partitioning that
+%% enables adaptive scoped broadcast in dynamic distributed
+%% systems. \NAME's operation guarantees that \processes eventually reach
+%% consistent partitioning by efficiently propagating their state
+%% changes. \NAME's overhead actually depends on its operations and
+%% current partitions in the system. When the system becomes quiescent,
+%% \processes eventually converge to their respective partition and do not
+%% require further communication afterward.
+
+%% \noindent This section starts by introducing consistent partitioning
+%% and its implementation when a \process can only become a new source to
+%% create a new partition, i.e., it cannot revoke its self-appointed
+%% status of source. Then, it extends to include the latter behavior: it
+%% introduces the properties that guarantee consistent partitioning in
+%% such context, and it details our implementation called \NAME along
+%% with its complexity analysis.
+
+To assign and maintain \processes to their best partition according to
+replica creations/removals as well as dynamic infrastructure changes,
+we designed and implemented \NAME (\NAME stands for
+\underline{A}daptive \underline{S}coped broad\underline{cast}).  \NAME
+relies on a primitive that allows a \process to broadcast a message
+within a limited scope.  This primitive is used in a first algorithm
+to deliver consistent partitioning each time \process creates a new
+replica within the system. This algorithm is then extended to include
+replica removals as well as dynamic changes of the infrastructure.
+This section discussed the different properties that guarantee
+consistent partitioning in such a context and details the \NAME
+implementation along with its complexity analysis.
+
+\subsection{Scoped broadcast}
+\label{subsec:scoped}
+
+%For instance, a \process from Paris could scoped broadcast messages to
+%all \processes in Paris; and \processes from other cities would never
+%deliver such messages.
+%Scoped broadcast only targets a connected \emph{subset} of \processes
+%in the whole distributed system.
 %
-Distributed systems such as Edge infrastructures comprise
-heterogeneous machines interconnected by communication
-links. \Processes may crash but are not byzantine.
 
 % \TODO{dynamic graph: superscript with $t$?}
+In the edge infrastructure we consider, nodes are heterogeneous and
+interconnected by communication links. \Processes involved in the
+management of the data sets may crash but are not byzantine.  Finally,
+\processes can reliably communicate through asynchronous message
+passing to other known \processes called neighbors.
+A more formal definition of our system is given below:
 
@@
 
-\Processes can reliably communicate through asynchronous message
-passing to other known \processes called neighbors. Using epidemic
-propagation (or gossiping), \processes can reliably broadcast messages
-by forwarding delivered messages from neighbors to
-neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
-  nedelec2018causal, raynal2013distributed}. However, uniform reliable
-broadcast states that \emph{all} correct \processes must deliver all
-broadcast messages. This proves costly in large scale systems
-comprising thousands of \processes. Instead, we define \emph{scoped
-broadcast} where messages reach only an application-dependant subset
-of connected \processes, thus significantly reducing the generated
-traffic of broadcast.
+%Using epidemic
+%propagation (or gossiping), \processes can reliably broadcast messages
+%by forwarding delivered messages from neighbors to
+%neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
+%  nedelec2018causal, raynal2013distributed}.
+%
+%However, uniform reliable
+%broadcast states that \emph{all} correct \processes must deliver all
+%broadcast messages. This proves costly in large scale systems
+%comprising thousands of \processes. Instead, we define \emph{scoped
+%broadcast} where messages reach only an application-dependant subset
+%of connected \processes, thus significantly reducing the generated
+%traffic of broadcast.
+
+We define the Scoped broadcast (\NAMEB) as a communication primitive that propagates a
+message around its broadcaster within an application-dependant scope :
 
@@
 This definition encompasses more specific definitions of related
-work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  This
-definition also highlights that epidemic propagation and scoped
-broadcast have well-aligned preoccupations: It highlights the
-transitive relevance of messages, thus \processes can stop forwarding
-messages as soon as the corresponding predicate becomes unverified.
-For instance, a \process from Paris could scoped broadcast messages to
-all \processes in Paris. This requires \processes to store and
-maintain their city location in their local state. \Processes stop
-delivering and forwarding their received messages when they come from
-a different city.  In another instance, a \process from Paris could
-scoped broadcast messages to all \processes in Paris plus neighboring
-cities. This requires \processes to overload forwarded messages the
-first time they reach another city. The predicate checks if messages
-already reached two distinct cities before delivery. Similarly to
-uniform reliable broadcast, scoped broadcast implementations expose
-different trade-offs on space, time, and communication.
+work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
+also highlights that epidemic propagation and scoped broadcast have
+well-aligned preoccupations. More precisely, it underlines the transitive relevance of
+messages, thus \processes can stop forwarding messages as soon as the
+corresponding predicate becomes unverified.
+%For instance, a \process
+%from Paris could scoped broadcast messages to all \processes in
+%Paris. This requires \processes to store and maintain their city
+%location in their local state. \Processes stop delivering and
+%forwarding their received messages when they come from a different
+%city.  In another instance, a \process from Paris could scoped
+%broadcast messages to all \processes in Paris plus neighboring
+%cities. This requires \processes to overload forwarded messages the
+%first time they reach another city. The predicate checks if messages
+%already reached two distinct cities before delivery. Similarly to
+%uniform reliable broadcast, scoped broadcast implementations expose
+%different trade-offs on space, time, and communication.
 
-Next Section introduces an adaptive scoped broadcast where the state
-of each \process is dynamic and changes depending on all distinct
-scopes that exist in the system.
-
-\section{Adaptive scoped broadcast}
-\label{sec:adaptive}
-
-In this section, we propose to dynamically adapt the scopes of \NAMEB
-using \NAMEB itself for the sake of efficiency: a \NAMEB message may
-modify the state of a \process, consequently changing predicate
-evaluations over deliveries.  At any time, a \process decides whether
-or not it becomes the center (or \emph{source}) of a scope (or
-\emph{partition}). \Processes must eventually rally the partition
-corresponding to their closest source despite concurrent operations,
-and dynamic changes in the network.
-
-\noindent In that regard, we introduce \NAME (stands for
-\underline{A}daptive \underline{S}coped broad\underline{cast}), a
-wait-free reactive protocol for dynamic logical partitioning that
-enables adaptive scoped broadcast in dynamic distributed
-systems. \NAME's operation guarantees that \processes eventually reach
-consistent partitioning by efficiently propagating their state
-changes. \NAME's overhead actually depends on its operations and
-current partitions in the system. When the system becomes quiescent,
-\processes eventually converge to their respective partition and do not
-require further communication afterward.
-
-\noindent This section starts by introducing consistent partitioning
-and its implementation when a \process can only become a new source to
-create a new partition, i.e., it cannot revoke its self-appointed
-status of source. Then, it extends to include the latter behavior: it
-introduces the properties that guarantee consistent partitioning in
-such context, and it details our implementation called \NAME along
-with its complexity analysis.
+\NAMEB is used to change the state of each \process dynamically, depending on all partitions that exist in the system.
 

### 2021-04-22 input/abstract.tex
wip intro, minor fix in other sections

@@
   Our complexity analysis supported by simulations shows that \NAME
-  scales well in terms of generated traffic and termination time,
-  especially in dynamic \TODO{weird, we do not really test dynamic}
-Edge infrastructures. As such, \NAME can
-  constitute the building block of new geo-distributed services.
+  scales well in terms of generated traffic and termination time. As
+  such, \NAME can constitute the building block of new geo-distributed
+  services.
 \end{abstract}
+
+\begin{IEEEkeywords}
+Edge infrastructures, decentralized content indexing, scoped
+broadcast, logical partitioning protocol
+\end{IEEEkeywords}
 

### 2021-04-22 input/background.tex
wip intro, minor fix in other sections

@@
 needs it. In that regard, \Process~$R$ only needs to disseminate a
-message notifying all other processes of its new content. \Process~$R$
+message notifying all other \processes of its new content. \Process~$R$
 can use uniform reliable broadcast~\REF and epidemic propagation~\REF
@@
 \begin{inparaenum}[(i)]
-\item every process eventually knows the content location
+\item every \process eventually knows the content location
 \item efficiently using neighbor-to-neighbor communication.
@@
 \processes to communicate with based on metrics~\REF, \processes in
-our context have no control over their neighboring processes.
+our context have no control over their neighboring \processes.
 
@@
 partitions. The scope of scoped broadcast changes over receipts by
-processes. Dynamic partitioning raises additional challenges related
+\processes. Dynamic partitioning raises additional challenges related
 to concurrent operations where removed partition would block the

### 2021-04-22 input/introduction.tex
fix refs
wip intro, minor fix in other sections

@@
 
-There is an ongoing evolution of storing data from the cloud to the
-edges of the network. Either because it is where it has been created
-and it is too expensive to be transmitted through the network, or
-because it has been replicated to bring data closer to the end users
-~\cite{shi2016edge, foggy_cache, cachier}.
+\input{input/figpartitionintuition.tex} %% positioning
+
+In recent years, the data storage paradigm shifted from centralized in
+the cloud to distributed at the edges of the network. 
+% There is an ongoing evolution of storing data from the cloud to the
+% edges of the network.
+This shift aims at keeping the data close to
+\begin{inparaenum}[(i)]
+\item its producers since data may be too expensive or sensitive to be
+  transmitted through the network; and
+\item its consumers so data may quickly and efficiently reach
+  them~\cite{cachier, foggy_cache, shi2016edge}.
+\end{inparaenum}
+%% It avoids transmitting Either because it is where it has been
+%% created and it is too expensive to be transmitted through the
+%% network, or because it has been replicated to bring data closer to
+%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
 %
-To favour this transition, the design and the development of building
-blocks to manage data sets across Edge infrastructures have been
-investigated for the last few years \cite{confais2017performance,
-  confais2017object, fogstore, hasenburg2020towards}.  Although these
-systems, provide good properties such as favouring network traffic
-confinement by writting data locally and replicating contents
-according to the effective needs, determining the location where to
-get the content might be more expensive than retrieving the content
-itself.
+To favour this transition, new designs for data management across Edge
+infrastructures have been investigated~\cite{confais2017object,
+  confais2017performance, fogstore, hasenburg2020towards}.  They
+enable strategies to confine traffic by writing data locally and
+replicating content according to effective needs. However, locating
+content remains challenging. Retrieving a content location may
+actually take more time than retrieving the content itself.
+%% Although
+%% these systems, provide good properties such as favouring network
+%% traffic confinement by writting data locally and replicating contents
+%% according to the effective needs, determining the location where to
+%% get the content might be more expensive than retrieving the content
+%% itself.
 %
-Indeed, those systems, when not using a centralized index stored in a
-Cloud, rely on a Distributed Hash Table (DHT) across the different
-nodes composing the infrastructure: When a client wants to access a
-specific content, it has to perform a request to a remote process to
-determine from which node(s) it will retrieve the content.  Once it has
-retrieved the content, a local replica
-is created to improve the performance for future accesses and the
-process in charge of maintaining the index is contacted once again to reflect this
-new location.
+Indeed, these systems, when not using a centralized index hosted in a
+Cloud~\REF, rely on distributed hash
+tables~\cite{maymounkov2002kademlia} spread across the different
+\processes composing the infrastructure. When a client wants to access
+specific content, it requests a remote \process to provide at least
+one \process identity to retrieve this content from. After it
+retrieved the content, the client can create another replica to
+improve the performance of future accesses, but it must contact the
+content indexing service again to notify of such change.
+%% a local replica is created to improve the performance for future
+%% accesses and the process in charge of maintaining the index is
+%% contacted once again to reflect this new location.
 %
@@
 
-Such a protocol contradicts with the objective of Edge
-infrastructures that aims at reducing the impact of the
-latency as well as the volume of data passing through the network:
-\begin{itemize}
-  \item In addition to hot spot and partitioning issues, accessing a
-    remote node to find the location(s) of a content incurs an
-    additional delay~\cite{asrese2019measuring, doan2019tracing} to
-    get the object, before being able to start its downloading.
-  \item There is no information to select the ``best'' node among the
-     possible candidates from which the content  could be
-     retrieved. In most cases, this results in parallel requests performed by the client node to
-     each candidate with the goal of retrieving the content as efficient
-     as possible.
-\end{itemize}
+These approaches directly contradict with the objectives of Edge
+infrastructures that aim at reducing the impact of latency as well as
+the volume of data passing through the network.
+%
+First, accessing a remote \node to request content location(s) raises
+hot spots and availability issues. But most importantly, it results in
+additional delays that occur even before the actual download
+started~\cite{asrese2019measuring, doan2019tracing}.
+%
+Second, the client gets a list of content locations at the discretion
+of content indexing services. Without information about these
+locations, it often ends up downloading from multiple replica hosts,
+yet only keeping the fastest answer~\REF. In turns, either a client wastes
+network resources, or faces lower response time.
+%% there is no information to select the ``best'' node among the possible
+%% candidates from which the content could be retrieved. In most cases,
+%% this results in parallel requests performed by the client node to each
+%% candidate with the goal of retrieving the content as efficient as
+%% possible.
 
@@
 details the motivation behind our proposal.
-Section~\ref{sec:adapative} describes the protocol behavior, as well
+Section~\ref{sec:adaptive} describes the protocol behavior, as well
 as the formal definition of the underlying

### 2021-04-22 input/introduction.tex
intro until contribution , In this paper [...]

@@
 locations, it often ends up downloading from multiple replica hosts,
-yet only keeping the fastest answer~\REF. In turns, either a client wastes
-network resources, or faces lower response time.
-%% there is no information to select the ``best'' node among the possible
-%% candidates from which the content could be retrieved. In most cases,
-%% this results in parallel requests performed by the client node to each
-%% candidate with the goal of retrieving the content as efficient as
-%% possible.
+yet only keeping the fastest answer~\REF. In turns, either clients
+waste network resources, or face lower response time. 
+%% there is no information to select the ``best'' node among the
+%% possible candidates from which the content could be retrieved. In
+%% most cases, this results in parallel requests performed by the
+%% client node to each candidate with the goal of retrieving the
+%% content as efficient as possible.
 
-A ``simple'' way to tackle the aforementioned limitations would be to
-maintain on each node composing the infrastructure and for each
-content, an index of all replicas (and their ``distance'').  In such
-an approach, each time a new replica is created or deleted, a message
-is broadcasted from the node that performed the operation (\ie the
-source) to all nodes, increasing the distance information at each hop.
-%
-In addition to being complicated for large-scale systems, maintaining
-a global view on each node is useless as there is no interest to
-inform a node of the creation/removal of a replica at the opposite of
-the network (each node trying to get content from the ``closest''
-one).  In other words, the broadcast should be limited to a partition
-of the infrastructure, (\ie the subset of nodes that has to update the
-current location for this particular content). Obviously, these
-partitions depend and evolve according to concurrent operations made
-by nodes (replica creation/removal) as well as dynamic changes in the
-infrastructure (network failures, node apparitions/leaves).
+To tackle aforementioned limitations, every \process that might
+request or replicate content must also host its own content indexing
+service in a fully decentralized fashion~\cite{kermarrec2015want}. At
+any time, it can immediately locate the closest replica of specific
+content.  A naive approach would be that every \process indexes and
+ranks \emph{every live} replica along with its \emph{location}
+information. When creating or destroying a replica, a \process would
+notify all other \processes by efficiently broadcasting its
+operation~\cite{birman1999bimodal, hadzilacos1994modular,
+  raynal2013distributed}. Unfortunately, this also contradicts with
+Edge infrastructure objectives, for such protocol does not confine the
+traffic generated to maintain its indexes. A \process may acknowledge
+the existence of replicas at the other side of the network while there
+already exists a replica right next to it.
+
+Instead, a \process creating a replica should notify all and only
+\processes that have no closer replica. This would create
+interconnected sets of \processes, or \emph{partitions}, gathered
+around a \emph{source} being their respective replica. A \process
+deleting its replica should notify all members of its partition so
+they can rally their current closest partition. A periodic
+advertisement protocol already provides both these operations for
+routing purposes~\cite{hemmati2015namebased}. However, its functioning
+requires
+\begin{inparaenum}[(i)]
+\item to generate traffic even when the system is quiescent, and
+\item to finely tune physical-time-based intervals that depend on
+  network topology parameters such as network diameter.
+\end{inparaenum}
+
+%% A ``simple'' way to tackle the aforementioned limitations would be to
+%% maintain on each node composing the infrastructure and for each
+%% content, an index of all replicas (and their ``distance'').  In such
+%% an approach, each time a new replica is created or deleted, a message
+%% is broadcasted from the node that performed the operation (\ie the
+%% source) to all nodes, increasing the distance information at each hop.
+%% %
+%% In addition to being complicated for large-scale systems, maintaining
+%% a global view on each node is useless as there is no interest to
+%% inform a node of the creation/removal of a replica at the opposite of
+%% the network (each node trying to get content from the ``closest''
+%% one).  In other words, the broadcast should be limited to a partition
+%% of the infrastructure, (\ie the subset of nodes that has to update the
+%% current location for this particular content). Obviously, these
+%% partitions depend and evolve according to concurrent operations made
+%% by nodes (replica creation/removal) as well as dynamic changes in the
+%% infrastructure (network failures, node apparitions/leaves).
 

### 2021-04-22 input/introduction.tex
reworkd intro done

@@
 locations, it often ends up downloading from multiple replica hosts,
-yet only keeping the fastest answer~\REF. In turns, either clients
+yet only keeping the fastest answer~\REF. In turns, clients either
 waste network resources, or face lower response time.
@@
 the existence of replicas at the other side of the network while there
-already exists a replica right next to it.
+already exists a replica next to it.
 
 Instead, a \process creating a replica should notify all and only
-\processes that have no closer replica. This would create
-interconnected sets of \processes, or \emph{partitions}, gathered
-around a \emph{source} being their respective replica. A \process
-deleting its replica should notify all members of its partition so
-they can rally their current closest partition. A periodic
-advertisement protocol already provides both these operations for
-routing purposes~\cite{hemmati2015namebased}. However, its functioning
-requires
+\processes that have no closer replica in the system. This would
+create interconnected sets of \processes, or \emph{partitions},
+gathered around a \emph{source} being their respective replica. A
+\process deleting its replica should notify all members of its
+partition so they can rally their current closest partition. A
+periodic advertisement protocol already provides both these operations
+for routing purposes~\cite{hemmati2015namebased}. However, its
+functioning requires
 \begin{inparaenum}[(i)]
@@
 
-In this paper, we propose a first implementation of such a protocol.
-Entitled Adaptive Scoped broadcast (\NAME), 
-our protocol relies on a primitive that forwards
-messages until a certain condition is reached, \ie the scope. The
-scope is defined by a boolean function (predicate) that returns
-whether a message should be propagated or not around its
-broadcaster. In the current scenario, the stop condition is related to
-the distance to the nearest replica : if the message that a node receives
-indicates a content has a longer distance than that which the node
-knows then the transfer of the message is useless and so stopped.
+In this paper, we first define scoped broadcast has a communication
+primitive that allows epidemic dissemination of messages as long as
+receiving \processes verify an application-dependant predicate.
+
+\noindent Then, we propose \NAME, a logical partitioning protocol that
+uses \underline{s}coped broad\underline{cast} to \underline{a}dapt its
+partitions, \ie scopes, to creations and deletions of partitions in
+the system. Each source advertises its existence to all possibly
+interested \processes, \ie only interconnected \processes of its
+partition plus \processes bordering its partition. In turns, \NAME
+scales well to the number of sources since the higher the number of
+partitions, the earlier the dissemination of notifications stops.
 %
-This primitive is used to guarantee that eventually, every node knows
-its best partition, hence its closest replica, despite concurrent
-events and receipt orders. Overall, \NAME is a wait-free reactive protocol for
-dynamic logical partitioning.  Its overhead actually depends on
-its operations and current partitions in the system. When the system
-becomes quiescent, nodes eventually converge to their respective
-partition and do not require further communication afterward.
+%% In this paper, we propose a first implementation of such a protocol.
+%% Entitled Adaptive Scoped broadcast (\NAME), 
+%% our protocol relies on a primitive that forwards
+%% messages until a certain condition is reached, \ie the scope. The
+%% scope is defined by a boolean function (predicate) that returns
+%% whether a message should be propagated or not around its
+%% broadcaster. In the current scenario, the stop condition is related to
+%% the distance to the nearest replica : if the message that a node receives
+%% indicates a content has a longer distance than that which the node
+%% knows then the transfer of the message is useless and so stopped.
+%
 
-\TODO{talk about the proof}
+\noindent In addition, \NAME guarantees that despite concurrent
+operations, every \process eventually knows one, and only one, source:
+its closest. \NAME being reactive, when the system becomes quiescent,
+\processes do not require further communications.
+%% This primitive is used to guarantee that eventually, every node knows
+%% its best partition, hence its closest replica, despite concurrent
+%% events and receipt orders. Overall, \NAME is a wait-free reactive protocol for
+%% dynamic logical partitioning.  Its overhead actually depends on
+%% its operations and current partitions in the system. When the system
+%% becomes quiescent, nodes eventually converge to their respective
+%% partition and do not require further communication afterward.
+% \TODO{talk about the proof}
 
-We evaluated our protocol through two simulation scenarios using
-\textit{Peersim}~\cite{montresor2009peersim}. First, we confirm that
-\NAME allow consistent partitioning in an ad-hoc network composed of
-10K nodes.  Second, we illustrate how \NAME enables the lock down of
-the traffic in dynamic inter autonomous systems.  More precisely, we
-simulated a worldwilde infrastructure by duplicating the GEANT
-topology - a real infrastructure spanning across Europe – and by
-connecting these two clusters with a high latency link: 200 ms
-simulating cross-continental communications such as Europe-America.
+\noindent Simulations empirically support our complexity analysis and
+the scalability of \NAME in large scale networks comprising 10k
+\processes. Our experiments also highlight the relevance of \NAME in
+autonomous systems. \NAME would allow to lock down the traffic
+generated by content indexing, even in contexts where \emph{physical}
+partitioning may occur.
 
-%\input{input/figadd.tex} %% positioning (belong to problem & motivation)
+\noindent In that regard, \NAME can constitute the building block of
+new geo-distributed services.
+
+%% We evaluated our protocol through two simulation scenarios using
+%% \textit{Peersim}~\cite{montresor2009peersim}. First, we confirm that
+%% \NAME allow consistent partitioning in an ad-hoc network composed of
+%% 10K nodes.  Second, we illustrate how \NAME enables the lock down of
+%% the traffic in dynamic inter autonomous systems.  More precisely, we
+%% simulated a worldwilde infrastructure by duplicating the GEANT
+%% topology - a real infrastructure spanning across Europe – and by
+%% connecting these two clusters with a high latency link: 200 ms
+%% simulating cross-continental communications such as Europe-America.
 
 The rest of this paper is organized as
-follows. Section~\ref{sec:background} introduces background, and
-details the motivation behind our proposal.
-Section~\ref{sec:adaptive} describes the protocol behavior, as well
-as the formal definition of the underlying
-algorithms. Section~\ref{sec:experimentation} presents the Peersim
-evaluations.  Related work is discussed in
-Section~\ref{sec:related_work} and finally
-Section~\ref{sec:conclusion} concludes this article and highlights a
-few future works.
+follows. Section~\ref{sec:background} illustrates the motivation and
+problem behind our proposal.  Section~\ref{sec:adaptive} describes
+dynamic consistent partitioning and its implementation along with its
+complexity. Section~\ref{sec:experimentation} presents our
+evaluations.  Section~\ref{sec:related_work} reviews related
+work. Finally, Section~\ref{sec:conclusion} concludes and discusses
+future work.
 

### 2021-04-22 input/abstract.tex
meow

@@
   partitioning:
-\TODO{weird}
   every \process only indexes its closest replica, and

### 2021-04-22 input/introduction.tex
meow

@@
 Indeed, these systems, when not using a centralized index hosted in a
-Cloud~\REF, rely on distributed hash
-tables~\cite{maymounkov2002kademlia} spread across the different
-\processes composing the infrastructure. When a client wants to access
-specific content, it requests a remote \process to provide at least
-one \process identity to retrieve this content from. After it
-retrieved the content, the client can create another replica to
-improve the performance of future accesses, but it must contact the
-content indexing service again to notify of such change.
+Cloud, rely on distributed hash tables~\cite{maymounkov2002kademlia}
+spread across the different \processes composing the
+infrastructure. When a client wants to access specific content, it
+requests a remote \process to provide at least one \process identity
+to retrieve this content from. After it retrieved the content, the
+client can create another replica to improve the performance of future
+accesses, but it must contact the content indexing service again to
+notify of such change.
 %% a local replica is created to improve the performance for future
@@
 hot spots and availability issues. But most importantly, it results in
-additional delays that occur even before the actual download
-started~\cite{asrese2019measuring, doan2019tracing}.
+additional delays~\cite{asrese2019measuring, doan2019tracing} that
+occur even before the actual download started.
 %
@@
 locations, it often ends up downloading from multiple replica hosts,
-yet only keeping the fastest answer~\REF. In turns, clients either
-waste network resources, or face lower response time.
+yet only keeping the fastest answer. In turns, clients either waste
+network resources, or face lower response time.
 %% there is no information to select the ``best'' node among the
@@
 
-In this paper, we first define scoped broadcast has a communication
+In this paper, we first define scoped broadcast as a communication
 primitive that allows epidemic dissemination of messages as long as

### 2021-04-22 input/background.tex
meow
background

@@
 content location.  In this paper, we tackle the content indexing issue
-as a logical partitioning problem. This section motivate this shift
-and explains the shortcomings of existing implementations.
+as a dynamic logical partitioning problem. This section motivates this
+shift and explains the shortcomings of existing implementations.
 
@@
 \item every \process eventually knows the content location
-\item efficiently using neighbor-to-neighbor communication.
+\item by efficiently using neighbor-to-neighbor communication.
 \end{inparaenum}
@@
 a lot of unnecessary traffic. Instead, \processes need a communication
-primitive that propagate notifications as long as \processes receiving
-them consider them useful based on location information they carry. We
-call such primitive \emph{scoped broadcast}, for messages transitively
-reach a subset of interconnected \processes (the \emph{scope}) by
-evaluating a predicate starting at its broadcaster (the
-\emph{source}). Using this primitive, \processes can lock down the
-traffic of content indexing to relevant \processes.
+primitive that propagates notifications within a scope by evaluating a
+predicate, starting at its broadcaster (the \emph{source}).
+In other terms, \processes propagate these notifications as long as they
+consider them useful based on location information they carry. We call
+such primitive \emph{scoped broadcast}, for messages transitively
+reach a subset of interconnected \processes (the \emph{scope})
+Using this primitive, \processes can lock down the traffic of content
+indexing to relevant \processes.
 
@@
 
-Every \process ends up with at least 1 known replica that is its
+Every \process ends up with at least one known replica that is its
 closest. The set of interconnected \processes with the same closest
@@
 one, partition. Contrarily to membership protocols that choose
-\processes to communicate with based on metrics~\REF, \processes in
-our context have no control over their neighboring \processes.
+neighboring \processes to communicate with based on metrics~\REF,
+\processes in our context have no control over their neighboring
+\processes: they cannot add nor remove communication links.
 
@@
 Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
-destroys its replica. Every \processes that belong to its green
+destroys its replica. Every \processes that belonged to its green
 partition must choose another partition to be in. While it makes sense
@@
 fill the gap left open by \Process~$G$. Instead, we want to trigger
-scoped broadcast at bordering \processes of red and blue
+once again scoped broadcast at bordering \processes of red and blue
 partitions. The scope of scoped broadcast changes over receipts by
 \processes. Dynamic partitioning raises additional challenges related
-to concurrent operations where removed partition would block the
+to concurrent operations where removed partitions would block the
 propagation of other partitions.
@@
 
-Next Section details adaptive scoped broadcast in dynamic networks. It
-details the properties of such protocol, and provides an
-implementation along with its complexity.
+Next Section details the properties of adaptive scoped broadcast in
+dynamic networks, and provides an implementation along with its
+complexity.
 

### 2021-04-22 input/proposal.tex
meow

@@
 neighboring \processes that estimate they are closer to this source
-than any other source. Such distance (or \emph{weight}) is
+than any other one. Such distance (or \emph{weight}) is
 application-dependant: in the context of maintaining distributed
@@
 At any time, a source can revoke its self-appointed status of source,
-hence deleting its partition from the system, by executing a
-\texttt{Del} operation. All \processes that belong to this partition
-must eventually choose another partition to belong to. In
+by executing a \texttt{Del} operation, hence deleting its partition
+from the system. All \processes that belong to this partition must
+eventually choose another partition to belong to. In
 Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$

### 2021-04-22 input/background.tex
add ref in section2

@@
 infrastructures ranging from centralized services to fully
-decentralized approaches~\REF. We advocate for the latter where
+decentralized approaches~\cite{squirrel}. We advocate for the latter where
 \processes host the service themselves so they do not need to request
@@
 message notifying all other \processes of its new content. \Process~$R$
-can use uniform reliable broadcast~\REF and epidemic propagation~\REF
+can use uniform reliable broadcast~\cite{hadzilacos1994modular} and epidemic propagation~\cite{epidemic-protocol}
 to guarantee that
@@
 one, partition. Contrarily to membership protocols that choose
-neighboring \processes to communicate with based on metrics~\REF,
+neighboring \processes to communicate with based on metrics~\cite{t-man},
 \processes in our context have no control over their neighboring

### 2021-04-22 input/figpartitionintuition.tex
add ref in section2

@@
 \subfloat[\Process $G$ destroys its replica.
-\Processes that belong to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
+\Processes that belonged to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
 %

### 2021-04-22 input/figproof.tex
some spacing and figure placement

--- 2021-04-20 input/figproof.tex
@@
       $\delta$ messages as often as possible (I'); detect possible inconsistencies
-      when parents' $\alpha$ messages contradict delivery history (III); notify
+      when parents' $\alpha$ messages contradict history or state (III); notify
       processes of possible inconsistencies (IV).]

### 2021-04-22 input/related_work.tex
update label
some spacing and figure placement
rework related work

@@
 \section{Related Work}
-\label{related_work}
+\label{sec:related_work}
+Content indexing in geo-distributed infrastructures has been studied through various approaches. 
+Offering an indexing service which is either hosted by a centralized entity or distributed through nodes of the network has long been the predominant one.
+This mainly requires (i) to have access to the list of current replica locations and (ii) to be aware of the topology to compute which replica is the closest for a given location.
 
-In the context of this paper, a content indexing service enables that for any content, every node is able to access its closest replica.
-Basically, offering such a service requires (i) to have access to the list of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location.
-
-(i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
-However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
-Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example.
+(i) Deploying a centralized server that maintains an index of all replica locations has been proposed in~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
+These solutions suffer from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
+Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, mdht} for example.
 In the latter, each node stores a part of the index, defined by an interval between hash values.
 Before downloading any object, a node first
-hashes the content to obtain the address of the node that stores the replica localizations of this given object.
+hashes the content to obtain the address of the node that stores the replica locations of this given object.
 After obtaining from the remote node the list of available replicas, it can select the closest copy to download from.
-We emphasize that, in this setting, the DHT only stores information about replicas localizations, not the content itself.
+We emphasize that, in this setting, the DHT only stores information about replicas locations, not the content itself.
 DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.
@@
 This is a well-studied problem in the network community and numerous protocols have been proposed.
-As for the index, this knowledge about the topology can be either centralized[REF] or distributed[REF].
+As for the index, this knowledge about the topology can be either centralized~\cite{topology-discovery} or distributed like in routing protocols such as OSPF (Open Shortest Path First).
+All these solutions require to contact a remote node (either a server or a DHT node) to request this index 
+which is costly in terms of latency while in contradiction with Edge infrastructure constraints, as previsouly explained.
 
-However, solutions that require to contact a remote node (either a server or a DHT node) to request this index usually implies reaching nodes out of the their geographical scope, as already explained.
+The opposite approach consists in hosting the index directly on the nodes, avoiding any prior request to access a content.   
+%This requires notifying nodes of replica creations and removals along with information about the evolving topology. 
+Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica locations for all nodes~\cite{nlsr}.
+Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
+Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}.
+Yet both solutions inherently imply that every nodes will eventually receive all messages.
+
 At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create a scope-related partioning, as proposed in this paper.
-Yet, such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology.
+Such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology.
 Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric.
@@
 Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.
-Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
-On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica.
+Likewise, this also prevents from using solutions that periodically advertise their cache content~\cite{hemmati2015namebased, garcia-lopez} as they also inccur an overhead even in quiet contexts without any update.
+Moreoever, such solutions necessarily rely on physical timeouts that could lead to either premature removals of partitions when they are still operating; or slow convergence where processes wrongly believe they belong to a partition that was removed.
+
+%Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
+%On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica.
 This enables for a request to be caught \textit{on-path}, and be redirected to the closest replica.

### 2021-04-22 input/background.tex

@@
 primitive that propagates notifications within a scope by evaluating a
-predicate, starting at its broadcaster (the \emph{source}).
-In other terms, \processes propagate these notifications as long as they
-consider them useful based on location information they carry. We call
-such primitive \emph{scoped broadcast}, for messages transitively
-reach a subset of interconnected \processes (the \emph{scope})
-Using this primitive, \processes can lock down the traffic of content
-indexing to relevant \processes.
+predicate, starting at its broadcaster (the \emph{source}).  In other
+terms, \processes propagate notifications as long as they consider
+them useful based on location information they carry. We call such
+primitive \emph{scoped broadcast}, for messages transitively reach a
+subset of interconnected \processes (the \emph{scope}). Using this
+primitive, \processes can lock down the traffic of content indexing to
+relevant \processes.
 
@@
 Next Section details the properties of adaptive scoped broadcast in
-dynamic networks, and provides an implementation along with its
+dynamic networks, and provides an implementation called \NAME along with its
 complexity.

### 2021-04-22 input/introduction.tex

@@
 primitive that allows epidemic dissemination of messages as long as
-receiving \processes verify an application-dependant predicate.
-
-\noindent Then, we propose \NAME, a logical partitioning protocol that
-uses \underline{s}coped broad\underline{cast} to \underline{a}dapt its
+receiving \processes verify an application-dependant predicate.  Then,
+we propose \emph{\NAME}, a logical partitioning protocol that uses
+\underline{s}coped broad\underline{cast} to \underline{a}dapt its
 partitions, \ie scopes, to creations and deletions of partitions in
@@
 scales well to the number of sources since the higher the number of
-partitions, the earlier the dissemination of notifications stops.
+partitions, the earlier the dissemination stops.
 %

### 2021-04-22 input/proposal.tex

@@
 
-\vfill \TODO{spacing for intro and related work: 2.5 pages}
-\newpage
+% \vfill \TODO{spacing for intro and related work: 2.5 pages}
+% \newpage
 
@@
   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
-  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from \Process
-  $i$ to \Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
-    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
-  \pi_{ij}[m+1] \rangle \in E$.
+  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
+  \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
+    k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
+  \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
 \end{definition}
@@
 \begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
-  When \Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
+  When \Process~$x$ scoped \underline{b}roadcasts $b_x(m)$ a
   \underline{m}essage $m$, every correct \process $y$ within a scope
@@
   Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
-  the \underline{p}artition including at least \Process $s$, each
-  \process belongs to at most one partition $\forall p,q \in V, \forall
+  the \underline{p}artition including at least \Process~$s$, each
+  \process belongs to at most one partition \smash{\small$\forall p,q \in V, \forall
   s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
-  \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
+  \vee s_1 = s_2$}, and there exists at least one path $\pi_{ps}$ of
   \processes that belong to this partition $\forall q \in \pi_{ps}: q
@@
 together, a \process becoming a source must notify every \process that
-is closer to it than any other source. As stated in
-Section~\ref{sec:scoped}, since epidemic dissemination and scoped
-broadcast have well-aligned preoccupations, we assume implementations
-relying on forwarding of messages from neighbor to neighbor.
+is closer to it than any other source. Since epidemic dissemination
+and scoped broadcast have well-aligned preoccupations, we assume
+implementations relying on forwarding of messages from neighbor to
+neighbor.
 
@@
 eventually receives the message $m$ \underline{s}ent to it by a
-\process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a monotonically growing
-system ($G^t \subseteq G^{t+1}$); \processes eventually reach
-consistent partitioning if each \process eventually forwards its best
-known partition.
+\process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
+reach consistent partitioning if each \process eventually forwards its
+best known partition.
 \end{theorem}
+
+\input{input/figadd.tex}
 
@@
   $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
-  hence forwards such $\alpha$ message to its -- current or future --
-  neighbors. Since communication links are reliable, neighboring
-  \processes eventually receive such notification $\forall \langle
-  s_1, q \rangle \in E, s_1 \in S \iff \eventually
-  r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most importantly, whatever the order
-  of received messages, every \process $q'$ in this neighborhood --
-  such that there exists no better partition $s_2$ than the received
-  one -- delivers and forwards it: $\forall s_2 \in S: |\Pi_{q' s_1}|
-  < |\Pi_{q' s_2}| \implies \eventually d_{q'}(\alpha_{s_1}^{w_{s_1
-      q'}})$. By transitivity, the message originating from $s_1$
-  reaches all such \processes through their shortest paths: $\forall
-  q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| < |\Pi_{q'' s_2}|
-  \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.
-  Since there exists only one best sum of weights per \process that
-  can never be retracted, \processes eventually reach consistent
-  partitioning.
+  hence forwards such $\alpha$ message to its neighbors. Since
+  communication links are reliable, neighboring \processes eventually
+  receive such notification $\forall \langle s_1, q \rangle \in E, s_1
+  \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
+  importantly, whatever the order of received messages, every \process
+  $q'$ in this neighborhood -- such that there exists no better
+  partition $s_2$ than the received one -- delivers and forwards it:
+  $\forall s_2 \in S: |\Pi_{q' s_1}| < |\Pi_{q' s_2}| \implies
+  \eventually d_{q'}(\alpha_{s_1}^{w_{s_1 q'}})$. By transitivity, the
+  message originating from $s_1$ reaches all such \processes through
+  their shortest paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q''
+    s_1}| < |\Pi_{q'' s_2}| \implies \eventually
+  d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.  Since there exists only
+  one best sum of weights per \process that can never be retracted,
+  \processes eventually reach consistent partitioning.
   %% /!\ not equivalence for there exists other implementations.
@@
   \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding a partition by \Process $p$.}
+  \caption{\label{algo:add}Adding a partition by \Process~$p$.}
 \end{algorithm}
-
-\input{input/figadd.tex}
 
@@
 
-At any time, a source can revoke its self-appointed status of source,
+At any time, a source can revoke its self-appointed status of source
 by executing a \texttt{Del} operation, hence deleting its partition
@@
 that respectively include $\{a\}$, and $\{b, c, d\}$. In
-Figure~\ref{fig:delA}, \Process $a$ deletes its partition. It notifies
-all neighboring \processes -- here only \Process $b$ -- that may
-belong to its partition using \NAMEB. Upon receipt, \Process $b$
+Figure~\ref{fig:delA}, \Process~$a$ deletes its partition. It notifies
+all neighboring \processes -- here only \Process~$b$ -- that may
+belong to its partition using \NAMEB. Upon receipt, \Process~$b$
 discards the message $\delta_a$, for the latter does not target the
-former's partition. \Process $b$ sends its own knowledge of best
-partition $\alpha_d^3$ that may prove to be the best for \Process
-$a$. Eventually, every \processes belong to the same partition
-$P_d$. In this scenario, they reach consistent partitioning.
+former's partition. \Process~$b$ sends its own knowledge of best
+partition $\alpha_d^3$ that may prove to be the best for
+\Process~$a$. Eventually, every \processes belong to the same
+partition $P_d$. In this scenario, they reach consistent partitioning.
 
@@
 \input{input/figdel.tex}
+
+\input{input/figproblem.tex}
 
@@
 
-\input{input/figproblem.tex}
-
 One could guarantee consistent partitioning by always propagating the
@@
 \processes join or leave the system, create or delete partitions, at
-any time.  \TODO{Another paragraph with JJ approach?}  Instead, we
-propose to use the delivery order at each \process to detect possible
-inconsistencies and solve them. Together, \processes eventually remove
-all stale control information (transiting messages and local states)
-of the system leaving room for propagation of messages about
-up-to-date partitions.
+any time.  Instead, we propose to use the delivery order at each
+\process to detect possible inconsistencies and solve them. Together,
+\processes eventually remove all stale control information (transiting
+messages and local states) of the system leaving room for propagation
+of messages about up-to-date partitions.
 
@@
 
+\vfill
+
+\TODO{spacing.}
+
+\newpage
+
 \subsection{Implementation and complexity}
@@
   \input{input/algoascast.tex}
-  \caption{\label{algo:ascast}\NAME at \Process $p$ in static networks.}
+  \caption{\label{algo:ascast}\NAME at \Process~$p$ in static networks.}
 \end{algorithm}
@@
   \input{input/algoedges.tex}
-  \caption{\label{algo:edges}\NAME at \Process $p$ in dynamic networks.}
+  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
 \end{algorithm}

### 2021-04-23 input/proposal.tex
minors

@@
 $\delta_a$. It never reaches \Process~$c$ nor \Process~$d$. Also,
-\Process~$c$ and \Process~$d$ do not deliver any $\alpha_d$ or
-$\delta_d$ since they already delivered it. The system converges to an
-inconsistent state where some \processes assume they belong to a
-partition while it does not exist anymore. Naive propagation of
-$\alpha$ and $\delta$ messages is insufficient to guarantee consistent
-partitioning when each \process can add or delete its partition at any
-time. \Processes need to exploit their local knowledge gathered over
-message receipts.
+\Process~$c$ does not deliver $\alpha_d$ and $\delta_d$ since it
+already delivered it. The system converges to an inconsistent state
+where some \processes assume they belong to a partition while it does
+not exist anymore. Naive propagation of $\alpha$ and $\delta$ messages
+is insufficient to guarantee consistent partitioning when any \process
+can add or delete its partition at any time. \Processes need to
+exploit their local knowledge gathered over message receipts.
 

### 2021-04-23 input/proposal.tex
mostly about implem

@@
 this answer, \processes act normally by propagating their changes when
-they improve. \TODO{Exemple with figure for detection?}
+they improve.
 
-\TODO{Rework this.}\NAME guarantees dynamic consistent partitioning by
-making extensive use of \process to \process communications. In terms
-of number of messages, in the average-case, a \process $i$ chosen
-uniformly at random among all \processes creates a logical
+\NAME guarantees dynamic consistent partitioning by making extensive
+use of \process-to-\process communications. It requires
+\begin{inparaenum}[(i)]
+\item purging stale control information, hence propagating $\delta$
+  messages; and
+\item retrieving the closest source, hence propagating $\alpha$
+  messages.
+\end{inparaenum}
+In terms of number of messages, in the average-case, a \process $i$
+chosen uniformly at random among all \processes creates a logical
 partition. Its messages $\alpha_i$ propagate through the network until
@@
       \log_2 a \rfloor}})$} \processes. This decreases every new
-partition until reaching $0$ \processes per new partition: even the
-chosen \process already belongs to its optimal partition. The average
-number of messages per \process is
+partition until reaching one \process per new partition: its
+source. The average number of messages per \process is
 \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
-      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
-  more messages (receipt bounded by $|O|$ as well).} Deleting the
-$a^{th}$ partition generates the exact same number of messages than
-the $a^{th}$ partition creation. \TODO{But what about echos?} In the
-worst-case, every new partition includes all but one \process
-belonging to the previous partition. The total number of messages
-after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
-a^2)$. As for the average-case, the number of messages for the
-partition deletion is identical to the number of messages of the
-corresponding partition creation.
+      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
+number of neighbors per \process. % \TODO{Multiple receipt and multiple
+%  delivery imply more messages (receipt bounded by $|O|$ as well).}
+Deleting the $a^{th}$ partition generates twice as many messages as
+creating the $a^{th}$ partition: $\delta$ messages travel through the
+partition, then $\alpha$ messages compete to fill the gap.  Overall,
+the communication complexity shows that \NAME scales well to the
+number of partitions.
+%% In the
+%% worst-case, every new partition includes all but one \process
+%% belonging to the previous partition. The total number of messages
+%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
+%% a^2)$. As for the average-case, the number of messages for the
+%% partition deletion is identical to the number of messages of the
+%% corresponding partition creation.
 
@@
 path of one of these \processes. Therefore, it triggers a competition
-between the two \processes only. Removing an edge between two
-\processes may invalidate the shortest path of one of involved
-\processes plus downstream \processes. To implement this behavior,
-\NAME uses the implementation of $\delta?$ messages. This prove costly
-but enables \NAME even in dynamic networks subject to physical
+between the two \processes only. If one or the other \process
+improves, the propagation of $\alpha$ messages operates normally.
+Removing an edge between two \processes may invalidate the shortest
+path of one of involved \processes plus downstream \processes. As a
+side effect, removing an edge may also impair the propagation of a
+partition delete. To implement this behavior, \NAME uses its
+implementation of $\delta?$ messages. This prove costly but
+enables \NAME even in dynamic networks subject to physical
 partitioning.
+
+Next Section provides the details of our experimentation that aim to
+evaluate the proposed implementation of logical dynamic partitioning
+in dynamic networks.
 

### 2021-04-23 input/conclusion.tex
temp commit

@@
 \label{sec:conclusion}
+
+How to design distributed system in order to deal with consistency,
+availability and partitioning is something our community has been
+working on for a long time.  Though important achievements have been
+with now building blocks have been proposed to help developers deal
+with these concerns, the advent of the Edge and IoT era raises a new
+complexity: how can we lock down the trafic only where it is
+essential!
 

### 2021-04-23 input/experiments.tex
minors
mostly about implem
address easy stuff in experiments

@@
-\vfill
-
-\TODO{spacing}
-
-\newpage
-
 \section{Experimentation}
@@
 
-This section aims at highlighting the properties of \NAME that enables
-adaptive scoped broadcast in dynamic networks. It answers the
-following questions: What is the overhead of reaching consistent
-partitioning using \NAME in large scale networks? Does \NAME is
-relevant in Edge infrastructures where \processes are geo-distributed
-into clusters? We performed the experimentation using PeerSim, a
-simulator written in Java that allows researchers to evaluate and
-assess distributed algorithms in large scale
-networks~\cite{montresor2009peersim}. The code is available on the
-Github platform at
-\TODO{\url{https://github.com/Chat-Wane/peersim-partition}}.
+This section describes the results of our experimentation evaluating
+the properties of \NAME that enables adaptive scoped broadcast in
+dynamic networks. It answers the following questions: What is the
+overhead of reaching consistent partitioning using \NAME in large
+scale networks?  Does \NAME is relevant in Edge infrastructures where
+\processes are geo-distributed into clusters? We performed the
+experimentation using PeerSim, a simulator written in Java that allows
+researchers to evaluate and assess distributed algorithms in large
+scale networks~\cite{montresor2009peersim}. The code is available on
+the Github platform at
+\url{https://anonymous.4open.science/r/peersim-partition-5592}.
 
@@
 \noindent We evaluate dynamic scoped broadcast. First, we create 100
-partitions one at a time: before adding a new partition, consistent
-partitioning must be reached. Second, we remove every partition one at
-a time, in the order of their creation, hence starting from the first
-and oldest partition that had been added.
+partitions one at a time: \processes reach consistent partitioning
+before we create each new partition. Second, we remove every partition
+one at a time, in the order of their creation, hence starting from the
+first and oldest partition that had been added.
 
@@
 Figure~\ref{fig:complexity} shows the results of this experiment. The
-top part of the figure shows the average traffic per \process per
-second divided between $\alpha$ and $\delta$ messages. The bottom part
-of the figure shows the time before reaching consistent partitioning.
+top part shows the average traffic per \process per second divided
+between $\alpha$ and $\delta$ messages. The bottom part shows the time
+before reaching consistent partitioning.
 
@@
 expensive, for $\alpha$'s must reach every \process which takes time
-and generate more traffic. Still, being reactive, as opposed as
-cycle-based protocols~\cite{jelasity2007gossip}, \NAME quickly
-converge towards consistent partitioning in only 350 milliseconds. The
-last and $100^{th}$ partition added around 21 seconds is the least
-expensive. By using scoped broadcast, control information only reaches
-a small subset of the whole network.
+and generate more traffic.  \NAME quickly converges towards consistent
+partitioning in only 350 milliseconds. The last and $100^{th}$
+partition added around 21 seconds is the least expensive. By using
+scoped broadcast, control information only reaches a small subset of
+the whole network.
 
@@
 triggering competition while the former aims at updating shortest
-paths. As corollary, the convergence time increases, for $\delta$'s
-must reach every partition border before any sound competitors
-propagate their partition. It is worth noting that this delete
-operation involves concurrency: removals continue to propagate while
-the competition is already partially triggered and propagating.
+paths. As corollary, the convergence time increases, for $\delta$
+messages must reach every partition border before any sound
+competitors propagate their partition. It is worth noting that this
+delete operation involves concurrency: removals continue to propagate
+while the competition is already partially triggered and propagating.
 
@@
 do not generate traffic anymore. Being reactive, \NAME has no overhead
-when there is no operation in the system.  \NAME's overhead actually
-depends on its usage.
+when there is no operation in the system. In other words, \NAME's
+overhead actually depends on its usage.
 
@@
   communications.}
-
-\begin{figure}
-  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
-  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
-\end{figure}
 
@@
 
+\begin{figure}
+  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
+  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
+\end{figure}
+
 \item [Results:]
@@
 \texttt{Add}s may reach consistent partitioning faster. In particular,
-Figure~\ref{fig:geant} depicts a slow down in traffic around $500$ ms
-due to the high latency inter-continental link. This link acts as a
-bottleneck that does not exist when each cluster has its own source.
+the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
+around $500$ ms due to the high latency inter-continental link. The
+first plateau corresponds to the source's autonomous system
+acknowledging this source, while the second plateau corresponds to the
+other autonomous system catching up.  The inter-continental link acts
+as a bottleneck that does not exist when each cluster has its own
+source.
 
@@
 partition. However, in the experiment involving one source \emph{per}
-cluster, the new link does not trigger noticeable traffic (only $2$
-messages total), for \processes already know their closest source
-located in their respective cluster.
+cluster, the new link does not trigger noticeable traffic, for
+\processes already know their closest source located in their
+respective cluster.
 
 \noindent Overall, this experimentation empirically demonstrates the
-benefits of \NAME in the context of Edge infrastructures:
-inter-connected autonomous systems where \processes may join or leave
-or crash, communications links may be added or removed. \NAME coupled
-with replication strategies designed for the Edge would allow locking
-down the traffic of replica indexing, while providing every \processes
-with quick access to replicated content.
+benefits of \NAME in the context of geo-distributed infrastructures,
+e.g., inter-connected autonomous systems where \processes may join or
+leave or crash, communications links may be added or removed. \NAME
+coupled with replication strategies designed for the Edge would allow
+locking down the traffic of replica indexing, while providing every
+\process with quick access to replicated content.
 

### 2021-04-23 input/conclusion.tex
first conclusion (but not convinced)

--- 2021-04-08 input/conclusion.tex
@@
 
-In this paper, we proposed a general purpose definition of scoped
-broadcast, and an extension to automatically adapt the scope of scoped
-broadcast in contexts where each process can decide whether or not it
-decide to be a source. We proposed an implementation called \NAME.
+With the advent of the edge and IoT era, major distributed services
+proposed by our community should be revised in order to mitigate as
+much as possible trafic between \processes.  In this paper, we tackled
+the problem of content indexing, a key service for storage systems.
+\TODO{pas vraiment du content indexing}
+%
+Our proposal relies on a logical partitioning of the infrastructure
+that is maintained according to replicas creations/removals and
+infrastructure changes. Through an efficient scoped broadcast, each
+\process composing the infrastructure knows eventually where the best
+replica for a particular content is. The major difficulty is to handle
+concurrent operations, each having a different scope and ensure the
+correct convergence of the system.
+%
+We proposed an implementation of this protocol called \NAME and
+evaluated it on top of Peersim. The simulations confirmed the
+correctness of our protocol as well as the confinement of the traffic
+only where it is needed.
 
-As future work, we plan on enhancing the
+% 
+From the technical viewpoint, this new service can easily be
+integrated in storage services such as
 \underline{I}nter\underline{P}lanetary \underline{F}ile
-\underline{S}ystem (IPFS)~\cite{henningsen2020mapping} with dynamic
-logical partitioning capabilities in order to improve its caching
-policy of popular contents at marginal cost.
+\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an integration would enabe us to
+to perform additional experiments and observe the gain with 
+respect to the DHT-based approach that is currently used.
 
-\noindent We propose an implementation that further decreases
-generated traffic and improves on
-anonymity~\cite{whitaker2002forwarding}.  \NAME makes extensive use of
-paths to enable deleting messages without incrementing local
-counters. Messages carry their respective path and processes detect
-when such messages have been looping when they carry their identity
-(see Lines~\ref{line:notloopingA} and \ref{line:notloopingB} of
-Algorithm~\ref{algo:adddelundo}). Since membership is all that
-matters, we propose to trade vectors of identities for Bloom
-filters~\cite{almeida2007scalable}. Processes know with high
-probability if they already received and forwarded each message
-without knowing the identity of all processes that received it.  False
-positive probability only incurs premature stopping of broadcast
-messages and does not invalidate the delete of specific
-messages. \TODO{Rework.}
+%
+%% More generally, it can be used in other services in order to share information while mitigating the traffic.
+%% MWhile we use the distance to the closest copy in this paper, It is
+%% notewothy that other scopes can be envisioned according to the
+%% use-cases.  For instance, the location of a city in order to broadcast
+%% message to all nodes in the city.  This requires nodes to store and
+%% maintain their city location in their local state. Nodes stop
+%% delivering and forwarding their received messages when they come from
+%% a different city. Such a predicate can be complexified in order to
+%% broadcast messages to all nodes in the city plus neighboring
+%% cities. This requires nodes to overload forwarded messages the first
+%% time they reach another city. The predicate checks if messages already
+%% reached two distinct cities before delivery.  The predicate can even
+%% be piggypack within the message and so be different for each
+%% message.\TODO{Complete the use-cases}
 
-\noindent We also plan on further improving scoped broadcast between
-multiple autonomous systems. Indeed, processes could leverage the
-hierarchical properties of such topology~\cite{nur2018geography} to
-avoid flooding the whole systems with control information about all
+From the scientific viewpoint, we are currently investigating how our
+proposal can be extended in orer to take into account multiple
+autonomous systems. Indeed, \processes could leverage the hierarchical
+properties of the Internet topology~\cite{nur2018geography} to avoid
+flooding the whole systems with control information about all
 partitions.
+\TODO{should we highlight this at the end of the experiment}
 

### 2021-04-23 input/conclusion.tex
highligh properties

@@
 %
-Our proposal relies on a logical partitioning of the infrastructure
-that is maintained according to replicas creations/removals and
+More precisely, we proposed to address it as a dynamic logical partitioning of the infrastructure
+that should be maintained according to replicas creations/removals and
 infrastructure changes. Through an efficient scoped broadcast, each
@@
 concurrent operations, each having a different scope and ensure the
-correct convergence of the system.
-%
+correct convergence of the system. We defined multiple properties that highlight this complexity.
+
 We proposed an implementation of this protocol called \NAME and

### 2021-04-23 input/conclusion.tex
add a first complete draft for the conclusion

@@
 the problem of content indexing, a key service for storage systems.
-\TODO{pas vraiment du content indexing}
 %
@@
 replica for a particular content is. The major difficulty is to handle
-concurrent operations, each having a different scope and ensure the
-correct convergence of the system. We defined multiple properties that highlight this complexity.
-
+concurrent operations, each having a different scope, and ensure the
+correct convergence of the system.
+We defined, in particular,  multiple properties that highlight this complexity.
+%
 We proposed an implementation of this protocol called \NAME and
-evaluated it on top of Peersim. The simulations confirmed the
+evaluated through simulations. Observations confirmed the
 correctness of our protocol as well as the confinement of the traffic
@@
 
+As ongoing and future work, we are currently studying how it might be
+possible to limit the scope of a partition to one autonomous system at
+most. Indeed, the gain of propagating changes to \processes belonging to
+another autonomous system might be negligible as the latency penalty
+is mainly due to inter autonomous systems' links (\eg trans-continental
+links).  Excatly, we are investigating how such a change can be
+formalized and its impact on the current protocol.
 %
-From the technical viewpoint, this new service can easily be
-integrated in storage services such as
+%autonomous systems. Indeed, \processes could leverage the hierarchical
+%properties of the Internet topology~\cite{nur2018geography} to avoid
+%flooding the whole systems with control information about all
+%partitions.
+%\TODO{should we highlight this at the end of the experiment}
+%
+In addition to this action, it would make sense to evaluate the use of \NAME
+within a concrete storage systems, such as
 \underline{I}nter\underline{P}lanetary \underline{F}ile
-\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an integration would enabe us to
-to perform additional experiments and observe the gain with 
-respect to the DHT-based approach that is currently used.
+\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
+integration would enabe us to to perform additional experiments and
+observe the gain with respect to the DHT-based approach that is
+currently used.
 
@@
 
-From the scientific viewpoint, we are currently investigating how our
-proposal can be extended in orer to take into account multiple
-autonomous systems. Indeed, \processes could leverage the hierarchical
-properties of the Internet topology~\cite{nur2018geography} to avoid
-flooding the whole systems with control information about all
-partitions.
-\TODO{should we highlight this at the end of the experiment}
-
 %%% Local Variables: 

### 2021-04-23 input/figproof.tex
wip

@@
     {\input{input/figproofB.tex}}
-    \caption{\label{fig:proof}Concurrent operations,
-      delivery orders, and stale control information may impair
-      consistent partitioning. Dynamic consistent partitioning
-      requires eventual purging of stale messages, and best eventual
-      forwarding.}
+    \caption{\label{fig:proof}Concurrent operations, delivery orders,
+      and stale control information may impair consistent
+      partitioning. Dynamic consistent partitioning requires eventual
+      purging of stale messages, and best eventual forwarding.
+      $before$, $last$, and $expect$ respectively refer to the
+      delivery history, the last delivered $\alpha$ message, and
+      the message expected to reach consistent partitioning.}
   \end{center}

### 2021-04-23 input/figproofB.tex
mostly about implem
wip

@@
   \newcommand\X{85pt}
-  \newcommand\Y{-50pt}
+  \newcommand\Y{-60pt}
 
@@
   \draw[<->] (5pt - \X, 0.4*\Y) --
-  node[below, font=\small]{\textbf{I': propagation}}
+  node[below, font=\small, align=center]{\textbf{I': propagation}\\\textbf{of $\delta$ messages}}
   (-5pt, 0.4*\Y); %% I as well
@@
   \draw[<->] (5pt , 0.4*\Y) --
-  node[below, font=\small]{\textbf{III: detection}}
+  node[below, font=\small, align=center]{\textbf{III: detection}}
   (-5pt + \X, 0.4*\Y); %% IV
@@
   \draw[<->] (5pt +\X , 0.4*\Y) --
-  node[below, font=\small]{\textbf{IV: propagation}}
+  node[below, font=\small, align=center]{\textbf{IV: propagation}\\\textbf{of $\delta?$ messages}}
   (-5pt + 2*\X, 0.4*\Y); %% V

### 2021-04-23 input/proposal.tex
wip

@@
 and scoped broadcast have well-aligned preoccupations, we assume
-implementations relying on forwarding of messages from neighbor to
-neighbor.
+implementations relying on forwarding of messages from
+neighbor-to-neighbor.
 
@@
     must also notify subsequent \processes that their current
-    partition \emph{may be} deleted, for their parent may have blocked
-    the corresponding $\delta$ messages. We note such notification
-    $\delta_d?$ to emphasize the uncertainty of a $\delta$ message.
+    partition \emph{may be} deleted. Indeed their parent may have
+    blocked the corresponding $\delta$ messages and subsequent
+    \processes must purge their possibly stale state, for the sake of
+    consistency.  We note such notification $\delta_d?$ to emphasize
+    the uncertainty of a $\delta$ message.
   \item [\processes with last $\alpha_d$ receiving $\delta_d?$ from
@@
 
-\vfill
+% \vfill
 
-\TODO{spacing.}
+% \TODO{spacing.}
 
-\newpage
+% \newpage
 
@@
 respective known local counter of each known source, or has-been
-source.  Each \process delivers and forwards
+source. Each message $m$ carries its source $s$ along with its version
+$c$ that we subscript $m_{s, c}$.  Each \process delivers and forwards
 \begin{inparaenum}[(i)]
@@
 \process ever known which is the number of \processes in the system
-$\mathcal{O}(V)$ in the worst case. Unfortunately, \processes cannot
-remove any entry from this vector without running a costly distributed
-consensus protocol to ensure that no \process can mistake an old but
-removed entry for a new one. However, following the principles of
-scoped broadcast, we expect that every \process knows only a small
-subset of sources.
+$\mathcal{O}(V)$ in the worst case.
+%% Unfortunately, \processes cannot
+%% remove any entry from this vector without running a costly distributed
+%% consensus protocol to ensure that no \process can mistake an old but
+%% removed entry for a new one.
+Nevertheless, following the principles of scoped broadcast, we expect
+that every \process only acknowledges a small subset of sources.
 
@@
 \processes that forwarded the corresponding $\alpha$ message. Such
-$\delta$ message implements the uncertain $\delta?$ message of
-Figure~\ref{fig:proofB}. It fulfils the double role of removing stale
-control information without modifying the local counter of the source
-(since the partition may still exist), and removing loops to ensure
-termination (since \processes do not modify their local state to
-reflect such delivery, messages piggyback monotonically such
+$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$ message
+of Figure~\ref{fig:proofB}. It fulfils the double role of removing
+stale control information without modifying the local counter of the
+source (since the partition may still exist), and removing loops to
+ensure termination (since \processes do not modify their local state
+to reflect such delivery, messages piggyback monotonically such
 increasing control information). Thus, $\delta$ messages used in

### 2021-04-23 input/related_work.tex

@@
+\vfill
+\TODO{spacing}
+\newpage
+
 \section{Related Work}
@@
 
-(i) Deploying a centralized server that maintains an index of all replica locations has been proposed in~\cite{fogstore, p2p-alto, p2p-oracle, snamp}.
+(i) Deploying a centralized server that maintains an index of all replica locations has been proposed in~\cite{snamp, p2p-oracle, fogstore, p2p-alto}.
 These solutions suffer from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
-Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, mdht} for example.
+Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{voronet, coin_19} or \underline{D}istributed \underline{H}ash \underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel} for example.
 In the latter, each node stores a part of the index, defined by an interval between hash values.
@@
 
-(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica .
+(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica.
 Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings.
 This is a well-studied problem in the network community and numerous protocols have been proposed.
-As for the index, this knowledge about the topology can be either centralized~\cite{topology-discovery} or distributed like in routing protocols such as OSPF (Open Shortest Path First).
+As for the index, this knowledge about the topology can be either centralized~\cite{topology-discovery} or distributed like in routing protocols such as \underline{O}pen \underline{S}hortest \underline{P}ath \underline{F}irst (OSPF).
+
 All these solutions require to contact a remote node (either a server or a DHT node) to request this index 
@@
 %This requires notifying nodes of replica creations and removals along with information about the evolving topology. 
-Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica locations for all nodes~\cite{nlsr}.
-Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
-Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}.
-Yet both solutions inherently imply that every nodes will eventually receive all messages.
+Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica locations for all nodes, as usually implemented in \underline{N}amed \underline{D}ata \underline{N}etworking (NDN)~\cite{nlsr}.
+Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily determine where the closest copy of a given object resides, without contacting any remote node.
+Similarly, one could solve this issue by using a \underline{C}onflict-\underline{F}ree \underline{R}eplicated \underline{D}atatype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}.
+Yet both solutions inherently imply that every node will eventually receive all messages.
 
@@
 Such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology.
-Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric.
+Moreover, membership protocols are usually implemented  by modifying the neighboring of a given node according to a certain metric in a logical overlay.
 On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed.
 Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.
-Likewise, this also prevents from using solutions that periodically advertise their cache content~\cite{hemmati2015namebased, garcia-lopez} as they also inccur an overhead even in quiet contexts without any update.
+Likewise, this also prevents from using solutions that periodically advertise their cache content~\cite{garcia-lopez, hemmati2015namebased} as they also inccur an overhead even in quiet contexts without any update.
 Moreoever, such solutions necessarily rely on physical timeouts that could lead to either premature removals of partitions when they are still operating; or slow convergence where processes wrongly believe they belong to a partition that was removed.

### 2021-04-23 input/experiments.tex
mostly implemand algo + transi xpe to related work

@@
 Figure~\ref{fig:geant} shows the results of this experimentation. The
-top part corresponds to the one source experiment, while the bottom
-part corresponds to the one source per cluster experiment.
+top part displays the one source experiment while the bottom part
+displays the one source per cluster experiment.
 
@@
 again. In the experiment involving one source for two clusters, it
-generates traffic. After a $200$ milliseconds delay corresponding to
+generates traffic. After a $200$ ms delay corresponding to
 the new link latency, the cut off cluster starts to communicate
@@
 
+Next Section reviews state-of-the-art approaches for content indexing
+in geo-distributed infrastructures and explains their shortcomings in
+such context.
+
 % \subsection{Use case: caching}

### 2021-04-23 input/proposal.tex
mostly implemand algo + transi xpe to related work

@@
 \processes that forwarded the corresponding $\alpha$ message. Such
-$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$ message
-of Figure~\ref{fig:proofB}. It fulfils the double role of removing
-stale control information without modifying the local counter of the
-source (since the partition may still exist), and removing loops to
-ensure termination (since \processes do not modify their local state
-to reflect such delivery, messages piggyback monotonically such
-increasing control information). Thus, $\delta$ messages used in
-Propagation~I' are more efficient both in propagation time and
-traffic, for they propagate using every communication link available
-in the partition, and they do not need to carry their path.
-Fortunately, Propagation~I' happens more often than Propagation~IV.
-Yet, \processes that belong to a partition need to save the path taken
-by the corresponding $\alpha$ messages to enable Propagation~IV.  In
-the worst case, the path includes every \processes in the system but
-converges in average to the average diameter of partitions. Thus,
-message paths and \NAME have an interesting synergy: Paths tend to be
-smaller as the number of sources in the system increases. Bloom
-filters could introduce another trade-off by further decreasing the
-size of path data structures at the cost of premature stopped
-propagation that could impair consistent
+$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$
+message of Figure~\ref{fig:proofB}. It fulfils the double role of
+removing stale control information without modifying the local counter
+of the source (since the partition may still exist), and removing
+loops to ensure termination (since \processes do not modify their
+local state to reflect such delivery, messages piggyback monotonically
+such increasing control information).
+
+$\delta_{s, c}$ messages used in Propagation~I' are more efficient
+than $\delta_{s, c}^\pi$ messages used in Propagation~IV, both in
+propagation time and traffic. First, the former propagate using every
+communication link available in the partition, while the latter
+propagate following the dissemination tree of the corresponding
+$\alpha$ to purge. Second, the former only piggyback source and
+counter while the latter piggyback the path taken by the corresponding
+$\alpha$ to purge.  In the worst case, a path includes every
+\processes in the system but converges on average to the average
+diameter of partitions. Nevertheless, message paths and \NAME
+synergyze with each other: Paths tend to be smaller as the number of
+sources in the system increases. Bloom filters could introduce another
+trade-off by further decreasing the size of path data structures at
+the cost of premature stopped propagation that could impair consistent
 partitioning~\cite{whitaker2002forwarding}.

### 2021-04-23 input/conclusion.tex
reworkd conclusion

@@
 
-With the advent of the edge and IoT era, major distributed services
+With the advent of the Edge and IoT era, major distributed services
 proposed by our community should be revised in order to mitigate as
-much as possible trafic between \processes.  In this paper, we tackled
-the problem of content indexing, a key service for storage systems.
+much as possible traffic between \processes.  In this paper, we
+tackled the problem of content indexing, a key service for storage
+systems.
 %
-More precisely, we proposed to address it as a dynamic logical partitioning of the infrastructure
-that should be maintained according to replicas creations/removals and
-infrastructure changes. Through an efficient scoped broadcast, each
-\process composing the infrastructure knows eventually where the best
-replica for a particular content is. The major difficulty is to handle
-concurrent operations, each having a different scope, and ensure the
-correct convergence of the system.
-We defined, in particular,  multiple properties that highlight this complexity.
+We proposed to address this problem as a dynamic logical partitioning
+in dynamic networks where partitions grow and shrink to reflect
+content and replicas locations, as well as infrastructure
+changes. Using an efficient communication primitive called scoped
+broadcast, each \process composing the infrastructure eventually knows
+the \process hosting the best replica of specific content.  The
+challenge resides in handling concurrent operations that may impair
+the propagation of messages, and in turns, lead to inconsistent
+partitioning. 
+%% The major difficulty lies in concurrent operations, each having a
+%% different scope, and ensure the correct convergence of the system.  We
+%% defined, in particular, multiple properties that highlight this
+%% complexity.
 %
-We proposed an implementation of this protocol called \NAME and
-evaluated through simulations. Observations confirmed the
-correctness of our protocol as well as the confinement of the traffic
-only where it is needed.
+We highlighted the properties that solve this problem and proposed an
+implementation called \NAME.  Our simulations confirmed that
+\processes quickly reach consistent partitioning together, and that
+the generated traffic remains locked down to partitions.
+%% correctness of our protocol as well as the confinement of
+%% the traffic only where it is needed.
 
-As ongoing and future work, we are currently studying how it might be
-possible to limit the scope of a partition to one autonomous system at
-most. Indeed, the gain of propagating changes to \processes belonging to
-another autonomous system might be negligible as the latency penalty
-is mainly due to inter autonomous systems' links (\eg trans-continental
-links).  Excatly, we are investigating how such a change can be
-formalized and its impact on the current protocol.
+As future work, we plan on extending the logical partitioning protocol
+to enable lazy retrieval of partitions. Indeed, using \NAME, every
+\process partakes in the propagation of indexes of content and
+replicas. We would like to leverage the hierarchical properties of
+interconnected autonomous systems to limit the propagation of such
+indexes only to interested systems.
+%
+%% As ongoing and future work, we are currently studying how it might be
+%% possible to limit the scope of a partition to one autonomous system at
+%% most. Indeed, the gain of propagating changes to \processes belonging to
+%% another autonomous system might be negligible as the latency penalty
+%% is mainly due to inter autonomous systems' links (\eg trans-continental
+%% links).  Exactly, we are investigating how such a change can be
+%% formalized and its impact on the current protocol.
 %
@@
 %
-In addition to this action, it would make sense to evaluate the use of \NAME
-within a concrete storage systems, such as
-\underline{I}nter\underline{P}lanetary \underline{F}ile
-\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
-integration would enabe us to to perform additional experiments and
-observe the gain with respect to the DHT-based approach that is
-currently used.
+
+\noindent We also would like to evaluate \NAME within a concrete
+storage systems such as \underline{I}nter\underline{P}lanetary
+\underline{F}ile \underline{S}ystem
+(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
+relevance of \NAME in a real system subject to high dynamicity, and
+compare it against its current DHT-based indexing system that does not
+include distance in its operation.
+
+%% Such an integration would enable us to to perform additional
+%% experiments and observe the gain with respect to the DHT-based
+%% approach that is currently used.
+
+%% In addition to this action, it would make sense to evaluate
+%% the use of \NAME within a concrete storage systems, such as
+%% \underline{I}nter\underline{P}lanetary \underline{F}ile
+%% \underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
+%% integration would enable us to to perform additional experiments and
+%% observe the gain with respect to the DHT-based approach that is
+%% currently used.
 

### 2021-04-23 input/proposal.tex
reworkd conclusion

@@
 the network state. For \processes to reach consistent partitioning
-together, a \process becoming a source must notify every \process that
-is closer to it than any other source. Since epidemic dissemination
-and scoped broadcast have well-aligned preoccupations, we assume
-implementations relying on forwarding of messages from
-neighbor-to-neighbor.
+together, a \Process $s$ becoming a source must send a notification
+$\alpha_s$ to every \process that is closer to it than any other
+source. Since epidemic dissemination and scoped broadcast have
+well-aligned preoccupations, we assume implementations relying on
+forwarding of messages from neighbor-to-neighbor.
 

### 2021-04-23 input/related_work.tex
mostly implemand algo + transi xpe to related work
reworkd conclusion

@@
-\vfill
-\TODO{spacing}
-\newpage
-
 \section{Related Work}
 \label{sec:related_work}
-Content indexing in geo-distributed infrastructures has been studied through various approaches. 
-Offering an indexing service which is either hosted by a centralized entity or distributed through nodes of the network has long been the predominant one.
-This mainly requires (i) to have access to the list of current replica locations and (ii) to be aware of the topology to compute which replica is the closest for a given location.
 
-(i) Deploying a centralized server that maintains an index of all replica locations has been proposed in~\cite{snamp, p2p-oracle, fogstore, p2p-alto}.
-These solutions suffer from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
-Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{voronet, coin_19} or \underline{D}istributed \underline{H}ash \underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel} for example.
-In the latter, each node stores a part of the index, defined by an interval between hash values.
-Before downloading any object, a node first
-hashes the content to obtain the address of the node that stores the replica locations of this given object.
-After obtaining from the remote node the list of available replicas, it can select the closest copy to download from.
-We emphasize that, in this setting, the DHT only stores information about replicas locations, not the content itself.
-DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.
+Content indexing in geo-distributed infrastructures has been studied
+through various approaches.  Offering an indexing service which is
+either hosted by a centralized entity or distributed through nodes of
+the network has long been the predominant one. This mainly requires
+(i) to have access to the list of current replica locations and (ii)
+to be aware of the topology to compute which replica is the closest
+for a given location.
 
-(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica.
-Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings.
-This is a well-studied problem in the network community and numerous protocols have been proposed.
-As for the index, this knowledge about the topology can be either centralized~\cite{topology-discovery} or distributed like in routing protocols such as \underline{O}pen \underline{S}hortest \underline{P}ath \underline{F}irst (OSPF).
+(i) Deploying a centralized server that maintains an index of all
+replica locations has been proposed in~\cite{snamp, p2p-oracle,
+  fogstore, p2p-alto}. These solutions suffer from well-known
+disadvantages inherent to centralized solutions (load balancing,
+robustness, locality, etc.) that are even magnified in an Edge
+context.  Distributing this index among nodes in the network
+circumvent some of these issues, either using coordinate-based
+overlays~\cite{voronet, coin_19} or \underline{D}istributed
+\underline{H}ash \underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel}
+for example. In the latter, each node stores a part of the index,
+defined by an interval between hash values.  Before downloading any
+object, a node first hashes the content to obtain the address of the
+node that stores the replica locations of this given object. After
+obtaining from the remote node the list of available replicas, it can
+select the closest copy to download from. We emphasize that, in this
+setting, the DHT only stores information about replicas locations, not
+the content itself. DHT-based approaches are well-studied and easy to
+deploy in order to offer such a localization service.
 
-All these solutions require to contact a remote node (either a server or a DHT node) to request this index 
-which is costly in terms of latency while in contradiction with Edge infrastructure constraints, as previsouly explained.
+(ii) Being centralized or distributed, this index should be enhanced
+with the topology knowledge in order to be able to decide where
+resides the closest replica. Maintaining a consistent view of an ever
+changing topology across a network is inherently complicated,
+especially in asynchronous settings. This is a well-studied problem in
+the network community and numerous protocols have been proposed. As
+for the index, this knowledge about the topology can be either
+centralized~\cite{topology-discovery} or distributed like in routing
+protocols such as \underline{O}pen \underline{S}hortest
+\underline{P}ath \underline{F}irst (OSPF).
 
-The opposite approach consists in hosting the index directly on the nodes, avoiding any prior request to access a content.   
-%This requires notifying nodes of replica creations and removals along with information about the evolving topology. 
-Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica locations for all nodes, as usually implemented in \underline{N}amed \underline{D}ata \underline{N}etworking (NDN)~\cite{nlsr}.
-Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily determine where the closest copy of a given object resides, without contacting any remote node.
-Similarly, one could solve this issue by using a \underline{C}onflict-\underline{F}ree \underline{R}eplicated \underline{D}atatype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}.
-Yet both solutions inherently imply that every node will eventually receive all messages.
+All these solutions require to contact a remote node (either a server
+or a DHT node) to request this index which is costly in terms of
+latency while in contradiction with Edge infrastructure constraints,
+as previously explained.
 
-At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create a scope-related partioning, as proposed in this paper.
-Such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology.
-Moreover, membership protocols are usually implemented  by modifying the neighboring of a given node according to a certain metric in a logical overlay.
-On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed.
-Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.
-Likewise, this also prevents from using solutions that periodically advertise their cache content~\cite{garcia-lopez, hemmati2015namebased} as they also inccur an overhead even in quiet contexts without any update.
-Moreoever, such solutions necessarily rely on physical timeouts that could lead to either premature removals of partitions when they are still operating; or slow convergence where processes wrongly believe they belong to a partition that was removed.
+The opposite approach consists in hosting the index directly on the
+nodes, avoiding any prior request to access a content.
+%This requires notifying nodes of replica creations and removals along
+%with information about the evolving topology.
+Broadcasting information about cache updates to all nodes in the
+system is a straightforward way to maintain consistent information
+about replica locations for all nodes, as usually implemented in
+\underline{N}amed \underline{D}ata \underline{N}etworking
+(NDN)~\cite{nlsr}.  Indeed, having the entire knowledge of all the
+replica localization along with distance information carried into
+messages, each node can easily determine where the closest copy of a
+given object resides, without contacting any remote node.  Similarly,
+one could solve this issue by using a
+\underline{C}onflict-\underline{F}ree \underline{R}eplicated
+\underline{D}atatype (CRDT) for set data structures, for
+example~\cite{shapiro2011crdts}. Yet both solutions inherently imply
+that every node will eventually receive all messages.
 
-%Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
-%On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica.
-This enables for a request to be caught \textit{on-path}, and be redirected to the closest replica.
-However, the announcement is only performed towards this original replica, that is requests can miss closer replicas that are not on this path, thus decreasing the efficiency of the cache sharing mechanism.
+At first glance, membership protocols as proposed in~\cite{t-man}
+would appear to provide suitable abstractions to create a
+scope-related partitioning, as proposed in this paper. Such protocols
+usually rely on gossip mechanism, implying contacts with random nodes
+that can be very far away in the physical topology. Moreover,
+membership protocols are usually implemented by modifying the
+neighboring of a given node according to a certain metric in a logical
+overlay.  On the contrary, we do not aim at building any overlay, as
+we only rely on the physical topology so the neighbors of a given node
+are not continuously modified. Lastly, these protocols are usually
+cycle-based, meaning that they impose a constant load on the network
+traffic, even when the system state does not change. Likewise, this
+also prevents from using solutions that periodically advertise their
+cache content~\cite{garcia-lopez, hemmati2015namebased} as they also
+incur an overhead even in quiet contexts without any update.
+Moreover, such solutions necessarily rely on physical timeouts that
+could lead to either premature removals of partitions when they are
+still operating; or slow convergence where processes wrongly believe
+they belong to a partition that was removed.
 
-%AVK: This should go where we explain the DEL, as this is really specific...
-%One could also solve this issue by removing partitions that were not advertised for a defined time~\cite{hemmati2015namebased, garcia-lopez}. 
-%However, relying on physical timeout could lead to either premature removals of partitions when they are still operating; or slow convergence where processes believe they belong to a partition that was removed (\TODO{plot ?}).
-In addition, since timeouts imply a
-%continuous maintenance of partitions, such partitioning protocol
-%incurs an overhead even in quiet contexts without dynamic partitions.
+%Finally, we emphasize that consistency is at the core of our design,
+%as \NAME provides the same guarantees for all nodes.  On the
+%contrary, to avoid flooding, authors in~\cite{opnl} propose to
+%propagate information about cache updates only towards the original
+%replica. This enables for a request to be caught \textit{on-path},
+%and be redirected to the closest replica. However, the announcement
+%is only performed towards this original replica, that is requests can
+%miss closer replicas that are not on this path, thus decreasing the
+%efficiency of the cache sharing mechanism.
 
-% AVK
-% t-man: T-Man: Gossip-Based Overlay Topology Management5doat a random time 
-% at a random time once in eachconsecutive interval of T time unit
-% This buffer contains a random sample of the nodes from the entirenetwork. It is provided by apeer sampling service
-% 
-% We do not try to to create a topology aware overlay ! Because locality.
-% We do not provide routing ! routing is two determine path between any pair of nodes. We only provide path to objects 
-% 
-% Koala locality aware routing. Long links. Lazzy (nothing happens)
-% Koala  shares  many  core  aspectswith similar overlays, such as Chord and Symphony.
-% 
-% VoroNet: overlay and routing. i.e. long links 
-% It links application objects rathen than physical nodes so that objects with similar characteristic are neighbors. 
-% are logigal overlay, that are not correlated to the physical infrstructure. 
-% Usually rely on long links...
-% AVK
+%AVK: This should go where we explain the DEL, as this is really
+%specific...  One could also solve this issue by removing partitions
+%that were not advertised for a defined
+%time~\cite{hemmati2015namebased, garcia-lopez}.  However, relying on
+%physical timeout could lead to either premature removals of
+%partitions when they are still operating; or slow convergence where
+%processes believe they belong to a partition that was removed
+%(\TODO{plot ?}). In addition, since timeouts imply a continuous
+%maintenance of partitions, such partitioning protocol incurs an
+%overhead even in quiet contexts without dynamic partitions.
 
-%% \begin{definition}[Dynamic optimal partitioning]
-%%   A dynamic optimal partitioning is an optimal partitioning where the
-%%   set of sources $S$ does not monotonically increase. We suffix this
-%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
-%%   of sources by \underline{a}dding its partition with messages
-%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
-%%   leaves the set of sources by \underline{d}eleting its partition with
-%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
-%% \end{definition}
-
-%% Unfortunately, due to differences in receipt order of messages between
-%% processes, stale information may stop prematurely the propagation of
-%% relevant messages leading to inconsistent partitioning.
-%% \TODO{Figure~\ref{fig:del} shows that.}
-% 
-% One could solve this issue by using a conflict-free replicated data
-% type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
-% require eventual delivery of messages to ensure convergence. All
-% processes need to receive, deliver, hence broadcast all
-% operations. Some processes may receive operations unnecessary to their
-% correct functioning, for these operations did not happen in their
-% locality.  One could also solve this issue by removing partitions that
-% were not advertised for a defined
-% time~\cite{hemmati2015namebased}. \TODO{check distance-vector
-%   protocols.} However, relying on physical timeout could lead to
-% either premature removals of partitions when they are still operating;
-% or slow convergence where processes believe they belong to a partition
-% that was removed (\TODO{plot ?}). In addition, since timeouts imply a
-% continuous maintenance of partitions, such partitioning protocol
-% incurs an overhead even in quiet contexts without dynamic partitions.
-
-%% \begin{problem}[\label{prob:intra}Consistent partitioning]
-%%   How to enable \emph{consistent} dynamic optimal partitioning in
-%%   dynamic network using scoped flooding?
-%% \end{problem}
-
-% \TODO{Dynamic Multiple-sources All-destinations shortest path on
-%  dynamic graphs?}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \input{input/figASmotivation.tex}
-%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
-%%       objects, processes do not know about all partitions that exist
-%%       in the whole distributed system.}
-%%   \end{center}
-%% \end{figure}
-
-%% To further improve scoped flooding in autonomous systems, processes
-%% may belong to multiple partitions representing the objects they are
-%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
-%% nature of autonomous systems. Autonomous systems have topological
-%% properties~\cite{nur2018geography} that processes can leverage to
-%% avoid flooding the whole systems with control information about all
-%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
-%% partition about a specific object, flooding Paris's AS to notify
-%% neighboring processes of the object. However, it does not flood the
-%% whole network, for control information stops at Process $b$. It
-%% significantly saves bandwidth compared to broadcast since processes
-%% below entrypoints of autonomous systems are order of magnitude more
-%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
-%% to return an object they are unaware of. Processes remain efficient in
-%% answering requests. \TODO{which is important for end users \REF.}
-
-%% \begin{definition}[Partitions in asynchronous systems]
-%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
-%%   \TODO{TODO} \TODO{or multi-partitioning?}
-%% \end{definition}
-
-%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
-%%   How to enable scoped flooding of objects in autonomous systems?
-%% \end{problem}
-
-%% Next Section presents our approach that solves these scientific
-%% problems by relying on logical control information only.
+% AVK t-man: T-Man: Gossip-Based Overlay Topology Management5doat a
+% random time at a random time once in eachconsecutive interval of T
+% time unit This buffer contains a random sample of the nodes from the
+% entirenetwork. It is provided by apeer sampling service We do not
+% try to to create a topology aware overlay ! Because locality.  We do
+% not provide routing ! routing is two determine path between any pair
+% of nodes. We only provide path to objects Koala locality aware
+% routing. Long links. Lazzy (nothing happens) Koala shares many core
+% aspectswith similar overlays, such as Chord and Symphony.  VoroNet:
+% overlay and routing. i.e. long links It links application objects
+% rathen than physical nodes so that objects with similar
+% characteristic are neighbors.  are logigal overlay, that are not
+% correlated to the physical infrstructure.  Usually rely on long
+% links...  AVK
 

### 2021-04-23 input/related_work.tex
positioning

@@
 the network has long been the predominant one. This mainly requires
-(i) to have access to the list of current replica locations and (ii)
-to be aware of the topology to compute which replica is the closest
-for a given location.
+\begin{inparaenum}[(i)]
+\item to have access to the list of current replica locations and
+\item to be aware of the topology to compute which replica is the
+  closest for a given location.
+\end{inparaenum}
 
-(i) Deploying a centralized server that maintains an index of all
-replica locations has been proposed in~\cite{snamp, p2p-oracle,
-  fogstore, p2p-alto}. These solutions suffer from well-known
-disadvantages inherent to centralized solutions (load balancing,
-robustness, locality, etc.) that are even magnified in an Edge
-context.  Distributing this index among nodes in the network
-circumvent some of these issues, either using coordinate-based
-overlays~\cite{voronet, coin_19} or \underline{D}istributed
-\underline{H}ash \underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel}
-for example. In the latter, each node stores a part of the index,
-defined by an interval between hash values.  Before downloading any
-object, a node first hashes the content to obtain the address of the
-node that stores the replica locations of this given object. After
-obtaining from the remote node the list of available replicas, it can
-select the closest copy to download from. We emphasize that, in this
-setting, the DHT only stores information about replicas locations, not
-the content itself. DHT-based approaches are well-studied and easy to
-deploy in order to offer such a localization service.
+Deploying a centralized server that maintains an index of all replica
+locations has been proposed in~\cite{snamp, p2p-oracle, fogstore,
+  p2p-alto}. These solutions suffer from well-known disadvantages
+inherent to centralized solutions (load balancing, robustness,
+locality, etc.) that are even magnified in an Edge context.
+Distributing this index among nodes in the network circumvent some of
+these issues, either using coordinate-based overlays~\cite{voronet,
+  coin_19} or \underline{D}istributed \underline{H}ash
+\underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel} for example. In
+the latter, each node stores a part of the index, defined by an
+interval between hash values.  Before downloading any object, a node
+first hashes the content to obtain the address of the node that stores
+the replica locations of this given object. After obtaining from the
+remote node the list of available replicas, it can select the closest
+copy to download from. We emphasize that, in this setting, the DHT
+only stores information about replicas locations, not the content
+itself. DHT-based approaches are well-studied and easy to deploy in
+order to offer such a localization service.
 
-(ii) Being centralized or distributed, this index should be enhanced
-with the topology knowledge in order to be able to decide where
-resides the closest replica. Maintaining a consistent view of an ever
-changing topology across a network is inherently complicated,
-especially in asynchronous settings. This is a well-studied problem in
-the network community and numerous protocols have been proposed. As
-for the index, this knowledge about the topology can be either
+Being centralized or distributed, this index should be enhanced with
+the topology knowledge in order to be able to decide where resides the
+closest replica. Maintaining a consistent view of an ever changing
+topology across a network is inherently complicated, especially in
+asynchronous settings. This is a well-studied problem in the network
+community and numerous protocols have been proposed. As for the index,
+this knowledge about the topology can be either
 centralized~\cite{topology-discovery} or distributed like in routing
@@
 still operating; or slow convergence where processes wrongly believe
-they belong to a partition that was removed.
+they belong to a partition that was removed. On the opposite
+Section~\ref{sec:experimentation} shows that \NAME quickly converges
+to consistent partitioning even in large scale networks.
 

### 2021-04-26 input/proposal.tex

--- 2021-04-23 input/proposal.tex
@@
-%% to better adapt positioning (I expect 2.5 pages
-%% intro+related work)
-
-% \vfill \TODO{spacing for intro and related work: 2.5 pages}
-% \newpage
-
 \section{Adaptive scoped broadcast}
@@
 
-%% In this section, we propose to dynamically adapt the scopes of \NAMEB
-%% using \NAMEB itself for the sake of efficiency: a \NAMEB message may
-%% modify the state of a \process, consequently changing predicate
-%% evaluations over deliveries.  At any time, a \process decides whether
-%% or not it becomes the center (or \emph{source}) of a scope (or
-%% \emph{partition}). \Processes must eventually rally the partition
-%% corresponding to their closest source despite concurrent operations,
-%% and dynamic changes in the network.
-
-%% \noindent In that regard, we introduce \NAME (stands for
-%% \underline{A}daptive \underline{S}coped broad\underline{cast}), a
-%% wait-free reactive protocol for dynamic logical partitioning that
-%% enables adaptive scoped broadcast in dynamic distributed
-%% systems. \NAME's operation guarantees that \processes eventually reach
-%% consistent partitioning by efficiently propagating their state
-%% changes. \NAME's overhead actually depends on its operations and
-%% current partitions in the system. When the system becomes quiescent,
-%% \processes eventually converge to their respective partition and do not
-%% require further communication afterward.
-
-%% \noindent This section starts by introducing consistent partitioning
-%% and its implementation when a \process can only become a new source to
-%% create a new partition, i.e., it cannot revoke its self-appointed
-%% status of source. Then, it extends to include the latter behavior: it
-%% introduces the properties that guarantee consistent partitioning in
-%% such context, and it details our implementation called \NAME along
-%% with its complexity analysis.
-
 To assign and maintain \processes to their best partition according to
-replica creations/removals as well as dynamic infrastructure changes,
-we designed and implemented \NAME (\NAME stands for
-\underline{A}daptive \underline{S}coped broad\underline{cast}).  \NAME
+replica creations and removals, as well as dynamic infrastructure
+changes, we designed and implemented \NAME.  \NAME stands for
+\underline{A}daptive \underline{S}coped broad\underline{cast}. It
 relies on a primitive that allows a \process to broadcast a message
-within a limited scope.  This primitive is used in a first algorithm
-to deliver consistent partitioning each time \process creates a new
-replica within the system. This algorithm is then extended to include
-replica removals as well as dynamic changes of the infrastructure.
-This section discussed the different properties that guarantee
-consistent partitioning in such a context and details the \NAME
-implementation along with its complexity analysis.
+within a limited scope. We first use this primitive to guarantee
+consistent partitioning when a \process can only create a new replica
+within the system. We highlight the issue when a process can also
+destroy a replica, and provide a second algorithm that handles replica
+removals as well as dynamic changes of the infrastructure.  This
+section describes the communication primitive called scoped broadcast,
+then discusses the properties that guarantee consistent partitioning
+in our context, and finally details our implementation \NAME and its
+complexity.
 
@@
 % \TODO{dynamic graph: superscript with $t$?}
-In the edge infrastructure we consider, nodes are heterogeneous and
-interconnected by communication links. \Processes involved in the
-management of the data sets may crash but are not byzantine.  Finally,
+In this paper, we consider edge infrastructures with heterogeneous
+\nodes interconnected by communication links. \Processes involved in
+the management of content may crash but are not byzantine.  Finally,
 \processes can reliably communicate through asynchronous message
-passing to other known \processes called neighbors.
-A more formal definition of our system is given below:
+passing to other known \processes called neighbors.  % A more formal
+%definition of our system is given below:
 
@@
 
-We define the Scoped broadcast (\NAMEB) as a communication primitive that propagates a
-message around its broadcaster within an application-dependant scope :
+We define scoped broadcast as a communication primitive that
+propagates a message around its broadcaster within an
+application-dependant scope:
 
@@
 %different trade-offs on space, time, and communication.
-
-\NAMEB is used to change the state of each \process dynamically, depending on all partitions that exist in the system.
+%
+We use \NAMEB to dynamically and efficiently modify the state of each
+\process depending on all partitions that exist in the system.
 
@@
 
-At any time, a \process can decide to become a source, hence creating
-a new partition in the system by executing an \texttt{Add}
+At any time, a \process can decide to become a \emph{source}, hence
+creating a new partition in the system by executing an \texttt{Add}
 operation. This partition includes at least its source plus
@@
   a logical partition comprising its closest source: $\forall p \in
-  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
+  P_{s_1}: \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
 \end{definition}
@@
 the network state. For \processes to reach consistent partitioning
-together, a \process becoming a source must notify every \process that
-is closer to it than any other source. Since epidemic dissemination
-and scoped broadcast have well-aligned preoccupations, we assume
-implementations relying on forwarding of messages from
-neighbor-to-neighbor.
+together, a \Process $s$ \underline{a}dding a partition must send a
+notification $\alpha_s$ to every \process that is closer to it than
+any other source. Since epidemic dissemination and scoped broadcast
+have well-aligned preoccupations, we assume implementations relying on
+message forwarding from neighbor-to-neighbor.
 
@@
 Figure~\ref{fig:delA}, \Process~$a$ deletes its partition. It notifies
-all neighboring \processes -- here only \Process~$b$ -- that may
+all neighboring \processes~--~here only \Process~$b$~-- that may
 belong to its partition using \NAMEB. Upon receipt, \Process~$b$
-discards the message $\delta_a$, for the latter does not target the
-former's partition. \Process~$b$ sends its own knowledge of best
-partition $\alpha_d^3$ that may prove to be the best for
-\Process~$a$. Eventually, every \processes belong to the same
-partition $P_d$. In this scenario, they reach consistent partitioning.
+discards the \underline{d}elete notification $\delta_a$ since
+$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
+sends its own best partition $\alpha_d^3$ that may be the best for
+\Process~$a$. Eventually, every \process belongs to Partition
+$P_d$. In this scenario, they reach consistent partitioning.
 
@@
 improves, the propagation of $\alpha$ messages operates normally.
-Removing an edge between two \processes may invalidate the shortest
-path of one of involved \processes plus downstream \processes. As a
-side effect, removing an edge may also impair the propagation of a
-partition delete. To implement this behavior, \NAME uses its
-implementation of $\delta?$ messages. This prove costly but
+
+\noindent Removing an edge between two \processes may invalidate the
+shortest path of one of involved \processes plus downstream
+\processes. As a side effect, removing an edge may also impair the
+propagation of a partition delete. To implement this behavior, \NAME
+uses its implementation of $\delta?$ messages. This prove costly but
 enables \NAME even in dynamic networks subject to physical

### 2021-04-26 input/introduction.tex
wip

@@
 
-In this paper, we first define scoped broadcast as a communication
-primitive that allows epidemic dissemination of messages as long as
-receiving \processes verify an application-dependant predicate.  Then,
-we propose \emph{\NAME}, a logical partitioning protocol that uses
-\underline{s}coped broad\underline{cast} to \underline{a}dapt its
-partitions, \ie scopes, to creations and deletions of partitions in
-the system. Each source advertises its existence to all possibly
-interested \processes, \ie only interconnected \processes of its
-partition plus \processes bordering its partition. In turns, \NAME
-scales well to the number of sources since the higher the number of
-partitions, the earlier the dissemination stops.
+\noindent The contribution of this paper is threefold:
+
+\begin{asparadesc} %% to remove left-margin :p
+\item [$\bullet$] We highlight the properties that guarantee
+  decentralized consistent partitioning in dynamic infrastructures. We
+  demonstrate that concurrent creation and removal of partitions may
+  impair the propagation of control information crucial for consistent
+  partitioning. Yet, \processes are able to purge stale information
+  forever using only neighbor-to-neighbor communication, hence leaving
+  room for up-to-date information propagation, and eventually
+  consistent partitioning.
+\item [$\bullet$] We provide an implementation entitled \NAME that
+  uses aforementioned principles to \underline{a}dapt its
+  partitioning, \ie \underline{s}copes, to creations and deletions of
+  partitions in the system. \NAME relies on a communication primitive
+  \underline{s}coped-broad\underline{cast} as \TODO{a communication
+    primitive that allows epidemic dissemination of messages as long
+    as receiving \processes verify an application-dependant
+    predicate.}
+
+\end{asparadesc}
+
+%% Then, we propose \emph{\NAME}, a logical partitioning protocol that
+%% uses \underline{s}coped broad\underline{cast} to \underline{a}dapt its
+%% partitions, \ie scopes, to creations and deletions of partitions in
+%% the system. Each source advertises its existence to all possibly
+%% interested \processes, \ie only interconnected \processes of its
+%% partition plus \processes bordering its partition. In turns, \NAME
+%% scales well to the number of sources since the higher the number of
+%% partitions, the earlier the dissemination stops.
+
 %

### 2021-04-26 input/abstract.tex
address most of comments, but NOT related work + spacing appeared between II and III

@@
   every \process only indexes its closest replica, and
-  connected \processes with similar index compose a partition. Our
-  decentralized implementation \NAME
+  connected \processes with a similar index compose a partition. Our
+  decentralized implementation \NAME is
   \begin{inparaenum}[(i)]
-  \item is efficient, for it uses partitions to lock down the traffic
+  \item efficient, for it uses partitions to lock down the traffic
     generated by its operations to relevant \processes, yet it
@@
   scales well in terms of generated traffic and termination time. As
-  such, \NAME can constitute the building block of new geo-distributed
+  such, \NAME can constitute a new building block for geo-distributed
   services.
@@
 
-\begin{IEEEkeywords}
-Edge infrastructures, decentralized content indexing, scoped
-broadcast, logical partitioning protocol
-\end{IEEEkeywords}
+%% \begin{IEEEkeywords}
+%% Edge infrastructures, decentralized content indexing, scoped
+%% broadcast, logical partitioning protocol
+%% \end{IEEEkeywords}
 

### 2021-04-26 input/background.tex
reworkd conclusion
address most of comments, but NOT related work + spacing appeared between II and III

@@
 infrastructures ranging from centralized services to fully
-decentralized approaches~\cite{squirrel}. We advocate for the latter where
-\processes host the service themselves so they do not need to request
-remote -- possibly far away third-party -- entities to retrieve their
-content location.  In this paper, we tackle the content indexing issue
-as a dynamic logical partitioning problem. This section motivates this
-shift and explains the shortcomings of existing implementations.
+decentralized approaches~\cite{squirrel}. We advocate for the latter
+where \processes host the service themselves so they do not need to
+request remote -- possibly far away third-party -- entities to
+retrieve their content location.  In this paper, we tackle the content
+indexing issue as a dynamic logical partitioning problem. This section
+motivates our positioning and explains the shortcomings of existing
+implementations.
 
@@
 needs it. In that regard, \Process~$R$ only needs to disseminate a
-message notifying all other \processes of its new content. \Process~$R$
-can use uniform reliable broadcast~\cite{hadzilacos1994modular} and epidemic propagation~\cite{epidemic-protocol}
-to guarantee that
+message notifying all other \processes of its new
+content. \Process~$R$ can use uniform reliable
+broadcast~\cite{hadzilacos1994modular} and epidemic
+propagation~\cite{epidemic-protocol} to guarantee that
 \begin{inparaenum}[(i)]
@@
 north \processes request its replica, and south \processes request the
-northern replica, \processes hosting a replica must add \emph{location
+northern one, \processes hosting a replica must add \emph{location
 information} along with their notifications. As consequence, every
@@
 new replica is actually much smaller than the network size. Uniform
-reliable broadcast is not designed for such context and would generate
-a lot of unnecessary traffic. Instead, \processes need a communication
-primitive that propagates notifications within a scope by evaluating a
-predicate, starting at its broadcaster (the \emph{source}).  In other
-terms, \processes propagate notifications as long as they consider
-them useful based on location information they carry. We call such
-primitive \emph{scoped broadcast}, for messages transitively reach a
-subset of interconnected \processes (the \emph{scope}). Using this
-primitive, \processes can lock down the traffic of content indexing to
-relevant \processes.
+reliable broadcast is not designed for such a context and would
+generate a lot of unnecessary traffic. Instead, \processes need a
+communication primitive that propagates notifications within a scope
+by evaluating a predicate, starting at its broadcaster (the
+\emph{source}).  In other terms, \processes propagate notifications as
+long as they consider them useful based on location information they
+carry. We call such primitive \emph{scoped broadcast} (see
+Section~\ref{subsec:scoped}), for messages transitively reach a subset
+of interconnected \processes (the \emph{scope}). Using this primitive,
+\processes can lock down the traffic of content indexing to relevant
+\processes.
 
@@
 replica is a \emph{partition}. Every \process belongs to one, and only
-one, partition. Contrarily to membership protocols that choose
-neighboring \processes to communicate with based on metrics~\cite{t-man},
-\processes in our context have no control over their neighboring
-\processes: they cannot add nor remove communication links.
+one, partition (see Section~\ref{subsec:consistent}).
+
+%% Contrarily to membership
+%% protocols that choose neighboring \processes to communicate with based
+%% on metrics~\cite{t-man}, \processes in our context have no control
+%% over their neighboring \processes: they cannot add nor remove
+%% communication links.
 
@@
 to concurrent operations where removed partitions would block the
-propagation of other partitions.
+propagation of other partitions (see Section~\ref{subsec:dynamic}).
 \end{asparadesc}
 
-Next Section details the properties of adaptive scoped broadcast in
-dynamic networks, and provides an implementation called \NAME along with its
-complexity.
+Next Section details the properties of scoped broadcast and dynamic
+partitioning in dynamic networks, and provides an implementation
+called \NAME along with its complexity.
+
+\vfill
+\TODO{spacing.}
+\newpage
 

### 2021-04-26 input/conclusion.tex
wip
address most of comments, but NOT related work + spacing appeared between II and III

@@
 We proposed to address this problem as a dynamic logical partitioning
-in dynamic networks where partitions grow and shrink to reflect
-content and replicas locations, as well as infrastructure
-changes. Using an efficient communication primitive called scoped
-broadcast, each \process composing the infrastructure eventually knows
-the \process hosting the best replica of specific content.  The
-challenge resides in handling concurrent operations that may impair
-the propagation of messages, and in turns, lead to inconsistent
-partitioning. 
+where partitions grow and shrink to reflect content and replicas
+locations, as well as infrastructure changes. Using an efficient
+communication primitive called scoped broadcast, each \process
+composing the infrastructure eventually knows the \process hosting the
+best replica of specific content.  The challenge resides in handling
+concurrent operations that may impair the propagation of messages, and
+in turns, lead to inconsistent partitioning.
 %% The major difficulty lies in concurrent operations, each having a

### 2021-04-26 input/experiments.tex
address most of comments, but NOT related work + spacing appeared between II and III

@@
 
-\noindent We evaluate dynamic scoped broadcast. First, we create 100
-partitions one at a time: \processes reach consistent partitioning
-before we create each new partition. Second, we remove every partition
-one at a time, in the order of their creation, hence starting from the
-first and oldest partition that had been added.
+\noindent We evaluate dynamic consistent partitioning. First, we
+create 100 partitions one at a time: \processes reach consistent
+partitioning before we create each new partition. Second, we remove
+every partition one at a time, in the order of their creation, hence
+starting from the first and oldest partition that had been added.
 
@@
 paths. As corollary, the convergence time increases, for $\delta$
-messages must reach every partition border before any sound
-competitors propagate their partition. It is worth noting that this
-delete operation involves concurrency: removals continue to propagate
-while the competition is already partially triggered and propagating.
+messages must reach the partition borders before sound competitors
+propagate their partition. It is worth noting that this delete
+operation involves concurrency: removals continue to propagate while
+the competition is already partially triggered and propagating.
 
@@
 cluster. Afterwards both scenarios are identical. At $850$~ms, we
-remove the link between the two clusters. At $1.7$~s, we insert this
-link again.
+remove the link between the two clusters. At $1.7$~s, we insert back this
+link.
 
@@
 
-\noindent Figure~\ref{fig:geant} shows that, when adding the
-inter-continental link again, the two clusters can communicate
-again. In the experiment involving one source for two clusters, it
-generates traffic. After a $200$ ms delay corresponding to
-the new link latency, the cut off cluster starts to communicate
-$\alpha$ messages again. Eventually, all \processes belong to the same
+\noindent Figure~\ref{fig:geant} shows that, when adding back the
+inter-continental link, the two clusters can communicate again. In the
+experiment involving one source for two clusters, it generates
+traffic. After a $200$ ms delay corresponding to the link latency, the
+cut off cluster starts to communicate $\alpha$ messages
+again. Eventually, all \processes belong to the same
 partition. However, in the experiment involving one source \emph{per}
@@
 benefits of \NAME in the context of geo-distributed infrastructures,
-e.g., inter-connected autonomous systems where \processes may join or
-leave or crash, communications links may be added or removed. \NAME
-coupled with replication strategies designed for the Edge would allow
-locking down the traffic of replica indexing, while providing every
-\process with quick access to replicated content.
+e.g., inter-connected autonomous systems where \processes and
+communications links may be added and removed at any time. \NAME
+coupled with replication strategies designed for Edge infrastructures
+would allow locking down the traffic of replica indexing, while
+providing every \process with quick access to replicated content.
 
@@
 Next Section reviews state-of-the-art approaches for content indexing
-in geo-distributed infrastructures and explains their shortcomings in
-such context.
+in geo-distributed infrastructures and explains their shortcomings.
 

### 2021-04-26 input/introduction.tex
address most of comments, but NOT related work + spacing appeared between II and III

--- 2021-04-22 input/introduction.tex
@@
 % edges of the network.
-This shift aims at keeping the data close to
+This change aims at keeping the data close to
 \begin{inparaenum}[(i)]
@@
 Indeed, these systems, when not using a centralized index hosted in a
-Cloud, rely on distributed hash tables~\cite{maymounkov2002kademlia}
-spread across the different \processes composing the
-infrastructure. When a client wants to access specific content, it
-requests a remote \process to provide at least one \process identity
-to retrieve this content from. After it retrieved the content, the
-client can create another replica to improve the performance of future
-accesses, but it must contact the content indexing service again to
-notify of such change.
+Cloud, rely on \underline{d}istributed \underline{h}ash
+\underline{t}ables (DHT)~\cite{maymounkov2002kademlia} spread across
+the different \processes composing the infrastructure. When a client
+wants to access specific content, it requests a remote \process to
+provide at least one \process identity to retrieve this content
+from. After it retrieved the content, the client can create another
+replica to improve the performance of future accesses, but it must
+contact the content indexing service again to notify of such a change.
 %% a local replica is created to improve the performance for future
@@
 
-These approaches directly contradict with the objectives of Edge
+These approaches contradict with the objectives of Edge
 infrastructures that aim at reducing the impact of latency as well as
@@
 \process deleting its replica should notify all members of its
-partition so they can rally their current closest partition. A
-periodic advertisement protocol already provides both these operations
-for routing purposes~\cite{hemmati2015namebased}. However, its
-functioning requires
+partition so they can identify and rally their new closest
+partition. A periodic advertisement protocol already provides both
+operations for routing purposes~\cite{hemmati2015namebased}. However,
+its functioning requires
 \begin{inparaenum}[(i)]

### 2021-04-26 input/introduction.tex
meow

--- 2021-04-26 input/introduction.tex
@@
 \item [$\bullet$] We provide an implementation entitled \NAME that
-  uses aforementioned principles to \underline{a}dapt its
-  partitioning, \ie \underline{s}copes, to creations and deletions of
-  partitions in the system. \NAME relies on a communication primitive
-  \underline{s}coped-broad\underline{cast} as \TODO{a communication
-    primitive that allows epidemic dissemination of messages as long
-    as receiving \processes verify an application-dependant
-    predicate.}
-
+  uses aforementioned principles to \underline{a}dapt its partitioning
+  to creations and deletions of partitions in the system. \NAME's
+  efficiency relies on a communication primitive called
+  \underline{s}coped-broad\underline{cast} that enables epidemic
+  dissemination of messages as long as receiving \processes verify an
+  application-dependant predicate.
+\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
+  empirically support our complexity analysis and the scalability of
+  \NAME in large scale networks comprising 10k \processes. Our
+  experiments also highlight the relevance of \NAME in autonomous
+  systems. \NAME would allow to lock down the traffic generated by
+  content indexing, even in contexts where \emph{physical}
+  partitioning may occur.
 \end{asparadesc}
@@
 
-\noindent In addition, \NAME guarantees that despite concurrent
-operations, every \process eventually knows one, and only one, source:
-its closest. \NAME being reactive, when the system becomes quiescent,
-\processes do not require further communications.
+% % %% \noindent In addition, \NAME guarantees that despite concurrent
+% % %% operations, every \process eventually knows one, and only one, source:
+% % %% its closest.
+% % %% \NAME being reactive, when the system becomes quiescent, \processes do
+% % %% not require further communications.
+
 %% This primitive is used to guarantee that eventually, every node knows
@@
 
-\noindent Simulations empirically support our complexity analysis and
-the scalability of \NAME in large scale networks comprising 10k
-\processes. Our experiments also highlight the relevance of \NAME in
-autonomous systems. \NAME would allow to lock down the traffic
-generated by content indexing, even in contexts where \emph{physical}
-partitioning may occur.
-
-\noindent In that regard, \NAME can constitute the building block of
-new geo-distributed services.
+\noindent \NAME can constitute a new building block for
+geo-distributed services.
 

### 2021-04-26 input/proposal.tex

@@
 % \TODO{dynamic graph: superscript with $t$?}
-In this paper, we consider edge infrastructures with heterogeneous
+In this paper, we consider Edge infrastructures with heterogeneous
 \nodes interconnected by communication links. \Processes involved in
@@
 \begin{definition}[Edge infrastructure]
-  An edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
+  An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
@@
 \subsection{Consistent partitioning}
+\label{subsec:consistent}
 
@@
 application-dependant: in the context of maintaining distributed
-indexes, weights would be link latency.
+indexes, this would be about link latency.
 
@@
   $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
-  hence forwards such $\alpha$ message to its neighbors. Since
+  hence forwards such an $\alpha$ message to its neighbors. Since
   communication links are reliable, neighboring \processes eventually
-  receive such notification $\forall \langle s_1, q \rangle \in E, s_1
-  \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
+  receive such a notification $\forall \langle s_1, q \rangle \in E,
+  s_1 \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
   importantly, whatever the order of received messages, every \process
@@
 
-Algorithm~\ref{algo:add} shows the instructions that implement such
+Algorithm~\ref{algo:add} shows the instructions that implement
 consistent partitioning when
@@
 discard last transiting messages. Despite the obvious lack of traffic
-optimization, the system reach consistent partitioning.
+optimization, the system reaches consistent partitioning.
 
@@
 \end{inparaenum}
-Figure~\ref{fig:problem} highlights such consistency issue with
+Figure~\ref{fig:problem} highlights such consistency issues with
 dynamic partitions, even in contexts where \processes have FIFO links,
@@
 \Process~$c$ and \Process~$d$ may need the notification of removal
-$\delta_a$ if it exists. However, such solution also implies that
+$\delta_a$ if it exists. However, such a solution also implies that
 \processes generate traffic not only related to their current
@@
 past. This would prove overly expensive in dynamic systems where
-\processes join or leave the system, create or delete partitions, at
+\processes join and leave the system, create and delete partitions, at
 any time.  Instead, we propose to use the delivery order at each
@@
   received. Figure~\ref{fig:proofA} depicts the only case where a
-  \process would block such epidemic propagation: the \process
-  received and delivered a message from a partition that has since
-  then been deleted but with a better sum of weights than newly
-  received ones (in the example $\alpha_d^y <
-  \alpha_a^{x'}$). Removing \emph{forever} all such stale messages
-  about deleted partitions would allow \processes to propagate their
-  best up-to-date partition again, eventually reaching consistent
-  partitioning together, as stated by Theorem~\ref{theo:bef}.
+  \process would block the epidemic propagation: the \process received
+  and delivered a message from a partition that has since then been
+  deleted but with a better sum of weights than newly received ones
+  (in the example $\alpha_d^y < \alpha_a^{x'}$). Removing
+  \emph{forever} all such stale messages about deleted partitions
+  would allow \processes to propagate their best up-to-date partition
+  again, eventually reaching consistent partitioning together, as
+  stated by Theorem~\ref{theo:bef}.
 \end{proof}
@@
     $\alpha_h^z$, for $\alpha_h^z < \alpha_d^y$:] \Processes such as
-    \Process~$e$ do not directly suffer from the non-delivery of
+    \Process~$e$ that do not directly suffer from the non-delivery of
     $\delta_d$. They need to purge their own $P_h$ if need
@@
   \item [\processes with $\delta_h \rightarrow \alpha_d$:] \Processes
-    such as \Process~$f$ do not belong to the preceding category, for
-    they already delivered $\delta_h$. However, best eventual
-    forwarding guarantees that they receive $\alpha_h$ that
-    contradicts their history or state. In such case, the detecting
+    such as \Process~$f$ that do not belong to the preceding category,
+    for they already delivered $\delta_h$. Nevertheless, best eventual
+    forwarding guarantees that they receive $\alpha_h$, which
+    contradicts their history or state. In such a case, the detecting
     \processes purge their own $\alpha_d$. The detecting \processes
@@
   \item [\processes with last $\alpha_d$ receiving $\delta_d?$ from
-    their parent:] \Processes such as \Process~$g$ have $\alpha_d$ and
-    preceding delivered messages have not importance. Such \processes
-    must trust detecting \processes by delivering and forwarding
-    $\delta_d?$. Messages are subject to all aforementioned blocking
+    their parent:] \Processes such as \Process~$g$ that have
+    $\alpha_d$ but preceding delivered messages are not
+    important. Such \processes must trust detecting \processes by
+    delivering and forwarding $\delta_d?$. It is worth noting that
+    these messages are subject to all aforementioned blocking
     conditions, but are also solved by aforementioned mechanisms.
@@
 
-  Propagation~I' terminates: a \process do not deliver a $\delta$
+  Propagation~I' terminates: a \process does not deliver a $\delta$
   message if it has already delivered it. Propagation~IV terminates: a
-  \process do not deliver a looping message.
+  \process does not deliver a looping message.
   % ; and since \processes forward the messages they deliver, upstream
@@
 \end{inparaenum}
-This vector enables both Propagation~I and Propagation~I'.  The size
-of such vector increases linearly with the number of sources that the
-\process ever known which is the number of \processes in the system
+This vector enables both Propagation~I and Propagation~I'.  Its size
+increases linearly with the number of sources that the \process ever
+known, which is the number of \processes in the system
 $\mathcal{O}(V)$ in the worst case.
@@
 loops to ensure termination (since \processes do not modify their
-local state to reflect such delivery, messages piggyback monotonically
-such increasing control information).
+local state to reflect such a delivery, messages piggyback
+monotonically such increasing control information).
 
@@
 counter while the latter piggyback the path taken by the corresponding
-$\alpha$ to purge.  In the worst case, a path includes every
-\processes in the system but converges on average to the average
-diameter of partitions. Nevertheless, message paths and \NAME
-synergyze with each other: Paths tend to be smaller as the number of
-sources in the system increases. Bloom filters could introduce another
-trade-off by further decreasing the size of path data structures at
-the cost of premature stopped propagation that could impair consistent
+$\alpha$ to purge.  In the worst case, a path includes every \process
+in the system but converges to the average diameter of
+partitions. Nevertheless, message paths and \NAME synergyze with each
+other: Paths tend to be smaller as the number of sources in the system
+increases. Bloom filters could introduce another trade-off by further
+decreasing the size of path data structures at the cost of premature
+stopped propagation that could impair consistent
 partitioning~\cite{whitaker2002forwarding}.
@@
 chosen uniformly at random among all \processes creates a logical
-partition. Its messages $\alpha_i$ propagate through the network until
+partition. Its messages $\alpha_i$ spread through the network until
 reaching \processes that belong to another partition closer to
@@
       \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
-number of neighbors per \process. % \TODO{Multiple receipt and multiple
+number of neighbors per \process. % \TODO{Multiple receipt and
+multiple
 %  delivery imply more messages (receipt bounded by $|O|$ as well).}
@@
 
-Next Section provides the details of our experimentation that aim to
-evaluate the proposed implementation of logical dynamic partitioning
-in dynamic networks.
+Next Section provides the details of our simulations that assess the
+proposed implementation.
 

### 2021-04-26 input/introduction.tex
intro reworkd with bullet and contribution

@@
   consistent partitioning.
+
 \item [$\bullet$] We provide an implementation entitled \NAME that
   uses aforementioned principles to \underline{a}dapt its partitioning
-  to creations and deletions of partitions in the system. \NAME's
-  efficiency relies on a communication primitive called
+  to creations and deletions of partitions even in dynamic systems
+  where \nodes join, leave, and crash at any time. \NAME's efficiency
+  relies on a communication primitive called
   \underline{s}coped-broad\underline{cast} that enables epidemic
@@
   application-dependant predicate.
+
 \item [$\bullet$] We evaluate \NAME with simulations. Our experiments
   empirically support our complexity analysis and the scalability of
-  \NAME in large scale networks comprising 10k \processes. Our
-  experiments also highlight the relevance of \NAME in autonomous
-  systems. \NAME would allow to lock down the traffic generated by
-  content indexing, even in contexts where \emph{physical}
-  partitioning may occur.
+  \NAME. Using scoped broadcast, \NAME quickly disseminate messages to
+  a subset of relevant \processes. The higher the number of
+  partitions, the smaller \NAME's overhead.  Most importantly, \NAME
+  does not generate traffic in quiescent systems.  Our experiments
+  also highlight the relevance of \NAME in autonomous systems. \NAME
+  would allow to lock down the traffic generated by content indexing,
+  even in contexts where \emph{physical} partitioning may occur.
+  As such, \NAME can constitute a new building block for geo-distributed
+  services.
 \end{asparadesc}
@@
 
-\noindent \NAME can constitute a new building block for
-geo-distributed services.
-
 %% We evaluated our protocol through two simulation scenarios using

### 2021-04-26 input/related_work.tex
meow
rework related work

@@
 
-Content indexing in geo-distributed infrastructures has been studied
-through various approaches.  Offering an indexing service which is
-either hosted by a centralized entity or distributed through nodes of
-the network has long been the predominant one. This mainly requires
+\begin{asparadesc}
+\item [Remote third-party:]
+Relying on a remote third party service is a popular approach to offer content indexing in geo-distributed infrastructures. 
+Such a remote service should
 \begin{inparaenum}[(i)]
-\item to have access to the list of current replica locations and
-\item to be aware of the topology to compute which replica is the
+\item have access to the list of current replica locations and
+\item be aware of the topology to decide which replica is the
   closest for a given location.
@@
 
-Deploying a centralized server that maintains an index of all replica
-locations has been proposed in~\cite{snamp, p2p-oracle, fogstore,
-  p2p-alto}. These solutions suffer from well-known disadvantages
-inherent to centralized solutions (load balancing, robustness,
-locality, etc.) that are even magnified in an Edge context.
+\begin{inparaenum}[(i)]
+\item Numerous solutions~\cite{snamp, p2p-oracle, fogstore, p2p-alto} maintain an index of all replica
+locations on a centralized server. This comes with well-known disadvantages
+inherent to centralized solutions such as load balancing, robustness or locality that are even magnified in an Edge context.
 Distributing this index among nodes in the network circumvent some of
@@
   coin_19} or \underline{D}istributed \underline{H}ash
-\underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel} for example. In
+\underline{T}ables (DHTs)~\cite{ipfs, mdht, squirrel}. In
 the latter, each node stores a part of the index, defined by an
@@
 only stores information about replicas locations, not the content
-itself. DHT-based approaches are well-studied and easy to deploy in
-order to offer such a localization service.
+itself.
 
-Being centralized or distributed, this index should be enhanced with
-the topology knowledge in order to be able to decide where resides the
-closest replica. Maintaining a consistent view of an ever changing
+\item Determining where resides the closest replica necessarily involves some knowledge about the current topology.
+Maintaining a consistent view of an ever changing
 topology across a network is inherently complicated, especially in
-asynchronous settings. This is a well-studied problem in the network
-community and numerous protocols have been proposed. As for the index,
+asynchronous settings. As for the index,
 this knowledge about the topology can be either
@@
 protocols such as \underline{O}pen \underline{S}hortest
-\underline{P}ath \underline{F}irst (OSPF).
+\underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
+\end{inparaenum}
 
-All these solutions require to contact a remote node (either a server
-or a DHT node) to request this index which is costly in terms of
-latency while in contradiction with Edge infrastructure constraints,
-as previously explained.
+All the aforementionned solutions require to contact a remote node to request this index which is costly in terms of
+latency while in contradiction with Edge infrastructure constraints, as previously explained.
 
+\item [Broadcast:]
 The opposite approach consists in hosting the index directly on the
 nodes, avoiding any prior request to access a content.
-%This requires notifying nodes of replica creations and removals along
-%with information about the evolving topology.
-Broadcasting information about cache updates to all nodes in the
-system is a straightforward way to maintain consistent information
-about replica locations for all nodes, as usually implemented in
 \underline{N}amed \underline{D}ata \underline{N}etworking
-(NDN)~\cite{nlsr}.  Indeed, having the entire knowledge of all the
-replica localization along with distance information carried into
+(NDN)~\cite{nlsr} broadcasts information about cache updates to all nodes in the
+system. Having the entire knowledge of all the
+replica locations along with distance information carried into
 messages, each node can easily determine where the closest copy of a
 given object resides, without contacting any remote node.  Similarly,
-one could solve this issue by using a
+one could use a
 \underline{C}onflict-\underline{F}ree \underline{R}eplicated
@@
 example~\cite{shapiro2011crdts}. Yet both solutions inherently imply
-that every node will eventually receive all messages.
+that every node will eventually receive all messages, contrary to \NAME.
 
-At first glance, membership protocols as proposed in~\cite{t-man}
+\item [Membership protocols:]
+At first glance, membership protocols~\cite{t-man}
 would appear to provide suitable abstractions to create a
 scope-related partitioning, as proposed in this paper. Such protocols
-usually rely on gossip mechanism, implying contacts with random nodes
-that can be very far away in the physical topology. Moreover,
-membership protocols are usually implemented by modifying the
+usually rely on gossip mechanisms, implying contacts with random nodes
+that can be far away in the physical topology. 
+They are mostly implemented by modifying the
 neighboring of a given node according to a certain metric in a logical
-overlay.  On the contrary, we do not aim at building any overlay, as
-we only rely on the physical topology so the neighbors of a given node
-are not continuously modified. Lastly, these protocols are usually
+overlay. On the contrary,  \NAME  does not aim at building any overlay, as
+it only relies on the physical topology so the neighbors of a given node
+are not continuously modified. These protocols are usually
 cycle-based, meaning that they impose a constant load on the network
-traffic, even when the system state does not change. Likewise, this
-also prevents from using solutions that periodically advertise their
-cache content~\cite{garcia-lopez, hemmati2015namebased} as they also
+traffic, even when the system state does not change. \NAME only generates traffic upon system changes.
+
+\item [Timeouts:]
+Solutions that periodically advertise their
+cache content~\cite{garcia-lopez, hemmati2015namebased} also
 incur an overhead even in quiet contexts without any update.
-Moreover, such solutions necessarily rely on physical timeouts that
+Moreover, they necessarily rely on physical timeouts that
 could lead to either premature removals of partitions when they are
 still operating; or slow convergence where processes wrongly believe
-they belong to a partition that was removed. On the opposite
+they belong to a partition that was removed. On the opposite,
 Section~\ref{sec:experimentation} shows that \NAME quickly converges
 to consistent partitioning even in large scale networks.
+
+\end{asparadesc}
 

### 2021-04-27 input/figproofA.tex
mostly about implem
wip
wip rw up to broadcast

@@
   \newcommand\X{95pt}
-  \newcommand\Y{-50pt}
+  \newcommand\Y{-60pt}
 
@@
 
-  \draw[<->] (5pt - \X, 0.4*\Y) -- node[below, font=\small]{\textbf{I: propagation}} (-5pt, 0.4*\Y); %% I
+  \draw[<->] (5pt - \X, 0.4*\Y) -- node[below, font=\small, align=center]{\textbf{I: propagation}\\\textbf{of $\alpha$ messages}} (-5pt, 0.4*\Y); %% I
 
@@
   \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
-  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below, font=\scriptsize]{somewhere: $\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
+  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below, font=\scriptsize]{some \process somewhere: $\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
 

### 2021-04-27 input/related_work.tex
wip rw up to broadcast

@@
 
+Content indexing services in geo-distributed infrastructures allow
+\processes to retrieve specific content while leveraging the
+advantages of replication. These systems mostly rely on dedicated
+location services host by possibly remote third-party \processes~\REF;
+and cutting the middleman requires that each \process maintains its
+own index in a decentralized fashion~\REF. This section reviews these
+approaches.
+
 \begin{asparadesc}
-\item [Remote third-party:]
-Relying on a remote third party service is a popular approach to offer content indexing in geo-distributed infrastructures. 
-Such a remote service should
+\item [Third-party:]
+
+Dedicated services possibly hosted by remote third-party \processes
+are popular, for they propose the simplest mean to deploy such
+service. They must maintain
 \begin{inparaenum}[(i)]
-\item have access to the list of current replica locations and
-\item be aware of the topology to decide which replica is the
-  closest for a given location.
+\item the list of current replicas along with their respective
+  location; and
+\item the network topology to determine the closest replica for every
+  requesting \process.
 \end{inparaenum}
 
+\noindent A central server that registers both these
+information~\cite{snamp, p2p-oracle, fogstore, p2p-alto} facilitates
+the computation, for it gathers all knowledge in one place. However,
+it comes with well-known issues inherent to its distribution paradigm
+such as load balancing, or single point of failure.
+%% Numerous solutions
+%% maintain an index of all replica locations on a centralized
+%% server. This comes with well-known disadvantages inherent to
+%% centralized solutions such as load balancing, robustness or locality
+%% that are even magnified in an Edge context.
+
+\noindent Distributing this index among \processes circumvents these
+issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
+locality issues where \processes
 \begin{inparaenum}[(i)]
-\item Numerous solutions~\cite{snamp, p2p-oracle, fogstore, p2p-alto} maintain an index of all replica
-locations on a centralized server. This comes with well-known disadvantages
-inherent to centralized solutions such as load balancing, robustness or locality that are even magnified in an Edge context.
-Distributing this index among nodes in the network circumvent some of
-these issues, either using coordinate-based overlays~\cite{voronet,
-  coin_19} or \underline{D}istributed \underline{H}ash
-\underline{T}ables (DHTs)~\cite{ipfs, mdht, squirrel}. In
-the latter, each node stores a part of the index, defined by an
-interval between hash values.  Before downloading any object, a node
-first hashes the content to obtain the address of the node that stores
-the replica locations of this given object. After obtaining from the
-remote node the list of available replicas, it can select the closest
-copy to download from. We emphasize that, in this setting, the DHT
-only stores information about replicas locations, not the content
-itself.
+\item request to a possibly far away location service the content
+  location, and then
+\item request the actual content from far away replicas.
+\end{inparaenum}
+For instance, using \underline{d}istributed \underline{h}ash
+\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
+stores a part of the index defined by an interval between hash values.
+The hash values are the keys to retrieve the associated content
+location.  Before downloading any content, a \node asks for its
+location using its key. After a series of round-trips between DHT
+servers possibly distant from each others, the \node gets a list of
+available replicas. Contrarily to \NAME, such services do not ensure
+to include the closest replica.
 
-\item Determining where resides the closest replica necessarily involves some knowledge about the current topology.
-Maintaining a consistent view of an ever changing
-topology across a network is inherently complicated, especially in
-asynchronous settings. As for the index,
-this knowledge about the topology can be either
-centralized~\cite{topology-discovery} or distributed like in routing
-protocols such as \underline{O}pen \underline{S}hortest
-\underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
-\end{inparaenum}
+\noindent In addition, they often do not include distance information
+along with replica location. Determining where resides the closest
+replica for every requesting \process necessarily involves some
+knowledge about the \emph{current} topology.  Maintaining a consistent
+view of an ever changing topology across a network is inherently
+complicated~\cite{topology-discovery, ospf}.
+%%  As for the index, this knowledge about the topology can be either
+%% centralized~\cite{topology-discovery} or distributed like in
+%% routing protocols such as \underline{O}pen \underline{S}hortest
+%% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
+As consequence, the requesting \node ends up downloading from multiple
+replica hosts, yet only keeping the fastest answer. \Processes either
+waste network resources, or face lower response time.
 
-All the aforementionned solutions require to contact a remote node to request this index which is costly in terms of
-latency while in contradiction with Edge infrastructure constraints, as previously explained.
+% We emphasize that, in this setting, the DHT only stores information
+% about replicas locations, not the content itself.
+
+%% Distributing this index among \processes in the network circumvent
+%% some of these issues, either using coordinate-based
+%% overlays~\cite{voronet, coin_19} or \underline{D}istributed
+%% \underline{H}ash \underline{T}ables (DHTs)~\cite{ipfs, mdht,
+%%   squirrel}. In the latter, each node stores a part of the index,
+%% defined by an interval between hash values.  Before downloading any
+%% object, a node first hashes the content to obtain the address of the
+%% node that stores the replica locations of this given object. After
+%% obtaining from the remote node the list of available replicas, it can
+%% select the closest copy to download from. We emphasize that, in this
+%% setting, the DHT only stores information about replicas locations, not
+%% the content itself.
+
+%% \noindent All the aforementionned solutions require to contact a remote node to
+%% request this index which is costly in terms of latency while in
+%% contradiction with Edge infrastructure constraints, as previously
+%% explained.
 

### 2021-04-27 input/related_work.tex
done, todo 10 pages

@@
 advantages of replication. These systems mostly rely on dedicated
-location services host by possibly remote third-party \processes~\REF;
-and cutting the middleman requires that each \process maintains its
-own index in a decentralized fashion~\REF. This section reviews these
-approaches.
+location services host by possibly remote third-party \processes; and
+cutting out the middleman requires that each \process maintains its
+own index in a decentralized fashion.
+% This section reviews these
+% approaches.
 
@@
 
-\item [Broadcast:]
-The opposite approach consists in hosting the index directly on the
-nodes, avoiding any prior request to access a content.
+\item [Fully decentralized:]
+
+Cutting out the middleman by hosting a location service on each and
+every \process improves response time of content retrieval. However,
+it still requires every \process to index every live replica as well
+as their respective distance in order to rank them.
+%% The opposite approach consists in hosting the index directly on the
+%% nodes, avoiding any prior request to access a content.
 \underline{N}amed \underline{D}ata \underline{N}etworking
-(NDN)~\cite{nlsr} broadcasts information about cache updates to all nodes in the
-system. Having the entire knowledge of all the
-replica locations along with distance information carried into
-messages, each node can easily determine where the closest copy of a
-given object resides, without contacting any remote node.  Similarly,
-one could use a
-\underline{C}onflict-\underline{F}ree \underline{R}eplicated
-\underline{D}atatype (CRDT) for set data structures, for
-example~\cite{shapiro2011crdts}. Yet both solutions inherently imply
-that every node will eventually receive all messages, contrary to \NAME.
+(NDN)~\cite{nlsr} broadcasts information about cache updates to all
+\nodes in the system. Having the entire knowledge of all the replica
+locations along with distance information carried into messages, each
+\node easily determine where the closest copy of specific content
+resides, without contacting any remote
+service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
+\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
+structures could also implement such a location service. \Processes
+would eventually have a set of all replicas, assuming eventual
+delivery of messages.
+\noindent Such solutions inherently imply that every \process receives
+every message, which contradicts with the principles of Edge
+infrastructures that aim at reducing the volume of data passing
+through the network. On the opposite, each \process running \NAME only
+registers its closest replica. This allows \NAME to use scoped
+broadcast as a communication primitive to lock down the traffic
+generated by content indexing based on distances.
+% Such solutions inherently imply that every node will
+% eventually receive all messages, contrary to \NAME.
 
-\item [Membership protocols:]
-At first glance, membership protocols~\cite{t-man}
-would appear to provide suitable abstractions to create a
-scope-related partitioning, as proposed in this paper. Such protocols
-usually rely on gossip mechanisms, implying contacts with random nodes
-that can be far away in the physical topology. 
-They are mostly implemented by modifying the
-neighboring of a given node according to a certain metric in a logical
-overlay. On the contrary,  \NAME  does not aim at building any overlay, as
-it only relies on the physical topology so the neighbors of a given node
-are not continuously modified. These protocols are usually
-cycle-based, meaning that they impose a constant load on the network
-traffic, even when the system state does not change. \NAME only generates traffic upon system changes.
+\item [Scoped flooding:]
 
-\item [Timeouts:]
-Solutions that periodically advertise their
-cache content~\cite{garcia-lopez, hemmati2015namebased} also
-incur an overhead even in quiet contexts without any update.
-Moreover, they necessarily rely on physical timeouts that
-could lead to either premature removals of partitions when they are
-still operating; or slow convergence where processes wrongly believe
-they belong to a partition that was removed. On the opposite,
-Section~\ref{sec:experimentation} shows that \NAME quickly converges
-to consistent partitioning even in large scale networks.
+Some state-of-the-art approaches also confine the dissemination of
+information to interested \processes based on distance. 
+% \item [Membership protocols:]
+
+\noindent Distance-based membership protocols such as
+T-Man~\cite{t-man} make \processes converge to a specific network
+topology depending on targeted properties. They periodically
+communicate with their neighbors to compare their state. Following
+this exchange, they add and remove communication links to other
+\processes. Over exchanges, they converge towards a topology ensuring
+the targeted properties.  While at first glance membership protocols
+and \NAME could share common preoccupations, \NAME does not aim at
+building any topology and never modifies neighbors of \processes.
+
+%% In
+%% addition, distance-based membership protocols often rely on random
+%% peer-sampling protocols to avoid falling in a local minimum that would
+%% stop them from reaching this targeted topology. This contradicts with
+%% the principles of Edge infrastructures as well, in a minor way.
+
+%% At first glance, membership protocols~\cite{t-man} would appear to
+%% provide suitable abstractions to create a scope-related
+%% partitioning, as proposed in this paper. Such protocols usually
+%% rely on gossip mechanisms, implying contacts with random nodes that
+%% can be far away in the physical topology.  They are mostly
+%% implemented by modifying the neighboring of a given node according
+%% to a certain metric in a logical overlay.
+
+%% These protocols are usually cycle-based, meaning that they impose a
+%% constant load on the network traffic, even when the system state does
+%% not change. \NAME only generates traffic upon system changes.
+
+\noindent The most closely related approaches to \NAME come from
+\underline{i}nformation-\underline{c}entric \underline{n}etworking
+(ICN)~\cite{garcia-lopez, hemmati2015namebased}. They periodically
+advertise their cache content, and advertisements stop as soon as they
+reach uninterested \processes. However their operation requires that
+\begin{inparaenum}[(i)]
+\item they constantly generate traffic even in quiescent systems where
+  \processes do not add nor destroy replicas; and 
+\item they define physical-clock-based timeouts the value of which
+  depends on network topology properties such as network diameter.
+  %also incur an overhead even in quiet contexts without any update.
+  % Moreover, they necessarily rely on physical timeouts
+  Unfitting timeouts lead to premature removals of live replicas; or
+  slow convergence where \processes wrongly believe that their closest
+  replica is live while it was destroyed.
+\end{inparaenum}
+On the opposite, \NAME quickly inform each \process of their closest
+replica even in large networks; and when the system becomes quiescent,
+\NAME has no overhead.
 

### 2021-04-27 input/related_work.tex
10 pages + typos

@@
 advantages of replication. These systems mostly rely on dedicated
-location services host by possibly remote third-party \processes; and
+location services host by possibly remote third-party \processes; but
 cutting out the middleman requires that each \process maintains its
@@
 
-\noindent A central server that registers both these
-information~\cite{snamp, p2p-oracle, fogstore, p2p-alto} facilitates
-the computation, for it gathers all knowledge in one place. However,
-it comes with well-known issues inherent to its distribution paradigm
-such as load balancing, or single point of failure.
+\noindent A central server that registers both these information
+facilitates the computation, for it gathers all knowledge in one
+place~\cite{snamp, p2p-oracle, fogstore, p2p-alto}. However, it comes with
+well-known issues such as load balancing, or single point of failure.
 %% Numerous solutions
@@
 delivery of messages.
-\noindent Such solutions inherently imply that every \process receives
-every message, which contradicts with the principles of Edge
-infrastructures that aim at reducing the volume of data passing
-through the network. On the opposite, each \process running \NAME only
-registers its closest replica. This allows \NAME to use scoped
-broadcast as a communication primitive to lock down the traffic
-generated by content indexing based on distances.
+\noindent Such solutions imply that every \process receives every
+message, which contradicts with the principles of Edge infrastructures
+that aim at reducing the volume of data passing through the
+network. On the opposite, each \process running \NAME only registers
+its closest replica. This allows \NAME to use scoped broadcast as a
+communication primitive to lock down the traffic generated by content
+indexing based on distances.
 % Such solutions inherently imply that every node will
@@
 
-Some state-of-the-art approaches also confine the dissemination of
-information to interested \processes based on distance. 
+Some state-of-the-art approaches confine the dissemination of messages
+to interested \processes too.
 % \item [Membership protocols:]
@@
 \end{inparaenum}
-On the opposite, \NAME quickly inform each \process of their closest
+On the opposite, \NAME quickly informs each \process of its closest
 replica even in large networks; and when the system becomes quiescent,

### 2021-04-27 input/proposal.tex
spacing

@@
 
-Algorithm~\ref{algo:edges} extends the instructions of \NAME that
-enable dynamic consistent partitioning in dynamic networks where
-\processes can join or leave the system without notification. We
-consider that removing a \process is equivalent to removing all its
-edges, and adding a \process is equivalent to add as many edges as
-necessary.
+Algorithm~\ref{algo:edges} extends \NAME to enable dynamic consistent
+partitioning in dynamic networks where \processes can join or leave
+the system without notification. We consider that removing a \process
+is equivalent to removing all its edges, and adding a \process is
+equivalent to add as many edges as necessary.
 
@@
 improves, the propagation of $\alpha$ messages operates normally.
-
-\noindent Removing an edge between two \processes may invalidate the
+Removing an edge between two \processes may invalidate the
 shortest path of one of involved \processes plus downstream

### 2021-06-09 rebuttal.tex
add rebuttal 495

We thank the reviewers for their thorough reading  and interesting comments.
We understand that althought the paper is relevant, some parts should be clarified. We would be happy to be shepperded if reviewers believe it is relevant.

Below, we reply to each remark in more detail.

- R1.1. "forwarding the best known partition"  consists in transmitting the best location where to get the replica.
It could be more formally defined.

- R1.2.  We agree ``Theorem'' is more appropriate than ``Corollary''. Regarding the proof, additional information would be given (under shepperding).

- R1.3. Regarding Theorem 2, we chose to list all cases to help understand the algorithm.
Every Add/Del operation creates a small subset of events that depends on its nature,
and the neighbors' history. This allows us to perform a neighbor-to-neighbor analysis of cases and avoid any combinatorial explosion.

- R2.1. Our objective is to introduce AS-cast and its properties in a generic manner. 
Hence, experiments focus on evaluating the correctness/costs of our protocol.
As stated in Conclusion, we plan to assess the use of AS-cast in IPFS distributed storage. This study would clarify its tradeoff depending on object size, update frequency, etc.

- R2.2. AS-cast is more efficient than CDN: it allows (i) retrieving the closest location eventually and (ii) partitioning the infrastructure dynamically according to the creation/removal of replicas. Contrarily, CDN relies on a static partitioning of the infrastructure: nodes get replicas from a subset of specific nodes and for all objects. A node may contact a peer of the CDN infrastructure while a replica may exist only one hop away (replicated by one of its neighbors). 
AS-cast natively deals with such cases as any node can serve a replica.

- R2.3.  The scalability issue related to the management of thousands of 
objects should be addressed. As stated in Conclusion, we propose to leverage the
hierarchical properties of inter-autonomous systems to avoid flooding uninterested nodes. 
However, this increases the complexity to prove that our protocol still converge.

- R3.1. In addition to  R2.3, we confirm that partitioning is per-object.
Yet, it would be straightforward indeed to mutualize traffic, e.g., using dedicated propagation windows to consolidate control messages together.

- R3.2. AS-cast does not handle replication strategies. If it exists only one source and it crashes, this reference eventually disappears from the system. AS-cast reacts similarly to crashes and departures of sources (see Algorithm 3 Line 4) to update the best partition known by impacted nodes.

- R3.3. We do not  address the issue of content mutability.
From our viewpoint, this aspect is application-dependent. For instance, mutability could be provided by versioning as done in IPFS, BlobSeer, etc.

- R3.4. Regarding the experiments remarks, please, refer to R2.2.

- R3.5. Several approaches tackle the indexation problem in NDN. We were unaware of NDNS and agree to add it in Related Work.

- R3.6. Although network topologies include triangular inequalities,  they do not endanger the AS-CAST correctness (AS-CAST relies on the shortest distance between vertices).

### 2021-09-01 paper-rr.tex
rapport recherche first step, need cosmetic fixes now.

\documentclass[twoside]{article}

\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{RR}
\usepackage{hyperref}
\usepackage[frenchb, british]{babel}

%% url
\usepackage{url}
%% maths
\usepackage{amsmath,amssymb,amsthm,bm}
%% \usepackage{amsfonts}

%% algorithms
\usepackage{algorithmicx}
\usepackage[ruled, linesnumbered, noend]{algorithm2e}

%% images
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
%% inparaenum
\usepackage{paralist}

%% tables
\usepackage{booktabs}
\usepackage{multirow}
%% figures
%\usepackage{caption}
\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,plotmarks,shapes,matrix}
%% transform eps in pdf crossplateform
\usepackage{epstopdf}
\usepackage{epsfig}

\usepackage{xspace}

\newcommand{\NAME}[0]{\mbox{AS-cast}\xspace}
\newcommand{\NAMEB}[0]{\mbox{S-cast}\xspace}
\newcommand{\TODO}[1]{\textcolor{red}{#1}}
\newcommand{\REF}[0]{\textcolor{purple}{REF}\xspace}

\newcommand{\PA}[0]{SkyBlue}
\newcommand{\PB}[0]{BurntOrange}
\newcommand{\PC}[0]{YellowGreen}
\newcommand{\PD}[0]{YellowGreen}
\newcommand{\PH}[0]{Orchid}
\newcommand{\WRONG}[0]{red!75}

\newtheorem{problem}{Problem Statement}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\eventually}{\square\,}
\newcommand{\ie}{{i.e.,}\xspace}
\newcommand{\eg}{{e.g.,}\xspace}

\newcommand{\process}{node\xspace}
\newcommand{\processes}{nodes\xspace}
\newcommand{\Process}{Node\xspace}
\newcommand{\Processes}{Nodes\xspace}
\newcommand{\node}{\process}
\newcommand{\nodes}{\processes}
\newcommand{\Node}{\Process}
\newcommand{\Nodes}{\Processes}

%% RR %%

\RRNo{XXXX}
\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  \thanksref{aff1}
  \and
  Alexandre Van Kempen
  \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation de contenu décentralisée au niveau du Edge} %% titre français long
\titlehead{\RRtitle{} } %% titre français court
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

\RRresume{%
  \begin{otherlanguage}{french}
  Bien qu'une solution parfaite pour le stockage et la manipulation de
  données au niveau des infrastructures Edge reste encore à
  déterminer, les approches de l'état de l'art ont d'ors et déjà
  démontré la pertinence des stratégies de réplication qui rapprochent
  le contenu des consommateurs : ces derniers bénéficient de meilleurs
  temps de réponse et le volume de données transitant par le réseau
  diminue globalement.
  %
  Malheureusement, localiser la réplique la plus proche d'un contenu
  spécifique nécessite d'indexer \emph{chacune} des répliques
  \emph{existantes} avec leurs informations de \emph{localisation}.
  %
  Se fier à des services distants entre en contradiction avec les
  propriétés des infrastructures Edge de telle sorte que localiser des
  répliques prend davantage de temps que de télécharger le contenu.  À
  l'opposé, chaque nœud ne peut maintenir l'index des toutes les
  répliques existantes car cela s'avèrerait extrêmement coûteux en
  termes de mémoire et de trafic, en particulier lorsque les nœuds
  sont libres de créer ou détruire des répliques à n'importe quel
  moment.
  %
  Dans cet article, nous abstrayons l'indexation de contenu par un
  problème de partitionnement réparti : chacun des nœuds maintient
  l'index de sa réplique la plus proche, et les nœuds connectés
  possédant un index similaire font partie d'une même partition. Notre
  implémentation décentralisée nommée \NAME est
  \begin{inparaenum}[(i)]
  \item efficace, car elle utilise les partitions afin de confiner
    le trafic généré par son fonctionnement aux seuls nœuds
    concernés, tout en
  \item garantissant le fait que chaque nœud finisse par identifier
    la partition à laquelle il appartient, et ce malgré les
    opérations concurrentes.
  \end{inparaenum}
  Notre analyse en complexité appuyée par des simulations montre que
  \NAME passe à l'échelle en termes de trafic généré et de temps de
  terminaison. De ce fait, \NAME peut constituer les nouvelles
  fondations pour construire des services géo-distribués.
  \end{otherlanguage}
}

\RRabstract{
  Although the holy grail to store and manipulate data in Edge
  infrastructures is yet to be found, state-of-the-art approaches
  demonstrated the relevance of replication strategies that bring
  contents closer to consumers: The latter enjoy better response time
  while the volume of data passing through the network decreases
  overall. Unfortunately, locating the closest replica of a specific
  content requires indexing \emph{every live} replica along with its
  \emph{location}.
  %
  Relying on remote services contradicts with the properties of Edge
  infrastructures as locating replicas may effectively take more time
  than actually downloading contents.  At the opposite, maintaining
  such an index at every \process would prove overly costly in terms
  of memory and traffic, especially since \processes can create and
  destroy replicas at any time.

  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
  every \process only indexes its closest replica, and
  connected \processes with a similar index compose a partition. Our
  decentralized implementation \NAME is
  \begin{inparaenum}[(i)]
  \item efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time. As
  such, \NAME can constitute a new building block for geo-distributed
  services.
}

\RRmotcle{Indexation de contenu, partitionnement logique, algorithme décentralisé}
\RRkeyword{Content indexing, logical partitioning, decentralized algorithm}

\RCRennes

\RRequipe{STACK}

% \title{\NAME: Lock Down the Traffic\\of Decentralized Content Indexing at the Edge}
%% \NAME: Adaptive scoped broadcast for the edge

%\author{Adrien L{\`e}bre, Brice N{\'e}delec, Alexandre Van Kempen
%% \author{\IEEEauthorblockN{Anonymous}
%%  \IEEEauthorblockA{\textit{Affiliation}, City, Country\\email address or ORCID}
%% }

\begin{document}
% \proceedings{}
%\copyright{Adrien l{\'ebre}, Brice N{\'e}delec, Alexandre Van Kempen}

\makeRR
\RRNo{XXXX}

%% \input{input/abstract.tex}

\input{input/introduction.tex}
\input{input/background.tex}
\input{input/proposal.tex}
\input{input/experiments.tex}
\input{input/related_work.tex}
\input{input/conclusion.tex}
%% \input{input/acknowledgment.tex}

\bibliographystyle{plainurl}
\bibliography{bibliographie}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-09-01 RR-9418.tex
cosmetic + number

--- 2021-09-01 paper-rr.tex
@@
 
-\RRNo{XXXX}
+\RRNo{9418}
 \RRdate{September 2021}
@@
   Adrien L{\`e}bre
-  \thanks[aff1]{Inria}
+  %%  \thanks[aff1]{Inria}
   \and
   Brice N{\'e}delec
-  \thanksref{aff1}
+  %% \thanksref{aff1}
   \and
   Alexandre Van Kempen
-  \thanksref{aff1}
+  %% \thanksref{aff1}
 }
 \authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
-\RRtitle{\NAME : Confiner le trafic de l'indexation de contenu décentralisée au niveau du Edge} %% titre français long
-\titlehead{\RRtitle{} } %% titre français court
+\RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long
+\titlehead{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français court
 \RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}
@@
 
-\RRmotcle{Indexation de contenu, partitionnement logique, algorithme décentralisé}
-\RRkeyword{Content indexing, logical partitioning, decentralized algorithm}
+\RRmotcle{Indexation de contenu, partitionnement logique, algorithme décentralisé, Edge}
+\RRkeyword{Content indexing, logical partitioning, decentralized algorithm, Edge}
 
@@
 \makeRR
-\RRNo{XXXX}
+\RRNo{9418}
 

### 2021-09-01 input/experiments.tex
spacing
cosmetic + number

@@
 \begin{figure}
-  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
+  \centering\includegraphics[width=0.8\columnwidth]{img/as_cast_complexity.eps}
   \caption{\label{fig:complexity}Overhead of consistent partitioning
@@
 \begin{figure}
-  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
+  \centering\includegraphics[width=0.8\columnwidth]{img/as_cast_geant.eps}
   \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
@@
 experiment involving one source for two clusters, it generates
-traffic. After a $200$ ms delay corresponding to the link latency, the
+traffic. After a $200$ milliseconds delay corresponding to the link latency, the
 cut off cluster starts to communicate $\alpha$ messages

### 2021-09-01 input/figproblem.tex
minors
cosmetic + number

@@
       3$.]{\input{input/figproblemA.tex}}
-    \hspace{5pt} \subfloat[Part B][\label{fig:problemB}\Process~$b$
+    \hspace{1pt}
+    \subfloat[Part B][\label{fig:problemB}\Process~$b$
       delivers and forwards the $\alpha$ message about $P_a$ while
@@
       messages about $P_d$.]  {\input{input/figproblemB.tex}}
-    \hspace{5pt} \subfloat[Part C][\label{fig:problemC}\Process~$b$
+    \hspace{1pt}
+    \subfloat[Part C][\label{fig:problemC}\Process~$b$
       already blocks the propagation of $\delta_a$ despite it
-      propagated $\alpha_a$ before. \Process~$c$ and \Process~$d$ do not
-      deliver $\alpha_d$, for they already deleted
-      it before.]{\input{input/figproblemC.tex}}
-    \hspace{5pt} \subfloat[Part D][\label{fig:problemD}\Processes
+      propagated $\alpha_a$ before. \Process~$c$ does not deliver
+      $\alpha_d$, for it already deleted it
+      before.]{\input{input/figproblemC.tex}}
+    \hspace{1pt}
+    \subfloat[Part D][\label{fig:problemD}\Processes
       discard remaining messages. Since \Process~$b$ cannot deliver

### 2021-09-01 input/proposal.tex
cosmetic + number

@@
   message, and a \underline{p}redicate $\phi$ verified from \process to
-  \process: {\small{$b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
-  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$}}.
+  \process: {$b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
+  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$}.
 \end{definition}
@@
   the \underline{p}artition including at least \Process~$s$, each
-  \process belongs to at most one partition \smash{\small$\forall p,q \in V, \forall
-  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
+  \process belongs to at most one partition \smash{$\forall p,q \in V, \forall
+  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies$} \smash{$p \neq q
   \vee s_1 = s_2$}, and there exists at least one path $\pi_{ps}$ of

### 2021-09-02 input/experiments.tex
first step in styling

@@
 
-\subsection{Confirm the complexity analysis stating that
-  communication and time overheads depend on the current partitioning
-  of the system.}
+%% \subsection{Confirm the complexity analysis stating that
+%%   communication and time overheads depend on the current partitioning
+%%   of the system.}
 
 \begin{asparadesc}
+\item [Objective:] Confirm the complexity analysis stating that
+  communication and time overheads depend on the current partitioning
+  of the system.
+
 \item [Description:]
@@
 
-% \subsection{Confirm the relevance of \NAME in the context of dynamic inter-autonomous
-%   system communications.}
-\subsection{Confirm that \NAME locks down the traffic of decentralized content
-  indexing in the context of dynamic inter-autonomous system
-  communications.}
+%% \subsection{Confirm that \NAME locks down the traffic of decentralized content
+%%   indexing in the context of dynamic inter-autonomous system
+%%   communications.}
 
 \begin{asparadesc}
+
+\item [Objective:] Confirm that \NAME locks down the traffic of decentralized content
+  indexing in the context of dynamic inter-autonomous system
+  communications.
+
 \item [Description:]

### 2021-09-02 input/abstract.tex
typos of review

@@
   demonstrated the relevance of replication strategies that bring
-  contents closer to consumers: The latter enjoy better response time
+  content closer to consumers: The latter enjoy better response time
   while the volume of data passing through the network decreases
@@
   % 
-  Relying on remote services contradicts with the properties of Edge
-  infrastructures as locating replicas may effectively take more time
-  than actually downloading contents.  At the opposite, maintaining
-  such an index at every \process would prove overly costly in terms
-  of memory and traffic, especially since \processes can create and
-  destroy replicas at any time.
+  Relying on remote services enters in contradiction with the
+  properties of Edge infrastructures as locating replicas may
+  effectively take more time than actually downloading content.  At
+  the opposite, maintaining such an index at every \process would
+  prove overly costly in terms of memory and traffic, especially since
+  \processes can create and destroy replicas at any time.
 

### 2021-09-02 input/background.tex
intro reworkd with bullet and contribution
cosmetic + number
first step in styling
typos of review

@@
 \label{sec:background}
+
+\input{input/figpartitionintuition.tex} %% positioning
 
@@
 northern one, \processes hosting a replica must add \emph{location
-information} along with their notifications. As consequence, every
+information} along with their notifications. As a consequence, every
 \process eventually knows every replica location and can download from
@@
 long as they consider them useful based on location information they
-carry. We call such primitive \emph{scoped broadcast} (see
+carry. We call such a primitive \emph{scoped broadcast} (see
 Section~\ref{subsec:scoped}), for messages transitively reach a subset
@@
 Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
-destroys its replica. Every \processes that belonged to its green
+destroys its replica. Every \process that belonged to its green
 partition must choose another partition to be in. While it makes sense
@@
 called \NAME along with its complexity.
-
-\vfill
-\TODO{spacing.}
-\newpage
 

### 2021-09-02 input/conclusion.tex
typos of review

@@
 concurrent operations that may impair the propagation of messages, and
-in turns, lead to inconsistent partitioning.
+in turn, lead to inconsistent partitioning.
 %% The major difficulty lies in concurrent operations, each having a
@@
 \noindent We also would like to evaluate \NAME within a concrete
-storage systems such as \underline{I}nter\underline{P}lanetary
+storage system such as \underline{I}nter\underline{P}lanetary
 \underline{F}ile \underline{S}ystem

### 2021-09-02 input/experiments.tex
typos of review

@@
 overhead of reaching consistent partitioning using \NAME in large
-scale networks?  Does \NAME is relevant in Edge infrastructures where
+scale networks?  Is \NAME relevant in Edge infrastructures where
 \processes are geo-distributed into clusters? We performed the
@@
 Figure~\ref{fig:geant} shows the results of this experimentation. The
-top part displays the one source experiment while the bottom part
-displays the one source per cluster experiment.
+top part displays the results with one source while the bottom part
+displays the results with one source per cluster.
 

### 2021-09-02 input/introduction.tex
cosmetic + number
first step in styling
typos of review

@@
 \section{Introduction}
-
-\input{input/figpartitionintuition.tex} %% positioning
 
@@
 
-These approaches contradict with the objectives of Edge
+These approaches are in contradiction with the objectives of Edge
 infrastructures that aim at reducing the impact of latency as well as
@@
 locations, it often ends up downloading from multiple replica hosts,
-yet only keeping the fastest answer. In turns, clients either waste
+yet only keeping the fastest answer. In turn, clients either waste
 network resources, or face lower response time.
@@
 
-To tackle aforementioned limitations, every \process that might
+To address the aforementioned limitations, every \process that might
 request or replicate content must also host its own content indexing
@@
 operation~\cite{birman1999bimodal, hadzilacos1994modular,
-  raynal2013distributed}. Unfortunately, this also contradicts with
-Edge infrastructure objectives, for such protocol does not confine the
+  raynal2013distributed}. Unfortunately, this also contradicts Edge
+infrastructure objectives, for such a protocol does not confine the
 traffic generated to maintain its indexes. A \process may acknowledge
@@
 problem behind our proposal.  Section~\ref{sec:adaptive} describes
-dynamic consistent partitioning and its implementation along with its
-complexity. Section~\ref{sec:experimentation} presents our
-evaluations.  Section~\ref{sec:related_work} reviews related
+dynamic consistent partitioning and its implementation along with an
+analysis of its complexity. Section~\ref{sec:experimentation} presents
+our evaluations.  Section~\ref{sec:related_work} reviews related
 work. Finally, Section~\ref{sec:conclusion} concludes and discusses

### 2021-09-02 input/proposal.tex
typos of review

--- 2021-04-27 input/proposal.tex
@@
 then discusses the properties that guarantee consistent partitioning
-in our context, and finally details our implementation \NAME and its
-complexity.
+in our context, and finally details our implementation \NAME and the
+analysis of its complexity.
 
@@
 At any time, a \process can decide to become a \emph{source}, hence
-creating a new partition in the system by executing an \texttt{Add}
+creating a new partition in the system by executing an exttt{Add}
 operation. This partition includes at least its source plus
 neighboring \processes that estimate they are closer to this source
-than any other one. Such distance (or \emph{weight}) is
+than any other one. Such a distance (or \emph{weight}) is
 application-dependant: in the context of maintaining distributed
@@
   b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
-  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
+  $\nexists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
   convey \emph{stale} control information.
@@
 \processes generate traffic not only related to their current
-partition, but also related to partitions they belong to in the
+partition, but also related to partitions they belonged to in the
 past. This would prove overly expensive in dynamic systems where
@@
     be. Nonetheless, they deliver and forward $\alpha_h$ that at least
-    one following \process will receive:
+    one following \process will receive.
   \item [\processes with $\delta_h \rightarrow \alpha_d$:] \Processes
@@
     \processes must purge their possibly stale state, for the sake of
-    consistency.  We note such notification $\delta_d?$ to emphasize
+    consistency.  We note such a notification $\delta_d?$ to emphasize
     the uncertainty of a $\delta$ message.
@@
 This vector enables both Propagation~I and Propagation~I'.  Its size
-increases linearly with the number of sources that the \process ever
-known, which is the number of \processes in the system
+increases linearly with the number of sources that the \process has
+ever known, which is the number of \processes in the system
 $\mathcal{O}(V)$ in the worst case.
@@
 of the partition along with a path $\pi$ comprising the identity of
-\processes that forwarded the corresponding $\alpha$ message. Such
+\processes that forwarded the corresponding $\alpha$ message. Such a
 $\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$
@@
 \end{inparaenum}
-In terms of number of messages, in the average-case, a \process $i$
+In terms of number of messages, in the average case, a \process $i$
 chosen uniformly at random among all \processes creates a logical
@@
 reaching \processes that belong to another partition closer to
-them. This splits partitions in half in average. Overall, the $a^{th}$
+them. This splits partitions in half on average. Overall, the $a^{th}$
 new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
@@
       \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
-number of neighbors per \process. % \TODO{Multiple receipt and
-multiple
+number of neighbors per \process.
+% \TODO{Multiple receipt and
+% multiple
 %  delivery imply more messages (receipt bounded by $|O|$ as well).}

### 2021-09-02 input/related_work.tex
typos of review

@@
 advantages of replication. These systems mostly rely on dedicated
-location services host by possibly remote third-party \processes; but
+location services hosted by possibly remote third-party \processes; but
 cutting out the middleman requires that each \process maintains its
@@
 Dedicated services possibly hosted by remote third-party \processes
-are popular, for they propose the simplest mean to deploy such
+are popular, for they propose the simplest mean to deploy such a
 service. They must maintain
@@
 location using its key. After a series of round-trips between DHT
-servers possibly distant from each others, the \node gets a list of
+servers possibly distant from each other, the \node gets a list of
 available replicas. Contrarily to \NAME, such services do not ensure
@@
 %% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
-As consequence, the requesting \node ends up downloading from multiple
+As a consequence, the requesting \node ends up downloading from multiple
 replica hosts, yet only keeping the fastest answer. \Processes either
@@
 \noindent Such solutions imply that every \process receives every
-message, which contradicts with the principles of Edge infrastructures
-that aim at reducing the volume of data passing through the
-network. On the opposite, each \process running \NAME only registers
-its closest replica. This allows \NAME to use scoped broadcast as a
-communication primitive to lock down the traffic generated by content
-indexing based on distances.
+message, which contradicts the principles of Edge infrastructures that
+aim at reducing the volume of data passing through the network. On the
+opposite, each \process running \NAME only registers its closest
+replica. This allows \NAME to use scoped broadcast as a communication
+primitive to lock down the traffic generated by content indexing based
+on distances.
 % Such solutions inherently imply that every node will

### 2021-09-03 RR-9418.tex
minor typo fixes

@@
 
-\RRNo{9418}
 \RRdate{September 2021}
@@
   %
-  Relying on remote services contradicts with the properties of Edge
-  infrastructures as locating replicas may effectively take more time
-  than actually downloading contents.  At the opposite, maintaining
-  such an index at every \process would prove overly costly in terms
-  of memory and traffic, especially since \processes can create and
-  destroy replicas at any time.
+  Relying on remote services enters in contradiction with the
+  properties of Edge infrastructures as locating replicas may
+  effectively take more time than actually downloading content.  At
+  the opposite, maintaining such an index at every \process would
+  prove overly costly in terms of memory and traffic, especially since
+  \processes can create and destroy replicas at any time.
 
@@
 
+\RRNo{9418}
 \makeRR
-\RRNo{9418}
 

### 2021-09-03 input/proposal.tex
negligible
slowly addressing reviews

@@
 At any time, a \process can decide to become a \emph{source}, hence
-creating a new partition in the system by executing an exttt{Add}
+creating a new partition in the system by executing an \texttt{Add}
 operation. This partition includes at least its source plus
@@
 application-dependant: in the context of maintaining distributed
-indexes, this would be about link latency.
+indexes, this would be about link latency that \nodes could monitor
+by aggregating \texttt{ping}s.
 
@@
   the \underline{p}artition including at least \Process~$s$, each
-  \process belongs to at most one partition \smash{\small$\forall p,q \in V, \forall
+  \process belongs to at most one partition $\forall p,q \in V, \forall
   s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
-  \vee s_1 = s_2$}, and there exists at least one path $\pi_{ps}$ of
+  \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
   \processes that belong to this partition $\forall q \in \pi_{ps}: q
@@
   from $x$ to $z$ the weight of which $|\Pi_{xz}|$ is lower than any
-  other path weight, the only consistent partitioning $\mathcal{P}$ is
-  a set of partitions $P_{s\in S}$ such that each \process belongs to
-  a logical partition comprising its closest source: $\forall p \in
-  P_{s_1}: \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
+  other path weight, with $|\Pi_{xx}|$ being the greatest lower bound
+  of $x$, the only consistent partitioning $\mathcal{P}$ is a set of
+  partitions $P_{s\in S}$ such that each \process belongs to a logical
+  partition comprising its closest source: $\forall p \in P_{s_1}:
+  \nexists P_{s_2}$ such that $|\Pi_{s_2p}| < |\Pi_{s_1p}|$.
 \end{definition}
@@
 \process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
-reach consistent partitioning if each \process eventually forwards its
-best known partition.
+reach consistent partitioning if each \process eventually
+\underline{f}orwards ($f_p(m) \implies \forall \langle p, q\rangle \in
+E: s_{pq}(m)$) its best known partition.
 \end{theorem}
@@
 While only adding logical partitions to the distributed system is
-straightforward, removing them introduces additional complexity.
+straightforward, removing them introduces additional complexity caused
+by concurrent operations.
 
@@
 
-\begin{corollary}[\label{theo:dcp}purge + BEF $\implies$
+\begin{theorem}[\label{theo:dcp}purge + BEF $\implies$
     \underline{D}ynamic \underline{c}onsistent
@@
 \end{inparaenum}
-\end{corollary}
+\end{theorem}
 

### 2021-09-03 input/figadd.tex
cosmetic + number
first step in styling
ongoing wip

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:addA}Both \Process~$a$ and \Process~$d$
+    \subfloat[Part A][\label{fig:addA}Both $a$ and $d$
       become sources.  $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
       3$.]  {\input{input/figaddA.tex}}
-    \hspace{5pt}
-    \subfloat[Part B][\label{fig:addB}Messages transit through communication
+    \hspace{1pt}
+    \subfloat[Part B][\label{fig:addB}Messages transit through %communication
       links and carry increasing weights.]{\input{input/figaddB.tex}}
-    \hspace{5pt} \subfloat[Part C][\label{fig:addC}\Process~$b$ and
-      \Process~$c$ receive, deliver, and forward $\alpha_{d}^{1}$ and
+    \hspace{1pt}
+    \subfloat[Part C][\label{fig:addC}$b$ and
+      $c$ receive, deliver, and forward $\alpha_{d}^{1}$ and
       $\alpha_d^3$ respectively.]{\input{input/figaddC.tex}}
-    \hspace{5pt} \subfloat[Part D][\label{fig:addD}$a$ and
+    \hspace{1pt}
+    \subfloat[Part D][\label{fig:addD}$a$ and
       $b$ discarded their received messages. $c$ still improved with $\alpha_d^2$.]

### 2021-09-03 input/figproblem.tex
first step in styling
ongoing wip

@@
       3$.]{\input{input/figproblemA.tex}}
-    \hspace{1pt}
-    \subfloat[Part B][\label{fig:problemB}\Process~$b$
+    \hspace{0pt}
+    \subfloat[Part B][\label{fig:problemB}$b$
       delivers and forwards the $\alpha$ message about $P_a$ while
@@
       messages about $P_d$.]  {\input{input/figproblemB.tex}}
-    \hspace{1pt}
-    \subfloat[Part C][\label{fig:problemC}\Process~$b$
+    \hspace{0pt}
+    \subfloat[Part C][\label{fig:problemC}$b$
       already blocks the propagation of $\delta_a$ despite it
-      propagated $\alpha_a$ before. \Process~$c$ does not deliver
+      propagated $\alpha_a$ before; and $c$ does not deliver
       $\alpha_d$, for it already deleted it
       before.]{\input{input/figproblemC.tex}}
-    \hspace{1pt}
+    \hspace{0pt}
     \subfloat[Part D][\label{fig:problemD}\Processes
-      discard remaining messages. Since \Process~$b$ cannot deliver
-      $\delta_a$, $c$ and $d$ remain in the deleted partition
-      $P_a$.]{\input{input/figproblemD.tex}}
+      discard remaining messages. Since $b$ cannot deliver
+      $\delta_a$, $c$ and $d$ remain in the deleted $P_a$.]
+             {\input{input/figproblemD.tex}}
   \end{center}

### 2021-09-03 input/proposal.tex
ongoing wip

@@
   message, and a \underline{p}redicate $\phi$ verified from \process to
-  \process: {\small{$b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
-  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$}}.
+  \process: $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
+  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$.
 \end{definition}
@@
 
-\begin{definition}[\label{def:lwo}Last win order and staleness]
-  When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
-  b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
-  $\nexists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
-  convey \emph{stale} control information.
+\begin{definition}[\label{def:lwo}Message staleness]
+  A message $m$ conveys \underline{s}tale control information if the
+  process that broadcast $m$ later broadcast another message $m'$:
+  $S(m) = \exists m': b_p(m) \rightarrow b_p(m')$.
+
+  %% When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
+  %% b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
+  %% $\nexists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
+  %% convey \emph{\underline{s}tale} control information: $S(m)$.
 \end{definition}
@@
 \ie where \processes receive the messages in the order of their
-sending. Both \Process~$a$ and \Process~$d$ add then delete their
+sending ($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
+r_q(m')$). Both \Process~$a$ and \Process~$d$ add then delete their
 partition concurrently. \Process~$c$ receives, delivers, and forwards
@@
 
-\begin{theorem}[\label{theo:dcp}purge + BEF $\implies$
+\begin{theorem}[\label{theo:dcp}Purge + BEF $\implies$
     \underline{D}ynamic \underline{c}onsistent
@@
 \begin{inparaenum}[(i)]
-\item eventual purging of stale messages ($b_p(m) \rightarrow b_p(m')
-  \implies \eventually (d_q(m) \implies d_q(m) \rightarrow
-  d_q(m''))$);
-\item and best eventual forwarding.
+\item eventual purging of stale messages ($S(m)
+  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
+  d_q(m'))$);
+\item and best eventual forwarding so such an $m'$ ends up originating from 
+  the best up-to-date source for $q$.
 \end{inparaenum}
@@
 \begin{proof}
-  \Processes deliver and forward the best sum of weights they
-  received. Figure~\ref{fig:proofA} depicts the only case where a
+  %% To reach consistent partitioning, the last message delivered by
+  %% every process is not stale and comes from its respective best
+  %% source: $d(m)$
+  % As for CP, DCP requires that every process' last delivery
+
+  \processes deliver and forward the best sum of weights they
+  received. Figure~\ref{fig:proofA} depicts the generic case where a
   \process would block the epidemic propagation: the \process received
@@
 
-\begin{theorem}[three-phase purge] % Propagations $+$ detection $\implies$ purge]
+\begin{theorem}[Three-phase purge] % Propagations $+$ detection $\implies$ purge]
   Purging stale control information from its source to every \process
@@
 
-To implement last win order as stated in Definition~\ref{def:lwo},
-each \process maintains a vector of versions that associates the
-respective known local counter of each known source, or has-been
-source. Each message $m$ carries its source $s$ along with its version
-$c$ that we subscript $m_{s, c}$.  Each \process delivers and forwards
+To implement the removal of stale messages as stated in
+Definition~\ref{def:lwo}, each \process maintains a vector of versions
+that associates the respective known local counter of each known
+source, or has-been source. Each message $m$ carries its source $s$
+along with its version $c$ that we subscript $m_{s, c}$.  Each
+\process delivers and forwards
 \begin{inparaenum}[(i)]

### 2021-09-03 input/proposal.tex
wip on theorem 8

@@
 
-\begin{theorem}[\label{theo:dcp}Purge + BEF $\implies$
+\begin{theorem}[\label{theo:dcp}BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
     \underline{D}ynamic \underline{c}onsistent
@@
 %
-When each \process can \texttt{Add} and \texttt{Del}ete its partition
-at any time, consistent partitioning requires
+When a \process can \texttt{Add} and \texttt{Del}ete its partition,
+consistent partitioning additionally requires
 \begin{inparaenum}[(i)]
@@
   d_q(m'))$);
-\item and best eventual forwarding so such an $m'$ ends up originating from 
-  the best up-to-date source for $q$.
+\item then best eventual forwarding so such an $m'$ ends up
+  originating from the best up-to-date source for $q$.
 \end{inparaenum}
@@
   %% source: $d(m)$
-  % As for CP, DCP requires that every process' last delivery
-
-  \processes deliver and forward the best sum of weights they
-  received. Figure~\ref{fig:proofA} depicts the generic case where a
-  \process would block the epidemic propagation: the \process received
-  and delivered a message from a partition that has since then been
-  deleted but with a better sum of weights than newly received ones
-  (in the example $\alpha_d^y < \alpha_a^{x'}$). Removing
-  \emph{forever} all such stale messages about deleted partitions
-  would allow \processes to propagate their best up-to-date partition
-  again, eventually reaching consistent partitioning together, as
-  stated by Theorem~\ref{theo:bef}.
+  Assuming BEF as default propagation behavior where \processes
+  deliver and forward the best sum of weights they received. We need
+  to prove that despite stale messages, the last delivery of every
+  process is the message that followed the shortest path to its
+  closest source.
+  \begin{asparadesc}
+  \item [BEF without Purge:] Figure~\ref{fig:proofA} depicts the
+    generic case where a \process $b$ precludes itself and subsequent
+    \processes such as $c$ of delivering the message from their
+    respective best source $a$. \Process $b$ received and delivered a
+    message from a partition that has since then been deleted but with
+    a better sum of weights than newly received ones ($\alpha_d^y <
+    \alpha_a^{x'}$). It forever discards such a message
+    $\alpha_a^{x'}$.
+  \item [Purge not followed by BEF:] Even assuming that every process
+    immediately removes stale control information $S(\alpha_d^y)
+    \implies d_b(\alpha_d^y) \rightarrow d_b(\delta_d)$, but received
+    $\alpha^{x'}_a$ earlier $d_b(\alpha^{x'}_a) \rightarrow
+    d_b(\alpha^y_d)$, it may never receive it again, hence staying
+    with an empty state or another message that did not follow its
+    shortest path to its best source.
+  \item [Purge then BEF:] Removing \emph{forever} all such stale
+    messages about deleted partitions would allow \processes to
+    propagate their best up-to-date partition again, eventually
+    reaching consistent partitioning together, as stated by
+    Theorem~\ref{theo:bef}.
+  \end{asparadesc}
 \end{proof}

### 2021-09-06 input/proposal.tex
meow

@@
 can add or delete its partition at any time. \Processes need to
-exploit their local knowledge gathered over message receipts.
-
-One could guarantee consistent partitioning by always propagating the
-$\delta$ messages corresponding to the $\alpha$ messages it propagated
-before. In Figure~\ref{fig:problem}, it means that as soon as
-\Process~$b$ forwards $\alpha_a^2$, it assumes that its neighbors
-\Process~$c$ and \Process~$d$ may need the notification of removal
-$\delta_a$ if it exists. However, such a solution also implies that
-\processes generate traffic not only related to their current
-partition, but also related to partitions they belonged to in the
-past. This would prove overly expensive in dynamic systems where
-\processes join and leave the system, create and delete partitions, at
-any time.  Instead, we propose to use the delivery order at each
-\process to detect possible inconsistencies and solve them. Together,
-\processes eventually remove all stale control information (transiting
-messages and local states) of the system leaving room for propagation
-of messages about up-to-date partitions.
+exploit their local knowledge gathered over message receipts to allow
+up-to-date messages to propagate to relevant \processes.
 
@@
   Assuming BEF as default propagation behavior where \processes
-  deliver and forward the best sum of weights they received. We need
-  to prove that despite stale messages, the last delivery of every
+  deliver and forward the best sum of weights they received. We must
+  prove that despite stale messages, the last delivery of every
   process is the message that followed the shortest path to its
@@
   \begin{asparadesc}
-  \item [BEF without Purge:] Figure~\ref{fig:proofA} depicts the
-    generic case where a \process $b$ precludes itself and subsequent
-    \processes such as $c$ of delivering the message from their
-    respective best source $a$. \Process $b$ received and delivered a
-    message from a partition that has since then been deleted but with
-    a better sum of weights than newly received ones ($\alpha_d^y <
-    \alpha_a^{x'}$). It forever discards such a message
-    $\alpha_a^{x'}$.
-  \item [Purge not followed by BEF:] Even assuming that every process
-    immediately removes stale control information $S(\alpha_d^y)
-    \implies d_b(\alpha_d^y) \rightarrow d_b(\delta_d)$, but received
-    $\alpha^{x'}_a$ earlier $d_b(\alpha^{x'}_a) \rightarrow
-    d_b(\alpha^y_d)$, it may never receive it again, hence staying
-    with an empty state or another message that did not follow its
-    shortest path to its best source.
-  \item [Purge then BEF:] Removing \emph{forever} all such stale
-    messages about deleted partitions would allow \processes to
-    propagate their best up-to-date partition again, eventually
-    reaching consistent partitioning together, as stated by
-    Theorem~\ref{theo:bef}.
+  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
+    \process may receive messages in such an order ($d_b(\alpha_d^1)
+    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
+    not forward messages required by other \processes
+    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
+    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
+    consistent partitioning.
+    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
+    %% $b$ precludes itself and subsequent \processes such as $c$ of
+    %% delivering the message from their respective best source
+    %% $a$. \Process $b$ received and delivered a message from a
+    %% partition that has since then been deleted but with a better sum
+    %% of weights than newly received ones ($\alpha_d^y <
+    %% \alpha_a^{x'}$). It forever discards such a message
+    %% $\alpha_a^{x'}$.
+  \item [Purge not followed by BEF:]
+    %% also transiting messages
+    Assuming that every process removes control information as soon as
+    they become stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
+    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
+    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
+    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
+    up-to-date messages propagation. However, even in such settings,
+    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
+    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a process
+    may never receive again, hence deliver and forward a message that
+    was received and discarded before ($\alpha_c^{y}$). When such a
+    message contains its best up-to-date partition, the \process never
+    ends up in its best partition. Therefore, \processes do not reach
+    consistent partitioning.
+  \item [Purge then BEF:] Assuming the eventual removal of stale
+    control information ,
+
+    nothing stops up-to-date control information to propagate, as in
+    Theorem~\ref{theo:bef}. Assuming that removal of stale control
+    information immediatly triggers a forwarding of best up-to-date
+    %% Removing \emph{forever} all such stale messages about
+    %% deleted partitions would allow \processes to propagate their best
+    %% up-to-date partition again, eventually reaching consistent
+    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
   \end{asparadesc}
@@
 
-\input{input/figproof.tex}
+%% \begin{figure}
+%%   \centering\input{input/figproofA.tex}
+%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
+%%       stop other $\alpha$ messages from reaching all \processes ($b$
+%%       and $c$) that require it along the shortest path. Consistent
+%%       partitioning requires eventual purging of stale messages (see
+%%       Figure~\ref{fig:proofB}).}
+%% \end{figure}
+
+One could guarantee consistent partitioning by always propagating the
+$\delta$ messages corresponding to the $\alpha$ messages it propagated
+before. In Figure~\ref{fig:problem}, it means that as soon as
+\Process~$b$ forwards $\alpha_a^2$, it assumes that its neighbors
+\Process~$c$ and \Process~$d$ may need the notification of removal
+$\delta_a$ if it exists. However, such a solution also implies that
+\processes generate traffic not only related to their current
+partition, but also related to partitions they belonged to in the
+past. This would prove overly expensive in dynamic systems where
+\processes join and leave the system, create and delete partitions, at
+any time.  Instead, we propose to use the delivery order at each
+\process to detect possible inconsistencies and solve them. Together,
+\processes eventually remove all stale control information (transiting
+messages and local states) of the system leaving room for propagation
+of messages about up-to-date partitions.
+
+%% \input{input/figproof.tex}
 
@@
 %% may be inconsistent without knowing it.
+
+\begin{figure}
+  \centering\input{input/figproofB.tex}
+  \caption{\label{fig:proofB}Stale $\alpha$ messages may
+      stop $\delta$ messages from reaching processes with the corresponding
+      partition. Consistent partitioning requires that all \processes propagate
+      $\delta$ messages as often as possible (I'); detect possible inconsistencies
+      when parents' $\alpha$ messages contradict history or state (III); notify
+      processes of possible inconsistencies (IV)}
+\end{figure}
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
   \input{input/algoascast.tex}

### 2021-09-06 input/proposal.tex
about proof

@@
 consistent partitioning when a \process can only create a new replica
-within the system. We highlight the issue when a process can also
+within the system. We highlight the issue when a \process can also
 destroy a replica, and provide a second algorithm that handles replica
@@
   A message $m$ conveys \underline{s}tale control information if the
-  process that broadcast $m$ later broadcast another message $m'$:
+  \process that broadcast $m$ later broadcast another message $m'$:
   $S(m) = \exists m': b_p(m) \rightarrow b_p(m')$.
@@
   prove that despite stale messages, the last delivery of every
-  process is the message that followed the shortest path to its
+  \process is the message that followed the shortest path to its
   closest source.
@@
     %% also transiting messages
-    Assuming that every process removes control information as soon as
-    they become stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
+    Assuming that every \process removes control information as soon as
+    it becomes stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
     \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
@@
     depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
-    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a process
+    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
     may never receive again, hence deliver and forward a message that
@@
     consistent partitioning.
-  \item [Purge then BEF:] Assuming the eventual removal of stale
-    control information ,
-
-    nothing stops up-to-date control information to propagate, as in
-    Theorem~\ref{theo:bef}. Assuming that removal of stale control
-    information immediatly triggers a forwarding of best up-to-date
+  \item [Purge then BEF:] Assuming the eventual and definitive removal
+    of stale messages at each \process, eventually every process only
+    delivers and forwards up-to-date messages, or no message at
+    all. Assuming that eventually, each removal triggers the
+    forwarding of best delivered messages, every \processes eventually
+    delivers and forwards the best up-to-date delivered
+    messages. \Processes reach consistent partitioning together.
     %% Removing \emph{forever} all such stale messages about
@@
 %% \end{figure}
+
+\TODO{The challenge is therefore about purging.}
 
@@
 
-\begin{figure}
-  \centering\input{input/figproofB.tex}
-  \caption{\label{fig:proofB}Stale $\alpha$ messages may
-      stop $\delta$ messages from reaching processes with the corresponding
-      partition. Consistent partitioning requires that all \processes propagate
-      $\delta$ messages as often as possible (I'); detect possible inconsistencies
-      when parents' $\alpha$ messages contradict history or state (III); notify
-      processes of possible inconsistencies (IV)}
-\end{figure}
-
 \begin{theorem}[Three-phase purge] % Propagations $+$ detection $\implies$ purge]
@@
 \end{theorem}
+
+\begin{figure}
+  \centering\input{input/figproofB.tex}
+  \caption{\label{fig:proofB}Stale $\alpha$ messages may
+      stop $\delta$ messages from reaching \processes with the corresponding
+      partition. Consistent partitioning requires that all \processes propagate
+      $\delta$ messages as often as possible (I'); detect possible inconsistencies
+      when parents' $\alpha$ messages contradict history or state (III); notify
+      \processes of possible inconsistencies (IV)}
+\end{figure}
 

### 2021-09-06 input/figproofB.tex
wip rw up to broadcast
cosmetic + number
first step in styling
meow
starting on three-phase purge

--- 2021-04-20 input/figproofB.tex
@@
-\begin{tikzpicture}[scale=0.87]
+\begin{tikzpicture}[scale=0.9]
 
@@
 
-  \newcommand\X{85pt}
-  \newcommand\Y{-50pt}
+  \newcommand\X{115pt}
+  \newcommand\Y{-60pt}
 
@@
   \newcommand\DEL{\delta}
+  \newcommand\DELDEL{\Delta}
 
   \draw[opacity=0] (-1.4*\X, 0) -- (2.4*\X, 0);
+
+  \draw[dotted] (-1.5*\X, 0pt) -- (-1.35*\X, 0pt); %% X ->
 
@@
   \draw[<->] (5pt - \X, 0.4*\Y) --
-  node[below, font=\small]{\textbf{I': propagation}}
+  node[below, font=\small, align=center]{\textbf{I: propagation}\\\textbf{of $\delta$ messages}}
   (-5pt, 0.4*\Y); %% I as well
@@
   \draw[->] (-\X + 5pt, 0)
-  node[below=-0.3em, below right, font=\scriptsize]{$\DEL_d \rightarrow$}
+  node[below=-0.3em, below right, font=\scriptsize]{$\DEL_X \rightarrow$}
   -- (0 - 5pt, 0)
-  node [below=-0.15em, below left, font=\tiny]{$\textcolor{\WRONG}{d \neq f}$}
+  node [below=-0.15em, below left, font=\tiny]{$\textcolor{\WRONG}{a \neq c}$}
   ; %% d - e
@@
   \draw[<->] (5pt , 0.4*\Y) --
-  node[below, font=\small]{\textbf{III: detection}}
+  node[below, font=\small, align=center]{\textbf{II: detection}}
   (-5pt + \X, 0.4*\Y); %% IV
@@
   \draw[->] (0 +5pt, 0)
-  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PH}{\ADD_h^{z'}} \rightarrow$}
+  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PY}{\ADD_Y^{y'}} \rightarrow$}
   --
   (\X -5pt, 0)
-  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_h \not\rightarrow \ADD_h^{z'}}$}
+  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_Y^{\vphantom{y'}} \not\rightarrow \ADD_Y^{y'}}$}
   ; %% e - f
@@
   \draw[<->] (5pt +\X , 0.4*\Y) --
-  node[below, font=\small]{\textbf{IV: propagation}}
+  node[below, font=\small, align=center]{\textbf{III: propagation}\\\textbf{of $\DELDEL$ messages}}
   (-5pt + 2*\X, 0.4*\Y); %% V
@@
 
-  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
-  \draw[fill=white] (0, 0) node[color=\PH]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{f}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (2*\X, 0) node[color=\PD]{$\bm{g}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[dotted] (0.5*\X, 1.25*\Y) -- (0.2*\X, 1.1*\Y); %% Y ->
+  \draw[dotted] (0.5*\X, 1.25*\Y) -- (0.8*\X, 1.1*\Y); %% Y ->
 
-  \draw (-\X, 5pt) node[above]{$\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
+  \draw[fill=white] (-1.5*\X, 0) node{$\bm{X}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
+  \draw[fill=white] (0, 0) node[color=\PY]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (\X, 0) node[color=\PX]{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (2*\X, 0) node[color=\PX]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0.5*\X, 1.25*\Y)node{$\bm{Y}$}+(-5pt, -5pt) rectangle +(5pt, 5pt);
+
+  \draw (-1.5*\X, 5pt) node[above]{$\textcolor{\PX}{\ADD_X} \rightarrow \DEL_X$};
+
+  \draw (-\X, 5pt) node[above, font=\tiny]{$\textcolor{\PX}{\ADD_X} \rightarrow \DEL_X$};
 
   \draw ( 0, 5pt) node[above, font=\footnotesize]{$
-    \xrightarrow[\textcolor{\PC}{\ADD_d^{\vphantom{z'}}}]{\mbox{\scriptsize{before}}}
-    \xrightarrow[\textcolor{\PH}{\ADD_h^{z\vphantom{'}}}]{\mbox{\scriptsize{last}}}
-    \xrightarrow[\DEL_h^{\vphantom{z'}} ]{\mbox{\scriptsize{expect}}}$};
+    \xrightarrow[\textcolor{\PX}{\ADD_X^{\vphantom{x'}}}]{\mbox{\tiny{before}}}
+    \xrightarrow[\textcolor{\PY}{\ADD_Y^{y\vphantom{'}}}]{\mbox{\tiny{last}}}
+    \xrightarrow[\DEL_Y^{\vphantom{y'}} ]{\mbox{\tiny{expect}}}$};
 
   \draw ( \X, 5pt) node[above, font=\footnotesize]{$
-    \xrightarrow[\textcolor{\PH}{\ADD_h^{\vphantom{y'}}} \rightarrow \DEL_h]{\mbox{\scriptsize{before}}}
-    \xrightarrow[\textcolor{\PC}{\ADD_d^{y'}}]{\mbox{\scriptsize{last}}}
-    \xrightarrow[\DEL_d^{\vphantom{z'}}?]{\mbox{\scriptsize{expect}}}$};
+    \xrightarrow[\textcolor{\PY}{\ADD_Y^{\vphantom{y'}}} \rightarrow
+      \DEL_Y^{\vphantom{y'}}]{\mbox{\tiny{before}}}
+    \xrightarrow[\textcolor{\PX}{\ADD_X^{x'}}]{\mbox{\tiny{last}}}
+    \xrightarrow[\DELDEL_X^{\vphantom{y'}}]{\mbox{\tiny{expect}}}$};
 
   \draw (2*\X, 5pt) node[above, font=\footnotesize]{$
-    \xrightarrow[\textcolor{\PC}{\ADD_d^{y''}}]{\mbox{\scriptsize{last}}}
-    \xrightarrow[\DEL_d^{\vphantom{y'}}?]{\mbox{\scriptsize{expect}}}$};
+    \xrightarrow[\textcolor{\PX}{\ADD_X^{x''}}]{\mbox{\tiny{last}}}
+    \xrightarrow[\DELDEL_X^{\vphantom{x'}}]{\mbox{\tiny{expect}}}$};
+
+  \draw (0.5*\X, 1.25*\Y+5pt) node[above] {$\textcolor{\PY}{\ADD_Y} \rightarrow \DEL_Y$};
 
@@
   \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
-  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below right, font=\scriptsize]{somewhere: $\textcolor{\PH}{\ADD_h} \rightarrow \DEL_h$};
+  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y);
 

### 2021-09-06 input/proposal.tex
starting on three-phase purge

@@
 
-\begin{theorem}[\label{theo:dcp}BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
+\begin{theorem}[\label{theo:dcp}BEF$^+$: BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
     \underline{D}ynamic \underline{c}onsistent
@@
 %
-When a \process can \texttt{Add} and \texttt{Del}ete its partition,
-consistent partitioning additionally requires
+When a \process can \texttt{Add} and \texttt{Del}ete its partition, to
+ensure consistent partitioning, best eventual forwarding (see
+Theorem~\ref{theo:bef}) additionally requires
 \begin{inparaenum}[(i)]
@@
     %% also transiting messages
-    Assuming that every \process removes control information as soon as
-    it becomes stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
+    Assuming that every \process removes control information as soon
+    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
     \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
@@
   \item [Purge then BEF:] Assuming the eventual and definitive removal
-    of stale messages at each \process, eventually every process only
+    of stale messages at each \process, eventually every \process only
     delivers and forwards up-to-date messages, or no message at
     all. Assuming that eventually, each removal triggers the
-    forwarding of best delivered messages, every \processes eventually
-    delivers and forwards the best up-to-date delivered
-    messages. \Processes reach consistent partitioning together.
+    forwarding of best delivered messages, every \process eventually
+    delivers and forwards the best up-to-date delivered messages.
     %% Removing \emph{forever} all such stale messages about
@@
   \end{asparadesc}
+  By using BEF along with purge of stale messages that triggers BEF,
+  \processes reach consistent partitioning together as in
+  Theorem~\ref{theo:bef}.
 \end{proof}
 
+%% Figure removed as it's kind of redundant with preceding figure that
+%% depicts the issue
 %% \begin{figure} 
@@
 
-\TODO{The challenge is therefore about purging.}
-
-One could guarantee consistent partitioning by always propagating the
-$\delta$ messages corresponding to the $\alpha$ messages it propagated
-before. In Figure~\ref{fig:problem}, it means that as soon as
-\Process~$b$ forwards $\alpha_a^2$, it assumes that its neighbors
-\Process~$c$ and \Process~$d$ may need the notification of removal
-$\delta_a$ if it exists. However, such a solution also implies that
-\processes generate traffic not only related to their current
-partition, but also related to partitions they belonged to in the
-past. This would prove overly expensive in dynamic systems where
+The main challenge consists in implementing a purging mechanism that
+ensures the \emph{eventual and definitive} removal of stale control
+information. One could guarantee consistent partitioning by always
+propagating the $\delta$ messages corresponding to the $\alpha$
+messages it propagated before. In Figure~\ref{fig:problem}, it means
+that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
+its neighbors \Process~$c$ and \Process~$d$ may need the notification
+of removal $\delta_a$ if it exists. However, such a solution also
+implies that \processes generate traffic not only related to their
+current partition, but also related to partitions they belonged to in
+the past. This would prove overly expensive in dynamic systems where
 \processes join and leave the system, create and delete partitions, at
 any time.  Instead, we propose to use the delivery order at each
-\process to detect possible inconsistencies and solve them. Together,
-\processes eventually remove all stale control information (transiting
-messages and local states) of the system leaving room for propagation
-of messages about up-to-date partitions.
+\process to detect possible inconsistencies and solve them.
+%% Together, \processes eventually remove all stale control information
+%% (transiting messages and local states) of the system leaving room for
+%% propagation of messages about up-to-date partitions.
 
@@
 
-\begin{theorem}[Three-phase purge] % Propagations $+$ detection $\implies$ purge]
+\begin{theorem}[\label{theo:threephase}Three-phase purge]
   Purging stale control information from its source to every \process
-  that may have delivered it last requires three
-  phases:
+  that may have delivered it last requires three phases:
   \begin{inparaenum}[(i)]
   \item propagation of delete notifications,
-  \item detection of possible blocking conditions, and
+  \item detection of possibly blocking conditions, and
   \item propagation of possibly deleted but blocked notifications.
@@
   \centering\input{input/figproofB.tex}
-  \caption{\label{fig:proofB}Stale $\alpha$ messages may
-      stop $\delta$ messages from reaching \processes with the corresponding
-      partition. Consistent partitioning requires that all \processes propagate
-      $\delta$ messages as often as possible (I'); detect possible inconsistencies
-      when parents' $\alpha$ messages contradict history or state (III); notify
-      \processes of possible inconsistencies (IV)}
+  \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
+    messages from reaching \processes with the corresponding
+    partition. Consistent partitioning requires that all \processes
+    propagate $\delta$ messages as often as possible (I); detect
+    possible inconsistencies when parents' $\alpha$ messages
+    contradict history or state (II); notify \processes of possible
+    inconsistencies (III).}
 \end{figure}
@@
   Figure~\ref{fig:proofB} depicts all possible cases that need
-  appropriate purging. A chain of \processes $[d, e, f, g]$ delivered
-  and forwarded a message $\alpha_d$. Some \processes may have
+  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
+  and forwarded a message $\alpha_a$. Some \processes may have
   delivered messages about other partitions before or after
-  $\alpha_d$.
+  $\alpha_a$.
   \begin{asparadesc}
-  \item [\processes with last $\alpha_d$:] \Processes such as
-    \Process~$d$ where the last and best partition is still $P_d$. By
-    propagating from \process to \process the corresponding $\delta_d$
-    message, these \processes purge $\alpha_d$.
-  \item [\processes with $\alpha_d^y \rightarrow \alpha_h^z$ with last
-    $\alpha_h^z$, for $\alpha_h^z < \alpha_d^y$:] \Processes such as
+  \item [\processes with last $\alpha_a$:] \Processes such as
+    \Process~$a$ where the last and best partition is still $P_a$. By
+    propagating from \process to \process the corresponding $\delta_a$
+    message, these \processes purge $\alpha_a$.
+  \item [\processes with $\alpha_a^y \rightarrow \alpha_e^z$ with last
+    $\alpha_e^z$, for $\alpha_e^z < \alpha_a^y$:] \Processes such as
     \Process~$e$ that do not directly suffer from the non-delivery of
-    $\delta_d$. They need to purge their own $P_h$ if need
-    be. Nonetheless, they deliver and forward $\alpha_h$ that at least
+    $\delta_a$. They need to purge their own $P_e$ if need
+    be. Nonetheless, they deliver and forward $\alpha_e$ that at least
     one following \process will receive.
-  \item [\processes with $\delta_h \rightarrow \alpha_d$:] \Processes
+  \item [\processes with $\delta_e \rightarrow \alpha_d$:] \Processes
     such as \Process~$f$ that do not belong to the preceding category,
-    for they already delivered $\delta_h$. Nevertheless, best eventual
-    forwarding guarantees that they receive $\alpha_h$, which
+    for they already delivered $\delta_e$. Nevertheless, best eventual
+    forwarding guarantees that they receive $\alpha_e$, which
     contradicts their history or state. In such a case, the detecting
-    \processes purge their own $\alpha_d$. The detecting \processes
+    \processes purge their own $\alpha_a$. The detecting \processes
     must also notify subsequent \processes that their current
@@
     \processes must purge their possibly stale state, for the sake of
-    consistency.  We note such a notification $\delta_d?$ to emphasize
+    consistency.  We note such a notification $\Delta_a$ to emphasize
     the uncertainty of a $\delta$ message.
-  \item [\processes with last $\alpha_d$ receiving $\delta_d?$ from
+  \item [\processes with last $\alpha_a$ receiving $\Delta_a$ from
     their parent:] \Processes such as \Process~$g$ that have
-    $\alpha_d$ but preceding delivered messages are not
+    $\alpha_a$ but preceding delivered messages are not
     important. Such \processes must trust detecting \processes by
-    delivering and forwarding $\delta_d?$. It is worth noting that
+    delivering and forwarding $\Delta_a$. It is worth noting that
     these messages are subject to all aforementioned blocking
@@
 \processes that forwarded the corresponding $\alpha$ message. Such a
-$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$
+$\delta_{s, c}^{\pi}$ message implements the uncertain $\Delta$
 message of Figure~\ref{fig:proofB}. It fulfils the double role of
@@
 improves, the propagation of $\alpha$ messages operates normally.
-Removing an edge between two \processes may invalidate the
-shortest path of one of involved \processes plus downstream
-\processes. As a side effect, removing an edge may also impair the
-propagation of a partition delete. To implement this behavior, \NAME
-uses its implementation of $\delta?$ messages. This prove costly but
-enables \NAME even in dynamic networks subject to physical
-partitioning.
+Removing an edge between two \processes may invalidate the shortest
+path of one of involved \processes plus downstream \processes. As a
+side effect, removing an edge may also impair the propagation of a
+partition delete. To implement this behavior, \NAME uses its
+implementation of $\Delta$ messages. This prove costly but enables
+\NAME even in dynamic networks subject to physical partitioning.
 

### 2021-09-06 input/experiments.tex
updated three-phase purge, small changes in implem, two column algo, smaller expe figs: 17 pages

@@
 
+%% \begin{figure*}
+%%   \begin{center}
+%%     \subfloat[Part A][\label{fig:complexity}Overhead of consistent partitioning
+%%       using \NAME]
+%%              {\includegraphics[width=0.5\columnwidth]{img/as_cast_complexity.eps}}
+%%              \hfill
+%%     \subfloat[Part B][\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.]
+%%              {\includegraphics[width=0.5\columnwidth]{img/as_cast_geant.eps}}
+%%   \end{center}
+%% \end{figure*}
+
 \begin{figure}
-  \centering\includegraphics[width=0.8\columnwidth]{img/as_cast_complexity.eps}
+  \centering\includegraphics[width=0.65\columnwidth]{img/as_cast_complexity.eps}
   \caption{\label{fig:complexity}Overhead of consistent partitioning
     using \NAME.}
+
   %% \caption{\label{fig:complexity}Cumulative average number of messages
@@
 \begin{figure}
-  \centering\includegraphics[width=0.8\columnwidth]{img/as_cast_geant.eps}
+  \centering\includegraphics[width=0.65\columnwidth]{img/as_cast_geant.eps}
   \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}

### 2021-09-06 input/figproofB.tex
updated three-phase purge, small changes in implem, two column algo, smaller expe figs: 17 pages

@@
-\begin{tikzpicture}[scale=0.9]
+\begin{tikzpicture}[scale=0.75]
 
@@
 
-  \newcommand\X{115pt}
+  \newcommand\X{120pt}
   \newcommand\Y{-60pt}
@@
   \draw[<->] (5pt , 0.4*\Y) --
-  node[below, font=\small, align=center]{\textbf{II: detection}}
+  node[below, font=\small, align=center]
+  {\textbf{II: detection}\\\textbf{of inconsistencies}}
   (-5pt + \X, 0.4*\Y); %% IV
@@
   \draw[fill=white] (2*\X, 0) node[color=\PX]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
-  \draw[fill=white] (0.5*\X, 1.25*\Y)node{$\bm{Y}$}+(-5pt, -5pt) rectangle +(5pt, 5pt);
+  \draw[fill=white] (0.5*\X, 1.25*\Y) node{$\bm{Y}$}+(-5pt, -5pt) rectangle +(5pt, 5pt);
 

### 2021-09-06 input/proposal.tex
updated three-phase purge, small changes in implem, two column algo, smaller expe figs: 17 pages

@@
   appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
-  and forwarded a message $\alpha_a$. Some \processes may have
+  and forwarded a message $\alpha_X$. Some \processes may have
   delivered messages about other partitions before or after
-  $\alpha_a$.
+  $\alpha_X$.
   \begin{asparadesc}
-  \item [\processes with last $\alpha_a$:] \Processes such as
-    \Process~$a$ where the last and best partition is still $P_a$. By
-    propagating from \process to \process the corresponding $\delta_a$
-    message, these \processes purge $\alpha_a$.
-  \item [\processes with $\alpha_a^y \rightarrow \alpha_e^z$ with last
-    $\alpha_e^z$, for $\alpha_e^z < \alpha_a^y$:] \Processes such as
-    \Process~$e$ that do not directly suffer from the non-delivery of
-    $\delta_a$. They need to purge their own $P_e$ if need
-    be. Nonetheless, they deliver and forward $\alpha_e$ that at least
+  \item [\processes with last $\alpha_X$:] \Processes such as
+    \Process~$a$ where the last and best partition is still $P_X$. By
+    propagating from \process to \process the corresponding $\delta_X$
+    message, these \processes purge $\alpha_X$.
+  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
+    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
+    \Process~$b$ that do not directly suffer from the non-delivery of
+    $\delta_X$. They need to purge their own $P_Y$ if need
+    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
     one following \process will receive.
-  \item [\processes with $\delta_e \rightarrow \alpha_d$:] \Processes
-    such as \Process~$f$ that do not belong to the preceding category,
-    for they already delivered $\delta_e$. Nevertheless, best eventual
-    forwarding guarantees that they receive $\alpha_e$, which
+  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
+    such as \Process~$c$ that do not belong to the preceding category,
+    for they already delivered $\delta_Y$. Nevertheless, best eventual
+    forwarding guarantees that they receive $\alpha_Y$, which
     contradicts their history or state. In such a case, the detecting
-    \processes purge their own $\alpha_a$. The detecting \processes
+    \processes purge their own $\alpha_X$. The detecting \processes
     must also notify subsequent \processes that their current
@@
     \processes must purge their possibly stale state, for the sake of
-    consistency.  We note such a notification $\Delta_a$ to emphasize
-    the uncertainty of a $\delta$ message.
-  \item [\processes with last $\alpha_a$ receiving $\Delta_a$ from
-    their parent:] \Processes such as \Process~$g$ that have
-    $\alpha_a$ but preceding delivered messages are not
+    consistency.  We note such a notification $\Delta_X$ to emphasize
+    their relative similarity to $\delta_X$ messages.
+    % the uncertainty of a $\delta$ message.
+  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
+    their parent:] \Processes such as \Process~$d$ that have
+    $\alpha_X$ but preceding delivered messages are not
     important. Such \processes must trust detecting \processes by
-    delivering and forwarding $\Delta_a$. It is worth noting that
+    delivering and forwarding $\Delta_X$. It is worth noting that
     these messages are subject to all aforementioned blocking
@@
 
-  Propagation~I' terminates: a \process does not deliver a $\delta$
-  message if it has already delivered it. Propagation~IV terminates: a
+  Propagation~I terminates: a \process does not deliver a $\delta$
+  message if it has already delivered it. Propagation~III terminates: a
   \process does not deliver a looping message.
@@
 
-\begin{algorithm}[h]
+\begin{algorithm}[h!]
   \input{input/algoascast.tex}
@@
 \end{inparaenum}
-This vector enables both Propagation~I and Propagation~I'.  Its size
-increases linearly with the number of sources that the \process has
-ever known, which is the number of \processes in the system
-$\mathcal{O}(V)$ in the worst case.
+% This vector enables the simplest Propagation~I and Propagation~I'.
+Its size increases linearly with the number of sources that the
+\process has ever known, which is the number of \processes in the
+system $\mathcal{O}(V)$ in the worst case.
 %% Unfortunately, \processes cannot
@@
 Figure~\ref{fig:proofB}. A detecting \process then propagates a
-$\delta$ message conveying the unique identifier $s$ and version $c$
+$\Delta$ message conveying the unique identifier $s$ and version $c$
 of the partition along with a path $\pi$ comprising the identity of
 \processes that forwarded the corresponding $\alpha$ message. Such a
-$\delta_{s, c}^{\pi}$ message implements the uncertain $\Delta$
-message of Figure~\ref{fig:proofB}. It fulfils the double role of
-removing stale control information without modifying the local counter
-of the source (since the partition may still exist), and removing
-loops to ensure termination (since \processes do not modify their
-local state to reflect such a delivery, messages piggyback
-monotonically such increasing control information).
+$\Delta_{s, c}^{\pi}$ fulfils the double role of removing stale
+control information without modifying the local counter of the source
+(since the partition may still exist), and removing loops to ensure
+termination (since \processes do not modify their local state to
+reflect such a delivery, messages piggyback monotonically such
+increasing control information).
 
-$\delta_{s, c}$ messages used in Propagation~I' are more efficient
-than $\delta_{s, c}^\pi$ messages used in Propagation~IV, both in
+$\delta_{s, c}$ messages used in Propagation~I are more efficient than
+$\Delta_{s, c}^\pi$ messages used in Propagation~III, both in
 propagation time and traffic. First, the former propagate using every
@@
 other: Paths tend to be smaller as the number of sources in the system
-increases. Bloom filters could introduce another trade-off by further
-decreasing the size of path data structures at the cost of premature
-stopped propagation that could impair consistent
-partitioning~\cite{whitaker2002forwarding}.
+increases.
+%% Bloom filters could introduce another trade-off by further
+%% decreasing the size of path data structures at the cost of premature
+%% stopped propagation that could impair consistent
+%% partitioning~\cite{whitaker2002forwarding}.
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[h!]
   \input{input/algoedges.tex}

### 2021-09-06 input/proposal.tex
wining space piece by piece

@@
 section describes the communication primitive called scoped broadcast,
-then discusses the properties that guarantee consistent partitioning
-in our context, and finally details our implementation \NAME and the
-analysis of its complexity.
+then discusses the properties that guarantee consistent partitioning,
+and finally details our implementation \NAME.
+% and the analysis of its complexity.
 
@@
 \nodes interconnected by communication links. \Processes involved in
-the management of content may crash but are not byzantine.  Finally,
-\processes can reliably communicate through asynchronous message
-passing to other known \processes called neighbors.  % A more formal
+the management of content may crash but are not byzantine.  \Processes
+can reliably communicate through asynchronous message passing to other
+known \processes called neighbors.  % A more formal
 %definition of our system is given below:
+We define scoped broadcast as a communication primitive that
+propagates a message around its broadcaster within an
+application-dependant scope.
 
@@
 
-We define scoped broadcast as a communication primitive that
-propagates a message around its broadcaster within an
-application-dependant scope:
-
 \begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
@@
 also highlights that epidemic propagation and scoped broadcast have
-well-aligned preoccupations. More precisely, it underlines the transitive relevance of
-messages, thus \processes can stop forwarding messages as soon as the
-corresponding predicate becomes unverified.
+well-aligned preoccupations. More precisely, it underlines the
+transitive relevance of messages, thus a \process can stop forwarding
+messages as soon as its predicate becomes unverified.
 %For instance, a \process
@@
 %
-We use \NAMEB to dynamically and efficiently modify the state of each
-\process depending on all partitions that exist in the system.
+We use \NAMEB to efficiently modify the state of each \process
+depending on the partitions that exist in the system.
 
@@
   \begin{asparadesc}
-  \item [\processes with last $\alpha_X$:] \Processes such as
-    \Process~$a$ where the last and best partition is still $P_X$. By
-    propagating from \process to \process the corresponding $\delta_X$
-    message, these \processes purge $\alpha_X$.
+  \item [\processes with last $\alpha_X$:] \Processes such as $a$
+    where the last and best partition is still $P_X$. By propagating
+    from \process to \process the corresponding $\delta_X$ message,
+    these \processes purge $\alpha_X$.
   \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
@@
     consistency.  We note such a notification $\Delta_X$ to emphasize
-    their relative similarity to $\delta_X$ messages.
+    their proximity to $\delta_X$ messages.
     % the uncertainty of a $\delta$ message.
@@
   \processes eventually purge stale $\alpha$ messages from the system,
-  leaving room for Propagation~I.
+  leaving room for best eventual forwarding of up-to-date messages.
   %
@@
   \input{input/algoascast.tex}
-  \caption{\label{algo:ascast}\NAME at \Process~$p$ in static networks.}
+  \caption{\label{algo:ascast}\NAME at \Process~$p$ in dynamic networks.}
 \end{algorithm}
@@
 
-\begin{algorithm}[h!]
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
-\end{algorithm}
+%% \begin{algorithm}[h!]
+%%   \input{input/algoedges.tex}
+%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
+%% \end{algorithm}
 
-Algorithm~\ref{algo:edges} extends \NAME to enable dynamic consistent
-partitioning in dynamic networks where \processes can join or leave
-the system without notification. We consider that removing a \process
-is equivalent to removing all its edges, and adding a \process is
-equivalent to add as many edges as necessary.
-
-Adding an edge between two \processes may only improve the shortest
-path of one of these \processes. Therefore, it triggers a competition
-between the two \processes only. If one or the other \process
-improves, the propagation of $\alpha$ messages operates normally.
-Removing an edge between two \processes may invalidate the shortest
-path of one of involved \processes plus downstream \processes. As a
-side effect, removing an edge may also impair the propagation of a
-partition delete. To implement this behavior, \NAME uses its
-implementation of $\Delta$ messages. This prove costly but enables
-\NAME even in dynamic networks subject to physical partitioning.
+Algorithm~\ref{algo:ascast} also enables dynamic consistent
+partitioning in dynamic networks where \processes can join, leave, or
+crash at any time. Removing a \process is equivalent to removing all
+its edges, and adding a \process is equivalent to add as many edges as
+necessary.  Adding an edge between two \processes may only improve the
+shortest path of one of these \processes. Therefore, it triggers a
+competition between the two \processes only. If one or the other
+\process improves, the propagation of $\alpha$ messages operates
+normally.  Removing an edge between two \processes may invalidate the
+shortest path of one of involved \processes plus downstream
+\processes. As a side effect, removing an edge may also impair the
+propagation of a partition delete. To implement this behavior, \NAME
+uses its implementation of $\Delta$ messages. This prove costly but
+enables \NAME even in dynamic networks subject to physical
+partitioning.
 

### 2021-09-06 input/experiments.tex
keywords

@@
 propagate their partition. It is worth noting that this delete
-operation involves concurrency: removals continue to propagate while
-the competition is already partially triggered and propagating.
+operation involves concurrency: removals still propagate while
+the competition has started. %%is already partially triggered and propagating.
 
@@
 do not generate traffic anymore. Being reactive, \NAME has no overhead
-when there is no operation in the system. In other words, \NAME's
-overhead actually depends on its usage.
+when there is no operation in the system. \NAME's overhead actually
+depends on its usage.
 

### 2021-09-07 input/conclusion.tex
wining space piece by piece
mostly about the implementation

@@
 As future work, we plan on extending the logical partitioning protocol
-to enable lazy retrieval of partitions. Indeed, using \NAME, every
-\process partakes in the propagation of indexes of content and
-replicas. We would like to leverage the hierarchical properties of
+to enable lazy retrieval of partitions \TODO{when a large number of
+  objects is involved}. Indeed, using \NAME, every \process partakes
+in the propagation of indexes \TODO{which raises scalability
+  issues}. We would like to leverage the hierarchical properties of
 interconnected autonomous systems to limit the propagation of such
 indexes only to interested systems.
+
 %

### 2021-09-07 input/proposal.tex
mostly about the implementation

@@
 
-% \vfill
-
-% \TODO{spacing.}
-
-% \newpage
-
 \subsection{Implementation and complexity}
@@
 that implement three-phase purge and best eventual forwarding to
-enable dynamic consistent partitioning.
-
-%% Similarly to Algorithm~\ref{algo:add}, local operations \texttt{Add}
-%% and \texttt{Del} generate messages that the initiating \process treats
-%% identically to receipts of messages from remote \processes.
-
-%% \begin{inparaenum}[(i)]
-%% \item \label{algo:most} most of the time, it propagates $\alpha$'s and
-%%   $\delta$'s when the partitions allow it;
-%% \item \label{algo:sometimes} sometimes, it detects possible
-%%   inconsistent partitioning and
-%% \item \label{algo:solves}solves it using propagation trees (as opposed
-%%   to propagation graphs);
-%% \item \label{algo:competition} when required, it triggers competitions
-%%   among neighboring partitions.
-%% \end{inparaenum}
-%% While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
-%% stale notifications, (\ref{algo:competition}) tackle the eventual
-%% delivery of the best up-to-date partitions.
+enable dynamic consistent partitioning. For the sake of simplicity, it
+does not handle multiple sessions and associated optimisation such as
+data structure sharing and message packing.
 
@@
 
-To implement the removal of stale messages as stated in
-Definition~\ref{def:lwo}, each \process maintains a vector of versions
-that associates the respective known local counter of each known
-source, or has-been source. Each message $m$ carries its source $s$
-along with its version $c$ that we subscript $m_{s, c}$.  Each
-\process delivers and forwards
+As stated in Theorem~\ref{theo:dcp}, every \process must purge stale
+messages.  To identify staleness, each \process maintains a vector of
+versions that associates the respective known local counter of each
+known source, or has-been source. Its size increases linearly with the
+number of sources that the \process has ever known, which is the
+number of \processes in the system $\mathcal{O}(V)$ in the worst case.
+Nevertheless, following the principles of scoped broadcast, we expect
+that every \process only acknowledges a small subset of sources.
+Using such a vector, every message $m$ carries its source $s$ along
+with its version $c$ that we subscript $m_{s, c}$.  Each \process
+delivers and forwards
 \begin{inparaenum}[(i)]
@@
 \end{inparaenum}
-% This vector enables the simplest Propagation~I and Propagation~I'.
-Its size increases linearly with the number of sources that the
-\process has ever known, which is the number of \processes in the
-system $\mathcal{O}(V)$ in the worst case.
-%% Unfortunately, \processes cannot
-%% remove any entry from this vector without running a costly distributed
-%% consensus protocol to ensure that no \process can mistake an old but
-%% removed entry for a new one.
-Nevertheless, following the principles of scoped broadcast, we expect
-that every \process only acknowledges a small subset of sources.
+This vector of versions constitutes a summary of local deliveries. It
+allows a \process to detect inconsistencies in message delivery: the
+parent delivered a stale message (see Line~\ref{line:ascast_version}),
+or the parent delivered a worse message (see
+Line~\ref{line:detectA}). This may happen in stage II of
+Figure~\ref{fig:proofB} between $b$ and $c$.
 
-This vector of versions constitutes a summary of deliveries. \NAME
-uses it to detect possible inconsistent partitioning as depicted in
-Figure~\ref{fig:proofB}. A detecting \process then propagates a
-$\Delta$ message conveying the unique identifier $s$ and version $c$
-of the partition along with a path $\pi$ comprising the identity of
-\processes that forwarded the corresponding $\alpha$ message. Such a
-$\Delta_{s, c}^{\pi}$ fulfils the double role of removing stale
-control information without modifying the local counter of the source
-(since the partition may still exist), and removing loops to ensure
-termination (since \processes do not modify their local state to
-reflect such a delivery, messages piggyback monotonically such
-increasing control information).
-
-$\delta_{s, c}$ messages used in Propagation~I are more efficient than
-$\Delta_{s, c}^\pi$ messages used in Propagation~III, both in
-propagation time and traffic. First, the former propagate using every
-communication link available in the partition, while the latter
-propagate following the dissemination tree of the corresponding
-$\alpha$ to purge. Second, the former only piggyback source and
-counter while the latter piggyback the path taken by the corresponding
-$\alpha$ to purge.  In the worst case, a path includes every \process
-in the system but converges to the average diameter of
-partitions. Nevertheless, message paths and \NAME synergyze with each
-other: Paths tend to be smaller as the number of sources in the system
-increases.
-%% Bloom filters could introduce another trade-off by further
-%% decreasing the size of path data structures at the cost of premature
-%% stopped propagation that could impair consistent
-%% partitioning~\cite{whitaker2002forwarding}.
+A \process ($c$) detecting an inconsistency disseminates a $\Delta$
+message. Such a $\Delta$ must not modify any vector of versions since
+the partition of the corresponding $\alpha$ may still exist.
+Therefore, it additionally includes and maintains a path $\pi$
+initialized to $\alpha$'s one. Such a $\Delta_{s, c}^{\pi}$
+transitively tracks and removes $\alpha$ messages that were forwarded
+by the detecting \process. The path $\pi$ also enables a quick stop of
+looping messages and in turns ensures termination. However, carrying
+paths in messages is costly. In the worst case, a message piggybacks
+the identity of all \processes in the system. Fortunately, message
+paths and \NAME synergyze well with each other, for paths tend to be
+smaller as the number of sources in the system increases. Contrarily
+to $\alpha$ and $\Delta$ messages, $\delta_{s, c}$ messages do not
+carry a path. They
+\begin{inparaenum}[(i)]
+\item solely rely on versions to operate, and
+\item use the whole dissemination graph to propagate in the system, as
+  opposed to $\Delta$ that must follow the dissemination tree of the
+  corresponding $\alpha$.
+\end{inparaenum}
 
@@
 also the retrieval of the best up-to-date partitions.  In that regard,
-both kinds of $\delta$ messages have dual use: since they already
-reach the borders of their partition when they remove stale control
-information, they also trigger a competition when reaching such
-bordering \processes (see Line~\ref{line:ascast_compete}). This simply
-consists in sending the current partition through the communication
-link from which the \process received the $\delta$. Upon receipt of
-this answer, \processes act normally by propagating their changes when
-they improve.
+both $\delta$ and $\Delta$ messages have dual use: since they already
+reach the borders of their partition by design, they also trigger a
+competition when reaching such bordering \processes (see
+Line~\ref{line:ascast_compete}).
+%% This simply consists in sending the
+%% current partition through the communication link from which the
+%% \process received the $\delta$. Upon receipt of this answer,
+%% \processes act normally by propagating their changes when they
+%% improve.
 
-\NAME guarantees dynamic consistent partitioning by making extensive
-use of \process-to-\process communications. It requires
-\begin{inparaenum}[(i)]
-\item purging stale control information, hence propagating $\delta$
-  messages; and
-\item retrieving the closest source, hence propagating $\alpha$
-  messages.
-\end{inparaenum}
+%% \NAME guarantees dynamic consistent partitioning by making extensive
+%% use of \process-to-\process communications. It requires
+%% \begin{inparaenum}[(i)]
+%% \item purging stale control information, hence propagating $\delta$
+%%   messages; and
+%% \item retrieving the closest source, hence propagating $\alpha$
+%%   messages.
+%% \end{inparaenum}
 In terms of number of messages, in the average case, a \process $i$

### 2021-09-07 input/conclusion.tex
wining space

--- 2021-09-02 input/conclusion.tex
@@
 As future work, we plan on extending the logical partitioning protocol
-to enable lazy retrieval of partitions. Indeed, using \NAME, every
-\process partakes in the propagation of indexes of content and
-replicas. We would like to leverage the hierarchical properties of
+to enable lazy retrieval of partitions when a large number of
+\TODO{objects} is involved. Indeed, using \NAME, every \process
+partakes in the propagation of indexes which raises scalability
+issues. We would like to leverage the hierarchical properties of
 interconnected autonomous systems to limit the propagation of such
 indexes only to interested systems.
+
 %

### 2021-09-07 input/experiments.tex
wining space

@@
 
+\begin{figure}
+  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_complexity.eps}
+  \caption{\label{fig:complexity}Overhead of consistent partitioning
+    using \NAME.}
+
+  %% \caption{\label{fig:complexity}Cumulative average number of messages
+  %%   per process in a network comprising 10k processes; along with the
+  %%   duration before reaching consistent partitioning after adding or
+  %%   removing a partition, totaling 100 new partition then removed.}
+\end{figure}
+
 \item [Results:]
@@
 %% \end{figure*}
-
-\begin{figure}
-  \centering\includegraphics[width=0.65\columnwidth]{img/as_cast_complexity.eps}
-  \caption{\label{fig:complexity}Overhead of consistent partitioning
-    using \NAME.}
-
-  %% \caption{\label{fig:complexity}Cumulative average number of messages
-  %%   per process in a network comprising 10k processes; along with the
-  %%   duration before reaching consistent partitioning after adding or
-  %%   removing a partition, totaling 100 new partition then removed.}
-\end{figure}
 
@@
 \begin{figure}
-  \centering\includegraphics[width=0.65\columnwidth]{img/as_cast_geant.eps}
+  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_geant.eps}
   \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
@@
 experiment involving one source for two clusters, it generates
-traffic. After a $200$ milliseconds delay corresponding to the link latency, the
-cut off cluster starts to communicate $\alpha$ messages
+traffic. After a $200$ milliseconds delay corresponding to the link
+latency, the cut off cluster starts to communicate $\alpha$ messages
 again. Eventually, all \processes belong to the same
@@
 cluster, the new link does not trigger noticeable traffic, for
-\processes already know their closest source located in their
-respective cluster.
+\processes already know their closest source located in their cluster.
 

### 2021-09-07 input/proposal.tex
wining space

@@
 sending ($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
-r_q(m')$). Both \Process~$a$ and \Process~$d$ add then delete their
-partition concurrently. \Process~$c$ receives, delivers, and forwards
-$\alpha_d^3$ followed by $\delta_d$. In the meantime, \Process~$b$
-receives, delivers, and forwards $\alpha_a^2$. In
-Figure~\ref{fig:problemC}, both \Process~$c$ and \Process~$d$ deliver
-the message about Partition $P_a$, for they did not have any known
-partition at receipt time. On the contrary, \Process~$b$ delivers
-$\alpha_d^1$, for it improves its distance to a known
-source. \Process~$b$ then blocks \Process~$a$'s removal notification
-$\delta_a$. It never reaches \Process~$c$ nor \Process~$d$. Also,
-\Process~$c$ does not deliver $\alpha_d$ and $\delta_d$ since it
-already delivered it. The system converges to an inconsistent state
-where some \processes assume they belong to a partition while it does
-not exist anymore. Naive propagation of $\alpha$ and $\delta$ messages
-is insufficient to guarantee consistent partitioning when any \process
-can add or delete its partition at any time. \Processes need to
-exploit their local knowledge gathered over message receipts to allow
-up-to-date messages to propagate to relevant \processes.
+r_q(m')$). Both $a$ and $d$ add then delete their partition
+concurrently. \Process~$c$ receives, delivers, and forwards
+$\alpha_d^3$ followed by $\delta_d$. In the meantime, $b$ receives,
+delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
+both $c$ and $d$ deliver the message about Partition $P_a$, for they
+did not have any known partition at receipt time. On the contrary, $b$
+delivers $\alpha_d^1$, for it improves its distance to a known
+source. \Process~$b$ then blocks $a$'s removal notification
+$\delta_a$. It never reaches $c$ nor $d$. Also, $c$ does not deliver
+$\alpha_d$ and $\delta_d$ since it already delivered it. The system
+converges to an inconsistent state where some \processes assume they
+belong to a partition while it does not exist anymore.
+
+%% Naive propagation of $\alpha$ and $\delta$ messages
+%% is insufficient to guarantee consistent partitioning when any \process
+%% can add or delete its partition at any time. \Processes need to
+%% exploit their local knowledge gathered over message receipts to allow
+%% up-to-date messages to propagate to relevant \processes.
 
@@
   \end{asparadesc}
-  By using BEF along with purge of stale messages that triggers BEF,
-  \processes reach consistent partitioning together as in
-  Theorem~\ref{theo:bef}.
+  Using BEF$^+$, \processes reach consistent partitioning together as
+  in Theorem~\ref{theo:bef}.
 \end{proof}
@@
 initialized to $\alpha$'s one. Such a $\Delta_{s, c}^{\pi}$
-transitively tracks and removes $\alpha$ messages that were forwarded
+transitively tracks and purges $\alpha$ messages that were forwarded
 by the detecting \process. The path $\pi$ also enables a quick stop of
@@
 to $\alpha$ and $\Delta$ messages, $\delta_{s, c}$ messages do not
-carry a path. They
+carry a path, and are therefore more efficient. They
 \begin{inparaenum}[(i)]
@@
 %% improve.
+
+Algorithm~\ref{algo:ascast} also enables dynamic consistent
+partitioning in dynamic networks where \processes can join, leave, or
+crash at any time. Removing a \process is equivalent to removing all
+its edges, and adding a \process is equivalent to add as many edges as
+necessary.  Adding an edge between two \processes may only improve the
+shortest path of one of these \processes. Therefore, it triggers a
+competition between the two \processes only. If one or the other
+\process improves, the propagation of $\alpha$ messages operates
+normally.  Removing an edge between two \processes may invalidate the
+shortest path of one of involved \processes plus downstream
+\processes. As a side effect, removing an edge may also impair the
+propagation of a partition delete. To implement this behavior, \NAME
+uses its implementation of $\Delta$ messages. This prove costly but
+enables \NAME even in dynamic networks subject to physical
+partitioning.
 
@@
 %% corresponding partition creation.
-
 %% \begin{algorithm}[h!]
@@
 %% \end{algorithm}
-
-Algorithm~\ref{algo:ascast} also enables dynamic consistent
-partitioning in dynamic networks where \processes can join, leave, or
-crash at any time. Removing a \process is equivalent to removing all
-its edges, and adding a \process is equivalent to add as many edges as
-necessary.  Adding an edge between two \processes may only improve the
-shortest path of one of these \processes. Therefore, it triggers a
-competition between the two \processes only. If one or the other
-\process improves, the propagation of $\alpha$ messages operates
-normally.  Removing an edge between two \processes may invalidate the
-shortest path of one of involved \processes plus downstream
-\processes. As a side effect, removing an edge may also impair the
-propagation of a partition delete. To implement this behavior, \NAME
-uses its implementation of $\Delta$ messages. This prove costly but
-enables \NAME even in dynamic networks subject to physical
-partitioning.
-
 Next Section provides the details of our simulations that assess the

### 2021-09-07 input/related_work.tex
wining space

@@
 location.  Before downloading any content, a \node asks for its
-location using its key. After a series of round-trips between DHT
-servers possibly distant from each other, the \node gets a list of
-available replicas. Contrarily to \NAME, such services do not ensure
-to include the closest replica.
+location using its key. After a series of round-trips between possibly
+distant DHT servers, the \node gets a list of available
+replicas. Contrarily to \NAME, such services do not ensure to include
+the closest replica.
 
@@
 \item [Scoped flooding:]
-
-Some state-of-the-art approaches confine the dissemination of messages
-to interested \processes too.
+  Some approaches also confine the dissemination of messages.
+  % to interested \processes too.
 % \item [Membership protocols:]
@@
 On the opposite, \NAME quickly informs each \process of its closest
-replica even in large networks; and when the system becomes quiescent,
-\NAME has no overhead.
+replica even in large networks; % when the system is quiescent,
+and has no overhead when the system is quiescent.
 

### 2021-09-07 input/conclusion.tex
cheating on biblio + changes here and there to get to 16 pages

--- 2021-09-02 input/conclusion.tex
@@
 
-As future work, we plan on extending the logical partitioning protocol
-to enable lazy retrieval of partitions. Indeed, using \NAME, every
-\process partakes in the propagation of indexes of content and
-replicas. We would like to leverage the hierarchical properties of
-interconnected autonomous systems to limit the propagation of such
-indexes only to interested systems.
+As future work, we plan to enable lazy retrieval of partitions when a
+large number of \TODO{objects} is involved. Indeed, using \NAME, every
+\process partakes in the propagation of all indexes which raises
+scalability issues. We would like to leverage the hierarchical
+properties of
+% interconnected
+autonomous systems to limit the
+propagation of such indexes only to interested systems.
+
 %

### 2021-09-07 input/experiments.tex
cheating on biblio + changes here and there to get to 16 pages
minors

@@
   \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_complexity.eps}
-  \caption{\label{fig:complexity}Overhead of consistent partitioning
+  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
     using \NAME.}
@@
   \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_geant.eps}
-  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
+  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
 \end{figure}
@@
 
-Next Section reviews state-of-the-art approaches for content indexing
-in geo-distributed infrastructures and explains their shortcomings.
+%% Next Section reviews state-of-the-art approaches for content indexing
+%% in geo-distributed infrastructures and explains their shortcomings.
 

### 2021-09-07 input/proposal.tex
minors

@@
 \begin{theorem}[\label{theo:threephase}Three-phase purge]
-  Purging stale control information from its source to every \process
-  that may have delivered it last requires three phases:
+  The following three phases are sufficient to eventually purge the
+  system from stale control information:
   \begin{inparaenum}[(i)]

### 2021-09-07 input/related_work.tex
cheating on biblio + changes here and there to get to 16 pages
minors

@@
 T-Man~\cite{t-man} make \processes converge to a specific network
-topology depending on targeted properties. They periodically
-communicate with their neighbors to compare their state. Following
-this exchange, they add and remove communication links to other
-\processes. Over exchanges, they converge towards a topology ensuring
-the targeted properties.  While at first glance membership protocols
-and \NAME could share common preoccupations, \NAME does not aim at
-building any topology and never modifies neighbors of \processes.
+topology depending on targeted properties. Following periodic
+exchanges, they add and remove communication links to other \processes
+to converge towards a topology ensuring the targeted properties.
+While membership protocols and \NAME share common preoccupations,
+\NAME does not aim at building any topology and never modifies
+neighbors of \processes.
 

### 2021-09-07 input/proposal.tex
wip on proof

@@
 
-\begin{theorem}[\label{theo:threephase}Three-phase purge]
+\begin{theorem}[\label{theo:threephase}\TODO{Three-phase purge}]
   The following three phases are sufficient to eventually purge the
@@
   delivered messages about other partitions before or after
-  $\alpha_X$.
+  $\alpha_X$. \Processes such as $a$ and $d$ have delivered unrelated
+  messages, but their last message is about $P_X$: $d_a(\_)
+  \rightarrow \ldots \rightarrow d_a(\alpha_X)$; \Processes such as $b$
+  and $c$ delivered messages about $P_X$ and $P_Y$ in different order;
+  For \processes such as $b$, the last delivery is $\alpha_Y$:
+  $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X) \rightarrow
+  \ldots \rightarrow d_b(\alpha_Y)$; For \processes such as $c$, the
+  last delivery is a stale $\alpha_X$, but they delivered the addition
+  and removal of $P_Y$: $d_c(\_) \rightarrow \ldots \rightarrow
+  d_c(\alpha_Y) \rightarrow \ldots \rightarrow d_c(\delta_Y)
+  \rightarrow \ldots \rightarrow d_c(\alpha_X)$.
+
   \begin{asparadesc}
-  \item [\processes with last $\alpha_X$:] \Processes such as $a$
-    where the last and best partition is still $P_X$. By propagating
+  \item [\TODO{source is type $a$}]
+  \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] By propagating
     from \process to \process the corresponding $\delta_X$ message,
     these \processes purge $\alpha_X$.
+  \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
+    latter does not target its current partition.
+  \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
+    that $[a, b, c, d]$ is solved and that it does not require to
+    purge $P_Y$.}
+  \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
+  \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
+    it detects $b$ is its parent, and possibly blocked any delta with
+    its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
+    sure, $\Delta$
+
   \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last

### 2021-09-07 input/related_work.tex
wip on proof

@@
 
-\noindent Distributing this index among \processes circumvents these
-issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
-locality issues where \processes
+\noindent \TODO{CDN in this category?=>} Distributing this index among
+\processes circumvents these issues~\cite{voronet, ipfs, mdht,
+  squirrel, coin_19}, but still raises locality issues where
+\processes
 \begin{inparaenum}[(i)]

### 2021-09-08 input/proposal.tex
wip

--- 2021-09-07 input/proposal.tex
@@
 \begin{proof}
-  Figure~\ref{fig:proofB} depicts all possible cases that need
-  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
-  and forwarded a message $\alpha_X$. Some \processes may have
-  delivered messages about other partitions before or after
-  $\alpha_X$.
-  \begin{asparadesc}
-  \item [\processes with last $\alpha_X$:] \Processes such as $a$
-    where the last and best partition is still $P_X$. By propagating
-    from \process to \process the corresponding $\delta_X$ message,
-    these \processes purge $\alpha_X$.
-  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
-    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
-    \Process~$b$ that do not directly suffer from the non-delivery of
-    $\delta_X$. They need to purge their own $P_Y$ if need
-    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
-    one following \process will receive.
-  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
-    such as \Process~$c$ that do not belong to the preceding category,
-    for they already delivered $\delta_Y$. Nevertheless, best eventual
-    forwarding guarantees that they receive $\alpha_Y$, which
-    contradicts their history or state. In such a case, the detecting
-    \processes purge their own $\alpha_X$. The detecting \processes
-    must also notify subsequent \processes that their current
-    partition \emph{may be} deleted. Indeed their parent may have
-    blocked the corresponding $\delta$ messages and subsequent
-    \processes must purge their possibly stale state, for the sake of
-    consistency.  We note such a notification $\Delta_X$ to emphasize
-    their proximity to $\delta_X$ messages.
-    % the uncertainty of a $\delta$ message.
-  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
-    their parent:] \Processes such as \Process~$d$ that have
-    $\alpha_X$ but preceding delivered messages are not
-    important. Such \processes must trust detecting \processes by
-    delivering and forwarding $\Delta_X$. It is worth noting that
-    these messages are subject to all aforementioned blocking
-    conditions, but are also solved by aforementioned mechanisms.
-  \end{asparadesc}
+  We must prove that every \process that delivered a stale $\alpha_X$
+  eventually
+  \begin{inparaenum}[(i)]
+  \item delivers a better $\alpha_Y$, or 
+  \item delivers a removal notification of $\alpha_X$.
+  \end{inparaenum}
+  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
+  involving concurrent operations:
 
-  Propagation~I terminates: a \process does not deliver a $\delta$
-  message if it has already delivered it. Propagation~III terminates: a
-  \process does not deliver a looping message.
+  If every \process (such as $a$) starting from the source delivers
+  and forwards a removal notification $\delta_X$ when their last
+  delivery is $\alpha_X$, then every such \process eventually delivers
+  the removal notification $\delta_X$ except \processes (such as $b$)
+  that delivered $\alpha_X$ from a \process that delivered a message
+  from another partition $\alpha_Y$ since then.
+
+  These exceptions eventually receive and deliver $\alpha_Y$ since
+  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
+  they already received and deliver the removal notification of $P_Y$
+  (such as $c$). These \processes may never receive hence deliver
+  $\delta_X$, and may never receive hence deliver a better message
+  than $\alpha_X$. They need an additional mechanism to eventually
+  purge $\alpha_X$ that cannot rely on the eventual purging of $P_Y$
+  to avoid deadlocks.
+
+  Assuming that every \process keeps an history of its past
+  deliveries, \processes (such as $c$) can detect the inconsistency,
+  since they receive from their parent an already deleted partition
+  $P_Y$. This notification means that the parent discards any
+  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
+  $\delta_X$ exists, it discards it. To ensure the purge of stale
+  messages, a detecting \process must assume the worst case that such
+  $\delta_X$ exists, and send another kind of message, noted $\Delta$
+  that notify the possible removal of $P_X$. Children \processes that
+  still have $P_X$ as last delivery must trust the detecting \process
+  and remove the possibly stale control information about $P_X$.
+
+  %% Some \processes may have delivered messages about other partitions
+  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
+  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
+  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
+  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
+  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
+  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
+  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
+  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
+  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
+  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
+  %% the chain: $d$ is a child of \processes that delivered messages
+  %% about $P_Y$.
+
+  %% \begin{asparadesc}
+  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
+  %%   like $a$.  By propagating from \process to \process the
+  %%   corresponding $\delta_X$ message, these \processes purge
+  %%   $\alpha_X$.
+  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
+  %%   latter does not target its current partition.
+  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
+  %%   that $[a, b, c, d]$ is solved and that it does not require to
+  %%   purge $P_Y$.}
+  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
+  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
+  %%   it detects $b$ is its parent, and possibly blocked any delta with
+  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
+  %%   sure, $\Delta$
+
+  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
+  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
+  %%   \Process~$b$ that do not directly suffer from the non-delivery of
+  %%   $\delta_X$. They need to purge their own $P_Y$ if need
+  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
+  %%   one following \process will receive.
+  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
+  %%   such as \Process~$c$ that do not belong to the preceding category,
+  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
+  %%   forwarding guarantees that they receive $\alpha_Y$, which
+  %%   contradicts their history or state. In such a case, the detecting
+  %%   \processes purge their own $\alpha_X$. The detecting \processes
+  %%   must also notify subsequent \processes that their current
+  %%   partition \emph{may be} deleted. Indeed their parent may have
+  %%   blocked the corresponding $\delta$ messages and subsequent
+  %%   \processes must purge their possibly stale state, for the sake of
+  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
+  %%   their proximity to $\delta_X$ messages.
+  %%   % the uncertainty of a $\delta$ message.
+  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
+  %%   their parent:] \Processes such as \Process~$d$ that have
+  %%   $\alpha_X$ but preceding delivered messages are not
+  %%   important. Such \processes must trust detecting \processes by
+  %%   delivering and forwarding $\Delta_X$. It is worth noting that
+  %%   these messages are subject to all aforementioned blocking
+  %%   conditions, but are also solved by aforementioned mechanisms.
+  %% \end{asparadesc}
+
+  %% Propagation~I terminates: a \process does not deliver a $\delta$
+  %% message if it has already delivered it. Propagation~III terminates: a
+  %% \process does not deliver a looping message.
+
   % ; and since \processes forward the messages they deliver, upstream

### 2021-09-08 input/proposal.tex
three phase purge

@@
 
-\begin{theorem}[\label{theo:threephase}\TODO{Three-phase purge}]
+\begin{theorem}[\label{theo:threephase}Three-phase purge]
   The following three phases are sufficient to eventually purge the
@@
   $\alpha_Y$ is better than $\alpha_X$ through this path, except if
-  they already received and deliver the removal notification of $P_Y$
-  (such as $c$). These \processes may never receive hence deliver
-  $\delta_X$, and may never receive hence deliver a better message
-  than $\alpha_X$. They need an additional mechanism to eventually
-  purge $\alpha_X$ that cannot rely on the eventual purging of $P_Y$
-  to avoid deadlocks.
+  they already received and delivered the removal notification of
+  $P_Y$ (such as $c$). These \processes may never receive hence
+  deliver $\delta_X$, and may never receive hence deliver a better
+  message than $\alpha_X$. They need an additional mechanism to
+  eventually purge $\alpha_X$ that cannot rely on the eventual purging
+  of $P_Y$ at \processes like $b$, to avoid deadlocks.
 
@@
   messages, a detecting \process must assume the worst case that such
-  $\delta_X$ exists, and send another kind of message, noted $\Delta$
-  that notify the possible removal of $P_X$. Children \processes that
-  still have $P_X$ as last delivery must trust the detecting \process
-  and remove the possibly stale control information about $P_X$.
+  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
+  that notify the possible removal of $P_X$.
+
+  A \process (such as $d$) whose last delivery is $\alpha_X$, but
+  whose parent is neither inconsistent (like $b$) nor receiving
+  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
+  \process, either directly or transitively, for such a child \process
+  ($d$) trusts the possible removal of $P_X$ by delivering and
+  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
+  conditions (between $b$ and $c$) than $\delta$, leading to the same
+  solutions of detection and propagation of $\Delta$. Eventually,
+  every \process whose last delivery is $\alpha_X$ receives and
+  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
 
@@
   % receives $\delta_f$ from \Process~$b'$.
-  These three phases propagation-detection-propagation ensure that
-  \processes eventually purge stale $\alpha$ messages from the system,
-  leaving room for best eventual forwarding of up-to-date messages.
+  Three-phase purge ensures that all \processes of the system
+  eventually removes stale $\alpha$ messages, leaving room for best
+  eventual forwarding of up-to-date messages.
   %

### 2021-09-08 input/experiments.tex
integrate CDN but not satisfying

@@
+\newcommand{\FIGSCALE}{0.59}
+
 \section{Experimentation}
@@
 
-This section describes the results of our experimentation evaluating
-the properties of \NAME that enables adaptive scoped broadcast in
-dynamic networks. It answers the following questions: What is the
-overhead of reaching consistent partitioning using \NAME in large
-scale networks?  Is \NAME relevant in Edge infrastructures where
+%% This section describes the results of our experimentation evaluating
+%% the properties of \NAME that enables adaptive scoped broadcast in
+%% dynamic networks.
+
+This section aims to answer the following questions about \NAME: What
+is the overhead of reaching consistent partitioning using \NAME in
+large scale networks?  Is \NAME relevant in Edge infrastructures where
 \processes are geo-distributed into clusters? We performed the
@@
 \begin{figure}
-  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_complexity.eps}
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.eps}
   \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
@@
 \begin{figure}
-  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_geant.eps}
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
   \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}

### 2021-09-08 input/proposal.tex
integrate CDN but not satisfying

@@
 
-\begin{theorem}[\label{theo:bef}\underline{B}est \underline{e}ventual
-    \underline{f}orwarding $(BEF) \implies CP$]
-%
-Assuming reliable communication links where a correct \process $q$
-eventually receives the message $m$ \underline{s}ent to it by a
-\process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
-reach consistent partitioning if each \process eventually
-\underline{f}orwards ($f_p(m) \implies \forall \langle p, q\rangle \in
-E: s_{pq}(m)$) its best known partition.
+\begin{theorem}[\label{theo:bef}\underline{E}ventual \underline{F}orwarding
+    of \underline{B}est $(EFB) \implies CP$] Assuming reliable
+  communication links where a correct \process $q$ eventually receives
+  the message $m$ \underline{s}ent to it by a \process $p$ ($s_{pq}(m)
+  \implies r_{q}(m)$), \processes eventually reach consistent
+  partitioning if each \process eventually \underline{f}orwards
+  ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
+  best known partition.
 \end{theorem}
@@
 \begin{proof}
-  % \begin{asparadesc}
-  % \item [$BEF \implies CP$:]
   When a \process $s_1$ becomes a source, it belongs to its own
@@
 
-\begin{theorem}[\label{theo:dcp}BEF$^+$: BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
+\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
     \underline{D}ynamic \underline{c}onsistent
@@
 When a \process can \texttt{Add} and \texttt{Del}ete its partition, to
-ensure consistent partitioning, best eventual forwarding (see
+ensure consistent partitioning, eventual forwarding of best (see
 Theorem~\ref{theo:bef}) additionally requires
@@
   d_q(m'))$);
-\item then best eventual forwarding so such an $m'$ ends up
+\item then the eventual forwarding of best such that $m'$ ends up
   originating from the best up-to-date source for $q$.
@@
   %% source: $d(m)$
-  Assuming BEF as default propagation behavior where \processes
+  Assuming EFB as default propagation behavior where \processes
   deliver and forward the best sum of weights they received. We must
@@
   \begin{asparadesc}
-  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
+  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
     \process may receive messages in such an order ($d_b(\alpha_d^1)
@@
     %% $\alpha_a^{x'}$.
-  \item [Purge not followed by BEF:]
+  \item [Purge not followed by EFB:]
     %% also transiting messages
@@
     consistent partitioning.
-  \item [Purge then BEF:] Assuming the eventual and definitive removal
+  \item [Purge then EFB:] Assuming the eventual and definitive removal
     of stale messages at each \process, eventually every \process only
@@
   \end{asparadesc}
-  Using BEF$^+$, \processes reach consistent partitioning together as
+  Using EFB$^+$, \processes reach consistent partitioning together as
   in Theorem~\ref{theo:bef}.
@@
 \begin{theorem}[\label{theo:threephase}Three-phase purge]
-  The following three phases are sufficient to eventually purge the
-  system from stale control information:
+  Three phases are sufficient to eventually purge the system from
+  stale control information:
   \begin{inparaenum}[(i)]
@@
   \item detection of possibly blocking conditions, and
-  \item propagation of possibly deleted but blocked notifications.
+  \item propagation of delete notifications that were possibly blocked.
   \end{inparaenum}
@@
   delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
-
+  %
   %% Some \processes may have delivered messages about other partitions
@@
   %% about $P_Y$.
-
+  %
   %% \begin{asparadesc}
@@
   %%   sure, $\Delta$
-
+  %
   %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
@@
   %% \end{asparadesc}
-
   %% Propagation~I terminates: a \process does not deliver a $\delta$
@@
   %% \process does not deliver a looping message.  
-
   % ; and since \processes forward the messages they deliver, upstream
@@
   % receives $\delta_f$ from \Process~$b'$.
-  Three-phase purge ensures that all \processes of the system
-  eventually removes stale $\alpha$ messages, leaving room for best
-  eventual forwarding of up-to-date messages.
+  %% Three-phase purge ensures that all \processes of the system
+  %% eventually removes stale messages, leaving room for best eventual
+  %% forwarding of up-to-date messages.
   %
@@
 
-\begin{algorithm}[h!]
+\begin{algorithm}
   \input{input/algoascast.tex}

### 2021-09-08 input/related_work.tex
integrate CDN but not satisfying

--- 2021-09-07 input/related_work.tex
@@
 own index in a decentralized fashion.
-% This section reviews these
-% approaches.
 
@@
 \noindent Distributing this index among \processes circumvents these
-issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
-locality issues where \processes
+issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
+  coin_19}, but still raises locality issues where \processes
 \begin{inparaenum}[(i)]
-\item request to a possibly far away location service the content
-  location, and then
-\item request the actual content from far away replicas.
+\item request to possibly far away location services the content
+  location (e.g. as in \underline{c}ontent \underline{d}elivery
+  \underline{n}etworks (CDN)~\cite{triukose2011measuring} based on
+  \underline{d}omain \underline{n}ame \underline{s}ystems (DNS)), and
+  then
+\item request the actual content from possibly far away replicas
+  (e.g. as with \underline{d}istributed \underline{h}ash
+  \underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}).
 \end{inparaenum}
-For instance, using \underline{d}istributed \underline{h}ash
-\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
+For instance, using DHTs~\cite{ipfs, mdht, squirrel}, each \process
 stores a part of the index defined by an interval between hash values.

### 2021-09-08 input/related_work.tex
revert related work

--- 2021-09-07 input/related_work.tex
@@
 \noindent Distributing this index among \processes circumvents these
-issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
-locality issues where \processes
+issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
+  coin_19}, but still raises locality issues where \processes
 \begin{inparaenum}[(i)]
-\item request to a possibly far away location service the content
+\item request to possibly far away location services the content
   location, and then
-\item request the actual content from far away replicas.
+\item request the actual content from possibly far away replicas.
 \end{inparaenum}

### 2021-09-08 input/proposal.tex
wip

@@
   \item [Purge then EFB:] Assuming the eventual and definitive removal
-    of stale messages at each \process, eventually every \process only
-    delivers and forwards up-to-date messages, or no message at
-    all. Assuming that eventually, each removal triggers the
-    forwarding of best delivered messages, every \process eventually
-    delivers and forwards the best up-to-date delivered messages.
+    of stale messages at each \process ($S(\alpha_a) \implies
+    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
+    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
+    removal eventually triggers the forwarding of best delivered
+    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
+    upon receipt of such $\alpha_y$, either the \process already 
+    \TODO{tododododotododoo.}
+
+    ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
+    S(\alpha_y)$)
+
+    eventually every \process only delivers and forwards up-to-date
+    messages, or no message at all ($\eventually d_c(m') \implies \neg
+    S(m')$).
+
+    , every \process eventually delivers and forwards the best
+    up-to-date delivered messages as in Theorem~\ref{theo:bef}.
     %% Removing \emph{forever} all such stale messages about
@@
   \end{asparadesc}
-  Using EFB$^+$, \processes reach consistent partitioning together as
-  in Theorem~\ref{theo:bef}.
+  Using EFB$^+$, \processes reach consistent partitioning together.
 \end{proof}
@@
 Algorithm~\ref{algo:ascast} provides the few instructions of \NAME
-that implement three-phase purge and best eventual forwarding to
+that implement three-phase purge and eventual forwarding of best to
 enable dynamic consistent partitioning. For the sake of simplicity, it
@@
 As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
-not only requires eventual purging of stale control information, but
-also the retrieval of the best up-to-date partitions.  In that regard,
-both $\delta$ and $\Delta$ messages have dual use: since they already
-reach the borders of their partition by design, they also trigger a
-competition when reaching such bordering \processes (see
+not only requires eventual purging of stale messages, but also the
+retrieval of the best up-to-date partitions.  In that regard, both
+$\delta$ and $\Delta$ messages have dual use: since they already reach
+the borders of their partition by design, they trigger a competition
+when reaching bordering \processes (see
 Line~\ref{line:ascast_compete}).

### 2021-09-09 input/experiments.tex
spacing, and slight work on last efb paragraph

@@
 around $500$ ms due to the high latency inter-continental link. The
-first plateau corresponds to the source's autonomous system
-acknowledging this source, while the second plateau corresponds to the
-other autonomous system catching up.  The inter-continental link acts
-as a bottleneck that does not exist when each cluster has its own
-source.
+first plateau shows the source's autonomous system acknowledging this
+source, while the second shows the other autonomous system catching
+up.  The inter-continental link is a bottleneck that does not exist
+when each cluster has its own source.
 

### 2021-09-09 input/proposal.tex
spacing, and slight work on last efb paragraph

@@
     \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
-    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
-    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
+    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
+    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
     up-to-date messages propagation. However, even in such settings,
@@
     messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
-    upon receipt of such $\alpha_y$, either the \process already 
-    \TODO{tododododotododoo.}
+    \processes may deliver other stale messages that will be 
+    eventually removed to never be delivered again. In the worst case,
+    all processes deliver and remove all stale messages to ultimately
+    deliver and forward only up-to-date messages ($\eventually d_c(m')
+    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
+    eventually deliver and forward their best up-to-date message.
 
-    ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
-    S(\alpha_y)$)
+    %% upon receipt of such $\alpha_y$, either the \process already
+    %% delivered its removal and it does
 
-    eventually every \process only delivers and forwards up-to-date
-    messages, or no message at all ($\eventually d_c(m') \implies \neg
-    S(m')$).
+    %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
+    %% S(\alpha_y)$)
 
-    , every \process eventually delivers and forwards the best
-    up-to-date delivered messages as in Theorem~\ref{theo:bef}.
+    %% eventually every \process only delivers and forwards up-to-date
+    %% messages, or no message at all
+
+    %% , every \process eventually delivers and forwards the best
+    %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.
+
     %% Removing \emph{forever} all such stale messages about
@@
   \end{asparadesc}
-  Using EFB$^+$, \processes reach consistent partitioning together.
+  Using EFB$^+$, \processes reach consistent partitioning together
+  even under dynamic partitioning settings where \nodes can
+  \texttt{Add} and \texttt{Del}ete their partition.
 \end{proof}
@@
 or the parent delivered a worse message (see
-Line~\ref{line:detectA}). This may happen in stage II of
-Figure~\ref{fig:proofB} between $b$ and $c$.
+Line~\ref{line:detectA}). % This may happen in stage II of
+% Figure~\ref{fig:proofB} between $b$ and $c$.
 

### 2021-09-09 input/related_work.tex
spacing, and slight work on last efb paragraph

@@
 stores a part of the index defined by an interval between hash values.
-The hash values are the keys to retrieve the associated content
-location.  Before downloading any content, a \node asks for its
-location using its key. After a series of round-trips between possibly
-distant DHT servers, the \node gets a list of available
-replicas. Contrarily to \NAME, such services do not ensure to include
-the closest replica.
+Hash values are keys to retrieve the associated content location.
+Before downloading any content, a \node requests its location using
+its key. After round-trips between possibly distant DHT servers, the
+\node gets available replicas. Contrarily to \NAME, such services do
+not ensure to include the closest replica.
 

### 2021-09-09 input/proposal.tex
start to seem final

@@
     eventually removed to never be delivered again. In the worst case,
-    all processes deliver and remove all stale messages to ultimately
+    all \processes deliver and remove all stale messages to ultimately
     deliver and forward only up-to-date messages ($\eventually d_c(m')

### 2021-09-09 input/abstract.tex
address Adrien's comments

@@
   %%% Our proposal
-  \noindent In this paper, we abstract content indexing as distributed
-  partitioning:
-  every \process only indexes its closest replica, and
-  connected \processes with a similar index compose a partition. Our
-  decentralized implementation \NAME is
+  \noindent In this paper, we abstract the content indexing challenge
+  as a distributed partitioning problem: every \process only indexes
+  its closest replica, and connected \processes with a similar index
+  compose a partition. Our decentralized implementation \NAME is
   \begin{inparaenum}[(i)]
@@
   Our complexity analysis supported by simulations shows that \NAME
-  scales well in terms of generated traffic and termination time. As
-  such, \NAME can constitute a new building block for geo-distributed
-  services.
+  scales well in terms of generated traffic and termination time.
+  %% As
+  %% such, \NAME can constitute a new building block for geo-distributed
+  %% services.
 \end{abstract}

### 2021-09-09 input/conclusion.tex
integrate CDN but not satisfying
address Adrien's comments

@@
 
-As future work, we plan to enable lazy retrieval of partitions when a
-large number of \TODO{objects} is involved. Indeed, using \NAME, every
-\process partakes in the propagation of all indexes which raises
-scalability issues. We would like to leverage the hierarchical
-properties of
-% interconnected
-autonomous systems to limit the
-propagation of such indexes only to interested systems.
+As future work, we plan to leverage the hierarchical properties of
+interconnected autonomous systems to further limit the propagation of
+indexes within interested systems only. Systems hosting a large number
+of contents would greatly benefit from this improvement.
+
+%% As future work, we plan to enable lazy retrieval of partitions when a
+%% large number of contents is involved. Indeed, using \NAME, every
+%% \process partakes in the propagation of all indexes which raises
+%% scalability issues. We would like to leverage the hierarchical
+%% properties of
+%% % interconnected
+%% autonomous systems to limit the
+%% propagation of such indexes only to interested systems.
 

### 2021-09-09 input/figdel.tex
cosmetic + number
ongoing wip
address Adrien's comments

@@
       partition.  It notifies all \processes that belong to its
-      partition using \NAMEB.]{\input{input/figdelA.tex}}
+      partition.]{\input{input/figdelA.tex}}
     \hspace{5pt}
     %
-    \subfloat[Part B][\label{fig:delB}$\delta$s stop as soon as they
+    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as they
       encounter another partition. \Process~$b$ answers with its
@@
   \caption{\label{fig:del}Efficient removal of a partition using
-    \NAMEB. \Process~$a$ eventually knows that it belong to Partition
-    $P_d$.}
+    \NAMEB. $a$ eventually knows that it belongs to $P_d$.}
 \end{figure}

### 2021-09-09 input/introduction.tex
address Adrien's comments

@@
 Cloud, rely on \underline{d}istributed \underline{h}ash
-\underline{t}ables (DHT)~\cite{maymounkov2002kademlia} spread across
-the different \processes composing the infrastructure. When a client
-wants to access specific content, it requests a remote \process to
-provide at least one \process identity to retrieve this content
+\underline{t}ables (DHT) spread across the different \processes
+composing the infrastructure~\cite{maymounkov2002kademlia}. When a
+client wants to access specific content, it requests a remote \process
+to provide at least one \process identity to retrieve this content
 from. After it retrieved the content, the client can create another
 replica to improve the performance of future accesses, but it must
-contact the content indexing service again to notify of such a change.
+contact the indexing service again to notify of the creation of this
+new replica.
 %% a local replica is created to improve the performance for future
@@
 
-These approaches are in contradiction with the objectives of Edge
+Such approaches are in contradiction with the objectives of Edge
 infrastructures that aim at reducing the impact of latency as well as
@@
 
-\noindent The contribution of this paper is threefold:
+\noindent In this paper, we address these issues and limitations
+regarding content indexing. Our contribution is threefold:
 
@@
   partitions, the smaller \NAME's overhead.  Most importantly, \NAME
-  does not generate traffic in quiescent systems.  Our experiments
-  also highlight the relevance of \NAME in autonomous systems. \NAME
-  would allow to lock down the traffic generated by content indexing,
-  even in contexts where \emph{physical} partitioning may occur.
-  As such, \NAME can constitute a new building block for geo-distributed
-  services.
+  does not generate traffic in quiescent systems.  % Our experiments
+  %  also highlight the relevance of \NAME in autonomous systems.
+  \NAME would allow to lock down the traffic generated by content
+  indexing, even in contexts where \emph{physical} partitioning may
+  occur.
+  %As such, \NAME can constitute a new building block for
+  % geo-distributed services.
 \end{asparadesc}

### 2021-09-09 input/proposal.tex
address Adrien's comments

@@
 converges to an inconsistent state where some \processes assume they
-belong to a partition while it does not exist anymore.
+belong to a partition while it does not exist anymore. The system
+needs to purge stale $\alpha$ messages that stop $\delta$ messages
+from reaching nodes.
+%The system needs to
+% purge its stale messages.
 
@@
     ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
-    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
-    consistent partitioning.
+    wrong ($\alpha_a^3$ instead of $\delta_a$).
+    % \Processes never
+    % reach consistent partitioning.
+    %
     %% Figure~\ref{fig:proofA} depicts the generic case where a \process
@@
     was received and discarded before ($\alpha_c^{y}$). When such a
-    message contains its best up-to-date partition, the \process never
-    ends up in its best partition. Therefore, \processes do not reach
-    consistent partitioning.
+    message contains its best up-to-date partition, a \process may
+    never end up in its best partition.
+    %    Therefore, \processes do not reach
+    % consistent partitioning.
   \item [Purge then EFB:] Assuming the eventual and definitive removal
@@
   We must prove that every \process that delivered a stale $\alpha_X$
-  eventually
-  \begin{inparaenum}[(i)]
-  \item delivers a better $\alpha_Y$, or 
-  \item delivers a removal notification of $\alpha_X$.
-  \end{inparaenum}
-  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
-  involving concurrent operations:
+  eventually delivers a better $\alpha_Y$, or delivers a removal
+  notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
+  issue of purging in scenarios involving concurrent operations.
 
-  If every \process (such as $a$) starting from the source delivers
-  and forwards a removal notification $\delta_X$ when their last
-  delivery is $\alpha_X$, then every such \process eventually delivers
-  the removal notification $\delta_X$ except \processes (such as $b$)
-  that delivered $\alpha_X$ from a \process that delivered a message
-  from another partition $\alpha_Y$ since then.
+  (i) If every \process (such as $a$) starting from the source
+  delivers and forwards a removal notification $\delta_X$ when their
+  last delivery is $\alpha_X$, then every such \process eventually
+  delivers the removal notification $\delta_X$ except \processes (such
+  as $b$) that delivered $\alpha_X$ from a \process that delivered a
+  message from another partition $\alpha_Y$ since then.
 
@@
 
-  Assuming that every \process keeps an history of its past
+  (ii) Assuming that every \process keeps an history of its past
   deliveries, \processes (such as $c$) can detect the inconsistency,
@@
 
-  A \process (such as $d$) whose last delivery is $\alpha_X$, but
-  whose parent is neither inconsistent (like $b$) nor receiving
+  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
+  but whose parent is neither inconsistent (like $b$) nor receiving
   $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting

### 2021-11-08 input/background.tex
wining space piece by piece
adapting to two columns, stilltodo. simpler problem display

@@
 
-\item [Dynamic partitioning and adaptive scoped broadcast:]
+\item [Dynamic partitioning:]
 
-Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
-destroys its replica. Every \process that belonged to its green
-partition must choose another partition to be in. While it makes sense
-for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
+In Figure~\ref{fig:partition_intuitionD}, \Process $G$ destroys its
+replica. Every \process that belonged to its green partition must
+choose another partition to be in. While it makes sense for
+\Process~$G$ to scoped broadcast its removal, \Process~$B$ and
 \Process~$R$ cannot afford to continuously advertise their replica to
@@
 propagation of other partitions (see Section~\ref{subsec:dynamic}).
+
+\item [Lazy partitioning:]
+
+\TODO{Finally, in Figure~\ref{fig:partition_intuition}, every nodes of
+  the system maintains an index to every content. In systems
+  comprising billions of content, this could constitute a scalability
+  issue. The partitioning protocol should take advantage of boundary
+  between autonomous systems in the Internet. For instance, the AS
+  from France should not flood the AS from Spain unless the latter
+  starts to host a replica. In addition, when the system removes its
+  last source, it should stop receiving messages from other ASes
+  designed to maintain the closest partition.}
+
 \end{asparadesc}

### 2021-11-08 input/figsimplerproblem.tex
adapting to two columns, stilltodo. simpler problem display

\begin{figure*}
  \newcommand{\SCALE}{0.9}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $d$ delete
      their partition while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ despite it propagated $\alpha_a$ before.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}$c$ stays in $P_a$ despite it has been deleted.]
             {\input{input/figsimplerproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, naive
    propagation of $\alpha$ and $\delta$ messages is insufficient to
    guarantee consistent partitioning. If $c$ had children, they would
    stay in the wrong partition as well. $c$ must acknowledge
    $P_a$'s \emph{possible} deletion and propagate it.}
\end{figure*}

### 2021-11-08 input/proposal.tex
adapting to two columns, stilltodo. simpler problem display

@@
 
-\subsection{Scoped broadcast}
+\subsection{Scoped broadcast \TODO{Is it so important?}}
 \label{subsec:scoped}
@@
 \begin{definition}[\label{def:lwo}Message staleness]
-  A message $m$ conveys \underline{s}tale control information if the
-  \process that broadcast $m$ later broadcast another message $m'$:
-  $S(m) = \exists m': b_p(m) \rightarrow b_p(m')$.
+  Only the latest message of a \process matters. A message $m$ conveys
+  \underline{s}tale control information if the \process that broadcast
+  $m$ later broadcast another message $m'$: $S(m) = \exists m': b_p(m)
+  \rightarrow b_p(m')$.
 
@@
 
-\input{input/figproblem.tex}
+\input{input/figsimplerproblem.tex}
 

### 2021-11-09 input/proposal.tex
meow

@@
   \input{input/algoascast.tex}
-  \caption{\label{algo:ascast}\NAME at \Process~$p$ in dynamic networks.}
+  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
 \end{algorithm}
@@
 
-Algorithm~\ref{algo:ascast} also enables dynamic consistent
-partitioning in dynamic networks where \processes can join, leave, or
-crash at any time. Removing a \process is equivalent to removing all
-its edges, and adding a \process is equivalent to add as many edges as
-necessary.  Adding an edge between two \processes may only improve the
-shortest path of one of these \processes. Therefore, it triggers a
-competition between the two \processes only. If one or the other
-\process improves, the propagation of $\alpha$ messages operates
-normally.  Removing an edge between two \processes may invalidate the
-shortest path of one of involved \processes plus downstream
-\processes. As a side effect, removing an edge may also impair the
-propagation of a partition delete. To implement this behavior, \NAME
-uses its implementation of $\Delta$ messages. This prove costly but
-enables \NAME even in dynamic networks subject to physical
-partitioning.
+\begin{algorithm}
+  \input{input/algoedges.tex}
+  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
+\end{algorithm}
+
+Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
+dynamic networks where \processes can join, leave, or crash at any
+time. Removing a \process is equivalent to removing all its edges, and
+adding a \process is equivalent to add as many edges as necessary.
+Adding an edge between two \processes may only improve the shortest
+path of one of these \processes. Therefore, it triggers a competition
+between the two \processes only. If one or the other \process
+improves, the propagation of $\alpha$ messages operates normally.
+Removing an edge between two \processes may invalidate the shortest
+path of one of involved \processes plus downstream \processes. As a
+side effect, removing an edge may also impair the propagation of a
+partition delete. To implement this behavior, \NAME uses its
+implementation of $\Delta$ messages. This prove costly but enables
+\NAME even in dynamic networks subject to physical partitioning.
 

### 2021-11-09 input/figsimplerproblem.tex
about example

@@
   \newcommand{\SCALE}{0.9}
+
+  \newcommand{\LEFT}{\triangleleft}
+  \newcommand{\RIGHT}{\triangleright}
+
   \begin{center}
-    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
+    \subfloat[Part A][\label{fig:problemA}(both) $a$ and $c$ become sources.
       $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
     \hspace{0pt}
-    \subfloat[Part B][\label{fig:problemB}Both $a$ and $d$ delete
-      their partition while $b$ delivers and forwards $\alpha_a$.]
+    \subfloat[Part B][\label{fig:problemB}(top) $c$ deletes its partition. (bottom)
+    $a$ and $c$ delete their partition. (both) $b$ delivers and forwards $\alpha_a$.]
              {\input{input/figsimplerproblemB.tex}}
     \hspace{0pt}
-    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
-      $\delta_a$ despite it propagated $\alpha_a$ before.]
+    \subfloat[Part C][\label{fig:problemC}(bottom) $b$ blocks the only transiting
+      $\delta_a$ despite it propagated $\alpha_a$ before. (both) $b$ delivers and forwards $\alpha_c$.]
              {\input{input/figsimplerproblemC.tex}}
     \hspace{0pt}
-    \subfloat[Part D][\label{fig:problemD}$c$ stays in $P_a$ despite it has been deleted.]
+    \subfloat[Part D][\label{fig:problemD}(both) $b$ delivers and forwards $\delta_c$. (top)
+    It reaches $a$ that answers with $\alpha_a$. $b$ delivers $\alpha_a$ again. (both) $c$
+    stays in $P_a$.]
              {\input{input/figsimplerproblemD.tex}}
@@
   \caption{\label{fig:problem}Even in the simplest scenarios, naive
-    propagation of $\alpha$ and $\delta$ messages is insufficient to
-    guarantee consistent partitioning. If $c$ had children, they would
-    stay in the wrong partition as well. $c$ must acknowledge
-    $P_a$'s \emph{possible} deletion and propagate it.}
+    propagation of $\alpha$ and $\delta$ messages may be insufficient
+    to guarantee consistent partitioning. In the bottom scenario, if
+    $c$ had children, they would stay in the wrong partition
+    too. Despite both scenarios look the same from $c$'s perspective,
+    $c$ must acknowledge $P_a$'s \emph{possible} deletion and
+    propagate it.}
 \end{figure*}

### 2021-11-10 input/proposal2.tex
starting with xas, small changes here and there

\section{\NAMEC}
\label{sec:proposal2}

\NAME enables indexing the closest replica of each \process without
flooding the whole network when a new replica appears or disappears.
Nevertheless, every node must partake in the indexing of each
content. When the networks accounts for billions of content, this
raises scalability issues. Inspired by the Internet topology that
comprises tens of thousands of interconnected autonomous systems
serving billions of people~\cite{nur2018crossas}, we want to further
lock-down traffic by leveraging the edges of networks as barriers, and
enable on-demand indexing.

To enable cross-network indexing, we designed and implemented \NAMEC
(stands for both \underline{cross} \underline{a}utonomous
\underline{s}ystems and \underline{ex}tended \underline{a}daptive
\underline{s}coped broad\underline{cast}). The main idea behind \NAMEC
is that every node maintains two \NAME:
\begin{inparaenum}[(i)]
\item the first maintaining the closest source intra-AS and
  acknowledges the interests of its AS;
\item the second maintaining the closest source cross-AS that also
  competes against the local closest source.
\end{inparaenum}
\NAMEC enables nodes to discard irrelevant indexes while maintaining
the closest source between connected ASes. \TODO{This section
  describes our proposal.}

\TODO{Added invariant: global is always smaller than local when they
  exist.}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-11-15 input/proposal.tex
starting with xas, small changes here and there
about purge

@@
 
-\subsection{Scoped broadcast \TODO{Is it so important?}}
+\subsection{Scoped broadcast}
 \label{subsec:scoped}
@@
 
-\begin{theorem}[\label{theo:bef}\underline{E}ventual \underline{F}orwarding
+\begin{theorem}[\label{theo:efb}\underline{E}ventual \underline{F}orwarding
     of \underline{B}est $(EFB) \implies CP$] Assuming reliable
@@
 \end{inparaenum}
+\TODO{Rework here.}
 Figure~\ref{fig:problem} highlights such consistency issues with
@@
 from reaching nodes.
-%The system needs to
-% purge its stale messages.
 
-%% Naive propagation of $\alpha$ and $\delta$ messages
-%% is insufficient to guarantee consistent partitioning when any \process
-%% can add or delete its partition at any time. \Processes need to
-%% exploit their local knowledge gathered over message receipts to allow
-%% up-to-date messages to propagate to relevant \processes.
+\begin{definition}[\label{def:purge}Message purge]
+  A system purges a message $P(m)$ when every \node $q$ that delivered
+  $m$ eventually delivers another message $m'$ never followed by the
+  delivery of the former message $m$: $d_q(m) \implies \eventually
+  (d_q(m) \rightarrow d_q(m'))$.
+\end{definition}
 
@@
 %
-When a \process can \texttt{Add} and \texttt{Del}ete its partition, to
-ensure consistent partitioning, eventual forwarding of best (see
-Theorem~\ref{theo:bef}) additionally requires
+  When a \process can \texttt{Add} and \texttt{Del}ete its partition,
+  to ensure consistent partitioning, eventual forwarding of best
+  (Theorem~\ref{theo:efb}) additionally requires
 \begin{inparaenum}[(i)]
-\item eventual purging of stale messages ($S(m)
-  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
-  d_q(m'))$);
-\item then the eventual forwarding of best such that $m'$ ends up
-  originating from the best up-to-date source for $q$.
+\item eventual purging of stale messages ($S(m) \implies P(m)$), then
+\item the eventual forwarding of best (Definition~\ref{theo:efb}).
 \end{inparaenum}
@@
     deliver and forward only up-to-date messages ($\eventually d_c(m')
-    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
+    \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
     eventually deliver and forward their best up-to-date message.
@@
 
-\begin{figure}
-  \centering\input{input/figproofB.tex}
-  \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
-    messages from reaching \processes with the corresponding
-    partition. Consistent partitioning requires that all \processes
-    propagate $\delta$ messages as often as possible (I); detect
-    possible inconsistencies when parents' $\alpha$ messages
-    contradict history or state (II); notify \processes of possible
-    inconsistencies (III).}
-\end{figure}
+%% \begin{figure}
+%%   \centering\input{input/figproofB.tex}
+%%   \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
+%%     messages from reaching \processes with the corresponding
+%%     partition. Consistent partitioning requires that all \processes
+%%     propagate $\delta$ messages as often as possible (I); detect
+%%     possible inconsistencies when parents' $\alpha$ messages
+%%     contradict history or state (II); notify \processes of possible
+%%     inconsistencies (III).}
+%% \end{figure}
 

### 2021-11-15 input/proposal.tex
mostly about algo text

@@
 
+\input{input/figdel.tex}
+
 At any time, a source can revoke its self-appointed status of source
@@
 
+\input{input/figsimplerproblem.tex}
+
 \begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
@@
 \end{definition}
-
-\input{input/figdel.tex}
-
-\input{input/figsimplerproblem.tex}
 
@@
 \begin{definition}[\label{def:purge}Message purge]
-  A system purges a message $P(m)$ when every \node $q$ that delivered
-  $m$ eventually delivers another message $m'$ never followed by the
-  delivery of the former message $m$: $d_q(m) \implies \eventually
-  (d_q(m) \rightarrow d_q(m'))$.
+  A system purges a message \TODO{$P(m)$} when every \node $q$ that
+  delivered $m$ eventually delivers another message $m'$ never
+  followed by the delivery of the former message $m$: $d_q(m) \implies
+  \eventually (d_q(m) \rightarrow d_q(m')) \TODO{\wedge}$.
 \end{definition}
@@
 \item eventual purging of stale messages ($S(m) \implies P(m)$), then
-\item the eventual forwarding of best (Definition~\ref{theo:efb}).
+\item the eventual forwarding of best (Theorem~\ref{theo:efb}).
 \end{inparaenum}
@@
   \begin{asparadesc}
-  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
-    \process may receive messages in such an order ($d_b(\alpha_d^1)
-    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
-    not forward messages required by other \processes
-    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
-    wrong ($\alpha_a^3$ instead of $\delta_a$).
+  \item [EFB without Purge:] A \process may receive messages in such
+    an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
+    \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
+    not forward messages required by other \processes ($\delta_a$ for
+    $c$). The last delivery of some nodes may be wrong (\eg in
+    Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
     % \Processes never
@@
   \item propagation of delete notifications,
-  \item detection of possibly blocking conditions, and
+  \item detection of possibly blocked deletion, and
   \item propagation of delete notifications that were possibly blocked.
@@
 
-Algorithm~\ref{algo:ascast} provides the few instructions of \NAME
-that implement three-phase purge and eventual forwarding of best to
-enable dynamic consistent partitioning. For the sake of simplicity, it
-does not handle multiple sessions and associated optimisation such as
-data structure sharing and message packing.
+Algorithm~\ref{algo:ascast} provides the instructions of \NAME that
+implement three-phase purge and eventual forwarding of best to enable
+dynamic consistent partitioning. For the sake of simplicity, it does
+not handle multiple sessions nor optimisation such as message packing.
 
@@
 Nevertheless, following the principles of scoped broadcast, we expect
-that every \process only acknowledges a small subset of sources.
-Using such a vector, every message $m$ carries its source $s$ along
-with its version $c$ that we subscript $m_{s, c}$.  Each \process
-delivers and forwards
-\begin{inparaenum}[(i)]
-\item only newest messages (see Line~\ref{line:ascast_version}) that
-\item improve their best known partition (see
-  Line~\ref{line:ascast_better}).
-\end{inparaenum}
-This vector of versions constitutes a summary of local deliveries. It
-allows a \process to detect inconsistencies in message delivery: the
-parent delivered a stale message (see Line~\ref{line:ascast_version}),
-or the parent delivered a worse message (see
-Line~\ref{line:detectA}). % This may happen in stage II of
-% Figure~\ref{fig:proofB} between $b$ and $c$.
+that every \process only acknowledges a small subset of sources.  In
+addition, each message carries the identifier and counter of each
+\node that forwarded it. Again, following the principles of scoped
+broadcast, we expect that versioned paths remain small. Using these
+data structures, each \process delivers and forwards only new messages
+that improve their best known partition (see
+Line~\ref{line:ascast_improve}).
 
-A \process ($c$) detecting an inconsistency disseminates a $\Delta$
-message. Such a $\Delta$ must not modify any vector of versions since
-the partition of the corresponding $\alpha$ may still exist.
-Therefore, it additionally includes and maintains a path $\pi$
-initialized to $\alpha$'s one. Such a $\Delta_{s, c}^{\pi}$
-transitively tracks and purges $\alpha$ messages that were forwarded
-by the detecting \process. The path $\pi$ also enables a quick stop of
-looping messages and in turns ensures termination. However, carrying
-paths in messages is costly. In the worst case, a message piggybacks
-the identity of all \processes in the system. Fortunately, message
-paths and \NAME synergyze well with each other, for paths tend to be
-smaller as the number of sources in the system increases. Contrarily
-to $\alpha$ and $\Delta$ messages, $\delta_{s, c}$ messages do not
-carry a path, and are therefore more efficient. They
-\begin{inparaenum}[(i)]
-\item solely rely on versions to operate, and
-\item use the whole dissemination graph to propagate in the system, as
-  opposed to $\Delta$ that must follow the dissemination tree of the
-  corresponding $\alpha$.
-\end{inparaenum}
+This vector of versions constitutes a summary of known progress of
+other \nodes. It discards stale messages and it enables detecting
+possible inconsistencies in message delivery: the current best
+partition comes from a neighbor that just delivered a stale message
+(see Line~\ref{line:ascast_detect}). Figure~\ref{fig:problem} shows
+that such a behavior may hide a delete notification. The detecting
+\process must act to reflect this possible change: all \processes
+whose last message comes from the detecting \process must remove it
+and accept the competition of other \processes. Since this behavior is
+similar to that of source deletion, we implement it in a similar way.
+
+A \process that removes its self-appointed status of source, or
+detects a possible inconsistency, increments its local counter and
+disseminates a delete notification message $\delta_{s, c}$
+piggybacking its identifier $s$ and counter $c$. Any \process that
+receives such delete notification deliver and forward it if their best
+message contains the has-been source or detector associated to a lower
+counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
+messages to quickly reach every downstream \process.
 
@@
 not only requires eventual purging of stale messages, but also the
-retrieval of the best up-to-date partitions.  In that regard, both
-$\delta$ and $\Delta$ messages have dual use: since they already reach
-the borders of their partition by design, they trigger a competition
-when reaching bordering \processes (see
-Line~\ref{line:ascast_compete}).
-%% This simply consists in sending the
-%% current partition through the communication link from which the
-%% \process received the $\delta$. Upon receipt of this answer,
-%% \processes act normally by propagating their changes when they
-%% improve.
+retrieval of the best up-to-date partitions.  In that regard, $\delta$
+messages have a dual use: since they already reach the borders of
+their partition by design, they trigger a competition when reaching
+bordering.  When a \process receives a delete notification from a
+neighbor $q$ but does not deliver it, it assumes that the just
+received $\delta$ message purged possibly stale messages, creating a
+gap that its own best partition could help fill. Consequently, it
+sends to $q$ its own best $\alpha$ message (see
+Line~\ref{line:ascast_echo}).
 
@@
 path of one of these \processes. Therefore, it triggers a competition
-between the two \processes only. If one or the other \process
-improves, the propagation of $\alpha$ messages operates normally.
-Removing an edge between two \processes may invalidate the shortest
-path of one of involved \processes plus downstream \processes. As a
-side effect, removing an edge may also impair the propagation of a
-partition delete. To implement this behavior, \NAME uses its
-implementation of $\Delta$ messages. This prove costly but enables
-\NAME even in dynamic networks subject to physical partitioning.
+between the two \processes. If one or the other \process improves, the
+propagation of $\alpha$ messages operates normally.  Removing an edge
+between two \processes may invalidate the shortest path of one of
+involved \processes plus downstream \processes. As a side effect,
+removing an edge may also impair the propagation of a partition
+delete. To implement this behavior, \NAME uses its implementation of
+$\delta$ messages. This enables \NAME even in dynamic networks subject
+to physical partitioning.
 

### 2021-11-15 input/proposal.tex
about issue

@@
 \end{inparaenum}
-\TODO{Rework here.}
 Figure~\ref{fig:problem} highlights such consistency issues with
-dynamic partitions, even in contexts where \processes have FIFO links,
-\ie where \processes receive the messages in the order of their
-sending ($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
-r_q(m')$). Both $a$ and $d$ add then delete their partition
-concurrently. \Process~$c$ receives, delivers, and forwards
-$\alpha_d^3$ followed by $\delta_d$. In the meantime, $b$ receives,
-delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
-both $c$ and $d$ deliver the message about Partition $P_a$, for they
-did not have any known partition at receipt time. On the contrary, $b$
-delivers $\alpha_d^1$, for it improves its distance to a known
-source. \Process~$b$ then blocks $a$'s removal notification
-$\delta_a$. It never reaches $c$ nor $d$. Also, $c$ does not deliver
-$\alpha_d$ and $\delta_d$ since it already delivered it. The system
-converges to an inconsistent state where some \processes assume they
-belong to a partition while it does not exist anymore. The system
-needs to purge stale $\alpha$ messages that stop $\delta$ messages
-from reaching nodes.
+dynamic partitions even in simple scenarios comprising three
+\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
+receive the messages in the order of their sending ($s_{pq}(m)
+\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
+Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
+their respective notification message to $b$. In
+Figure~\ref{fig:problemB} (bottom), both $a$ and $c$ delete their
+partition while $b$ receives, delivers, and forwards $\alpha_a^2$. In
+Figure~\ref{fig:problemC} (bottom), $b$ receives, delivers, and
+forwards $\alpha_c^1$, for it improves its best partition. Then it
+receives and discards $\delta_a$, for its best partition does not
+match the deleted one. The bottom part of Figure~\ref{fig:problemD}
+shows that eventually, $c$ stays in the deleted partition $P_a$ for
+not having received $\delta_a$ that $b$ blocked earlier. As a
+cascading effect, not only $c$ wrongfully believes that it belongs to
+$a$'s partition when $a$ already deleted it, but it could contribute
+to its inconsistency by blocking farther but up-to-date messages from
+actual sources. Using local knowledge only, the system needs to purge
+all stale messages to guarantee consistent partitioning.
 
@@
 piggybacking its identifier $s$ and counter $c$. Any \process that
-receives such delete notification deliver and forward it if their best
+receives such delete notification delivers and forwards it if its best
 message contains the has-been source or detector associated to a lower

### 2021-11-16 input/figsimplerproblem.tex
separating issues

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:problemA}(both) $a$ and $c$ become sources.
+    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
       $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
     \hspace{0pt}
-    \subfloat[Part B][\label{fig:problemB}(top) $c$ deletes its partition. (bottom)
-    $a$ and $c$ delete their partition. (both) $b$ delivers and forwards $\alpha_a$.]
+    \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
+     while $b$ delivers and forwards $\alpha_a$.]
              {\input{input/figsimplerproblemB.tex}}
     \hspace{0pt}
-    \subfloat[Part C][\label{fig:problemC}(bottom) $b$ blocks the only transiting
-      $\delta_a$ despite it propagated $\alpha_a$ before. (both) $b$ delivers and forwards $\alpha_c$.]
+    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
+      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
              {\input{input/figsimplerproblemC.tex}}
     \hspace{0pt}
-    \subfloat[Part D][\label{fig:problemD}(both) $b$ delivers and forwards $\delta_c$. (top)
-    It reaches $a$ that answers with $\alpha_a$. $b$ delivers $\alpha_a$ again. (both) $c$
-    stays in $P_a$.]
+    \subfloat[Part D][\label{fig:problemD}$b$ delivers and forwards $\delta_c$. $c$
+    stays in the deleted partition $P_a$.]
              {\input{input/figsimplerproblemD.tex}}
@@
     $c$ had children, they would stay in the wrong partition
-    too. Despite both scenarios look the same from $c$'s perspective,
-    $c$ must acknowledge $P_a$'s \emph{possible} deletion and
-    propagate it.}
+    too.
+
+    % Despite both scenarios look the same from $c$'s perspective, $c$
+    % must acknowledge $P_a$'s \emph{possible} deletion and propagate
+    % it.
+  }
 \end{figure*}

### 2021-11-16 input/figundoproblem.tex
separating issues

\begin{figure*}
  \newcommand{\SCALE}{0.9}

  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}

  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:undoproblemB}($c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:undoproblemD}(both) $b$ delivers and forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective, this
    scenario and Figure~\ref{fig:problem} are similar. Even when $a$
    did not delete its partition, $c$ must acknowledge $P_a$'s
    \emph{possible} deletion and propagate it.}
\end{figure*}

### 2021-11-16 input/proposal.tex
separating issues

@@
 
-At any time, a source can revoke its self-appointed status of source
-by executing a \texttt{Del} operation, hence deleting its partition
-from the system. All \processes that belong to this partition must
-eventually choose another partition to belong to. In
-Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
-that respectively include $\{a\}$, and $\{b, c, d\}$. In
-Figure~\ref{fig:delA}, \Process~$a$ deletes its partition. It notifies
-all neighboring \processes~--~here only \Process~$b$~-- that may
-belong to its partition using \NAMEB. Upon receipt, \Process~$b$
-discards the \underline{d}elete notification $\delta_a$ since
-$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
-sends its own best partition $\alpha_d^3$ that may be the best for
-\Process~$a$. Eventually, every \process belongs to Partition
-$P_d$. In this scenario, they reach consistent partitioning.
+At any time, a source can revoke its status of source by executing a
+\texttt{Del} operation, hence deleting its partition from the
+system. All \processes that belong to this partition must eventually
+choose another partition to belong to.
+
+\input{input/figsimplerproblem.tex}
+
+A naive implementation resembles echos in acoustics:
+\underline{d}elete notifications $\delta$ propagate as long as
+receivers' current partition is the targeted one, and when delete
+notifications reach the bordering \processes of the deleted partition,
+it triggers a competition that goes backward to fill the gap left open
+by removals.  For example, in Figure~\ref{fig:del}, two partitions
+initially exist: $P_a$ and $P_d$ that respectively include $\{a\}$,
+and $\{b, c, d\}$. In Figure~\ref{fig:delA}, \Process~$a$ deletes its
+partition. It notifies all neighboring \processes~--~here only
+\Process~$b$~-- that may belong to its partition using \NAMEB. Upon
+receipt, \Process~$b$ discards the delete notification $\delta_a$
+since $\delta_a$ does not target the former's partition
+$P_d$. \Process~$b$ sends its own best partition $\alpha_d^3$ that may
+be the best for \Process~$a$. Eventually, every \process belongs to
+Partition $P_d$. In this scenario, they reach consistent partitioning.
 
@@
 
-\input{input/figsimplerproblem.tex}
+\input{input/figundoproblem.tex}
 
@@
 \end{inparaenum}
-Figure~\ref{fig:problem} highlights such consistency issues with
-dynamic partitions even in simple scenarios comprising three
+Figure~\ref{fig:problem} depicts a scenario comprising only three
 \processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
@@
 their respective notification message to $b$. In
-Figure~\ref{fig:problemB} (bottom), both $a$ and $c$ delete their
-partition while $b$ receives, delivers, and forwards $\alpha_a^2$. In
-Figure~\ref{fig:problemC} (bottom), $b$ receives, delivers, and
-forwards $\alpha_c^1$, for it improves its best partition. Then it
-receives and discards $\delta_a$, for its best partition does not
-match the deleted one. The bottom part of Figure~\ref{fig:problemD}
-shows that eventually, $c$ stays in the deleted partition $P_a$ for
-not having received $\delta_a$ that $b$ blocked earlier. As a
-cascading effect, not only $c$ wrongfully believes that it belongs to
-$a$'s partition when $a$ already deleted it, but it could contribute
-to its inconsistency by blocking farther but up-to-date messages from
-actual sources. Using local knowledge only, the system needs to purge
-all stale messages to guarantee consistent partitioning.
+Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
+while $b$ receives, delivers, and forwards $\alpha_a^2$. In
+Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
+$\alpha_c^1$, for it improves its best partition. Then it receives and
+discards $\delta_a$, for its best partition does not match the deleted
+one. It produces an echo but since $\alpha_c^3$ is already transiting
+towards $a$, we simplify it. Finally, Figure~\ref{fig:problemD} shows
+that eventually, $c$ stays in the deleted partition $P_a$ for not
+having received $\delta_a$ that $b$ blocked earlier. As a cascading
+effect, not only $c$ wrongfully believes that it belongs to $a$'s
+partition when $a$ already deleted it, but it could contribute to its
+inconsistency by blocking farther but up-to-date messages from actual
+sources. The system needs to purge all stale messages to guarantee
+consistent partitioning.
 

### 2021-11-16 input/proposal.tex
meow

@@
   \underline{s}tale control information if the \process that broadcast
-  $m$ later broadcast another message $m'$: $S(m) = \exists m': b_p(m)
-  \rightarrow b_p(m')$.
+  $m$ later broadcast another message $m'$: $\mathcal{S}(m)
+  = \exists m': b_p(m) \rightarrow b_p(m')$.
 
@@
 \begin{definition}[\label{def:purge}Message purge]
-  A system purges a message \TODO{$P(m)$} when every \node $q$ that
-  delivered $m$ eventually delivers another message $m'$ never
-  followed by the delivery of the former message $m$: $d_q(m) \implies
-  \eventually (d_q(m) \rightarrow d_q(m')) \TODO{\wedge}$.
+  A system \underline{p}urges a message $\mathcal{P}(m)$ when every
+  \node $q$ that delivered $m$ eventually delivers another message
+  $m'$ never followed by the delivery of the former message $m$:
+  $d_q(m) \implies \exists m': \eventually (d_q(m)
+  \rightarrow d_q(m') \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
 \end{definition}
@@
 \begin{inparaenum}[(i)]
-\item eventual purging of stale messages ($S(m) \implies P(m)$), then
+\item eventual purging of stale messages ($\mathcal{S}(m) \implies
+  \mathcal{P}(m)$), then
 \item the eventual forwarding of best (Theorem~\ref{theo:efb}).

### 2021-11-16 input/implementation.tex
very start of algo

--- 2021-11-15 input/proposal.tex
@@
-\section{Adaptive scoped broadcast}
-\label{sec:adaptive}
+\section{Implementation and complexity analysis}
+\label{sec:implementation}
 
-To assign and maintain \processes to their best partition according to
-replica creations and removals, as well as dynamic infrastructure
-changes, we designed and implemented \NAME.  \NAME stands for
-\underline{A}daptive \underline{S}coped broad\underline{cast}. It
-relies on a primitive that allows a \process to broadcast a message
-within a limited scope. We first use this primitive to guarantee
-consistent partitioning when a \process can only create a new replica
-within the system. We highlight the issue when a \process can also
-destroy a replica, and provide a second algorithm that handles replica
-removals as well as dynamic changes of the infrastructure.  This
-section describes the communication primitive called scoped broadcast,
-then discusses the properties that guarantee consistent partitioning,
-and finally details our implementation \NAME.
-% and the analysis of its complexity.
-
-\subsection{Scoped broadcast}
-\label{subsec:scoped}
-
-%For instance, a \process from Paris could scoped broadcast messages to
-%all \processes in Paris; and \processes from other cities would never
-%deliver such messages.
-%Scoped broadcast only targets a connected \emph{subset} of \processes
-%in the whole distributed system.
-%
-
-% \TODO{dynamic graph: superscript with $t$?}
-In this paper, we consider Edge infrastructures with heterogeneous
-\nodes interconnected by communication links. \Processes involved in
-the management of content may crash but are not byzantine.  \Processes
-can reliably communicate through asynchronous message passing to other
-known \processes called neighbors.  % A more formal
-%definition of our system is given below:
-We define scoped broadcast as a communication primitive that
-propagates a message around its broadcaster within an
-application-dependant scope.
-
-\begin{definition}[Edge infrastructure]
-  An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
-  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
-  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
-  \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
-    k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
-  \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
-\end{definition}
-
-%Using epidemic
-%propagation (or gossiping), \processes can reliably broadcast messages
-%by forwarding delivered messages from neighbors to
-%neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
-%  nedelec2018causal, raynal2013distributed}.
-%
-%However, uniform reliable
-%broadcast states that \emph{all} correct \processes must deliver all
-%broadcast messages. This proves costly in large scale systems
-%comprising thousands of \processes. Instead, we define \emph{scoped
-%broadcast} where messages reach only an application-dependant subset
-%of connected \processes, thus significantly reducing the generated
-%traffic of broadcast.
-
-\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
-  When \Process~$x$ scoped \underline{b}roadcasts $b_x(m)$ a
-  \underline{m}essage $m$, every correct \process $y$ within a scope
-  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
-  $d_y(m)$. The scope depends on the \underline{s}tate $\sigma$ of
-  each \process, the \underline{m}etadata $\mu$ piggybacked by each
-  message, and a \underline{p}redicate $\phi$ verified from \process to
-  \process: $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
-  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$.
-\end{definition}
-
-This definition encompasses more specific definitions of related
-work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
-also highlights that epidemic propagation and scoped broadcast have
-well-aligned preoccupations. More precisely, it underlines the
-transitive relevance of messages, thus a \process can stop forwarding
-messages as soon as its predicate becomes unverified.
-%For instance, a \process
-%from Paris could scoped broadcast messages to all \processes in
-%Paris. This requires \processes to store and maintain their city
-%location in their local state. \Processes stop delivering and
-%forwarding their received messages when they come from a different
-%city.  In another instance, a \process from Paris could scoped
-%broadcast messages to all \processes in Paris plus neighboring
-%cities. This requires \processes to overload forwarded messages the
-%first time they reach another city. The predicate checks if messages
-%already reached two distinct cities before delivery. Similarly to
-%uniform reliable broadcast, scoped broadcast implementations expose
-%different trade-offs on space, time, and communication.
-%
-We use \NAMEB to efficiently modify the state of each \process
-depending on the partitions that exist in the system.
-
-\subsection{Consistent partitioning}
-\label{subsec:consistent}
-
-At any time, a \process can decide to become a \emph{source}, hence
-creating a new partition in the system by executing an \texttt{Add}
-operation. This partition includes at least its source plus
-neighboring \processes that estimate they are closer to this source
-than any other one. Such a distance (or \emph{weight}) is
-application-dependant: in the context of maintaining distributed
-indexes, this would be about link latency that \nodes could monitor
-by aggregating \texttt{ping}s.
-
-\begin{definition}[\label{def:partitioning}Partitioning]
-  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
-  the \underline{p}artition including at least \Process~$s$, each
-  \process belongs to at most one partition $\forall p,q \in V, \forall
-  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
-  \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
-  \processes that belong to this partition $\forall q \in \pi_{ps}: q
-  \in P_s$.
-\end{definition}
-
-Definition~\ref{def:scoped} and Definition~\ref{def:partitioning}
-share the transitive relevance of \process states. However, we further
-constrain the partitioning in order to guarantee the existence of
-exactly one consistent partitioning that \processes eventually converge
-to.
-
-\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  Let $W_{xy} = W_{yx}$ be the positive symmetric \underline{w}eight
-  between $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath
-  from $x$ to $z$ the weight of which $|\Pi_{xz}|$ is lower than any
-  other path weight, with $|\Pi_{xx}|$ being the greatest lower bound
-  of $x$, the only consistent partitioning $\mathcal{P}$ is a set of
-  partitions $P_{s\in S}$ such that each \process belongs to a logical
-  partition comprising its closest source: $\forall p \in P_{s_1}:
-  \nexists P_{s_2}$ such that $|\Pi_{s_2p}| < |\Pi_{s_1p}|$.
-\end{definition}
-
-Unfortunately, \processes do not share a common global knowledge of
-the network state. For \processes to reach consistent partitioning
-together, a \Process $s$ \underline{a}dding a partition must send a
-notification $\alpha_s$ to every \process that is closer to it than
-any other source. Since epidemic dissemination and scoped broadcast
-have well-aligned preoccupations, we assume implementations relying on
-message forwarding from neighbor-to-neighbor.
-
-\begin{theorem}[\label{theo:efb}\underline{E}ventual \underline{F}orwarding
-    of \underline{B}est $(EFB) \implies CP$] Assuming reliable
-  communication links where a correct \process $q$ eventually receives
-  the message $m$ \underline{s}ent to it by a \process $p$ ($s_{pq}(m)
-  \implies r_{q}(m)$), \processes eventually reach consistent
-  partitioning if each \process eventually \underline{f}orwards
-  ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
-  best known partition.
-\end{theorem}
-
-\input{input/figadd.tex}
-
-\begin{proof}
-  When a \process $s_1$ becomes a source, it belongs to its own
-  partition, for there exists no better partition than its own:
-  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
-  hence forwards such an $\alpha$ message to its neighbors. Since
-  communication links are reliable, neighboring \processes eventually
-  receive such a notification $\forall \langle s_1, q \rangle \in E,
-  s_1 \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
-  importantly, whatever the order of received messages, every \process
-  $q'$ in this neighborhood -- such that there exists no better
-  partition $s_2$ than the received one -- delivers and forwards it:
-  $\forall s_2 \in S: |\Pi_{q' s_1}| < |\Pi_{q' s_2}| \implies
-  \eventually d_{q'}(\alpha_{s_1}^{w_{s_1 q'}})$. By transitivity, the
-  message originating from $s_1$ reaches all such \processes through
-  their shortest paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q''
-    s_1}| < |\Pi_{q'' s_2}| \implies \eventually
-  d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.  Since there exists only
-  one best sum of weights per \process that can never be retracted,
-  \processes eventually reach consistent partitioning.
-  %% /!\ not equivalence for there exists other implementations.
-  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
-  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
-  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
-  %%   following \processes from $q'$ to $p$ may mistake another
-  %%   partition for their  because it needs the weight $W_{pq}$.
-  %% \end{asparadesc}
-\end{proof}
-
-\begin{algorithm}
-  \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding a partition by \Process~$p$.}
-\end{algorithm}
-
-Algorithm~\ref{algo:add} shows the instructions that implement
-consistent partitioning when
-\begin{inparaenum}[(i)]
-\item weights are scalar values,
-\item \processes only add new partitions to the system,
-\item and \processes never crash nor leave the system.
-\end{inparaenum}
-Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
-\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
-become the sources of their partition. They \NAMEB a notification
-\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
-initialize their own state with the lowest possible bound $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
-neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
-receives $\alpha_{d}^{1}$. Since it improves its own partition
-distance, it keeps it and forwards it to its neighbors. In
-Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
-does not improve its partition distance. \Processes $c$ and $d$ will
-never acknowledge that Source~$a$ exists. Ultimately, \processes
-discard last transiting messages. Despite the obvious lack of traffic
-optimization, the system reaches consistent partitioning.
-
-While only adding logical partitions to the distributed system is
-straightforward, removing them introduces additional complexity caused
-by concurrent operations.
-
-\subsection{Dynamic consistent partitioning}
-\label{subsec:dynamic}
-
-%% At any time, a \process can become a source, hence adding a new
-%% partition to the system. This partition eventually includes all
-%% \processes that are closer from this new source than any other
-%% else. \Processes naturally converge towards their respective best
-%% partition by only piggybacking a monotonically increasing distance in
-%% forwarded messages.
-
-\input{input/figdel.tex}
-
-At any time, a source can revoke its self-appointed status of source
-by executing a \texttt{Del} operation, hence deleting its partition
-from the system. All \processes that belong to this partition must
-eventually choose another partition to belong to. In
-Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
-that respectively include $\{a\}$, and $\{b, c, d\}$. In
-Figure~\ref{fig:delA}, \Process~$a$ deletes its partition. It notifies
-all neighboring \processes~--~here only \Process~$b$~-- that may
-belong to its partition using \NAMEB. Upon receipt, \Process~$b$
-discards the \underline{d}elete notification $\delta_a$ since
-$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
-sends its own best partition $\alpha_d^3$ that may be the best for
-\Process~$a$. Eventually, every \process belongs to Partition
-$P_d$. In this scenario, they reach consistent partitioning.
-
-Delete operations add a new notion of order between events, and most
-importantly between message deliveries. Delete operations implicitly
-state that all preceding events become obsolete, and that all messages
-originating from these preceding events convey stale control
-information.
-
-\input{input/figsimplerproblem.tex}
-
-\begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
-  The transitive, irreflexive, and antisymmetric happens-before
-  relationship defines a strict partial order between events. Two
-  messages are concurrent if none happens before the other.
-\end{definition}
-
-\begin{definition}[\label{def:lwo}Message staleness]
-  Only the latest message of a \process matters. A message $m$ conveys
-  \underline{s}tale control information if the \process that broadcast
-  $m$ later broadcast another message $m'$: $S(m) = \exists m': b_p(m)
-  \rightarrow b_p(m')$.
-
-  %% When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
-  %% b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
-  %% $\nexists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
-  %% convey \emph{\underline{s}tale} control information: $S(m)$.
-\end{definition}
-
-Unfortunately, stale control information as stated in
-Definition~\ref{def:lwo} may impair the propagation of both
-\begin{inparaenum}[(i)]
-\item notifications about actual sources, and
-\item notifications about deleted partitions.
-\end{inparaenum}
-Figure~\ref{fig:problem} highlights such consistency issues with
-dynamic partitions even in simple scenarios comprising three
-\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
-receive the messages in the order of their sending ($s_{pq}(m)
-\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
-Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
-their respective notification message to $b$. In
-Figure~\ref{fig:problemB} (bottom), both $a$ and $c$ delete their
-partition while $b$ receives, delivers, and forwards $\alpha_a^2$. In
-Figure~\ref{fig:problemC} (bottom), $b$ receives, delivers, and
-forwards $\alpha_c^1$, for it improves its best partition. Then it
-receives and discards $\delta_a$, for its best partition does not
-match the deleted one. The bottom part of Figure~\ref{fig:problemD}
-shows that eventually, $c$ stays in the deleted partition $P_a$ for
-not having received $\delta_a$ that $b$ blocked earlier. As a
-cascading effect, not only $c$ wrongfully believes that it belongs to
-$a$'s partition when $a$ already deleted it, but it could contribute
-to its inconsistency by blocking farther but up-to-date messages from
-actual sources. Using local knowledge only, the system needs to purge
-all stale messages to guarantee consistent partitioning.
-
-\begin{definition}[\label{def:purge}Message purge]
-  A system purges a message \TODO{$P(m)$} when every \node $q$ that
-  delivered $m$ eventually delivers another message $m'$ never
-  followed by the delivery of the former message $m$: $d_q(m) \implies
-  \eventually (d_q(m) \rightarrow d_q(m')) \TODO{\wedge}$.
-\end{definition}
-
-\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
-    \underline{D}ynamic \underline{c}onsistent
-    \underline{p}artitioning (DCP)]
-%
-  When a \process can \texttt{Add} and \texttt{Del}ete its partition,
-  to ensure consistent partitioning, eventual forwarding of best
-  (Theorem~\ref{theo:efb}) additionally requires
-\begin{inparaenum}[(i)]
-\item eventual purging of stale messages ($S(m) \implies P(m)$), then
-\item the eventual forwarding of best (Theorem~\ref{theo:efb}).
-\end{inparaenum}
-\end{theorem}
-
-\begin{proof}
-  %% To reach consistent partitioning, the last message delivered by
-  %% every process is not stale and comes from its respective best
-  %% source: $d(m)$
-  Assuming EFB as default propagation behavior where \processes
-  deliver and forward the best sum of weights they received. We must
-  prove that despite stale messages, the last delivery of every
-  \process is the message that followed the shortest path to its
-  closest source.
 \begin{asparadesc}
-  \item [EFB without Purge:] A \process may receive messages in such
-    an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
-    \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
-    not forward messages required by other \processes ($\delta_a$ for
-    $c$). The last delivery of some nodes may be wrong (\eg in
-    Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
-    % \Processes never
-    % reach consistent partitioning.
-    %
-    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
-    %% $b$ precludes itself and subsequent \processes such as $c$ of
-    %% delivering the message from their respective best source
-    %% $a$. \Process $b$ received and delivered a message from a
-    %% partition that has since then been deleted but with a better sum
-    %% of weights than newly received ones ($\alpha_d^y <
-    %% \alpha_a^{x'}$). It forever discards such a message
-    %% $\alpha_a^{x'}$.
-  \item [Purge not followed by EFB:]
-    %% also transiting messages
-    Assuming that every \process removes control information as soon
-    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
-    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
-    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
-    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
-    up-to-date messages propagation. However, even in such settings,
-    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
-    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
-    may never receive again, hence deliver and forward a message that
-    was received and discarded before ($\alpha_c^{y}$). When such a
-    message contains its best up-to-date partition, a \process may
-    never end up in its best partition.
-    %    Therefore, \processes do not reach
-    % consistent partitioning.
-  \item [Purge then EFB:] Assuming the eventual and definitive removal
-    of stale messages at each \process ($S(\alpha_a) \implies
-    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
-    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
-    removal eventually triggers the forwarding of best delivered
-    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
-    \processes may deliver other stale messages that will be 
-    eventually removed to never be delivered again. In the worst case,
-    all \processes deliver and remove all stale messages to ultimately
-    deliver and forward only up-to-date messages ($\eventually d_c(m')
-    \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
-    eventually deliver and forward their best up-to-date message.
-
-    %% upon receipt of such $\alpha_y$, either the \process already
-    %% delivered its removal and it does
-
-    %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
-    %% S(\alpha_y)$)
-
-    %% eventually every \process only delivers and forwards up-to-date
-    %% messages, or no message at all
-
-    %% , every \process eventually delivers and forwards the best
-    %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.
-
-    %% Removing \emph{forever} all such stale messages about
-    %% deleted partitions would allow \processes to propagate their best
-    %% up-to-date partition again, eventually reaching consistent
-    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
+\item [Dynamic consistent partitioning:]
+  Algorithm~\ref{algo:ascast}
+  provides the instructions of \NAME that implement three-phase purge
+  and eventual forwarding of best to enable dynamic consistent
+  partitioning. For the sake of simplicity, it does not handle
+  multiple sessions nor optimisation such as message packing.
 \end{asparadesc}
-  Using EFB$^+$, \processes reach consistent partitioning together
-  even under dynamic partitioning settings where \nodes can
-  \texttt{Add} and \texttt{Del}ete their partition.
-\end{proof}
-
-%% Figure removed as it's kind of redundant with preceding figure that
-%% depicts the issue
-%% \begin{figure} 
-%%   \centering\input{input/figproofA.tex}
-%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
-%%       stop other $\alpha$ messages from reaching all \processes ($b$
-%%       and $c$) that require it along the shortest path. Consistent
-%%       partitioning requires eventual purging of stale messages (see
-%%       Figure~\ref{fig:proofB}).}
-%% \end{figure}
-
-The main challenge consists in implementing a purging mechanism that
-ensures the \emph{eventual and definitive} removal of stale control
-information. One could guarantee consistent partitioning by always
-propagating the $\delta$ messages corresponding to the $\alpha$
-messages it propagated before. In Figure~\ref{fig:problem}, it means
-that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
-its neighbors \Process~$c$ and \Process~$d$ may need the notification
-of removal $\delta_a$ if it exists. However, such a solution also
-implies that \processes generate traffic not only related to their
-current partition, but also related to partitions they belonged to in
-the past. This would prove overly expensive in dynamic systems where
-\processes join and leave the system, create and delete partitions, at
-any time.  Instead, we propose to use the delivery order at each
-\process to detect possible inconsistencies and solve them.
-%% Together, \processes eventually remove all stale control information
-%% (transiting messages and local states) of the system leaving room for
-%% propagation of messages about up-to-date partitions.
-
-%% \input{input/figproof.tex}
-
-%% Figure~\ref{fig:proof} depicts the issues with staleness and message
-%% orderings. In Figure~\ref{fig:proofA}, the shortest path from any
-%% source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
-%% a stale $\alpha_d^{0.5}$ without knowing. When it receives
-%% $\alpha_a^1$, it discards it, for it assumes that downstream \processes
-%% are more interested in $\alpha_d^{0.5}$. To reach consistent
-%% partitioning, \Process $b$ first needs to purge its current partition
-%% to later accept that of its current actual shortest path:
-%% $\alpha_a^1$.
-
-%% \noindent Figure~\ref{fig:proofB} shows that removing stale control
-%% information is even more complex. The removal must reach all \processes
-%% of the previous shortest path going from $d$ to $b''$. Label I' shows
-%% the most obvious issue where \Process $e$ changed partition for a
-%% better but stale $\alpha_f$. Since it can remember its previous
-%% deliveries, it could still forward $\delta_d$ for the sake of
-%% consistency. However, this would lead to every \process forwarding
-%% every $\delta$ they ever delivered. Such protocol's overhead would
-%% depend on past partitioning instead of current one. Label III shows
-%% the issue when the blocking partition is already known to be stale at
-%% \Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
-%% $e$. However, it cannot deliver it, for it would break last win order.
-%% \Process $b'$ may be in an inconsistent state. Label IV shows the
-%% corollary issue: \Process $b''$ delivered a message from a \process that
-%% may be inconsistent without knowing it.
-
-\begin{theorem}[\label{theo:threephase}Three-phase purge]
-  Three phases are sufficient to eventually purge the system from
-  stale control information:
-  \begin{inparaenum}[(i)]
-  \item propagation of delete notifications,
-  \item detection of possibly blocked deletion, and
-  \item propagation of delete notifications that were possibly blocked.
-  \end{inparaenum}
-\end{theorem}
-
-%% \begin{figure}
-%%   \centering\input{input/figproofB.tex}
-%%   \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
-%%     messages from reaching \processes with the corresponding
-%%     partition. Consistent partitioning requires that all \processes
-%%     propagate $\delta$ messages as often as possible (I); detect
-%%     possible inconsistencies when parents' $\alpha$ messages
-%%     contradict history or state (II); notify \processes of possible
-%%     inconsistencies (III).}
-%% \end{figure}
-
-\begin{proof}
-  We must prove that every \process that delivered a stale $\alpha_X$
-  eventually delivers a better $\alpha_Y$, or delivers a removal
-  notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
-  issue of purging in scenarios involving concurrent operations.
-
-  (i) If every \process (such as $a$) starting from the source
-  delivers and forwards a removal notification $\delta_X$ when their
-  last delivery is $\alpha_X$, then every such \process eventually
-  delivers the removal notification $\delta_X$ except \processes (such
-  as $b$) that delivered $\alpha_X$ from a \process that delivered a
-  message from another partition $\alpha_Y$ since then.
-
-  These exceptions eventually receive and deliver $\alpha_Y$ since
-  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
-  they already received and delivered the removal notification of
-  $P_Y$ (such as $c$). These \processes may never receive hence
-  deliver $\delta_X$, and may never receive hence deliver a better
-  message than $\alpha_X$. They need an additional mechanism to
-  eventually purge $\alpha_X$ that cannot rely on the eventual purging
-  of $P_Y$ at \processes like $b$, to avoid deadlocks.
-
-  (ii) Assuming that every \process keeps an history of its past
-  deliveries, \processes (such as $c$) can detect the inconsistency,
-  since they receive from their parent an already deleted partition
-  $P_Y$. This notification means that the parent discards any
-  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
-  $\delta_X$ exists, it discards it. To ensure the purge of stale
-  messages, a detecting \process must assume the worst case that such
-  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
-  that notify the possible removal of $P_X$.
-
-  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
-  but whose parent is neither inconsistent (like $b$) nor receiving
-  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
-  \process, either directly or transitively, for such a child \process
-  ($d$) trusts the possible removal of $P_X$ by delivering and
-  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
-  conditions (between $b$ and $c$) than $\delta$, leading to the same
-  solutions of detection and propagation of $\Delta$. Eventually,
-  every \process whose last delivery is $\alpha_X$ receives and
-  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
-  %
-  %% Some \processes may have delivered messages about other partitions
-  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
-  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
-  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
-  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
-  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
-  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
-  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
-  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
-  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
-  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
-  %% the chain: $d$ is a child of \processes that delivered messages
-  %% about $P_Y$.
-  %
-  %% \begin{asparadesc}
-  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
-  %%   like $a$.  By propagating from \process to \process the
-  %%   corresponding $\delta_X$ message, these \processes purge
-  %%   $\alpha_X$.
-  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
-  %%   latter does not target its current partition.
-  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
-  %%   that $[a, b, c, d]$ is solved and that it does not require to
-  %%   purge $P_Y$.}
-  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
-  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
-  %%   it detects $b$ is its parent, and possibly blocked any delta with
-  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
-  %%   sure, $\Delta$
-  %
-  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
-  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
-  %%   \Process~$b$ that do not directly suffer from the non-delivery of
-  %%   $\delta_X$. They need to purge their own $P_Y$ if need
-  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
-  %%   one following \process will receive.
-  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
-  %%   such as \Process~$c$ that do not belong to the preceding category,
-  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
-  %%   forwarding guarantees that they receive $\alpha_Y$, which
-  %%   contradicts their history or state. In such a case, the detecting
-  %%   \processes purge their own $\alpha_X$. The detecting \processes
-  %%   must also notify subsequent \processes that their current
-  %%   partition \emph{may be} deleted. Indeed their parent may have
-  %%   blocked the corresponding $\delta$ messages and subsequent
-  %%   \processes must purge their possibly stale state, for the sake of
-  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
-  %%   their proximity to $\delta_X$ messages.
-  %%   % the uncertainty of a $\delta$ message.
-  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
-  %%   their parent:] \Processes such as \Process~$d$ that have
-  %%   $\alpha_X$ but preceding delivered messages are not
-  %%   important. Such \processes must trust detecting \processes by
-  %%   delivering and forwarding $\Delta_X$. It is worth noting that
-  %%   these messages are subject to all aforementioned blocking
-  %%   conditions, but are also solved by aforementioned mechanisms.
-  %% \end{asparadesc}
-  %% Propagation~I terminates: a \process does not deliver a $\delta$
-  %% message if it has already delivered it. Propagation~III terminates: a
-  %% \process does not deliver a looping message.  
-  % ; and since \processes forward the messages they deliver, upstream
-  % \processes eventually receive and may deliver messages detected as
-  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
-  % receives $\delta_f$ from \Process~$b'$.
-  %% Three-phase purge ensures that all \processes of the system
-  %% eventually removes stale messages, leaving room for best eventual
-  %% forwarding of up-to-date messages.
-  %
-  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
-  % delete to $e$, it will solve the inconsistency.}
-  %
-  %% In the meantime, \processes that still belong to a partition can
-  %% propagate their respective last $\alpha$ message, and reach
-    %% consistent partitioning.
-\end{proof}
-
-\subsection{Implementation and complexity}
-
-Algorithm~\ref{algo:ascast} provides the instructions of \NAME that
-implement three-phase purge and eventual forwarding of best to enable
-dynamic consistent partitioning. For the sake of simplicity, it does
-not handle multiple sessions nor optimisation such as message packing.
 
@@
 
-Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
-dynamic networks where \processes can join, leave, or crash at any
-time. Removing a \process is equivalent to removing all its edges, and
-adding a \process is equivalent to add as many edges as necessary.
-Adding an edge between two \processes may only improve the shortest
-path of one of these \processes. Therefore, it triggers a competition
-between the two \processes. If one or the other \process improves, the
-propagation of $\alpha$ messages operates normally.  Removing an edge
-between two \processes may invalidate the shortest path of one of
-involved \processes plus downstream \processes. As a side effect,
-removing an edge may also impair the propagation of a partition
-delete. To implement this behavior, \NAME uses its implementation of
-$\delta$ messages. This enables \NAME even in dynamic networks subject
-to physical partitioning.
+\begin{asparadesc}
+\item [Dynamic network:] Algorithm~\ref{algo:edges} enables dynamic
+  consistent partitioning in dynamic networks where \processes can
+  join, leave, or crash at any time. Removing a \process is equivalent
+  to removing all its edges, and adding a \process is equivalent to
+  add as many edges as necessary.  Adding an edge between two
+  \processes may only improve the shortest path of one of these
+  \processes. Therefore, it triggers a competition between the two
+  \processes. If one or the other \process improves, the propagation
+  of $\alpha$ messages operates normally.  Removing an edge between
+  two \processes may invalidate the shortest path of one of involved
+  \processes plus downstream \processes. As a side effect, removing an
+  edge may also impair the propagation of a partition delete. To
+  implement this behavior, \NAME uses its implementation of $\delta$
+  messages. This enables \NAME even in dynamic networks subject to
+  physical partitioning.
+\end{asparadesc}
 
@@
 %% \end{algorithm}
+
+\begin{asparadesc}
+\item [Lazy partitioning:] \TODO{Meow.}
+\end{asparadesc}
+
+\begin{algorithm}
+  \input{input/algoxascast.tex}
+  \caption{\label{algo:xascast}\NAMEC at \Process~$p$. \TODO{TODO.}}
+\end{algorithm}
+
 Next Section provides the details of our simulations that assess the

### 2021-11-16 input/proposal.tex
very start of algo

@@
 
-\subsection{Implementation and complexity}
+\subsection{Lazy partitioning}
+\label{subsec:lazy}
 
-Algorithm~\ref{algo:ascast} provides the instructions of \NAME that
-implement three-phase purge and eventual forwarding of best to enable
-dynamic consistent partitioning. For the sake of simplicity, it does
-not handle multiple sessions nor optimisation such as message packing.
+\NAME enables indexing the closest replica of each \process without
+flooding the whole network when a new replica appears or disappears.
+Nevertheless, every node must partake in the indexing of each
+content. When the networks accounts for billions of content, this
+raises scalability issues. Inspired by the Internet topology that
+comprises tens of thousands of interconnected autonomous systems
+serving billions of people~\cite{nur2018crossas}, we want to further
+lock-down traffic by leveraging the edges of networks as barriers, and
+enable on-demand indexing.
 
-\begin{algorithm}
-  \input{input/algoascast.tex}
-  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
-\end{algorithm}
+To enable cross-network indexing, we designed and implemented \NAMEC
+(stands for both \underline{cross} \underline{a}utonomous
+\underline{s}ystems and \underline{ex}tended \underline{a}daptive
+\underline{s}coped broad\underline{cast}). The main idea behind \NAMEC
+is that every node maintains two \NAME:
+\begin{inparaenum}[(i)]
+\item the first maintaining the closest source intra-AS and
+  acknowledges the interests of its AS;
+\item the second maintaining the closest source cross-AS that also
+  competes against the local closest source.
+\end{inparaenum}
+\NAMEC enables nodes to discard irrelevant indexes while maintaining
+the closest source between connected ASes. \TODO{This section
+  describes our proposal.}
 
-As stated in Theorem~\ref{theo:dcp}, every \process must purge stale
-messages.  To identify staleness, each \process maintains a vector of
-versions that associates the respective known local counter of each
-known source, or has-been source. Its size increases linearly with the
-number of sources that the \process has ever known, which is the
-number of \processes in the system $\mathcal{O}(V)$ in the worst case.
-Nevertheless, following the principles of scoped broadcast, we expect
-that every \process only acknowledges a small subset of sources.  In
-addition, each message carries the identifier and counter of each
-\node that forwarded it. Again, following the principles of scoped
-broadcast, we expect that versioned paths remain small. Using these
-data structures, each \process delivers and forwards only new messages
-that improve their best known partition (see
-Line~\ref{line:ascast_improve}).
-
-This vector of versions constitutes a summary of known progress of
-other \nodes. It discards stale messages and it enables detecting
-possible inconsistencies in message delivery: the current best
-partition comes from a neighbor that just delivered a stale message
-(see Line~\ref{line:ascast_detect}). Figure~\ref{fig:problem} shows
-that such a behavior may hide a delete notification. The detecting
-\process must act to reflect this possible change: all \processes
-whose last message comes from the detecting \process must remove it
-and accept the competition of other \processes. Since this behavior is
-similar to that of source deletion, we implement it in a similar way.
-
-A \process that removes its self-appointed status of source, or
-detects a possible inconsistency, increments its local counter and
-disseminates a delete notification message $\delta_{s, c}$
-piggybacking its identifier $s$ and counter $c$. Any \process that
-receives such delete notification delivers and forwards it if its best
-message contains the has-been source or detector associated to a lower
-counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
-messages to quickly reach every downstream \process.
-
-As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
-not only requires eventual purging of stale messages, but also the
-retrieval of the best up-to-date partitions.  In that regard, $\delta$
-messages have a dual use: since they already reach the borders of
-their partition by design, they trigger a competition when reaching
-bordering.  When a \process receives a delete notification from a
-neighbor $q$ but does not deliver it, it assumes that the just
-received $\delta$ message purged possibly stale messages, creating a
-gap that its own best partition could help fill. Consequently, it
-sends to $q$ its own best $\alpha$ message (see
-Line~\ref{line:ascast_echo}).
-
-\begin{algorithm}
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
-\end{algorithm}
-
-Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
-dynamic networks where \processes can join, leave, or crash at any
-time. Removing a \process is equivalent to removing all its edges, and
-adding a \process is equivalent to add as many edges as necessary.
-Adding an edge between two \processes may only improve the shortest
-path of one of these \processes. Therefore, it triggers a competition
-between the two \processes. If one or the other \process improves, the
-propagation of $\alpha$ messages operates normally.  Removing an edge
-between two \processes may invalidate the shortest path of one of
-involved \processes plus downstream \processes. As a side effect,
-removing an edge may also impair the propagation of a partition
-delete. To implement this behavior, \NAME uses its implementation of
-$\delta$ messages. This enables \NAME even in dynamic networks subject
-to physical partitioning.
-
-%% \NAME guarantees dynamic consistent partitioning by making extensive
-%% use of \process-to-\process communications. It requires
-%% \begin{inparaenum}[(i)]
-%% \item purging stale control information, hence propagating $\delta$
-%%   messages; and
-%% \item retrieving the closest source, hence propagating $\alpha$
-%%   messages.
-%% \end{inparaenum}
-In terms of number of messages, in the average case, a \process $i$
-chosen uniformly at random among all \processes creates a logical
-partition. Its messages $\alpha_i$ spread through the network until
-reaching \processes that belong to another partition closer to
-them. This splits partitions in half on average. Overall, the $a^{th}$
-new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
-      \log_2 a \rfloor}})$} \processes. This decreases every new
-partition until reaching one \process per new partition: its
-source. The average number of messages per \process is
-\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
-      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
-number of neighbors per \process.
-% \TODO{Multiple receipt and
-% multiple
-%  delivery imply more messages (receipt bounded by $|O|$ as well).}
-Deleting the $a^{th}$ partition generates twice as many messages as
-creating the $a^{th}$ partition: $\delta$ messages travel through the
-partition, then $\alpha$ messages compete to fill the gap.  Overall,
-the communication complexity shows that \NAME scales well to the
-number of partitions.
-%% In the
-%% worst-case, every new partition includes all but one \process
-%% belonging to the previous partition. The total number of messages
-%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
-%% a^2)$. As for the average-case, the number of messages for the
-%% partition deletion is identical to the number of messages of the
-%% corresponding partition creation.
-%% \begin{algorithm}[h!]
-%%   \input{input/algoedges.tex}
-%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
-%% \end{algorithm}
-Next Section provides the details of our simulations that assess the
-proposed implementation.
+\TODO{Added invariant: global is always smaller than local when they
+  exist.}
 

### 2021-11-18 input/implementation.tex
reorganize

@@
 \label{sec:implementation}
+
+\TODO{To assign and maintain \processes to their best partition according to
+replica creations and removals, as well as dynamic infrastructure
+changes, we designed and implemented \NAME.  \NAME stands for
+\underline{A}daptive \underline{S}coped broad\underline{cast}. It
+relies on a primitive that allows a \process to broadcast a message
+within a limited scope. We first use this primitive to guarantee
+consistent partitioning when a \process can only create a new replica
+within the system. We highlight the issue when a \process can also
+destroy a replica, and provide a second algorithm that handles replica
+removals as well as dynamic changes of the infrastructure. Finally, we
+propose \NAMEC that improves \NAME by leveraging the network topology
+to further reduce generated traffic at the Edge.  This section
+describes the communication primitive called scoped broadcast, then
+discusses the properties that guarantee consistent partitioning, and
+finally details our implementation \NAME.}
 

### 2021-11-18 input/proposal.tex
reorganize

@@
 
-To assign and maintain \processes to their best partition according to
-replica creations and removals, as well as dynamic infrastructure
-changes, we designed and implemented \NAME.  \NAME stands for
-\underline{A}daptive \underline{S}coped broad\underline{cast}. It
-relies on a primitive that allows a \process to broadcast a message
-within a limited scope. We first use this primitive to guarantee
-consistent partitioning when a \process can only create a new replica
-within the system. We highlight the issue when a \process can also
-destroy a replica, and provide a second algorithm that handles replica
-removals as well as dynamic changes of the infrastructure.  This
-section describes the communication primitive called scoped broadcast,
-then discusses the properties that guarantee consistent partitioning,
-and finally details our implementation \NAME.
-% and the analysis of its complexity.
+To provide lazy and dynamic logical partitioning in dynamic networks
+using scoped broadcast, all live \processes must collaborate to
+disseminate messages that notify new or removed sources to all and
+only interested \processes. This section reviews step-by-step the
+properties that allow \processes to converge to the desired state
+together. It first defines scoped broadcast, then uses it to guarantee
+consistent partitioning when a \process can only become a new source
+in the system. It highlights the issue when a \process can also remove
+its status of source. It shows that using local knowledge and scoped
+broadcast, \processes can still reach dynamic consistent partitioning
+when they are able to detect possible blocking conditions in the
+dissemination of required notifications. Finally, it further constrain
+the system by allowing only subsets of \processes to reach lazy
+consistent partitioning. \TODO{It shows that it only needs what?}
 
@@
 
-%For instance, a \process from Paris could scoped broadcast messages to
-%all \processes in Paris; and \processes from other cities would never
-%deliver such messages.
-%Scoped broadcast only targets a connected \emph{subset} of \processes
-%in the whole distributed system.
-%
+In this paper, we consider Edge infrastructures as a set of
+interconnected autonomous systems comprising heterogeneous \nodes
+interconnected by communication links. \Processes involved in the
+management of content may crash but are not byzantine.  \Processes can
+reliably communicate through asynchronous message passing to other
+known \processes called neighbors.  We define scoped broadcast as a
+communication primitive that propagates a message around its
+broadcaster within an application-dependant scope.
 
-% \TODO{dynamic graph: superscript with $t$?}
-In this paper, we consider Edge infrastructures with heterogeneous
-\nodes interconnected by communication links. \Processes involved in
-the management of content may crash but are not byzantine.  \Processes
-can reliably communicate through asynchronous message passing to other
-known \processes called neighbors.  % A more formal
-%definition of our system is given below:
-We define scoped broadcast as a communication primitive that
-propagates a message around its broadcaster within an
-application-dependant scope.
-
-\begin{definition}[Edge infrastructure]
-  An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
-  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
-  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
+\begin{definition}[Autonomous systems]
+  An autonomous system is a network comprising nodes and communication
+  links that we represent as a \underline{g}raph of
+  \underline{v}ertices and \underline{e}dges: $G = \langle V, E
+  \rangle$ with $E \in V \times V$. A \underline{p}ath $\pi_{ij}$ from
   \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
@@
 
-%Using epidemic
-%propagation (or gossiping), \processes can reliably broadcast messages
-%by forwarding delivered messages from neighbors to
-%neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
-%  nedelec2018causal, raynal2013distributed}.
-%
-%However, uniform reliable
-%broadcast states that \emph{all} correct \processes must deliver all
-%broadcast messages. This proves costly in large scale systems
-%comprising thousands of \processes. Instead, we define \emph{scoped
-%broadcast} where messages reach only an application-dependant subset
-%of connected \processes, thus significantly reducing the generated
-%traffic of broadcast.
+%% \begin{definition}[Edge infrastructure]
+%%   An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
+%%   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
+%%   \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
+%%   \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
+%%     k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
+%%   \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
+%% \end{definition}
 
@@
 
+Edge infrastructures are networks of networks. \TODO{Meow.}
+
+\begin{definition}[Edge infrastructure]
+  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
+  interconnected with additional links $\mathcal{E} \in V_1 \times
+  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
+  \ldots G_n\}, \mathcal{E} \rangle$.
+\end{definition}
+
 \NAME enables indexing the closest replica of each \process without

### 2021-11-19 input/implementation.tex
not much

@@
 \begin{asparadesc}
-\item [Lazy partitioning:] \TODO{Meow.}
+\item [Lazy partitioning:]
+  To enable lazy partitioning in networks of networks, we designed and
+  implemented \NAMEC (stands for both \underline{cross}
+  \underline{a}utonomous \underline{s}ystems and \underline{ex}tended
+  \underline{a}daptive \underline{s}coped broad\underline{cast}). The
+  main idea behind \NAMEC is that every node maintains two \NAME:
+  \begin{inparaenum}[(i)]
+\item the first maintaining the closest source intra-AS and
+  acknowledges the interests of its AS;
+\item the second maintaining the closest source cross-AS that also
+  competes against the local closest source.
+\end{inparaenum}
+\NAMEC enables nodes to discard irrelevant indexes while maintaining
+the closest source between connected ASes.
+
 \end{asparadesc}
@@
 Next Section provides the details of our simulations that assess the
-proposed implementation.
+proposed implementations.
 

### 2021-11-19 input/proposal.tex
meow
not much

@@
 \begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  Let $W_{xy} = W_{yx}$ be the positive symmetric \underline{w}eight
+  Let $W_{xy} = W_{yx}$ be the positive \TODO{symmetric} \underline{w}eight
   between $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath
@@
 
-\begin{theorem}[\label{theo:efb}\underline{E}ventual \underline{F}orwarding
-    of \underline{B}est $(EFB) \implies CP$] Assuming reliable
-  communication links where a correct \process $q$ eventually receives
-  the message $m$ \underline{s}ent to it by a \process $p$ ($s_{pq}(m)
-  \implies r_{q}(m)$), \processes eventually reach consistent
-  partitioning if each \process eventually \underline{f}orwards
+\begin{theorem}[\label{theo:efb}\underline{E}ventual
+  \underline{F}orwarding of \underline{B}est $(EFB) \implies CP$]
+  Assuming reliable communication links where a correct \process $q$
+  eventually receives the message $m$ \underline{s}ent to it by a
+  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
+  reach consistent partitioning if each \process eventually
+  \underline{f}orwards
   ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
-  best known partition.
+  best known partition. \TODO{setminus parent to comply with implem'.}
 \end{theorem}
@@
 
-\subsection{Lazy partitioning}
+\subsection{Lazy dynamic consistent partitioning}
 \label{subsec:lazy}
 
-Edge infrastructures are networks of networks. \TODO{Meow.}
+In Edge infrastructures comprising tens of thousands of autonomous
+systems~\cite{nur2018crossas}, only a small subset of autonomous
+systems needs logical partitioning. At any time, an autonomous system
+start logical partitioning when a \process from this network becomes a
+source.  Then every \process from this network belongs to the
+partition of its closest source not only from their own network but
+that of adjacent networks that started logical partitioning as well.
+At any time, an autonomous system stops logical partitioning when the
+last source from this network revokes its status of
+source. Eventually, all nodes from this network do not belong to any
+partition and the generated traffic stops.
 
@@
 
-\NAME enables indexing the closest replica of each \process without
-flooding the whole network when a new replica appears or disappears.
-Nevertheless, every node must partake in the indexing of each
-content. When the networks accounts for billions of content, this
-raises scalability issues. Inspired by the Internet topology that
-comprises tens of thousands of interconnected autonomous systems
-serving billions of people~\cite{nur2018crossas}, we want to further
-lock-down traffic by leveraging the edges of networks as barriers, and
-enable on-demand indexing.
+\begin{definition}[\TODO{Lazy DCP}]
 
-To enable cross-network indexing, we designed and implemented \NAMEC
-(stands for both \underline{cross} \underline{a}utonomous
-\underline{s}ystems and \underline{ex}tended \underline{a}daptive
-\underline{s}coped broad\underline{cast}). The main idea behind \NAMEC
-is that every node maintains two \NAME:
-\begin{inparaenum}[(i)]
-\item the first maintaining the closest source intra-AS and
-  acknowledges the interests of its AS;
-\item the second maintaining the closest source cross-AS that also
-  competes against the local closest source.
-\end{inparaenum}
-\NAMEC enables nodes to discard irrelevant indexes while maintaining
-the closest source between connected ASes. \TODO{This section
-  describes our proposal.}
+\end{definition}
+
+To provide lazy partitioning, \emph{gateway} \nodes that link
+autonomous systems together must acknowledge if there exists a source
+in their network.
+
+Must differentiate local from global when they cross the gates.
+
+% \NAME enables indexing the closest replica of each \process without
+% flooding the whole network when a new replica appears or disappears.
+% Nevertheless, every node must partake in the indexing of each
+% content. When the networks accounts for billions of content, this
+% raises scalability issues. Inspired by the Internet topology that
+% comprises tens of thousands of interconnected autonomous systems
+% serving billions of , we want to further
+% lock-down traffic by leveraging the edges of networks as barriers, and
+% enable on-demand indexing.
 

### 2021-11-22 input/proposal.tex
mostly on consistent partitioning...

@@
 application-dependant: in the context of maintaining distributed
-indexes, this would be about link latency that \nodes could monitor
-by aggregating \texttt{ping}s.
+indexes, this would be about link latency that \nodes could monitor by
+aggregating \texttt{ping}s; or operational costs when dealing with
+multiple tenants.
 
 \begin{definition}[\label{def:partitioning}Partitioning]
-  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
-  the \underline{p}artition including at least \Process~$s$, each
-  \process belongs to at most one partition $\forall p,q \in V, \forall
-  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
-  \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
+  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_{s\in
+    S}$ be the \underline{p}artition including at least \Process~$s$,
+  each \process belongs to at most one partition $\forall p,q \in V,
+  \forall s,s' \in S: (p \in P_{s} \wedge q \in P_{s'}) \implies (p \neq
+  q \vee s = s')$, and there exists at least one path $\pi_{ps}$ of
   \processes that belong to this partition $\forall q \in \pi_{ps}: q
@@
 \begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  Let $W_{xy} = W_{yx}$ be the positive \TODO{symmetric} \underline{w}eight
-  between $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath
-  from $x$ to $z$ the weight of which $|\Pi_{xz}|$ is lower than any
-  other path weight, with $|\Pi_{xx}|$ being the greatest lower bound
-  of $x$, the only consistent partitioning $\mathcal{P}$ is a set of
-  partitions $P_{s\in S}$ such that each \process belongs to a logical
-  partition comprising its closest source: $\forall p \in P_{s_1}:
-  \nexists P_{s_2}$ such that $|\Pi_{s_2p}| < |\Pi_{s_1p}|$.
+  Let $W_{xy}$ be the positive \underline{w}eight from $x$ to $y$,
+  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
+  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
+  with $|\Pi_{xx}|$ being the greatest lower bound of $x$, the only
+  consistent partitioning $\mathcal{P}$ is a set of partitions
+  $P_{s\in S}$ such that each \process belongs to a logical partition
+  comprising its closest source: $\forall p \in P_{s}: \nexists
+  P_{s'}$ such that $|\Pi_{s'p}| < |\Pi_{sp}|$.
 \end{definition}
@@
 any other source. Since epidemic dissemination and scoped broadcast
-have well-aligned preoccupations, we assume implementations relying on
+have well-aligned objectives, we assume implementations relying on
 message forwarding from neighbor-to-neighbor.
 
-\begin{theorem}[\label{theo:efb}\underline{E}ventual
-  \underline{F}orwarding of \underline{B}est $(EFB) \implies CP$]
-  Assuming reliable communication links where a correct \process $q$
-  eventually receives the message $m$ \underline{s}ent to it by a
-  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
-  reach consistent partitioning if each \process eventually
-  \underline{f}orwards
-  ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
-  best known partition. \TODO{setminus parent to comply with implem'.}
+\begin{definition}[\label{def:forwarding}Forwarding]
+  A \process $p$ \underline{f}orwards a message $m$ by
+  \underline{s}ending it to its neighbors: $f_p(m) \implies \forall
+  \langle p, q\rangle \in E: \TODO{s_{pq}(m)}$.
+\end{definition}
+
+\begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
+  $\implies\eventually$CP] Assuming reliable communication links
+  ($s_{pq}(m) \iff \eventually r_{qp}(m)$), \processes eventually
+  reach consistent partitioning if each \process delivers the message
+  notifying its shortest path weight to a source among its set of
+  \underline{r}eceived messages $R_p$ ($(m = \min R_p) \implies
+  d_p(m)$), and forwards the message notifying its shortest path
+  weight to a source $s$ among its set of \underline{d}elivered
+  messages $D_p$ ($(m = \min D_p) \implies f_p(m)$).
 \end{theorem}
@@
 \begin{proof}
-  When a \process $s_1$ becomes a source, it belongs to its own
-  partition, for there exists no better partition than its own:
-  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
-  hence forwards such an $\alpha$ message to its neighbors. Since
-  communication links are reliable, neighboring \processes eventually
-  receive such a notification $\forall \langle s_1, q \rangle \in E,
-  s_1 \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
-  importantly, whatever the order of received messages, every \process
-  $q'$ in this neighborhood -- such that there exists no better
-  partition $s_2$ than the received one -- delivers and forwards it:
-  $\forall s_2 \in S: |\Pi_{q' s_1}| < |\Pi_{q' s_2}| \implies
-  \eventually d_{q'}(\alpha_{s_1}^{w_{s_1 q'}})$. By transitivity, the
-  message originating from $s_1$ reaches all such \processes through
-  their shortest paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q''
-    s_1}| < |\Pi_{q'' s_2}| \implies \eventually
-  d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.  Since there exists only
-  one best sum of weights per \process that can never be retracted,
-  \processes eventually reach consistent partitioning.
+  When there are no sources, no \process receives, nor delivers hence
+  forwards any message. \Processes do not belong to any partition.
+
+  \noindent Whenever a \process $s$ becomes a source, it delivers its
+  own message $d_p(\alpha_{s})$. Whatever its set of received
+  messages, its own partition $P_s$ becomes and remains its closest
+  partition $\alpha_{s} = \min D_p$ since $\forall p \neq s: |\Pi_{s
+    s}| < |\Pi_{s p}|$.
+
+  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
+  Since communication links are reliable, neighboring \processes
+  eventually receive such a notification $\forall \langle s, q \rangle
+  \in E \iff \eventually r_q(\alpha_{s})$. Most importantly,
+  whatever the order of received messages, every \process $q$ in this
+  neighborhood such that there exists no closer source $s'$ than the
+  received one $s$, delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.
+
+  \noindent They forward it and their respective neighbors eventually
+  receive it. By transitivity, the message originating from $s$
+  reaches all \processes belonging to $P_s$ at least through their
+  shortest paths: $\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
+  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s})$.  Since there
+  exists only one best sum of weights per \process that can never be
+  retracted, \processes eventually reach consistent partitioning.
   %% /!\ not equivalence for there exists other implementations.
@@
 Algorithm~\ref{algo:add} shows the instructions that implement
-consistent partitioning when
+forwarding of best to reach consistent partitioning when
 \begin{inparaenum}[(i)]
@@
 \item and \processes never crash nor leave the system.
-\end{inparaenum}
+\end{inparaenum} \TODO{Disambiguator and comparison with $\alpha < A$.}
+\TODO{Why not towards parent?}
 Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
@@
 notifications reach the bordering \processes of the deleted partition,
-it triggers a competition that goes backward to fill the gap left open
-by removals.  For example, in Figure~\ref{fig:del}, two partitions
-initially exist: $P_a$ and $P_d$ that respectively include $\{a\}$,
-and $\{b, c, d\}$. In Figure~\ref{fig:delA}, \Process~$a$ deletes its
-partition. It notifies all neighboring \processes~--~here only
-\Process~$b$~-- that may belong to its partition using \NAMEB. Upon
-receipt, \Process~$b$ discards the delete notification $\delta_a$
-since $\delta_a$ does not target the former's partition
-$P_d$. \Process~$b$ sends its own best partition $\alpha_d^3$ that may
-be the best for \Process~$a$. Eventually, every \process belongs to
-Partition $P_d$. In this scenario, they reach consistent partitioning.
+it triggers a competition -- or an echo -- that goes backward to fill
+the gap left open by removals.  For example, in Figure~\ref{fig:del},
+two partitions initially exist: $P_a$ and $P_d$ that respectively
+include $\{a\}$, and $\{b, c, d\}$. In Figure~\ref{fig:delA},
+\Process~$a$ deletes its partition. It notifies all neighboring
+\processes~--~here only \Process~$b$~-- that may belong to its
+partition using \NAMEB. Upon receipt, \Process~$b$ discards the delete
+notification $\delta_a$ since $\delta_a$ does not target the former's
+partition $P_d$. \Process~$b$ sends its own best partition
+$\alpha_d^3$ that may be the best for \Process~$a$. Eventually, every
+\process belongs to Partition $P_d$. In this scenario, they reach
+consistent partitioning.
 
@@
 \begin{definition}[\label{def:purge}Message purge]
-  A system \underline{p}urges a message $\mathcal{P}(m)$ when every
+  A system \underline{p}urges a message $\TODO{\mathcal{P}}(m)$ when every
   \node $q$ that delivered $m$ eventually delivers another message

### 2021-11-22 input/proposal.tex
meow

@@
 \begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
-  $\implies\eventually$CP] Assuming reliable communication links
-  ($s_{pq}(m) \iff \eventually r_{qp}(m)$), \processes eventually
-  reach consistent partitioning if each \process delivers the message
-  notifying its shortest path weight to a source among its set of
-  \underline{r}eceived messages $R_p$ ($(m = \min R_p) \implies
-  d_p(m)$), and forwards the message notifying its shortest path
-  weight to a source $s$ among its set of \underline{d}elivered
-  messages $D_p$ ($(m = \min D_p) \implies f_p(m)$).
+    $\implies\eventually$CP]
+  %
+  Assuming reliable communication links ($s_{pq}(m) \iff \eventually
+  r_{qp}(m)$), \processes eventually reach consistent partitioning if
+  each \process delivers and forwards its best message among
+  \underline{r}eceived messages $R_p$, \ie the message $\alpha_s^d$
+  with the smallest distance $d$ to the source $s$ ($(\alpha_s^d = \min R_p)
+  \implies (d_p(\alpha_s^d) \wedge f_p(\TODO{\alpha_s^d}))$).
 \end{theorem}
@@
   eventually receive such a notification $\forall \langle s, q \rangle
-  \in E \iff \eventually r_q(\alpha_{s})$. Most importantly,
+  \in E \iff \eventually r_q(\alpha_{s}^{w_{pq}})$. Most importantly,
   whatever the order of received messages, every \process $q$ in this
@@
 \begin{inparaenum}[(i)]
-\item weights are scalar values,
+\item weights are scalar values piggybacked in messages and
+  accumulated over forwardings,
 \item \processes only add new partitions to the system,
-\item and \processes never crash nor leave the system.
-\end{inparaenum} \TODO{Disambiguator and comparison with $\alpha < A$.}
-\TODO{Why not towards parent?}
-Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
-\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
-become the sources of their partition. They \NAMEB a notification
-\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
-initialize their own state with the lowest possible bound $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
-neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
-receives $\alpha_{d}^{1}$. Since it improves its own partition
-distance, it keeps it and forwards it to its neighbors. In
-Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
-does not improve its partition distance. \Processes $c$ and $d$ will
-never acknowledge that Source~$a$ exists. Ultimately, \processes
-discard last transiting messages. Despite the obvious lack of traffic
-optimization, the system reaches consistent partitioning.
+\item and \processes never join, crash nor leave the system.
+\end{inparaenum}
+For the sake of simplicity, a \process does not forward a notification
+to its sender (Line~\ref{line:accumulator}).  Figure~\ref{fig:add}
+illustrates its behavior on a system comprising 4 \processes $a$, $b$,
+$c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
+their partition.  They \NAMEB a notification \underline{a}dd message:
+$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
+the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
+send a message to each of their neighbors by accumulating the
+corresponding edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
+it improves its own partition distance, it keeps it and forwards it to
+its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
+$\alpha_{a}^{2}$, for it does not improve its partition
+distance. \Processes $c$ and $d$ will never acknowledge that
+Source~$a$ exists. Ultimately, \processes discard last transiting
+messages. Despite the obvious lack of traffic optimization, the system
+reaches consistent partitioning.
 

### 2021-11-22 input/proposal.tex
meow

@@
   links that we represent as a \underline{g}raph of
-  \underline{v}ertices and \underline{e}dges: $G = \langle V, E
-  \rangle$ with $E \in V \times V$. A \underline{p}ath $\pi_{ij}$ from
-  \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
-    k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
-  \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
+  \underline{v}ertices and \underline{e}dges:
+  $G = \langle V, E \rangle$ with $E \in V \times V$. A
+  \underline{p}ath $\pi_{xz}$ from \Process~$x$ to \Process~$z$ is a
+  sequence of contiguous edges
+  $[\langle x, y_1 \rangle, \langle y_1, y_2\rangle, \ldots, \langle
+  y_n, z \rangle]$.
 \end{definition}
@@
   each \process, the \underline{m}etadata $\mu$ piggybacked by each
-  message, and a \underline{p}redicate $\phi$ verified from \process to
-  \process: $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
-  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$.
+  message, and a \underline{p}redicate $\phi$ verified from \process
+  to \process:
+  $(b_x(m) \wedge r_y(m)) \implies \exists \pi_{xy}: \forall z \in
+  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
 \end{definition}
@@
 work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
-also highlights that epidemic propagation and scoped broadcast have
-well-aligned preoccupations. More precisely, it underlines the
-transitive relevance of messages, thus a \process can stop forwarding
-messages as soon as its predicate becomes unverified.
+also highlights that the functioning of epidemic propagation is
+well-aligned with the objectives of scoped broadcast. More precisely,
+it underlines the transitive relevance of messages, thus a \process
+can stop forwarding messages as soon as its predicate becomes
+unverified.
 %For instance, a \process
@@
     S}$ be the \underline{p}artition including at least \Process~$s$,
-  each \process belongs to at most one partition $\forall p,q \in V,
-  \forall s,s' \in S: (p \in P_{s} \wedge q \in P_{s'}) \implies (p \neq
-  q \vee s = s')$, and there exists at least one path $\pi_{ps}$ of
-  \processes that belong to this partition $\forall q \in \pi_{ps}: q
+  each \process belongs to at most one partition $\forall x, y \in V,
+  \forall s,s' \in S: (x \in P_{s} \wedge y \in P_{s'}) \implies (x \neq
+  y \vee s = s')$, and there exists at least one path $\pi_{xs}$ of
+  \processes that belong to this partition $\forall z \in \pi_{xs}: z
   \in P_s$.
@@
 \begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  Let $W_{xy}$ be the positive \underline{w}eight from $x$ to $y$,
-  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
-  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
-  with $|\Pi_{xx}|$ being the greatest lower bound of $x$, the only
-  consistent partitioning $\mathcal{P}$ is a set of partitions
-  $P_{s\in S}$ such that each \process belongs to a logical partition
-  comprising its closest source: $\forall p \in P_{s}: \nexists
-  P_{s'}$ such that $|\Pi_{s'p}| < |\Pi_{sp}|$.
+  We associate each edge $\langle x, y \rangle \in E$ with a pair of
+  positive \underline{w}eights $w_{xy}$ and $w_{yx}$. The shortest
+  \underline{p}ath $\Pi_{xz}$ has a distance as a sum of weights
+  $\sum\{w_{pq} | \langle p, q \rangle \in \Pi_{xz}\} = |\Pi_{xz}|$
+  that is smaller than any other path, with $\Pi_{xx}$ being the
+  greatest lower bound of $x$. The only consistent partitioning is a
+  set of logical partitions $P_{s\in S}$ such that every \process
+  belongs to the partition of its closest source:
+  $\forall x \in P_{s}: \nexists P_{s'}$ such that
+  $|\Pi_{s'x}| < |\Pi_{sx}|$.
 \end{definition}
@@
 \begin{definition}[\label{def:forwarding}Forwarding]
-  A \process $p$ \underline{f}orwards a message $m$ by
-  \underline{s}ending it to its neighbors: $f_p(m) \implies \forall
-  \langle p, q\rangle \in E: \TODO{s_{pq}(m)}$.
+  A \process $x$ \underline{f}orwards a message $m$ by
+  \underline{s}ending it to its neighbors:
+  $f_x(m) \implies \forall \langle x, y\rangle \in E:
+  \TODO{s_{xy}(m)}$.
 \end{definition}
@@
     % 
-  Assuming reliable communication links ($s_{pq}(m) \iff \eventually
-  r_{qp}(m)$), \processes eventually reach consistent partitioning if
-  each \process delivers and forwards its best message among
-  \underline{r}eceived messages $R_p$, \ie the message $\alpha_s^d$
-  with the smallest distance $d$ to the source $s$ ($(\alpha_s^d = \min R_p)
-  \implies (d_p(\alpha_s^d) \wedge f_p(\TODO{\alpha_s^d}))$).
+    Assuming reliable communication links
+    ($s_{xy}(m) \iff \eventually r_{yx}(m)$), \processes eventually
+    reach consistent partitioning if each \process delivers its best
+    message among \underline{r}eceived messages $R_x$, and forwards
+    its best message among \underline{d}elivered messages $D_x$.
+    % , \ie
+    % the message $\alpha_s^d$ with the smallest distance $d$ to the
+    % source $s$
+    % ($(\alpha_s^d = \min R_x) \implies (d_x(\alpha_s^d) \wedge
+    % f_x(\TODO{\alpha_s^d}))$).
 \end{theorem}
@@
 \begin{proof}
-  When there are no sources, no \process receives, nor delivers hence
-  forwards any message. \Processes do not belong to any partition.
+  % When there are no sources, no \process receives, nor delivers hence
+  % forwards any message. \Processes do not belong to any partition.
 
   \noindent Whenever a \process $s$ becomes a source, it delivers its
-  own message $d_p(\alpha_{s})$. Whatever its set of received
+  own message $d_s(\alpha_{s})$. Whatever its set of received
   messages, its own partition $P_s$ becomes and remains its closest
-  partition $\alpha_{s} = \min D_p$ since $\forall p \neq s: |\Pi_{s
-    s}| < |\Pi_{s p}|$.
-
+  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq s: |\Pi_{s
+    s}| < |\Pi_{s x}|$.
+  %
   \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
   Since communication links are reliable, neighboring \processes
-  eventually receive such a notification $\forall \langle s, q \rangle
-  \in E \iff \eventually r_q(\alpha_{s}^{w_{pq}})$. Most importantly,
-  whatever the order of received messages, every \process $q$ in this
-  neighborhood such that there exists no closer source $s'$ than the
-  received one $s$, delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.
-
+  eventually receive such a notification
+  $\forall \langle s, y \rangle \in E \iff \eventually
+  r_y(\alpha_{s}^{d})$. Most importantly, whatever the order of
+  received messages, every \process $q$ in this neighborhood such that
+  there exists no closer source $s'$ than the received one $s$,
+  delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.
+  %
   \noindent They forward it and their respective neighbors eventually
@@
 \item weights are scalar values piggybacked in messages and
-  accumulated over forwardings,
+  accumulated over forwarding,
 \item \processes only add new partitions to the system,
@@
 to its sender (Line~\ref{line:accumulator}).  Figure~\ref{fig:add}
-illustrates its behavior on a system comprising 4 \processes $a$, $b$,
-$c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
-their partition.  They \NAMEB a notification \underline{a}dd message:
-$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
-the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
-send a message to each of their neighbors by accumulating the
-corresponding edge weight (see Line~\ref{line:accumulator}). In
-Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
-it improves its own partition distance, it keeps it and forwards it to
-its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
-$\alpha_{a}^{2}$, for it does not improve its partition
-distance. \Processes $c$ and $d$ will never acknowledge that
-Source~$a$ exists. Ultimately, \processes discard last transiting
-messages. Despite the obvious lack of traffic optimization, the system
-reaches consistent partitioning.
+illustrates the behavior of this algorithm on a system comprising 4
+\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
+become the sources of their partition.  They \NAMEB a notification
+\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
+initialize their own state with the lowest possible bound $0$ (see
+Line~\ref{line:lowestbound}), and send a message to each of their
+neighbors by accumulating the corresponding edge weight (see
+Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
+receives $\alpha_{d}^{1}$. Since it improves its own partition
+distance, it keeps it and forwards it to its neighbors. In
+Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
+does not improve its partition distance. \Processes $c$ and $d$ will
+never acknowledge that Source~$a$ exists. Ultimately, \processes
+discard last transiting messages. Despite the obvious lack of traffic
+optimization, the system reaches consistent partitioning.
 

### 2021-11-23 input/proposal.tex
not much

@@
 it underlines the transitive relevance of messages, thus a \process
-can stop forwarding messages as soon as its predicate becomes
+can stop \TODO{forwarding messages} as soon as its predicate becomes
 unverified.
@@
     ($s_{xy}(m) \iff \eventually r_{yx}(m)$), \processes eventually
-    reach consistent partitioning if each \process delivers its best
+    reach consistent partitioning if each \process delivers its \TODO{best}
     message among \underline{r}eceived messages $R_x$, and forwards
-    its best message among \underline{d}elivered messages $D_x$.
+    its \TODO{best} message among \underline{d}elivered messages $D_x$.
     % , \ie
@@
   messages, its own partition $P_s$ becomes and remains its closest
-  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq s: |\Pi_{s
-    s}| < |\Pi_{s x}|$.
+  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq
+  s: |\Pi_{s s}| < |\Pi_{s x}|$.
   %
@@
   there exists no closer source $s'$ than the received one $s$,
-  delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.
+  delivers it, since $w_{sq} < |\Pi_{s'q}|$.
   %
@@
   reaches all \processes belonging to $P_s$ at least through their
-  shortest paths: $\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
-  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s})$.  Since there
-  exists only one best sum of weights per \process that can never be
-  retracted, \processes eventually reach consistent partitioning.
+  shortest paths: $\smash{\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
+  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s}^{|\Pi_{sq'}|})}$.
+  Since there exists only one best sum of weights per \process that
+  can never be retracted, \processes eventually reach consistent
+  partitioning.
   %% /!\ not equivalence for there exists other implementations.
@@
 \end{inparaenum}
-For the sake of simplicity, a \process does not forward a notification
-to its sender (Line~\ref{line:accumulator}).  Figure~\ref{fig:add}
-illustrates the behavior of this algorithm on a system comprising 4
-\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
-become the sources of their partition.  They \NAMEB a notification
-\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
-initialize their own state with the lowest possible bound $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
-neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
-receives $\alpha_{d}^{1}$. Since it improves its own partition
-distance, it keeps it and forwards it to its neighbors. In
-Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
-does not improve its partition distance. \Processes $c$ and $d$ will
-never acknowledge that Source~$a$ exists. Ultimately, \processes
-discard last transiting messages. Despite the obvious lack of traffic
-optimization, the system reaches consistent partitioning.
+For the sake of simplicity and to remove obvious loops, a \process
+does not forward a notification to its sender
+(Line~\ref{line:accumulator}).  Figure~\ref{fig:add} illustrates the
+behavior of this algorithm on a system comprising 4 \processes $a$,
+$b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
+their partition.  They \NAMEB a notification \underline{a}dd message:
+$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
+the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
+send a message to each of their neighbors by accumulating the
+corresponding edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
+it improves its own partition distance, it keeps it and forwards it to
+its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
+$\alpha_{a}^{2}$, for it does not improve its partition
+distance. \Processes $c$ and $d$ will never acknowledge that
+Source~$a$ exists. Ultimately, \processes discard last transiting
+messages. Despite the obvious lack of traffic optimization, the system
+reaches consistent partitioning.
 

### 2021-11-23 input/proposal.tex
meow

@@
 
+\begin{definition}[\label{def:dcp}\underline{D}ynamic
+  \underline{c}onsistent \underline{p}artitioning (DCP)]
+  Dynamic consistent partitioning is consistent partitioning where
+  \processes can join or leave the set of sources at any time.
+\end{definition}
+
 \input{input/figsimplerproblem.tex}
@@
 
-\begin{definition}[\label{def:lwo}Message staleness]
+\begin{definition}[\label{def:lwo}Stale messages]
   Only the latest message of a \process matters. A message $m$ conveys
   \underline{s}tale control information if the \process that broadcast
-  $m$ later broadcast another message $m'$: $\mathcal{S}(m)
-  = \exists m': b_p(m) \rightarrow b_p(m')$.
-
-  %% When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
-  %% b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
-  %% $\nexists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
-  %% convey \emph{\underline{s}tale} control information: $S(m)$.
+  $m$ later broadcast another message $m'$:
+  $\mathcal{S}(m) = \exists m': b_x(m) \rightarrow b_x(m')$.
 \end{definition}
@@
 \processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
-receive the messages in the order of their sending ($s_{pq}(m)
-\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
-Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
-their respective notification message to $b$. In
+receive the messages in the order of their sending
+($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
+r_q(m')$). In Figure~\ref{fig:problemA}, both $a$ and $c$ become
+sources, sending their respective notification message to $b$. In
 Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
@@
 inconsistency by blocking farther but up-to-date messages from actual
-sources. The system needs to purge all stale messages to guarantee
-consistent partitioning.
+sources. To reach consistent partitioning, \processes need
+\begin{inparaenum}[(i)]
+\item to purge all stale messages which
+\item implies detecting possibly blocking conditions
+\item by acknowledging the last partition of neighbors.
+\end{inparaenum}
 
 \begin{definition}[\label{def:purge}Message purge]
-  A system \underline{p}urges a message $\TODO{\mathcal{P}}(m)$ when every
-  \node $q$ that delivered $m$ eventually delivers another message
-  $m'$ never followed by the delivery of the former message $m$:
-  $d_q(m) \implies \exists m': \eventually (d_q(m)
-  \rightarrow d_q(m') \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
+  A system \underline{p}urges a message when every \node $q$ that
+  delivered $m$ eventually delivers another message $m'$ never
+  followed by the delivery of the former message $m$:
+  $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
+  \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
 \end{definition}
+
+\begin{lemma}[FB $\wedge$ \underline{F}orwarding of \underline{S}tale
+  (FS) $\implies$ Detection]
+  \TODO{meow!}
+\end{lemma}
+
+\TODO{rest to rework\ldots}
 
@@
 
+\begin{definition}[\TODO{DCP $\implies$ eventual acknowledgement of at
+    least one source}]
+\end{definition}
+
 To provide lazy partitioning, \emph{gateway} \nodes that link

### 2021-11-24 input/proposal.tex
meow proposal

@@
     % 
-    Assuming reliable communication links
-    ($s_{xy}(m) \iff \eventually r_{yx}(m)$), \processes eventually
-    reach consistent partitioning if each \process delivers its \TODO{best}
-    message among \underline{r}eceived messages $R_x$, and forwards
-    its \TODO{best} message among \underline{d}elivered messages $D_x$.
+    Assuming reliable communication links ($s_{xy}(m) \iff \eventually
+    r_{yx}(m)$), and a total order on messages ($<$), \processes
+    eventually reach consistent partitioning if each \process delivers
+    its best message among \underline{r}eceived messages $R_x$, and
+    forwards its best message among \underline{d}elivered messages
+    $D_x$.
     % , \ie
@@
 
-  \noindent Whenever a \process $s$ becomes a source, it delivers its
-  own message $d_s(\alpha_{s})$. Whatever its set of received
-  messages, its own partition $P_s$ becomes and remains its closest
-  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq
-  s: |\Pi_{s s}| < |\Pi_{s x}|$.
+  \noindent \TODO{use total order ($<$) and sets $R_p D_p$} Whenever a
+  \process $s$ becomes a source, it delivers its own message
+  $d_s(\alpha_{s})$. Whatever its set of received messages, its own
+  partition $P_s$ becomes and remains its closest partition
+  $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq s:
+  |\Pi_{s s}| < |\Pi_{s x}|$.
   %
@@
 two partitions initially exist: $P_a$ and $P_d$ that respectively
-include $\{a\}$, and $\{b, c, d\}$. In Figure~\ref{fig:delA},
-\Process~$a$ deletes its partition. It notifies all neighboring
-\processes~--~here only \Process~$b$~-- that may belong to its
-partition using \NAMEB. Upon receipt, \Process~$b$ discards the delete
-notification $\delta_a$ since $\delta_a$ does not target the former's
-partition $P_d$. \Process~$b$ sends its own best partition
-$\alpha_d^3$ that may be the best for \Process~$a$. Eventually, every
-\process belongs to Partition $P_d$. In this scenario, they reach
-consistent partitioning.
+include $\{a\}$, and $\{b, c, d\}$. In Figure~\ref{fig:delA}, $a$
+deletes its partition. It notifies all neighboring \processes~--~here
+only $b$~-- that may belong to its partition using \NAMEB. Upon
+receipt, $b$ discards the delete notification $\delta_a$ since
+$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
+sends its own best partition $\alpha_d^3$ that may be the best for
+$a$. Eventually, every \process belongs to Partition $P_d$. In this
+scenario, they reach consistent partitioning.
 
@@
 
-\begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
+\begin{definition}[Happens-before ($\rightarrow$)~\cite{lamport1978time}]
   The transitive, irreflexive, and antisymmetric happens-before
@@
 \begin{definition}[\label{def:lwo}Stale messages]
-  Only the latest message of a \process matters. A message $m$ conveys
-  \underline{s}tale control information if the \process that broadcast
-  $m$ later broadcast another message $m'$:
-  $\mathcal{S}(m) = \exists m': b_x(m) \rightarrow b_x(m')$.
+  Only the latest broadcast of a \node matters.  A message $m$ conveys
+  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
+  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
+  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
+  \process only sends messages that it assumes up-to-date:
+  $s_x(\alpha_s) \implies \delta_s \not\in R_x$.
 \end{definition}
 
-Unfortunately, stale control information as stated in
-Definition~\ref{def:lwo} may impair the propagation of both
+\begin{definition}[\label{def:fd}\underline{F}orwarding of
+    \underline{s}taleness (FS)]
+  %
+  To \NAMEB staleness, a \process $x$ delivers and forwards a received
+  staleness notification if it is not yet delivered and targets its
+  best delivered message: $\delta_s \in R_x \setminus D_x \wedge
+  \alpha_s = \min D_x \TODO{\implies} d_x(\delta_s) \wedge
+  f_x(\delta_s)$.
+\end{definition}
+
+\begin{definition}[\label{def:echo}\underline{E}chos (E)]
+  A \process $x$ that receives a stale message sends back --~or
+  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
+  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
+  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in D_x$.
+\end{definition}
+
+\begin{lemma}[\label{def:fbfse}FB+FS+E $\centernot\implies$ DCP]
+  Forwarding of best up-to-date, forwarding of staleness, and echos is
+  not sufficient to guarantee dynamic consistent partitioning.
+\end{lemma}
+
+\begin{proof}
+Stale control information as stated in Definition~\ref{def:lwo} may
+impair the propagation of both
 \begin{inparaenum}[(i)]
@@
 \processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
-receive the messages in the order of their sending
-($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
-r_q(m')$). In Figure~\ref{fig:problemA}, both $a$ and $c$ become
-sources, sending their respective notification message to $b$. In
+receive the messages in the order of their sending ($s_{pq}(m)
+\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
+Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
+their respective notification message to $b$. In
 Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
@@
 discards $\delta_a$, for its best partition does not match the deleted
-one. It produces an echo but since $\alpha_c^3$ is already transiting
-towards $a$, we simplify it. Finally, Figure~\ref{fig:problemD} shows
-that eventually, $c$ stays in the deleted partition $P_a$ for not
-having received $\delta_a$ that $b$ blocked earlier. As a cascading
-effect, not only $c$ wrongfully believes that it belongs to $a$'s
-partition when $a$ already deleted it, but it could contribute to its
-inconsistency by blocking farther but up-to-date messages from actual
-sources. To reach consistent partitioning, \processes need
+one. We simplify the echo since $\alpha_c^3$ is already transiting
+towards $a$. Finally, Figure~\ref{fig:problemD} shows that eventually,
+$c$ stays in the deleted partition $P_a$ for not having received
+$\delta_a$ that $b$ blocked earlier. \end{proof}
+
+As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
+wrongfully believes that it belongs to $a$'s partition when $a$
+already deleted it, but it could contribute to its inconsistency by
+blocking farther but up-to-date messages from actual sources. To reach
+consistent partitioning, \processes need
 \begin{inparaenum}[(i)]
-\item to purge all stale messages which
-\item implies detecting possibly blocking conditions
-\item by acknowledging the last partition of neighbors.
+\item to detect possibly blocking conditions 
+\item to purge all stale messages from the system
+\item enabling up-to-date notifications to eventually reach every
+  \process.
 \end{inparaenum}
+
+\begin{lemma}[\label{def:detection}Detector existence]
+  Assuming a chain of \process $[x,\ldots, z]$ that delivered a
+  message $\alpha_x$, if $x$ deletes its partition, either all
+  \processes eventually deliver $\delta_s$, or a \process along the
+  chain detects the blocking of the delete notification
+\end{lemma}
+
+\TODO{But cannot just delete. It must be deleted only downstream, see
+  figure.}
 
@@
 
-\begin{lemma}[FB $\wedge$ \underline{F}orwarding of \underline{S}tale
-  (FS) $\implies$ Detection]
-  \TODO{meow!}
+\begin{lemma}[FB $\wedge$ FD $\implies$ Detection] \TODO{meow!}
 \end{lemma}
+
+\begin{definition}[\TODO{Assuming purge, echo => DCP}]
+\end{definition}
 

### 2021-11-24 input/proposal.tex
better plan?

@@
 
+\input{input/figadd.tex}
+
 \begin{definition}[\label{def:partitioning}Partitioning]
@@
 
-\input{input/figadd.tex}
-
 \begin{proof}
@@
 $b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
-their partition.  They \NAMEB a notification \underline{a}dd message:
-$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
-the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
-send a message to each of their neighbors by accumulating the
-corresponding edge weight (see Line~\ref{line:accumulator}). In
-Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
-it improves its own partition distance, it keeps it and forwards it to
-its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
-$\alpha_{a}^{2}$, for it does not improve its partition
-distance. \Processes $c$ and $d$ will never acknowledge that
-Source~$a$ exists. Ultimately, \processes discard last transiting
-messages. Despite the obvious lack of traffic optimization, the system
-reaches consistent partitioning.
+their partition.  They \NAMEB a notification \TODO{\underline{a}dd
+  message}: $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
+state with the lowest possible bound $0$ (see
+Line~\ref{line:lowestbound}), and send a message to each of their
+neighbors by accumulating the corresponding edge weight (see
+Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
+receives $\alpha_{d}^{1}$. Since it improves its own partition
+distance, it keeps it and forwards it to its neighbors. In
+Figure~\ref{fig:addD}, $b$ discards $\alpha_{a}^{2}$, for it does not
+improve its partition distance. \Processes $c$ and $d$ will never
+acknowledge that Source~$a$ exists. Ultimately, \processes discard
+last transiting messages. Despite the obvious lack of traffic
+optimization, the system reaches consistent partitioning.
 
@@
 
-\input{input/figdel.tex}
-
 At any time, a source can revoke its status of source by executing a
@@
 choose another partition to belong to.
+
+\input{input/figsimplerproblem.tex} %% positioning
+
+\input{input/figdel.tex}
 
@@
 \end{definition}
-
-\input{input/figsimplerproblem.tex}
 
@@
 
-\input{input/figundoproblem.tex}
-
 \begin{definition}[Happens-before ($\rightarrow$)~\cite{lamport1978time}]
@@
 
+\input{input/figundoproblem.tex}
+
 \begin{definition}[\label{def:fd}\underline{F}orwarding of
@@
 
-\begin{definition}[\label{def:echo}\underline{E}chos (E)]
-  A \process $x$ that receives a stale message sends back --~or
+\begin{definition}[\label{def:echo}FB$^+$: echos] FB where a
+  \process $x$ that receives a stale message sends back --~or
   echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
@@
 
-\begin{lemma}[\label{def:fbfse}FB+FS+E $\centernot\implies$ DCP]
-  Forwarding of best up-to-date, forwarding of staleness, and echos is
-  not sufficient to guarantee dynamic consistent partitioning.
+\begin{lemma}[\label{def:fbfse}FB$^+ \wedge$ FS $\centernot\implies$ DCP]
+  Forwarding best up-to-date, forwarding staleness, and echoing is not
+  sufficient to guarantee dynamic consistent partitioning.
 \end{lemma}
@@
 $c$ stays in the deleted partition $P_a$ for not having received
-$\delta_a$ that $b$ blocked earlier. \end{proof}
+$\delta_a$ that $b$ blocked earlier. The system does not reach
+consistent partitioning. \end{proof}
 
@@
 \item to purge all stale messages from the system
-\item enabling up-to-date notifications to eventually reach every
-  \process.
+\item enabling up-to-date notifications to eventually echo back to
+  every \process.
 \end{inparaenum}
 
-\begin{lemma}[\label{def:detection}Detector existence]
-  Assuming a chain of \process $[x,\ldots, z]$ that delivered a
-  message $\alpha_x$, if $x$ deletes its partition, either all
-  \processes eventually deliver $\delta_s$, or a \process along the
-  chain detects the blocking of the delete notification
+\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
+  Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
+  message $\alpha_x$, when $x$ deletes its partition, either every
+  \process of this chain eventually deliver $\delta_s$, or a \process
+  along the chain detects the blocking of the staleness notification
+  $\delta_s$.
 \end{lemma}
 
-\TODO{But cannot just delete. It must be deleted only downstream, see
-  figure.}
-
-\begin{definition}[\label{def:purge}Message purge]
-  A system \underline{p}urges a message when every \node $q$ that
-  delivered $m$ eventually delivers another message $m'$ never
-  followed by the delivery of the former message $m$:
-  $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
-  \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
-\end{definition}
-
-\begin{lemma}[FB $\wedge$ FD $\implies$ Detection] \TODO{meow!}
-\end{lemma}
-
-\begin{definition}[\TODO{Assuming purge, echo => DCP}]
-\end{definition}
-
-\TODO{rest to rework\ldots}
-
-\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
-    \underline{D}ynamic \underline{c}onsistent
-    \underline{p}artitioning (DCP)]
-%
-  When a \process can \texttt{Add} and \texttt{Del}ete its partition,
-  to ensure consistent partitioning, eventual forwarding of best
-  (Theorem~\ref{theo:efb}) additionally requires
-\begin{inparaenum}[(i)]
-\item eventual purging of stale messages ($\mathcal{S}(m) \implies
-  \mathcal{P}(m)$), then
-\item the eventual forwarding of best (Theorem~\ref{theo:efb}).
-\end{inparaenum}
-\end{theorem}
-
 \begin{proof}
-  %% To reach consistent partitioning, the last message delivered by
-  %% every process is not stale and comes from its respective best
-  %% source: $d(m)$
-  Assuming EFB as default propagation behavior where \processes
-  deliver and forward the best sum of weights they received. We must
-  prove that despite stale messages, the last delivery of every
-  \process is the message that followed the shortest path to its
-  closest source.
-  \begin{asparadesc}
-  \item [EFB without Purge:] A \process may receive messages in such
-    an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
-    \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
-    not forward messages required by other \processes ($\delta_a$ for
-    $c$). The last delivery of some nodes may be wrong (\eg in
-    Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
-    % \Processes never
-    % reach consistent partitioning.
-    %
-    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
-    %% $b$ precludes itself and subsequent \processes such as $c$ of
-    %% delivering the message from their respective best source
-    %% $a$. \Process $b$ received and delivered a message from a
-    %% partition that has since then been deleted but with a better sum
-    %% of weights than newly received ones ($\alpha_d^y <
-    %% \alpha_a^{x'}$). It forever discards such a message
-    %% $\alpha_a^{x'}$.
-  \item [Purge not followed by EFB:]
-    %% also transiting messages
-    Assuming that every \process removes control information as soon
-    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
-    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
-    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
-    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
-    up-to-date messages propagation. However, even in such settings,
-    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
-    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
-    may never receive again, hence deliver and forward a message that
-    was received and discarded before ($\alpha_c^{y}$). When such a
-    message contains its best up-to-date partition, a \process may
-    never end up in its best partition.
-    %    Therefore, \processes do not reach
-    % consistent partitioning.
-  \item [Purge then EFB:] Assuming the eventual and definitive removal
-    of stale messages at each \process ($S(\alpha_a) \implies
-    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
-    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
-    removal eventually triggers the forwarding of best delivered
-    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
-    \processes may deliver other stale messages that will be 
-    eventually removed to never be delivered again. In the worst case,
-    all \processes deliver and remove all stale messages to ultimately
-    deliver and forward only up-to-date messages ($\eventually d_c(m')
-    \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
-    eventually deliver and forward their best up-to-date message.
-
-    %% upon receipt of such $\alpha_y$, either the \process already
-    %% delivered its removal and it does
-
-    %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
-    %% S(\alpha_y)$)
-
-    %% eventually every \process only delivers and forwards up-to-date
-    %% messages, or no message at all
-
-    %% , every \process eventually delivers and forwards the best
-    %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.
-
-    %% Removing \emph{forever} all such stale messages about
-    %% deleted partitions would allow \processes to propagate their best
-    %% up-to-date partition again, eventually reaching consistent
-    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
-  \end{asparadesc}
-  Using EFB$^+$, \processes reach consistent partitioning together
-  even under dynamic partitioning settings where \nodes can
-  \texttt{Add} and \texttt{Del}ete their partition.
-\end{proof}
-
-%% Figure removed as it's kind of redundant with preceding figure that
-%% depicts the issue
-%% \begin{figure} 
-%%   \centering\input{input/figproofA.tex}
-%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
-%%       stop other $\alpha$ messages from reaching all \processes ($b$
-%%       and $c$) that require it along the shortest path. Consistent
-%%       partitioning requires eventual purging of stale messages (see
-%%       Figure~\ref{fig:proofB}).}
-%% \end{figure}
-
-The main challenge consists in implementing a purging mechanism that
-ensures the \emph{eventual and definitive} removal of stale control
-information. One could guarantee consistent partitioning by always
-propagating the $\delta$ messages corresponding to the $\alpha$
-messages it propagated before. In Figure~\ref{fig:problem}, it means
-that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
-its neighbors \Process~$c$ and \Process~$d$ may need the notification
-of removal $\delta_a$ if it exists. However, such a solution also
-implies that \processes generate traffic not only related to their
-current partition, but also related to partitions they belonged to in
-the past. This would prove overly expensive in dynamic systems where
-\processes join and leave the system, create and delete partitions, at
-any time.  Instead, we propose to use the delivery order at each
-\process to detect possible inconsistencies and solve them.
-%% Together, \processes eventually remove all stale control information
-%% (transiting messages and local states) of the system leaving room for
-%% propagation of messages about up-to-date partitions.
-
-%% \input{input/figproof.tex}
-
-%% Figure~\ref{fig:proof} depicts the issues with staleness and message
-%% orderings. In Figure~\ref{fig:proofA}, the shortest path from any
-%% source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
-%% a stale $\alpha_d^{0.5}$ without knowing. When it receives
-%% $\alpha_a^1$, it discards it, for it assumes that downstream \processes
-%% are more interested in $\alpha_d^{0.5}$. To reach consistent
-%% partitioning, \Process $b$ first needs to purge its current partition
-%% to later accept that of its current actual shortest path:
-%% $\alpha_a^1$.
-
-%% \noindent Figure~\ref{fig:proofB} shows that removing stale control
-%% information is even more complex. The removal must reach all \processes
-%% of the previous shortest path going from $d$ to $b''$. Label I' shows
-%% the most obvious issue where \Process $e$ changed partition for a
-%% better but stale $\alpha_f$. Since it can remember its previous
-%% deliveries, it could still forward $\delta_d$ for the sake of
-%% consistency. However, this would lead to every \process forwarding
-%% every $\delta$ they ever delivered. Such protocol's overhead would
-%% depend on past partitioning instead of current one. Label III shows
-%% the issue when the blocking partition is already known to be stale at
-%% \Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
-%% $e$. However, it cannot deliver it, for it would break last win order.
-%% \Process $b'$ may be in an inconsistent state. Label IV shows the
-%% corollary issue: \Process $b''$ delivered a message from a \process that
-%% may be inconsistent without knowing it.
-
-\begin{theorem}[\label{theo:threephase}Three-phase purge]
-  Three phases are sufficient to eventually purge the system from
-  stale control information:
-  \begin{inparaenum}[(i)]
-  \item propagation of delete notifications,
-  \item detection of possibly blocked deletion, and
-  \item propagation of delete notifications that were possibly blocked.
-  \end{inparaenum}
-\end{theorem}
-
-%% \begin{figure}
-%%   \centering\input{input/figproofB.tex}
-%%   \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
-%%     messages from reaching \processes with the corresponding
-%%     partition. Consistent partitioning requires that all \processes
-%%     propagate $\delta$ messages as often as possible (I); detect
-%%     possible inconsistencies when parents' $\alpha$ messages
-%%     contradict history or state (II); notify \processes of possible
-%%     inconsistencies (III).}
-%% \end{figure}
-
-\begin{proof}
-  We must prove that every \process that delivered a stale $\alpha_X$
-  eventually delivers a better $\alpha_Y$, or delivers a removal
-  notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
-  issue of purging in scenarios involving concurrent operations.
+  \TODO{Rework this!} We must prove that every \process that delivered
+  a stale $\alpha_X$ eventually delivers a better $\alpha_Y$, or
+  delivers a removal notification of $\alpha_X$.
+  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
+  involving concurrent operations.
 
@@
   delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
-  %
-  %% Some \processes may have delivered messages about other partitions
-  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
-  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
-  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
-  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
-  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
-  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
-  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
-  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
-  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
-  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
-  %% the chain: $d$ is a child of \processes that delivered messages
-  %% about $P_Y$.
-  %
+\end{proof}
+
+To reach dynamic consistent partitioning, the detecting \process must
+broadcast a message notifying the \emph{possible} staleness of its
+last delivered and forwarded message to its \emph{downstream}
+\processes. Indeed, Figure~\ref{fig:undoproblem} shows that from
+detector's perspective, the chain of events is identical, yet it must
+react to the worst case scenario where $\delta_a$ existed and was
+blocked. \TODO{More about figure.} \TODO{Challenging?}
+
+\begin{definition}[FS$^+$: forwarding staleness downstream]
+  To further reduce the scope  \TODO{Meow.}
+\end{definition}
+
+\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{D} \implies \textup{DCP}$]
+  \TODO{Miaw}
+\end{theorem}
+
+\begin{proof}
+  \TODO{Meow.}
+\end{proof}
+
+%% \begin{definition}[\label{def:purge}Message purge]
+%%   A system \underline{p}urges a message when every \node $q$ that
+%%   delivered $m$ eventually delivers another message $m'$ never
+%%   followed by the delivery of the former message $m$:
+%%   $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
+%%   \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
+%% \end{definition}
+
+%% \begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
+%%     \underline{D}ynamic \underline{c}onsistent
+%%     \underline{p}artitioning (DCP)]
+%% %
+%%   When a \process can \texttt{Add} and \texttt{Del}ete its partition,
+%%   to ensure consistent partitioning, eventual forwarding of best
+%%   (Theorem~\ref{theo:efb}) additionally requires
+%% \begin{inparaenum}[(i)]
+%% \item eventual purging of stale messages ($\mathcal{S}(m) \implies
+%%   \mathcal{P}(m)$), then
+%% \item the eventual forwarding of best (Theorem~\ref{theo:efb}).
+%% \end{inparaenum}
+%% \end{theorem}
+
+%% \begin{proof}
+%%   %% To reach consistent partitioning, the last message delivered by
+%%   %% every process is not stale and comes from its respective best
+%%   %% source: $d(m)$
+%%   Assuming EFB as default propagation behavior where \processes
+%%   deliver and forward the best sum of weights they received. We must
+%%   prove that despite stale messages, the last delivery of every
+%%   \process is the message that followed the shortest path to its
+%%   closest source.
 %%   \begin{asparadesc}
-  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
-  %%   like $a$.  By propagating from \process to \process the
-  %%   corresponding $\delta_X$ message, these \processes purge
-  %%   $\alpha_X$.
-  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
-  %%   latter does not target its current partition.
-  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
-  %%   that $[a, b, c, d]$ is solved and that it does not require to
-  %%   purge $P_Y$.}
-  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
-  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
-  %%   it detects $b$ is its parent, and possibly blocked any delta with
-  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
-  %%   sure, $\Delta$
-  %
-  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
-  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
-  %%   \Process~$b$ that do not directly suffer from the non-delivery of
-  %%   $\delta_X$. They need to purge their own $P_Y$ if need
-  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
-  %%   one following \process will receive.
-  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
-  %%   such as \Process~$c$ that do not belong to the preceding category,
-  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
-  %%   forwarding guarantees that they receive $\alpha_Y$, which
-  %%   contradicts their history or state. In such a case, the detecting
-  %%   \processes purge their own $\alpha_X$. The detecting \processes
-  %%   must also notify subsequent \processes that their current
-  %%   partition \emph{may be} deleted. Indeed their parent may have
-  %%   blocked the corresponding $\delta$ messages and subsequent
-  %%   \processes must purge their possibly stale state, for the sake of
-  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
-  %%   their proximity to $\delta_X$ messages.
-  %%   % the uncertainty of a $\delta$ message.
-  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
-  %%   their parent:] \Processes such as \Process~$d$ that have
-  %%   $\alpha_X$ but preceding delivered messages are not
-  %%   important. Such \processes must trust detecting \processes by
-  %%   delivering and forwarding $\Delta_X$. It is worth noting that
-  %%   these messages are subject to all aforementioned blocking
-  %%   conditions, but are also solved by aforementioned mechanisms.
+%%   \item [EFB without Purge:] A \process may receive messages in such
+%%     an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
+%%     \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
+%%     not forward messages required by other \processes ($\delta_a$ for
+%%     $c$). The last delivery of some nodes may be wrong (\eg in
+%%     Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
+%%     % \Processes never
+%%     % reach consistent partitioning.
+%%     %
+%%     %% Figure~\ref{fig:proofA} depicts the generic case where a \process
+%%     %% $b$ precludes itself and subsequent \processes such as $c$ of
+%%     %% delivering the message from their respective best source
+%%     %% $a$. \Process $b$ received and delivered a message from a
+%%     %% partition that has since then been deleted but with a better sum
+%%     %% of weights than newly received ones ($\alpha_d^y <
+%%     %% \alpha_a^{x'}$). It forever discards such a message
+%%     %% $\alpha_a^{x'}$.
+%%   \item [Purge not followed by EFB:]
+%%     %% also transiting messages
+%%     Assuming that every \process removes control information as soon
+%%     as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
+%%     \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
+%%     anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
+%%     \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
+%%     up-to-date messages propagation. However, even in such settings,
+%%     depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
+%%     r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
+%%     may never receive again, hence deliver and forward a message that
+%%     was received and discarded before ($\alpha_c^{y}$). When such a
+%%     message contains its best up-to-date partition, a \process may
+%%     never end up in its best partition.
+%%     %    Therefore, \processes do not reach
+%%     % consistent partitioning.
+%%   \item [Purge then EFB:] Assuming the eventual and definitive removal
+%%     of stale messages at each \process ($S(\alpha_a) \implies
+%%     (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
+%%     d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
+%%     removal eventually triggers the forwarding of best delivered
+%%     messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
+%%     \processes may deliver other stale messages that will be 
+%%     eventually removed to never be delivered again. In the worst case,
+%%     all \processes deliver and remove all stale messages to ultimately
+%%     deliver and forward only up-to-date messages ($\eventually d_c(m')
+%%     \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
+%%     eventually deliver and forward their best up-to-date message.
+
+%%     %% upon receipt of such $\alpha_y$, either the \process already
+%%     %% delivered its removal and it does
+
+%%     %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
+%%     %% S(\alpha_y)$)
+
+%%     %% eventually every \process only delivers and forwards up-to-date
+%%     %% messages, or no message at all
+
+%%     %% , every \process eventually delivers and forwards the best
+%%     %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.
+
+%%     %% Removing \emph{forever} all such stale messages about
+%%     %% deleted partitions would allow \processes to propagate their best
+%%     %% up-to-date partition again, eventually reaching consistent
+%%     %% partitioning together, as stated by Theorem~\ref{theo:bef}.
 %%   \end{asparadesc}
-  %% Propagation~I terminates: a \process does not deliver a $\delta$
-  %% message if it has already delivered it. Propagation~III terminates: a
-  %% \process does not deliver a looping message.  
-  % ; and since \processes forward the messages they deliver, upstream
-  % \processes eventually receive and may deliver messages detected as
-  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
-  % receives $\delta_f$ from \Process~$b'$.
-  %% Three-phase purge ensures that all \processes of the system
-  %% eventually removes stale messages, leaving room for best eventual
-  %% forwarding of up-to-date messages.
-  %
-  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
-  % delete to $e$, it will solve the inconsistency.}
-  %
-  %% In the meantime, \processes that still belong to a partition can
-  %% propagate their respective last $\alpha$ message, and reach
-    %% consistent partitioning.
-\end{proof}
+%%   Using EFB$^+$, \processes reach consistent partitioning together
+%%   even under dynamic partitioning settings where \nodes can
+%%   \texttt{Add} and \texttt{Del}ete their partition.
+%% \end{proof}
+
+%% Figure removed as it's kind of redundant with preceding figure that
+%% depicts the issue
+%% \begin{figure} 
+%%   \centering\input{input/figproofA.tex}
+%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
+%%       stop other $\alpha$ messages from reaching all \processes ($b$
+%%       and $c$) that require it along the shortest path. Consistent
+%%       partitioning requires eventual purging of stale messages (see
+%%       Figure~\ref{fig:proofB}).}
+%% \end{figure}
+
+%% The main challenge consists in implementing a purging mechanism that
+%% ensures the \emph{eventual and definitive} removal of stale control
+%% information.
+%% One could guarantee consistent partitioning by always
+%% propagating the $\delta$ messages corresponding to the $\alpha$
+%% messages it propagated before. In Figure~\ref{fig:problem}, it means
+%% that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
+%% its neighbors \Process~$c$ and \Process~$d$ may need the notification
+%% of removal $\delta_a$ if it exists. However, such a solution also
+%% implies that \processes generate traffic not only related to their
+%% current partition, but also related to partitions they belonged to in
+%% the past. This would prove overly expensive in dynamic systems where
+%% \processes join and leave the system, create and delete partitions, at
+%% any time.  Instead, we propose to use the delivery order at each
+%% \process to detect possible inconsistencies and solve them.
+%% Together, \processes eventually remove all stale control information
+%% (transiting messages and local states) of the system leaving room for
+%% propagation of messages about up-to-date partitions.
+
+%% \input{input/figproof.tex}
+
+%% Figure~\ref{fig:proof} depicts the issues with staleness and message
+%% orderings. In Figure~\ref{fig:proofA}, the shortest path from any
+%% source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
+%% a stale $\alpha_d^{0.5}$ without knowing. When it receives
+%% $\alpha_a^1$, it discards it, for it assumes that downstream \processes
+%% are more interested in $\alpha_d^{0.5}$. To reach consistent
+%% partitioning, \Process $b$ first needs to purge its current partition
+%% to later accept that of its current actual shortest path:
+%% $\alpha_a^1$.
+
+%% \noindent Figure~\ref{fig:proofB} shows that removing stale control
+%% information is even more complex. The removal must reach all \processes
+%% of the previous shortest path going from $d$ to $b''$. Label I' shows
+%% the most obvious issue where \Process $e$ changed partition for a
+%% better but stale $\alpha_f$. Since it can remember its previous
+%% deliveries, it could still forward $\delta_d$ for the sake of
+%% consistency. However, this would lead to every \process forwarding
+%% every $\delta$ they ever delivered. Such protocol's overhead would
+%% depend on past partitioning instead of current one. Label III shows
+%% the issue when the blocking partition is already known to be stale at
+%% \Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
+%% $e$. However, it cannot deliver it, for it would break last win order.
+%% \Process $b'$ may be in an inconsistent state. Label IV shows the
+%% corollary issue: \Process $b''$ delivered a message from a \process that
+%% may be inconsistent without knowing it.
+
+%% \begin{theorem}[\label{theo:threephase}Three-phase purge]
+%%   Three phases are sufficient to eventually purge the system from
+%%   stale control information:
+%%   \begin{inparaenum}[(i)]
+%%   \item propagation of delete notifications,
+%%   \item detection of possibly blocked deletion, and
+%%   \item propagation of delete notifications that were possibly blocked.
+%%   \end{inparaenum}
+%% \end{theorem}
+
+%% \begin{figure}
+%%   \centering\input{input/figproofB.tex}
+%%   \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
+%%     messages from reaching \processes with the corresponding
+%%     partition. Consistent partitioning requires that all \processes
+%%     propagate $\delta$ messages as often as possible (I); detect
+%%     possible inconsistencies when parents' $\alpha$ messages
+%%     contradict history or state (II); notify \processes of possible
+%%     inconsistencies (III).}
+%% \end{figure}
+
+%% \begin{proof}
+%%   We must prove that every \process that delivered a stale $\alpha_X$
+%%   eventually delivers a better $\alpha_Y$, or delivers a removal
+%%   notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
+%%   issue of purging in scenarios involving concurrent operations.
+
+%%   (i) If every \process (such as $a$) starting from the source
+%%   delivers and forwards a removal notification $\delta_X$ when their
+%%   last delivery is $\alpha_X$, then every such \process eventually
+%%   delivers the removal notification $\delta_X$ except \processes (such
+%%   as $b$) that delivered $\alpha_X$ from a \process that delivered a
+%%   message from another partition $\alpha_Y$ since then.
+
+%%   These exceptions eventually receive and deliver $\alpha_Y$ since
+%%   $\alpha_Y$ is better than $\alpha_X$ through this path, except if
+%%   they already received and delivered the removal notification of
+%%   $P_Y$ (such as $c$). These \processes may never receive hence
+%%   deliver $\delta_X$, and may never receive hence deliver a better
+%%   message than $\alpha_X$. They need an additional mechanism to
+%%   eventually purge $\alpha_X$ that cannot rely on the eventual purging
+%%   of $P_Y$ at \processes like $b$, to avoid deadlocks.
+
+%%   (ii) Assuming that every \process keeps an history of its past
+%%   deliveries, \processes (such as $c$) can detect the inconsistency,
+%%   since they receive from their parent an already deleted partition
+%%   $P_Y$. This notification means that the parent discards any
+%%   $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
+%%   $\delta_X$ exists, it discards it. To ensure the purge of stale
+%%   messages, a detecting \process must assume the worst case that such
+%%   $\delta_X$ exists, and send another kind of message, noted $\Delta$,
+%%   that notify the possible removal of $P_X$.
+
+%%   (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
+%%   but whose parent is neither inconsistent (like $b$) nor receiving
+%%   $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
+%%   \process, either directly or transitively, for such a child \process
+%%   ($d$) trusts the possible removal of $P_X$ by delivering and
+%%   forwarding such $\Delta$. $\Delta$ suffers from identical blocking
+%%   conditions (between $b$ and $c$) than $\delta$, leading to the same
+%%   solutions of detection and propagation of $\Delta$. Eventually,
+%%   every \process whose last delivery is $\alpha_X$ receives and
+%%   delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
+%%   %
+%%   %% Some \processes may have delivered messages about other partitions
+%%   %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
+%%   %% messages about $P_Y$.  For \processes such as $b$, the last delivery
+%%   %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
+%%   %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
+%%   %% as $c$, the last delivery is $\alpha_X$, and they delivered the
+%%   %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
+%%   %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
+%%   %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
+%%   %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
+%%   %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
+%%   %% the chain: $d$ is a child of \processes that delivered messages
+%%   %% about $P_Y$.
+%%   %
+%%   %% \begin{asparadesc}
+%%   %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
+%%   %%   like $a$.  By propagating from \process to \process the
+%%   %%   corresponding $\delta_X$ message, these \processes purge
+%%   %%   $\alpha_X$.
+%%   %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
+%%   %%   latter does not target its current partition.
+%%   %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
+%%   %%   that $[a, b, c, d]$ is solved and that it does not require to
+%%   %%   purge $P_Y$.}
+%%   %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
+%%   %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
+%%   %%   it detects $b$ is its parent, and possibly blocked any delta with
+%%   %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
+%%   %%   sure, $\Delta$
+%%   %
+%%   %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
+%%   %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
+%%   %%   \Process~$b$ that do not directly suffer from the non-delivery of
+%%   %%   $\delta_X$. They need to purge their own $P_Y$ if need
+%%   %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
+%%   %%   one following \process will receive.
+%%   %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
+%%   %%   such as \Process~$c$ that do not belong to the preceding category,
+%%   %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
+%%   %%   forwarding guarantees that they receive $\alpha_Y$, which
+%%   %%   contradicts their history or state. In such a case, the detecting
+%%   %%   \processes purge their own $\alpha_X$. The detecting \processes
+%%   %%   must also notify subsequent \processes that their current
+%%   %%   partition \emph{may be} deleted. Indeed their parent may have
+%%   %%   blocked the corresponding $\delta$ messages and subsequent
+%%   %%   \processes must purge their possibly stale state, for the sake of
+%%   %%   consistency.  We note such a notification $\Delta_X$ to emphasize
+%%   %%   their proximity to $\delta_X$ messages.
+%%   %%   % the uncertainty of a $\delta$ message.
+%%   %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
+%%   %%   their parent:] \Processes such as \Process~$d$ that have
+%%   %%   $\alpha_X$ but preceding delivered messages are not
+%%   %%   important. Such \processes must trust detecting \processes by
+%%   %%   delivering and forwarding $\Delta_X$. It is worth noting that
+%%   %%   these messages are subject to all aforementioned blocking
+%%   %%   conditions, but are also solved by aforementioned mechanisms.
+%%   %% \end{asparadesc}
+%%   %% Propagation~I terminates: a \process does not deliver a $\delta$
+%%   %% message if it has already delivered it. Propagation~III terminates: a
+%%   %% \process does not deliver a looping message.  
+%%   % ; and since \processes forward the messages they deliver, upstream
+%%   % \processes eventually receive and may deliver messages detected as
+%%   % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
+%%   % receives $\delta_f$ from \Process~$b'$.
+%%   %% Three-phase purge ensures that all \processes of the system
+%%   %% eventually removes stale messages, leaving room for best eventual
+%%   %% forwarding of up-to-date messages.
+%%   %
+%%   %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
+%%   % delete to $e$, it will solve the inconsistency.}
+%%   %
+%%   %% In the meantime, \processes that still belong to a partition can
+%%   %% propagate their respective last $\alpha$ message, and reach
+%%     %% consistent partitioning.
+%% \end{proof}
 
@@
 
-\begin{definition}[\TODO{Lazy DCP}]
-
+\begin{definition}[Lazy dynamic consistent partitioning (LDCP)]
+  \TODO{If there exists at least a source in a network, its nodes must
+    belong to the partition of the closest partition in adjacent
+    networks. Otherwise, nodes must eventually belong to no
+    partition.}
 \end{definition}
 
-\begin{definition}[\TODO{DCP $\implies$ eventual acknowledgement of at
-    least one source}]
-\end{definition}
+\begin{lemma}[Source existence]
+  When a system becomes quiescent, DCP guarantees that every \process
+  eventually acknowledges the existence or non-existence of a source
+  in its system.
+\end{lemma}
+
+\begin{proof}
+  By design, obvious.
+\end{proof}
 

### 2021-11-25 input/proposal.tex
wip

@@
 
-%% \begin{definition}[Edge infrastructure]
-%%   An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
-%%   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
-%%   \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
-%%   \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
-%%     k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
-%%   \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
-%% \end{definition}
-
 \begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
@@
 can stop \TODO{forwarding messages} as soon as its predicate becomes
-unverified.
-%For instance, a \process
-%from Paris could scoped broadcast messages to all \processes in
-%Paris. This requires \processes to store and maintain their city
-%location in their local state. \Processes stop delivering and
-%forwarding their received messages when they come from a different
-%city.  In another instance, a \process from Paris could scoped
-%broadcast messages to all \processes in Paris plus neighboring
-%cities. This requires \processes to overload forwarded messages the
-%first time they reach another city. The predicate checks if messages
-%already reached two distinct cities before delivery. Similarly to
-%uniform reliable broadcast, scoped broadcast implementations expose
-%different trade-offs on space, time, and communication.
-%
-We use \NAMEB to efficiently modify the state of each \process
-depending on the partitions that exist in the system.
+unverified.  We use \NAMEB to efficiently modify the state of each
+\process depending on the partitions that exist in the system.
 
@@
   Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
-  message $\alpha_x$, when $x$ deletes its partition, either every
-  \process of this chain eventually deliver $\delta_s$, or a \process
-  along the chain detects the blocking of the staleness notification
-  $\delta_s$.
+  message $\alpha_x$ with $\alpha_x = \min D_z$, when $x$ deletes its
+  partition, either every \process of this chain eventually delivers
+  $\delta_x$, or a \process along the chain detects the blocking of
+  the staleness notification $\delta_s$.
 \end{lemma}
@@
 \begin{proof}
-  \TODO{Rework this!} We must prove that every \process that delivered
-  a stale $\alpha_X$ eventually delivers a better $\alpha_Y$, or
-  delivers a removal notification of $\alpha_X$.
-  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
-  involving concurrent operations.
+  Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that
+  $\alpha_x \min D$
+
+  Assuming $[x, x_2, \ldots, x_k, y, y_1, y_2, \ldots, y_\ell, z]$,
 
@@
   V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
-  \ldots G_n\}, \mathcal{E} \rangle$.
+  \ldots G_n\}, \mathcal{E} \rangle$. A \emph{gateway} $g$ is a
+  \process with at least one link towards another network: $\langle g,
+  \_ \rangle \in \mathcal{E}$.
 \end{definition}
@@
 
+To enable LDCP in an Edge infrastructure, we use the property provided
+by DCP in an autonomous system to all its \processes and among others,
+to its gateways.
+
 \begin{lemma}[Source existence]
@@
 \begin{proof}
-  By design, obvious.
+  By design, \TODO{obvious}.
 \end{proof}
 
-To provide lazy partitioning, \emph{gateway} \nodes that link
-autonomous systems together must acknowledge if there exists a source
-in their network.
+The gateways become responsible for the flooding or the stopping of
+notifications foreign to their respective network. They must
+differentiate between local and global notifications. Local
+notifications provide both \begin{inparaenum}[(i)]
+\item local source existence, and
+\item closest local source in the network
+\end{inparaenum}; while global notifications only improve on closest global sources,
+\ie it does not need to propagate when the foreign source is farther
+than the local one.
 
-Must differentiate local from global when they cross the gates.
+\begin{definition}[\underline{B}roadcasting of \underline{u}ninterested (BU)]
+  \TODO{meow}
+\end{definition}
 
-% \NAME enables indexing the closest replica of each \process without
-% flooding the whole network when a new replica appears or disappears.
-% Nevertheless, every node must partake in the indexing of each
-% content. When the networks accounts for billions of content, this
-% raises scalability issues. Inspired by the Internet topology that
-% comprises tens of thousands of interconnected autonomous systems
-% serving billions of , we want to further
-% lock-down traffic by leveraging the edges of networks as barriers, and
-% enable on-demand indexing.
+\TODO{Blocking condition local global remains.}
 

### 2021-11-25 input/proposal.tex
meow meow

@@
 
-\begin{definition}[\label{def:fd}\underline{F}orwarding of
+\begin{definition}[\label{def:fs}\underline{F}orwarding of
     \underline{s}taleness (FS)]
@@
 \begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
-  Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
-  message $\alpha_x$ with $\alpha_x = \min D_z$, when $x$ deletes its
-  partition, either every \process of this chain eventually delivers
-  $\delta_x$, or a \process along the chain detects the blocking of
-  the staleness notification $\delta_s$.
+  Assuming a chain of delivery of $\alpha_x$ from \Process~$x$ to
+  \Process~$z$ with $\alpha_x = \min D_z$, if $x$ broadcasts a
+  staleness notification $\delta_x$, either $z$ eventually delivers
+  it, or a \process of the delivery chain $[x,\ldots, z]$ eventually
+  detects its blocking.
+  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
 \end{lemma}
@@
 \begin{proof}
+  %% knowing that b_p delta is sufficient to say that processes will
+  %% receive delta or detect blocking
+  (A) Assuming a chain of delivery $C = [x, \ldots, z]$ of $\alpha_x$ with
+  $\forall p \in C: \alpha_x = \min D_p$, and assuming
+  $d_x(\delta_x)$, then with forwarding of staleness
+  (Definition~\ref{def:fs}), $f_{C[k]}(\delta_x) \implies \eventually
+  d_{C[k+1]}(\delta_x)$ except if $\delta_x \in D_{C[k+1]}$ which
+  means that $C[k+1]$ already delivered and forwarded $\delta_x$
+  following another such a chain of delivery. Therefore, $z$
+  eventually receives, hence delivers $\delta_x$.
+
+  \noindent Assuming a chain of delivery $C = [x, \ldots, z]$ of
+  $\alpha_x$ with $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$,
+  then by (A), the staleness notification reaches a \process $y\in C$
+
+  every \process eventually deliver and forward $\delta_x$ either
+  following the same chain, except if $\alpha_x$ is already stale
+  which
+
+  $z$ does not receive, hence deliver $\delta_x$ when a \process $y$
+  between $x$ and $z$ stops forwarding $\delta_x$ because it delivered
+  another message $\alpha_s$ with $\alpha_s < \alpha_x$.
+
   Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that

### 2021-11-25 input/proposal.tex
reworking proof of detection

@@
   %% receive delta or detect blocking
-  (A) Assuming a chain of delivery $C = [x, \ldots, z]$ of $\alpha_x$ with
-  $\forall p \in C: \alpha_x = \min D_p$, and assuming
+  (A) Assuming a chain of delivery $C = [x, \ldots, z]$ of $\alpha_x$
+  with $\forall p \in C: \alpha_x = \min D_p$, and assuming
   $d_x(\delta_x)$, then with forwarding of staleness
@@
 
-  \noindent Assuming a chain of delivery $C = [x, \ldots, z]$ of
-  $\alpha_x$ with $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$,
-  then by (A), the staleness notification reaches a \process $y\in C$
+  \noindent (B) Assuming a chain of delivery $C = [x, \ldots, z]$ of
+  $\alpha_x$ with at least $\alpha_x = \min D_z$, and assuming
+  $d_x(\delta_x)$, then by (A), the staleness notification reaches a
+  \process $C[k]$. By Definition~\ref{def:fs}, the fowarding stops
+  when $C[k]$ already delivered $\delta_x$ (covered by (A)) or
+  delivered a better message $\alpha_x \neq \alpha_y = \min
+  D_{C[k]}$. The latter means that $\eventually d_{C[k+1]}(\alpha_y)$
+  or $\delta_y \in D_{C[k+1]}$.
 
-  every \process eventually deliver and forward $\delta_x$ either
-  following the same chain, except if $\alpha_x$ is already stale
-  which
+  %% (i) If every \process (such as $a$) starting from the source
+  %% delivers and forwards a removal notification $\delta_X$ when their
+  %% last delivery is $\alpha_X$, then every such \process eventually
+  %% delivers the removal notification $\delta_X$ except \processes (such
+  %% as $b$) that delivered $\alpha_X$ from a \process that delivered a
+  %% message from another partition $\alpha_Y$ since then.
 
-  $z$ does not receive, hence deliver $\delta_x$ when a \process $y$
-  between $x$ and $z$ stops forwarding $\delta_x$ because it delivered
-  another message $\alpha_s$ with $\alpha_s < \alpha_x$.
+  %% These exceptions eventually receive and deliver $\alpha_Y$ since
+  %% $\alpha_Y$ is better than $\alpha_X$ through this path, except if
+  %% they already received and delivered the removal notification of
+  %% $P_Y$ (such as $c$). These \processes may never receive hence
+  %% deliver $\delta_X$, and may never receive hence deliver a better
+  %% message than $\alpha_X$. They need an additional mechanism to
+  %% eventually purge $\alpha_X$ that cannot rely on the eventual purging
+  %% of $P_Y$ at \processes like $b$, to avoid deadlocks.
 
-  Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that
-  $\alpha_x \min D$
+  %% (ii) Assuming that every \process keeps an history of its past
+  %% deliveries, \processes (such as $c$) can detect the inconsistency,
+  %% since they receive from their parent an already deleted partition
+  %% $P_Y$. This notification means that the parent discards any
+  %% $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
+  %% $\delta_X$ exists, it discards it. To ensure the purge of stale
+  %% messages, a detecting \process must assume the worst case that such
+  %% $\delta_X$ exists, and send another kind of message, noted $\Delta$,
+  %% that notify the possible removal of $P_X$.
 
-  Assuming $[x, x_2, \ldots, x_k, y, y_1, y_2, \ldots, y_\ell, z]$,
-
-  (i) If every \process (such as $a$) starting from the source
-  delivers and forwards a removal notification $\delta_X$ when their
-  last delivery is $\alpha_X$, then every such \process eventually
-  delivers the removal notification $\delta_X$ except \processes (such
-  as $b$) that delivered $\alpha_X$ from a \process that delivered a
-  message from another partition $\alpha_Y$ since then.
-
-  These exceptions eventually receive and deliver $\alpha_Y$ since
-  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
-  they already received and delivered the removal notification of
-  $P_Y$ (such as $c$). These \processes may never receive hence
-  deliver $\delta_X$, and may never receive hence deliver a better
-  message than $\alpha_X$. They need an additional mechanism to
-  eventually purge $\alpha_X$ that cannot rely on the eventual purging
-  of $P_Y$ at \processes like $b$, to avoid deadlocks.
-
-  (ii) Assuming that every \process keeps an history of its past
-  deliveries, \processes (such as $c$) can detect the inconsistency,
-  since they receive from their parent an already deleted partition
-  $P_Y$. This notification means that the parent discards any
-  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
-  $\delta_X$ exists, it discards it. To ensure the purge of stale
-  messages, a detecting \process must assume the worst case that such
-  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
-  that notify the possible removal of $P_X$.
-
-  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
-  but whose parent is neither inconsistent (like $b$) nor receiving
-  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
-  \process, either directly or transitively, for such a child \process
-  ($d$) trusts the possible removal of $P_X$ by delivering and
-  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
-  conditions (between $b$ and $c$) than $\delta$, leading to the same
-  solutions of detection and propagation of $\Delta$. Eventually,
-  every \process whose last delivery is $\alpha_X$ receives and
-  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
+  %% (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
+  %% but whose parent is neither inconsistent (like $b$) nor receiving
+  %% $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
+  %% \process, either directly or transitively, for such a child \process
+  %% ($d$) trusts the possible removal of $P_X$ by delivering and
+  %% forwarding such $\Delta$. $\Delta$ suffers from identical blocking
+  %% conditions (between $b$ and $c$) than $\delta$, leading to the same
+  %% solutions of detection and propagation of $\Delta$. Eventually,
+  %% every \process whose last delivery is $\alpha_X$ receives and
+  %% delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
 \end{proof}

### 2021-11-25 input/proposal.tex
minor

@@
 
-\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
-  Assuming a chain of delivery of $\alpha_x$ from \Process~$x$ to
-  \Process~$z$ with $\alpha_x = \min D_z$, if $x$ broadcasts a
-  staleness notification $\delta_x$, either $z$ eventually delivers
-  it, or a \process of the delivery chain $[x,\ldots, z]$ eventually
+\begin{lemma}[\label{def:detection}$\textup{FB}^+ \wedge \textup{FS}
+  \implies$ \underline{D}etector existence (D)]
+  Assuming $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on
+  $\pi_{xz}$ of $\alpha_x$ with $\alpha_x = \min D_z$, if $x$
+  broadcasts a staleness notification $\delta_x$, either $z$
+  eventually delivers it, or a \process $y\in\pi_{xz}$ eventually
   detects its blocking.
@@
   %% receive delta or detect blocking
-  (A) Assuming a chain of delivery $C = [x, \ldots, z]$ of $\alpha_x$
-  with $\forall p \in C: \alpha_x = \min D_p$, and assuming
-  $d_x(\delta_x)$, then with forwarding of staleness
-  (Definition~\ref{def:fs}), $f_{C[k]}(\delta_x) \implies \eventually
-  d_{C[k+1]}(\delta_x)$ except if $\delta_x \in D_{C[k+1]}$ which
-  means that $C[k+1]$ already delivered and forwarded $\delta_x$
+  (A) Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
+  $\alpha_x$ with $\forall y \in \pi_{xz}: \alpha_x = \min D_y$, and
+  assuming $d_x(\delta_x)$, then with forwarding of staleness
+  (Definition~\ref{def:fs}),
+  $f_{\pi_{xz}[k]}(\delta_x) \implies \eventually
+  d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in D_{\pi_{xz}[k+1]}$ which
+  means that $\pi_{xz}[k+1]$ already delivered and forwarded $\delta_x$
   following another such a chain of delivery. Therefore, $z$
@@
 
-  \noindent (B) Assuming a chain of delivery $C = [x, \ldots, z]$ of
-  $\alpha_x$ with at least $\alpha_x = \min D_z$, and assuming
-  $d_x(\delta_x)$, then by (A), the staleness notification reaches a
-  \process $C[k]$. By Definition~\ref{def:fs}, the fowarding stops
-  when $C[k]$ already delivered $\delta_x$ (covered by (A)) or
-  delivered a better message $\alpha_x \neq \alpha_y = \min
-  D_{C[k]}$. The latter means that $\eventually d_{C[k+1]}(\alpha_y)$
-  or $\delta_y \in D_{C[k+1]}$.
-
+  \noindent (B) Assuming a chain of delivery
+  $\pi_{xz} = [x, \ldots, z]$ of $\alpha_x$ with at least
+  $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$, then by (A),
+  the staleness notification reaches a \process $\pi_{xz}[k]$. By
+  Definition~\ref{def:fs}, the fowarding stops when $\pi_{xz}[k]$
+  already delivered $\delta_x$ (covered by (A)) or delivered a better
+  message $\alpha_x \neq \alpha_y = \min D_{\pi_{xz}[k]}$. The latter
+  means that $\eventually d_{\pi_{xz}[k+1]}(\alpha_y)$ or
+  $\delta_y \in D_{\pi_{xz}[k+1]}$.
+  %
   %% (i) If every \process (such as $a$) starting from the source
@@
   %% message from another partition $\alpha_Y$ since then.
-
+  %
   %% These exceptions eventually receive and deliver $\alpha_Y$ since
@@
   %% of $P_Y$ at \processes like $b$, to avoid deadlocks.
-
+  %
   %% (ii) Assuming that every \process keeps an history of its past
@@
   %% that notify the possible removal of $P_X$.
-
+  %
   %% (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,

### 2021-11-26 input/proposal.tex
reworkd proof of detection

@@
 
-\begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
+\begin{theorem}[\label{theo:fb}\underline{F}orwarding of \underline{B}est (FB)
     $\implies\eventually$CP]
@@
 
-\begin{definition}[\label{def:echo}FB$^+$: echos] FB where a
+\begin{definition}[\label{def:fbplus}FB$^+$: echos] FB where a
   \process $x$ that receives a stale message sends back --~or
@@
 
-\begin{lemma}[\label{def:fbfse}FB$^+ \wedge$ FS $\centernot\implies$ DCP]
+\begin{lemma}[\label{lem:fbfse}FB$^+ \wedge$ FS $\centernot\implies$ DCP]
   Forwarding best up-to-date, forwarding staleness, and echoing is not
@@
   broadcasts a staleness notification $\delta_x$, either $z$
-  eventually delivers it, or a \process $y\in\pi_{xz}$ eventually
-  detects its blocking.
+  eventually delivers it, or a \process $y$ in such a chain of
+  delivery $\pi_{xz}'$ eventually detects its blocking.
   % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
@@
   $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$, then by (A),
-  the staleness notification reaches a \process $\pi_{xz}[k]$. By
-  Definition~\ref{def:fs}, the fowarding stops when $\pi_{xz}[k]$
-  already delivered $\delta_x$ (covered by (A)) or delivered a better
-  message $\alpha_x \neq \alpha_y = \min D_{\pi_{xz}[k]}$. The latter
-  means that $\eventually d_{\pi_{xz}[k+1]}(\alpha_y)$ or
-  $\delta_y \in D_{\pi_{xz}[k+1]}$.
+  the staleness notification reaches a \process $ y = \pi_{xz}[k]$. By
+  Definition~\ref{def:fs}, the fowarding stops when $y$ already
+  delivered $\delta_x$ ($\delta_x \in D_y$ covered by (A)) or
+  delivered a better message $\alpha_s = \min D_y$ with
+  $\alpha_s \neq \alpha_x$. With $y'=\pi_{xz}[k+1]$, forwarding of
+  best (Definition~\ref{def:fbplus}) implies three possible outcomes:
+  \begin{enumerate}[(i)]
+  \item $\alpha_{s'} = \min D_{y'}$ with $\alpha_{s'} \neq \alpha_x$
+    hence $y' \iff y$ which leaves two possible outcomes:
+  \item
+    $r_{y'}(\alpha_s) \wedge \alpha_x = \min D_{y'} \wedge \alpha_x <
+    \alpha_s$ which means that a shorter path of delivery $\pi_{xz}'$
+    exists that either forwards appropriate staleness notifications
+    (A) or detects its possible blocking:
+  \item
+    $r_{y'}(\alpha_s) \wedge \delta_s \in D_{y'} \wedge \alpha_x =
+    \min D_{y'}$ which detects a possible blocking of
+    $\delta_x$. Without global knowledge, $y'$ assumes it belongs to
+    the shortest and only path of delivery of $\alpha_x$
+    ($\pi_{xy'} \subseteq \Pi_{xz}$) thus it does not further delegate
+    the detection to another \process.
+  \end{enumerate} \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed
   %

### 2021-11-26 input/proposal.tex
text after proof to motivate fs plus

@@
 
-\begin{lemma}[\label{def:detection}$\textup{FB}^+ \wedge \textup{FS}
+\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
   \implies$ \underline{D}etector existence (D)]
@@
 
-To reach dynamic consistent partitioning, the detecting \process must
-broadcast a message notifying the \emph{possible} staleness of its
-last delivered and forwarded message to its \emph{downstream}
-\processes. Indeed, Figure~\ref{fig:undoproblem} shows that from
-detector's perspective, the chain of events is identical, yet it must
-react to the worst case scenario where $\delta_a$ existed and was
-blocked. \TODO{More about figure.} \TODO{Challenging?}
+Proof of Lemma~\ref{lem:detector} shows that there exists false
+positive in the blocking detection: $\delta_x$ may not exist but $y'$
+still receives $\alpha_s$ after the delivery of $\delta_s$ from the
+path it delivered $\alpha_x$. Figure~\ref{fig:undoproblem} highlights
+this behavior. In Figure~\ref{fig:undoproblemB}, $a$ does not delete
+its partition. In Figure~\ref{fig:undoproblemD} and because of \NAMEB,
+$c$ received the same series of messages as in
+Figure~\ref{fig:problemD}. Yet, $c$ must assume the existence of
+$\delta_a$ and act accordingly by forcing the staleness of its best
+delivered message and disseminate this information to its neighbors.
+To avoid flooding the system with false positive staleness
+notifications, we propose to reduce the scope of staleness
+notifications by including only downstream \processes. In
+Figure~\ref{fig:undoproblemD}, false positives would not affect $a$
+and $b$.
 

### 2021-11-29 input/proposal.tex
reorder again, mb better, todiscuss

@@
 the system by allowing only subsets of \processes to reach lazy
-consistent partitioning. \TODO{It shows that it only needs what?}
+consistent partitioning. This improvement only requires \processes to
+know which of their neighbors belong to their own network.
 
@@
   Dynamic consistent partitioning is consistent partitioning where
-  \processes can join or leave the set of sources at any time.
+  \processes can join or leave the set of sources at any \TODO{time}.
 \end{definition}
@@
   the staleness notification reaches a \process $ y = \pi_{xz}[k]$. By
-  Definition~\ref{def:fs}, the fowarding stops when $y$ already
+  Definition~\ref{def:fs}, the forwarding stops when $y$ already
   delivered $\delta_x$ ($\delta_x \in D_y$ covered by (A)) or
@@
 
-\begin{definition}[FS$^+$: forwarding staleness downstream]
-  To further reduce the scope  \TODO{Meow.}
+\begin{definition}[\label{def:fsplus}$\textup{FS}^+$: forwarding
+  staleness downstream]
+  To \NAMEB staleness downstream, a node $x$ delivers and forwards a
+  received staleness notification if it is not yet delivered and it
+  comes from the path of delivery of its best up-to-date delivered
+  message. \TODO{more.}
 \end{definition}
 
+It is worth noting that forwarding of staleness as stated in
+Definition~\ref{def:fs} becomes a specific case of
+Definition~\ref{def:fsplus} where the source itself forwards a
+staleness notification downstream. The notification must reach all
+\processes in its partition since the source has no \processes
+upstream, and belongs to the delivery path of all \processes that
+delivered this message.
+
 \begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{D} \implies \textup{DCP}$]
-  \TODO{Miaw}
+  A protocol guarantees dynamic consistent partitioning if it
+  implements forwarding of best up-to-date messages with echos,
+  forwarding of staleness messages downstream, and detection of
+  possible blocking of staleness notifications.
 \end{theorem}
@@
 
-%% \begin{definition}[\label{def:purge}Message purge]
-%%   A system \underline{p}urges a message when every \node $q$ that
-%%   delivered $m$ eventually delivers another message $m'$ never
-%%   followed by the delivery of the former message $m$:
-%%   $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
-%%   \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
-%% \end{definition}
+\begin{algorithm}
+  \input{input/algoascast.tex}
+  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
+\end{algorithm}
 
-%% \begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
-%%     \underline{D}ynamic \underline{c}onsistent
-%%     \underline{p}artitioning (DCP)]
-%% %
-%%   When a \process can \texttt{Add} and \texttt{Del}ete its partition,
-%%   to ensure consistent partitioning, eventual forwarding of best
-%%   (Theorem~\ref{theo:efb}) additionally requires
+\TODO{Rework this to remove repetitions. Since implem is close from
+  section.}
+
+Algorithm~\ref{algo:ascast} shows the instructions implementing
+dynamic consistent partitioning. To implement staleness, each \process
+maintains a vector of versions that associates the respective known
+local counter of each known source, or has-been source. Its size
+increases linearly with the number of sources that the \process has
+ever known, which is the number of \processes in the system
+$\mathcal{O}(V)$ in the worst case.  Nevertheless, following the
+principles of scoped broadcast, we expect that every \process only
+acknowledges a small subset of sources.  In addition, each message
+carries the identifier and counter of each \node that forwarded
+it. Again, following the principles of scoped broadcast, we expect
+that versioned paths remain small. Using these data structures, each
+\process delivers and forwards only new messages that improve their
+best known partition (see Line~\ref{line:ascast_improve}).
+
+This vector of versions constitutes a summary of known progress of
+other \nodes. It discards stale messages and it enables detecting
+possible blocking of staleness notifications: the current best
+partition comes from a neighbor that just delivered a stale message
+(see Line~\ref{line:ascast_detect}). Figure~\ref{fig:problem} shows
+that such a behavior may hide a delete notification. The detecting
+\process must act to reflect this possible change: all \processes
+whose last message comes from the detecting \process must remove it
+and accept the competition of other \processes. Since this behavior is
+similar to that of source deletion, we implement it in a similar way.
+
+A \process that removes its self-appointed status of source, or
+detects a possible inconsistency, increments its local counter and
+disseminates a delete notification message $\delta_{s, c}$
+piggybacking its identifier $s$ and counter $c$. Any \process that
+receives such delete notification delivers and forwards it if its best
+message contains the has-been source or detector associated to a lower
+counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
+messages to quickly reach every downstream \process.
+
+As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
+not only requires eventual purging of stale messages, but also the
+retrieval of the best up-to-date partitions.  In that regard, $\delta$
+messages have a dual use: since they already reach the borders of
+their partition by design, they trigger a competition when reaching
+bordering.  When a \process receives a delete notification from a
+neighbor $q$ but does not deliver it, it assumes that the just
+received $\delta$ message purged possibly stale messages, creating a
+gap that its own best partition could help fill. Consequently, it
+sends to $q$ its own best $\alpha$ message (see
+Line~\ref{line:ascast_echo}).
+
+\begin{algorithm}[h]
+  \input{input/algoedges.tex}
+  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
+\end{algorithm}
+
+Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
+dynamic networks where \processes can join, leave, or crash at any
+time. Removing a \process is equivalent to removing all its edges, and
+adding a \process is equivalent to add as many edges as necessary.
+Adding an edge between two \processes may only improve the shortest
+path of one of these \processes. Therefore, it triggers a competition
+between the two \processes. If one or the other \process improves, the
+propagation of $\alpha$ messages operates normally.  Removing an edge
+between two \processes may invalidate the shortest path of one of
+involved \processes plus downstream \processes. As a side effect,
+removing an edge may also impair the propagation of a partition
+delete. To implement this behavior, \NAME uses its implementation of
+$\delta$ messages. This enables \NAME even in dynamic networks subject
+to physical partitioning.
+
+%% \NAME guarantees dynamic consistent partitioning by making extensive
+%% use of \process-to-\process communications. It requires
 %% \begin{inparaenum}[(i)]
-%% \item eventual purging of stale messages ($\mathcal{S}(m) \implies
-%%   \mathcal{P}(m)$), then
-%% \item the eventual forwarding of best (Theorem~\ref{theo:efb}).
+%% \item purging stale control information, hence propagating $\delta$
+%%   messages; and
+%% \item retrieving the closest source, hence propagating $\alpha$
+%%   messages.
 %% \end{inparaenum}
-%% \end{theorem}
-
-%% \begin{proof}
-%%   %% To reach consistent partitioning, the last message delivered by
-%%   %% every process is not stale and comes from its respective best
-%%   %% source: $d(m)$
-%%   Assuming EFB as default propagation behavior where \processes
-%%   deliver and forward the best sum of weights they received. We must
-%%   prove that despite stale messages, the last delivery of every
-%%   \process is the message that followed the shortest path to its
-%%   closest source.
-%%   \begin{asparadesc}
-%%   \item [EFB without Purge:] A \process may receive messages in such
-%%     an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
-%%     \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
-%%     not forward messages required by other \processes ($\delta_a$ for
-%%     $c$). The last delivery of some nodes may be wrong (\eg in
-%%     Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
-%%     % \Processes never
-%%     % reach consistent partitioning.
-%%     %
-%%     %% Figure~\ref{fig:proofA} depicts the generic case where a \process
-%%     %% $b$ precludes itself and subsequent \processes such as $c$ of
-%%     %% delivering the message from their respective best source
-%%     %% $a$. \Process $b$ received and delivered a message from a
-%%     %% partition that has since then been deleted but with a better sum
-%%     %% of weights than newly received ones ($\alpha_d^y <
-%%     %% \alpha_a^{x'}$). It forever discards such a message
-%%     %% $\alpha_a^{x'}$.
-%%   \item [Purge not followed by EFB:]
-%%     %% also transiting messages
-%%     Assuming that every \process removes control information as soon
-%%     as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
-%%     \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
-%%     anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
-%%     \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
-%%     up-to-date messages propagation. However, even in such settings,
-%%     depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
-%%     r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
-%%     may never receive again, hence deliver and forward a message that
-%%     was received and discarded before ($\alpha_c^{y}$). When such a
-%%     message contains its best up-to-date partition, a \process may
-%%     never end up in its best partition.
-%%     %    Therefore, \processes do not reach
-%%     % consistent partitioning.
-%%   \item [Purge then EFB:] Assuming the eventual and definitive removal
-%%     of stale messages at each \process ($S(\alpha_a) \implies
-%%     (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
-%%     d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
-%%     removal eventually triggers the forwarding of best delivered
-%%     messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
-%%     \processes may deliver other stale messages that will be 
-%%     eventually removed to never be delivered again. In the worst case,
-%%     all \processes deliver and remove all stale messages to ultimately
-%%     deliver and forward only up-to-date messages ($\eventually d_c(m')
-%%     \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
-%%     eventually deliver and forward their best up-to-date message.
-
-%%     %% upon receipt of such $\alpha_y$, either the \process already
-%%     %% delivered its removal and it does
-
-%%     %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
-%%     %% S(\alpha_y)$)
-
-%%     %% eventually every \process only delivers and forwards up-to-date
-%%     %% messages, or no message at all
-
-%%     %% , every \process eventually delivers and forwards the best
-%%     %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.
-
-%%     %% Removing \emph{forever} all such stale messages about
-%%     %% deleted partitions would allow \processes to propagate their best
-%%     %% up-to-date partition again, eventually reaching consistent
-%%     %% partitioning together, as stated by Theorem~\ref{theo:bef}.
-%%   \end{asparadesc}
-%%   Using EFB$^+$, \processes reach consistent partitioning together
-%%   even under dynamic partitioning settings where \nodes can
-%%   \texttt{Add} and \texttt{Del}ete their partition.
-%% \end{proof}
-
-%% Figure removed as it's kind of redundant with preceding figure that
-%% depicts the issue
-%% \begin{figure} 
-%%   \centering\input{input/figproofA.tex}
-%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
-%%       stop other $\alpha$ messages from reaching all \processes ($b$
-%%       and $c$) that require it along the shortest path. Consistent
-%%       partitioning requires eventual purging of stale messages (see
-%%       Figure~\ref{fig:proofB}).}
-%% \end{figure}
-
-%% The main challenge consists in implementing a purging mechanism that
-%% ensures the \emph{eventual and definitive} removal of stale control
-%% information.
-%% One could guarantee consistent partitioning by always
-%% propagating the $\delta$ messages corresponding to the $\alpha$
-%% messages it propagated before. In Figure~\ref{fig:problem}, it means
-%% that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
-%% its neighbors \Process~$c$ and \Process~$d$ may need the notification
-%% of removal $\delta_a$ if it exists. However, such a solution also
-%% implies that \processes generate traffic not only related to their
-%% current partition, but also related to partitions they belonged to in
-%% the past. This would prove overly expensive in dynamic systems where
-%% \processes join and leave the system, create and delete partitions, at
-%% any time.  Instead, we propose to use the delivery order at each
-%% \process to detect possible inconsistencies and solve them.
-%% Together, \processes eventually remove all stale control information
-%% (transiting messages and local states) of the system leaving room for
-%% propagation of messages about up-to-date partitions.
-
-%% \input{input/figproof.tex}
-
-%% Figure~\ref{fig:proof} depicts the issues with staleness and message
-%% orderings. In Figure~\ref{fig:proofA}, the shortest path from any
-%% source to \Process $c$ is $[a, b, c]$. However, \Process $b$ still holds
-%% a stale $\alpha_d^{0.5}$ without knowing. When it receives
-%% $\alpha_a^1$, it discards it, for it assumes that downstream \processes
-%% are more interested in $\alpha_d^{0.5}$. To reach consistent
-%% partitioning, \Process $b$ first needs to purge its current partition
-%% to later accept that of its current actual shortest path:
-%% $\alpha_a^1$.
-
-%% \noindent Figure~\ref{fig:proofB} shows that removing stale control
-%% information is even more complex. The removal must reach all \processes
-%% of the previous shortest path going from $d$ to $b''$. Label I' shows
-%% the most obvious issue where \Process $e$ changed partition for a
-%% better but stale $\alpha_f$. Since it can remember its previous
-%% deliveries, it could still forward $\delta_d$ for the sake of
-%% consistency. However, this would lead to every \process forwarding
-%% every $\delta$ they ever delivered. Such protocol's overhead would
-%% depend on past partitioning instead of current one. Label III shows
-%% the issue when the blocking partition is already known to be stale at
-%% \Process $b'$. \Process $b''$ eventually receives $\alpha_f$ from
-%% $e$. However, it cannot deliver it, for it would break last win order.
-%% \Process $b'$ may be in an inconsistent state. Label IV shows the
-%% corollary issue: \Process $b''$ delivered a message from a \process that
-%% may be inconsistent without knowing it.
-
-%% \begin{theorem}[\label{theo:threephase}Three-phase purge]
-%%   Three phases are sufficient to eventually purge the system from
-%%   stale control information:
-%%   \begin{inparaenum}[(i)]
-%%   \item propagation of delete notifications,
-%%   \item detection of possibly blocked deletion, and
-%%   \item propagation of delete notifications that were possibly blocked.
-%%   \end{inparaenum}
-%% \end{theorem}
-
-%% \begin{figure}
-%%   \centering\input{input/figproofB.tex}
-%%   \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
-%%     messages from reaching \processes with the corresponding
-%%     partition. Consistent partitioning requires that all \processes
-%%     propagate $\delta$ messages as often as possible (I); detect
-%%     possible inconsistencies when parents' $\alpha$ messages
-%%     contradict history or state (II); notify \processes of possible
-%%     inconsistencies (III).}
-%% \end{figure}
-
-%% \begin{proof}
-%%   We must prove that every \process that delivered a stale $\alpha_X$
-%%   eventually delivers a better $\alpha_Y$, or delivers a removal
-%%   notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
-%%   issue of purging in scenarios involving concurrent operations.
-
-%%   (i) If every \process (such as $a$) starting from the source
-%%   delivers and forwards a removal notification $\delta_X$ when their
-%%   last delivery is $\alpha_X$, then every such \process eventually
-%%   delivers the removal notification $\delta_X$ except \processes (such
-%%   as $b$) that delivered $\alpha_X$ from a \process that delivered a
-%%   message from another partition $\alpha_Y$ since then.
-
-%%   These exceptions eventually receive and deliver $\alpha_Y$ since
-%%   $\alpha_Y$ is better than $\alpha_X$ through this path, except if
-%%   they already received and delivered the removal notification of
-%%   $P_Y$ (such as $c$). These \processes may never receive hence
-%%   deliver $\delta_X$, and may never receive hence deliver a better
-%%   message than $\alpha_X$. They need an additional mechanism to
-%%   eventually purge $\alpha_X$ that cannot rely on the eventual purging
-%%   of $P_Y$ at \processes like $b$, to avoid deadlocks.
-
-%%   (ii) Assuming that every \process keeps an history of its past
-%%   deliveries, \processes (such as $c$) can detect the inconsistency,
-%%   since they receive from their parent an already deleted partition
-%%   $P_Y$. This notification means that the parent discards any
-%%   $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
-%%   $\delta_X$ exists, it discards it. To ensure the purge of stale
-%%   messages, a detecting \process must assume the worst case that such
-%%   $\delta_X$ exists, and send another kind of message, noted $\Delta$,
-%%   that notify the possible removal of $P_X$.
-
-%%   (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
-%%   but whose parent is neither inconsistent (like $b$) nor receiving
-%%   $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
-%%   \process, either directly or transitively, for such a child \process
-%%   ($d$) trusts the possible removal of $P_X$ by delivering and
-%%   forwarding such $\Delta$. $\Delta$ suffers from identical blocking
-%%   conditions (between $b$ and $c$) than $\delta$, leading to the same
-%%   solutions of detection and propagation of $\Delta$. Eventually,
-%%   every \process whose last delivery is $\alpha_X$ receives and
-%%   delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
-%%   %
-%%   %% Some \processes may have delivered messages about other partitions
-%%   %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
-%%   %% messages about $P_Y$.  For \processes such as $b$, the last delivery
-%%   %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
-%%   %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
-%%   %% as $c$, the last delivery is $\alpha_X$, and they delivered the
-%%   %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
-%%   %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
-%%   %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
-%%   %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
-%%   %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
-%%   %% the chain: $d$ is a child of \processes that delivered messages
-%%   %% about $P_Y$.
-%%   %
-%%   %% \begin{asparadesc}
-%%   %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
-%%   %%   like $a$.  By propagating from \process to \process the
-%%   %%   corresponding $\delta_X$ message, these \processes purge
-%%   %%   $\alpha_X$.
-%%   %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
-%%   %%   latter does not target its current partition.
-%%   %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
-%%   %%   that $[a, b, c, d]$ is solved and that it does not require to
-%%   %%   purge $P_Y$.}
-%%   %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
-%%   %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
-%%   %%   it detects $b$ is its parent, and possibly blocked any delta with
-%%   %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
-%%   %%   sure, $\Delta$
-%%   %
-%%   %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
-%%   %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
-%%   %%   \Process~$b$ that do not directly suffer from the non-delivery of
-%%   %%   $\delta_X$. They need to purge their own $P_Y$ if need
-%%   %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
-%%   %%   one following \process will receive.
-%%   %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
-%%   %%   such as \Process~$c$ that do not belong to the preceding category,
-%%   %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
-%%   %%   forwarding guarantees that they receive $\alpha_Y$, which
-%%   %%   contradicts their history or state. In such a case, the detecting
-%%   %%   \processes purge their own $\alpha_X$. The detecting \processes
-%%   %%   must also notify subsequent \processes that their current
-%%   %%   partition \emph{may be} deleted. Indeed their parent may have
-%%   %%   blocked the corresponding $\delta$ messages and subsequent
-%%   %%   \processes must purge their possibly stale state, for the sake of
-%%   %%   consistency.  We note such a notification $\Delta_X$ to emphasize
-%%   %%   their proximity to $\delta_X$ messages.
-%%   %%   % the uncertainty of a $\delta$ message.
-%%   %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
-%%   %%   their parent:] \Processes such as \Process~$d$ that have
-%%   %%   $\alpha_X$ but preceding delivered messages are not
-%%   %%   important. Such \processes must trust detecting \processes by
-%%   %%   delivering and forwarding $\Delta_X$. It is worth noting that
-%%   %%   these messages are subject to all aforementioned blocking
-%%   %%   conditions, but are also solved by aforementioned mechanisms.
-%%   %% \end{asparadesc}
-%%   %% Propagation~I terminates: a \process does not deliver a $\delta$
-%%   %% message if it has already delivered it. Propagation~III terminates: a
-%%   %% \process does not deliver a looping message.  
-%%   % ; and since \processes forward the messages they deliver, upstream
-%%   % \processes eventually receive and may deliver messages detected as
-%%   % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
-%%   % receives $\delta_f$ from \Process~$b'$.
-%%   %% Three-phase purge ensures that all \processes of the system
-%%   %% eventually removes stale messages, leaving room for best eventual
-%%   %% forwarding of up-to-date messages.
-%%   %
-%%   %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
-%%   % delete to $e$, it will solve the inconsistency.}
-%%   %
-%%   %% In the meantime, \processes that still belong to a partition can
-%%   %% propagate their respective last $\alpha$ message, and reach
-%%     %% consistent partitioning.
-%% \end{proof}
+In terms of number of messages, in the average case, a \process $i$
+chosen uniformly at random among all \processes creates a logical
+partition. Its messages $\alpha_i$ spread through the network until
+reaching \processes that belong to another partition closer to
+them. This splits partitions in half on average. Overall, the $a^{th}$
+new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
+      \log_2 a \rfloor}})$} \processes. This decreases every new
+partition until reaching one \process per new partition: its
+source. The average number of messages per \process is
+\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
+      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
+number of neighbors per \process.
+% \TODO{Multiple receipt and
+% multiple
+%  delivery imply more messages (receipt bounded by $|O|$ as well).}
+Deleting the $a^{th}$ partition generates twice as many messages as
+creating the $a^{th}$ partition: $\delta$ messages travel through the
+partition, then $\alpha$ messages compete to fill the gap.  Overall,
+the communication complexity shows that \NAME scales well to the
+number of partitions.
+%% In the
+%% worst-case, every new partition includes all but one \process
+%% belonging to the previous partition. The total number of messages
+%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
+%% a^2)$. As for the average-case, the number of messages for the
+%% partition deletion is identical to the number of messages of the
+%% corresponding partition creation.
+%% \begin{algorithm}[h!]
+%%   \input{input/algoedges.tex}
+%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
+%% \end{algorithm}
 
@@
 \begin{proof}
-  By design, \TODO{obvious}.
+  By design.
 \end{proof}
@@
 
+\begin{algorithm}[h]
+  \input{input/algoxascast.tex}
+  \caption{\label{algo:xascast}\NAMEC at \Process~$p$. \TODO{TODO.}}
+\end{algorithm}
+
 %%% Local Variables: 

### 2021-12-02 input/experiments.tex
adapting to two columns, stilltodo. simpler problem display
reorder again, mb better, todiscuss
include figure of what it could look like to have xascast experiment

@@
-\newcommand{\FIGSCALE}{0.59}
+\newcommand{\FIGSCALE}{0.99}
 
@@
 the Github platform at
-\url{https://anonymous.4open.science/r/peersim-partition-5592}.
+\TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.
 
@@
 
+\begin{figure*}
+  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
+    comprising 40 interconnected autonomous systems spanning across
+    Europe. The generated trace marked with red dots starts from
+    Lisboa to reach Copenhagen 10 seconds later.]{
+    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
+  } \subfloat[PartB][\label{fig:xascast}\TODO{PLACEHOLDER}
+    \TODO{Experiment with ascast against xascast?}]{
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
+  }
+  \caption{\TODO{Experiment measuring something on such a trace.}}
+\end{figure*}
+
 %% Next Section reviews state-of-the-art approaches for content indexing

### 2021-12-02 input/proposal.tex
include figure of what it could look like to have xascast experiment

@@
   \process only sends messages that it assumes up-to-date:
-  $s_x(\alpha_s) \implies \delta_s \not\in R_x$.
+  $s_x(\alpha_s) \implies \delta_s \not\in R_x$. \TODO{Only keep last?
+    Tothink what happens if we keep all as in def now.}
 \end{definition}
@@
 \begin{proof}
-  \TODO{Meow.}
+  Detection triggers forwarding of staleness downstream which
+  completes the case study of Lemma~\ref{lem:detector} by ensuring
+  that, when a source broadcasts its staleness notification, all
+  \processes that belong to its partition eventually deliver such a
+  staleness notification. All downstream bordering \processes also
+  eventually receive such a staleness notification and echo back their
+  best delivered message. This triggers another competition as in
+  Theorem~\ref{theo:fb} for the \processes that delivered the
+  staleness notification.
 \end{proof}

### 2021-12-02 input/proposal.tex
about algo

@@
 
-\TODO{Rework this to remove repetitions. Since implem is close from
-  section.}
-
-Algorithm~\ref{algo:ascast} shows the instructions implementing
-dynamic consistent partitioning. To implement staleness, each \process
-maintains a vector of versions that associates the respective known
-local counter of each known source, or has-been source. Its size
-increases linearly with the number of sources that the \process has
-ever known, which is the number of \processes in the system
-$\mathcal{O}(V)$ in the worst case.  Nevertheless, following the
-principles of scoped broadcast, we expect that every \process only
-acknowledges a small subset of sources.  In addition, each message
-carries the identifier and counter of each \node that forwarded
-it. Again, following the principles of scoped broadcast, we expect
-that versioned paths remain small. Using these data structures, each
-\process delivers and forwards only new messages that improve their
-best known partition (see Line~\ref{line:ascast_improve}).
-
-This vector of versions constitutes a summary of known progress of
-other \nodes. It discards stale messages and it enables detecting
-possible blocking of staleness notifications: the current best
-partition comes from a neighbor that just delivered a stale message
-(see Line~\ref{line:ascast_detect}). Figure~\ref{fig:problem} shows
-that such a behavior may hide a delete notification. The detecting
-\process must act to reflect this possible change: all \processes
-whose last message comes from the detecting \process must remove it
-and accept the competition of other \processes. Since this behavior is
-similar to that of source deletion, we implement it in a similar way.
-
-A \process that removes its self-appointed status of source, or
-detects a possible inconsistency, increments its local counter and
-disseminates a delete notification message $\delta_{s, c}$
-piggybacking its identifier $s$ and counter $c$. Any \process that
-receives such delete notification delivers and forwards it if its best
-message contains the has-been source or detector associated to a lower
-counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
-messages to quickly reach every downstream \process.
-
-As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
-not only requires eventual purging of stale messages, but also the
-retrieval of the best up-to-date partitions.  In that regard, $\delta$
-messages have a dual use: since they already reach the borders of
-their partition by design, they trigger a competition when reaching
-bordering.  When a \process receives a delete notification from a
-neighbor $q$ but does not deliver it, it assumes that the just
-received $\delta$ message purged possibly stale messages, creating a
-gap that its own best partition could help fill. Consequently, it
-sends to $q$ its own best $\alpha$ message (see
-Line~\ref{line:ascast_echo}).
+Algorithm~\ref{algo:ascast} shows the instructions of our
+implementation called \NAME that enables dynamic consistent
+partitioning. It implements forwarding of best (see
+Line~\ref{line:fb}) and echos (see Line~\ref{line:echo}). To implement
+forwarding of staleness downstream as stated in
+Definition~\ref{def:fsplus},
+\begin{inparaenum}[(A)]
+\item each \process maintains a vector of versions that associates the
+  respective known local counter of each known source, or has-been
+  source. It constitutes a summary of known progress of other
+  \processes; 
+\item each notification message $\alpha$ carries the list of
+  identifier and counter of each \node that forwarded it. In the worst
+  case, both these structures grow linearly with the number of
+  \processes in the system $\mathcal{O}(V)$. Nevertheless, following
+  the principles of scoped broadcast, we expect that \processes only
+  acknowledge a small subset of sources and messages;
+\item each staleness notifications $\delta$ only carry the identifier
+  and counter of the \process~--~source or detector~--~that generated
+  it. Only downstream \processes may deliver such message, since they
+  carry the identifier of the generator. 
+\end{inparaenum}
+To implement the detection as stated in Lemma~\ref{lem:detector}, each
+\process only requires to know the direct parent of its best delivered
+message which is already included in the piggybacked path of this
+message. Receiving a message known to be stale from this parent
+triggers the generation of staleness notifications that force
+downstream \processes to reevaluate the partition they are in (see
+Line~\ref{line:detect}).
 
@@
 
-Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
-dynamic networks where \processes can join, leave, or crash at any
-time. Removing a \process is equivalent to removing all its edges, and
-adding a \process is equivalent to add as many edges as necessary.
-Adding an edge between two \processes may only improve the shortest
-path of one of these \processes. Therefore, it triggers a competition
-between the two \processes. If one or the other \process improves, the
-propagation of $\alpha$ messages operates normally.  Removing an edge
-between two \processes may invalidate the shortest path of one of
-involved \processes plus downstream \processes. As a side effect,
-removing an edge may also impair the propagation of a partition
-delete. To implement this behavior, \NAME uses its implementation of
-$\delta$ messages. This enables \NAME even in dynamic networks subject
-to physical partitioning.
+By reusing \NAME's default behavior, Algorithm~\ref{algo:edges}
+enables dynamic consistent partitioning in dynamic networks where
+\processes can join, leave, or crash at any time.  Adding a \process
+is equivalent to add as many edges as necessary. Since adding an edge
+may improve shortest paths, the protocol triggers a competition using
+echos of Definition~\ref{def:fbplus}.  Removing a \process is
+equivalent to removing all its edges. Removing an edge between two
+\processes may invalidate the shortest path of one of involved
+\processes plus downstream \processes, or impair the propagation of
+staleness notifications. Therefore, the protocol reuses its detection
+mechanism of Lemma~\ref{lem:detector} as a solution.
+Algorithm~\ref{algo:edges} even extends \NAME to dynamic networks
+subject to physical partitioning.
 
@@
 %% \end{inparaenum}
-In terms of number of messages, in the average case, a \process $i$
-chosen uniformly at random among all \processes creates a logical
-partition. Its messages $\alpha_i$ spread through the network until
-reaching \processes that belong to another partition closer to
-them. This splits partitions in half on average. Overall, the $a^{th}$
-new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
-      \log_2 a \rfloor}})$} \processes. This decreases every new
-partition until reaching one \process per new partition: its
-source. The average number of messages per \process is
-\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
-      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
-number of neighbors per \process.
+\TODO{TODOUBLECHECK}. In terms of number of messages, in the average
+case, a \process $i$ chosen uniformly at random among all \processes
+creates a logical partition. Its messages $\alpha_i$ spread through
+the network until reaching \processes that belong to another partition
+closer to them. This splits partitions in half on average. Overall,
+the $a^{th}$ new partition comprises
+\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
+\processes. This decreases every new partition until reaching one
+\process per new partition: its source. The average number of messages
+per \process is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor
+      \log_2 a \rfloor}})$}, where \smash{$\overline{|O|}$} is the
+average number of neighbors per \process.
 % \TODO{Multiple receipt and

### 2021-12-03 input/proposal.tex
notes

@@
 \begin{definition}[\label{def:fbplus}FB$^+$: echos] FB where a
-  \process $x$ that receives a stale message sends back --~or
+  \process $x$ that receives a staleness notification sends back --~or
   echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
   \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
-  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in D_x$.
+  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in
+  D_x$. \TODO{Rework min}
 \end{definition}
+
+\TODO{Naive implementation is FB$^+$ etc. It does not work.}
 
@@
 \begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
-  \implies$ \underline{D}etector existence (D)]
-  Assuming $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on
-  $\pi_{xz}$ of $\alpha_x$ with $\alpha_x = \min D_z$, if $x$
-  broadcasts a staleness notification $\delta_x$, either $z$
-  eventually delivers it, or a \process $y$ in such a chain of
-  delivery $\pi_{xz}'$ eventually detects its blocking.
+  \implies$ \underline{D}etector existence (D)] Assuming
+  $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
+  $\alpha_x$ with $\alpha_x = \min D_z$, if $x$ broadcasts a staleness
+  notification $\delta_x$, either $z$ eventually delivers it, or a
+  \process $y$ in such a chain of delivery $\pi_{xz}'$ eventually
+  \TODO{detects} its \TODO{blocking}.
   % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
@@
 
-\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{D} \implies \textup{DCP}$]
+\TODO{$FB \subseteq FB+$}.
+
+\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \TODO{\wedge \textup{D}} \implies \textup{DCP}$]
   A protocol guarantees dynamic consistent partitioning if it

### 2021-12-06 input/proposal.tex
rework start of CP

@@
 work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}. It
-also highlights that the functioning of epidemic propagation is
-well-aligned with the objectives of scoped broadcast. More precisely,
-it underlines the transitive relevance of messages, thus a \process
-can stop \TODO{forwarding messages} as soon as its predicate becomes
-unverified.  We use \NAMEB to efficiently modify the state of each
+underlines the transitive relevance of messages. It also highlights
+that the functioning of epidemic propagation is well-aligned with the
+objectives of scoped broadcast. As consequence, we assume
+implementations relying on the forwarding of messages from
+neighbor-to-neighbor.
+
+\begin{definition}[\label{def:forwarding}Forwarding]
+  A \process $x$ \underline{f}orwards a message $m$ by
+  \underline{s}ending it to its neighbors with metadata that depends
+  on its local knowledge: $f_x(m) \implies \forall \langle x, y\rangle
+  \in E: s_{xy}(m \oplus \sigma_x)$.
+\end{definition}
+
+We use scoped broadcast to efficiently modify the state of each
 \process depending on the partitions that exist in the system.
@@
 operation. This partition includes at least its source plus
-neighboring \processes that estimate they are closer to this source
-than any other one. Such a distance (or \emph{weight}) is
-application-dependant: in the context of maintaining distributed
-indexes, this would be about link latency that \nodes could monitor by
-aggregating \texttt{ping}s; or operational costs when dealing with
-multiple tenants.
+neighboring \processes that are closer to this source than any other
+one. Such a distance (or \emph{weight}) is application-dependant: in
+the context of maintaining distributed indexes, this would be about
+link latency that \nodes could monitor by aggregating \texttt{ping}s;
+or operational costs when dealing with multiple tenants.
 
@@
 
-\begin{definition}[\label{def:partitioning}Partitioning]
-  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_{s\in
-    S}$ be the \underline{p}artition including at least \Process~$s$,
-  each \process belongs to at most one partition $\forall x, y \in V,
-  \forall s,s' \in S: (x \in P_{s} \wedge y \in P_{s'}) \implies (x \neq
-  y \vee s = s')$, and there exists at least one path $\pi_{xs}$ of
-  \processes that belong to this partition $\forall z \in \pi_{xs}: z
-  \in P_s$.
-\end{definition}
+%% \begin{definition}[\label{def:partitioning}Partitioning]
+%%   Let $S \subseteq V$ be the set of \underline{s}ources, and $P_{s\in
+%%     S}$ be the \underline{p}artition including at least \Process~$s$,
+%%   each \process belongs to at most one partition $\forall x, y \in V,
+%%   \forall s,s' \in S: (x \in P_{s} \wedge y \in P_{s'}) \implies (x \neq
+%%   y \vee s = s')$, and there exists at least one path $\pi_{xs}$ of
+%%   \processes that belong to this partition $\forall z \in \pi_{xs}: z
+%%   \in P_s$.
+%% \end{definition}
 
-Definition~\ref{def:scoped} and Definition~\ref{def:partitioning}
-share the transitive relevance of \process states. However, we further
-constrain the partitioning in order to guarantee the existence of
-exactly one consistent partitioning that \processes eventually converge
-to.
+%% Definition~\ref{def:scoped} and Definition~\ref{def:partitioning}
+%% share the transitive relevance of \process states. However, we further
+%% constrain the partitioning in order to guarantee the existence of
+%% exactly one consistent partitioning that \processes eventually
+%% converge to.
 
 \begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
-  We associate each edge $\langle x, y \rangle \in E$ with a pair of
-  positive \underline{w}eights $w_{xy}$ and $w_{yx}$. The shortest
-  \underline{p}ath $\Pi_{xz}$ has a distance as a sum of weights
-  $\sum\{w_{pq} | \langle p, q \rangle \in \Pi_{xz}\} = |\Pi_{xz}|$
-  that is smaller than any other path, with $\Pi_{xx}$ being the
-  greatest lower bound of $x$. The only consistent partitioning is a
-  set of logical partitions $P_{s\in S}$ such that every \process
-  belongs to the partition of its closest source:
-  $\forall x \in P_{s}: \nexists P_{s'}$ such that
-  $|\Pi_{s'x}| < |\Pi_{sx}|$.
+  Assuming a set of \underline{s}ources $S\subseteq V$, a positive
+  \underline{w}eight $w_{xy}$ associated with each edge $\langle x, y
+  \rangle \in E$, we define consistent partitioning as a set of
+  logical partitions $P_{s\in S}$ where each \node $x$ belongs to the
+  partition of its closest source $s$, \ie there exists a
+  \underline{p}ath $\pi_{sx}$ with a sum of weights $|\pi_{sx}| =
+  \sum\{w_{pq} | \langle p, q \rangle \in \pi_{sx}\}$ smaller than any
+  other path, with $|\pi_{xx}|$ being $x$'s greatest lower bound.
+  %$\forall x \in
+  % P_{s}:  \nexists P_{s'}$ such that $|\pi_{s'x}| < |\pi_{sx}|$.
 \end{definition}
@@
 Unfortunately, \processes do not share a common global knowledge of
-the network state. For \processes to reach consistent partitioning
-together, a \Process $s$ \underline{a}dding a partition must send a
-notification $\alpha_s$ to every \process that is closer to it than
-any other source. Since epidemic dissemination and scoped broadcast
-have well-aligned objectives, we assume implementations relying on
-message forwarding from neighbor-to-neighbor.
-
-\begin{definition}[\label{def:forwarding}Forwarding]
-  A \process $x$ \underline{f}orwards a message $m$ by
-  \underline{s}ending it to its neighbors:
-  $f_x(m) \implies \forall \langle x, y\rangle \in E:
-  \TODO{s_{xy}(m)}$.
-\end{definition}
+the network state. For \processes to eventually ($\eventually$) reach
+consistent partitioning, each source $s$ must send notifications
+$\alpha_s$ to all \processes that are closer to it than any other
+source, along with enough control information to allow them to decide
+of their closest source.
 
 \begin{theorem}[\label{theo:fb}\underline{F}orwarding of \underline{B}est (FB)
-    $\implies\eventually$CP]
+    $\implies\eventually \textup{CP}$]
     % 

### 2021-12-06 input/proposal.tex
reworking theo 1

@@
 $\alpha_s$ to all \processes that are closer to it than any other
-source, along with enough control information to allow them to decide
-of their closest source.
+source, along with enough metadata to allow them to decide of their
+closest source. A simple implementation consists in ensuring that each
+\process $x$ eventually receives $\alpha_s^{|\Pi_{sx}|}$ where
+$\Pi_{sx}$ is the \emph{best} path from any source to it; the value
+$|\Pi_{sx}|$ being built over forwarding along this path.
 
@@
     % 
-    Assuming reliable communication links ($s_{xy}(m) \iff \eventually
-    r_{yx}(m)$), and a total order on messages ($<$), \processes
-    eventually reach consistent partitioning if each \process delivers
-    its best message among \underline{r}eceived messages $R_x$, and
+    Assuming that each \process $x$ stores its outgoing weights
+    ($\forall \langle x, y \rangle \in E: \pi_{xy} \in \sigma_x$), a
+    total order on messages based on weights ($m^d_s < m^{d'}_{s'}$
+    when $d < d' \vee (d = d' \wedge s< s')$), reliable communication
+    links ($s_{xy}(m) \iff r_{yx}(m)$), \processes eventually reach
+    consistent partitioning if each \process delivers its best (\ie
+    smallest) message among \underline{r}eceived messages $R_x$, and
     forwards its best message among \underline{d}elivered messages
-    $D_x$.
-    % , \ie
-    % the message $\alpha_s^d$ with the smallest distance $d$ to the
-    % source $s$
+    $D_x$ such that $f_x(\alpha^d_s) \implies \forall \langle x, y
+    \rangle \in E: s_{xy}(\alpha_s^d \oplus ^{w_{xy}})$, \ie by
+    accumulating the respective weight of used edges.
     % ($(\alpha_s^d = \min R_x) \implies (d_x(\alpha_s^d) \wedge
@@
   % forwards any message. \Processes do not belong to any partition.
-
   \noindent \TODO{use total order ($<$) and sets $R_p D_p$} Whenever a
   \process $s$ becomes a source, it delivers its own message
-  $d_s(\alpha_{s})$. Whatever its set of received messages, its own
-  partition $P_s$ becomes and remains its closest partition
-  $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq s:
-  |\Pi_{s s}| < |\Pi_{s x}|$.
+  $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever its set of received
+  messages, its own partition $P_s$ becomes and remains its closest
+  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq
+  s: |\Pi_{s s}| < |\Pi_{s x}|$.
   %
@@
 
-Algorithm~\ref{algo:add} shows the instructions that implement
-forwarding of best to reach consistent partitioning when
+Algorithm~\ref{algo:add} shows the instructions that implement a
+\emph{reactive} forwarding of best to reach consistent partitioning
+when
 \begin{inparaenum}[(i)]
@@
 \end{inparaenum}
-For the sake of simplicity and to remove obvious loops, a \process
-does not forward a notification to its sender
-(Line~\ref{line:accumulator}).  Figure~\ref{fig:add} illustrates the
-behavior of this algorithm on a system comprising 4 \processes $a$,
-$b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
-their partition.  They \NAMEB a notification \TODO{\underline{a}dd
-  message}: $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
-state with the lowest possible bound $0$ (see
+\TODO{We only keep last.}  For the sake of simplicity and to remove
+obvious loops, a \process does not forward a notification to its
+sender (Line~\ref{line:accumulator}).  Figure~\ref{fig:add}
+illustrates the behavior of this algorithm on a system comprising 4
+\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
+become the sources of their partition.  They \NAMEB a notification
+\TODO{\underline{a}dd message}: $\alpha_a^0$ and $\alpha_d^0$. They
+initialize their own state with the lowest possible bound $0$ (see
 Line~\ref{line:lowestbound}), and send a message to each of their

### 2021-12-06 input/proposal.tex
almost nothing here

@@
   % forwards any message. \Processes do not belong to any partition.
-  \noindent \TODO{use total order ($<$) and sets $R_p D_p$} Whenever a
-  \process $s$ becomes a source, it delivers its own message
-  $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever its set of received
+  % \noindent \TODO{use total order ($<$) and sets $R_p D_p$}
+  Whenever a \process $s$ becomes a source, it delivers its own
+  message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever its set of received
   messages, its own partition $P_s$ becomes and remains its closest
-  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq
-  s: |\Pi_{s s}| < |\Pi_{s x}|$.
+  partition $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ since $|\pi_{ss}|$ is
+  its greatest lower bound.
   %

### 2021-12-07 input/proposal.tex
proof FB + algo

--- 2021-12-06 input/proposal.tex
@@
   A \process $x$ \underline{f}orwards a message $m$ by
-  \underline{s}ending it to its neighbors with metadata that depends
-  on its local knowledge: $f_x(m) \implies \forall \langle x, y\rangle
-  \in E: s_{xy}(m \oplus \sigma_x)$.
+  \underline{s}ending it to its neighbors $y$ with metadata that
+  depends on its local knowledge: $f_x(m) \implies \forall \langle x,
+  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
 \end{definition}
@@
 the network state. For \processes to eventually ($\eventually$) reach
-consistent partitioning, each source $s$ must send notifications
-$\alpha_s$ to all \processes that are closer to it than any other
-source, along with enough control information to allow them to decide
-of their closest source.
+consistent partitioning, each source $s$ must send
+\texttt{\underline{A}dd} notifications $\alpha_s$ to all \processes
+that are closer to it than any other source, along with enough
+metadata to allow them to decide of their closest source. A simple
+implementation consists in ensuring that each \process $x$ eventually
+receives $\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best}
+path from any source to it; the value $|\Pi_{sx}|$ being built over
+forwarding along this path.
 
@@
     % 
-    Assuming reliable communication links ($s_{xy}(m) \iff \eventually
-    r_{yx}(m)$), and a total order on messages ($<$), \processes
-    eventually reach consistent partitioning if each \process delivers
-    its best message among \underline{r}eceived messages $R_x$, and
+    Assuming that each \process $x$ stores its outgoing weights
+    ($\forall \langle x, y \rangle \in E: \pi_{xy} \in \sigma_x$), a
+    total order on messages based on weights ($m^d_s < m^{d'}_{s'}$
+    when $d < d' \vee (d = d' \wedge s< s')$), reliable communication
+    links ($s_{xy}(m) \iff \eventually r_{yx}(m)$), \processes eventually reach
+    consistent partitioning if each \process delivers its best (\ie
+    smallest) message among \underline{r}eceived messages $R_x$, and
     forwards its best message among \underline{d}elivered messages
-    $D_x$.
-    % , \ie
-    % the message $\alpha_s^d$ with the smallest distance $d$ to the
-    % source $s$
-    % ($(\alpha_s^d = \min R_x) \implies (d_x(\alpha_s^d) \wedge
-    % f_x(\TODO{\alpha_s^d}))$).
+    $D_x$ such that $f_x(\alpha^d_s) \implies \forall \langle x, y
+    \rangle \in E: s_{xy}(\alpha_s^d \oplus ^{w_{xy}})$, \ie by
+    accumulating the respective weight of used edges.
 \end{theorem}
@@
 \begin{proof}
-  % When there are no sources, no \process receives, nor delivers hence
-  % forwards any message. \Processes do not belong to any partition.
-
-  \noindent \TODO{use total order ($<$) and sets $R_p D_p$} Whenever a
-  \process $s$ becomes a source, it delivers its own message
-  $d_s(\alpha_{s})$. Whatever its set of received messages, its own
-  partition $P_s$ becomes and remains its closest partition
-  $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq s:
-  |\Pi_{s s}| < |\Pi_{s x}|$.
-  %
-  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
-  Since communication links are reliable, neighboring \processes
-  eventually receive such a notification
-  $\forall \langle s, y \rangle \in E \iff \eventually
-  r_y(\alpha_{s}^{d})$. Most importantly, whatever the order of
-  received messages, every \process $q$ in this neighborhood such that
-  there exists no closer source $s'$ than the received one $s$,
-  delivers it, since $w_{sq} < |\Pi_{s'q}|$.
-  %
-  \noindent They forward it and their respective neighbors eventually
-  receive it. By transitivity, the message originating from $s$
-  reaches all \processes belonging to $P_s$ at least through their
-  shortest paths: $\smash{\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
-  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s}^{|\Pi_{sq'}|})}$.
-  Since there exists only one best sum of weights per \process that
-  can never be retracted, \processes eventually reach consistent
-  partitioning.
-  %% /!\ not equivalence for there exists other implementations.
-  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
-  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
-  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
-  %%   following \processes from $q'$ to $p$ may mistake another
-  %%   partition for their  because it needs the weight $W_{pq}$.
-  %% \end{asparadesc}
+  Whenever a \process~$s$ becomes a source, it broadcasts hence
+  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
+  its set of received messages, it acknowledges that it belongs to its
+  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
+  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
+  \noindent Such a source forwards its notification to its neighbors.
+  Every neighbor eventually receives its notification since
+  communication links are reliable. Whatever the order of received
+  messages $R_x$ at neighboring \process~$x$, total order ensures that
+  it delivers notifications $\alpha_s^{d}$ when $d= |\pi_{ss}| +
+  w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$ is the lightest
+  weight of $x$ to any source $s'$.
+  \noindent Among these neighbors, at least those that fulfill the
+  latest condition forward their respective notification.  By
+  transitivity, the message originating from $s$ reaches all
+  \processes that belong to $P_s$ at least through their respective
+  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
+    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
+    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
+  quiescent, \ie no \process becomes source anymore, every \process
+  eventually acknowledges the partition it belongs to, \ie \processes
+  eventually reach consistent partitioning together. In addition, the
+  protocol terminates: a \process never delivers hence forwards a
+  message after it received, delivered, and forwarded the message of
+  its closest source from its lightest path.
 \end{proof}
@@
 
-Algorithm~\ref{algo:add} shows the instructions that implement
-forwarding of best to reach consistent partitioning when
-\begin{inparaenum}[(i)]
-\item weights are scalar values piggybacked in messages and
-  accumulated over forwarding,
-\item \processes only add new partitions to the system,
-\item and \processes never join, crash nor leave the system.
-\end{inparaenum}
-For the sake of simplicity and to remove obvious loops, a \process
-does not forward a notification to its sender
-(Line~\ref{line:accumulator}).  Figure~\ref{fig:add} illustrates the
-behavior of this algorithm on a system comprising 4 \processes $a$,
-$b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
-their partition.  They \NAMEB a notification \TODO{\underline{a}dd
-  message}: $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
-state with the lowest possible bound $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
-neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
-receives $\alpha_{d}^{1}$. Since it improves its own partition
-distance, it keeps it and forwards it to its neighbors. In
-Figure~\ref{fig:addD}, $b$ discards $\alpha_{a}^{2}$, for it does not
-improve its partition distance. \Processes $c$ and $d$ will never
-acknowledge that Source~$a$ exists. Ultimately, \processes discard
-last transiting messages. Despite the obvious lack of traffic
-optimization, the system reaches consistent partitioning.
+Algorithm~\ref{algo:add} shows the few instructions that implement a
+\emph{reactive} forwarding of best to reach consistent partitioning in
+a static network where \processes never join, crash, nor leave the
+system. As soon as a \process receives a better message, it delivers
+and forwards it. The trade-off consists in decreasing termination time
+at cost of increased traffic. For the sake of simplicity and to remove
+obvious loops, a \process does not forward a notification to its
+sender (Line~\ref{line:accumulator}). Figure~\ref{fig:add} illustrates
+the behavior of this algorithm on a system comprising 4 \processes
+$a$, $b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
+notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
+state with the lowest value $0$ (see Line~\ref{line:lowestbound}), and
+send a message to each of their neighbors by accumulating the
+corresponding edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, $b$ receives $\alpha_{d}^{1}$. Since it
+improves its own partition distance, it keeps it and forwards it to
+its neighbors. In Figure~\ref{fig:addD}, $b$ discards
+$\alpha_{a}^{2}$, for it does not improve its partition
+distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
+exists. Ultimately, \processes discard last transiting
+messages.
+% Despite the obvious lack of traffic optimization,
+The system reaches consistent partitioning.
 

### 2021-12-07 input/proposal.tex
not much

@@
 
-\begin{definition}[Autonomous systems]
+\begin{definition}[Autonomous system]
   An autonomous system is a network comprising nodes and communication
@@
 metadata to allow them to decide of their closest source. A simple
-implementation consists in ensuring that each \process $x$ eventually
-receives $\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best}
-path from any source to it; the value $|\Pi_{sx}|$ being built over
-forwarding along this path.
+implementation based on Definition~\ref{def:scoped} consists in
+ensuring that each \process $x$ eventually receives
+$\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
+any source to it; the value $|\Pi_{sx}|$ being built over forwarding
+along this path.
 
@@
   \input{input/algoadd.tex}
-  \caption{\label{algo:add}Adding a partition by \Process~$p$.}
+  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
 \end{algorithm}
@@
 \begin{definition}[\label{def:dcp}\underline{D}ynamic
-  \underline{c}onsistent \underline{p}artitioning (DCP)]
-  Dynamic consistent partitioning is consistent partitioning where
-  \processes can join or leave the set of sources at any \TODO{time}.
+    \underline{c}onsistent \underline{p}artitioning (DCP)] A DCP
+  protocol enables \processes to join or leave the set of sources at
+  any time while ensuring eventual consistent partitioning.
+  % Dynamic consistent partitioning is consistent partitioning where
+  % \processes can join or leave the set of sources at any \TODO{time}.
 \end{definition}
@@
 scenario, they reach consistent partitioning.
+
+%% Unfortunately, depending on receipt order of messages, \processes may
+%% converge to
 
@@
 
-\begin{definition}[\label{def:fbplus}FB$^+$: echos] FB where a
+\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where a
   \process $x$ that receives a staleness notification sends back --~or
@@
 
-\TODO{Naive implementation is FB$^+$ etc. It does not work.}
+\TODO{The naive implementation described above is $\textup{FB}^+
+  \wedge FS$. And it does  not work.}
 
-\begin{lemma}[\label{lem:fbfse}FB$^+ \wedge$ FS $\centernot\implies$ DCP]
-  Forwarding best up-to-date, forwarding staleness, and echoing is not
-  sufficient to guarantee dynamic consistent partitioning.
+\begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
+    \centernot\implies \textup{DCP}$] Forwarding best up-to-date,
+  forwarding staleness, and echoing is not sufficient to guarantee
+  dynamic consistent partitioning.
 \end{lemma}
@@
   \input{input/algoascast.tex}
-  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
+  \caption{\label{algo:ascast}\NAME: DCP protocol at \Process~$p$.}
 \end{algorithm}

### 2021-12-07 input/figundoproblem.tex
meow
reworked order of things

@@
   \newcommand{\SCALE}{0.9}
-
   \newcommand{\LEFT}{\triangleleft}
   \newcommand{\RIGHT}{\triangleright}
-
   \begin{center}
@@
     \hspace{0pt}
-    \subfloat[Part B][\label{fig:undoproblemB}($c$ deletes its partition but $a$ does not.
+    \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
       $b$ delivers and forwards $\alpha_a$.]
@@
     \hspace{0pt}
-    \subfloat[Part D][\label{fig:undoproblemD}(both) $b$ delivers and forwards $\delta_c$.]
+    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
              {\input{input/figundoproblemD.tex}}

### 2021-12-07 input/proposal.tex
reworked order of things

@@
 
-A naive implementation resembles echos in acoustics:
-\underline{d}elete notifications $\delta$ propagate as long as
-receivers' current partition is the targeted one, and when delete
-notifications reach the bordering \processes of the deleted partition,
-it triggers a competition -- or an echo -- that goes backward to fill
-the gap left open by removals.  For example, in Figure~\ref{fig:del},
-two partitions initially exist: $P_a$ and $P_d$ that respectively
-include $\{a\}$, and $\{b, c, d\}$. In Figure~\ref{fig:delA}, $a$
-deletes its partition. It notifies all neighboring \processes~--~here
-only $b$~-- that may belong to its partition using \NAMEB. Upon
-receipt, $b$ discards the delete notification $\delta_a$ since
-$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
-sends its own best partition $\alpha_d^3$ that may be the best for
-$a$. Eventually, every \process belongs to Partition $P_d$. In this
-scenario, they reach consistent partitioning.
-
-%% Unfortunately, depending on receipt order of messages, \processes may
-%% converge to
-
-Delete operations add a new notion of order between events, and most
-importantly between message deliveries. Delete operations implicitly
-state that all preceding events become obsolete, and that all messages
-originating from these preceding events convey stale control
-information.
+Delete operations bring a new notion of order between events, and most
+importantly between message deliveries. When a \process $s$ performs a
+\texttt{Del} operation, this implicitly states that all its preceding
+\texttt{Add} operations become obsolete. As consequence, their results
+-- scoped broadcast in the form of \texttt{\underline{A}dd}
+notifications $\alpha_s$ -- should be canceled by the corresponding
+\texttt{\underline{D}el} notifications $\delta_s$.
 
@@
 \end{definition}
+
+A naive implementation based on scoped broadcast as stated in
+Definition~\ref{def:scoped} resembles echos in acoustics: staleness
+notifications propagate as long as receivers' current partition is the
+targeted one, and when staleness notifications reach the bordering
+\processes of the deleted partition, it triggers a competition -- or
+an echo -- that goes backward to fill the gap left open by removals.
 
@@
 
-\TODO{The naive implementation described above is $\textup{FB}^+
-  \wedge FS$. And it does  not work.}
+Figure~\ref{fig:del} illustrates the behavior of this intuitive
+implementation.  Two partitions initially exist: $P_a$ and $P_d$ that
+respectively include $\{a\}$, and $\{b, c, d\}$. In
+Figure~\ref{fig:delA}, $a$ deletes its partition. It notifies all
+neighboring \processes~--~here only $b$~-- that may belong to its
+partition. Upon receipt, $b$ discards the delete notification
+$\delta_a$ since $\delta_a$ does not target the former's partition
+$P_d$. \Process~$b$ sends its own best partition $\alpha_d^3$ that may
+be the best for $a$. Eventually, every \process belongs to Partition
+$P_d$. In this scenario, they reach consistent
+partitioning. Unfortunately, this protocol does not ensure consistent
+partitioning in every scenario.
+
+% \TODO{The naive implementation described above is $\textup{FB}^+
+%  \wedge FS$. And it does  not work.}
 

### 2021-12-08 input/proposal.tex
fs fb+

@@
 The system reaches consistent partitioning.
+\TODO{Traffic complexity here?}
 
@@
 \label{subsec:dynamic}
-
-%% At any time, a \process can become a source, hence adding a new
-%% partition to the system. This partition eventually includes all
-%% \processes that are closer from this new source than any other
-%% else. \Processes naturally converge towards their respective best
-%% partition by only piggybacking a monotonically increasing distance in
-%% forwarded messages.
 
@@
 Delete operations bring a new notion of order between events, and most
-importantly between message deliveries. When a \process $s$ performs a
-\texttt{Del} operation, this implicitly states that all its preceding
+importantly between message deliveries. A \process $s$ that performs a
+\texttt{Del} operation implicitly states that all its preceding
 \texttt{Add} operations become obsolete. As consequence, their results
@@
   \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
-  \process only sends messages that it assumes up-to-date:
-  $s_x(\alpha_s) \implies \delta_s \not\in R_x$. \TODO{Only keep last?
-    Tothink what happens if we keep all as in def now.}
+  \process only sends messages that it assumes
+  \underline{u}p-\underline{t}o-\underline{d}ate.
+  % : $s_x(\alpha_s)
+  % \implies \delta_s \not\in R_x$.
+  For convenience, we define $\textup{minUTD(}D\textup{)} = \min
+  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$.
+  %  \TODO{Only keep last?  Tothink what happens if we keep all as in
+%    def now.}
 \end{definition}
 
-A naive implementation based on scoped broadcast as stated in
-Definition~\ref{def:scoped} resembles echos in acoustics: staleness
-notifications propagate as long as receivers' current partition is the
-targeted one, and when staleness notifications reach the bordering
-\processes of the deleted partition, it triggers a competition -- or
-an echo -- that goes backward to fill the gap left open by removals.
+A naive attempt at implementing DCP resembles echoes in
+acoustics. Following the principles of scoped broadcast as stated in
+Definition~\ref{def:scoped}, staleness notifications propagate as long
+as receivers' current partition is the targeted one, and when
+staleness notifications reach the bordering \processes of the deleted
+partition, it triggers a competition -- or an echo -- that goes
+backward to fill the gap left open by removals.
 
@@
   %
-  To \NAMEB staleness, a \process $x$ delivers and forwards a received
-  staleness notification if it is not yet delivered and targets its
-  best delivered message: $\delta_s \in R_x \setminus D_x \wedge
-  \alpha_s = \min D_x \TODO{\implies} d_x(\delta_s) \wedge
-  f_x(\delta_s)$.
+  A \process $x$ delivers and forwards a received staleness
+  notification if it targets its best up-to-date delivered message:
+  $(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
+  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.
 \end{definition}
@@
   echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
-  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
-  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in
+  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
+  ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
   D_x$. \TODO{Rework min}
@@
 
-Figure~\ref{fig:del} illustrates the behavior of this intuitive
-implementation.  Two partitions initially exist: $P_a$ and $P_d$ that
-respectively include $\{a\}$, and $\{b, c, d\}$. In
-Figure~\ref{fig:delA}, $a$ deletes its partition. It notifies all
-neighboring \processes~--~here only $b$~-- that may belong to its
-partition. Upon receipt, $b$ discards the delete notification
-$\delta_a$ since $\delta_a$ does not target the former's partition
-$P_d$. \Process~$b$ sends its own best partition $\alpha_d^3$ that may
-be the best for $a$. Eventually, every \process belongs to Partition
+Figure~\ref{fig:del} illustrates the behavior of this implementation
+($\textup{FB}^+ \wedge \textup{FS}$).  Two partitions initially exist:
+$P_a$ and $P_d$ that respectively include $\{a\}$, and $\{b, c,
+d\}$. In Figure~\ref{fig:delA}, $a$ deletes its partition. FS in
+Definition~\ref{def:fs} states that $a$ must notify all its
+neighbors~--~here only $b$~-- that may belong to its partition.  In
+Figure~\ref{fig:delB}, $b$ receives but does not deliver $\delta_a$
+since $\delta_a$ does not target its current partition $P_d$.
+$\textup{FB}^+$ in Definition~\ref{def:fbplus} states that $b$ must
+echo back its own best up-to-date message $\alpha_d^3$, for it may be
+the best for $a$. Eventually, every \process belongs to Partition
 $P_d$. In this scenario, they reach consistent

### 2021-12-08 input/proposal.tex
proposal for last

@@
 notifications $\alpha_s$ -- should be canceled by the corresponding
-\texttt{\underline{D}el} notifications $\delta_s$.
+\texttt{\underline{D}el} notifications $\delta_s$. \TODO{From algo, we
+  see that last is also best, so we want to exploit this. but why ? or
+  should we show ``forwarding all staleness'' first.}
 
@@
   \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
-  \process only sends messages that it assumes
+  \process only delivers or sends messages that it assumes
   \underline{u}p-\underline{t}o-\underline{d}ate.
@@
   For convenience, we define $\textup{minUTD(}D\textup{)} = \min
-  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$.
+  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$, and
+  $\textup{last(}D\textup{)} = \alpha_s \in D: \nexists \alpha_{s'}
+  \in D: d_x(\alpha_s) \rightarrow d_x(\alpha_{s'})$.
   %  \TODO{Only keep last?  Tothink what happens if we keep all as in
@@
   A \process $x$ delivers and forwards a received staleness
-  notification if it targets its best up-to-date delivered message:
-  $(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
-  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.
+  notification if it targets its best up-to-date delivered message:\\
+  \TODO{$(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
+  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.}\\
+  $\textup{last}~D = \alpha_s \wedge d_x(\alpha_s) \rightarrow r_x(\delta_s)
+  \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
 \end{definition}

### 2021-12-08 input/proposal.tex
meow

@@
   % \implies \delta_s \not\in R_x$.
-  For convenience, we define $\textup{minUTD(}D\textup{)} = \min
-  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$, and
+  For convenience, we define \TODO{$\textup{minUTD(}D\textup{)} = \min
+  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$}, and
   $\textup{last(}D\textup{)} = \alpha_s \in D: \nexists \alpha_{s'}
@@
 
-\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where a
-  \process $x$ that receives a staleness notification sends back --~or
-  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
-  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
-  ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
-  D_x$. \TODO{Rework min}
+\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where
+  a \process $x$ that receives but does not deliver a staleness
+  notification sends back --~or echoes~-- its best up-to-date
+  delivered message:
+  $\textup{last}~D_x = \alpha_s^d \wedge \delta_s
+  \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}) \implies
+  s_{xy}(\alpha_s^d\oplus^{w_{xy}})$.
+
+  % $r_{xy}(\alpha_s)
+  % \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
+  % ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
+  % D_x$. \TODO{Rework min}
+
 \end{definition}

### 2021-12-09 input/proposal.tex
mostly todo and notes to discuss to improve

@@
   % 
-  A \process $x$ delivers and forwards a received staleness
+  \TODO{A source broadcasts.}
+  A \process $x$ delivers and forwards \TODO{at most once} a received staleness
   notification if it targets its best up-to-date delivered message:\\
@@
 \end{inparaenum}
+\TODO{A lot of blockings occur, only that of example is a problem.
+  Could be $b$ or $c$ that detects? We put burden on $c$ since
+  unconsistency starts here. Problem: how to make sure that $c$
+  receives a staleness notification in this case?}
 
@@
   staleness downstream]
-  To \NAMEB staleness downstream, a node $x$ delivers and forwards a
+  \TODO{Any process broadcast.}  A node $x$ delivers and forwards a
   received staleness notification if it is not yet delivered and it

### 2021-12-09 input/proposal.tex
todos

@@
   depends on its local knowledge: $f_x(m) \implies \forall \langle x,
-  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
+  y\rangle \in E: s_{xy}(m \TODO{\oplus} \sigma_x)$.
 \end{definition}
@@
 $\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
-any source to it; the value $|\Pi_{sx}|$ being built over forwarding
-along this path.
+any source to it; the best value $|\Pi_{sx}|$ being built over
+forwarding along this path.
 
@@
 and forwards it. The trade-off consists in decreasing termination time
-at cost of increased traffic. For the sake of simplicity and to remove
-obvious loops, a \process does not forward a notification to its
-sender (Line~\ref{line:accumulator}). Figure~\ref{fig:add} illustrates
-the behavior of this algorithm on a system comprising 4 \processes
-$a$, $b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
-notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
-state with the lowest value $0$ (see Line~\ref{line:lowestbound}), and
-send a message to each of their neighbors by accumulating the
-corresponding edge weight (see Line~\ref{line:accumulator}). In
-Figure~\ref{fig:addC}, $b$ receives $\alpha_{d}^{1}$. Since it
-improves its own partition distance, it keeps it and forwards it to
-its neighbors. In Figure~\ref{fig:addD}, $b$ discards
-$\alpha_{a}^{2}$, for it does not improve its partition
+at cost of increased traffic. \TODO{For the sake of simplicity and to
+  remove obvious loops, a \process does not forward a notification to
+  its sender (Line~\ref{line:accumulator})}. Figure~\ref{fig:add}
+illustrates the behavior of this algorithm on a system comprising 4
+\processes $a$, $b$, $c$, and $d$. Both $a$ and $d$ become sources.
+They \NAMEB notifications $\alpha_a^0$ and $\alpha_d^0$. They
+initialize their own state with the lowest value $0$ (see
+Line~\ref{line:lowestbound}), and send a message to each of their
+neighbors by accumulating the corresponding edge weight (see
+Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, $b$ receives
+$\alpha_{d}^{1}$. Since it improves its own partition distance, it
+keeps it and forwards it to its neighbors. In Figure~\ref{fig:addD},
+$b$ discards $\alpha_{a}^{2}$, for it does not improve its partition
 distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
-exists. Ultimately, \processes discard last transiting
-messages.
+exists. Ultimately, \processes discard last transiting messages.
 % Despite the obvious lack of traffic optimization,
 The system reaches consistent partitioning.
-\TODO{Traffic complexity here?}
+
+\noindent \TODO{In terms of space complexity.} In terms of number of
+messages, in the average case, a \process $x$ chosen uniformly at
+random among all \processes creates a logical partition. Its messages
+$\alpha_x$ spread through the network until reaching \processes that
+belong to another partition closer to them. This splits partitions in
+half on average. Overall, the $n^{th}$ new partition comprises
+\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 n \rfloor}})$}
+\processes. This decreases every new partition until reaching one
+\process per new partition: its source. The average number of messages
+per \process is
+\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
+      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
+number of neighbors per \process.
 
@@
 acoustics. Following the principles of scoped broadcast as stated in
-Definition~\ref{def:scoped}, staleness notifications propagate as long
-as receivers' current partition is the targeted one, and when
-staleness notifications reach the bordering \processes of the deleted
-partition, it triggers a competition -- or an echo -- that goes
-backward to fill the gap left open by removals.
+Definition~\ref{def:scoped}, a \process that receives a staleness
+notification forwards it only if the latter targets its current
+partition. The staleness notifications propagate through the network
+as long as they remain in the deleted partition. When they reach the
+bordering \processes of the deleted partition, it triggers a
+competition -- or an echo -- that goes backward to fill the gap left
+open by removals. \TODO{as in FB.}
 
@@
 %% \end{inparaenum}
-\TODO{TODOUBLECHECK}. In terms of number of messages, in the average
-case, a \process $i$ chosen uniformly at random among all \processes
-creates a logical partition. Its messages $\alpha_i$ spread through
-the network until reaching \processes that belong to another partition
-closer to them. This splits partitions in half on average. Overall,
-the $a^{th}$ new partition comprises
-\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
-\processes. This decreases every new partition until reaching one
-\process per new partition: its source. The average number of messages
-per \process is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor
-      \log_2 a \rfloor}})$}, where \smash{$\overline{|O|}$} is the
-average number of neighbors per \process.
+\TODO{TODOUBLECHECK}.
 % \TODO{Multiple receipt and

### 2021-12-13 input/proposal.tex
meow

@@
 and forwards it. The trade-off consists in decreasing termination time
-at cost of increased traffic. \TODO{For the sake of simplicity and to
-  remove obvious loops, a \process does not forward a notification to
-  its sender (Line~\ref{line:accumulator})}. Figure~\ref{fig:add}
-illustrates the behavior of this algorithm on a system comprising 4
-\processes $a$, $b$, $c$, and $d$. Both $a$ and $d$ become sources.
-They \NAMEB notifications $\alpha_a^0$ and $\alpha_d^0$. They
-initialize their own state with the lowest value $0$ (see
-Line~\ref{line:lowestbound}), and send a message to each of their
-neighbors by accumulating the corresponding edge weight (see
-Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, $b$ receives
-$\alpha_{d}^{1}$. Since it improves its own partition distance, it
-keeps it and forwards it to its neighbors. In Figure~\ref{fig:addD},
-$b$ discards $\alpha_{a}^{2}$, for it does not improve its partition
+at cost of increased traffic.  Figure~\ref{fig:add} illustrates the
+behavior of this algorithm on a system comprising 4 \processes $a$,
+$b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
+notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
+state with the lowest value $0$ (see Line~\ref{line:lowestbound}), and
+send a message to each of their neighbors by accumulating the
+corresponding edge weight (see Line~\ref{line:accumulator}). In
+Figure~\ref{fig:addC}, $b$ receives $\alpha_{d}^{1}$. Since it
+improves its own partition distance, it keeps it and forwards it to
+its neighbors. In Figure~\ref{fig:addD}, $b$ discards
+$\alpha_{a}^{2}$, for it does not improve its partition
 distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
 exists. Ultimately, \processes discard last transiting messages.
-% Despite the obvious lack of traffic optimization,
-The system reaches consistent partitioning.
+Despite the obvious lack of traffic optimization, the system reaches
+consistent partitioning.
 
-\noindent \TODO{In terms of space complexity.} In terms of number of
-messages, in the average case, a \process $x$ chosen uniformly at
-random among all \processes creates a logical partition. Its messages
-$\alpha_x$ spread through the network until reaching \processes that
-belong to another partition closer to them. This splits partitions in
-half on average. Overall, the $n^{th}$ new partition comprises
-\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 n \rfloor}})$}
-\processes. This decreases every new partition until reaching one
-\process per new partition: its source. The average number of messages
-per \process is
+Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
+|V|))$, and generates messages of identical space complexity. In terms
+of number messages, in the average case, a \process $x$ chosen
+uniformly at random among all \processes creates a logical
+partition. Its messages $\alpha_x$ spread through the network until
+reaching \processes that belong to another partition closer to
+them. This splits partitions in half on average. Overall, the $n^{th}$
+new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
+      \log_2 n \rfloor}})$} \processes. This decreases every new
+partition until reaching one \process per new partition: its
+source. The average number of messages per \process is
 \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
@@
 While only adding logical partitions to the distributed system is
-straightforward, removing them introduces additional complexity caused
-by concurrent operations.
+straightforward and lightweight, removing them introduces additional
+complexity and costs caused by concurrent operations.
 
@@
 notifications $\alpha_s$ -- should be canceled by the corresponding
-\texttt{\underline{D}el} notifications $\delta_s$. \TODO{From algo, we
-  see that last is also best, so we want to exploit this. but why ? or
-  should we show ``forwarding all staleness'' first.}
+\texttt{\underline{D}el} notifications $\delta_s$. We focus on the
+last delivery of each \process, since the best is also the last, as
+highlighted by Algorithm~\ref{algo:add}.
 
@@
   \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
-  \process only delivers or sends messages that it assumes
-  \underline{u}p-\underline{t}o-\underline{d}ate.
+  \process only delivers or sends messages that it assumes up-to-date.
   % : $s_x(\alpha_s)
   % \implies \delta_s \not\in R_x$.
-  For convenience, we define \TODO{$\textup{minUTD(}D\textup{)} = \min
-  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$}, and
+  For convenience, we define
+  % \TODO{$\textup{minUTD(}D\textup{)} = \min
+  %  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$}, and
   $\textup{last(}D\textup{)} = \alpha_s \in D: \nexists \alpha_{s'}
@@
 as long as they remain in the deleted partition. When they reach the
-bordering \processes of the deleted partition, it triggers a
-competition -- or an echo -- that goes backward to fill the gap left
-open by removals. \TODO{as in FB.}
+bordering \processes of the deleted partition, it creates an echo of
+bordering partitions that will go backward to fill the gap left open
+by removals using forwarding of best (FB) as stated by
+Theorem~\ref{theo:fb}.
 
@@
   %
-  \TODO{A source broadcasts.}
-  A \process $x$ delivers and forwards \TODO{at most once} a received staleness
-  notification if it targets its best up-to-date delivered message:\\
-  \TODO{$(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
-  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.}\\
-  $\textup{last}~D = \alpha_s \wedge d_x(\alpha_s) \rightarrow r_x(\delta_s)
-  \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
+  Any source can broadcast a staleness notification at any
+  time. Every \process $x$ delivers and forwards a received staleness
+  notification if it targets its best up-to-date delivered message:
+  %% \TODO{$(\delta_s \in R_x \wedge \alpha_s =
+  %%     \textup{minUTD}~D_x) \iff \eventually (d_x(\delta_s) \rightarrow
+  %% f_x(\delta_s))$.}
+  $(\textup{last}~D_x = \alpha_s \wedge d_x(\alpha_s) \rightarrow
+  r_x(\delta_s)) \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
+  % \wedge \nexists d'_s: d_x(\delta_s) \TODO{\not\rightarrow} d_x(\delta_s'))$.
 \end{definition}
@@
   notification sends back --~or echoes~-- its best up-to-date
-  delivered message:
-  $\textup{last}~D_x = \alpha_s^d \wedge \delta_s
-  \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}) \implies
+  delivered message: $(\textup{last}~D_x = \alpha_s^d \wedge \delta_s
+  \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}))
+  \implies r_{xy}(\delta_{s'}) \rightarrow
   s_{xy}(\alpha_s^d\oplus^{w_{xy}})$.
@@
   % D_x$. \TODO{Rework min}
-
 \end{definition}
@@
 \begin{definition}[\label{def:fsplus}$\textup{FS}^+$: forwarding
-  staleness downstream]
-  \TODO{Any process broadcast.}  A node $x$ delivers and forwards a
-  received staleness notification if it is not yet delivered and it
-  comes from the path of delivery of its best up-to-date delivered
+    staleness downstream] Any \emph{\process} can broadcast a
+  staleness notification at any time. A \emph{child \process} $x$
+  delivers and forwards a received staleness notification if it comes
+  from the path of delivery of its best up-to-date delivered
   message. \TODO{more.}

### 2021-12-13 input/proposal.tex
reworked figures mostly

@@
 
-\TODO{$FB \subseteq FB+$}.
-
-\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \TODO{\wedge \textup{D}} \implies \textup{DCP}$]
+\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \implies \textup{DCP}$]
   A protocol guarantees dynamic consistent partitioning if it
   implements forwarding of best up-to-date messages with echos,
-  forwarding of staleness messages downstream, and detection of
-  possible blocking of staleness notifications.
+  forwarding of staleness messages downstream, and the detection of
+  possible blocking triggers the forwarding of staleness notifications
+  downstream.
 \end{theorem}
@@
 
-In Edge infrastructures comprising tens of thousands of autonomous
+\TODO{In Edge infrastructures comprising tens of thousands of autonomous
 systems~\cite{nur2018crossas}, only a small subset of autonomous
@@
 source. Eventually, all nodes from this network do not belong to any
-partition and the generated traffic stops.
+partition and the generated traffic stops.}
+
+\TODO{Further scale, follow up of motivations.}
 

### 2021-12-14 input/proposal.tex
meow

@@
 distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
-exists. Ultimately, \processes discard last transiting messages.
-Despite the obvious lack of traffic optimization, the system reaches
-consistent partitioning.
+exists.  The protocol lacks of obvious traffic optimization, \eg grey
+messages are useless in this scenario. Nevertheless, the system
+discards last transiting messages after it reached consistent
+partitioning.
 
@@
 
-As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
+As a cascading effect in Figure~\ref{fig:problemD}, not only $c$
 wrongfully believes that it belongs to $a$'s partition when $a$
 already deleted it, but it could contribute to its inconsistency by
-blocking farther but up-to-date messages from actual sources. To reach
-consistent partitioning, \processes need
+blocking farther but up-to-date messages from actual sources.
+
+To reach consistent partitioning, \processes need
 \begin{inparaenum}[(i)]
@@
 \end{inparaenum}
+Since Figure~\ref{fig:problemD} highlights that when the protocol
+terminates, $c$ is the \process that remains in the wrong partition,
+we put the burden of detection and resolution on it.
+
 \TODO{A lot of blockings occur, only that of example is a problem.
@@
   unconsistency starts here. Problem: how to make sure that $c$
-  receives a staleness notification in this case?}
+  receives a staleness notification in this case? Also, $b$ is not
+  sure to receive $\delta_c$ since composable problem.}
 
@@
   $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
-  $\alpha_x$ with $\alpha_x = \min D_z$, if $x$ broadcasts a staleness
+  $\alpha_x$ with $\alpha_x = \textup{last}~D_z$, if $x$ broadcasts a staleness
   notification $\delta_x$, either $z$ eventually delivers it, or a
   \process $y$ in such a chain of delivery $\pi_{xz}'$ eventually
-  \TODO{detects} its \TODO{blocking}.
+  acknowledges its blocking.
   % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 

### 2021-12-14 input/proposal.tex
reworked detection and followup text

@@
 
+\newcommand{\last}{\textup{last}~}
+
 A naive attempt at implementing DCP resembles echoes in
@@
   %% f_x(\delta_s))$.}
-  $(\textup{last}~D_x = \alpha_s \wedge d_x(\alpha_s) \rightarrow
+  $(\last D_x = \alpha_s \wedge d_x(\alpha_s) \rightarrow
   r_x(\delta_s)) \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
@@
   notification sends back --~or echoes~-- its best up-to-date
-  delivered message: $(\textup{last}~D_x = \alpha_s^d \wedge \delta_s
+  delivered message: $(\last D_x = \alpha_s^d \wedge \delta_s
   \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}))
@@
 
-To reach consistent partitioning, \processes need
-\begin{inparaenum}[(i)]
-\item to detect possibly blocking conditions
-\item to purge all stale messages from the system
-\item enabling up-to-date notifications to eventually echo back to
-  every \process.
-\end{inparaenum}
-Since Figure~\ref{fig:problemD} highlights that when the protocol
-terminates, $c$ is the \process that remains in the wrong partition,
-we put the burden of detection and resolution on it.
+A first step to avoid staying in inconsistent state is to extend the
+behavior of each \process so \processes such as $c$, that would remain
+in a wrong partition, use their history of receipt and delivery to
+detect the blocking of staleness notifications that can hinder
+reaching consistent partitioning. For instance, $c$ detects the
+blocking of $\delta_a$ because it acknowledges that its parent $b$
+delivered a stale notification $\alpha_c^1$, \ie between the delivery
+of $\alpha_c^1$ and the delivery of $\delta_c$, $b$ blocked any other
+$\delta$.
 
-\TODO{A lot of blockings occur, only that of example is a problem.
-  Could be $b$ or $c$ that detects? We put burden on $c$ since
-  unconsistency starts here. Problem: how to make sure that $c$
-  receives a staleness notification in this case? Also, $b$ is not
-  sure to receive $\delta_c$ since composable problem.}
+%% \Begincomme{inparaenum}[(i)] \item to detect possibly blocking
+%% conditions that can hinder \item to purge all stale messages from
+%% the system \item enabling up-to-date notifications to eventually
+%% echo back to every \process.  \end{inparaenum} Since
+%% Figure~\ref{fig:problemD} highlights that when the protocol
+%% terminates, $c$ is the \process that remains in the wrong
+%% partition, we put the burden of detection and resolution on it.
+
+%% \TODO{A lot of blockings occur, only that of example is a problem.
+%%   Could be $b$ or $c$ that detects? We put burden on $c$ since
+%%   unconsistency starts here. Problem: how to make sure that $c$
+%%   receives a staleness notification in this case? Also, $b$ is not
+%%   sure to receive $\delta_c$ since composable problem.}
 
 \begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
-  \implies$ \underline{D}etector existence (D)] Assuming
-  $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
-  $\alpha_x$ with $\alpha_x = \textup{last}~D_z$, if $x$ broadcasts a staleness
+  \implies$ Detector existence] Assuming
+  $\textup{FB}^+$ and $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
+  $\alpha_x$ with $\alpha_x = \last D_z$, if $x$ broadcasts a staleness
   notification $\delta_x$, either $z$ eventually delivers it, or a
@@
   (A) Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
-  $\alpha_x$ with $\forall y \in \pi_{xz}: \alpha_x = \min D_y$, and
+  $\alpha_x$ with $\forall y \in \pi_{xz}: \alpha_x = \last D_y$, and
   assuming $d_x(\delta_x)$, then with forwarding of staleness
@@
   $\pi_{xz} = [x, \ldots, z]$ of $\alpha_x$ with at least
-  $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$, then by (A),
+  $\alpha_x = \last D_z$, and assuming $d_x(\delta_x)$, then by (A),
   the staleness notification reaches a \process $ y = \pi_{xz}[k]$. By
@@
   delivered $\delta_x$ ($\delta_x \in D_y$ covered by (A)) or
-  delivered a better message $\alpha_s = \min D_y$ with
+  delivered a better message $\alpha_s = \last D_y$ with
   $\alpha_s \neq \alpha_x$. With $y'=\pi_{xz}[k+1]$, forwarding of
@@
   \begin{enumerate}[(i)]
-  \item $\alpha_{s'} = \min D_{y'}$ with $\alpha_{s'} \neq \alpha_x$
+  \item $\alpha_{s'} = \last D_{y'}$ with $\alpha_{s'} \neq \alpha_x$
     hence $y' \iff y$ which leaves two possible outcomes:
   \item
-    $r_{y'}(\alpha_s) \wedge \alpha_x = \min D_{y'} \wedge \alpha_x <
+    $r_{y'}(\alpha_s) \wedge \alpha_x = \last D_{y'} \wedge \alpha_x <
     \alpha_s$ which means that a shorter path of delivery $\pi_{xz}'$
@@
     $r_{y'}(\alpha_s) \wedge \delta_s \in D_{y'} \wedge \alpha_x =
-    \min D_{y'}$ which detects a possible blocking of
+    \last D_{y'}$ which detects a possible blocking of
     $\delta_x$. Without global knowledge, $y'$ assumes it belongs to
@@
 
-Proof of Lemma~\ref{lem:detector} shows that there exists false
-positive in the blocking detection: $\delta_x$ may not exist but $y'$
-still receives $\alpha_s$ after the delivery of $\delta_s$ from the
-path it delivered $\alpha_x$. Figure~\ref{fig:undoproblem} highlights
-this behavior. In Figure~\ref{fig:undoproblemB}, $a$ does not delete
-its partition. In Figure~\ref{fig:undoproblemD} and because of \NAMEB,
-$c$ received the same series of messages as in
+As a second step, detecting \processes must proactively purge the
+system from their forwarded notifications. For instance in
+Figure~\ref{fig:problemD}, $c$ could broadcast $\delta_a$ in order to
+acknowledge the staleness of its own $\alpha_a^3$ and inform
+neighboring \processes that delivered it as well. Unfortunately, proof
+of Lemma~\ref{lem:detector} shows that there exists false positive in
+the blocking detection: $\delta_x$ may not exist but $y'$ still
+receives $\alpha_s$ after the delivery of $\delta_s$ from the path it
+delivered $\alpha_x$. Figure~\ref{fig:undoproblem} highlights this
+behavior. In Figure~\ref{fig:undoproblemB}, $a$ does not delete its
+partition. In Figure~\ref{fig:undoproblemD} and because of scoped
+broadcast, $c$ received the same series of messages as in
 Figure~\ref{fig:problemD}. Yet, $c$ must assume the existence of
@@
   from the path of delivery of its best up-to-date delivered
-  message. \TODO{more.}
+  message.
 \end{definition}
@@
 
-%% \NAME guarantees dynamic consistent partitioning by making extensive
-%% use of \process-to-\process communications. It requires
-%% \begin{inparaenum}[(i)]
-%% \item purging stale control information, hence propagating $\delta$
-%%   messages; and
-%% \item retrieving the closest source, hence propagating $\alpha$
-%%   messages.
-%% \end{inparaenum}
-\TODO{TODOUBLECHECK}.
-% \TODO{Multiple receipt and
-% multiple
-%  delivery imply more messages (receipt bounded by $|O|$ as well).}
-Deleting the $a^{th}$ partition generates twice as many messages as
-creating the $a^{th}$ partition: $\delta$ messages travel through the
-partition, then $\alpha$ messages compete to fill the gap.  Overall,
-the communication complexity shows that \NAME scales well to the
-number of partitions.
+% \TODO{Multiple receipt and multiple delivery}
+In terms of number of messages, deleting the $a^{th}$ partition
+generates twice as many messages as creating the $a^{th}$ partition:
+$\delta$ messages travel through the partition, then $\alpha$ messages
+compete to fill the gap \TODO{which is?}. \TODO{What about false
+  positives?} Overall, the communication complexity shows that \NAME
+scales well to the number of partitions.
 %% In the
@@
 %% corresponding partition creation.
-%% \begin{algorithm}[h!]
-%%   \input{input/algoedges.tex}
-%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
-%% \end{algorithm}
 

### 2021-12-14 input/proposal.tex
xas

@@
 By reusing \NAME's default behavior, Algorithm~\ref{algo:edges}
-enables dynamic consistent partitioning in dynamic networks where
-\processes can join, leave, or crash at any time.  Adding a \process
-is equivalent to add as many edges as necessary. Since adding an edge
-may improve shortest paths, the protocol triggers a competition using
-echos of Definition~\ref{def:fbplus}.  Removing a \process is
-equivalent to removing all its edges. Removing an edge between two
-\processes may invalidate the shortest path of one of involved
-\processes plus downstream \processes, or impair the propagation of
-staleness notifications. Therefore, the protocol reuses its detection
-mechanism of Lemma~\ref{lem:detector} as a solution.
-Algorithm~\ref{algo:edges} even extends \NAME to dynamic networks
-subject to physical partitioning.
+enables dynamic consistent partitioning in dynamic networks subject to
+physical partitioning where \processes can join, leave, or crash at
+any time. Adding a \process is equivalent to add as many edges as
+necessary. Since adding an edge may improve shortest paths, the
+protocol triggers a competition using echos of
+Definition~\ref{def:fbplus}.  Removing a \process is equivalent to
+removing all its edges. Removing an edge between two \processes may
+invalidate the shortest path of one of involved \processes plus
+downstream \processes, or impair the propagation of staleness
+notifications. Therefore, the protocol reuses its detectors of
+Lemma~\ref{lem:detector} to remove irrelevant messages from the
+system.
 
-% \TODO{Multiple receipt and multiple delivery}
-In terms of number of messages, deleting the $a^{th}$ partition
-generates twice as many messages as creating the $a^{th}$ partition:
-$\delta$ messages travel through the partition, then $\alpha$ messages
-compete to fill the gap \TODO{which is?}. \TODO{What about false
-  positives?} Overall, the communication complexity shows that \NAME
-scales well to the number of partitions.
+\TODO{Multiple receipt and multiple delivery} In terms of number of
+messages, deleting the $a^{th}$ partition generates twice as many
+messages as creating the $a^{th}$ partition: $\delta$ messages travel
+through the partition, then $\alpha$ messages compete to fill the gap
+\TODO{which is?}. \TODO{What about false positives?} Overall, the
+communication complexity shows that \NAME scales well to the number of
+partitions.
 %% In the
@@
 
-\TODO{In Edge infrastructures comprising tens of thousands of autonomous
-systems~\cite{nur2018crossas}, only a small subset of autonomous
-systems needs logical partitioning. At any time, an autonomous system
-start logical partitioning when a \process from this network becomes a
-source.  Then every \process from this network belongs to the
-partition of its closest source not only from their own network but
-that of adjacent networks that started logical partitioning as well.
-At any time, an autonomous system stops logical partitioning when the
-last source from this network revokes its status of
-source. Eventually, all nodes from this network do not belong to any
-partition and the generated traffic stops.}
-
-\TODO{Further scale, follow up of motivations.}
+To further reduce the traffic generated by our DCP protocol, we
+leverage that an Edge infrastructure is a network of autonomous
+systems, only a small subset of which needs logical partitioning.
 
@@
   V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
-  \ldots G_n\}, \mathcal{E} \rangle$. A \emph{gateway} $g$ is a
+  \ldots G_n\}, \mathcal{E} \rangle$. A \underline{g}ateway $g$ is a
   \process with at least one link towards another network: $\langle g,
@@
 \end{definition}
+
+At any time, an autonomous system start logical partitioning when a
+\process from this network becomes a source.  Then every \process from
+this network belongs to the partition of its closest source not only
+from their own network but that of adjacent networks that started
+logical partitioning as well.  At any time, an autonomous system stops
+logical partitioning when the last source from this network revokes
+its status of source. Eventually, all nodes from this network do not
+belong to any partition and the generated traffic stops.
 

### 2021-12-15 input/conclusion.tex
figure with colors, removing pdf
few fixes, add physarum to biblio

@@
 
-As future work, we plan to leverage the hierarchical properties of
-interconnected autonomous systems to further limit the propagation of
-indexes within interested systems only. Systems hosting a large number
-of contents would greatly benefit from this improvement.
+%% As future work, we plan to leverage the hierarchical properties of
+%% interconnected autonomous systems to further limit the propagation of
+%% indexes within interested systems only. We expect that such an
+%% improvement would greatly benefit the autonomous systems, and
+%% particularly those hosting a large number of contents.
+
+%% Systems hosting a large number of contents would greatly benefit from
+%% this improvement.
 
@@
 
-\noindent We also would like to evaluate \NAME within a concrete
+\noindent As future work, we plan to evaluate \NAME within a concrete
 storage system such as \underline{I}nter\underline{P}lanetary

### 2021-12-15 input/proposal.tex
few fixes, add physarum to biblio

@@
   A \process $x$ \underline{f}orwards a message $m$ by
-  \underline{s}ending it to its neighbors $y$ with metadata that
-  depends on its local knowledge: $f_x(m) \implies \forall \langle x,
-  y\rangle \in E: s_{xy}(m \TODO{\oplus} \sigma_x)$.
+  \underline{s}ending it to its neighbors $y$ \TODO{enriched}
+  ($\oplus$) with metadata that depends on its local knowledge
+  $\sigma_x$: $f_x(m) \implies \forall \langle x, y\rangle \in E:
+  s_{xy}(m \TODO{\oplus} \sigma_x)$.
 \end{definition}
@@
 metadata to allow them to decide of their closest source. A simple
-implementation based on Definition~\ref{def:scoped} consists in
-ensuring that each \process $x$ eventually receives
-$\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
-any source to it; the best value $|\Pi_{sx}|$ being built over
-forwarding along this path.
+implementation based on Definition~\ref{def:scoped} and
+Definition~\ref{def:forwarding} consists in ensuring that each
+\process $x$ eventually receives $\alpha_s^{|\Pi_{sx}|}$ where
+$\Pi_{sx}$ is the \emph{best} path from any source to it; the best
+value $|\Pi_{sx}|$ being built over forwarding along this path.
 
@@
 
-Algorithm~\ref{algo:add} shows the few instructions that implement a
+Algorithm~\ref{algo:add} shows the instructions that implement a
 \emph{reactive} forwarding of best to reach consistent partitioning in
@@
 
-While only adding logical partitions to the distributed system is
+While adding logical partitions to the distributed system is
 straightforward and lightweight, removing them introduces additional
@@
 \begin{proof}
-Stale control information as stated in Definition~\ref{def:lwo} may
-impair the propagation of both
+Stale control information (see Definition~\ref{def:lwo}) may impair
+the propagation of both
 \begin{inparaenum}[(i)]
@@
 of $\alpha_c^1$ and the delivery of $\delta_c$, $b$ blocked any other
-$\delta$.
+$\delta$ and therefore $\delta_a$.
 
@@
 notifications, we propose to reduce the scope of staleness
-notifications by including only downstream \processes. In
+notifications by including \TODO{only downstream \processes}. In
 Figure~\ref{fig:undoproblemD}, false positives would not affect $a$

### 2021-12-16 input/proposal.tex
address some issues, todo others

@@
 
-\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
+\begin{definition}[\label{def:scoped}Scoped broadcast]
   When \Process~$x$ scoped \underline{b}roadcasts $b_x(m)$ a
@@
 \begin{definition}[\label{def:forwarding}Forwarding]
-  A \process $x$ \underline{f}orwards a message $m$ by
-  \underline{s}ending it to its neighbors $y$ \TODO{enriched}
-  ($\oplus$) with metadata that depends on its local knowledge
-  $\sigma_x$: $f_x(m) \implies \forall \langle x, y\rangle \in E:
-  s_{xy}(m \TODO{\oplus} \sigma_x)$.
+  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
+  \underline{s}ends $s_{xy}(m)$ the latter to all its neighbors $y$
+  \TODO{enriched} ($\oplus$) with metadata that depends on its local
+  knowledge $\sigma_x$:
+  $f_x(m) \implies \forall \langle x, y\rangle \in E: s_{xy}(m
+  \TODO{\oplus} \sigma_x)$.
 \end{definition}
@@
 the network state. For \processes to eventually ($\eventually$) reach
-consistent partitioning, each source $s$ must send
+consistent partitioning (CP), each source $s$ must send
 \texttt{\underline{A}dd} notifications $\alpha_s$ to all \processes
 that are closer to it than any other source, along with enough
-metadata to allow them to decide of their closest source. A simple
-implementation based on Definition~\ref{def:scoped} and
-Definition~\ref{def:forwarding} consists in ensuring that each
-\process $x$ eventually receives $\alpha_s^{|\Pi_{sx}|}$ where
-$\Pi_{sx}$ is the \emph{best} path from any source to it; the best
-value $|\Pi_{sx}|$ being built over forwarding along this path.
+metadata to allow them to decide of their closest source. Based on
+Definition~\ref{def:scoped} and Definition~\ref{def:forwarding}, this
+consists in ensuring that each \process $x$ eventually receives
+$\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
+any source to it; the best value $|\Pi_{sx}|$ being built over
+forwarding along this path.
 
@@
     Assuming that each \process $x$ stores its outgoing weights
-    ($\forall \langle x, y \rangle \in E: \pi_{xy} \in \sigma_x$), a
+    ($\forall \langle x, y \rangle \in E: w_{xy} \in \sigma_x$), a
     total order on messages based on weights ($m^d_s < m^{d'}_{s'}$
@@
   messages $R_x$ at neighboring \process~$x$, total order ensures that
-  it delivers notifications $\alpha_s^{d}$ when $d= |\pi_{ss}| +
-  w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$ is the lightest
-  weight of $x$ to any source $s'$.
+  it delivers notifications $\alpha_s^{d}$ when
+  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
+  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
+  this case.
   \noindent Among these neighbors, at least those that fulfill the
@@
 behavior of this algorithm on a system comprising 4 \processes $a$,
-$b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
+$b$, $c$, and $d$. Both $a$ and $d$ become sources.  They scoped broadcast
 notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
@@
 notifications $\alpha_s$ -- should be canceled by the corresponding
-\texttt{\underline{D}el} notifications $\delta_s$. We focus on the
-last delivery of each \process, since the best is also the last, as
-highlighted by Algorithm~\ref{algo:add}.
+\texttt{\underline{D}el} notifications of staleness $\delta_s$. We
+focus on the last delivery of each \process, since the best is also
+the last, as highlighted by Algorithm~\ref{algo:add}. \TODO{More about
+  useless $\alpha$ ?}
 
@@
 
-A naive attempt at implementing DCP resembles echoes in
-acoustics. Following the principles of scoped broadcast as stated in
-Definition~\ref{def:scoped}, a \process that receives a staleness
-notification forwards it only if the latter targets its current
-partition. The staleness notifications propagate through the network
-as long as they remain in the deleted partition. When they reach the
-bordering \processes of the deleted partition, it creates an echo of
-bordering partitions that will go backward to fill the gap left open
-by removals using forwarding of best (FB) as stated by
-Theorem~\ref{theo:fb}.
+A naive attempt at implementing DCP resembles echoes in acoustics: a
+sound propagates in the air before crashing into surrounding walls to
+finally come back altered. Following the principles of scoped
+broadcast as stated in Definition~\ref{def:scoped}, a \process $x$
+that receives a staleness notification $\delta_s$ forwards it only if
+the latter targets its current partition $\alpha_s$. The staleness
+notifications propagate through the network as long as they remain in
+the deleted partition. When they reach the bordering \processes of the
+deleted partition, it creates an echo of bordering partitions that
+will go backward to fill the gap left open by removals using
+forwarding of best (FB) as stated by Theorem~\ref{theo:fb}.
 
@@
 already deleted it, but it could contribute to its inconsistency by
-blocking farther but up-to-date messages from actual sources.
+not forwarding farther but up-to-date messages from actual sources.
 
@@
 of $\alpha_c^1$ and the delivery of $\delta_c$, $b$ blocked any other
-$\delta$ and therefore $\delta_a$.
+$\delta$ and therefore $\delta_a$.  \TODO{Must take action because its
+  parent has forwarded something already stale so previous cannot be
+  good.}
 

### 2021-12-20 input/experiments.tex
about algo
update figure, not nearly done though

@@
     comprising 40 interconnected autonomous systems spanning across
-    Europe. The generated trace marked with red dots starts from
-    Lisboa to reach Copenhagen 10 seconds later.]{
+    Europe~\cite{knight2011internet}. The generated trace marked with
+    red dots starts from Lisboa to reach Copenhagen 10 seconds
+    later.]{
     \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
   } \subfloat[PartB][\label{fig:xascast}\TODO{PLACEHOLDER}
-    \TODO{Experiment with ascast against xascast?}]{
-    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
+    \TODO{Experiment with ascast against xascast? with different cache
+      size}]{
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/xas_cast_line.eps}
   }
-  \caption{\TODO{Experiment measuring something on such a trace.}}
+  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
 \end{figure*}

### 2021-12-21 input/figsimplerproblem.tex
meow
reworked figures mostly
all figures completed with what happens

@@
   \newcommand{\SCALE}{0.9}
+
+  \newcommand{\SMSG}{\tiny}
+  \newcommand{\OACK}{0.5}
+
+  \thickmuskip=0mu
+  \medmuskip=0mu
+  \thinmuskip=0mu
+
+  \newcommand\X{50pt}
+  \newcommand\Y{-50pt}
 
@@
       $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
-    \hspace{0pt}
+    \hspace{5pt}
     \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
@@
              {\input{input/figsimplerproblemB.tex}}
-    \hspace{0pt}
+    \hspace{5pt}
     \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
@@
              {\input{input/figsimplerproblemC.tex}}
-    \hspace{0pt}
-    \subfloat[Part D][\label{fig:problemD}$b$ delivers and forwards $\delta_c$. $c$
+    \hspace{5pt}
+    \subfloat[Part D][\label{fig:problemD}\TODO{$b$ blocks the only transiting
+      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.}]
+             {\input{input/figsimplerproblemD.tex}}
+    \hspace{5pt}
+    \subfloat[Part E][\label{fig:problemE}\TODO{$b$ blocks the only transiting
+      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.}]
+             {\input{input/figsimplerproblemE.tex}}
+    \hspace{5pt}
+    \subfloat[Part F][\label{fig:problemF}$b$ delivers and forwards $\delta_c$. $c$
     stays in the deleted partition $P_a$.]
-             {\input{input/figsimplerproblemD.tex}}
+             {\input{input/figsimplerproblemF.tex}}
   \end{center}
@@
     too.
-
+    %
     % Despite both scenarios look the same from $c$'s perspective, $c$

### 2021-12-21 input/figundoproblem.tex
reworked figures mostly
all figures completed with what happens

@@
   \newcommand{\SCALE}{0.9}
+
+  \thickmuskip=0mu
+  \medmuskip=0mu
+  \thinmuskip=0mu
+
+  \newcommand\X{50pt}
+  \newcommand\Y{-50pt}
+
+  \newcommand{\OACK}{0.5}
+  \newcommand{\SMSG}{\tiny}
+
   \newcommand{\LEFT}{\triangleleft}
   \newcommand{\RIGHT}{\triangleright}
+
   \begin{center}
@@
       $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
-    \hspace{0pt}
+    \hspace{5pt}
     \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
@@
              {\input{input/figundoproblemB.tex}}
-    \hspace{0pt}
+    \hspace{5pt}
     \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
              {\input{input/figundoproblemC.tex}}
-    \hspace{0pt}
-    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
+    \hspace{5pt}
+    \subfloat[Part D][\label{fig:undoproblemD}\TODO{$b$ delivers and forwards $\alpha_c$.}]
              {\input{input/figundoproblemD.tex}}
+    \hspace{5pt}
+    \subfloat[Part E][\label{fig:undoproblemE}\TODO{$b$ delivers and forwards $\alpha_c$.}]
+             {\input{input/figundoproblemE.tex}}
+    \hspace{5pt}
+    \subfloat[Part F][\label{fig:undoproblemF}$b$ delivers and forwards $\delta_c$.]
+             {\input{input/figundoproblemF.tex}}
   \end{center}

### 2021-12-21 input/figdel.tex
adapting to two columns, stilltodo. simpler problem display
about example
mostly about algo text
separating issues
better plan?
meow

@@
 \begin{figure}
+  \newcommand{\SCALE}{0.95}
+
+  \newcommand{\LEFT}{\triangleleft}
+  \newcommand{\RIGHT}{\triangleright}
+
   \begin{center}
-    \subfloat[Part A][\label{fig:delA}\Process~$a$ deletes its
-      partition.  It notifies all \processes that belong to its
+    \subfloat[Part A][\label{fig:delA}$a$ deletes its partition. It
+      notifies all \processes that belong to its
       partition.]{\input{input/figdelA.tex}}
-    \hspace{5pt}
-    %
-    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as they
-      encounter another partition. \Process~$b$ answers with its
-      partition.]{\input{input/figdelB.tex}}
+    \hspace{3pt}
+    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as it encounters
+      another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
   \end{center}
   \caption{\label{fig:del}Efficient removal of a partition using
-    \NAMEB. $a$ eventually knows that it belongs to $P_d$.}
+    scoped broadast. $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
 \end{figure}

### 2021-12-21 input/figsimplerproblem.tex
meow

--- 2021-11-16 input/figsimplerproblem.tex
@@
              {\input{input/figsimplerproblemC.tex}}
-    \hspace{0pt}
-    \subfloat[Part D][\label{fig:problemD}$b$ delivers and forwards $\delta_c$. $c$
-    stays in the deleted partition $P_a$.]
+    \hspace{5pt}
+    \subfloat[Part D][\label{fig:problemD}$\alpha_c^3$ reaches $a$ that delivers it.]
              {\input{input/figsimplerproblemD.tex}}
+    \hspace{5pt}
+    \subfloat[Part E][\label{fig:problemE}$\delta_c$ reaches $a$ that delivers it.]
+             {\input{input/figsimplerproblemE.tex}}
+    \hspace{5pt}
+    \subfloat[Part F][\label{fig:problemF}$a$ and $b$ do not belong to any partition but
+      $c$ stays forever in a stale one: $P_a$.]
+             {\input{input/figsimplerproblemF.tex}}
   \end{center}
-  \caption{\label{fig:problem}Even in the simplest scenarios, naive
-    propagation of $\alpha$ and $\delta$ messages may be insufficient
-    to guarantee consistent partitioning. In the bottom scenario, if
-    $c$ had children, they would stay in the wrong partition
-    too.
-
-    % Despite both scenarios look the same from $c$'s perspective, $c$
-    % must acknowledge $P_a$'s \emph{possible} deletion and propagate
-    % it.
-  }
+  \caption{\label{fig:problem}Even in the simplest scenarios, the
+    naive propagation of $\alpha$ and $\delta$ messages may be
+    insufficient to guarantee consistent partitioning. If $c$ had
+    children, they would stay in the wrong partition too.}
 \end{figure*}

### 2021-12-21 input/figundoproblem.tex
meow

--- 2021-12-07 input/figundoproblem.tex
@@
              {\input{input/figundoproblemB.tex}}
-    \hspace{0pt}
+    \hspace{5pt}
     \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
              {\input{input/figundoproblemC.tex}}
-    \hspace{0pt}
+    \hspace{5pt}
     \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
              {\input{input/figundoproblemD.tex}}
+    \hspace{5pt}
+    \subfloat[Part E][\label{fig:undoproblemE}$a$ echoes back $\alpha_a^2$ that $b$ needs.]
+             {\input{input/figundoproblemE.tex}}
+    \hspace{5pt}
+    \subfloat[Part F][\label{fig:undoproblemF}$a$, $b$, and $c$ belong to $P_a$.]
+             {\input{input/figundoproblemF.tex}}
   \end{center}
-  \caption{\label{fig:undoproblem}From $c$'s perspective, this
-    scenario and Figure~\ref{fig:problem} are similar. Even when $a$
-    did not delete its partition, $c$ must acknowledge $P_a$'s
-    \emph{possible} deletion and propagate it.}
+  \caption{\label{fig:undoproblem}From $c$'s perspective,
+    Figure~\ref{fig:problemE} and Figure~\ref{fig:undoproblemE} are
+    similar in terms of received messages, but the outcomes eventually
+    differ. Yet, $c$ must act on Figure~\ref{fig:undoproblemE}, and
+    acknowledge then propagate the \emph{possible} staleness of its
+    partition $P_a$.}
 \end{figure*}

### 2022-01-03 input/proposal.tex
wip

@@
 discards $\delta_a$, for its best partition does not match the deleted
-one. We simplify the echo since $\alpha_c^3$ is already transiting
-towards $a$. Finally, Figure~\ref{fig:problemD} shows that eventually,
-$c$ stays in the deleted partition $P_a$ for not having received
-$\delta_a$ that $b$ blocked earlier. The system does not reach
-consistent partitioning. \end{proof}
+one. It echoes back $\alpha_c^3$ to $a$. In Figures~\ref{fig:problemD}
+and \ref{fig:problemE}, $a$ and $b$ handle transiting
+notifications. Finally, Figure~\ref{fig:problemF} shows that
+eventually, $c$ stays in the deleted partition $P_a$ for not having
+received $\delta_a$ that $b$ blocked earlier. The system does not
+reach consistent partitioning. \end{proof}
 
-As a cascading effect in Figure~\ref{fig:problemD}, not only $c$
-wrongfully believes that it belongs to $a$'s partition when $a$
-already deleted it, but it could contribute to its inconsistency by
-not forwarding farther but up-to-date messages from actual sources.
+The issue is that each \process trusts its parent to forward all
+staleness notifications relevant to it. When this fails, as in
+Figure~\ref{fig:problem}, not only a \process ($c$) may wrongfully
+stay in a partition ($P_a$) when its source ($a$) already deleted it,
+but it may contribute to its inconsistency by not forwarding farther
+but up-to-date messages from live sources.
 
@@
 detect the blocking of staleness notifications that can hinder
-reaching consistent partitioning. For instance, $c$ detects the
-blocking of $\delta_a$ because it acknowledges that its parent $b$
-delivered a stale notification $\alpha_c^1$, \ie between the delivery
-of $\alpha_c^1$ and the delivery of $\delta_c$, $b$ blocked any other
-$\delta$ and therefore $\delta_a$.  \TODO{Must take action because its
-  parent has forwarded something already stale so previous cannot be
-  good.}
+reaching consistent partitioning.  In Figure~\ref{fig:problem}, $b$
+blocked the staleness notification $\delta_a$ that $c$ needs since it
+belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
+stale before $b$ does. Therefore, $c$ can detect the blocking of
+$\delta_a$ since it acknowledges that its parent $b$ received,
+delivered, and forwarded the stale notification $\alpha_c^1$. In other
+terms, $c$ acknowledges that between the delivery of $\alpha_c^1$ and
+the delivery of $\delta_c$, $b$ blocked any other $\delta$ and
+therefore, it could have blocked $\delta_a$.
 
@@
   $\alpha_x$ with $\alpha_x = \last D_z$, if $x$ broadcasts a staleness
-  notification $\delta_x$, either $z$ eventually delivers it, or a
-  \process $y$ in such a chain of delivery $\pi_{xz}'$ eventually
-  acknowledges its blocking.
+  notification $\delta_x$, either
+  \begin{inparaenum}[(A)]
+  \item\label{lem:detectorA}  $z$ eventually delivers it, or 
+  \item\label{lem:detectorB} a \process $y$ in such a chain of
+    delivery $\pi_{xz}'$ eventually acknowledges its blocking.
+  \end{inparaenum}
   % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
@@
   %% receive delta or detect blocking
-  (A) Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
-  $\alpha_x$ with $\forall y \in \pi_{xz}: \alpha_x = \last D_y$, and
-  assuming $d_x(\delta_x)$, then with forwarding of staleness
-  (Definition~\ref{def:fs}),
-  $f_{\pi_{xz}[k]}(\delta_x) \implies \eventually
-  d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in D_{\pi_{xz}[k+1]}$ which
-  means that $\pi_{xz}[k+1]$ already delivered and forwarded $\delta_x$
-  following another such a chain of delivery. Therefore, $z$
-  eventually receives, hence delivers $\delta_x$.
+  Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
+  $\alpha_x$, we must prove that whatever the possible states of
+  \nodes that belong to this chain, \TODO{WIP}
+  \begin{asparadesc}
+  \item [In the same partition:] $\forall y \in \pi_{xz}: \alpha_x =
+    \last D_y$, and assuming $d_x(\delta_x)$, then with forwarding of
+    staleness (Definition~\ref{def:fs}), $f_{\pi_{xz}[k]}(\delta_x)
+    \implies \eventually d_{\pi_{xz}[k+1]}(\delta_x)$ except if
+    $\delta_x \in D_{\pi_{xz}[k+1]}$ which means that $\pi_{xz}[k+1]$
+    already delivered and forwarded $\delta_x$ following another such
+    a chain of delivery. Therefore, $z$ eventually receives, hence
+    delivers $\delta_x$.
 
-  \noindent (B) Assuming a chain of delivery
+  \item[ (\ref{lem:detectorB})] Assuming a chain of delivery
   $\pi_{xz} = [x, \ldots, z]$ of $\alpha_x$ with at least
@@
     the detection to another \process.
-  \end{enumerate} \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed
+  \end{enumerate}
+  \end{asparadesc}
+  \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed
   %

### 2022-01-03 input/proposal.tex
address comments up to IIID

@@
   Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
-  $\alpha_x$, we must prove that whatever the possible states of
-  \nodes that belong to this chain, \TODO{WIP}
+  $\alpha_x$ with $\alpha_x = \last D_z$ and $d_x(\delta_x$), we must
+  prove that whatever the possible states of \nodes that belong to
+  this chain, it either leads to outcome (\ref{lem:detectorA}) or
+  (\ref{lem:detectorB}).
   \begin{asparadesc}
-  \item [In the same partition:] $\forall y \in \pi_{xz}: \alpha_x =
-    \last D_y$, and assuming $d_x(\delta_x)$, then with forwarding of
-    staleness (Definition~\ref{def:fs}), $f_{\pi_{xz}[k]}(\delta_x)
-    \implies \eventually d_{\pi_{xz}[k+1]}(\delta_x)$ except if
-    $\delta_x \in D_{\pi_{xz}[k+1]}$ which means that $\pi_{xz}[k+1]$
-    already delivered and forwarded $\delta_x$ following another such
-    a chain of delivery. Therefore, $z$ eventually receives, hence
-    delivers $\delta_x$.
+  \item [(I) Same last partition:] $\forall y \in \pi_{xz}: \alpha_x =
+    \last D_y$, with forwarding of staleness
+    (Definition~\ref{def:fs}), $f_{\pi_{xz}[k]}(\delta_x) \implies
+    \eventually d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in
+    D_{\pi_{xz}[k+1]}$ which means that $\pi_{xz}[k+1]$ already
+    delivered and forwarded $\delta_x$ following another such a chain
+    of delivery. Therefore, $z$ eventually receives, hence delivers
+    $\delta_x$ (outcome \ref{lem:detectorA}).
 
-  \item[ (\ref{lem:detectorB})] Assuming a chain of delivery
-  $\pi_{xz} = [x, \ldots, z]$ of $\alpha_x$ with at least
-  $\alpha_x = \last D_z$, and assuming $d_x(\delta_x)$, then by (A),
-  the staleness notification reaches a \process $ y = \pi_{xz}[k]$. By
-  Definition~\ref{def:fs}, the forwarding stops when $y$ already
-  delivered $\delta_x$ ($\delta_x \in D_y$ covered by (A)) or
-  delivered a better message $\alpha_s = \last D_y$ with
-  $\alpha_s \neq \alpha_x$. With $y'=\pi_{xz}[k+1]$, forwarding of
-  best (Definition~\ref{def:fbplus}) implies three possible outcomes:
-  \begin{enumerate}[(i)]
-  \item $\alpha_{s'} = \last D_{y'}$ with $\alpha_{s'} \neq \alpha_x$
-    hence $y' \iff y$ which leaves two possible outcomes:
-  \item
-    $r_{y'}(\alpha_s) \wedge \alpha_x = \last D_{y'} \wedge \alpha_x <
-    \alpha_s$ which means that a shorter path of delivery $\pi_{xz}'$
-    exists that either forwards appropriate staleness notifications
-    (A) or detects its possible blocking:
-  \item
-    $r_{y'}(\alpha_s) \wedge \delta_s \in D_{y'} \wedge \alpha_x =
-    \last D_{y'}$ which detects a possible blocking of
-    $\delta_x$. Without global knowledge, $y'$ assumes it belongs to
-    the shortest and only path of delivery of $\alpha_x$
-    ($\pi_{xy'} \subseteq \Pi_{xz}$) thus it does not further delegate
-    the detection to another \process.
-  \end{enumerate}
+  \item[(II) Different last partitions:] $\exists y \in \pi_{xz}
+    \setminus \{x, z\}: \alpha_s = \last D_y$, by (I), the staleness
+    notification reaches the first of such a \process $y =
+    \pi_{xz}[k]$.  Forwarding of staleness (Definition~\ref{def:fs})
+    states that the forwarding stops when $y$ already delivered
+    $\delta_x$ ($\delta_x \in D_y$ covered by (I)) or delivered a
+    better message $\alpha_s = \last D_y$.  With $y'=\pi_{xz}[k+1]$,
+    forwarding of best (Definition~\ref{def:fbplus}) implies three
+    possible results:
+  \begin{asparadesc}
+  \item [(i) $y'$ equivalent to $y$:] $\alpha_{s'} = \last D_{y'}$
+    with $\alpha_{s'} \neq \alpha_x$ hence $y' \iff y$ which leaves
+    two possible results as follows:
+  \item [(ii) $y'$ in $P_x$ from another parent:] $r_{y'}(\alpha_s)
+    \wedge \alpha_x = \last D_{y'} \wedge \alpha_x < \alpha_s$ which
+    means that a shorter path of delivery $\pi_{xz}'$ exists that
+    either forwards appropriate staleness notifications (covered by
+    (I)) or detects its possible blocking as follows:
+  \item [(iii) $y'$ in $P_x$ with $y$ as parent] but does not deliver
+    the $y$'s last partition for it already delivered the
+    corresponding staleness notification: $r_{y'}(\alpha_s) \wedge
+    \delta_s \in D_{y'} \wedge \alpha_x = \last D_{y'}$ which detects
+    a possible blocking of $\delta_x$ (outcome
+    (\ref{lem:detectorB})). Without global knowledge, $y'$ assumes it
+    belongs to the shortest and only path of delivery of $\alpha_x$
+    % ($\pi_{xy'} \subseteq \Pi_{xz}$)
+    thus it cannot further delegate the detection to another \process.
+  \end{asparadesc}
   \end{asparadesc}
@@
 system from their forwarded notifications. For instance in
-Figure~\ref{fig:problemD}, $c$ could broadcast $\delta_a$ in order to
+Figure~\ref{fig:problemF}, $c$ detects the blocking of the staleness
+notification $\delta_a$. It could broadcast $\delta_a$ in order to
 acknowledge the staleness of its own $\alpha_a^3$ and inform
-neighboring \processes that delivered it as well. Unfortunately, proof
-of Lemma~\ref{lem:detector} shows that there exists false positive in
-the blocking detection: $\delta_x$ may not exist but $y'$ still
-receives $\alpha_s$ after the delivery of $\delta_s$ from the path it
-delivered $\alpha_x$. Figure~\ref{fig:undoproblem} highlights this
-behavior. In Figure~\ref{fig:undoproblemB}, $a$ does not delete its
-partition. In Figure~\ref{fig:undoproblemD} and because of scoped
-broadcast, $c$ received the same series of messages as in
-Figure~\ref{fig:problemD}. Yet, $c$ must assume the existence of
+neighboring \processes that delivered it as well. Unfortunately, there
+exists false positive in the blocking detection.
+Lemma~\ref{lem:detector}'s proof shows that the detection at $y'$ does
+not depend on $\delta_x$. Therefore $\delta_x$ may not exist but $y'$
+still receives $\alpha_s$ after the delivery of $\delta_s$ from the
+path it received and delivered
+$\alpha_x$. Figure~\ref{fig:undoproblem} highlights this behavior. In
+Figure~\ref{fig:undoproblemB}, $a$ does not delete its partition. In
+Figure~\ref{fig:undoproblemF} and because of scoped broadcast, $c$
+received the same series of messages as in
+Figure~\ref{fig:problemF}. Yet, $c$ must assume the existence of
 $\delta_a$ and act accordingly by forcing the staleness of its best
@@
 To avoid flooding the system with false positive staleness
-notifications, we propose to reduce the scope of staleness
-notifications by including \TODO{only downstream \processes}. In
-Figure~\ref{fig:undoproblemD}, false positives would not affect $a$
-and $b$.
+notifications, we reduce the scope of staleness notifications by
+including only downstream \processes. In
+Figure~\ref{fig:undoproblemF}, false positives would generate traffic
+at $c$ and its children if it had any, without impacting $a$ and $b$.
 
@@
 forwarding of staleness downstream as stated in
-Definition~\ref{def:fsplus},
+Definition~\ref{def:fsplus}:
 \begin{inparaenum}[(A)]
@@
 message. Receiving a message known to be stale from this parent
-triggers the generation of staleness notifications that force
-downstream \processes to reevaluate the partition they are in (see
-Line~\ref{line:detect}).
+triggers the generation of staleness notifications that can only be
+delivered by downstream \processes (see Line~\ref{line:detect}).
 
@@
 
-By reusing \NAME's default behavior, Algorithm~\ref{algo:edges}
-enables dynamic consistent partitioning in dynamic networks subject to
-physical partitioning where \processes can join, leave, or crash at
-any time. Adding a \process is equivalent to add as many edges as
-necessary. Since adding an edge may improve shortest paths, the
-protocol triggers a competition using echos of
-Definition~\ref{def:fbplus}.  Removing a \process is equivalent to
-removing all its edges. Removing an edge between two \processes may
-invalidate the shortest path of one of involved \processes plus
-downstream \processes, or impair the propagation of staleness
-notifications. Therefore, the protocol reuses its detectors of
-Lemma~\ref{lem:detector} to remove irrelevant messages from the
+By reusing \NAME's default behavior of echos and downstream staleness,
+Algorithm~\ref{algo:edges} enables dynamic consistent partitioning
+even in dynamic networks subject to physical partitioning where
+\processes can join, leave, or crash at any time. Adding a \process is
+equivalent to add as many edges as necessary. Since adding an edge may
+improve shortest paths, the protocol triggers a competition using
+echos of Definition~\ref{def:fbplus}.  Removing a \process is
+equivalent to removing all its edges. Removing an edge between two
+\processes may invalidate the shortest path of one of involved
+\processes plus downstream \processes, or impair the propagation of
+staleness notifications. Therefore, the protocol reuses its detectors
+of Lemma~\ref{lem:detector} to remove irrelevant messages from the
 system.

### 2022-01-06 input/proposal.tex
skeletton for xascast, discarded for submit

@@
 
+\input{input/figxasproblem.tex}
+
 To further reduce the traffic generated by our DCP protocol, we
-leverage that an Edge infrastructure is a network of autonomous
-systems, only a small subset of which needs logical partitioning.
+leverage that an Edge infrastructure is a \TODO{network of autonomous
+systems}, only a small subset of which needs logical partitioning.
 
@@
 
+\begin{definition}[\TODO{Adjacent networks}]
+\end{definition}
+
 \begin{definition}[Lazy dynamic consistent partitioning (LDCP)]
@@
 
-To enable LDCP in an Edge infrastructure, we use the property provided
+\TODO{A naive implementation would consist in using gateways as
+  additional gatekeepers of scoped broadcast. Figure that shows that
+  it works mostly.}
+
+\begin{lemma}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{G} \centernot\implies \textup{LDCP}$]
+  \TODO{meow}
+\end{lemma}
+
+\begin{proof}
+  \TODO{meow meow}
+\end{proof}
+
+\TODO{To enable LDCP in an Edge infrastructure, we use the property provided
 by DCP in an autonomous system to all its \processes and among others,
-to its gateways.
+to its gateways.}
 

### 2022-01-06 input/background.tex
starting with xas, small changes here and there
comment xas-cast

--- 2021-09-02 input/background.tex
@@
 \label{sec:background}
-
-\input{input/figpartitionintuition.tex} %% positioning
 
@@
 propagation of other partitions (see Section~\ref{subsec:dynamic}).
+
+%% \item [Lazy partitioning:]
+
+%% \TODO{Finally, in Figure~\ref{fig:partition_intuition}, every nodes of
+%%   the system maintains an index to every content. In systems
+%%   comprising billions of content, this could constitute a scalability
+%%   issue. The partitioning protocol should take advantage of boundary
+%%   between autonomous systems in the Internet. For instance, the AS
+%%   from France should not flood the AS from Spain unless the latter
+%%   starts to host a replica. In addition, when the system removes its
+%%   last source, it should stop receiving messages from other ASes
+%%   designed to maintain the closest partition.}
+
 \end{asparadesc}

### 2022-01-06 input/proposal.tex
comment xas-cast

--- 2022-01-03 input/proposal.tex
@@
 when they are able to detect possible blocking conditions in the
-dissemination of required notifications. Finally, it further constrain
+dissemination of required notifications. \TODO{Finally, it further constrain
 the system by allowing only subsets of \processes to reach lazy
 consistent partitioning. This improvement only requires \processes to
-know which of their neighbors belong to their own network.
+know which of their neighbors belong to their own network.}
 
@@
 
-\subsection{Lazy dynamic consistent partitioning}
-\label{subsec:lazy}
+%% \subsection{Lazy dynamic consistent partitioning}
+%% \label{subsec:lazy}
 
-To further reduce the traffic generated by our DCP protocol, we
-leverage that an Edge infrastructure is a network of autonomous
-systems, only a small subset of which needs logical partitioning.
+%% \input{input/figxasproblem.tex}
 
-\begin{definition}[Edge infrastructure]
-  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
-  interconnected with additional links $\mathcal{E} \in V_1 \times
-  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
-  \ldots G_n\}, \mathcal{E} \rangle$. A \underline{g}ateway $g$ is a
-  \process with at least one link towards another network: $\langle g,
-  \_ \rangle \in \mathcal{E}$.
-\end{definition}
+%% To further reduce the traffic generated by our DCP protocol, we
+%% leverage that an Edge infrastructure is a \TODO{network of autonomous
+%% systems}, only a small subset of which needs logical partitioning.
 
-At any time, an autonomous system start logical partitioning when a
-\process from this network becomes a source.  Then every \process from
-this network belongs to the partition of its closest source not only
-from their own network but that of adjacent networks that started
-logical partitioning as well.  At any time, an autonomous system stops
-logical partitioning when the last source from this network revokes
-its status of source. Eventually, all nodes from this network do not
-belong to any partition and the generated traffic stops.
+%% \begin{definition}[Edge infrastructure]
+%%   An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
+%%   interconnected with additional links $\mathcal{E} \in V_1 \times
+%%   V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
+%%   \ldots G_n\}, \mathcal{E} \rangle$. A \underline{g}ateway $g$ is a
+%%   \process with at least one link towards another network: $\langle g,
+%%   \_ \rangle \in \mathcal{E}$.
+%% \end{definition}
 
-\begin{definition}[Lazy dynamic consistent partitioning (LDCP)]
-  \TODO{If there exists at least a source in a network, its nodes must
-    belong to the partition of the closest partition in adjacent
-    networks. Otherwise, nodes must eventually belong to no
-    partition.}
-\end{definition}
+%% At any time, an autonomous system start logical partitioning when a
+%% \process from this network becomes a source.  Then every \process from
+%% this network belongs to the partition of its closest source not only
+%% from their own network but that of adjacent networks that started
+%% logical partitioning as well.  At any time, an autonomous system stops
+%% logical partitioning when the last source from this network revokes
+%% its status of source. Eventually, all nodes from this network do not
+%% belong to any partition and the generated traffic stops.
 
-To enable LDCP in an Edge infrastructure, we use the property provided
-by DCP in an autonomous system to all its \processes and among others,
-to its gateways.
+%% \begin{definition}[\TODO{Adjacent networks}]
+%% \end{definition}
 
-\begin{lemma}[Source existence]
-  When a system becomes quiescent, DCP guarantees that every \process
-  eventually acknowledges the existence or non-existence of a source
-  in its system.
-\end{lemma}
+%% \begin{definition}[Lazy dynamic consistent partitioning (LDCP)]
+%%   \TODO{If there exists at least a source in a network, its nodes must
+%%     belong to the partition of the closest partition in adjacent
+%%     networks. Otherwise, nodes must eventually belong to no
+%%     partition.}
+%% \end{definition}
 
-\begin{proof}
-  By design.
-\end{proof}
+%% \TODO{A naive implementation would consist in using gateways as
+%%   additional gatekeepers of scoped broadcast. Figure that shows that
+%%   it works mostly.}
 
-The gateways become responsible for the flooding or the stopping of
-notifications foreign to their respective network. They must
-differentiate between local and global notifications. Local
-notifications provide both \begin{inparaenum}[(i)]
-\item local source existence, and
-\item closest local source in the network
-\end{inparaenum}; while global notifications only improve on closest global sources,
-\ie it does not need to propagate when the foreign source is farther
-than the local one.
+%% \begin{lemma}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{G} \centernot\implies \textup{LDCP}$]
+%%   \TODO{meow}
+%% \end{lemma}
 
-\begin{definition}[\underline{B}roadcasting of \underline{u}ninterested (BU)]
-  \TODO{meow}
-\end{definition}
+%% \begin{proof}
+%%   \TODO{meow meow}
+%% \end{proof}
 
-\TODO{Blocking condition local global remains.}
+%% \TODO{To enable LDCP in an Edge infrastructure, we use the property provided
+%% by DCP in an autonomous system to all its \processes and among others,
+%% to its gateways.}
 
-\TODO{Added invariant: global is always smaller than local when they
-  exist.}
+%% \begin{lemma}[Source existence]
+%%   When a system becomes quiescent, DCP guarantees that every \process
+%%   eventually acknowledges the existence or non-existence of a source
+%%   in its system.
+%% \end{lemma}
 
-\begin{algorithm}[h]
-  \input{input/algoxascast.tex}
-  \caption{\label{algo:xascast}\NAMEC at \Process~$p$. \TODO{TODO.}}
-\end{algorithm}
+%% \begin{proof}
+%%   By design.
+%% \end{proof}
+
+%% The gateways become responsible for the flooding or the stopping of
+%% notifications foreign to their respective network. They must
+%% differentiate between local and global notifications. Local
+%% notifications provide both \begin{inparaenum}[(i)]
+%% \item local source existence, and
+%% \item closest local source in the network
+%% \end{inparaenum}; while global notifications only improve on closest global sources,
+%% \ie it does not need to propagate when the foreign source is farther
+%% than the local one.
+
+%% \begin{definition}[\underline{B}roadcasting of \underline{u}ninterested (BU)]
+%%   \TODO{meow}
+%% \end{definition}
+
+%% \TODO{Blocking condition local global remains.}
+
+%% \TODO{Added invariant: global is always smaller than local when they
+%%   exist.}
+
+%% \begin{algorithm}[h]
+%%   \input{input/algoxascast.tex}
+%%   \caption{\label{algo:xascast}\NAMEC at \Process~$p$. \TODO{TODO.}}
+%% \end{algorithm}
+
+\TODO{Transition to experiments.}
 

### 2022-01-10 input/related_work.tex
adapting to two columns, stilltodo. simpler problem display
few fixes, add physarum to biblio
physarum related work

@@
 
+\TODO{Vector routing protocols.} 
 Content indexing services in geo-distributed infrastructures allow
@@
 \underline{i}nformation-\underline{c}entric \underline{n}etworking
-(ICN)~\cite{garcia-lopez, hemmati2015namebased}. They periodically
-advertise their cache content, and advertisements stop as soon as they
-reach uninterested \processes. However their operation requires that
+(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
+clustering~\cite{sohier2012physarum}. The sources advertise themselves
+periodically. Advertisements either stop as soon as they reach
+uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
+probabilistically propagate through most likely interested
+\processes~\cite{sohier2012physarum}. However their operation requires
+that
 \begin{inparaenum}[(i)]
@@
   \processes do not add nor destroy replicas; and 
-\item they define physical-clock-based timeouts the value of which
-  depends on network topology properties such as network diameter.
+\item they either operate in synchronous
+  systems~\cite{sohier2012physarum} or must define
+  physical-clock-based timeouts the value of which depends on network
+  topology properties such as network diameter~\cite{garcia-lopez,
+    hemmati2015namebased}.
   %also incur an overhead even in quiet contexts without any update.
@@
 On the opposite, \NAME quickly informs each \process of its closest
-replica even in large networks; % when the system is quiescent,
-and has no overhead when the system is quiescent.
+replica even in large and dynamic networks with asynchronous
+communications; and has no overhead when the system is quiescent.
 

### 2022-01-10 input/experiments.tex
experiment europe

--- 2021-09-09 input/experiments.tex
@@
 
+\begin{figure*}
+  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
+    comprising 40 interconnected autonomous systems spanning across
+    Europe~\cite{knight2011internet}.]{
+    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
+  } \subfloat[PartB][\label{fig:xascast}
+    \TODO{Experiment with ascast against xascast? with different cache
+      size}]{
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
+  }
+  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
+\end{figure*}
+
 %% Next Section reviews state-of-the-art approaches for content indexing

### 2022-01-12 input/experiments.tex
move complexity to expe + positioning fig + small fix

@@
 %% dynamic networks.
+
+\TODO{Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
+|V|))$, and generates messages of identical space complexity. In terms
+of number messages, in the average case, a \process $x$ chosen
+uniformly at random among all \processes creates a logical
+partition. Its messages $\alpha_x$ spread through the network until
+reaching \processes that belong to another partition closer to
+them. This splits partitions in half on average. Overall, the $n^{th}$
+new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
+      \log_2 n \rfloor}})$} \processes. This decreases every new
+partition until reaching one \process per new partition: its
+source. The average number of messages per \process is
+\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
+      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
+number of neighbors per \process.}
+\TODO{\TODO{Multiple receipt and multiple delivery} In terms of number of
+messages, deleting the $a^{th}$ partition generates twice as many
+messages as creating the $a^{th}$ partition: $\delta$ messages travel
+through the partition, then $\alpha$ messages compete to fill the gap
+\TODO{which is?}. \TODO{What about false positives?} Overall, the
+communication complexity shows that \NAME scales well to the number of
+partitions.}
+
+%% In the
+%% worst-case, every new partition includes all but one \process
+%% belonging to the previous partition. The total number of messages
+%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
+%% a^2)$. As for the average-case, the number of messages for the
+%% partition deletion is identical to the number of messages of the
+%% corresponding partition creation.
 
@@
 
+\begin{figure}
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
+  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
+\end{figure}
+
 \item [Objective:] Confirm that \NAME locks down the traffic of decentralized content
@@
 
-\begin{figure}
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
-  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
-\end{figure}
+\begin{figure*}
+  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
+    comprising 40 interconnected autonomous systems spanning across
+    Europe~\cite{knight2011internet}.]{
+    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
+  } \subfloat[PartB][\label{fig:xascast}
+    \TODO{Experiment with ascast against xascast? with different cache
+      size}]{
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
+  }
+  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
-    comprising 40 interconnected autonomous systems spanning across
-    Europe~\cite{knight2011internet}.]{
-    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
-  } \subfloat[PartB][\label{fig:xascast}
-    \TODO{Experiment with ascast against xascast? with different cache
-      size}]{
-    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
-  }
-  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
-\end{figure*}
-
 %% Next Section reviews state-of-the-art approaches for content indexing

### 2022-01-12 input/proposal.tex
move complexity to expe + positioning fig + small fix

@@
 
-Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
-|V|))$, and generates messages of identical space complexity. In terms
-of number messages, in the average case, a \process $x$ chosen
-uniformly at random among all \processes creates a logical
-partition. Its messages $\alpha_x$ spread through the network until
-reaching \processes that belong to another partition closer to
-them. This splits partitions in half on average. Overall, the $n^{th}$
-new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
-      \log_2 n \rfloor}})$} \processes. This decreases every new
-partition until reaching one \process per new partition: its
-source. The average number of messages per \process is
-\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
-      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
-number of neighbors per \process.
-
-While adding logical partitions to the distributed system is
-straightforward and lightweight, removing them introduces additional
-complexity and costs caused by concurrent operations.
+Adding logical partitions to a static network is straightforward and
+lightweight. Unfortunately, removing partitions or introducing dynamic
+network membership increases complexity and costs caused by concurrent
+operations.
 
@@
 importantly between message deliveries. A \process $s$ that performs a
-\texttt{Del} operation implicitly states that all its preceding
-\texttt{Add} operations become obsolete. As consequence, their results
+\texttt{Del} operation implicitly states that its preceding
+\texttt{Add} operation becomes obsolete. As consequence, their results
 -- scoped broadcast in the form of \texttt{\underline{A}dd}
@@
 focus on the last delivery of each \process, since the best is also
-the last, as highlighted by Algorithm~\ref{algo:add}. \TODO{More about
-  useless $\alpha$ ?}
+the last, as highlighted by Algorithm~\ref{algo:add}.
+
+%% \TODO{More about useless $\alpha$ ?}
 
@@
 
-\TODO{Multiple receipt and multiple delivery} In terms of number of
-messages, deleting the $a^{th}$ partition generates twice as many
-messages as creating the $a^{th}$ partition: $\delta$ messages travel
-through the partition, then $\alpha$ messages compete to fill the gap
-\TODO{which is?}. \TODO{What about false positives?} Overall, the
-communication complexity shows that \NAME scales well to the number of
-partitions.
-%% In the
-%% worst-case, every new partition includes all but one \process
-%% belonging to the previous partition. The total number of messages
-%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
-%% a^2)$. As for the average-case, the number of messages for the
-%% partition deletion is identical to the number of messages of the
-%% corresponding partition creation.
-
 %% \subsection{Lazy dynamic consistent partitioning}
@@
 
-\TODO{Transition to experiments.}
+\NAME follows the principles of scoped broadcast to efficiently and
+consistently propagate notifications to \processes that need them
+despite concurrent operations. \TODO{Next section aims at providing
+empirical evidence of the scalability and properties of \NAME.}
 

### 2022-01-13 input/experiments.tex
objective and description of expe, todo results

@@
     \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
-  } \subfloat[PartB][\label{fig:xascast}
+  } \subfloat[PartB][\label{fig:europe_as_vs_xas}
     \TODO{Experiment with ascast against xascast? with different cache
@@
 
+\begin{asparadesc}
+  \item[Objective:] Highlight the shortcoming of \NAME in Edge
+    infrastructures and propose an improvement called \NAMEC (stands
+    for \underline{cross} \underline{\NAME}) that fits this context by
+    enabling lazy dynamic partitioning.
+
+  \item[Description:] We build a network of networks by using an Edge
+    infrastructure comprising 1157 \processes distributed in 40
+    interconnected autonomous systems spanning across
+    Europe~\cite{knight2011internet} as depicted in
+    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
+    the figure) link autonomous systems together, \eg a Lisbon \node
+    links Portugal to Spain and United Kingdoms through a Madrid \node
+    and a London \node respectively.
+
+    \noindent Figure~\ref{fig:europe-ases} depicts the operations executed
+    during the simulation that lasts 7 seconds: at 1 second, a \node
+    located in Lisbon, Portugal performs an \texttt{Add}; at 2
+    seconds, a \node located in Palma de Majorque, Spain performs an
+    \texttt{Add}; at 3 seconds, a \node located in Paris, France
+    performs an \texttt{Add}; at 4 seconds, a \node located in
+    Hvanneyri, Iceland performs an \texttt{Add}; and finally, at 5
+    seconds, the \node in Spain performs a \texttt{Del}.
+
+    \noindent \NAMEC extends \NAME to enable lazy dynamic partitioning
+    by allowing gateways to stop notifications when their respective
+    network does not appear to have a source. Using \NAMEC, each
+    \process maintains a \emph{local} index that corresponds to the
+    best partition of its autonomous systems, and a \emph{global}
+    index that corresponds to the best partition cross autonomous
+    systems, \ie contiguous autonomous systems that have at least one
+    source.
+
+    \noindent We measure the number of messages transiting through the
+    network for each operation, and we measure the number of
+    \processes that index (\ie belong to a partition) over time.
+
+  \item[Results:] Figure~\ref{fig:europe_as_vs_xas} shows the results
+    of this experiment.
+\end{asparadesc}
+
 %% Next Section reviews state-of-the-art approaches for content indexing
 %%  in geo-distributed infrastructures and explains their shortcomings.
-
-% \subsection{Use case: caching}
-% \subsection{Use case: routing}
-% \subsection{Use case: broadcast domain}
 

### 2022-01-15 input/experiments.tex
results

--- 2022-01-10 input/experiments.tex
@@
 %% dynamic networks.
+
+%% \TODO{Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
+%% |V|))$, and generates messages of identical space complexity. In terms
+%% of number messages, in the average case, a \process $x$ chosen
+%% uniformly at random among all \processes creates a logical
+%% partition. Its messages $\alpha_x$ spread through the network until
+%% reaching \processes that belong to another partition closer to
+%% them. This splits partitions in half on average. Overall, the $n^{th}$
+%% new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
+%%       \log_2 n \rfloor}})$} \processes. This decreases every new
+%% partition until reaching one \process per new partition: its
+%% source. The average number of messages per \process is
+%% \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
+%%       \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
+%% number of neighbors per \process.}
+%% \TODO{\TODO{Multiple receipt and multiple delivery} In terms of number of
+%% messages, deleting the $a^{th}$ partition generates twice as many
+%% messages as creating the $a^{th}$ partition: $\delta$ messages travel
+%% through the partition, then $\alpha$ messages compete to fill the gap
+%% \TODO{which is?}. \TODO{What about false positives?} Overall, the
+%% communication complexity shows that \NAME scales well to the number of
+%% partitions.}
+
+%% In the
+%% worst-case, every new partition includes all but one \process
+%% belonging to the previous partition. The total number of messages
+%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
+%% a^2)$. As for the average-case, the number of messages for the
+%% partition deletion is identical to the number of messages of the
+%% corresponding partition creation.
 
@@
 \begin{asparadesc}
-\item [Objective:] Confirm the complexity analysis stating that
-  communication and time overheads depend on the current partitioning
-  of the system.
+\item [Objective:] Confirm the scalability of \NAME by higlighting the
+  trade-off between the current partitioning of the system and the
+  protocol's overhead in terms of traffic and termination time.
 
@@
 \noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
-depends on the size of partitions. The first partition is the most
-expensive, for $\alpha$'s must reach every \process which takes time
-and generate more traffic.  \NAME quickly converges towards consistent
-partitioning in only 350 milliseconds. The last and $100^{th}$
-partition added around 21 seconds is the least expensive. By using
-scoped broadcast, control information only reaches a small subset of
-the whole network.
+depends on the size of partitions. In this scenario, it empirically
+corresponds to a complexity in terms of number of messages of
+$\mathcal{O}(\frac{|E|}{|V|\cdot|P|})$ where $E$ is the number of
+links, $V$ is the number of \processes, and $P$ is the number of
+partitions. In other terms, the $p^{th}$ partition contains $1/p$
+\processes and reduces the size of closest partitions so every
+partition has $1/p$ \processes on average.
+
+\noindent Therefore, the first partition is the most expensive, for $\alpha$'s
+must reach every \process which takes time and generate more traffic.
+\NAME quickly converges towards consistent partitioning in only 350
+milliseconds. The last and $100^{th}$ partition added around 21
+seconds is the least expensive. By using scoped broadcast, control
+information only reaches a small subset of the whole network.
 
@@
 
-\begin{figure}
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
-  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
-\end{figure}
+\begin{figure*}
+  \subfloat {
+    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
+  }
+  \hspace{5pt}
+  \subfloat {
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
+  }
+  \caption{\label{fig:europe-ases}Traffic overhead and indexes
+    maintained by \NAME and its extension \NAMEC in an Edge
+    infrastructure comprising 40 interconnected autonomous systems of
+    1157 \processes spanning across Europe~\cite{knight2011internet}}
+\end{figure*}
 
@@
 
-\noindent Overall, this experimentation empirically demonstrates the
-benefits of \NAME in the context of geo-distributed infrastructures,
-e.g., inter-connected autonomous systems where \processes and
-communications links may be added and removed at any time. \NAME
-coupled with replication strategies designed for Edge infrastructures
-would allow locking down the traffic of replica indexing, while
-providing every \process with quick access to replicated content.
+\end{asparadesc}
+
+\begin{asparadesc}
+  \item[Objective:] Highlight the shortcoming of \NAME in Edge
+    infrastructures and propose an improvement called \NAMEC (stands
+    for \underline{cross} \underline{\NAME}) that fits this context by
+    enabling lazy dynamic partitioning.
+
+  \item[Description:] We build a network of networks by using an Edge
+    infrastructure comprising 1157 \processes distributed in 40
+    interconnected autonomous systems spanning across
+    Europe~\cite{knight2011internet} as depicted in the left
+    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
+    the figure) link autonomous systems together, \eg a Lisbon \node
+    links Portugal to Spain and United Kingdoms through a Madrid \node
+    and a London \node respectively.
+
+    \noindent The left Figure~\ref{fig:europe-ases} depicts the
+    operations executed during the simulation that lasts 7 seconds: at
+    1 second, a \node located in Lisbon, Portugal performs an
+    \texttt{Add}; at 2 seconds, a \node located in Palma de Majorque,
+    Spain performs an \texttt{Add}; at 3 seconds, a \node located in
+    Paris, France performs an \texttt{Add}; at 4 seconds, a \node
+    located in Hvanneyri, Iceland performs an \texttt{Add}; and
+    finally, at 5 seconds, the \node in Spain performs a \texttt{Del}.
+
+    \noindent \NAMEC extends \NAME to enable lazy dynamic partitioning
+    by allowing gateways to stop notifications when their respective
+    network does not appear to have a source. Using \NAMEC, each
+    \process maintains a \emph{local} index that corresponds to the
+    best partition of its autonomous systems, and a \emph{global}
+    index that corresponds to the best partition cross autonomous
+    systems, \ie adjacent autonomous systems that have at least one
+    source.
+
+    \noindent We measure the number of messages transiting through the
+    network for each operation, and we measure the number of
+    \processes that index (\ie belong to a partition) over time.
+
+  \item[Results:] Figure~\ref{fig:europe-ases} shows the results
+    of this experiment. The top part highlights the cost of each
+    partitioning protocol after each operation, while the bottom part
+    provides the insight that explains these costs by displaying the
+    number of indexes maintained by each protocol.
+
+    \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
+    \texttt{Add} costs an order of magnitude more with \NAME compared
+    to \NAMEC.  \NAME's messages propagate through all Europe, for
+    \NAME regards Europe as 1 network of 1157 \processes while
+    \NAMEC's messages propagate through Portugal's network of 23
+    \processes only.
+
+    \noindent Figure~\ref{fig:europe-ases} shows that Spain's
+    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
+    \process in Madrid links Portugal to Spain and the rest of
+    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
+    is, only 11 \processes in Spain actually need to receive and
+    deliver the new notification, hence the small overhead of this
+    operation with \NAME. Using \NAMEC, the overhead is slightly
+    higher since
+    \begin{inparaenum}[(i)]
+    \item the 20 \processes of Spain's network need to receive and
+      deliver the new notification, \emph{and}
+    \item Madrid's \process echoes Lisbon's notification as soon as it
+      receives Palma's notification to 11 \processes.
+    \end{inparaenum}
+
+    \noindent Figure~\ref{fig:europe-ases} highlights the worst
+    case scenario of \NAME: the cost of France's \texttt{Add} is close
+    to that of Portugal's \texttt{Add} since it updates the whole
+    Europe excluding Portugal and Spain. On the opposite, \NAMEC only
+    updates France's 39 \processes.
+
+    \noindent Figure~\ref{fig:europe-ases} shows that Iceland's
+    \texttt{Add} has similar cost for \NAME and \NAMEC. Indeed, they
+    both update Iceland, and when the notifications reach Copenhagen
+    in Danemark, they stop either because France's notifications are
+    closer (\NAME) or the Danish network does not have any source
+    (\NAMEC).
+
+    \noindent Finally, Figure~\ref{fig:europe-ases} shows that
+    Spain's \texttt{Del} have similar cost for \NAME and
+    \NAMEC. Nevertheless, the trade-off is different: \NAME's overhead
+    comes from the 11 \nodes that need to acknowledge staleness and
+    deliver the echos from Portugal; \NAMEC's overhead comes from the
+    20 \nodes that need to acknowledge staleness. Using \NAMEC,
+    Spain's network does not propagate echos since it does not have
+    any source anymore.
 
@@
 
-\begin{figure*}
-  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
-    comprising 40 interconnected autonomous systems spanning across
-    Europe~\cite{knight2011internet}.]{
-    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
-  } \subfloat[PartB][\label{fig:xascast}
-    \TODO{Experiment with ascast against xascast? with different cache
-      size}]{
-    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
-  }
-  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
-\end{figure*}
+%% \begin{asparadesc}
+%%   \item[\TODO{Overall:}] this experimentation empirically demonstrates the
+%%     benefits of \NAME in the context of geo-distributed
+%%     infrastructures, e.g., inter-connected autonomous systems where
+%%     \processes and communications links may be added and removed at
+%%     any time. \NAME coupled with replication strategies designed for
+%%     Edge infrastructures would allow locking down the traffic of
+%%     replica indexing, while providing every \process with quick access
+%%     to replicated content.
+%% \end{asparadesc}
+
+\TODO{Overall + transition.}
 
@@
 %%  in geo-distributed infrastructures and explains their shortcomings.
-
-% \subsection{Use case: caching}
-% \subsection{Use case: routing}
-% \subsection{Use case: broadcast domain}
 

### 2022-01-16 input/experiments.tex
meow

@@
 \label{sec:experimentation}
-
-%% This section describes the results of our experimentation evaluating
-%% the properties of \NAME that enables adaptive scoped broadcast in
-%% dynamic networks.
-
-%% \TODO{Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
-%% |V|))$, and generates messages of identical space complexity. In terms
-%% of number messages, in the average case, a \process $x$ chosen
-%% uniformly at random among all \processes creates a logical
-%% partition. Its messages $\alpha_x$ spread through the network until
-%% reaching \processes that belong to another partition closer to
-%% them. This splits partitions in half on average. Overall, the $n^{th}$
-%% new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
-%%       \log_2 n \rfloor}})$} \processes. This decreases every new
-%% partition until reaching one \process per new partition: its
-%% source. The average number of messages per \process is
-%% \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
-%%       \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
-%% number of neighbors per \process.}
-%% \TODO{\TODO{Multiple receipt and multiple delivery} In terms of number of
-%% messages, deleting the $a^{th}$ partition generates twice as many
-%% messages as creating the $a^{th}$ partition: $\delta$ messages travel
-%% through the partition, then $\alpha$ messages compete to fill the gap
-%% \TODO{which is?}. \TODO{What about false positives?} Overall, the
-%% communication complexity shows that \NAME scales well to the number of
-%% partitions.}
-
-%% In the
-%% worst-case, every new partition includes all but one \process
-%% belonging to the previous partition. The total number of messages
-%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
-%% a^2)$. As for the average-case, the number of messages for the
-%% partition deletion is identical to the number of messages of the
-%% corresponding partition creation.
 
@@
   trade-off between the current partitioning of the system and the
-  protocol's overhead in terms of traffic and termination time.
+  protocol's overhead in terms of generated traffic and termination
+  time.
 
@@
 
-\noindent We focus on the complexity of \NAME. We measure the average
-number of messages generated per \process per second during the
-experiment; and the time before reaching consistent partitioning after
-adding or removing a partition.
+\noindent We measure the average number of messages generated per
+\process per second; and the time before reaching consistent
+partitioning after adding or removing a partition.
 
@@
 \noindent Figure~\ref{fig:complexity} also confirms that \NAME's
-delete operations are more expensive than add operations. Indeed, the
-top part of the figure shows that after 21 seconds, when the
-experiment involves removals, traffic includes both $\alpha$'s and
-$\delta$'s. The latter aims at removing stale information and
-triggering competition while the former aims at updating shortest
-paths. As corollary, the convergence time increases, for $\delta$
-messages must reach the partition borders before sound competitors
-propagate their partition. It is worth noting that this delete
-operation involves concurrency: removals still propagate while
-the competition has started. %%is already partially triggered and propagating.
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \subfloat[Part A][\label{fig:complexity}Overhead of consistent partitioning
-%%       using \NAME]
-%%              {\includegraphics[width=0.5\columnwidth]{img/as_cast_complexity.eps}}
-%%              \hfill
-%%     \subfloat[Part B][\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.]
-%%              {\includegraphics[width=0.5\columnwidth]{img/as_cast_geant.eps}}
-%%   \end{center}
-%% \end{figure*}
+delete operations are roughly twice as expensive as \texttt{Add}
+operations. Indeed, the top part of the figure shows that after 21
+seconds, when the experiment involves removals, traffic includes both
+$\alpha$'s and $\delta$'s. The latter aims at removing stale
+information and triggering competition while the former aims at
+updating shortest paths. As corollary, the convergence time increases,
+for $\delta$ messages must reach the partition borders before sound
+competitors propagate their partition. It is worth noting that this
+delete operation involves concurrency: removals still propagate while
+the competition has started. %%is already partially triggered and
+propagating.
 
@@
 
-%% \subsection{Distribution and hotspots}
-
-%% \subsection{Confirm that \NAME locks down the traffic of decentralized content
-%%   indexing in the context of dynamic inter-autonomous system
-%%   communications.}
-
 \begin{asparadesc}
@@
 
-\item [Objective:] Confirm that \NAME locks down the traffic of decentralized content
-  indexing in the context of dynamic inter-autonomous system
-  communications.
+\item [Objective:] Confirm that \NAME locks down the traffic of
+  decentralized content indexing in the context of dynamic
+  inter-autonomous system communications.
 
@@
 We build a network by duplicating the G{\'E}ANT
-topology~\cite{knight2011internet} -- a real infrastructure spanning
-across Europe -- and by connecting these two clusters with a high
+topology~\cite{knight2011internet} -- an infrastructure of 271 \nodes
+spanning across Europe -- and we link these two clusters with a high
 latency link: $200$ ms simulating cross-continental communications
@@
 
-  \item[Description:] We build a network of networks by using an Edge
-    infrastructure comprising 1157 \processes distributed in 40
+  \item[Description:] We build a network of networks by using another
+    Edge infrastructure comprising 1157 \processes distributed in 40
     interconnected autonomous systems spanning across
@@
     Paris, France performs an \texttt{Add}; at 4 seconds, a \node
-    located in Hvanneyri, Iceland performs an \texttt{Add}; and
-    finally, at 5 seconds, the \node in Spain performs a \texttt{Del}.
+    located in Hvanneyri, Iceland performs an \texttt{Add};
+    finally at 5 seconds, the \node in Spain performs a \texttt{Del}.
 
-    \noindent \NAMEC extends \NAME to enable lazy dynamic partitioning
-    by allowing gateways to stop notifications when their respective
-    network does not appear to have a source. Using \NAMEC, each
-    \process maintains a \emph{local} index that corresponds to the
-    best partition of its autonomous systems, and a \emph{global}
-    index that corresponds to the best partition cross autonomous
-    systems, \ie adjacent autonomous systems that have at least one
-    source.
+    \noindent We evaluate \NAME against an extension of \NAME called
+    \NAMEC that enables lazy dynamic partitioning by allowing gateways
+    to stop notifications when their respective network does not
+    appear to have a source. Using \NAMEC, each \process maintains a
+    \emph{local} index that corresponds to the best partition of its
+    autonomous systems, and a \emph{global} index that corresponds to
+    the best partition cross autonomous systems, \ie adjacent
+    autonomous systems that have at least one source.
 
@@
     network for each operation, and we measure the number of
-    \processes that index (\ie belong to a partition) over time.
+    \processes that maintain an index (\ie that belong to a partition)
+    over time.
 
-  \item[Results:] Figure~\ref{fig:europe-ases} shows the results
-    of this experiment. The top part highlights the cost of each
-    partitioning protocol after each operation, while the bottom part
-    provides the insight that explains these costs by displaying the
-    number of indexes maintained by each protocol.
+  \item[Results:] The right of Figure~\ref{fig:europe-ases} shows the
+    results of this experiment. The top part highlights the cost of
+    each partitioning protocol after each operation, while the bottom
+    part provides the insight that explains these costs by displaying
+    the number of indexes maintained by each protocol.
 
@@
     \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
-    \process in Madrid links Portugal to Spain and the rest of
+    gateway in Madrid links Portugal to Spain and the rest of
     Europe. Since Lisbon is closer to Madrid than Palma de Majorque
@@
       deliver the new notification, \emph{and}
-    \item Madrid's \process echoes Lisbon's notification as soon as it
+    \item Madrid's gateway echoes Lisbon's notification as soon as it
       receives Palma's notification to 11 \processes.
@@
 
-\TODO{Overall + transition.}
+\begin{asparadesc}
+  \item[Overall,] these experiments highlight the scalability of \NAME
+    and \NAMEC in dynamic networks such as Edge infrastructures. Next
+    Section reviews state-of-the-art approaches designed to index
+    content in geo-distributed infrastructures.
+\end{asparadesc}
+
+% \TODO{Overall + transition.}
 

### 2022-01-17 input/proposal.tex
meow
Add distance-vector in related work and remove stuff about Xascast in III

@@
 when they are able to detect possible blocking conditions in the
-dissemination of required notifications. \TODO{Finally, it further constrain
-the system by allowing only subsets of \processes to reach lazy
-consistent partitioning. This improvement only requires \processes to
-know which of their neighbors belong to their own network.}
+dissemination of required notifications.
 
@@
 consistently propagate notifications to \processes that need them
-despite concurrent operations. \TODO{Next section aims at providing
-empirical evidence of the scalability and properties of \NAME.}
+despite concurrent operations. Next Section aims at providing the
+empirical evidence of scalability and properties of the proposed
+approach.
 

### 2022-01-21 input/abstract.tex
adapting to two columns, stilltodo. simpler problem display
Pass sur abstract

@@
   % 
-  Relying on remote services enters in contradiction with the
+  Relying on remote services for such a aim,  enters in contradiction with the
   properties of Edge infrastructures as locating replicas may
@@
   %%% Our proposal
-  \noindent In this paper, we abstract the content indexing challenge
+  \noindent In this paper, we abstract the content indexation challenge
   as a distributed partitioning problem: every \process only indexes
@@
   %% operations and receipt orders.
-  Our complexity analysis supported by simulations shows that \NAME
-  scales well in terms of generated traffic and termination time.
+  Our prototype, implemented on top of PeerSim, shows that \NAME
+  scales well in terms of generated messages and termination
+  time.
+
+  %% \NAME is a crazy contribution
+  \color{red}\NAME can constitute a new building block for
+  geo-distribuetd service. Among the concrete use-cases we envision is
+  the sharing of web objects regularly used in social networks (including viral pictures/video but also css,
+  javascript objects): instead of contacting CDN nodes, it
+  would be possible to retrieve objects closer and so mitigate the
+  traffic overall.
+
   %% As
@@
 
-%% \begin{IEEEkeywords}
-%% Edge infrastructures, decentralized content indexing, scoped
-%% broadcast, logical partitioning protocol
-%% \end{IEEEkeywords}
+\begin{IEEEkeywords}
+  Edge infrastructures, decentralized content indexing, scoped
+  broadcast, logical partitioning protocol
+\end{IEEEkeywords}
 

### 2022-01-21 input/introduction.tex
figure with colors, removing pdf
starting with xas, small changes here and there
pass on introduction

@@
 
-In recent years, the data storage paradigm shifted from centralized in
+The data storage paradigm shifted from centralized in
 the cloud to distributed at the edges of the network. 
@@
 Cloud, rely on \underline{d}istributed \underline{h}ash
-\underline{t}ables (DHT) spread across the different \processes
-composing the infrastructure~\cite{maymounkov2002kademlia}. When a
-client wants to access specific content, it requests a remote \process
-to provide at least one \process identity to retrieve this content
-from. After it retrieved the content, the client can create another
-replica to improve the performance of future accesses, but it must
-contact the indexing service again to notify of the creation of this
-new replica.
+\underline{t}ables (DHT) spread across different \processes composing
+the infrastructure~\cite{maymounkov2002kademlia}. When a client wants
+to access specific content, it requests a remote \process to provide
+at least one \process identity to retrieve this content from. After
+retrieving the content, the client can create another replica to
+improve the performance of future accesses, but it must recontact the
+indexing service to notify of the creation of this new replica.
 %% a local replica is created to improve the performance for future
@@
 %\end{itemize}
+
+\input{input/figpartitionintuition.tex} %% positioning
 
@@
 
-\noindent In this paper, we address these issues and limitations
-regarding content indexing. Our contribution is threefold:
+\noindent In this paper, we address the content indexing challenge as
+a distributed partitioning problem. Our contribution is threefold:
 
@@
 
-\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
-  empirically support our complexity analysis and the scalability of
-  \NAME. Using scoped broadcast, \NAME quickly disseminate messages to
-  a subset of relevant \processes. The higher the number of
-  partitions, the smaller \NAME's overhead.  Most importantly, \NAME
-  does not generate traffic in quiescent systems.  % Our experiments
+\item [$\bullet$] We evaluate \NAME through simulations using
+  PeerSim~\cite{montresor2009peersim}. Results show the consistent
+  partitioning of the algorithm as well as its scalability. Using
+  scoped broadcast, \NAME quickly disseminate messages to a subset of
+  relevant \processes. The higher the number of partitions, the
+  smaller \NAME's overhead.  Most importantly, \NAME does not generate
+  traffic in quiescent systems.  % Our experiments
   %  also highlight the relevance of \NAME in autonomous systems.
@@
 problem behind our proposal.  Section~\ref{sec:adaptive} describes
-dynamic consistent partitioning and its implementation along with an
-analysis of its complexity. Section~\ref{sec:experimentation} presents
-our evaluations.  Section~\ref{sec:related_work} reviews related
+dynamic consistent partitioning and its
+implementation. Section~\ref{sec:experimentation} presents our
+evaluations.  Section~\ref{sec:related_work} reviews related
 work. Finally, Section~\ref{sec:conclusion} concludes and discusses

### 2022-01-21 input/related_work.tex
with the related work

@@
 
-\TODO{Vector routing protocols.} 
 Content indexing services in geo-distributed infrastructures allow
@@
 resides, without contacting any remote
-service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
+service.
+In a routing context, distance-vector routing protocols such as BGP or OSPF~\cite{ospf} similarly broadcast information to all other nodes to infer a topology map of the network and derive routing tables.
+\underline{C}onflict-\underline{f}ree \underline{r}eplicated
 \underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data

### 2022-01-21 input/abstract.tex
last sentence abstract

@@
   %% \NAME is a crazy contribution
-  \color{red}\NAME can constitute a new building block for
-  geo-distribuetd service. Among the concrete use-cases we envision is
-  the sharing of web objects regularly used in social networks (including viral pictures/video but also css,
-  javascript objects): instead of contacting CDN nodes, it
-  would be possible to retrieve objects closer and so mitigate the
-  traffic overall.
+  \color{red} \NAME can constitute a novel building block for
+  geo-distributed services, \eg sharing the locations of downloaded
+  web objects to allow nodes benefit from neighborhood downloads,
+  resource discovery in the vicinity of a region, etc.
+
+%  javascript objects)
+%  we envision is
+%  the sharing of web objects regularly used in social networks (including viral picture/video but also css,
+%  javascript objects): instead of contacting CDN nodes, it
+%  would be possible to retrieve objects closer and so mitigate the
+%  traffic overall.
 

### 2022-01-21 input/proposal.tex
meow

@@
   %
-  Any source can broadcast a staleness notification at any
-  time. Every \process $x$ delivers and forwards a received staleness
-  notification if it targets its best up-to-date delivered message:
+  Any source can broadcast a staleness notification at any time. Every
+  \process $x$ delivers and forwards a received staleness notification
+  $\delta_s$ if it targets its best up-to-date delivered message:
   %% \TODO{$(\delta_s \in R_x \wedge \alpha_s =
@@
 
-\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where
-  a \process $x$ that receives but does not deliver a staleness
-  notification sends back --~or echoes~-- its best up-to-date
-  delivered message: $(\last D_x = \alpha_s^d \wedge \delta_s
-  \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}))
-  \implies r_{xy}(\delta_{s'}) \rightarrow
-  s_{xy}(\alpha_s^d\oplus^{w_{xy}})$.
+\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos]
+  In addition to FB, a \process $x$ that receives but does not deliver
+  a staleness notification $\delta_{s}$ sends back --~or echoes~-- its
+  best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
+  \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow
+  r_{xy}(\delta_{s})) \implies r_{xy}(\delta_{s}) \rightarrow
+  s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.
 
@@
 in a wrong partition, use their history of receipt and delivery to
-detect the blocking of staleness notifications that can hinder
-reaching consistent partitioning.  In Figure~\ref{fig:problem}, $b$
-blocked the staleness notification $\delta_a$ that $c$ needs since it
-belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
-stale before $b$ does. Therefore, $c$ can detect the blocking of
-$\delta_a$ since it acknowledges that its parent $b$ received,
+detect the possible blocking of staleness notifications that can
+hinder reaching consistent partitioning.  In Figure~\ref{fig:problem},
+$b$ blocked the staleness notification $\delta_a$ that $c$ needs since
+it belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
+stale before $b$ does. Therefore, $c$ can detect the possible blocking
+of $\delta_a$ since it acknowledges that its parent $b$ received,
 delivered, and forwarded the stale notification $\alpha_c^1$. In other
@@
   \item\label{lem:detectorB} a \process $y$ in such a chain of
-    delivery $\pi_{xz}'$ eventually acknowledges its blocking.
+    delivery $\pi_{xz}'$ eventually detects the possible blocking of $\delta_x$.
   \end{inparaenum}

### 2022-01-24 input/experiments.tex
reworked figures

@@
 \begin{figure}
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.eps}
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
   \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
@@
 \begin{figure}
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
   \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
@@
   \subfloat {
-    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
   }
@@
     and \NAMEC in dynamic networks such as Edge infrastructures. Next
-    Section reviews state-of-the-art approaches designed to index
-    content in geo-distributed infrastructures.
+    Section reviews state-of-the-art approaches that can index content
+    in geo-distributed infrastructures.
 \end{asparadesc}
-
-% \TODO{Overall + transition.}
 

### 2022-01-24 input/experiments.tex
meow

@@
 researchers to evaluate and assess distributed algorithms in large
-scale networks~\cite{montresor2009peersim}. The code is available on
-the Github platform at
+scale networks~\cite{montresor2009peersim}. All the code is available
+on the Github platform at
 \TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.
@@
 the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
-around $500$ ms due to the high latency inter-continental link. The
+around $300$ ms due to the high latency inter-continental link. The
 first plateau shows the source's autonomous system acknowledging this
@@
 
-\noindent Figure~\ref{fig:geant} highlights that removing the
-inter-continental link generates additional traffic. The cluster cut
-off from the source must purge all control information about this
-source.  Most importantly, Figure~\ref{fig:geant} shows that \NAME
-still operates well when \emph{physical} partitions appear. \Processes
-from the cluster without source do not belong to any partition while
-\processes from the other cluster belong to the same partition.
+\noindent Figure~\ref{fig:geant} highlights that \NAME operates well
+even when \emph{physical} partitions appear. Indeed, the disconnection
+of the only inter-continental link existing between the two clusters
+either leads to 
+\begin{inparaenum}[(i)]
+\item additional traffic when the \processes do not have any source in
+  their cluster, for \processes need to purge all indexes about the
+  remote unreachable source until reaching consistent partitioning; or
+\item an already consistent partitioning, for \processes of each
+  cluster already target the source in their respective cluster.
+\end{inparaenum}
 
@@
     infrastructures and propose an improvement called \NAMEC (stands
-    for \underline{cross} \underline{\NAME}) that fits this context by
-    enabling lazy dynamic partitioning.
+    for \underline{cross} \underline{\NAME}) that enables \emph{lazy}
+    dynamic partitioning by allowing gateways to stop notifications
+    when their respective network does not appear to have a source.
 
@@
 
-    \noindent We evaluate \NAME against an extension of \NAME called
-    \NAMEC that enables lazy dynamic partitioning by allowing gateways
-    to stop notifications when their respective network does not
-    appear to have a source. Using \NAMEC, each \process maintains a
-    \emph{local} index that corresponds to the best partition of its
-    autonomous systems, and a \emph{global} index that corresponds to
-    the best partition cross autonomous systems, \ie adjacent
-    autonomous systems that have at least one source.
+    \noindent We evaluate \NAME against \NAMEC. Using \NAMEC, each
+    \process maintains a \emph{local} index that corresponds to the
+    best partition of its autonomous systems, and a \emph{global}
+    index that corresponds to the best partition cross autonomous
+    systems, \ie adjacent autonomous systems that have at least one
+    source.
 

### 2022-01-24 input/experiments.tex
miaw

@@
   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
-  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
+  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2
+    clusters connected by a long distance link.}
 \end{figure}
@@
 cluster. Afterwards both scenarios are identical. At $850$~ms, we
-remove the link between the two clusters. At $1.7$~s, we insert back this
-link.
+remove the link between the two clusters. At $1.7$~s, we insert back
+this link.
 
@@
     infrastructures and propose an improvement called \NAMEC (stands
-    for \underline{cross} \underline{\NAME}) that enables \emph{lazy}
-    dynamic partitioning by allowing gateways to stop notifications
-    when their respective network does not appear to have a source.
+    for \underline{cross} \underline{\NAME}) that enables
+    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
+    further detailed in the 2 additional pages available for the
+    camera-ready version of the paper} dynamic partitioning by
+    allowing gateways to stop notifications when their respective
+    network does not appear to have a source.
 

### 2022-01-26 input/abstract.tex
small rewording to avoid downloaded repetition

@@
   \color{red} \NAME can constitute a novel building block for
-  geo-distributed services, \eg sharing the locations of downloaded
-  web objects to allow nodes benefit from neighborhood downloads,
+  geo-distributed services, \eg sharing the locations of 
+  web object replicas to allow nodes benefit from neighborhood downloads,
   resource discovery in the vicinity of a region, etc.

### 2022-01-26 input/introduction.tex
add comments on introduction

@@
 
-Instead, a \process creating a replica should notify all and only
+To mitigate the broadcasting overhead, a \process creating a replica should notify all and only
 \processes that have no closer replica in the system. This would
@@
 partition so they can identify and rally their new closest
-partition. A periodic advertisement protocol already provides both
+partition.
+% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
+\textcolor{red}{
+A periodic advertisement protocol already provides both
 operations for routing purposes~\cite{hemmati2015namebased}. However,
@@
 \end{inparaenum}
-
+}
 %% A ``simple'' way to tackle the aforementioned limitations would be to
@@
   application-dependant predicate.
+  \textcolor{red}{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
 

### 2022-01-26 input/abstract.tex
mostly about abstract intro

@@
   % 
-  Relying on remote services for such a aim,  enters in contradiction with the
-  properties of Edge infrastructures as locating replicas may
+  Relying on remote services for such a aim enters in contradiction
+  with the properties of Edge infrastructures as locating replicas may
   effectively take more time than actually downloading content.  At
@@
   %% \NAME is a crazy contribution
-  \color{red} \NAME can constitute a novel building block for
-  geo-distributed services, \eg sharing the locations of 
-  web object replicas to allow nodes benefit from neighborhood downloads,
-  resource discovery in the vicinity of a region, etc.
+  \noindent As such, \NAME can constitute a novel building block for
+  geo-distributed services, \eg by efficiently sharing the locations
+  of replicated web objects in the vicinity of downloading \processes,
+  or by enabling efficient resource discovery in the vicinity of a
+  region.
 

### 2022-01-26 input/experiments.tex
mostly about abstract intro

@@
     further detailed in the 2 additional pages available for the
-    camera-ready version of the paper} dynamic partitioning by
+    camera-ready version of the paper.} dynamic partitioning by
     allowing gateways to stop notifications when their respective

### 2022-01-26 input/introduction.tex
mostly about abstract intro

--- 2022-01-21 input/introduction.tex
@@
 information. When creating or destroying a replica, a \process would
-notify all other \processes by efficiently broadcasting its
+notify all other \processes by broadcasting its
 operation~\cite{birman1999bimodal, hadzilacos1994modular,
@@
 partition so they can identify and rally their new closest
-partition. A periodic advertisement protocol already provides both
-operations for routing purposes~\cite{hemmati2015namebased}. However,
-its functioning requires
+partition. Periodic advertisement protocols already provide both
+operations~\cite{hemmati2015namebased, sohier2012physarum}. However,
+their functioning requires
 \begin{inparaenum}[(i)]
 \item to generate traffic even when the system is quiescent, and
-\item to finely tune physical-time-based intervals that depend on
-  network topology parameters such as network diameter.
+\item the use of synchronous communications~\cite{sohier2012physarum}
+  or physical-time-based intervals tuned according to network topology
+  parameters such as network diameter~\cite{hemmati2015namebased}.
 \end{inparaenum}
@@
   to creations and deletions of partitions even in dynamic systems
-  where \nodes join, leave, and crash at any time. \NAME's efficiency
-  relies on a communication primitive called
+  where \nodes can join, leave, or crash at any time. \NAME's
+  efficiency relies on a communication primitive called
   \underline{s}coped-broad\underline{cast} that enables epidemic
@@
 \item [$\bullet$] We evaluate \NAME through simulations using
-  PeerSim~\cite{montresor2009peersim}. Results show the consistent
-  partitioning of the algorithm as well as its scalability. Using
-  scoped broadcast, \NAME quickly disseminate messages to a subset of
-  relevant \processes. The higher the number of partitions, the
-  smaller \NAME's overhead.  Most importantly, \NAME does not generate
-  traffic in quiescent systems.  % Our experiments
-  %  also highlight the relevance of \NAME in autonomous systems.
-  \NAME would allow to lock down the traffic generated by content
-  indexing, even in contexts where \emph{physical} partitioning may
-  occur.
-  %As such, \NAME can constitute a new building block for
-  % geo-distributed services.
+  PeerSim~\cite{montresor2009peersim}. Results empirically show that
+  \begin{inparaenum}[(i)]
+  \item \NAME manages to quickly disseminate messages to the subset of
+    relevant \processes;
+  \item \NAME's overhead decreases when the number of partitions
+    increases;
+  \item \NAME does not generate traffic in quiescent systems; and
+  \item \NAME enables consistent partitioning even in networks subject
+    to physical partitioning.
+  \end{inparaenum}
 \end{asparadesc}
+
+As such, \NAME can constitute a novel building block for
+geo-distributed services, \eg by efficiently sharing the locations of
+replicated web objects in the vicinity of downloading nodes, or by
+enabling efficient resource discovery in the vicinity of a region.
+\TODO{More detail, name drop that we can support CDN.}
 

### 2022-01-26 input/background.tex

@@
 request remote -- possibly far away third-party -- entities to
-retrieve their content location.  In this paper, we tackle the content
+retrieve content locations.  More precisely, we propose to consider the content
 indexing issue as a dynamic logical partitioning problem. This section
@@
 \end{inparaenum}
-
+\textcolor{red}{Je ne vois pas l'interet des enums ici? ca casse la lecture}
 \item [Location:]

### 2022-01-26 input/introduction.tex

@@
 
-Instead, a \process creating a replica should notify all and only
-\processes that have no closer replica in the system. This would
-create interconnected sets of \processes, or \emph{partitions},
-gathered around a \emph{source} being their respective replica. A
-\process deleting its replica should notify all members of its
-partition so they can identify and rally their new closest
-partition. Periodic advertisement protocols already provide both
-operations~\cite{hemmati2015namebased, sohier2012physarum}. However,
+To mitigate the broadcasting overhead, a \process creating a replica
+should notify all and only \processes that have no closer replica in
+the system. This would create interconnected sets of \processes, or
+\emph{partitions}, gathered around a \emph{source} being their
+respective replica. A \process deleting its replica should notify all
+members of its partition so they can identify and rally their new
+closest partition. \TODO{Periodic advertisement protocols} already
+provide both
+operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
 their functioning requires
+% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
 \begin{inparaenum}[(i)]

### 2022-01-26 input/abstract.tex
enable note + one comment in the abstract

@@
   geo-distributed services, \eg by efficiently sharing the locations
-  of replicated web objects in the vicinity of downloading \processes,
+  of replicated web objects in the vicinity of downloading \processes, \note{vicinity redundant + see tex}
+  %ici on perd la notion que les autres noeuds en périphérie peuvent en beneficier + redondance sur vicinity
   or by enabling efficient resource discovery in the vicinity of a

### 2022-01-26 input/introduction.tex
add two comments in the introduction

@@
 members of its partition so they can identify and rally their new
-closest partition. \TODO{Periodic advertisement protocols} already
-provide both
-operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
+closest partition. Periodic advertisement protocols \note{Why a periodic protocol solves the ''correct cast/scope''? I miss the point here}
+already provide both operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
 their functioning requires
-% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
 \begin{inparaenum}[(i)]
@@
   efficiency relies on a communication primitive called
-  \underline{s}coped-broad\underline{cast} that enables epidemic
+  \underline{s}coped-broad\underline{cast}
+ \note{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
+  that enables epidemic
   dissemination of messages as long as receiving \processes verify an
   application-dependant predicate.
-  \textcolor{red}{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
 
@@
 enabling efficient resource discovery in the vicinity of a region.
-\TODO{More detail, name drop that we can support CDN.}
-
+\note{More detail, name drop that we can support CDN.}
+\note{Why C/P abstract sentence here? I would rather skip here and C/P and complete in the conclusion?}
 %% Then, we propose \emph{\NAME}, a logical partitioning protocol that

### 2022-01-26 input/background.tex
complete pass on background + comment

@@
 \end{inparaenum}
-\textcolor{red}{Je ne vois pas l'interet des enums ici? ca casse la lecture}
+\note{Je ne vois pas l'interet des enums ici? ca casse la lecture}
 \item [Location:]
@@
 long as they consider them useful based on location information they
-carry. We call such a primitive \emph{scoped broadcast} (see
+carry. We call such a primitive \emph{scoped broadcast}
+\note{connerie: ca marche pas comme ca la propagation des routes dans les routeurs?On est pas entrain de reinventer une algo qui existe depuis bien longtemps dans la communauté reseau?
+Si ce n'est pas le cas alors nous avons une autre application pour as-cast}
+(see
 Section~\ref{subsec:scoped}), for messages transitively reach a subset
@@
 one, partition (see Section~\ref{subsec:consistent}).
+In Figure~\ref{fig:partition_intuitionC}, there are three logical partitions.
 
@@
 \Process~$R$ cannot afford to continuously advertise their replica to
-fill the gap left open by \Process~$G$. Instead, we want to trigger
-once again scoped broadcast at bordering \processes of red and blue
-partitions. The scope of scoped broadcast changes over receipts by
-\processes. Dynamic partitioning raises additional challenges related
-to concurrent operations where removed partitions would block the
-propagation of other partitions (see Section~\ref{subsec:dynamic}).
+fill the gap left open by \Process~$G$. A better approach would
+consist in triggering scoped broadcast at bordering \processes of red
+and blue partitions once again. In other words, the scope of scoped broadcast changes
+over receipts by \processes. This dynamic partitioning raises additional
+challenges related to concurrent operations where removed partitions
+would\note{can?} block the propagation of other partitions (see
+Section~\ref{subsec:dynamic}).
 
@@
 Next Section details the properties of scoped broadcast and dynamic
-partitioning in dynamic networks, and provides an implementation
-called \NAME along with its complexity.
+partitioning, % in dynamic networks,
+and provides an implementation called \NAME.% along with its complexity.
 

### 2022-01-26 input/proposal.tex
two comments on Section III

@@
 
-To provide lazy and dynamic logical partitioning in dynamic networks
+To provide lazy and dynamic logical partitioning in dynamic networks \note{skip: in dynamic networks}
 using scoped broadcast, all live \processes must collaborate to
@@
 when they are able to detect possible blocking conditions in the
-dissemination of required notifications.
+dissemination of required notifications. \note{add node apparitions/removals to clearly state what is a dynamic network and because such a removal can also impact the convergence of the system}
 

### 2022-01-26 input/experiments.tex
essai decoupage en soussection experiments

@@
 
-This section aims to answer the following questions about \NAME: What
-is the overhead of reaching consistent partitioning using \NAME in
-large scale networks?  Is \NAME relevant in Edge infrastructures where
-\processes are geo-distributed into clusters? We performed the
-experimentation using PeerSim, a simulator written in Java that allows
-researchers to evaluate and assess distributed algorithms in large
-scale networks~\cite{montresor2009peersim}. All the code is available
-on the Github platform at
-\TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.
+%To answer questions such as: what is the overhead of reaching
+%consistent partitioning using \NAME in large scale networks and is
+%\NAME relevant in Edge infrastructures where \processes are
+%geo-distributed into clusters?
+In this section, we discuss the evaluations we conducted on top of
+PeerSim, a simulator that allows researchers to
+evaluate and assess distributed algorithms in large scale
+networks~\cite{montresor2009peersim}. All the code is available on the
+Github platform at \url{https://anonymous.4open.science/r/peersim-partition-5592} \note{fix URL}.
 
@@
 
+\subsection{Scalability}
 \begin{asparadesc}
@@
 
+\subsection{Trafic containment}
 \item [Objective:] Confirm that \NAME locks down the traffic of
@@
 
+\subsection{Cross \NAME}
 \begin{asparadesc}

### 2022-01-26 input/abstract.tex
finalize abstract comment
final abstract

@@
   geo-distributed services, \eg by efficiently sharing the locations
-  of replicated web objects in the vicinity of downloading \processes, \note{vicinity redundant + see tex}
-  %ici on perd la notion que les autres noeuds en périphérie peuvent en beneficier + redondance sur vicinity
+  of replicated web objects
+  to allow nodes benefit from neighborhood downloads
+  %in the vicinity of downloading \processes, \note{vicinity redundant + see tex}
+  %ici on perd la notion que les autres noeuds en périphérie peuvent en beneficier (to allow nodes benefit from neighborhood downloads) + redondance sur vicinit:
   or by enabling efficient resource discovery in the vicinity of a

### 2022-01-26 input/introduction.tex
final pass intro

--- 2022-01-26 input/introduction.tex
@@
 members of its partition so they can identify and rally their new
-closest partition. \TODO{Periodic advertisement protocols} already
-provide both
-operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
+closest partition.
+%
+Some periodic advertisement protocols~\cite{hemmati2015namebased,sohier2012physarum}
+already provide both creation and deletion operations. However,
 their functioning requires
-% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
 \begin{inparaenum}[(i)]
@@
   efficiency relies on a communication primitive called
-  \underline{s}coped-broad\underline{cast} that enables epidemic
+  \underline{s}coped-broad\underline{cast}
+   that enables epidemic
   dissemination of messages as long as receiving \processes verify an
   application-dependant predicate.
-  \textcolor{red}{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
 
@@
 \end{asparadesc}
-
-As such, \NAME can constitute a novel building block for
-geo-distributed services, \eg by efficiently sharing the locations of
-replicated web objects in the vicinity of downloading nodes, or by
-enabling efficient resource discovery in the vicinity of a region.
-\TODO{More detail, name drop that we can support CDN.}
 

### 2022-01-26 input/background.tex
final background

@@
 broadcast~\cite{hadzilacos1994modular} and epidemic
-propagation~\cite{epidemic-protocol} to guarantee that
-\begin{inparaenum}[(i)]
-\item every \process eventually knows the content location
-\item by efficiently using neighbor-to-neighbor communication.
-\end{inparaenum}
-\note{Je ne vois pas l'interet des enums ici? ca casse la lecture}
+propagation~\cite{epidemic-protocol} to guarantee that every \process
+eventually knows the content location by efficiently using
+neighbor-to-neighbor communication.
+
 \item [Location:]
@@
 long as they consider them useful based on location information they
-carry. We call such a primitive \emph{scoped broadcast}
-\note{connerie: ca marche pas comme ca la propagation des routes dans les routeurs?On est pas entrain de reinventer une algo qui existe depuis bien longtemps dans la communauté reseau?
-Si ce n'est pas le cas alors nous avons une autre application pour as-cast}
-(see
+carry. We call such a primitive \emph{scoped broadcast} (see
 Section~\ref{subsec:scoped}), for messages transitively reach a subset
@@
 challenges related to concurrent operations where removed partitions
-would\note{can?} block the propagation of other partitions (see
+could block the propagation of other partitions (see
 Section~\ref{subsec:dynamic}).

### 2022-01-26 input/proposal.tex
preamble section 3

--- 2022-01-21 input/proposal.tex
@@
 
-To provide lazy and dynamic logical partitioning in dynamic networks
-using scoped broadcast, all live \processes must collaborate to
-disseminate messages that notify new or removed sources to all and
-only interested \processes. This section reviews step-by-step the
-properties that allow \processes to converge to the desired state
-together. It first defines scoped broadcast, then uses it to guarantee
-consistent partitioning when a \process can only become a new source
-in the system. It highlights the issue when a \process can also remove
-its status of source. It shows that using local knowledge and scoped
-broadcast, \processes can still reach dynamic consistent partitioning
-when they are able to detect possible blocking conditions in the
-dissemination of required notifications.
+To provide dynamic logical partitioning using scoped broadcast, all
+live \processes must collaborate to disseminate messages that notify
+new or removed sources to all and only interested \processes. This
+section reviews step-by-step the properties that allow \processes to
+converge to the desired state together. It first defines scoped
+broadcast, then uses it to guarantee consistent partitioning when a
+\process can only become a new source in the system. It highlights the
+issue when a \process can also remove its status of source. It shows
+that using local knowledge and scoped broadcast, \processes can still
+reach dynamic consistent partitioning when they are able to detect
+possible blocking conditions in the dissemination of required
+notifications.  This also applies to dynamic networks where nodes
+join, leave, or crash at any time.
 

### 2022-01-27 input/experiments.tex
small fix in intro, url in expe, replaced enriched in proposal

@@
 %geo-distributed into clusters?
-In this section, we discuss the evaluations we conducted on top of
-PeerSim, a simulator that allows researchers to
-evaluate and assess distributed algorithms in large scale
-networks~\cite{montresor2009peersim}. All the code is available on the
-Github platform at \url{https://anonymous.4open.science/r/peersim-partition-5592} \note{fix URL}.
+In this section, we discuss the evaluations conducted on PeerSim, a
+simulator that allows researchers to evaluate and assess distributed
+algorithms in large scale networks~\cite{montresor2009peersim}. All
+the code is available on the Github platform at
+\mbox{\url{https://github.com/ane-wane/as-cast}}.
 
@@
 
-\subsection{Scalability}
+\subsection{Scalability and trade-off}
 \begin{asparadesc}
@@
 
-\subsection{Trafic containment}
+\subsection{Traffic containment}
 \item [Objective:] Confirm that \NAME locks down the traffic of
@@
 
-\subsection{Cross \NAME}
+\subsection{Cross autonomous systems}
 \begin{asparadesc}

### 2022-01-27 input/proposal.tex
small fix in intro, url in expe, replaced enriched in proposal

@@
   When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
-  \underline{s}ends $s_{xy}(m)$ the latter to all its neighbors $y$
-  \TODO{enriched} ($\oplus$) with metadata that depends on its local
-  knowledge $\sigma_x$:
-  $f_x(m) \implies \forall \langle x, y\rangle \in E: s_{xy}(m
-  \TODO{\oplus} \sigma_x)$.
+  \underline{s}ends the latter ($s_{xy}(m)$) to all its neighbors $y$
+  accumulating or aggregating ($\oplus$) metadata that depends on its
+  local knowledge $\sigma_x$: $f_x(m) \implies \forall \langle x,
+  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
 \end{definition}

### 2022-01-27 input/experiments.tex
Experiment review until sub section C

@@
 %geo-distributed into clusters?
-In this section, we discuss the evaluations conducted on PeerSim, a
-simulator that allows researchers to evaluate and assess distributed
-algorithms in large scale networks~\cite{montresor2009peersim}. All
-the code is available on the Github platform at
-\mbox{\url{https://github.com/ane-wane/as-cast}}.
+In this section, we discuss the evaluations of \NAME we conducted on top of
+PeerSim, a simulator to
+evaluate and assess distributed algorithms in large scale
+networks~\cite{montresor2009peersim}. All the code is available on the
+Github platform at \mbox{\url{https://github.com/ane-wane/as-cast}}.
 
@@
 distribution. We set the weight of links between 5 and 15 at random
-following a uniform distribution. Weights and latency are different,
+following a uniform distribution also. Weights and latency are different,
 hence the first $\alpha$ received by a \process may not be that of its
 shortest path. It implies more concurrent operations, hence more
-traffic to reach consistent partitioning.
+traffic to reach consistent partitioning.\note{Pour moi ce n'est pas assez claire pourquoi more traffic to reach CP +proposition de reformulation voir tex}
+% Weight and latency are different in order to imply more concurrent operations (hence more traffic to reach consistent partitioning): the first $\alpha$ received by a node may not be that of its shortest path.
 
-\noindent We evaluate dynamic consistent partitioning. First, we
+\noindent To evaluate dynamic consistent partitioning we, first, 
 create 100 partitions one at a time: \processes reach consistent
@@
 
-\noindent Therefore, the first partition is the most expensive, for $\alpha$'s
+\noindent Therefore, the first partition is the most expensive, for $\alpha$'s\note{'s pas compris? all $alpha$ sounds better?}
 must reach every \process which takes time and generate more traffic.
-\NAME quickly converges towards consistent partitioning in only 350
-milliseconds. The last and $100^{th}$ partition added around 21
+\NAME quickly converges towards consistent partitioning in only\note{in only... why only? compare to what ? Is it good bad? why?}
+% we should give additional elements to explain why it is rather ok to converge in 350ms: maybe by underlining the nb of nodes and the average latency between nodes.
+350 milliseconds. The last and $100^{th}$ partition added around 21
 seconds is the least expensive. By using scoped broadcast, control
@@
 \noindent Figure~\ref{fig:complexity} also confirms that \NAME's
-delete operations are roughly twice as expensive as \texttt{Add}
-operations. Indeed, the top part of the figure shows that after 21
-seconds, when the experiment involves removals, traffic includes both
+delete operations are roughly twice as expensive as creation
+ones. Indeed, the top part of the figure shows that after 21 seconds,
+when the experiment involves removals, traffic includes both
 $\alpha$'s and $\delta$'s. The latter aims at removing stale
@@
 delete operation involves concurrency: removals still propagate while
-the competition has started. %%is already partially triggered and
-propagating.
+the competition has started.
+%%is already partially triggered and propagating.
 
@@
 \noindent Finally, Figure~\ref{fig:complexity} highlights that after
-49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
-do not generate traffic anymore. Being reactive, \NAME has no overhead
+49 seconds, i.e., after the 100 creations and the 100 deletes, \processes
+do not generate traffic anymore. Being reactive, \NAME has no overhead \note{can we precise: no overhead related to the indexation updates but heartbeat behind the scene which is crucial?}
 when there is no operation in the system. \NAME's overhead actually
@@
 even when \emph{physical} partitions appear. Indeed, the disconnection
-of the only inter-continental link existing between the two clusters
+of the inter-continental link existing between the two clusters
 either leads to 
@@
 \item additional traffic when the \processes do not have any source in
-  their cluster, for \processes need to purge all indexes about the
+  their cluster because \processes need to purge all indexes about the
   remote unreachable source until reaching consistent partitioning; or
-\item an already consistent partitioning, for \processes of each
+  %\item an already consistent partitioning as \processes of each
+  \item a status quo as \processes of each 
   cluster already target the source in their respective cluster.
@@
 
-\noindent Figure~\ref{fig:geant} shows that, when adding back the
+\noindent Finally, Figure~\ref{fig:geant} shows that, when adding back the
 inter-continental link, the two clusters can communicate again. In the
 experiment involving one source for two clusters, it generates
-traffic. After a $200$ milliseconds delay corresponding to the link
+traffic. After a $200$ milliseconds delay corresponding to the inter-continental link
 latency, the cut off cluster starts to communicate $\alpha$ messages

### 2022-01-27 input/experiments.tex
few changes on subsection C

@@
 \begin{figure*}
-  \subfloat {
+  \subfloat[An infrastructure composed of 40 interconnected autonomous systems and
+    1157 \processes spanning across Europe~\cite{knight2011internet}]{
     \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
@@
   \hspace{5pt}
-  \subfloat {
+  \subfloat[Traffic overhead and indexes
+    maintained by \NAME and its extension \NAMEC]{
     \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
   }
-  \caption{\label{fig:europe-ases}Traffic overhead and indexes
-    maintained by \NAME and its extension \NAMEC in an Edge
-    infrastructure comprising 40 interconnected autonomous systems of
-    1157 \processes spanning across Europe~\cite{knight2011internet}}
+  \caption{\label{fig:europe-ases} Comparison between \NAME and \NAMEC}
 \end{figure*}
@@
   \item[Objective:] Highlight the shortcoming of \NAME in Edge
-    infrastructures and propose an improvement called \NAMEC (stands
-    for \underline{cross} \underline{\NAME}) that enables
+    infrastructures composed of multilple autonomous systems and
+    discuss an improvement called \underline{cross} \underline{\NAME}
+    (\NAMEC). At coarse-grained, \NAMEC enables
     \emph{lazy}\footnote{Laziness properties and \NAMEC would be
-    further detailed in the 2 additional pages available for the
-    camera-ready version of the paper.} dynamic partitioning by
-    allowing gateways to stop notifications when their respective
+    further detailed in the  additional two pages available in the
+    camera-ready version of the article.} dynamic partitioning by
+    allowing AS' gateways to stop notifications when their respective
     network does not appear to have a source.
@@
     interconnected autonomous systems spanning across
-    Europe~\cite{knight2011internet} as depicted in the left
-    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
+    Europe~\cite{knight2011internet} \note{Ici c'est Géant aussi. pourquoi nous n'avions pas 40 ASes dans l'experience précedente + Mentionné que c'est une vision de Geant?}
+     as depicted in Figure~\ref{fig:europe-ases} (a). \emph{Gateway} \processes (dark in
     the figure) link autonomous systems together, \eg a Lisbon \node
@@
 
-    \noindent The left Figure~\ref{fig:europe-ases} depicts the
-    operations executed during the simulation that lasts 7 seconds: at
-    1 second, a \node located in Lisbon, Portugal performs an
-    \texttt{Add}; at 2 seconds, a \node located in Palma de Majorque,
-    Spain performs an \texttt{Add}; at 3 seconds, a \node located in
-    Paris, France performs an \texttt{Add}; at 4 seconds, a \node
-    located in Hvanneyri, Iceland performs an \texttt{Add};
-    finally at 5 seconds, the \node in Spain performs a \texttt{Del}.
+    \noindent Figure~\ref{fig:europe-ases} (a) also depicts the
+    operations executed during the 7 seconds simulation: at 1 second,
+    a \node located in Lisbon, Portugal performs an \texttt{Add} (\ie
+    Lisbon becomes a new source); at 2 seconds, a \node located in
+    Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
+    \node located in Paris, France performs an \texttt{Add}; at 4
+    seconds, a \node located in Hvanneyri, Iceland performs an
+    \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
+    \texttt{Del} (the Spanish source is removed). Each \node has been
+    chosen in order to illustrate the limitation of \NAME and so the
+    interest of containning the propagation within an AS as proposed by
+    \NAMEC.
 
-    \noindent We evaluate \NAME against \NAMEC. Using \NAMEC, each
+    \noindent In \NAMEC, each
     \process maintains a \emph{local} index that corresponds to the
@@
 
-    \noindent We measure the number of messages transiting through the
-    network for each operation, and we measure the number of
+    \noindent To compare \NAME against \NAMEC, we measure the number of messages transiting through the
+    network for each operation, as well as the number of
     \processes that maintain an index (\ie that belong to a partition)
@@
 
-  \item[Results:] The right of Figure~\ref{fig:europe-ases} shows the
+  \item[Results:] Figure~\ref{fig:europe-ases} (b) shows the
     results of this experiment. The top part highlights the cost of
@@
     to \NAMEC.  \NAME's messages propagate through all Europe, for
-    \NAME regards Europe as 1 network of 1157 \processes while
+    \NAME regards Europe as a single network of 1157 \processes while
     \NAMEC's messages propagate through Portugal's network of 23
     \processes only.
-
-    \noindent Figure~\ref{fig:europe-ases} shows that Spain's
+    % 
+    \noindent  Spain's
     \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
@@
     is, only 11 \processes in Spain actually need to receive and
-    deliver the new notification, hence the small overhead of this
+    deliver the new notification, which explains the small overhead of this
     operation with \NAME. Using \NAMEC, the overhead is slightly
@@
 
-    \noindent Figure~\ref{fig:europe-ases} highlights the worst
+    \noindent Figure~\ref{fig:europe-ases} also highlights the worst
     case scenario of \NAME: the cost of France's \texttt{Add} is close
@@
 
-    \noindent Figure~\ref{fig:europe-ases} shows that Iceland's
-    \texttt{Add} has similar cost for \NAME and \NAMEC. Indeed, they
-    both update Iceland, and when the notifications reach Copenhagen
-    in Danemark, they stop either because France's notifications are
-    closer (\NAME) or the Danish network does not have any source
-    (\NAMEC).
+    \noindent The last \texttt{Add} operation in Iceland has similar
+    cost for \NAME and \NAMEC. Indeed, they both update Iceland, and
+    when the notifications reach Copenhagen in Danemark, they stop
+    either because France's notifications are closer (\NAME) or the
+    Danish network does not have any source (\NAMEC).
 

### 2022-01-27 input/conclusion.tex
stupid comment
comments from the thursday meeting

@@
 With the advent of the Edge and IoT era, major distributed services
-proposed by our community should be revised in order to mitigate as
-much as possible traffic between \processes.  In this paper, we
-tackled the problem of content indexing, a key service for storage
-systems.
-%
-We proposed to address this problem as a dynamic logical partitioning
-where partitions grow and shrink to reflect content and replicas
-locations, as well as infrastructure changes. Using an efficient
+proposed by our community should be revised to mitigate as much as
+possible traffic between \processes.  In this paper, we addressed the
+challenge of content indexing, a key service for storage systems, as a
+dynamic logical partitioning problem where partitions grow and shrink
+to reflect content and replicas locations, as well as infrastructure
+changes.
+
+Using an efficient
 communication primitive called scoped broadcast, each \process
 composing the infrastructure eventually knows the \process hosting the
-best replica of specific content.  The challenge resides in handling
+best replica of a specific content.  The challenge resides in handling
 concurrent operations that may impair the propagation of messages, and
@@
 \processes quickly reach consistent partitioning together, and that
-the generated traffic remains locked down to partitions.
+the generated traffic remains locked down to partitions.  We also
+briefly discussed an improvement to contain the traffic in relevant
+autonomous systems.
 %% correctness of our protocol as well as the confinement of
@@
 include distance in its operation.
+\note{Parler de l'application au CDN (voir tex)}
 

### 2022-01-27 input/experiments.tex
comments from the thursday meeting

@@
 of links between 20 and 40 ms at random following a uniform
-distribution. We set the weight of links between 5 and 15 at random
-following a uniform distribution also. Weights and latency are different,
-hence the first $\alpha$ received by a \process may not be that of its
-shortest path. It implies more concurrent operations, hence more
-traffic to reach consistent partitioning.\note{Pour moi ce n'est pas assez claire pourquoi more traffic to reach CP +proposition de reformulation voir tex}
-% Weight and latency are different in order to imply more concurrent operations (hence more traffic to reach consistent partitioning): the first $\alpha$ received by a node may not be that of its shortest path.
+distribution.
+%
+To favor more concurrent operations, we voluntary set
+weights and latency to different values: each link has a weight
+between 5 and 15 set randomly using a uniform distribution. This
+allows nodes to receive messages in a different order than their
+respective shortest path generating more messages to reach consistent
+partionning.
 
@@
 
-\noindent Therefore, the first partition is the most expensive, for $\alpha$'s\note{'s pas compris? all $alpha$ sounds better?}
-must reach every \process which takes time and generate more traffic.
-\NAME quickly converges towards consistent partitioning in only\note{in only... why only? compare to what ? Is it good bad? why?}
-% we should give additional elements to explain why it is rather ok to converge in 350ms: maybe by underlining the nb of nodes and the average latency between nodes.
-350 milliseconds. The last and $100^{th}$ partition added around 21
-seconds is the least expensive. By using scoped broadcast, control
-information only reaches a small subset of the whole network.
+\noindent Therefore, the first partition is the most expensive, for
+$\alpha$ messages must reach every \process which takes time and
+generate more traffic.  \NAME quickly converges towards consistent
+partitioning in 350 milliseconds.
+% TODO: Is 350ms is the optimal? if so it would be great to explain it.
+The last and $100^{th}$ partition
+added around 21 seconds is the least expensive. By using scoped
+broadcast, control information only reaches a small subset of the
+whole network.
 
@@
 when the experiment involves removals, traffic includes both
-$\alpha$'s and $\delta$'s. The latter aims at removing stale
+$\alpha$ and $\delta$ messagess. The latter aims at removing stale
 information and triggering competition while the former aims at
@@
 49 seconds, i.e., after the 100 creations and the 100 deletes, \processes
-do not generate traffic anymore. Being reactive, \NAME has no overhead \note{can we precise: no overhead related to the indexation updates but heartbeat behind the scene which is crucial?}
+do not generate traffic anymore. Being reactive, \NAME has no overhead
+%\note{can we precise: no overhead related to the indexation updates but heartbeat behind the scene which is crucial?}
  when there is no operation in the system. \NAME's overhead actually
@@
 \begin{asparadesc}
-  \item[Objective:] Highlight the shortcoming of \NAME in Edge
+\item[Objective:] Highlight the shortcoming of \NAME in
   infrastructures composed of multilple autonomous systems and
@@
 
-  \item[Description:] We build a network of networks by using another
-    Edge infrastructure comprising 1157 \processes distributed in 40
+  \item[Description:] We build a network of networks, following the
+    GEANT network and the underlying European NRENs.
+    Figure~\ref{fig:europe-ases} (a) depicts the resulting
+    infrastructure composed of 1157 \processes distributed in 40
     interconnected autonomous systems spanning across
-    Europe~\cite{knight2011internet} \note{Ici c'est Géant aussi. pourquoi nous n'avions pas 40 ASes dans l'experience précedente + Mentionné que c'est une vision de Geant?}
-     as depicted in Figure~\ref{fig:europe-ases} (a). \emph{Gateway} \processes (dark in
-    the figure) link autonomous systems together, \eg a Lisbon \node
-    links Portugal to Spain and United Kingdoms through a Madrid \node
-    and a London \node respectively.
+    Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
+    in the figure) link autonomous systems together, \eg a Lisbon
+    \node links Portugal to Spain and United Kingdoms through a Madrid
+    \node and a London \node respectively.
 

### 2022-01-28 input/experiments.tex
reread and fix some

@@
 \begin{asparadesc}
-\item [Objective:] Confirm the scalability of \NAME by higlighting the
+\item [Objective:] Confirm the scalability of \NAME by highlighting the
   trade-off between the current partitioning of the system and the
@@
 respective shortest path generating more messages to reach consistent
-partionning.
+partitioning.
 
-\noindent To evaluate dynamic consistent partitioning we, first, 
+\noindent To evaluate dynamic consistent partitioning, we first
 create 100 partitions one at a time: \processes reach consistent
@@
 when the experiment involves removals, traffic includes both
-$\alpha$ and $\delta$ messagess. The latter aims at removing stale
+$\alpha$ and $\delta$ messages. The latter aims at removing stale
 information and triggering competition while the former aims at
@@
 subset of this membership.  \NAME's overhead actually depends on
-current partitioning as opposed to past partitionings.
+current partitions as opposed to past partitions.
 
@@
 \begin{figure*}
-  \subfloat[An infrastructure composed of 40 interconnected autonomous systems and
-    1157 \processes spanning across Europe~\cite{knight2011internet}]{
+  \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
+    1157 \processes~\cite{knight2011internet}.]{
     \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
@@
   \hspace{5pt}
-  \subfloat[Traffic overhead and indexes
-    maintained by \NAME and its extension \NAMEC]{
+  \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
     \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
   }
-  \caption{\label{fig:europe-ases} Comparison between \NAME and \NAMEC}
+  \caption{Limitations of \NAME and evaluation of \NAMEC for lazy dynamic partitioning.}
 \end{figure*}
@@
 \item[Objective:] Highlight the shortcoming of \NAME in
-  infrastructures composed of multilple autonomous systems and
+  infrastructures composed of multiple autonomous systems and
     discuss an improvement called \underline{cross} \underline{\NAME}
@@
 
-  \item[Description:] We build a network of networks, following the
-    GEANT network and the underlying European NRENs.
-    Figure~\ref{fig:europe-ases} (a) depicts the resulting
-    infrastructure composed of 1157 \processes distributed in 40
-    interconnected autonomous systems spanning across
+  \item[Description:] We build a network of networks comprising
+    G{\'E}ANT along with the underlying European NRENs.
+    Figure~\ref{fig:nrens} depicts the resulting infrastructure
+    composed of 1157 \processes distributed in 40 interconnected
+    autonomous systems spanning across
     Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
@@
 
-    \noindent Figure~\ref{fig:europe-ases} (a) also depicts the
+    \noindent Figure~\ref{fig:nrens} also depicts the
     operations executed during the 7 seconds simulation: at 1 second,
-    a \node located in Lisbon, Portugal performs an \texttt{Add} (\ie
-    Lisbon becomes a new source); at 2 seconds, a \node located in
+    a \node located in Lisbon, Portugal performs an \texttt{Add}, \ie
+    Lisbon becomes a new source; at 2 seconds, a \node located in
     Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
@@
     \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
-    \texttt{Del} (the Spanish source is removed). Each \node has been
-    chosen in order to illustrate the limitation of \NAME and so the
-    interest of containning the propagation within an AS as proposed by
-    \NAMEC.
+    \texttt{Del}, \ie the Spanish source is removed. We chose each source
+    with the aim to illustrate the limitations of \NAME further highlighting
+    the interest in containing the propagation within relevant autonomous systems
+    as proposed by \NAMEC.
 
@@
     \process maintains a \emph{local} index that corresponds to the
-    best partition of its autonomous systems, and a \emph{global}
+    best partition of its autonomous system, and a \emph{global}
     index that corresponds to the best partition cross autonomous
@@
 
-    \noindent To compare \NAME against \NAMEC, we measure the number of messages transiting through the
-    network for each operation, as well as the number of
-    \processes that maintain an index (\ie that belong to a partition)
-    over time.
+    \noindent To compare \NAME against \NAMEC, we measure the number
+    of messages transiting through the network for each operation, as
+    well as the number of \processes that maintain an index (\ie that
+    belong to a partition) over time.
 
-  \item[Results:] Figure~\ref{fig:europe-ases} (b) shows the
+  \item[Results:] Figure~\ref{fig:europe-ases} shows the
     results of this experiment. The top part highlights the cost of

### 2022-01-28 input/proposal.tex
reread and fix some

--- 2022-01-26 input/proposal.tex
@@
   When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
-  \underline{s}ends $s_{xy}(m)$ the latter to all its neighbors $y$
-  \TODO{enriched} ($\oplus$) with metadata that depends on its local
-  knowledge $\sigma_x$:
-  $f_x(m) \implies \forall \langle x, y\rangle \in E: s_{xy}(m
-  \TODO{\oplus} \sigma_x)$.
+  \underline{s}ends it ($s_{xy}(m)$) to all its neighbors $y$
+  accumulating and aggregating ($\oplus$) metadata that depends on its
+  local knowledge $\sigma_x$: $f_x(m) \implies \forall \langle x,
+  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
 \end{definition}

### 2022-01-28 input/related_work.tex
reread and fix some

@@
 uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
-probabilistically propagate through most likely interested
+propagate through most likely interested
 \processes~\cite{sohier2012physarum}. However their operation requires

### 2022-01-28 input/conclusion.tex
final draft for conclusion

@@
 possible traffic between \processes.  In this paper, we addressed the
-challenge of content indexing, a key service for storage systems, as a
-dynamic logical partitioning problem where partitions grow and shrink
-to reflect content and replicas locations, as well as infrastructure
-changes.
-
-Using an efficient
-communication primitive called scoped broadcast, each \process
-composing the infrastructure eventually knows the \process hosting the
-best replica of a specific content.  The challenge resides in handling
-concurrent operations that may impair the propagation of messages, and
-in turn, lead to inconsistent partitioning.
+challenge of content indexing as a dynamic logical partitioning
+problem where partitions grow and shrink to reflect content and
+replicas locations, as well as infrastructure changes.  Using an
+efficient communication primitive called scoped broadcast, each
+\process composing the infrastructure eventually knows the \process
+hosting the best replica of a specific content.  The challenge resides
+in handling concurrent operations that may impair the propagation of
+messages, and in turn, lead to inconsistent partitioning.
 %% The major difficulty lies in concurrent operations, each having a
@@
 the generated traffic remains locked down to partitions.  We also
-briefly discussed an improvement to contain the traffic in relevant
+briefly discussed \NAMEC, an improvement to contain the traffic in relevant
 autonomous systems.
@@
 
-\noindent As future work, we plan to evaluate \NAME within a concrete
+At mid-term, we plan to evaluate our proposal within a concrete
 storage system such as \underline{I}nter\underline{P}lanetary
@@
 (IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
-relevance of \NAME in a real system subject to high dynamicity, and
-compare it against its current DHT-based indexing system that does not
-include distance in its operation.
-\note{Parler de l'application au CDN (voir tex)}
+relevance of the \NAME approach in a real system subject to high
+dynamicity, and compare it against its current DHT-based indexing
+system that does not include distance in its operation. More generally,
+we claim \NAME (or \NAMEC) can constitute a novel building block for
+geo-distributed services.  Among the use-cases we have identified,
+\NAME can be used to complement content delivery infrastructures by
+efficiently sharing between \process attached to the same CDN server
+the locatiosn of web objects that have been already downloaded. This
+would allow the containment of web traffic even lower in our networks,
+and so reduce the overall traffic footprint.
 

### 2022-01-28 input/conclusion.tex
few fixes in conclusions

@@
 dynamicity, and compare it against its current DHT-based indexing
-system that does not include distance in its operation. More generally,
-we claim \NAME (or \NAMEC) can constitute a novel building block for
-geo-distributed services.  Among the use-cases we have identified,
-\NAME can be used to complement content delivery infrastructures by
-efficiently sharing between \process attached to the same CDN server
-the locatiosn of web objects that have been already downloaded. This
-would allow the containment of web traffic even lower in our networks,
-and so reduce the overall traffic footprint.
+system that does not include distance in its operation. More
+generally, we claim that \NAME (or \NAMEC) can constitute a novel
+building block for geo-distributed services.  For instance, \NAME
+could complement content delivery infrastructures by efficiently
+sharing between \processes attached to the same CDN server the
+locations of web objects that have already been downloaded. This would
+further improve the containment of web traffic in our networks, and in
+turns, reduce the overall traffic footprint.
 

### 2022-01-28 input/introduction.tex
small fix in intro, url in expe, replaced enriched in proposal
Remove some stuff to cope with the 11 pages

@@
 notify all other \processes by broadcasting its
-operation~\cite{birman1999bimodal, hadzilacos1994modular,
-  raynal2013distributed}. Unfortunately, this also contradicts Edge
+operation~\cite{birman1999bimodal, hadzilacos1994modular}. Unfortunately, this also contradicts Edge
 infrastructure objectives, for such a protocol does not confine the
@@
 respective replica. A \process deleting its replica should notify all
-members of its partition so they can identify and rally their new
+members of its partition so they can rally their new
 closest partition.
 %
-Some periodic advertisement protocols~\cite{hemmati2015namebased,sohier2012physarum}
-already provide both creation and deletion operations. However,
-their functioning requires
+Some periodic advertisement
+protocols~\cite{hemmati2015namebased,sohier2012physarum} already
+provide both creation and deletion. Yet, their functioning
+requires
 \begin{inparaenum}[(i)]

### 2022-04-19 input/appendices.tex
appendix with notation table

\appendix[Table of notations]

Table~\ref{table:notations} summarizes the notations used throughout
this paper. For the sake of clarity, we divide them into three
categories: network, \process, and message.

\begin{table*}
  \centering
  \caption{\label{table:notations}Notation table.}
  \begin{tabularx}{\textwidth}{@{}lll@{}}
    \toprule
    Notation & Short & Description \\
    \midrule

    $G$ & \underline{G}raph    & Represents a network.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\

    \midrule

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\

    $D_x$ & \underline{d}elivered & Set of delivered messages by \Process $x$.\\ 
    \midrule

    $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
    $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\

    $\mathcal{S}(m)$ & \underline{s}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\

    \bottomrule
  \end{tabularx}
\end{table*}

### 2022-04-19 input/appendices.tex
small summary table of related work

@@
-\appendix[Table of notations]
+\appendices
+
+\section{Table of notations}
 
@@
     $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
+    $D_x$ & \underline{d}elivered & Set of delivered messages by \Process $x$.\\
 
-    $D_x$ & \underline{d}elivered & Set of delivered messages by \Process $x$.\\ 
     \midrule
@@
     $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\
-
-    $\mathcal{S}(m)$ & \underline{s}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\
+    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\
 
@@
 \end{table*}
+
+\section{Related work summary}
+
+Table~\ref{table:relatedwork} provides a summary of state-of-the-art
+approaches along with the reason they fail to enable quick content
+indexing in large scale dynamic systems.
+
+\newcommand{\rxmark}{\textcolor{\WRONG}{\xmark}}
+\newcommand{\rcmark}{\textcolor{\WRONG}{\cmark}}
+\newcommand{\NO}[1]{\textcolor{\WRONG}{#1}}
+
+\begin{table}[h!]
+  \scriptsize
+  \centering
+  \caption{\label{table:relatedwork}Related work summary.}
+  \begin{tabularx}{\columnwidth}{@{}lcccc@{}}
+  \toprule
+
+  Approaches & \multirow{2}{5em}{\centering Third-party service} & Update & \multirow{2}{3.5em}{Eventually Consistent} & \multirow{2}{5em}{\centering\underline{R}eactive or \underline{C}yclic} \\
+  \\
+  \midrule
+
+  \NO{Centralized}~\cite{snamp, p2p-oracle, fogstore, p2p-alto} & \rcmark & one & \cmark & R\\
+  DHT~\cite{ipfs, mdht, squirrel}                               & \rcmark & few & \cmark & R\\
+
+  \midrule
+
+  Vector-based routing~\cite{nlsr, ospf}   & \xmark & \NO{all} & \cmark & R\\
+  Replicated store~\cite{shapiro2011crdts} & \xmark & \NO{all} & \cmark & R\\
+
+  \midrule
+
+  Timeout-based ads~\cite{garcia-lopez, hemmati2015namebased}   & \xmark & scope & \rxmark & \NO{C}\\
+  Random walks~\cite{barjon2014maintaining, sohier2012physarum} & \xmark & scope & \cmark  & \NO{C}\\
+
+  \addlinespace
+
+  \textbf{This paper} & \textbf{\xmark} & \textbf{scope} & \textbf{\cmark} & \textbf{R}\\
+
+  \bottomrule
+  \end{tabularx}  
+\end{table}

### 2022-04-19 input/experiments.tex
Remove some stuff to cope with the 11 pages
very small space winning...

@@
 We build a network comprising 10k \processes. First, we chain
-\processes together, then we add another communication link per
+\processes together, then we add another link per
 \process to another random \process. Since links are bidirectional,
@@
     (\NAMEC). At coarse-grained, \NAMEC enables
-    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
-    further detailed in the  additional two pages available in the
-    camera-ready version of the article.} dynamic partitioning by
+    \emph{lazy} %\footnote{Laziness properties and \NAMEC would be
+    %    further detailed in the  additional two pages available in the
+    %    camera-ready version of the article.}
+    dynamic partitioning by
     allowing AS' gateways to stop notifications when their respective
@@
     to that of Portugal's \texttt{Add} since it updates the whole
-    Europe excluding Portugal and Spain. On the opposite, \NAMEC only
+    Europe excluding Portugal and Spain. Contrarily, \NAMEC only
     updates France's 39 \processes.

### 2022-04-19 input/figpartitionintuition.tex
wining space piece by piece
starting with xas, small changes here and there
very small space winning...

--- 2021-04-21 input/figpartitionintuition.tex
@@
-\begin{figure*}
+\begin{figure*}[t]
 \centering
-\subfloat[\Process~$R$ efficiently advertises its content using epidemic propagation.
-Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}
+\subfloat[\Process~$R$ efficiently advertises its content by epidemic propagation.
+Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-1.png}}
 \hfill
 \subfloat[\Process $G$ creates a second replica splitting the red set in two.
-\Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
+\Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
 \subfloat[\Process $B$ creates another replica.
-\Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
-\subfloat[\Process $G$ destroys its replica.
-\Processes that belong to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
+\Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
+\subfloat[$G$ destroys its replica.
+\Processes that belonged to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-4.png}}
 %
-\caption{The french RENATER topology. Partitions
+\caption{% The french RENATER topology.
+  Partitions
   grow and shrink depending on creations and removals of

### 2022-04-19 input/abstract.tex
reworked abstract

--- 2022-01-26 input/abstract.tex
@@
   the opposite, maintaining such an index at every \process would
-  prove overly costly in terms of memory and traffic, especially since
-  \processes can create and destroy replicas at any time.
+  prove overly costly in terms of memory and traffic.%, especially since
+%  \processes can create and destroy replicas at any time.
 
   %%% Our proposal
-  \noindent In this paper, we abstract the content indexation challenge
-  as a distributed partitioning problem: every \process only indexes
-  its closest replica, and connected \processes with a similar index
-  compose a partition. Our decentralized implementation \NAME is
+  \noindent In this paper, we propose a decentralized implementation
+  of content indexing called \NAME. Using \NAME, every \process only
+  indexes its closest replica; and all connected \processes with a similar
+  index compose a \emph{partition}.
+  %%
+%  \noindent In this paper, we abstract the content indexation challenge
+%  as a distributed partitioning problem: every \process only indexes
+%  its closest replica, and connected \processes with a similar index
+  %  compose a partition.
+  \NAME is
   \begin{inparaenum}[(i)]
@@
   \item guarantees that every \process eventually acknowledges its
-    partition despite concurrent operations.
+    closest replica despite concurrent operations.
   \end{inparaenum}
@@
   %% operations and receipt orders.
-  Our prototype, implemented on top of PeerSim, shows that \NAME
+  Our prototype, implemented on PeerSim, shows that \NAME
   scales well in terms of generated messages and termination
@@
   \noindent As such, \NAME can constitute a novel building block for
-  geo-distributed services, \eg by efficiently sharing the locations
-  of replicated web objects in the vicinity of downloading \processes,
-  or by enabling efficient resource discovery in the vicinity of a
-  region.
+  geo-distributed services in need of efficient resource sharing in the vicinity
+  of regions. % such as content delivery networks.
+
+%%   , \eg by efficiently sharing the locations
+%%   of replicated web objects
+%%   to allow nodes to benefit from neighborhood downloads
+%%   %in the vicinity of downloading \processes, \note{vicinity redundant + see tex}
+%%   %ici on perd la notion que les autres noeuds en périphérie peuvent en beneficier (to allow nodes benefit from neighborhood downloads) + redondance sur vicinit:
+%%   or by enabling efficient resource discovery in the vicinity of a
+%%   region.
 
@@
 
-\begin{IEEEkeywords}
-  Edge infrastructures, decentralized content indexing, scoped
-  broadcast, logical partitioning protocol
-\end{IEEEkeywords}
+%% \begin{IEEEkeywords}
+%%   Edge infrastructures, decentralized content indexing, scoped
+%%   broadcast, logical partitioning protocol
+%% \end{IEEEkeywords}
 

### 2022-04-21 input/appendices.tex
rework order and appendix

--- 2022-04-19 input/appendices.tex
@@
 \end{table*}
+
+\section{Proof of Theorem~\ref{theo:fb}}
+\label{appendix:fb}
+
+\begin{proof}
+  Whenever a \process~$s$ becomes a source, it broadcasts hence
+  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
+  its set of received messages, it acknowledges that it belongs to its
+  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
+  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
+  \noindent Such a source forwards its notification to its neighbors.
+  Every neighbor eventually receives its notification since
+  communication links are reliable. Whatever the order of received
+  messages $R_x$ at neighboring \process~$x$, total order ensures that
+  it delivers notifications $\alpha_s^{d}$ when
+  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
+  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
+  this case.
+  \noindent Among these neighbors, at least those that fulfill the
+  latest condition forward their respective notification.  By
+  transitivity, the message originating from $s$ reaches all
+  \processes that belong to $P_s$ at least through their respective
+  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
+    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
+    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
+  quiescent, \ie no \process becomes source anymore, every \process
+  eventually acknowledges the partition it belongs to, \ie \processes
+  eventually reach consistent partitioning together. In addition, the
+  protocol terminates: a \process never delivers hence forwards a
+  message after it received, delivered, and forwarded the message of
+  its closest source from its lightest path.
+\end{proof}
+
+\section{Proof of Theorem~\ref{theo:fbfsdcp}}
+\label{appendix:fbfsdcp}
+
+\begin{proof}
+  Detection triggers forwarding of staleness downstream which
+  completes the case study of Lemma~\ref{lem:detector} by ensuring
+  that, when a source broadcasts its staleness notification, all
+  \processes that belong to its partition eventually deliver such a
+  staleness notification. All downstream bordering \processes also
+  eventually receive such a staleness notification and echo back their
+  best delivered message. This triggers another competition as in
+  Theorem~\ref{theo:fb} for the \processes that delivered the
+  staleness notification.
+\end{proof}
+
+%% \section{Related work summary}
+
+%% Table~\ref{table:relatedwork} provides a summary of state-of-the-art
+%% approaches along with the reason they fail to enable quick content
+%% indexing in large scale dynamic systems.
+
+%% \input{input/tablerelatedwork.tex}

### 2022-04-21 input/proposal.tex
rework order and appendix

@@
 \begin{proof}
-  Whenever a \process~$s$ becomes a source, it broadcasts hence
-  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
-  its set of received messages, it acknowledges that it belongs to its
-  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
-  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
-  \noindent Such a source forwards its notification to its neighbors.
-  Every neighbor eventually receives its notification since
-  communication links are reliable. Whatever the order of received
-  messages $R_x$ at neighboring \process~$x$, total order ensures that
-  it delivers notifications $\alpha_s^{d}$ when
-  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
-  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
-  this case.
-  \noindent Among these neighbors, at least those that fulfill the
-  latest condition forward their respective notification.  By
-  transitivity, the message originating from $s$ reaches all
-  \processes that belong to $P_s$ at least through their respective
-  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
-    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
-    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
-  quiescent, \ie no \process becomes source anymore, every \process
-  eventually acknowledges the partition it belongs to, \ie \processes
-  eventually reach consistent partitioning together. In addition, the
-  protocol terminates: a \process never delivers hence forwards a
-  message after it received, delivered, and forwarded the message of
-  its closest source from its lightest path.
+  Proof in Appendix~\ref{appendix:fb}.
+%%   Whenever a \process~$s$ becomes a source, it broadcasts hence
+%%   delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
+%%   its set of received messages, it acknowledges that it belongs to its
+%%   own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
+%%   it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
+%%   \noindent Such a source forwards its notification to its neighbors.
+%%   Every neighbor eventually receives its notification since
+%%   communication links are reliable. Whatever the order of received
+%%   messages $R_x$ at neighboring \process~$x$, total order ensures that
+%%   it delivers notifications $\alpha_s^{d}$ when
+%%   $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
+%%   is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
+%%   this case.
+%%   \noindent Among these neighbors, at least those that fulfill the
+%%   latest condition forward their respective notification.  By
+%%   transitivity, the message originating from $s$ reaches all
+%%   \processes that belong to $P_s$ at least through their respective
+%%   lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
+%%     |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
+%%     d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
+%%   quiescent, \ie no \process becomes source anymore, every \process
+%%   eventually acknowledges the partition it belongs to, \ie \processes
+%%   eventually reach consistent partitioning together. In addition, the
+%%   protocol terminates: a \process never delivers hence forwards a
+%%   message after it received, delivered, and forwarded the message of
+%%   its closest source from its lightest path.
 \end{proof}
@@
 
-\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \implies \textup{DCP}$]
+\begin{theorem}[\label{theo:fbfsdcp}$\textup{FB}^+ \wedge \textup{FS}^+ \implies \textup{DCP}$]
   A protocol guarantees dynamic consistent partitioning if it
@@
 \begin{proof}
-  Detection triggers forwarding of staleness downstream which
-  completes the case study of Lemma~\ref{lem:detector} by ensuring
-  that, when a source broadcasts its staleness notification, all
-  \processes that belong to its partition eventually deliver such a
-  staleness notification. All downstream bordering \processes also
-  eventually receive such a staleness notification and echo back their
-  best delivered message. This triggers another competition as in
-  Theorem~\ref{theo:fb} for the \processes that delivered the
-  staleness notification.
+  Proof in Appendix~\ref{appendix:fbfsdcp}.
+%%   Detection triggers forwarding of staleness downstream which
+%%   completes the case study of Lemma~\ref{lem:detector} by ensuring
+%%   that, when a source broadcasts its staleness notification, all
+%%   \processes that belong to its partition eventually deliver such a
+%%   staleness notification. All downstream bordering \processes also
+%%   eventually receive such a staleness notification and echo back their
+%%   best delivered message. This triggers another competition as in
+%%   Theorem~\ref{theo:fb} for the \processes that delivered the
+%%   staleness notification.
 \end{proof}

### 2022-04-21 input/tablerelatedwork.tex
rework order and appendix

\newcommand{\rxmark}{\textcolor{\WRONG}{\xmark}}
\newcommand{\rcmark}{\textcolor{\WRONG}{\cmark}}
\newcommand{\NO}[1]{\textcolor{\WRONG}{#1}}

\begin{table}[t]
  \scriptsize
  \centering
  \caption{\label{table:relatedwork}Related work summary.}
  \begin{tabularx}{\columnwidth}{@{}lcccc@{}}
  \toprule

  Approaches & \multirow{2}{5em}{\centering Third-party service} & Update & \multirow{2}{3.5em}{Eventually Consistent} & \multirow{2}{5em}{\centering\underline{R}eactive or \underline{C}yclic} \\
  \\
  \midrule

  \NO{Centralized}~\cite{snamp, p2p-oracle, fogstore, p2p-alto} & \rcmark & one & \cmark & R\\
  DHT~\cite{ipfs, mdht, squirrel}                               & \rcmark & few & \cmark & R\\

  \midrule

  Vector-based routing~\cite{nlsr, ospf}   & \xmark & \NO{all} & \cmark & R\\
  Replicated store~\cite{shapiro2011crdts} & \xmark & \NO{all} & \cmark & R\\

  \midrule

  Timeout-based ads~\cite{garcia-lopez, hemmati2015namebased}   & \xmark & scope & \rxmark & \NO{C}\\
  Random walks~\cite{barjon2014maintaining, sohier2012physarum} & \xmark & scope & \cmark  & \NO{C}\\

  \addlinespace

  \textbf{This paper} & \textbf{\xmark} & \textbf{scope} & \textbf{\cmark} & \textbf{R}\\

  \bottomrule
  \end{tabularx}  
\end{table}

### 2022-04-21 input/tablerelatedwork.tex
related work

@@
 
-  Approaches & \multirow{2}{5em}{\centering Third-party service} & Update & \multirow{2}{3.5em}{Eventually Consistent} & \multirow{2}{5em}{\centering\underline{R}eactive or \underline{C}yclic} \\
+  Approaches & \multirow{2}{5em}{\centering Without Third-party} & Update & \multirow{2}{3.5em}{Eventually Consistent} & \multirow{2}{5em}{\centering\underline{R}eactive or \underline{C}yclic} \\
   \\
@@
 
-  \NO{Centralized}~\cite{snamp, p2p-oracle, fogstore, p2p-alto} & \rcmark & one & \cmark & R\\
-  DHT~\cite{ipfs, mdht, squirrel}                               & \rcmark & few & \cmark & R\\
+  \NO{Centralized}~\cite{snamp, p2p-oracle, fogstore, p2p-alto} & \rxmark & one & \cmark & R\\
+  DHT~\cite{ipfs, mdht, squirrel}                               & \rxmark & few & \cmark & R\\
 
@@
 
-  Vector-based routing~\cite{nlsr, ospf}   & \xmark & \NO{all} & \cmark & R\\
-  Replicated store~\cite{shapiro2011crdts} & \xmark & \NO{all} & \cmark & R\\
+  Vector-based routing~\cite{nlsr, ospf}   & \cmark & \NO{all} & \cmark & R/C\\
+  Replicated store~\cite{shapiro2011crdts} & \cmark & \NO{all} & \cmark & R/C\\
 
@@
 
-  Timeout-based ads~\cite{garcia-lopez, hemmati2015namebased}   & \xmark & scope & \rxmark & \NO{C}\\
-  Random walks~\cite{barjon2014maintaining, sohier2012physarum} & \xmark & scope & \cmark  & \NO{C}\\
+  Timeout-based~\cite{garcia-lopez, hemmati2015namebased}   & \cmark & scope & \rxmark & \NO{C}\\
+  Random walks~\cite{sohier2012physarum} & \cmark & scope & \cmark  & \NO{C}\\
+  Spanning Forest~\cite{barjon2014maintaining} & \cmark & scope & \cmark & \NO{C}\\
 
@@
 
-  \textbf{This paper} & \textbf{\xmark} & \textbf{scope} & \textbf{\cmark} & \textbf{R}\\
+  \textbf{This paper} & \textbf{\cmark} & \textbf{scope} & \textbf{\cmark} & \textbf{R}\\
 

### 2022-04-25 input/conclusion.tex
Remove some stuff to cope with the 11 pages
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

--- 2022-01-27 input/conclusion.tex
@@
 possible traffic between \processes.  In this paper, we addressed the
-challenge of content indexing, a key service for storage systems, as a
-dynamic logical partitioning problem where partitions grow and shrink
-to reflect content and replicas locations, as well as infrastructure
-changes.
-
-Using an efficient
-communication primitive called scoped broadcast, each \process
-composing the infrastructure eventually knows the \process hosting the
-best replica of a specific content.  The challenge resides in handling
-concurrent operations that may impair the propagation of messages, and
-in turn, lead to inconsistent partitioning.
+challenge of content indexing as a dynamic logical partitioning
+problem where partitions grow and shrink to reflect content locations,
+and infrastructure changes.  Using an efficient communication
+primitive called scoped broadcast, each \process composing the
+infrastructure eventually knows the \process hosting the closest replica
+of a specific content.  The challenge resides in handling concurrent
+operations that may impair the propagation of messages, and in turn,
+lead to inconsistent partitioning.
 %% The major difficulty lies in concurrent operations, each having a
@@
 We highlighted the properties that solve this problem and proposed an
-implementation called \NAME.  Our simulations confirmed that
-\processes quickly reach consistent partitioning together, and that
-the generated traffic remains locked down to partitions.  We also
-briefly discussed an improvement to contain the traffic in relevant
+implementation called \NAME.  Simulations confirmed that
+\processes quickly reach consistent partitioning together while the
+generated traffic remains locked down to partitions.  We also 
+discussed an improvement further containing the traffic inside relevant
 autonomous systems.
@@
 
-\noindent As future work, we plan to evaluate \NAME within a concrete
+As future work, we plan to evaluate our proposal within a concrete
 storage system such as \underline{I}nter\underline{P}lanetary
-\underline{F}ile \underline{S}ystem
-(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
-relevance of \NAME in a real system subject to high dynamicity, and
-compare it against its current DHT-based indexing system that does not
-include distance in its operation.
-\note{Parler de l'application au CDN (voir tex)}
+\underline{F}ile \underline{S}ystem (IPFS)~\cite{ipfs}. This would
+assess the relevance of \NAME in real systems subject to high
+dynamicity, and compare it against its current DHT-based indexing
+system that does not include distance in its operation. More
+generally, we claim that \NAME and its extension can constitute
+novel building blocks for geo-distributed services.  For instance,
+\NAME could complement content delivery infrastructures by efficiently
+sharing between \processes attached to the same CDN server the
+locations of web objects that have already been downloaded. This would
+further improve the containment of web traffic in our networks, and in
+turns, reduce the overall traffic footprint.
 

### 2022-04-25 input/experiments.tex
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

@@
   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
-  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
-    using \NAME.}
+  \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}
 
@@
 
-    \noindent Figure~\ref{fig:nrens} also depicts the
-    operations executed during the 7 seconds simulation: at 1 second,
-    a \node located in Lisbon, Portugal performs an \texttt{Add}, \ie
-    Lisbon becomes a new source; at 2 seconds, a \node located in
-    Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
-    \node located in Paris, France performs an \texttt{Add}; at 4
-    seconds, a \node located in Hvanneyri, Iceland performs an
-    \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
-    \texttt{Del}, \ie the Spanish source is removed. We chose each source
-    with the aim to illustrate the limitations of \NAME further highlighting
-    the interest in containing the propagation within relevant autonomous systems
-    as proposed by \NAMEC.
+    \noindent Figure~\ref{fig:nrens} also depicts the operations
+    executed during the 7 seconds simulation: at 1 second, a \node
+    located in Lisbon, Portugal performs an \texttt{Add}, \ie Lisbon
+    becomes a new source; at 2 seconds, a \node located in Palma de
+    Majorque, Spain performs an \texttt{Add}; at 3 seconds, a \node
+    located in Paris, France performs an \texttt{Add}; at 4 seconds, a
+    \node located in Hvanneyri, Iceland performs an \texttt{Add};
+    finally at 5 seconds, the \node in Spain performs a \texttt{Del},
+    \ie the Spanish source is removed. We chose these sources to
+    illustrate the limitations of \NAME while further motivating the
+    importance of containing the traffic within relevant
+    autonomous systems as proposed by \NAMEC.
 

### 2022-04-25 input/proposal.tex
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

@@
 possible blocking conditions in the dissemination of required
-notifications.  This also applies to dynamic networks where nodes
-join, leave, or crash at any time.
+notifications, even in dynamic networks where nodes join, leave, or
+crash at any time. For convenience, Appendix~\ref{appendix:notations}
+summarizes the notations used throughout the paper.
 

### 2022-04-25 input/related_work.tex
Remove some stuff to cope with the 11 pages
rework order and appendix
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

@@
 advantages of replication. These systems mostly rely on dedicated
-location services hosted by possibly remote third-party \processes; but
-cutting out the middleman requires that each \process maintains its
-own index in a decentralized fashion.
+location services hosted by possibly remote third-party \processes;
+but cutting out the middleman requires that each \process maintains
+its own index in a decentralized
+fashion. Table~\ref{table:relatedwork} summarizes the pros and cons of
+state-of-the-art approaches.
 
@@
 not ensure to include the closest replica.
+
+\input{input/tablerelatedwork.tex}
 
@@
   Some approaches also confine the dissemination of messages.
-  % to interested \processes too.
-% \item [Membership protocols:]
-
 \noindent Distance-based membership protocols such as
@@
 propagate through most likely interested
-\processes~\cite{sohier2012physarum}. However their operation requires
-that
+\processes~\cite{sohier2012physarum}. However their cyclic operation
+requires that
 \begin{inparaenum}[(i)]
@@
 \item they either operate in synchronous
-  systems~\cite{sohier2012physarum} or must define
+  systems~\cite{barjon2014maintaining, sohier2012physarum} or must define
   physical-clock-based timeouts the value of which depends on network
@@
 replica even in large and dynamic networks with asynchronous
-communications; and has no overhead when the system is quiescent.
+communications; and has no overhead in quiescent systems.
 

### 2022-04-25 input/appendices.tex
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok
minors

@@
 \section{Table of notations}
+\label{appendix:notations}
 
@@
     $G$ & \underline{G}raph    & Represents a network.\\
+    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
     $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
-    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
+    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
     $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
     $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\
-    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
 
@@
     $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
-    $D_x$ & \underline{d}elivered & Set of delivered messages by \Process $x$.\\
+    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\
 

### 2022-04-25 input/conclusion.tex
minors

@@
 system that does not include distance in its operation. More
-generally, we claim that \NAME and its extension can constitute
-novel building blocks for geo-distributed services.  For instance,
-\NAME could complement content delivery infrastructures by efficiently
-sharing between \processes attached to the same CDN server the
-locations of web objects that have already been downloaded. This would
-further improve the containment of web traffic in our networks, and in
-turns, reduce the overall traffic footprint.
+generally, we claim that \NAME and its extension can constitute novel
+building blocks for geo-distributed services.  For instance, \NAME
+could complement content delivery
+infrastructures~\cite{triukose2011measuring} by efficiently sharing
+between \processes attached to the same CDN server the locations of
+web objects that have already been downloaded. This would further
+improve the containment of web traffic in our networks, and in turns,
+reduce the overall traffic footprint.
 

### 2022-06-01 rebuttal2.txt
rebutall draft

We thank the three reviewers for their thorough reading and
interesting comments.

* About motivation and practical application: (TODO) Add reference to Bastien's paper
A user from Europe wants to download a video indexed only in
Australia despite a neighbor
European having a replica (because he was interested in the video as
well). Still, the former originates a round-trip to Australia only to
discover that it wasted time looking for the location of the video
that was next to him.  DHTs also have this pitfall where nodes knowing
the video locations might be running in Australia. Our approach
proposes a trade-off that allows close node to answer location
requests, even in dynamic networks where nodes can quickly reconfigure
to meet the changes in a peer-to-peer fashion.
** Action: We use such an example throughout the paper, complementing
the figure descriptions with real-world usage and location.
** Side note: Out of the scope of networking, our approach also
constitutes an efficient way to perform a multi-destinations shortest
path in dynamic graphs.

* About failure detection: We agree with Reviewer 2 that implementing
link failure detection is often done using heartbeats. Our approach is
built on top of such links and benefits, as many other running
protocols, from such failure detection. Since this is a shared overhead,
we do not account it as being part of our protocol.
** Action: Clarify this prerequisite and its implication on the overhead.

* About crash recovery: As of now, crashes may have immediate impact
on neighboring nodes depending on their crash detection
speed. Therefore, a node must always restart anew, thus retrieving and
propagating relevant information again.
** Side note: There exists a trade-off between convergence speed and
and generated traffic when buffering incoming messages and only
propagating most relevant ones. We kept this out of scope for the
sake of simplicity.

* About the experiments: PeerSim, despite being old, remains a
flexible framework to run large scale simulations. It fits our goal of
isolating the behavior of our protocol under desired circumstances.
Nevertheless, we agree with Reviewer 1 that more realistic
configurations are of interest. We left this as future work, where we
would like to replace the DHT of IPFS by our protocol, and deploy it
on a real distributed infrastructure.

** About Figure 7 link: We agree with Reviewer 2 that a single
intercontinental link is not realistic, however this allows us
to confirm and highlight the very important property that our
protocol works even in a network with physical partitions. // (TODO) more ?
** About Figure 7 time: We use simulated time as x-axis to highlight that
the convergence speed depends on the simulated latency between links.
** Action: Use both cycle and simulated time as x-axis label.
** About simulated time and real network conditions: we only simulated 
the link latency using event-based PeerSim, i.e., the number of cycles
(simulated milliseconds to help human understanding) between the
sending of a message and its receipt by a neighbor. Other network conditions
such as hardware limitations, packet loss, would indeed increase convergence
time, but we expect it to remain in the same order of magnitude when not catastrophic.
// (TODO) rewrite this…

** Comparison with state-of-the-art: As stated in Related Work,
state-of-the-art approaches have shortcomings that disqualify them as
contender in our context: Centralized and DHT approaches have slow
response time; vector-based routing and replicated stores flood the
whole network; timeout-based, random walks, and spanning forests are
cycle-based which never-endlessly floods the network.

// 582 words [2022-06-01 Mer] 11:58

### 2022-06-02 rebuttal2.txt
reworking the motiv

@@
 We thank the three reviewers for their thorough reading and
-interesting comments.
+interesting comments. We hope that our response will clarify all of
+their interrogations.
 
 * About motivation and practical application: (TODO) Add reference to Bastien's paper
-A user from Europe wants to download a video indexed only in
-Australia despite a neighbor
-European having a replica (because he was interested in the video as
-well). Still, the former originates a round-trip to Australia only to
-discover that it wasted time looking for the location of the video
-that was next to him.  DHTs also have this pitfall where nodes knowing
-the video locations might be running in Australia. Our approach
-proposes a trade-off that allows close node to answer location
-requests, even in dynamic networks where nodes can quickly reconfigure
-to meet the changes in a peer-to-peer fashion.
-** Action: We use such an example throughout the paper, complementing
-the figure descriptions with real-world usage and location.
-** Side note: Out of the scope of networking, our approach also
-constitutes an efficient way to perform a multi-destinations shortest
-path in dynamic graphs.
+
+Our primer target, as the title states, is distributed content
+indexing, and more specifically, its content location
+service. "Retrieving a content location may actually take more time
+than retrieving the content itself."  As an example, consider Alice
+from Europe who wants to download a video. She first needs to know
+where to download it from. Therefore, she asks to a content location
+service that is unfortunately, centralized, and hosted in Australia.
+After a round-trip of messaging, she realizes that she wasted time
+since the video, or a replica of it, was next to her in Europe all
+along.
+
+One might think that distributing the indexing service in Europe using
+DHTs would be sufficient to avoid this pitfall. However, DHTs do not
+colocate content and location services. Therefore, despite having a
+DHT node in Europe, the one that actually knows where to find the
+video is still in Australia. Alice still wastes time.
+
+Content delivery networks (CDN) is most often the solution. However,
+it requires a priori configuration. Missconfigured CDN still makes
+Alice search for her content location in Australia.
+
+On the opposite, using our approach, the node in Europe automatically
+knows its closest content location. When Alice asks for the video, she
+asks to the European node that answer her immediately with the video
+hosted in Europe.
+
+Our approach is not limited to content indexing, and generalizes to
+any replicated service. On a side note, it even constitutes an
+efficient way to perform multi-destinations shortest path in dynamic
+graphs.
+
+** Action: We agree with Reviewer 1. We add such running example
+throughout the paper, thus complementing the text description of
+figures, to further help the reader.
 
@@
 protocols, from such failure detection. Since this is a shared overhead,
-we do not account it as being part of our protocol.
-** Action: Clarify this prerequisite and its implication on the overhead.
+we do not account it as being part of our protocol. // (TODO) better wording
+** Action: We clarify this requirement and its implication on the overhead.
 
-* About crash recovery: As of now, crashes may have immediate impact
-on neighboring nodes depending on their crash detection
-speed. Therefore, a node must always restart anew, thus retrieving and
+* About crash recovery: Crashes may have immediate impact
+on neighboring nodes depending on their crash detection speed.
+Therefore, a node must always restart anew, thus retrieving and
 propagating relevant information again.

### 2022-06-02 rebuttal2.md
985 words

We thank reviewers for their thorough reading and interesting
comments. We hope that our response will clarify their interrogations.

# Reviewer 1

## Motivation and practical application:
The starting point of our study is about minimizing response time of
locating content in geo-distributed infrastructures. Each time someone
looks for a particular content, it must start by locating it in the
infrastructure: a first node is reached to determine its location and
then, the content is retrieved from a second node [1]. "Retrieving a
content location may actually take more time than retrieving the
content itself".

For instance, let us consider Alice from Vienna who wants to download
a video. She first needs to know where to retrieve it from, and so
asks a content location service. If the latter is centralized and
hosted far away in Australia, the round-trip time to interact with the
location service is detrimental, especially when the video is actually
stored close to Vienna.

One might think that distributing the indexing service using DHTs
would be sufficient to avoid this pitfall. However, DHTs do not
collocate content and location services. Therefore, despite having a
DHT node in Vienna, the one that actually knows where to find the
video Alice is looking for is still in Australia. Hence, the
interaction with the location service is still time-consuming.

Using our approach, each node in charge of maintaining content
locations knows at any time the closest location for a particular
content. This allows Alice to contact its close Vienna location
service to then download the video from her closest location, thus
improving response time.

Our approach is not limited to content indexing, and generalizes to
any replicated service. On a side note, it even constitutes an
efficient way to perform multi-destinations shortest path in dynamic
graphs.

### Action:
Slightly revise the introduction to instantiate this Vienna example
and complement the description of figures to further help the reader.

## Simulations vs emulations vs in-vivo:
PeerSim, despite being old, remains a simple and flexible framework to
run large scale simulations in comparison to Splay, Mininet etc.  It
fits our goal of isolating the behavior of our protocol under desired
circumstances.

We focus our experiments on link latency. Other network conditions
such as hardware limitations and heterogeneity, packet loss, link
congestion, would indeed increase convergence time, but we expect it
to remain in the same order of magnitude when not catastrophic.

Nevertheless, we agree that more realistic configurations are of
interest. We leave this as future work, where we would replace the DHT
of IPFS by AS-cast, and deploy it on a real distributed
infrastructure.

## Comparison against state-of-the-art:
While previous works proposed such comparisons [1], we voluntarily
discard them as they have well-identified shortcomings: Centralized
and DHT approaches do not collocate content and location services,
leading to slow response time; vector-based routing and replicated
stores flood the whole network at each event; timeout-based, random
walks, and spanning forests are cycle-based which never-endlessly
floods (part of) the network.

## Figure 7 time:
The time reported on Figure 7 corresponds to the simulated one. A
cycle is a simulated millisecond.

### Action:
Underline in the legend that every reported time is a simulated one.

# Reviewer 2

## Centralized and DHT
Please, look at the first anwser provided to Reviewer 1.

## Node failures:
Algorithm 3 is designed to handle changes in the infrastructure.
"Removing a node is equivalent to removing all its edges". Therefore,
"What happens if this direct parent fails?": Algorithm 3, line 4
states that this event is equivalent to a possible deletion. The
detecting node must propagate the changes to its neighbors
accordingly.

Regarding the detection of failures, we indeed assume a low level
mechanism, such as heartbeats.  AS-cast is built on top of such a
mechanism, and as many other running protocols, benefits from such
failure detection.

### Action:
We clarify this requirement and its implication on the overhead.

## Scenarios 3e and 5e
Figure 3 illustrates the challenge of maintaining consistent
information.  Figure 5 demonstrates that Node C cannot distinguish the
two scenarios.  The node must assume the worst possible outcome and
propagate delete messages in both cases, that would be true in Figure
3f, but false positives in Figure 5f. AS-cast guarantees that every
node converge to its proper partition afterwards.

## First evaluation practicability
The topology is indeed arbitrary as we do not find any real
geo-distributed topology reaching such a scale of 10K nodes.  We
thought of instantiating multiple times the GEANT topology but
interconnecting them would also be arbitrary.

## About worst-case scenario
Let us consider a chained set of Z nodes [A-Z] and the sequential
creation of partitions, the number of messages in the worst case is:
25×2 + 24×2+ … + 1×2 = O(2×Z^2).

When creating the same partitions in parallel, the number of messages
is only: 2×25.

## Size of packets
We agree that transferred bytes would be of interest, especially to
compare with other approaches in more realistic settings as we plan in
future work.

## Single link between continents
We agree that this scenario is unrealistic; and also that partitions
may span multiple continents. AS-cast would work in such scenario.
This experiment aim to demonstrate that AS-cast behaves correctly in
case of physical partitions. We find this result most interesting
since decentralized protocols often fail to do so.

# Reviewer 3

## Content indexing formal problem 
We chose to abstract the content indexing challenge as a more general
partitioning problem and so formalize it this way (see also first
answer to R1-R2).

## Scope predicate
This is indeed an interesting point. We thank to reviewer for this
valuable remark and let it as future work.

## Black-and-white
### Action:
We agree and make colored figures black-and-white friendly.

## Crash recovery
Crashes may have immediate impact on neighboring nodes.  Therefore, a
node always restart anew, retrieving and propagating relevant
information again.

[1] https://hal.archives-ouvertes.fr/hal-02190125/file/tnsm.pdf

### 2022-06-02 rebuttal2.md
926 words

@@
 ## Motivation and practical application:
-The starting point of our study is about minimizing response time of
-locating content in geo-distributed infrastructures. Each time someone
-looks for a particular content, it must start by locating it in the
-infrastructure: a first node is reached to determine its location and
-then, the content is retrieved from a second node [1]. "Retrieving a
-content location may actually take more time than retrieving the
-content itself".
+Our starting point is about minimizing response time of locating
+content in geo-distributed infrastructures. Each time someone looks
+for a particular content, a first node is reached to determine its
+location and then, the content is retrieved from a second node
+[1]. "Retrieving a content location may actually take more time than
+retrieving the content itself".
 
@@
 asks a content location service. If the latter is centralized and
-hosted far away in Australia, the round-trip time to interact with the
+hosted far away in Australia, the round-trip to interact with the
 location service is detrimental, especially when the video is actually
@@
 video Alice is looking for is still in Australia. Hence, the
-interaction with the location service is still time-consuming.
+interaction with the location service remains time-consuming.
 
-Using our approach, each node in charge of maintaining content
-locations knows at any time the closest location for a particular
-content. This allows Alice to contact its close Vienna location
-service to then download the video from her closest location, thus
-improving response time.
+Using AS-cast, each node in charge of maintaining content locations
+knows at any time the closest location for a particular content.
+Alice contacts her Vienna location service then downloads the video
+from her closest host, hence improving quality of service.
 
-Our approach is not limited to content indexing, and generalizes to
-any replicated service. On a side note, it even constitutes an
-efficient way to perform multi-destinations shortest path in dynamic
-graphs.
+AS-cast is not limited to content indexing, and generalizes well to
+any replicated service. It even constitutes an efficient way to
+perform multi-destinations shortest path in dynamic graphs.
 
-### Action:
-Slightly revise the introduction to instantiate this Vienna example
-and complement the description of figures to further help the reader.
+**Action:** Slightly revise the introduction to instantiate this
+Vienna example and complement the description of figures to further
+help the reader.
 
@@
 We focus our experiments on link latency. Other network conditions
-such as hardware limitations and heterogeneity, packet loss, link
-congestion, would indeed increase convergence time, but we expect it
-to remain in the same order of magnitude when not catastrophic.
+such as hardware limitations, hardware heterogeneity, packet loss,
+link congestion, would indeed increase convergence time, but we expect
+it to remain in the same order of magnitude when not catastrophic.
 
@@
 
-### Action:
-Underline in the legend that every reported time is a simulated one.
-
 # Reviewer 2
@@
 ## Centralized and DHT
-Please, look at the first anwser provided to Reviewer 1.
+Please, read the first anwser provided to Reviewer 1.
 
 ## Node failures:
-Algorithm 3 is designed to handle changes in the infrastructure.
-"Removing a node is equivalent to removing all its edges". Therefore,
-"What happens if this direct parent fails?": Algorithm 3, line 4
-states that this event is equivalent to a possible deletion. The
-detecting node must propagate the changes to its neighbors
-accordingly.
+Algorithm 3 handle changes in infrastructures.  "Removing a node is
+equivalent to removing all its edges". Therefore, "What happens if
+this direct parent fails?": Algorithm 3, line 4 states that this event
+is equivalent to a possible source deletion. The detecting node
+propagates the changes to its neighbors accordingly.
 
-Regarding the detection of failures, we indeed assume a low level
-mechanism, such as heartbeats.  AS-cast is built on top of such a
-mechanism, and as many other running protocols, benefits from such
-failure detection.
+To detect failures, we indeed assume a low level mechanism, such as
+heartbeats. Since many other running protocols benefit from provided
+failure detection, we do not consider it as an overhead of our
+protocol.
 
-### Action:
-We clarify this requirement and its implication on the overhead.
+**Action:** Clarify this requirement and the implication on the
+overhead.
 
@@
 Figure 3 illustrates the challenge of maintaining consistent
-information.  Figure 5 demonstrates that Node C cannot distinguish the
-two scenarios.  The node must assume the worst possible outcome and
-propagate delete messages in both cases, that would be true in Figure
-3f, but false positives in Figure 5f. AS-cast guarantees that every
-node converge to its proper partition afterwards.
+information.  Figure 5 shows that Node C cannot distinguish the two
+scenarios.  The node assumes the worst outcome and propagates delete
+messages in both cases, that would be true in Figure 3f, but false
+positives in Figure 5f. AS-cast guarantees that every node converges
+to its proper partition afterwards.
 
@@
 geo-distributed topology reaching such a scale of 10K nodes.  We
-thought of instantiating multiple times the GEANT topology but
-interconnecting them would also be arbitrary.
+thought of instantiating GEANT multiple times but this remains
+arbitrary.
 
@@
 Let us consider a chained set of Z nodes [A-Z] and the sequential
-creation of partitions, the number of messages in the worst case is:
-25×2 + 24×2+ … + 1×2 = O(2×Z^2).
+creation of partitions, the number of messages is: 25×2 + 24×2+ … +
+1×2 = O(2×Z^2).
 
-When creating the same partitions in parallel, the number of messages
-is only: 2×25.
+When creating all partitions in parallel, the number of messages is
+only: 2×25.
 
-## Size of packets
+## Packets size
 We agree that transferred bytes would be of interest, especially to
@@
 may span multiple continents. AS-cast would work in such scenario.
-This experiment aim to demonstrate that AS-cast behaves correctly in
-case of physical partitions. We find this result most interesting
-since decentralized protocols often fail to do so.
+Nevertheless, this experiment aims to demonstrate that AS-cast behaves
+correctly in case of physical partitions. We find this result most
+interesting since decentralized protocols often fail in such context.
 
@@
 We chose to abstract the content indexing challenge as a more general
-partitioning problem and so formalize it this way (see also first
-answer to R1-R2).
+partitioning problem and formalize it this way (see also first answer
+to Reviewer 1).
 
 ## Scope predicate
-This is indeed an interesting point. We thank to reviewer for this
-valuable remark and let it as future work.
+We agree that predicates need another constraint to qualify the
+broadcast as scoped broadcast. Although we leave this as future work.
 
 ## Black-and-white
-### Action:
-We agree and make colored figures black-and-white friendly.
+**Action:** We agree and make colored figures black-and-white
+friendly.
 
 ## Crash recovery
-Crashes may have immediate impact on neighboring nodes.  Therefore, a
-node always restart anew, retrieving and propagating relevant
+Crashes may have immediate impact on neighboring nodes.  Therefore,
+nodes always restart anew, retrieving and propagating relevant
 information again.

### 2022-06-02 rebuttal2.md
845 words

@@
 
-## Motivation and practical application:
+## Motivation and applications:
 Our starting point is about minimizing response time of locating
-content in geo-distributed infrastructures. Each time someone looks
-for a particular content, a first node is reached to determine its
-location and then, the content is retrieved from a second node
-[1]. "Retrieving a content location may actually take more time than
-retrieving the content itself".
+content in geo-distributed infrastructures. When looking for a
+content, a first node is reached to determine its location and then,
+the content is retrieved from a second node [1]. "Retrieving a content
+location may actually take more time than retrieving the content
+itself".
 
 For instance, let us consider Alice from Vienna who wants to download
-a video. She first needs to know where to retrieve it from, and so
-asks a content location service. If the latter is centralized and
-hosted far away in Australia, the round-trip to interact with the
-location service is detrimental, especially when the video is actually
-stored close to Vienna.
+a video. She must know where to retrieve it from, therefore she asks a
+content location service. If the latter is centralized and hosted far
+away in Australia, the round-trip with the service is detrimental,
+especially when the video is actually stored close to Vienna.
 
-One might think that distributing the indexing service using DHTs
-would be sufficient to avoid this pitfall. However, DHTs do not
-collocate content and location services. Therefore, despite having a
-DHT node in Vienna, the one that actually knows where to find the
-video Alice is looking for is still in Australia. Hence, the
-interaction with the location service remains time-consuming.
+Distributing the indexing service using DHTs is insufficient to avoid
+this pitfall: DHTs do not collocate content and location
+services. Therefore, despite having a DHT node in Vienna, the one that
+actually knows where to find the video Alice is looking for is still
+in Australia. Interacting with the location service remains
+time-consuming.
 
-Using AS-cast, each node in charge of maintaining content locations
-knows at any time the closest location for a particular content.
-Alice contacts her Vienna location service then downloads the video
-from her closest host, hence improving quality of service.
+Using AS-cast improves quality of service since each node in charge of
+maintaining content locations knows at any time the closest location
+for a particular content.  Alice contacts her Vienna location service
+then downloads the video from her closest host.
 
@@
 **Action:** Slightly revise the introduction to instantiate this
-Vienna example and complement the description of figures to further
-help the reader.
+Vienna example and complement figure descriptions to further help the
+reader.
 
@@
 We focus our experiments on link latency. Other network conditions
-such as hardware limitations, hardware heterogeneity, packet loss,
+such as hardware limitations/heterogeneity, packet loss,
 link congestion, would indeed increase convergence time, but we expect
@@
 Nevertheless, we agree that more realistic configurations are of
-interest. We leave this as future work, where we would replace the DHT
-of IPFS by AS-cast, and deploy it on a real distributed
-infrastructure.
+interest. We leave this as future work: replace the DHT of IPFS by
+AS-cast, and deploy it on a real distributed infrastructure.
 
-## Comparison against state-of-the-art:
-While previous works proposed such comparisons [1], we voluntarily
-discard them as they have well-identified shortcomings: Centralized
-and DHT approaches do not collocate content and location services,
-leading to slow response time; vector-based routing and replicated
-stores flood the whole network at each event; timeout-based, random
-walks, and spanning forests are cycle-based which never-endlessly
-floods (part of) the network.
+## State-of-the-art comparison:
+Previous works proposed such comparisons [1]. We discard them as they
+have well-identified shortcomings: Centralized and DHT approaches do
+not collocate content and location services, leading to slow response
+time; vector-based routing and replicated stores flood the whole
+network at each event; timeout-based, random walks, and spanning
+forests are cycle-based which never-endlessly floods (parts of) the
+network.
 
@@
 ## Node failures:
-Algorithm 3 handle changes in infrastructures.  "Removing a node is
+Algorithm 3 handles infrastructure changes.  "Removing a node is
 equivalent to removing all its edges". Therefore, "What happens if
-this direct parent fails?": Algorithm 3, line 4 states that this event
-is equivalent to a possible source deletion. The detecting node
-propagates the changes to its neighbors accordingly.
+this direct parent fails?": Algorithm 3, line 4 triggers a *possible*
+source deletion. The detecting node propagates the changes to its
+neighbors accordingly.
 
@@
 Figure 3 illustrates the challenge of maintaining consistent
-information.  Figure 5 shows that Node C cannot distinguish the two
-scenarios.  The node assumes the worst outcome and propagates delete
-messages in both cases, that would be true in Figure 3f, but false
-positives in Figure 5f. AS-cast guarantees that every node converges
-to its proper partition afterwards.
+information.  Figure 5 highlights the challenge that Node C cannot
+distinguish the two scenarios.  The node assumes the worst and
+propagates delete messages in both cases, rightfully in Figure 3f,
+wrongfully in Figure 5f. Afterwards, AS-cast ensures that every node
+converges to the correct partition.
 
@@
 The topology is indeed arbitrary as we do not find any real
-geo-distributed topology reaching such a scale of 10K nodes.  We
-thought of instantiating GEANT multiple times but this remains
-arbitrary.
+geo-distributed topology reaching 10K nodes.  Instantiating GEANT
+multiple times would remain arbitrary.
 
-## About worst-case scenario
-Let us consider a chained set of Z nodes [A-Z] and the sequential
-creation of partitions, the number of messages is: 25×2 + 24×2+ … +
-1×2 = O(2×Z^2).
+## Worst-case scenario
+Let us consider Z chained nodes [A->Z] and a sequential creation of
+partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 =
+O(2×Z^2).
 
@@
 ## Packets size
-We agree that transferred bytes would be of interest, especially to
-compare with other approaches in more realistic settings as we plan in
+We agree that transferred bytes would be interesting, especially to
+compare with other approaches in realistic settings as we plan in
 future work.
@@
 ## Single link between continents
-We agree that this scenario is unrealistic; and also that partitions
-may span multiple continents. AS-cast would work in such scenario.
-Nevertheless, this experiment aims to demonstrate that AS-cast behaves
-correctly in case of physical partitions. We find this result most
-interesting since decentralized protocols often fail in such context.
+We agree that this scenario is unrealistic.  Nevertheless, this
+experiment aims to demonstrate that AS-cast behaves correctly in case
+of physical partitions. We find this result most interesting since
+decentralized protocols often fail in such context.
 
@@
 
-## Content indexing formal problem 
+## Content indexing problem 
 We chose to abstract the content indexing challenge as a more general
-partitioning problem and formalize it this way (see also first answer
-to Reviewer 1).
+partitioning problem and formalize it this way.
 
 ## Scope predicate
-We agree that predicates need another constraint to qualify the
-broadcast as scoped broadcast. Although we leave this as future work.
+We advocate that any predicate would work: the scope of an always true
+predicate would simply be "all nodes".
 
 ## Black-and-white
-**Action:** We agree and make colored figures black-and-white
-friendly.
+**Action:** Make figures black-and-white friendly.
 

### 2022-06-03 rebuttal2.md
809 words

@@
 Our starting point is about minimizing response time of locating
-content in geo-distributed infrastructures. When looking for a
-content, a first node is reached to determine its location and then,
-the content is retrieved from a second node [1]. "Retrieving a content
-location may actually take more time than retrieving the content
-itself".
+content in geo-distributed infrastructures. When looking for a content,
+a node is reached to determine its location and then, the content is
+retrieved from another node [1]. __"Retrieving a content location may
+actually take more time than retrieving the content itself"__.
 
-For instance, let us consider Alice from Vienna who wants to download
-a video. She must know where to retrieve it from, therefore she asks a
-content location service. If the latter is centralized and hosted far
-away in Australia, the round-trip with the service is detrimental,
-especially when the video is actually stored close to Vienna.
+Let us consider Alice from Vienna who wants to download a video. She
+must know where to retrieve it from, therefore she asks a content
+location service. If the latter is centralized and hosted faraway in
+Australia, the round-trip to the service is detrimental, especially
+when the video is actually stored close to Vienna.
 
-Distributing the indexing service using DHTs is insufficient to avoid
+Distributing indexing services using DHTs is insufficient to avoid
 this pitfall: DHTs do not collocate content and location
@@
 
-Using AS-cast improves quality of service since each node in charge of
-maintaining content locations knows at any time the closest location
-for a particular content.  Alice contacts her Vienna location service
-then downloads the video from her closest host.
+AS-cast improves quality of service since each node in charge of
+maintaining content locations always knows the closest location for a
+particular content.  Alice contacts her Vienna location service then
+downloads the video from her closest host.
 
@@
 **Action:** Slightly revise the introduction to instantiate this
-Vienna example and complement figure descriptions to further help the
-reader.
+Vienna example and complement figure descriptions.
 
 ## Simulations vs emulations vs in-vivo:
-PeerSim, despite being old, remains a simple and flexible framework to
-run large scale simulations in comparison to Splay, Mininet etc.  It
-fits our goal of isolating the behavior of our protocol under desired
-circumstances.
+PeerSim remains a simple and flexible framework to run large scale
+simulations in comparison to Splay, Mininet etc.  It fits our goal of
+isolating the behavior of our protocol under desired circumstances.
 
 We focus our experiments on link latency. Other network conditions
-such as hardware limitations/heterogeneity, packet loss,
-link congestion, would indeed increase convergence time, but we expect
-it to remain in the same order of magnitude when not catastrophic.
+such as hardware limitations/heterogeneity, packet loss, link
+congestion, would indeed increase convergence time, but we expect an
+identical order of magnitude when not catastrophic.
 
@@
 ## Centralized and DHT
-Please, read the first anwser provided to Reviewer 1.
+Please, read the first answer provided to Reviewer 1.
 
 ## Node failures:
-Algorithm 3 handles infrastructure changes.  "Removing a node is
-equivalent to removing all its edges". Therefore, "What happens if
-this direct parent fails?": Algorithm 3, line 4 triggers a *possible*
+Algorithm 3 handles infrastructure changes.  __"Removing a node is
+equivalent to removing all its edges"__.  Therefore, "What happens if
+this direct parent fails?": Algorithm 3, line 4 triggers a _possible_
 source deletion. The detecting node propagates the changes to its
@@
 
-**Action:** Clarify this requirement and the implication on the
-overhead.
+**Action:** Clarify requirements and overhead implications.
 
@@
 wrongfully in Figure 5f. Afterwards, AS-cast ensures that every node
-converges to the correct partition.
+converges to its correct partition.
 
@@
 ## Worst-case scenario
-Let us consider Z chained nodes [A->Z] and a sequential creation of
-partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 =
-O(2×Z^2).
-
-When creating all partitions in parallel, the number of messages is
-only: 2×25.
+Let us consider [A..Z] chained nodes, and a sequential creation of
+partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 = O(2×Z^2).
+Whereas in parallel, the number of messages is only: 2×25.
 
@@
 
-## Single link between continents
+## Intercontinental link
 We agree that this scenario is unrealistic.  Nevertheless, this
@@
 ## Scope predicate
-We advocate that any predicate would work: the scope of an always true
-predicate would simply be "all nodes".
+Any predicate would work: the scope of an always true predicate would
+trivially be "all nodes".
 
@@
 ## Crash recovery
-Crashes may have immediate impact on neighboring nodes.  Therefore,
+Crashes may impact neighboring nodes immediately.  Therefore,
 nodes always restart anew, retrieving and propagating relevant

### 2022-06-03 rebuttal2.md
integrate minor changes

@@
 ## Simulations vs emulations vs in-vivo:
-PeerSim remains a simple and flexible framework to run large scale
-simulations in comparison to Splay, Mininet etc.  It fits our goal of
-isolating the behavior of our protocol under desired circumstances.
+PeerSim, despite being old,  remains a simple and flexible framework to 
+run large scale simulations in comparison to Splay, Mininet etc.  It 
+fits our goal of isolating the behavior of our protocol simulating link latencies.
 
-We focus our experiments on link latency. Other network conditions
-such as hardware limitations/heterogeneity, packet loss, link
-congestion, would indeed increase convergence time, but we expect an
+Other network conditions such as hardware diversity,  packet loss, congestion, would indeed increase convergence time, but we expect an
 identical order of magnitude when not catastrophic.
 
-Nevertheless, we agree that more realistic configurations are of
-interest. We leave this as future work: replace the DHT of IPFS by
-AS-cast, and deploy it on a real distributed infrastructure.
+Nevertheless, we agree more realistic configurations are of
+interest. We leave this as future work by revising IPFS by
+AS-cast, and deploy it on a real infrastructure.
 

### 2022-06-03 rebuttal2.md
750 words

--- 2022-06-03 rebuttal2.md
@@
 Our starting point is about minimizing response time of locating
-content in geo-distributed infrastructures. When looking for a content,
-a node is reached to determine its location and then, the content is
-retrieved from another node [1]. __"Retrieving a content location may
-actually take more time than retrieving the content itself"__.
+content in geo-distributed infrastructures. When looking for a
+content, a node is reached to determine its location, then, the
+content is retrieved from another node [1]. _"Retrieving a content
+location may actually take more time than retrieving the content
+itself"_.
 
-Let us consider Alice from Vienna who wants to download a video. She
-must know where to retrieve it from, therefore she asks a content
-location service. If the latter is centralized and hosted faraway in
-Australia, the round-trip to the service is detrimental, especially
-when the video is actually stored close to Vienna.
+Consider Alice from Vienna who wants to download a video. She must
+know where to retrieve it from, therefore she asks a content location
+service. If the latter is centralized and hosted faraway in Australia,
+the round-trip to the service is detrimental, especially when the
+video is actually stored close to Vienna.
 
-Distributing indexing services using DHTs is insufficient to avoid
-this pitfall: DHTs do not collocate content and location
-services. Therefore, despite having a DHT node in Vienna, the one that
-actually knows where to find the video Alice is looking for is still
-in Australia. Interacting with the location service remains
-time-consuming.
+Distributing location services using DHTs is insufficient: DHTs do not
+collocate content and location services. Therefore, despite having a
+DHT node in Vienna, the one that knows where to find the video Alice
+is looking for may still be in Australia. Interacting with the service
+remains time-consuming.
 
-AS-cast improves quality of service since each node in charge of
-maintaining content locations always knows the closest location for a
-particular content.  Alice contacts her Vienna location service then
-downloads the video from her closest host.
+AS-cast improves QoS since every node maintaining content locations
+always knows its closest location for a particular content.  Alice
+contacts her Vienna location service then downloads the video from her
+closest host.
 
@@
 
-**Action:** Slightly revise the introduction to instantiate this
-Vienna example and complement figure descriptions.
+**Action:** Slightly revise Introduction using this example and
+complement figure descriptions.
 
 ## Simulations vs emulations vs in-vivo:
-PeerSim remains a simple and flexible framework to run large scale
-simulations in comparison to Splay, Mininet etc.  It fits our goal of
-isolating the behavior of our protocol under desired circumstances.
+PeerSim remains a flexible framework to run large scale
+simulations. It fits our goal of isolating our protocol's behavior
+under desired circumstances.
 
-We focus our experiments on link latency. Other network conditions
-such as hardware limitations/heterogeneity, packet loss, link
-congestion, would indeed increase convergence time, but we expect an
-identical order of magnitude when not catastrophic.
+Experiments focus on link latency. Other network conditions (hardware
+limitations/heterogeneity, loss, congestion…) would indeed increase
+convergence time, but we expect an identical order of magnitude when
+not catastrophic.
 
 Nevertheless, we agree that more realistic configurations are of
-interest. We leave this as future work: replace the DHT of IPFS by
-AS-cast, and deploy it on a real distributed infrastructure.
+interest. We leave this as future work: replace IPFS's DHT by AS-cast,
+and deploy on real distributed infrastructures.
 
@@
 not collocate content and location services, leading to slow response
-time; vector-based routing and replicated stores flood the whole
-network at each event; timeout-based, random walks, and spanning
-forests are cycle-based which never-endlessly floods (parts of) the
-network.
+time; vector-based routing and replicated stores flood the network at
+each event; timeout-based, random walks, and spanning forests are
+cycle-based which never-endlessly floods the network.
 
 ## Figure 7 time:
-The time reported on Figure 7 corresponds to the simulated one. A
-cycle is a simulated millisecond.
+The time reported on Figure 7 is the simulated one. A cycle is a
+simulated millisecond.
 
@@
 ## Node failures:
-Algorithm 3 handles infrastructure changes.  __"Removing a node is
-equivalent to removing all its edges"__.  Therefore, "What happens if
+Algorithm 3 handles infrastructure changes.  _"Removing a node is
+equivalent to removing all its edges"_.  Therefore, "What happens if
 this direct parent fails?": Algorithm 3, line 4 triggers a _possible_
@@
 
-To detect failures, we indeed assume a low level mechanism, such as
-heartbeats. Since many other running protocols benefit from provided
-failure detection, we do not consider it as an overhead of our
-protocol.
+To detect failures, we indeed assume a low level mechanism
+(eg. heartbeats). Since many other running protocols benefit from it,
+we do not consider it an overhead of AS-cast.
 
@@
 ## Scenarios 3e and 5e
-Figure 3 illustrates the challenge of maintaining consistent
-information.  Figure 5 highlights the challenge that Node C cannot
-distinguish the two scenarios.  The node assumes the worst and
-propagates delete messages in both cases, rightfully in Figure 3f,
-wrongfully in Figure 5f. Afterwards, AS-cast ensures that every node
-converges to its correct partition.
+Figure 3 illustrates the challenge of consistency.  Figure 5
+highlights the *challenge* that Node C *cannot* distinguish the two
+scenarios.  The node assumes the worst and propagates delete messages:
+rightfully in Figure 3f, wrongfully in Figure 5f. Afterwards, AS-cast
+still ensures convergence.
 
@@
 ## Worst-case scenario
-Let us consider [A..Z] chained nodes, and a sequential creation of
+Consider [A..Z] chained nodes, and a sequential creation of
 partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 = O(2×Z^2).
@@
 We agree that this scenario is unrealistic.  Nevertheless, this
-experiment aims to demonstrate that AS-cast behaves correctly in case
-of physical partitions. We find this result most interesting since
+experiment aims to demonstrate that AS-cast behaves correctly when
+physical partitions occur. We find this result most interesting since
 decentralized protocols often fail in such context.

### 2022-06-03 rebuttal2.md
744 words

@@
 ## Simulations vs emulations vs in-vivo:
-PeerSim remains a flexible framework to run large scale
-simulations. It fits our goal of isolating our protocol's behavior
-under desired circumstances.
 
-Experiments focus on link latency. Other network conditions (hardware
-limitations/heterogeneity, loss, congestion…) would indeed increase
-convergence time, but we expect an identical order of magnitude when
-not catastrophic.
+PeerSim, despite old w.r.t. highlight solutions, remains a flexible
+framework to run large scale simulations. It fits our goal of
+isolating our protocol's behavior focusing on link latency.
 
-Nevertheless, we agree that more realistic configurations are of
+Other network conditions (hardware limitations/heterogeneity, loss,
+congestion…) would indeed increase convergence time, but we expect an
+identical order of magnitude when not catastrophic.
+
+Nevertheless, we agree more realistic configurations are of
 interest. We leave this as future work: replace IPFS's DHT by AS-cast,
-and deploy on real distributed infrastructures.
+and deploy on real infrastructures.
 
 ## State-of-the-art comparison:
-Previous works proposed such comparisons [1]. We discard them as they
-have well-identified shortcomings: Centralized and DHT approaches do
+Previous works proposed such comparisons [1]. We discard them due to
+their well-identified shortcomings: Centralized and DHT approaches do
 not collocate content and location services, leading to slow response
@@
 
-## Black-and-white
-**Action:** Make figures black-and-white friendly.
-
 ## Crash recovery
-Crashes may impact neighboring nodes immediately.  Therefore,
-nodes always restart anew, retrieving and propagating relevant
+Crashes may impact neighboring nodes immediately.  Therefore, nodes
+always restart in fresh state, retrieving and propagating relevant
 information again.

### 2022-06-03 rebuttal2.md
last changes

@@
 Distributing location services using DHTs is insufficient: DHTs do not
-collocate content and location services. Therefore, despite having a
-DHT node in Vienna, the one that knows where to find the video Alice
-is looking for may still be in Australia. Interacting with the service
-remains time-consuming.
+collocate content and location services. Despite having a DHT node in
+Vienna, the corresponding hash of the video may still be the charge of
+the node in Australia. Therefore, interacting with the service remains
+time-consuming.
 
-AS-cast improves QoS since every node maintaining content locations
-always knows its closest location for a particular content.  Alice
-contacts her Vienna location service then downloads the video from her
-closest host.
+AS-cast tackles this problem since every node maintaining content
+locations always knows its closest location for a particular content.
+Alice contacts her Vienna location service then downloads the video
+from her closest host.
 

### 2022-06-24 input/introduction.tex
minors
quick format

@@
 \item its consumers so data may quickly and efficiently reach
-  them~\cite{cachier, foggy_cache, shi2016edge}.
+  them~\cite{cachier,foggy_cache,shi2016edge}.
 \end{inparaenum}
@@
 To favour this transition, new designs for data management across Edge
-infrastructures have been investigated~\cite{confais2017object,
-  confais2017performance, fogstore, hasenburg2020towards}.  They
+infrastructures have been investigated~\cite{confais2017object,confais2017performance,fogstore,hasenburg2020towards}.  They
 enable strategies to confine traffic by writing data locally and
@@
 hot spots and availability issues. But most importantly, it results in
-additional delays~\cite{asrese2019measuring, doan2019tracing} that
+additional delays~\cite{asrese2019measuring,doan2019tracing} that
 occur even before the actual download started.
@@
 yet only keeping the fastest answer. In turn, clients either waste
-network resources, or face lower response time.
+network resources, or face slower response time.
 %% there is no information to select the ``best'' node among the
@@
 notify all other \processes by broadcasting its
-operation~\cite{birman1999bimodal, hadzilacos1994modular}. Unfortunately, this also contradicts Edge
+operation~\cite{birman1999bimodal,hadzilacos1994modular}. Unfortunately, this also contradicts Edge
 infrastructure objectives, for such a protocol does not confine the
@@
 
+%% Ultimately, \NAME can constitute a novel building block for
+%% geo-distributed services in need of efficient resource sharing in the
+%% vicinity of regions. For instance, AS-cast could complement content
+%% delivery infrastructures~\cite{triukose2011measuring} by efficiently
+%% sharing between nodes attached to the same CDN server the locations of
+%% web objects that have already been downloaded.  \NAME could even
+%% constitute a decentralized implementation solving the multiple
+%% destinations shortest path problem.
+
 %% Then, we propose \emph{\NAME}, a logical partitioning protocol that

### 2022-06-24 input/related_work.tex
quick format

@@
 facilitates the computation, for it gathers all knowledge in one
-place~\cite{snamp, p2p-oracle, fogstore, p2p-alto}. However, it comes with
+place~\cite{snamp,p2p-oracle,fogstore,p2p-alto}. However, it comes with
 well-known issues such as load balancing, or single point of failure.
@@
 \noindent Distributing this index among \processes circumvents these
-issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
-  coin_19}, but still raises locality issues where \processes
+issues~\cite{voronet,ipfs,mdht,squirrel,triukose2011measuring,coin_19}, but still raises locality issues where \processes
 \begin{inparaenum}[(i)]
@@
 For instance, using \underline{d}istributed \underline{h}ash
-\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
+\underline{t}ables (DHT)~\cite{ipfs,mdht,squirrel}, each \process
 stores a part of the index defined by an interval between hash values.
@@
 view of an ever changing topology across a network is inherently
-complicated~\cite{topology-discovery, ospf}.
+complicated~\cite{topology-discovery,ospf}.
 %%  As for the index, this knowledge about the topology can be either

### 2022-06-24 input/tablerelatedwork.tex
quick format

@@
 
-  \NO{Centralized}~\cite{snamp, p2p-oracle, fogstore, p2p-alto} & \rxmark & one & \cmark & R\\
-  DHT~\cite{ipfs, mdht, squirrel}                               & \rxmark & few & \cmark & R\\
+  \NO{Centralized}~\cite{snamp,p2p-oracle,fogstore,p2p-alto} & \rxmark & one & \cmark & R\\
+  DHT~\cite{ipfs,mdht,squirrel}                               & \rxmark & few & \cmark & R\\
 
@@
 
-  Vector-based routing~\cite{nlsr, ospf}   & \cmark & \NO{all} & \cmark & R/C\\
+  Vector-based routing~\cite{nlsr,ospf}   & \cmark & \NO{all} & \cmark & R/C\\
   Replicated store~\cite{shapiro2011crdts} & \cmark & \NO{all} & \cmark & R/C\\
@@
 
-  Timeout-based~\cite{garcia-lopez, hemmati2015namebased}   & \cmark & scope & \rxmark & \NO{C}\\
+  Timeout-based~\cite{garcia-lopez,hemmati2015namebased}   & \cmark & scope & \rxmark & \NO{C}\\
   Random walks~\cite{sohier2012physarum} & \cmark & scope & \cmark  & \NO{C}\\

### 2022-06-27 input/appendices.tex
quick format
lowering page number, still long way to go 23 over 20

@@
-\appendices
+\appendix
 
@@
 
-\begin{table*}
-  \centering
-  \caption{\label{table:notations}Notation table.}
-  \begin{tabularx}{\textwidth}{@{}lll@{}}
-    \toprule
-    Notation & Short & Description \\
-    \midrule
-
-    $G$ & \underline{G}raph    & Represents a network.\\
-    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
-    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
-    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
-    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
-    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\
-
-    \midrule
-
-    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
-    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
-    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
-    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
-    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
-    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
-    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
-    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
-    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
-    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
-    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\
-
-    \midrule
-
-    $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
-    $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\
-    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\
-
-    \bottomrule
-  \end{tabularx}
-\end{table*}
+\input{input/tablenotations.tex}
 

### 2022-06-27 input/experiments.tex
lowering page number, still long way to go 23 over 20

@@
-\newcommand{\FIGSCALE}{0.99}
+\newcommand{\FIGSCALE}{0.48}
 
@@
 
-\begin{figure}
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
-  \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}
+\begin{figure*}[t]
+  \subfloat[\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.]{
+    \includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf} 
+  }
+  \hspace{5pt}
+  \subfloat[\label{fig:geant}Partitioning overhead of 2
+    clusters connected by a long distance link.]{
+    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
+  }
+  \caption{\TODO{\NAME overhead}.}
+\end{figure*}
 
-  %% \caption{\label{fig:complexity}Cumulative average number of messages
-  %%   per process in a network comprising 10k processes; along with the
-  %%   duration before reaching consistent partitioning after adding or
-  %%   removing a partition, totaling 100 new partition then removed.}
-\end{figure}
+%% \begin{figure}[t]
+%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
+%%   \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}
+
+%%   %% \caption{\label{fig:complexity}Cumulative average number of messages
+%%   %%   per process in a network comprising 10k processes; along with the
+%%   %%   duration before reaching consistent partitioning after adding or
+%%   %%   removing a partition, totaling 100 new partition then removed.}
+%% \end{figure}
 
@@
 
-\begin{figure}
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
-  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2
-    clusters connected by a long distance link.}
-\end{figure}
+%% \begin{figure}[t]
+%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
+%%   \caption{\label{fig:geant}Partitioning overhead of 2
+%%     clusters connected by a long distance link.}
+%% \end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure*}[t]
   \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
@@
   }
-  \caption{Limitations of \NAME and evaluation of \NAMEC for lazy dynamic partitioning.}
+  \caption{Evaluation of \NAMEC for \emph{lazy} dynamic partitioning.}
 \end{figure*}

### 2022-06-27 input/figundoproblem.tex
meow
lowering page number, still long way to go 23 over 20

@@
-\begin{figure*}
-  \newcommand{\SCALE}{0.9}
+\begin{figure*}[t]
+  \newcommand{\SCALE}{0.8}
 
@@
 
-  \newcommand\X{50pt}
-  \newcommand\Y{-50pt}
+  \newcommand\X{42pt}
+  \newcommand\Y{-40pt}
 
@@
     \hspace{5pt}
-    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
+    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers + forwards $\alpha_c$.]
              {\input{input/figundoproblemC.tex}}
     \hspace{5pt}
-    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
+    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers + forwards $\delta_c$.]
              {\input{input/figundoproblemD.tex}}
     \hspace{5pt}
-    \subfloat[Part E][\label{fig:undoproblemE}$a$ echoes back $\alpha_a^2$ that $b$ needs.]
+    \subfloat[Part E][\label{fig:undoproblemE}$a$ echoes back $\alpha_a^2$ to $b$.]
              {\input{input/figundoproblemE.tex}}
     \hspace{5pt}
-    \subfloat[Part F][\label{fig:undoproblemF}$a$, $b$, and $c$ belong to $P_a$.]
+    \subfloat[Part F][\label{fig:undoproblemF}$a$, $b$, $c$ belong to $P_a$.]
              {\input{input/figundoproblemF.tex}}
@@
     differ. Yet, $c$ must act on Figure~\ref{fig:undoproblemE}, and
-    acknowledge then propagate the \emph{possible} staleness of its
-    partition $P_a$.}
+    acknowledge then propagate the \emph{possible} staleness of
+    Partition $P_a$.}
 \end{figure*}

### 2022-06-27 input/proposal.tex
quick format
lowering page number, still long way to go 23 over 20

@@
 This definition encompasses more specific definitions of related
-work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}. It
+work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}. It
 underlines the transitive relevance of messages. It also highlights
@@
 
-\begin{algorithm}
+\begin{algorithm}[t]
   \input{input/algoadd.tex}
@@
   \end{asparadesc}
-  \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed
+  % \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed
   %
@@
 
-\begin{algorithm}
+\begin{algorithm}[t]
   \input{input/algoascast.tex}
@@
 
-\begin{algorithm}[h]
+\begin{algorithm}[t]
   \input{input/algoedges.tex}

### 2022-06-27 input/related_work.tex
lowering page number, still long way to go 23 over 20

@@
 \underline{i}nformation-\underline{c}entric \underline{n}etworking
-(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
+(ICN)~\cite{garcia-lopez,hemmati2015namebased} and distributed
 clustering~\cite{sohier2012physarum}. The sources advertise themselves
 periodically. Advertisements either stop as soon as they reach
-uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
+uninterested \processes~\cite{garcia-lopez,hemmati2015namebased}, or
 propagate through most likely interested
@@
 \item they either operate in synchronous
-  systems~\cite{barjon2014maintaining, sohier2012physarum} or must define
+  systems~\cite{barjon2014maintaining,sohier2012physarum} or must define
   physical-clock-based timeouts the value of which depends on network
-  topology properties such as network diameter~\cite{garcia-lopez,
-    hemmati2015namebased}.
+  topology properties such as network diameter~\cite{garcia-lopez,hemmati2015namebased}.
   %also incur an overhead even in quiet contexts without any update.

### 2022-06-27 input/tablenotations.tex
lowering page number, still long way to go 23 over 20

\begin{table*}
  \scriptsize
  \centering
  \caption{\label{table:notations}Notation table.}
  \begin{tabularx}{\textwidth}{@{}lll@{}}
    \toprule
    Notation & Short & Description \\
    \midrule

    $G$ & \underline{G}raph    & Represents a network.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\

    \midrule

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\

    \midrule

    $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
    $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\
    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\

    \bottomrule
  \end{tabularx}
\end{table*}

### 2022-06-28 input/experiments.tex
almost 20p

@@
 
-\begin{figure*}[t]
-  \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
-    1157 \processes~\cite{knight2011internet}.]{
-    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
-  }
-  \hspace{5pt}
-  \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
-    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
-  }
-  \caption{Evaluation of \NAMEC for \emph{lazy} dynamic partitioning.}
-\end{figure*}
+%% \begin{figure*}[t]
+%%   \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
+%%     1157 \processes~\cite{knight2011internet}.]{
+%%     \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
+%%   }
+%%   \hspace{5pt}
+%%   \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
+%%     \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
+%%   }
+%%   \caption{Evaluation of \NAMEC for \emph{lazy} dynamic partitioning.}
+%% \end{figure*}
 
@@
 
-\subsection{Cross autonomous systems}
-\begin{asparadesc}
-\item[Objective:] Highlight the shortcoming of \NAME in
-  infrastructures composed of multiple autonomous systems and
-    discuss an improvement called \underline{cross} \underline{\NAME}
-    (\NAMEC). At coarse-grained, \NAMEC enables
-    \emph{lazy} %\footnote{Laziness properties and \NAMEC would be
-    %    further detailed in the  additional two pages available in the
-    %    camera-ready version of the article.}
-    dynamic partitioning by
-    allowing AS' gateways to stop notifications when their respective
-    network does not appear to have a source.
+%% \subsection{Cross autonomous systems}
+%% \begin{asparadesc}
+%% \item[Objective:] Highlight the shortcoming of \NAME in
+%%   infrastructures composed of multiple autonomous systems and
+%%     discuss an improvement called \underline{cross} \underline{\NAME}
+%%     (\NAMEC). At coarse-grained, \NAMEC enables
+%%     \emph{lazy} %\footnote{Laziness properties and \NAMEC would be
+%%     %    further detailed in the  additional two pages available in the
+%%     %    camera-ready version of the article.}
+%%     dynamic partitioning by
+%%     allowing AS' gateways to stop notifications when their respective
+%%     network does not appear to have a source.
 
-  \item[Description:] We build a network of networks comprising
-    G{\'E}ANT along with the underlying European NRENs.
-    Figure~\ref{fig:nrens} depicts the resulting infrastructure
-    composed of 1157 \processes distributed in 40 interconnected
-    autonomous systems spanning across
-    Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
-    in the figure) link autonomous systems together, \eg a Lisbon
-    \node links Portugal to Spain and United Kingdoms through a Madrid
-    \node and a London \node respectively.
+%%   \item[Description:] We build a network of networks comprising
+%%     G{\'E}ANT along with the underlying European NRENs.
+%%     Figure~\ref{fig:nrens} depicts the resulting infrastructure
+%%     composed of 1157 \processes distributed in 40 interconnected
+%%     autonomous systems spanning across
+%%     Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
+%%     in the figure) link autonomous systems together, \eg a Lisbon
+%%     \node links Portugal to Spain and United Kingdoms through a Madrid
+%%     \node and a London \node respectively.
 
-    \noindent Figure~\ref{fig:nrens} also depicts the operations
-    executed during the 7 seconds simulation: at 1 second, a \node
-    located in Lisbon, Portugal performs an \texttt{Add}, \ie Lisbon
-    becomes a new source; at 2 seconds, a \node located in Palma de
-    Majorque, Spain performs an \texttt{Add}; at 3 seconds, a \node
-    located in Paris, France performs an \texttt{Add}; at 4 seconds, a
-    \node located in Hvanneyri, Iceland performs an \texttt{Add};
-    finally at 5 seconds, the \node in Spain performs a \texttt{Del},
-    \ie the Spanish source is removed. We chose these sources to
-    illustrate the limitations of \NAME while further motivating the
-    importance of containing the traffic within relevant
-    autonomous systems as proposed by \NAMEC.
+%%     \noindent Figure~\ref{fig:nrens} also depicts the operations
+%%     executed during the 7 seconds simulation: at 1 second, a \node
+%%     located in Lisbon, Portugal performs an \texttt{Add}, \ie Lisbon
+%%     becomes a new source; at 2 seconds, a \node located in Palma de
+%%     Majorque, Spain performs an \texttt{Add}; at 3 seconds, a \node
+%%     located in Paris, France performs an \texttt{Add}; at 4 seconds, a
+%%     \node located in Hvanneyri, Iceland performs an \texttt{Add};
+%%     finally at 5 seconds, the \node in Spain performs a \texttt{Del},
+%%     \ie the Spanish source is removed. We chose these sources to
+%%     illustrate the limitations of \NAME while further motivating the
+%%     importance of containing the traffic within relevant
+%%     autonomous systems as proposed by \NAMEC.
 
-    \noindent In \NAMEC, each
-    \process maintains a \emph{local} index that corresponds to the
-    best partition of its autonomous system, and a \emph{global}
-    index that corresponds to the best partition cross autonomous
-    systems, \ie adjacent autonomous systems that have at least one
-    source.
+%%     \noindent In \NAMEC, each
+%%     \process maintains a \emph{local} index that corresponds to the
+%%     best partition of its autonomous system, and a \emph{global}
+%%     index that corresponds to the best partition cross autonomous
+%%     systems, \ie adjacent autonomous systems that have at least one
+%%     source.
 
-    \noindent To compare \NAME against \NAMEC, we measure the number
-    of messages transiting through the network for each operation, as
-    well as the number of \processes that maintain an index (\ie that
-    belong to a partition) over time.
+%%     \noindent To compare \NAME against \NAMEC, we measure the number
+%%     of messages transiting through the network for each operation, as
+%%     well as the number of \processes that maintain an index (\ie that
+%%     belong to a partition) over time.
 
-  \item[Results:] Figure~\ref{fig:europe-ases} shows the
-    results of this experiment. The top part highlights the cost of
-    each partitioning protocol after each operation, while the bottom
-    part provides the insight that explains these costs by displaying
-    the number of indexes maintained by each protocol.
+%%   \item[Results:] Figure~\ref{fig:europe-ases} shows the
+%%     results of this experiment. The top part highlights the cost of
+%%     each partitioning protocol after each operation, while the bottom
+%%     part provides the insight that explains these costs by displaying
+%%     the number of indexes maintained by each protocol.
 
-    \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
-    \texttt{Add} costs an order of magnitude more with \NAME compared
-    to \NAMEC.  \NAME's messages propagate through all Europe, for
-    \NAME regards Europe as a single network of 1157 \processes while
-    \NAMEC's messages propagate through Portugal's network of 23
-    \processes only.
-    % 
-    \noindent  Spain's
-    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
-    gateway in Madrid links Portugal to Spain and the rest of
-    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
-    is, only 11 \processes in Spain actually need to receive and
-    deliver the new notification, which explains the small overhead of this
-    operation with \NAME. Using \NAMEC, the overhead is slightly
-    higher since
-    \begin{inparaenum}[(i)]
-    \item the 20 \processes of Spain's network need to receive and
-      deliver the new notification, \emph{and}
-    \item Madrid's gateway echoes Lisbon's notification as soon as it
-      receives Palma's notification to 11 \processes.
-    \end{inparaenum}
+%%     \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
+%%     \texttt{Add} costs an order of magnitude more with \NAME compared
+%%     to \NAMEC.  \NAME's messages propagate through all Europe, for
+%%     \NAME regards Europe as a single network of 1157 \processes while
+%%     \NAMEC's messages propagate through Portugal's network of 23
+%%     \processes only.
+%%     % 
+%%     \noindent  Spain's
+%%     \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
+%%     gateway in Madrid links Portugal to Spain and the rest of
+%%     Europe. Since Lisbon is closer to Madrid than Palma de Majorque
+%%     is, only 11 \processes in Spain actually need to receive and
+%%     deliver the new notification, which explains the small overhead of this
+%%     operation with \NAME. Using \NAMEC, the overhead is slightly
+%%     higher since
+%%     \begin{inparaenum}[(i)]
+%%     \item the 20 \processes of Spain's network need to receive and
+%%       deliver the new notification, \emph{and}
+%%     \item Madrid's gateway echoes Lisbon's notification as soon as it
+%%       receives Palma's notification to 11 \processes.
+%%     \end{inparaenum}
 
-    \noindent Figure~\ref{fig:europe-ases} also highlights the worst
-    case scenario of \NAME: the cost of France's \texttt{Add} is close
-    to that of Portugal's \texttt{Add} since it updates the whole
-    Europe excluding Portugal and Spain. Contrarily, \NAMEC only
-    updates France's 39 \processes.
+%%     \noindent Figure~\ref{fig:europe-ases} also highlights the worst
+%%     case scenario of \NAME: the cost of France's \texttt{Add} is close
+%%     to that of Portugal's \texttt{Add} since it updates the whole
+%%     Europe excluding Portugal and Spain. Contrarily, \NAMEC only
+%%     updates France's 39 \processes.
 
-    \noindent The last \texttt{Add} operation in Iceland has similar
-    cost for \NAME and \NAMEC. Indeed, they both update Iceland, and
-    when the notifications reach Copenhagen in Danemark, they stop
-    either because France's notifications are closer (\NAME) or the
-    Danish network does not have any source (\NAMEC).
+%%     \noindent The last \texttt{Add} operation in Iceland has similar
+%%     cost for \NAME and \NAMEC. Indeed, they both update Iceland, and
+%%     when the notifications reach Copenhagen in Danemark, they stop
+%%     either because France's notifications are closer (\NAME) or the
+%%     Danish network does not have any source (\NAMEC).
 
-    \noindent Finally, Figure~\ref{fig:europe-ases} shows that
-    Spain's \texttt{Del} have similar cost for \NAME and
-    \NAMEC. Nevertheless, the trade-off is different: \NAME's overhead
-    comes from the 11 \nodes that need to acknowledge staleness and
-    deliver the echos from Portugal; \NAMEC's overhead comes from the
-    20 \nodes that need to acknowledge staleness. Using \NAMEC,
-    Spain's network does not propagate echos since it does not have
-    any source anymore.
+%%     \noindent Finally, Figure~\ref{fig:europe-ases} shows that
+%%     Spain's \texttt{Del} have similar cost for \NAME and
+%%     \NAMEC. Nevertheless, the trade-off is different: \NAME's overhead
+%%     comes from the 11 \nodes that need to acknowledge staleness and
+%%     deliver the echos from Portugal; \NAMEC's overhead comes from the
+%%     20 \nodes that need to acknowledge staleness. Using \NAMEC,
+%%     Spain's network does not propagate echos since it does not have
+%%     any source anymore.
 
-\end{asparadesc}
+%% \end{asparadesc}
 

### 2022-06-28 input/proposal.tex
almost 20p

@@
 notifications, even in dynamic networks where nodes join, leave, or
-crash at any time. For convenience, Appendix~\ref{appendix:notations}
-summarizes the notations used throughout the paper.
+crash. % at any time. % For convenience, Appendix~\ref{appendix:notations}
+% summarizes the notations used throughout the paper.
 
@@
 \begin{definition}[\label{def:forwarding}Forwarding]
-  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
+  When $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
   \underline{s}ends it ($s_{xy}(m)$) to all its neighbors $y$

### 2022-06-28 input/experiments.tex
meow

@@
 \item [Objective:] Confirm that \NAME locks down the traffic of
-  decentralized content indexing in the context of dynamic
-  inter-autonomous system communications.
+  decentralized content indexing in dynamic
+  inter-autonomous systems.
 
@@
 cluster, the new link does not trigger noticeable traffic, for
-\processes already know their closest source located in their cluster.
+\processes already know their closest source in their cluster.
 

### 2022-06-28 input/experiments.tex
meow

@@
-\newcommand{\FIGSCALE}{0.48}
+\newcommand{\FIGSCALE}{0.68}
 
@@
 evaluate and assess distributed algorithms in large scale
-networks~\cite{montresor2009peersim}. All the code is available on the
-Github platform at \mbox{\url{https://github.com/ane-wane/as-cast}}.
+networks~\cite{montresor2009peersim}. All the code is available % on % the
+%Github platform
+at \mbox{\url{https://github.com/ane-wane/as-cast}}.
 
@@
 %
-To favor more concurrent operations, we voluntary set
+To favor more concurrent operations, we % voluntary
+set
 weights and latency to different values: each link has a weight
 between 5 and 15 set randomly using a uniform distribution. This
-allows nodes to receive messages in a different order than their
-respective shortest path generating more messages to reach consistent
+allows nodes to receive messages in different orders, % than their
+% respective shortest path
+therefore generating more messages to reach consistent
 partitioning.
@@
 
-\noindent We measure the average number of messages generated per
+\noindent We measure the average number of messages % generated
+per
 \process per second; and the time before reaching consistent
@@
 
-\begin{figure*}[t]
-  \subfloat[\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.]{
-    \includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf} 
-  }
-  \hspace{5pt}
-  \subfloat[\label{fig:geant}Partitioning overhead of 2
-    clusters connected by a long distance link.]{
-    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
-  }
-  \caption{\TODO{\NAME overhead}.}
-\end{figure*}
+%% \begin{figure*}[t]
+%%   \subfloat[\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.]{
+%%     \includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf} 
+%%   }
+%%   \hspace{5pt}
+%%   \subfloat[\label{fig:geant}Partitioning overhead of 2
+%%     clusters connected by a long distance link.]{
+%%     \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
+%%   }
+%%   \caption{\TODO{\NAME overhead}.}
+%% \end{figure*}
 
-%% \begin{figure}[t]
-%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
-%%   \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}
+\begin{figure}[t]
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
+  \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}
 
@@
 %%   %%   removing a partition, totaling 100 new partition then removed.}
-%% \end{figure}
+\end{figure}
 
@@
 \noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
-depends on the size of partitions. In this scenario, it empirically
+depends on the size of partitions. % In this scenario,
+This % empirically
 corresponds to a complexity in terms of number of messages of
@@
 for $\delta$ messages must reach the partition borders before sound
-competitors propagate their partition. It is worth noting that this
+competitors propagate their partition. % It is worth noting that
+This
 delete operation involves concurrency: removals still propagate while
@@
 
-%% \begin{figure}[t]
-%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
-%%   \caption{\label{fig:geant}Partitioning overhead of 2
-%%     clusters connected by a long distance link.}
-%% \end{figure}
+\begin{figure}[t]
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
+  \caption{\label{fig:geant}Partitioning overhead of 2
+    clusters connected by a long distance link.}
+\end{figure}
 

### 2022-06-28 input/introduction.tex
meow

@@
 The rest of this paper is organized as
-follows. Section~\ref{sec:background} illustrates the motivation and
-problem behind our proposal.  Section~\ref{sec:adaptive} describes
+follows. Sec.~\ref{sec:background} illustrates the motivation and
+problem behind our proposal.  Sec.~\ref{sec:adaptive} describes
 dynamic consistent partitioning and its
-implementation. Section~\ref{sec:experimentation} presents our
-evaluations.  Section~\ref{sec:related_work} reviews related
-work. Finally, Section~\ref{sec:conclusion} concludes and discusses
+implementation. Sec.~\ref{sec:experimentation} presents our
+evaluations.  Sec.~\ref{sec:related_work} reviews related
+work. Finally, Sec.~\ref{sec:conclusion} concludes and discusses
 future work.

### 2022-06-28 input/proposal.tex
meow

@@
 \begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
-    \centernot\implies \textup{DCP}$] Forwarding best up-to-date,
-  forwarding staleness, and echoing is not sufficient to guarantee
+    \centernot\implies \textup{DCP}$] Forwarding best up-to-date
+  and staleness, and echoing is not sufficient to guarantee
   dynamic consistent partitioning.
@@
     \eventually d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in
-    D_{\pi_{xz}[k+1]}$ which means that $\pi_{xz}[k+1]$ already
-    delivered and forwarded $\delta_x$ following another such a chain
-    of delivery. Therefore, $z$ eventually receives, hence delivers
+    D_{\pi_{xz}[k+1]}$ meaning that $\pi_{xz}[k+1]$ already
+    delivered and forwarded $\delta_x$ following another 
+    delivery chain. Therefore, $z$ eventually receives, hence delivers
     $\delta_x$ (outcome \ref{lem:detectorA}).

### 2022-06-28 input/appendices.tex
almost 20p
major changes everywhere

@@
 \label{appendix:notations}
-
-Table~\ref{table:notations} summarizes the notations used throughout
-this paper. For the sake of clarity, we divide them into three
-categories: network, \process, and message.
-
 \input{input/tablenotations.tex}
 
-\section{Proof of Theorem~\ref{theo:fb}}
-\label{appendix:fb}
+%% Table~\ref{table:notations} summarizes the notations used throughout
+%% this paper. For the sake of clarity, we divide them into three
+%% categories: network, \process, and message.
 
-\begin{proof}
-  Whenever a \process~$s$ becomes a source, it broadcasts hence
-  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
-  its set of received messages, it acknowledges that it belongs to its
-  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
-  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
-  \noindent Such a source forwards its notification to its neighbors.
-  Every neighbor eventually receives its notification since
-  communication links are reliable. Whatever the order of received
-  messages $R_x$ at neighboring \process~$x$, total order ensures that
-  it delivers notifications $\alpha_s^{d}$ when
-  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
-  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
-  this case.
-  \noindent Among these neighbors, at least those that fulfill the
-  latest condition forward their respective notification.  By
-  transitivity, the message originating from $s$ reaches all
-  \processes that belong to $P_s$ at least through their respective
-  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
-    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
-    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
-  quiescent, \ie no \process becomes source anymore, every \process
-  eventually acknowledges the partition it belongs to, \ie \processes
-  eventually reach consistent partitioning together. In addition, the
-  protocol terminates: a \process never delivers hence forwards a
-  message after it received, delivered, and forwarded the message of
-  its closest source from its lightest path.
-\end{proof}
+% \section{Appendix: Proofs of Theorem~\ref{theo:fb} and Theorem~\ref{theo:fbfsdcp}}
+% \label{appendix:fb}
 
-\section{Proof of Theorem~\ref{theo:fbfsdcp}}
-\label{appendix:fbfsdcp}
-
-\begin{proof}
-  Detection triggers forwarding of staleness downstream which
-  completes the case study of Lemma~\ref{lem:detector} by ensuring
-  that, when a source broadcasts its staleness notification, all
-  \processes that belong to its partition eventually deliver such a
-  staleness notification. All downstream bordering \processes also
-  eventually receive such a staleness notification and echo back their
-  best delivered message. This triggers another competition as in
-  Theorem~\ref{theo:fb} for the \processes that delivered the
-  staleness notification.
-\end{proof}
-
-%% \section{Related work summary}
-
-%% Table~\ref{table:relatedwork} provides a summary of state-of-the-art
-%% approaches along with the reason they fail to enable quick content
-%% indexing in large scale dynamic systems.
-
-%% \input{input/tablerelatedwork.tex}
+%%\section{Proof of Theorem~\ref{theo:fbfsdcp}}
+%% \label{appendix:fbfsdcp}

### 2022-06-28 input/experiments.tex
meow
major changes everywhere

@@
 
-\subsection{Scalability and trade-off}
+\subsection{Scalability and trade-off of \NAME}
 \begin{asparadesc}
-\item [Objective:] Confirm the scalability of \NAME by highlighting the
-  trade-off between the current partitioning of the system and the
-  protocol's overhead in terms of generated traffic and termination
-  time.
+%% \item [Objective:] Confirm the scalability of \NAME by highlighting the
+%%   trade-off between the current partitioning of the system and the
+%%   protocol's overhead in terms of generated traffic and termination
+%%   time.
 
@@
 
-\begin{figure}[t]
-  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
-  \caption{\label{fig:geant}Partitioning overhead of 2
-    clusters connected by a long distance link.}
-\end{figure}
-
-\subsection{Traffic containment}
-\item [Objective:] Confirm that \NAME locks down the traffic of
-  decentralized content indexing in dynamic
-  inter-autonomous systems.
+\subsection{Traffic containment in dynamic inter-autonomous systems}
+%% \item [Objective:] Confirm that \NAME locks down the traffic of
+%%   decentralized content indexing in dynamic
+%%   inter-autonomous systems.
 
@@
 %% \end{figure*}
+
+\begin{figure}[t]
+  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
+  \caption{\label{fig:geant}Partitioning overhead of 2
+    clusters connected by a long distance link.}
+\end{figure}
 
@@
 \item[Overall,] these experiments highlight the scalability of \NAME
-    and \NAMEC in dynamic networks such as Edge infrastructures. Next
+  %and \NAMEC
+  in dynamic networks such as Edge infrastructures. Next
   Section reviews state-of-the-art approaches that can index content

### 2022-06-28 input/figsimplerproblem.tex
meow
lowering page number, still long way to go 23 over 20
major changes everywhere

@@
 
-  \newcommand\X{50pt}
-  \newcommand\Y{-50pt}
+  \newcommand\X{41pt}
+  \newcommand\Y{-40pt}
 
@@
     \hspace{5pt}
-    \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
-     while $b$ delivers and forwards $\alpha_a$.]
+    \subfloat[Part B][\label{fig:problemB}$a$ and $c$ delete their partition while $b$ delivers and forwards $\alpha_a$.]
              {\input{input/figsimplerproblemB.tex}}
@@
     \hspace{5pt}
-    \subfloat[Part D][\label{fig:problemD}$\alpha_c^3$ reaches $a$ that delivers it.]
+    \subfloat[Part D][\label{fig:problemD}$a$ receives + delivers $\alpha_c^3$.]
+    %$\alpha_c^3$ reaches $a$ that delivers it.]
              {\input{input/figsimplerproblemD.tex}}
     \hspace{5pt}
-    \subfloat[Part E][\label{fig:problemE}$\delta_c$ reaches $a$ that delivers it.]
+    \subfloat[Part E][\label{fig:problemE}$a$ receives + delivers $\delta_c$.]
+    %$\delta_c$ reaches $a$ that delivers it.]
              {\input{input/figsimplerproblemE.tex}}
     \hspace{5pt}
-    \subfloat[Part F][\label{fig:problemF}$a$ and $b$ do not belong to any partition but
-      $c$ stays forever in a stale one: $P_a$.]
+    \subfloat[Part F][\label{fig:problemF}$c$ is stuck in a stale $P_a$.]%$c$ stays forever in a stale partition: $P_a$.]
              {\input{input/figsimplerproblemF.tex}}
   \end{center}
-  \caption{\label{fig:problem}Even in the simplest scenarios, the
-    naive propagation of $\alpha$ and $\delta$ messages may be
+  \caption{\label{fig:problem}% Even in the simplest scenarios,
+    The naive propagation of messages is
     insufficient to guarantee consistent partitioning. If $c$ had

### 2022-06-28 input/introduction.tex
20p
major changes everywhere

@@
 
-\input{input/figpartitionintuition.tex} %% positioning
-
 Such approaches are in contradiction with the objectives of Edge
@@
 of content indexing services. Without information about these
-locations, it often ends up downloading from multiple replica hosts,
+locations, it often ends up downloading from multiple %replica
+hosts,
 yet only keeping the fastest answer. In turn, clients either waste
@@
   \item \NAME does not generate traffic in quiescent systems; and
-  \item \NAME enables consistent partitioning even in networks subject
+  \item \NAME operates even in networks subject
     to physical partitioning.

### 2022-06-28 input/proposal.tex
20p
major changes everywhere

@@
+\begin{table}
+  \caption{\label{table:notations}Notation table.}
+  \input{input/tablenotations.tex}
+\end{table}
+
 \section{Adaptive scoped broadcast}
@@
 notifications, even in dynamic networks where nodes join, leave, or
-crash. % at any time. % For convenience, Appendix~\ref{appendix:notations}
-% summarizes the notations used throughout the paper.
+crash. % at any time.
+For convenience, Table~\ref{table:notations}
+summarizes the notations used throughout the paper.
 
@@
 We use scoped broadcast to efficiently modify the state of each
-\process depending on the partitions that exist in the system.
+\process depending on the partitions that exist in the system to reach consistent partitioning.
 
@@
 or operational costs when dealing with multiple tenants.
-
-\input{input/figadd.tex}
 
@@
 \begin{proof}
-  Proof in Appendix~\ref{appendix:fb}.
-%%   Whenever a \process~$s$ becomes a source, it broadcasts hence
-%%   delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
-%%   its set of received messages, it acknowledges that it belongs to its
-%%   own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
-%%   it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
-%%   \noindent Such a source forwards its notification to its neighbors.
-%%   Every neighbor eventually receives its notification since
-%%   communication links are reliable. Whatever the order of received
-%%   messages $R_x$ at neighboring \process~$x$, total order ensures that
-%%   it delivers notifications $\alpha_s^{d}$ when
-%%   $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
-%%   is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
-%%   this case.
-%%   \noindent Among these neighbors, at least those that fulfill the
-%%   latest condition forward their respective notification.  By
-%%   transitivity, the message originating from $s$ reaches all
-%%   \processes that belong to $P_s$ at least through their respective
-%%   lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
-%%     |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
-%%     d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
-%%   quiescent, \ie no \process becomes source anymore, every \process
-%%   eventually acknowledges the partition it belongs to, \ie \processes
-%%   eventually reach consistent partitioning together. In addition, the
-%%   protocol terminates: a \process never delivers hence forwards a
-%%   message after it received, delivered, and forwarded the message of
-%%   its closest source from its lightest path.
+  \input{input/prooftheoremfb}
+  % Proof in Appendix~\ref{appendix:fb}.
 \end{proof}
 
-\begin{algorithm}[t]
-  \input{input/algoadd.tex}
-  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
-\end{algorithm}
+\input{input/figadd.tex}
 
@@
 
-\input{input/figsimplerproblem.tex} %% positioning
-
-\input{input/figdel.tex}
-
 \begin{definition}[\label{def:dcp}\underline{D}ynamic
@@
 \texttt{Del} operation implicitly states that its preceding
-\texttt{Add} operation becomes obsolete. As consequence, their results
+\texttt{Add} operation becomes obsolete. % As consequence,
+Their results
 -- scoped broadcast in the form of \texttt{\underline{A}dd}
@@
 
+\begin{algorithm}[t]
+  \input{input/algoadd.tex}
+  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
+\end{algorithm}
+
 \newcommand{\last}{\textup{last}~}
+
+\input{input/figdel.tex}
 
@@
 forwarding of best (FB) as stated by Theorem~\ref{theo:fb}.
-
-\input{input/figundoproblem.tex}
 
@@
 \begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
-    \centernot\implies \textup{DCP}$] Forwarding best up-to-date
-  and staleness, and echoing is not sufficient to guarantee
-  dynamic consistent partitioning.
+    \centernot\implies \textup{DCP}$] Forwarding best up-to-date,
+  staleness, and echoes is not sufficient to guarantee dynamic
+  consistent partitioning.
 \end{lemma}
@@
 Figure~\ref{fig:problem} depicts a scenario comprising only three
-\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
-receive the messages in the order of their sending ($s_{pq}(m)
-\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
+\processes $a$, $b$, $c$ chained with FIFO links where \processes
+receive the messages in the order of their sending. % ($s_{pq}(m)
+%\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$).
+In
 Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
@@
 reach consistent partitioning. \end{proof}
+
+\input{input/figsimplerproblem.tex}
 
@@
 
+\input{input/figundoproblem.tex}
+
 As a second step, detecting \processes must proactively purge the
@@
 \begin{proof}
-  Proof in Appendix~\ref{appendix:fbfsdcp}.
-%%   Detection triggers forwarding of staleness downstream which
-%%   completes the case study of Lemma~\ref{lem:detector} by ensuring
-%%   that, when a source broadcasts its staleness notification, all
-%%   \processes that belong to its partition eventually deliver such a
-%%   staleness notification. All downstream bordering \processes also
-%%   eventually receive such a staleness notification and echo back their
-%%   best delivered message. This triggers another competition as in
-%%   Theorem~\ref{theo:fb} for the \processes that delivered the
-%%   staleness notification.
+  \input{input/prooftheoremfbfsdcp}
 \end{proof}
@@
 
-\begin{algorithm}[t]
-  \input{input/algoedges.tex}
-  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
-\end{algorithm}
+%% \begin{algorithm}[t]
+%%   \input{input/algoedges.tex}
+%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
+%% \end{algorithm}
 
 By reusing \NAME's default behavior of echos and downstream staleness,
-Algorithm~\ref{algo:edges} enables dynamic consistent partitioning
+Algorithm~\ref{algo:ascast} also enables dynamic consistent partitioning
 even in dynamic networks subject to physical partitioning where

### 2022-06-28 input/tablenotations.tex
major changes everywhere

@@
-\begin{table*}
+% \begin{table*}
   \scriptsize
-  \centering
-  \caption{\label{table:notations}Notation table.}
+%  \centering
+%  \caption{\label{table:notations}Notation table.}
   \begin{tabularx}{\textwidth}{@{}lll@{}}
@@
     $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
-    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
-    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\
+    $\pi_{xz}$/$\Pi_{xz}$  & \underline{p}ath/best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
+    $|\pi_{xz}|$/$|\Pi_{xz}|$ & sum of weights & Positive sum of weights of the path.\\
 
@@
     $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
-    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
+    $r_y(m)$/$r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node/\Process $x$.\\
     $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
@@
     $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
-    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
+    $\phi(\mu, \sigma)$ & predicate & Checks the metadata $\mu$ using the state $\sigma$.\\
     $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
-    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
+    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. $d$, $s$, $r$ etc. are events.\\
     $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\
@@
     $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
-    $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\
-    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\
+    $\delta_x$   & source \underline{d}eletion & Message that notifies the possible deletion of Source $x$ by \Process $x$.\\
+    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information.\\% since its broadcaster broadcast a newer message.\\
 
@@
   \end{tabularx}
-\end{table*}
+% \end{table*}

### 2022-06-28 input/proposal.tex
reworked figure and 20p

@@
 \begin{table}
-  \caption{\label{table:notations}Notation table.}
+  \caption{\label{table:notations}Summary of notations.}
   \input{input/tablenotations.tex}
@@
 \end{inparaenum}
-Figure~\ref{fig:problem} depicts a scenario comprising only three
-\processes $a$, $b$, $c$ chained with FIFO links where \processes
+In Figure~\ref{fig:problem}, $a$, $b$, $c$ are chained with FIFO links, \ie \processes
 receive the messages in the order of their sending. % ($s_{pq}(m)
 %\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$).
-In
-Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
+In Figure~\ref{fig:problemA}, $a$ and $c$ become sources, sending
 their respective notification message to $b$. In
-Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
-while $b$ receives, delivers, and forwards $\alpha_a^2$. In
+Figure~\ref{fig:problemB}, $a$ and $c$ delete their partition while
+$b$ receives, delivers, and forwards $\alpha_a^2$. In
 Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
@@
 and \ref{fig:problemE}, $a$ and $b$ handle transiting
-notifications. Finally, Figure~\ref{fig:problemF} shows that
-eventually, $c$ stays in the deleted partition $P_a$ for not having
-received $\delta_a$ that $b$ blocked earlier. The system does not
-reach consistent partitioning. \end{proof}
+notifications. Finally, Figure~\ref{fig:problemF} shows that $c$ is stuck
+in the deleted $P_a$ for not having received $\delta_a$ that
+$b$ blocked earlier. The system does not reach consistent
+partitioning. \end{proof}
 

### 2022-06-28 input/figdel.tex
lowering page number, still long way to go 23 over 20
major changes everywhere
reworkd figures so they dont overlap, added a figure about naive deletes

@@
-\begin{figure}
-  \newcommand{\SCALE}{0.95}
+\begin{figure}[t]
+  \newcommand{\SCALE}{0.8}
+
+  \newcommand\X{42pt}
+  \newcommand\Y{-40pt}
+
+  \thickmuskip=0mu
+  \medmuskip=0mu
+  \thinmuskip=0mu
+
+  \newcommand\INVISIBLESPACING{1.6}
+  \newcommand\ADD{\alpha}
+  \newcommand\DEL{\delta}
+
+  \newcommand{\OACK}{0.5} %% opacity of acknowledgement alpha messages
 
@@
     \hspace{3pt}
-    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as it encounters
+    \subfloat[Part B][\label{fig:delB}$\delta$ stops when it encounters
       another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
+    \hspace{3pt}
+    \subfloat[Part C][\label{fig:delC}$a$ receives, delivers, and forwards the message $\alpha_d^3$.
+      Every node belongs to $P_d$.]{\input{input/figdelC.tex}}
   \end{center}
   \caption{\label{fig:del}Efficient removal of a partition using
-    scoped broadast. $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
+    scoped broadast.} % $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
 \end{figure}

### 2022-06-28 input/introduction.tex
reworkd figures so they dont overlap, added a figure about naive deletes

--- 2022-06-24 input/introduction.tex
@@
 evaluations.  Section~\ref{sec:related_work} reviews related
-work. Finally, Section~\ref{sec:conclusion} concludes and discusses
+work. Section~\ref{sec:conclusion} concludes and discusses
 future work.

### 2022-06-28 input/proposal.tex
reworkd figures so they dont overlap, added a figure about naive deletes

@@
   In addition to FB, a \process $x$ that receives but does not deliver
-  a staleness notification $\delta_{s}$ sends back --~or echoes~-- its
+  a staleness notification $\delta_{s}$ replies by --~or echoes~-- its
   best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
@@
   s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.
-
-  % $r_{xy}(\alpha_s)
-  % \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
-  % ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
-  % D_x$. \TODO{Rework min}
 \end{definition}
@@
 echo back its own best up-to-date message $\alpha_d^3$, for it may be
-the best for $a$. Eventually, every \process belongs to Partition
-$P_d$. In this scenario, they reach consistent
+the best for $a$. Figure~\ref{fig:delC} shows that every \process eventually belongs to 
+$P_d$, therefore reaching consistent
 partitioning. Unfortunately, this protocol does not ensure consistent

### 2022-08-31 input/conclusion.tex
meow
toward camera ready

@@
 lead to inconsistent partitioning.
-%% The major difficulty lies in concurrent operations, each having a
-%% different scope, and ensure the correct convergence of the system.  We
-%% defined, in particular, multiple properties that highlight this
-%% complexity.
 %
 We highlighted the properties that solve this problem and proposed an
-implementation called \NAME.  Simulations confirmed that
+implementation called \NAME for \underline{A}daptive
+\underline{S}coped broad\underline{cast}.  Simulations confirmed that
 \processes quickly reach consistent partitioning together while the
-generated traffic remains locked down to partitions.  We also 
-discussed an improvement further containing the traffic inside relevant
-autonomous systems.
-%% correctness of our protocol as well as the confinement of
-%% the traffic only where it is needed.
+generated traffic remains locked down to partitions.
 
-%% As future work, we plan to leverage the hierarchical properties of
-%% interconnected autonomous systems to further limit the propagation of
-%% indexes within interested systems only. We expect that such an
-%% improvement would greatly benefit the autonomous systems, and
-%% particularly those hosting a large number of contents.
+As future work, we plan to leverage the hierarchical properties of
+interconnected autonomous systems~\cite{nur2018geography} to further
+limit the propagation of indexes within interested systems only.  We
+expect that such an improvement would greatly benefit the autonomous
+systems, and particularly those hosting a large number of contents.
+Indeed, \NAME ensures that every \process eventually acknowledges its
+closest content replica. This feature unfortunately becomes an issue
+when each \process is only interested by a small portion of
+content.
 
-%% Systems hosting a large number of contents would greatly benefit from
-%% this improvement.
-
-%% As future work, we plan to enable lazy retrieval of partitions when a
-%% large number of contents is involved. Indeed, using \NAME, every
-%% \process partakes in the propagation of all indexes which raises
-%% scalability issues. We would like to leverage the hierarchical
-%% properties of
-%% % interconnected
-%% autonomous systems to limit the
-%% propagation of such indexes only to interested systems.
-
-%
-%% As ongoing and future work, we are currently studying how it might be
-%% possible to limit the scope of a partition to one autonomous system at
-%% most. Indeed, the gain of propagating changes to \processes belonging to
-%% another autonomous system might be negligible as the latency penalty
-%% is mainly due to inter autonomous systems' links (\eg trans-continental
-%% links).  Exactly, we are investigating how such a change can be
-%% formalized and its impact on the current protocol.
-%
-%autonomous systems. Indeed, \processes could leverage the hierarchical
-%properties of the Internet topology~\cite{nur2018geography} to avoid
-%flooding the whole systems with control information about all
-%partitions.
-%\TODO{should we highlight this at the end of the experiment}
-%
-
-As future work, we plan to evaluate our proposal within a concrete
-storage system such as \underline{I}nter\underline{P}lanetary
-\underline{F}ile \underline{S}ystem (IPFS)~\cite{ipfs}. This would
-assess the relevance of \NAME in real systems subject to high
-dynamicity, and compare it against its current DHT-based indexing
-system that does not include distance in its operation. More
-generally, we claim that \NAME and its extension can constitute novel
-building blocks for geo-distributed services.  For instance, \NAME
-could complement content delivery
+We also plan to evaluate our proposal within a concrete storage system
+such as \underline{I}nter\underline{P}lanetary \underline{F}ile
+\underline{S}ystem (IPFS)~\cite{ipfs}. This would assess the relevance
+of \NAME in real systems subject to high dynamics, and compare it
+against its current DHT-based indexing system that does not include
+distance in its operation. More generally, we claim that \NAME and its
+extension can constitute novel building blocks for geo-distributed
+services.  For instance, \NAME could complement content delivery
 infrastructures~\cite{triukose2011measuring} by efficiently sharing
@@
 reduce the overall traffic footprint.
-
-%% Such an integration would enable us to to perform additional
-%% experiments and observe the gain with respect to the DHT-based
-%% approach that is currently used.
-
-%% In addition to this action, it would make sense to evaluate
-%% the use of \NAME within a concrete storage systems, such as
-%% \underline{I}nter\underline{P}lanetary \underline{F}ile
-%% \underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
-%% integration would enable us to to perform additional experiments and
-%% observe the gain with respect to the DHT-based approach that is
-%% currently used.
-
 %

### 2022-08-31 input/proposal.tex
toward camera ready

@@
 notifications, even in dynamic networks where nodes join, leave, or
-crash. % at any time.
+crash at any time.
 For convenience, Table~\ref{table:notations}
@@
 
+\begin{algorithm}[t]
+  \input{input/algoadd.tex}
+  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
+\end{algorithm}
+
 \subsection{Dynamic consistent partitioning}
@@
 
-\begin{algorithm}[t]
-  \input{input/algoadd.tex}
-  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
-\end{algorithm}
-
 \newcommand{\last}{\textup{last}~}
@@
 that receives a staleness notification $\delta_s$ forwards it only if
-the latter targets its current partition $\alpha_s$. The staleness
-notifications propagate through the network as long as they remain in
-the deleted partition. When they reach the bordering \processes of the
-deleted partition, it creates an echo of bordering partitions that
-will go backward to fill the gap left open by removals using
-forwarding of best (FB) as stated by Theorem~\ref{theo:fb}.
+the latter targets its current partition $\alpha_s$. These messages
+propagate as long as they remain in the deleted partition. When they
+reach the bordering \processes of the deleted partition, it creates an
+echo of bordering partitions that will go backward to fill the gap
+left open by removals using forwarding of best (FB) as stated by
+Theorem~\ref{theo:fb}.
 
@@
   a staleness notification $\delta_{s}$ replies by --~or echoes~-- its
-  best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
+  best up-to-date delivered message:\\$(\last D_x = \alpha_{s'}^d
   \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow

### 2022-09-14 input/proposal.tex
Typos to cope with American english

@@
 communication primitive that propagates a message around its
-broadcaster within an application-dependant scope.
+broadcaster within an application-dependent scope.
 
@@
 neighboring \processes that are closer to this source than any other
-one. Such a distance (or \emph{weight}) is application-dependant: in
+one. Such a distance (or \emph{weight}) is application-dependent: in
 the context of maintaining distributed indexes, this would be about

### 2022-09-14 input/figsimplerproblem.tex
reworked figure and 20p
toward camera ready
working on newpages

@@
 \begin{figure*}[t]
-  \newcommand{\SCALE}{0.8}
+  \renewcommand{\SCALE}{0.8}
 
+  \newcommand{\SNODE}{\scriptsize}
   \newcommand{\SMSG}{\tiny}
@@
       $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
-    \hspace{5pt}
+    \hspace{2pt}
     \subfloat[Part B][\label{fig:problemB}$a$ and $c$ delete their partition while $b$ delivers and forwards $\alpha_a$.]
              {\input{input/figsimplerproblemB.tex}}
-    \hspace{5pt}
+    \hspace{2pt}
     \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
@@
              {\input{input/figsimplerproblemC.tex}}
-    \hspace{5pt}
-    \subfloat[Part D][\label{fig:problemD}$a$ receives + delivers $\alpha_c^3$.]
+    \hspace{2pt}
+    \subfloat[Part D][\label{fig:problemD}$a$ receives, delivers, and forwards $\alpha_c^3$.]
     %$\alpha_c^3$ reaches $a$ that delivers it.]
              {\input{input/figsimplerproblemD.tex}}
-    \hspace{5pt}
-    \subfloat[Part E][\label{fig:problemE}$a$ receives + delivers $\delta_c$.]
+    \hspace{2pt}
+    \subfloat[Part E][\label{fig:problemE}$a$ receives, delivers, and forwards $\delta_c$.]
     %$\delta_c$ reaches $a$ that delivers it.]
              {\input{input/figsimplerproblemE.tex}}
-    \hspace{5pt}
-    \subfloat[Part F][\label{fig:problemF}$c$ is stuck in a stale $P_a$.]%$c$ stays forever in a stale partition: $P_a$.]
+    \hspace{2pt}
+    \subfloat[Part F][\label{fig:problemF}$c$ is stuck in a stale partition $P_a$.]%$c$ stays forever in a stale partition: $P_a$.]
              {\input{input/figsimplerproblemF.tex}}

### 2022-09-14 input/proposal.tex
working on newpages

@@
 delivered, and forwarded the stale notification $\alpha_c^1$. In other
-terms, $c$ acknowledges that between the delivery of $\alpha_c^1$ and
-the delivery of $\delta_c$, $b$ blocked any other $\delta$ and
-therefore, it could have blocked $\delta_a$.
+terms, \Node $c$ acknowledges that between the delivery of
+$\alpha_c^1$ and the delivery of $\delta_c$, \Process $b$ blocked all other
+$\delta$ messages and therefore, it could have blocked the most
+important staleness notification: $\delta_a$.
 

### 2022-09-15 input/proposal.tex
positioning

@@
     either forwards appropriate staleness notifications (covered by
-    (I)) or detects its possible blocking as follows:
+    (I)) or detects a possible blocking of the latter as follows:
   \item [(iii) $y'$ in $P_x$ with $y$ as parent] but does not deliver
@@
 Figure~\ref{fig:undoproblemF}, false positives would generate traffic
-at $c$ and its children if it had any, without impacting $a$ and $b$.
+at $c$ and in turns, to its children if it had any. Nevertheless, this
+would not affect $a$ nor $b$.
 

### 2022-10-19 RR-9418.tex
meow

@@
 %% maths
-\usepackage{amsmath,amssymb,amsthm,bm}
+\usepackage{amsmath,amssymb,amsthm,bm,centernot}
 %% \usepackage{amsfonts}
@@
 \usepackage[ruled, linesnumbered, noend]{algorithm2e}
+\usepackage{multicol}
 
@@
 %% tables
-\usepackage{booktabs}
-\usepackage{multirow}
+\usepackage{booktabs, tabularx, multirow}
 %% figures
@@
 \usepackage{xspace}
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 
@@
 \newtheorem{definition}{Definition}
+\newtheorem{lemma}{Lemma}
 \newtheorem{theorem}{Theorem}
@@
 \newcommand{\Nodes}{\Processes}
+
+\newcommand{\SCALE}{1} %% used in figures, forces renewcommand for consistent behavior
 
@@
 \RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long
-\titlehead{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français court
+
+\titlehead{\NAME : Lock Down the Traffic of Decentralized Content Indexing at the Edge}
 \RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}
@@
 
+\RRnote{\TODO{This preprint has not undergone peer review (when
+    applicable) or any post-submission improvements or
+    corrections. The Version of Record of this contribution is
+    published in [insert volume title], and is available online at
+    https://doi.org/[insert DOI]}}
+
+%% \RRnote{This version of the contribution has been accepted for
+%%   publication, after peer review (when applicable) but is not the
+%%   Version of Record and does not reflect post-acceptance improvements,
+%%   or any corrections. The Version of Record is available online at:
+%%   http://dx.doi.org/[insert DOI]. Use of this Accepted Version is
+%%   subject to the publisher’s Accepted Manuscript terms of use
+%%   \url{https://www.springernature.com/gp/open-research/policies/accepted-manuscript-terms}}
+
 % \title{\NAME: Lock Down the Traffic\\of Decentralized Content Indexing at the Edge}
@@
 \RRNo{9418}
+
 \makeRR

### 2022-10-19 input/figdel.tex
toward camera ready

@@
 \begin{figure}[t]
-  \newcommand{\SCALE}{0.8}
+  \renewcommand{\SCALE}{0.8}
 
@@
 
-  \newcommand\INVISIBLESPACING{1.6}
+  \newcommand\INVISIBLESPACING{1.55}
   \newcommand\ADD{\alpha}
@@
   \caption{\label{fig:del}Efficient removal of a partition using
-    scoped broadast.} % $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
+    scoped broadcast.} % $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
 \end{figure}

### 2022-10-19 input/figproblem.tex

@@
   \begin{center}
-    \subfloat[Part A][\label{fig:problemA}Both \Process~$a$ and
-      \Process~$d$ add then delete their partition. For the recall,
-      $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
+    \subfloat[Part A][\label{fig:problemA}Both nodes $a$ and $d$ create a
+      new partition.  $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
       3$.]{\input{input/figproblemA.tex}}
     \hspace{0pt}
-    \subfloat[Part B][\label{fig:problemB}$b$
-      delivers and forwards the $\alpha$ message about $P_a$ while
-      \Process~$c$ delivers and forwards both $\alpha$ and $\delta$
-      messages about $P_d$.]  {\input{input/figproblemB.tex}}
+    \subfloat[Part B][\label{fig:problemB}Both $a$ and $d$ delete
+      their partition. $b$ delivers and forwards $\alpha_a$ while
+      $c$ delivers and forwards both $\alpha_d$ and $\delta_d$.]
+             {\input{input/figproblemB.tex}}
     \hspace{0pt}

### 2022-10-19 input/introduction.tex

@@
 %
-To favour this transition, new designs for data management across Edge
+To favor this transition, new designs for data management across Edge
 infrastructures have been investigated~\cite{confais2017object,confais2017performance,fogstore,hasenburg2020towards}.  They
@@
   dissemination of messages as long as receiving \processes verify an
-  application-dependant predicate.
+  application-dependent predicate.
 

### 2022-10-19 input/prooftheoremfb.tex

Whenever a \process~$s$ becomes a source, it broadcasts hence
delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
its set of received messages, it acknowledges that it belongs to its
own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
\noindent Such a source forwards its notification to its neighbors.
Every neighbor eventually receives its notification since
communication links are reliable. Whatever the order of received
messages $R_x$ at neighboring \process~$x$, total order ensures that
it delivers notifications $\alpha_s^{d}$ when
$d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
this case.
\noindent Among these neighbors, at least those that fulfill the
latest condition forward their respective notification.  By
transitivity, the message originating from $s$ reaches all
\processes that belong to $P_s$ at least through their respective
lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
  |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
  d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
quiescent, \ie no \process becomes source anymore, every \process
eventually acknowledges the partition it belongs to, \ie \processes
eventually reach consistent partitioning together. In addition, the
protocol terminates: a \process never delivers hence forwards a
message after it received, delivered, and forwarded the message of
its closest source from its lightest path.

### 2022-10-19 input/prooftheoremfbfsdcp.tex

Detection triggers forwarding of staleness downstream which
completes the case study of Lemma~\ref{lem:detector} by ensuring
that, when a source broadcasts its staleness notification, all
\processes that belong to its partition eventually deliver such a
staleness notification. All downstream bordering \processes also
eventually receive such a staleness notification and echo back their
best delivered message. This triggers another competition as in
Theorem~\ref{theo:fb} for the \processes that delivered the
staleness notification.

### 2022-10-19 input/tablerelatedwork.tex

@@
   \toprule
-
-  Approaches & \multirow{2}{5em}{\centering Without Third-party} & Update & \multirow{2}{3.5em}{Eventually Consistent} & \multirow{2}{5em}{\centering\underline{R}eactive or \underline{C}yclic} \\
-  \\
+  Approaches & Without Third-party & Update & Eventually Consistent & \underline{R}eactive or \underline{C}yclic \\
   \midrule

### 2023-01-12 RR-9418.tex
last update for RR

@@
-\documentclass[twoside]{article}
+\documentclass{article}
 
@@
 
-\RRnote{\TODO{This preprint has not undergone peer review (when
-    applicable) or any post-submission improvements or
-    corrections. The Version of Record of this contribution is
-    published in [insert volume title], and is available online at
-    https://doi.org/[insert DOI]}}
+\RRnote{This preprint has not undergone peer review or any
+  post-submission improvements or corrections. The Version of Record
+  of this contribution is published in \emph{Algorithms and
+  Architectures for Parallel Processing (LNCS volume 13777)}, and is
+  available online at
+  \url{https://doi.org/10.1007/978-3-031-22677-9_23}}
 
@@
 \input{input/conclusion.tex}
-%% \input{input/acknowledgment.tex}
+\input{input/acknowledgements.tex}
 
